### 2021-09-04 talk/talk.tex
A new short talk

\documentclass{beamer}
\usepackage[utf8]{inputenc}
\usepackage[UKenglish]{babel}
\usepackage[UKenglish]{isodate}
\usepackage[style=verbose]{biblatex}
\usepackage{amsmath}
\usepackage{tikz}

\usetikzlibrary{shapes}
\usetikzlibrary{arrows}
\usetikzlibrary{arrows.meta}

\beamertemplatenavigationsymbolsempty
\addbibresource{talk.bib}
\DeclareRobustCommand{\stirling}{\genfrac\{\}{0pt}{}}

\author{Paulius Dilkas}
\title{Symmetric Weighted First-Order Model Counting and Factorial-Like Functions}
\date{}

\begin{document}
\addtobeamertemplate{block begin}{\setlength\abovedisplayskip{0pt}}

\maketitle

\begin{frame}{WFOMC: State of the Art}
  I'm excluding techniques that are restricted to two variables and purely
  theoretical results.
  \begin{enumerate}
  \item \cite{DBLP:conf/nips/KazemiKBP16}
    \begin{itemize}
    \item generic domain recursion (implementation unavailable)
    \end{itemize}
  \item \alert{Forclift}: \cite{DBLP:conf/ijcai/BroeckTMDR11}
    \begin{itemize}
    \item somewhat restrictive but well-developed
    \end{itemize}
  \item \alert{L2C}: \cite{DBLP:conf/kr/KazemiP16}
    \begin{itemize}
    \item very basic
    \end{itemize}
  \item \alert{Alchemy}: \cite{DBLP:conf/aaai/DomingosKPRS06}
    \begin{itemize}
    \item old, mostly focused on approximations
    \end{itemize}
  \end{enumerate}
\end{frame}

\begin{frame}{Counting (Unweighted) Functions: Currently Unliftable (1)}
  \cite{stanley2011enumerative}
  \begin{block}{Functions $M \to N$ (let $|M| = m$ and $|N| = n$)}
    Theory:
    \begin{align*}
      \forall x \in M. \forall y, z \in N. &P(x, y) \land P(x, z) \Rightarrow y=z \\
      \forall x \in M. \exists y \in N. &P(x, y)
    \end{align*}
    Answer: $n^m$.
  \end{block}
  \begin{block}{Injections}
    Theory:
    \begin{align*}
      \forall x \in M. \forall y, z \in N. &P(x, y) \land P(x, z) \Rightarrow y=z \\
      \forall x \in M. \exists y \in N. &P(x, y) \\
      \alert{\forall w, x \in M. \forall y \in N.} &\alert{P(w, y) \land P(x, y) \Rightarrow w=x}
    \end{align*}
    Answer: $(n)_m = n \cdot (n-1)\cdots(n-m+1)$.
  \end{block}
\end{frame}

\begin{frame}{Counting (Unweighted) Functions: Currently Unliftable (2)}
  \begin{block}{Surjections}
    Theory:
    \begin{align*}
      \forall x \in M. \forall y, z \in N. &P(x, y) \land P(x, z) \Rightarrow y=z \\
      \forall x \in M. \exists y \in N. &P(x, y) \\
      \alert{\forall y \in N. \exists x \in M.} &\alert{P(x, y)}
    \end{align*}
    Answer: $n!\stirling{m}{n} = \sum_{i=0}^n (-1)^i\binom{n}{i}(n-i)^m$.
  \end{block}
  \begin{block}{Bijections}
    Theory:
    \begin{align*}
      \forall x \in M. \forall y, z \in N. &P(x, y) \land P(x, z) \Rightarrow y=z \\
      \forall x \in M. \exists y \in N. &P(x, y) \\
      \alert{\forall w, x \in M. \forall y \in N.} &\alert{P(w, y) \land P(x, y) \Rightarrow w=x} \\
      \alert{\forall y \in N. \exists x \in M.} &\alert{P(x, y)}
    \end{align*}
    Answer: $n!$ if $m=n$.
  \end{block}
\end{frame}

\begin{frame}{Counting (Unweighted) Functions: Currently Unliftable (3)}
  These ones could contain errors.
  \begin{block}{Partial functions}
    Theory: $\forall x \in M. \forall y, z \in N. P(x, y) \land P(x, z)
    \Rightarrow y=z$

    Answer: $(n+1)^m$.
  \end{block}
  \begin{block}{Partial injections}
    Theory:
    \begin{align*}
      \forall x \in M. \forall y, z \in N. &P(x, y) \land P(x, z) \Rightarrow y=z \\
      \forall w, x \in M. \forall y \in N. &P(w, y) \land P(x, y) \Rightarrow w=x
    \end{align*}
    Answer: $\sum_{k=0}^{\min\{m, n\}} k!\binom{m}{k}\binom{n}{k}$.
  \end{block}
\end{frame}

\begin{frame}{Conceptual Plan of Action}
  \centering
  \begin{tikzpicture}[triangle/.style = {regular polygon, regular polygon sides=3}]
    \node[draw,ellipse] (a) at (0, 0) {$\phi(n)$};
    \node[draw,ellipse] (b) at (0, -2) {$\psi(n-1)$};
    \node[draw,ellipse] (c) at (-1, -4) {$\phi(n-1)$};
    \node[draw,triangle] (d) at (1, -4) {};
    \draw[-{Latex[length=2mm]}] (a) -- (b) node [midway,xshift=50] {domain recursion};
    \draw[-{Latex[length=2mm]}] (b) -- (c);
    \draw[-{Latex[length=2mm]}] (b) -- (d);
    \draw[-{Latex[length=2mm]}] (c) to [bend left=45] node [midway,xshift=-30] () {$n \mapsto n-1$} (a);
  \end{tikzpicture}
\end{frame}

\begin{frame}{Remarks on the Implementation}
  \begin{itemize}
  \item WMC computation now loops over the graph.
  \item We propagate information (e.g., for smoothing) in reverse until convergence.
  \item Need a good way to recognise equivalent/isomorphic theories.
  \item Need to be careful about the order of operations:
    \begin{itemize}
    \item Create a (half-empty) vertex $v$.
    \item Add it to the cache.
    \item Recurse on its direct successors $S$.
    \item Add the edges from $v$ to $S$.
    \item After the graph is constructed, propagate information through the
      graph that would otherwise cause infinite loops.
    \end{itemize}
  \end{itemize}
\end{frame}

\end{document}

### 2021-10-05 example.py
Fix a bug with domain size reduction. Partial injection counting now works!

@@ -1,12 +1,11 @@
 import math
 
-def f(n):
-    return (sum(math.comb(n, k) * math.comb(n, m) * 2**(n*(k+m)-k*m) for k in range(n+1) for m in range(n+1)))**n
+def my_partial_injections(m, n):
+    return sum(math.factorial(k) * math.comb(m, k) * math.comb(n, k) for k in range(min(m, n) + 1))
 
-def g(n):
-    return (4**n + 2**(n+1) + 3**n)**n
+def forclift_partial_injections(m, n):
+    return 1 if m == 0 else sum(math.comb(n, k) * forclift_partial_injections(m-1, n-k) for k in range(min(n, 1) + 1))
 
-print(g(1))
-print(g(2))
-print(g(3))
-
+for m in range(1, 5):
+    for n in range(1, 5):
+        print("m =", m, ", n =", n, "mine =", my_partial_injections(m, n), ", forclift =", forclift_partial_injections(m, n))

### 2021-10-06 talk/talk.tex
Fix a bug with domain size reduction. Partial injection counting now works!
Injection counting (but exponential...)

@@
     \end{align*}
-    Answer: $(n)_m = n \cdot (n-1)\cdots(n-m+1)$.
+    Answer: $n^{\underline{m}} = n \cdot (n-1)\cdots(n-m+1)$ if $m \le n$ and $0$ otherwise (for positive $m$ and $n$).
   \end{block}
@@
 \begin{frame}{Counting (Unweighted) Functions: Currently Unliftable (3)}
-  These ones could contain errors.
   \begin{block}{Partial functions}
@@
     \end{align*}
-    Answer: $\sum_{k=0}^{\min\{m, n\}} k!\binom{m}{k}\binom{n}{k}$.
+    My answer: $\sum_{k=0}^{\min\{m, n\}} k!\binom{m}{k}\binom{n}{k}$.
+
+    \pause
+    \alert{Answer found by Forclift:}
+    \[
+    f(m, n) =
+    \begin{cases}
+      1 & \text{if } m = 0 \\
+      \sum_{k=0}^n \binom{n}{k} [k < 2] f(m-1, k) & \text{otherwise.}
+    \end{cases}
+    \]
+    (exponential...)
   \end{block}

### 2021-10-06 example.py

@@ -6,6 +6,22 @@ def my_partial_injections(m, n):
 def forclift_partial_injections(m, n):
     return 1 if m == 0 else sum(math.comb(n, k) * forclift_partial_injections(m-1, n-k) for k in range(min(n, 1) + 1))
 
+# for m in range(1, 5):
+#     for n in range(1, 5):
+#         print("m =", m, ", n =", n, "mine =", my_partial_injections(m, n), ", forclift =", forclift_partial_injections(m, n))
+
+def injections(m, n):
+    return sum(math.comb(m, k) * (-1)**(m-k) * injections2(k, n) for k in range(m + 1))
+
+def injections2(k, n):
+    return 1 if k == 0 else injections2(k-1, n) + n * injections2(k-1, n-1)
+
+
 for m in range(1, 5):
     for n in range(1, 5):
-        print("m =", m, ", n =", n, "mine =", my_partial_injections(m, n), ", forclift =", forclift_partial_injections(m, n))
+        print("f({}, {}) = {}".format(m, n, injections(m, n)))
+
+print()
+for m in range(5):
+    for n in range(5):
+        print("g({}, {}) = {}".format(m, n, injections2(m, n)))

### 2021-10-17 talk/talk.tex
Make the greedy search code more flexible in preparation for breadth-first search
A barebones implementation of breadth-first search

@@
 \author{Paulius Dilkas}
-\title{Symmetric Weighted First-Order Model Counting and Factorial-Like Functions}
+\title{Empowering (Domain) Recursion in Symmetric Weighted First-Order Model Counting}
 \date{}
@@
 \begin{frame}{Counting (Unweighted) Functions: Currently Unliftable (1)}
-  \cite{stanley2011enumerative}
-  \begin{block}{Functions $M \to N$ (let $|M| = m$ and $|N| = n$)}
-    Theory:
-    \begin{align*}
-      \forall x \in M. \forall y, z \in N. &P(x, y) \land P(x, z) \Rightarrow y=z \\
-      \forall x \in M. \exists y \in N. &P(x, y)
-    \end{align*}
-    Answer: $n^m$.
-  \end{block}
+  %% \cite{stanley2011enumerative}
+  %% \begin{block}{Functions $M \to N$ (let $|M| = m$ and $|N| = n$)}
+  %%   Theory:
+  %%   \begin{align*}
+  %%     \forall x \in M. \forall y, z \in N. &P(x, y) \land P(x, z) \Rightarrow y=z \\
+  %%     \forall x \in M. \exists y \in N. &P(x, y)
+  %%   \end{align*}
+  %%   Answer: $n^m$.
+  %% \end{block}
   \begin{block}{Injections}
@@
       \forall x \in M. \exists y \in N. &P(x, y) \\
-      \alert{\forall w, x \in M. \forall y \in N.} &\alert{P(w, y) \land P(x, y) \Rightarrow w=x}
+      \forall w, x \in M. \forall y \in N. &P(w, y) \land P(x, y) \Rightarrow w=x
     \end{align*}
     Answer: $n^{\underline{m}} = n \cdot (n-1)\cdots(n-m+1)$ if $m \le n$ and $0$ otherwise (for positive $m$ and $n$).
+
+    \pause
+    \alert{Answer found by Forclift:}
+    \[
+    f(m, n) = \sum_{k=0}^m \binom{m}{k}(-1)^{m-k}g(k, n),
+    \]
+    where
+    \[
+    g(k, n) =
+    \begin{cases}
+      1 & \text{if } k = 0 \\
+      \sum_{l=0}^n [l < 2]g(k-1, n-l) & \text{otherwise.}
+    \end{cases}
+    \]
+    (exponential...)
   \end{block}
@@
 
+\begin{frame}{Domain Size Comparisons}
+  \begin{block}{$|N| < 2$ (Forclift can already do this!)}
+    \[
+    \phi \equiv \forall x, y \in N \text{ s.t. } x \ne y\text{, } P,
+    \]
+    where $w(P) = 0$. The algebraic (multiplicative) contribution of $\phi$ is $w(P)^{\mathrm{gr}(\phi)}$.
+    \begin{itemize}
+    \item If $|N| \ge 2$, then $\mathrm{gr}(\phi) > 0$, and so $0^{\mathrm{gr}(\phi)} = 0$.
+    \item If $|N| < 2$, then we get $0^0 = 1$.
+    \item Of course, 2 can be replaced by any other positive integer.
+    \end{itemize}
+  \end{block}
+  \pause
+  \begin{block}{$m < n$ (possible, but a bit complicated)}
+    \[
+    f(m, n) = \begin{cases}
+      0 & \text{if } n = 0 \\
+      1 & \text{if } m = 0 \text{ and } n > 0 \\
+      f(m-1, n-1) & \text{otherwise.}
+    \end{cases}
+    \]
+  \end{block}
+\end{frame}
+
 \end{document}

### 2021-12-27 talk/talk.tex
First implementation of (working?) breadth-first search

@@
 \usepackage{amsmath}
+\usepackage{mathtools}
 \usepackage{tikz}
+
+\usetheme{CambridgeUS}
 
@@
 \author{Paulius Dilkas}
-\title{Empowering (Domain) Recursion in Symmetric Weighted First-Order Model Counting}
+\title[Empowering Domain Recursion]{Empowering Domain Recursion in Symmetric Weighted First-Order Model Counting}
 \date{}
@@
 \maketitle
+
+\begin{frame}{Overview}
+  \begin{block}{Hypothesis}
+    Partial injections can be counted in polynomial time using (a modification of) \textsc{ForcLift}.
+  \end{block}
+  \begin{block}{Key Ideas \& Progress}
+    \begin{itemize}
+    \item[\textcolor{green}{100\%}] Support for cycles in circuits
+    \item[\textcolor{green}{95\%}] Transforming $X \ne x$ constraints into domain reductions $\Delta' \coloneqq \Delta \setminus \{ x \}$
+    \item[\textcolor{green}{95\%}] A less restrictive version of domain recursion
+    \item[\textcolor{orange}{90\%}] A hybrid search algorithm
+    \item[\textcolor{red}{0\%}] Complexity identification
+    \end{itemize}
+  \end{block}
+\end{frame}
+
+\begin{frame}{Search}
+  \begin{definition}
+    A \alert{partial solution} (i.e., a search node) is a tuple consisting of:
+    \begin{itemize}
+    \item a partial circuit, i.e., a \textsc{ForcLift}-style DAG,
+      \begin{itemize}
+      \item Each node type has a predefined out-degree.
+      \item Some of them may be `arcs to nothing'.
+      \end{itemize}
+    \item a cache (i.e., a formula $\to$ node hashmap), used to identify opportunities for recursion,
+    \item a list of formulas that still need to be compiled, listed in a particular order.
+    \end{itemize}
+  \end{definition}
+  % Sink and non-sink rules
+\end{frame}
+
+\begin{frame}{Search}
+  Some rules are applied in a greedy manner:
+  \begin{itemize}
+  \item identifying the current formula as something that's already been compiled using the cache;
+  \item sink nodes: tautologies, contradictions, unit clauses;
+  \item some formula-simplifying rules;
+  \item unit propagation.
+  \end{itemize}
+  And some rules are used to branch out into several possibilities:
+  \begin{itemize}
+  \item independent subtheories,
+  \item shattering,
+  \item ground decomposition,
+  \item inclusion-exclusion,
+  \item independent partial grounding,
+  \item counting,
+  \item (my version of) domain recursion.
+  \end{itemize}
+\end{frame}
 

### 2022-01-10 notes/notes.tex
Some writing + make identifyRecursion more efficient

\documentclass{article}
\usepackage[UKenglish]{babel}
\usepackage[UKenglish]{isodate}
\usepackage[utf8]{inputenc}
\usepackage{fullpage}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{mathrsfs}
\usepackage{oz}
\usepackage[ruled,vlined]{algorithm2e}

\theoremstyle{definition}
\newtheorem{definition}{Definition}
\newtheorem{example}{Example}

\DeclareMathOperator{\Imm}{Im}
\DeclareMathOperator{\Doms}{Doms}
\DeclareMathOperator{\Vars}{Vars}
\DeclareMathOperator{\WMC}{WMC}

\title{Empowering Domain Recursion in Symmetric Weighted First-Order Model Counting}

\begin{document}
\maketitle

\section{Basic Definitions}
% TODO (later): maybe mathcal instead of mathscr

\paragraph{Things I might need to explain.}
\begin{itemize}
\item notation: $\Imm$
\item atom
\item inequality constraint
\item $\Vars$, $\Vars(c) = \Vars(P) \cup \Vars(N) \cup \Vars(C)$
\item $\Doms$ on both formulas and clauses. $\Doms(c) = \Imm \delta$, and $\Doms(\phi) = \bigcup_{c \in \phi} \Doms(c)$.
\item the hash codes of clauses and formulas. Introduce the $\#$ notation.
\item substitution
\item (strict) equality of clauses. It's important to mention that we check the number of variables but not their domains.
\item size of a domain, how each domain is partitioned into two, and how we iterate over all possible integer partitions of length two.
\item maybe: endomorphism, notation for partial function, notation for powerset
\end{itemize}

Let $\mathscr{V}$ be the set of circuit nodes.

TODO: merge $\kappa$ and $\iota$ into one.

\begin{definition}
  A \emph{domain} is a set with elements not used anywhere else.\footnote{In the context of functions, the domain of a function $f$ retains its usual meaning and is denoted $\dom(f)$.} Let $\mathscr{D}$ be the set of all domains (note that this set expands during compilation).

  We now define two partial maps $\pi$ and $\kappa$ with the same domain $\dom(\pi) = \dom(\kappa) \subset \mathscr{D}$. First, let $\pi\colon \mathscr{D} \pfun \mathscr{D}$ be a partial endomorphism on $\mathscr{D}$ that denotes the \emph{parent} relation, i.e., if $\pi(d) = e$ for some $d, e \in \mathscr{D}$, then we call $e$ the parent (domain) of $d$, and $e$ a child of $d$. Intuitively, $\pi$ arranges all domains into a forest. Second, let $\kappa\colon \mathscr{D} \pfun \mathscr{V}$ be a partial map that assigns a \emph{cause node} to all non-root domains. Third, let $\iota\colon \mathscr{D} \pfun \{\, 0, 1 \,\}$ unambiguously order the children of any internal node, i.e., $\iota(d) \ne \iota(e)$ whenever $\pi(d) = \pi(e)$ for any $d, e \in \mathscr{D}$.\footnote{Here, each internal node has at most two children.}
\end{definition}

\begin{definition}
  A \emph{clause} is a triple $c = (P, N, C, \delta)$, where $P$ and $N$ are sets of atoms interpreted as positive and negative literals respectively, $C$ is a set of inequality constraints, and $\delta\colon \Vars(c) \to \mathscr{D}$ is a function that maps all variables in $c$ to their domains. Two clauses $c$ and $d = (P', N', C', \delta')$ are \emph{equivalent} (written $c \equiv d$) if there is a bijection $\beta\colon \Vars(c) \to \Vars(d)$ such that $c\beta = d\beta$.
\end{definition}

A \emph{formula} is a set of clauses.

\section{Identifying Possibilities for Recursion}

For succinctness, let $\mathscr{S} = \mathscr{D} \times \mathscr{D} \times 2^{\mathscr{V} \times \{\, 0, 1 \,\}}$. TODO: explain the idea.

Let $\nu\colon \mathscr{S} \to 2^{\mathscr{S}}$ be a map defined as
\[
\nu(a, b, S) =
\begin{cases}
  \{\,(\pi(a), b, S \cup \{\, \kappa(a) \,\})\,\} & \text{if } a \in \dom(\pi) \\
  \emptyset & \text{if } a \not\in \dom(\pi)
\end{cases}
\]
for all $(a, b, S) \in \mathscr{S}$. Furthermore, let $\nu'\colon 2^{\mathscr{S}} \to 2^{\mathscr{S}}$ be an endomorphism defined as $\nu'(S) = \bigcup_{s \in S} \nu(s)$ for all $S \subseteq \mathscr{S}$.

% TODO: postprocess will be part of the main algorithm.
\begin{algorithm}
  \caption{A recursive function for checking whether one can reuse the circuit for computing $\WMC(\psi)$ to compute $\WMC(\phi)$. Both $\phi$ and $\psi$ are formulas, and $\rho\colon \Doms(\phi) \protect\pfun \Doms(\psi)$ is a partial map.}
  \SetKwProg{Fn}{Function}{:}{}
  \SetKwFunction{identifyRecursion}{identifyRecursion}
  \Fn{\identifyRecursion{$\phi$, $\psi$, $\rho = \emptyset$}}{
    \lIf{$|\phi| \ne |\psi|$ {\bf or} $\#\phi \ne \#\psi$}{TODO: none}
    \uElseIf{$\phi = \emptyset$}{
      TODO
    }
    \Else{
      TODO
    }
  }
\end{algorithm}

\begin{example}
  % TODO: Need a good example.
  Let...
\end{example}

\end{document}

### 2022-01-13 notes/notes.tex
Make the algorithm more robust to incomplete implementations and unexpectedly easy inputs

@@
 \usepackage{oz}
-\usepackage[ruled,vlined]{algorithm2e}
+\usepackage[linesnumbered,ruled,vlined]{algorithm2e}
+\usepackage{tikz}
+\usepackage[capitalize]{cleveref}
+
+\usetikzlibrary{arrows,fit,positioning,trees}
 
@@
 \item $\Vars$, $\Vars(c) = \Vars(P) \cup \Vars(N) \cup \Vars(C)$
-\item $\Doms$ on both formulas and clauses. $\Doms(c) = \Imm \delta$, and $\Doms(\phi) = \bigcup_{c \in \phi} \Doms(c)$.
+\item $\Doms$ on both formulas and clauses. $\Doms(c) = \Imm \delta_c$, and $\Doms(\phi) = \bigcup_{c \in \phi} \Doms(c)$.
 \item the hash codes of clauses and formulas. Introduce the $\#$ notation.
@@
 \item size of a domain, how each domain is partitioned into two, and how we iterate over all possible integer partitions of length two.
-\item maybe: endomorphism, notation for partial function, notation for powerset
+\item maybe: notation for partial function, notation for powerset
+\item notation for projection (or avoid it?)
+\item $\WMC$
 \end{itemize}
@@
 
+TODO: maybe $\pi$ and $\kappa$ are global enough to have more unique names.
+
 \begin{definition}
@@
 First, let $\pi\colon \mathscr{D} \pfun \mathscr{D}$ be a partial endomorphism on $\mathscr{D}$ that denotes the \emph{parent} relation, i.e., if $\pi(d) = e$ for some $d, e \in \mathscr{D}$, then we call $e$ the parent (domain) of $d$, and $e$ a child of $d$.
-Intuitively, $\pi$ arranges all domains into a forest.
+Intuitively, $\pi$ arranges all domains into a forest---thus, we often use graph theoretical terminology to describe properties of and relationships between domains.
 Second, let $\kappa\colon \mathscr{D} \pfun \mathscr{V}$ be a partial map that assigns a \emph{cause node} to all non-root domains.
@@
 \begin{definition}
-  A \emph{clause} is a triple $c = (P, N, C, \delta)$, where $P$ and $N$ are sets of atoms interpreted as positive and negative literals respectively, $C$ is a set of inequality constraints, and $\delta\colon \Vars(c) \to \mathscr{D}$ is a function that maps all variables in $c$ to their domains.
-Two clauses $c$ and $d = (P', N', C', \delta')$ are \emph{equivalent} (written $c \equiv d$) if there is a bijection $\beta\colon \Vars(c) \to \Vars(d)$ such that $c\beta = d\beta$.
+  A \emph{clause} is a triple $c = (P, N, C, \delta_c)$, where $P$ and $N$ are sets of atoms interpreted as positive and negative literals respectively, $C$ is a set of inequality constraints, and $\delta_c\colon \Vars(c) \to \mathscr{D}$ is a function that maps all variables in $c$ to their domains.
+Two clauses $c$ and $d = (P', N', C', \delta_d)$ are \emph{equivalent} (written $c \equiv d$) if there is a bijection $\beta\colon \Vars(c) \to \Vars(d)$ such that $c\beta = d\beta$.
+TODO: we will always use this subscript notation for the $\delta$'s.
 \end{definition}
@@
 
-For succinctness, let $\mathscr{S} = \mathscr{D} \times \mathscr{D} \times 2^{\mathscr{V} \times \{\, 0, 1 \,\}}$. TODO: explain the idea.
+%% For succinctness, let $\mathscr{S} = \mathscr{D} \times \mathscr{D} \times 2^{\mathscr{V} \times \{\, 0, 1 \,\}}$.
 
-Let $\nu\colon \mathscr{S} \to 2^{\mathscr{S}}$ be a map defined as
-\[
-\nu(a, b, S) =
-\begin{cases}
-  \{\,(\pi(a), b, S \cup \{\, \kappa(a) \,\})\,\} & \text{if } a \in \dom(\pi) \\
-  \emptyset & \text{if } a \not\in \dom(\pi)
-\end{cases}
-\]
-for all $(a, b, S) \in \mathscr{S}$.
+%% Let $\nu\colon \mathscr{S} \to 2^{\mathscr{S}}$ be a map defined as
+%% \[
+%% \nu(a, b, S) =
+%% \begin{cases}
+%%   \{\,(\pi(a), b, S \cup \{\, \kappa(a) \,\})\,\} & \text{if } a \in \dom(\pi) \\
+%%   \emptyset & \text{if } a \not\in \dom(\pi)
+%% \end{cases}
+%% \]
+%% for all $(a, b, S) \in \mathscr{S}$.
 Furthermore, let $\nu'\colon 2^{\mathscr{S}} \to 2^{\mathscr{S}}$ be an endomorphism defined as $\nu'(S) = \bigcup_{s \in S} \nu(s)$ for all $S \subseteq \mathscr{S}$.
 
-% TODO: postprocess will be part of the main algorithm.
-\begin{algorithm}
+\begin{algorithm}[t]
   \caption{A recursive function for checking whether one can reuse the circuit for computing $\WMC(\psi)$ to compute $\WMC(\phi)$.
-Both $\phi$ and $\psi$ are formulas, and $\rho\colon \Doms(\phi) \protect\pfun \Doms(\psi)$ is a partial map.}
+Both $\phi$ and $\psi$ are formulas, and $\rho\colon \Doms(\phi) \protect\pfun \Doms(\psi) \times 2^{\mathscr{V} \times \{\, 0, 1 \,\}}$ is a partial map.
+TODO: explain more about $\rho$.}
   \SetKwProg{Fn}{Function}{:}{}
   \SetKwFunction{identifyRecursion}{identifyRecursion}
+  \SetKwFunction{findHistory}{findHistory}
+  \SetKwData{suitable}{suitable}
   \Fn{\identifyRecursion{$\phi$, $\psi$, $\rho = \emptyset$}}{
-    \lIf{$|\phi| \ne |\psi|$ {\bf or} $\#\phi \ne \#\psi$}{TODO: none}
-    \uElseIf{$\phi = \emptyset$}{
-      TODO
+    \lIf{$\phi = \psi = \emptyset$}{\Return{$\rho$}}
+    \lIf{$|\phi| \ne |\psi|$ {\bf or} $\#\phi \ne \#\psi$}{\Return{\normalfont \texttt{null}}}
+    \ForEach{clause $c \in \phi$}{
+      \ForEach{clause $d \in \psi$ such that $\#d = \#c$} {
+        \ForEach{bijection $\beta\colon \Vars(c) \to \Vars(d)$}{
+          $\suitable \gets {\normalfont \texttt{true}}$\;
+          \If{$\forall v \in \Vars(c). (\delta_c(v) \not\in {\normalfont \dom}(\rho) \lor \pi_1(\rho(\delta_c(v))) = \delta_d(\beta(v)))$ {\bf and} $c\beta = d$}{
+            $\rho' \gets \rho$\;
+            \ForEach{$v \in \Vars(c)$}{
+              $H \gets \findHistory{$\delta_c(v)$, $\delta_d(\beta(v))$}$\;
+              \If{$H = {\normalfont \texttt{null}}$}{
+                $\suitable \gets {\normalfont \texttt{false}}$\;
+                break\;
               }
-    \Else{
-      TODO
+              $\rho' \gets \rho \cup \{\, \delta_c(v) \mapsto (\delta_d(\beta(v)), H) \,\}$\;
             }
+            \If{\suitable}{
+              $\rho'' \gets \identifyRecursion{$\phi \setminus \{\, c \,\}$, $\psi \setminus \{\, d \,\}$, $\rho'$}$\;
+              \lIf{$\rho'' \ne {\normalfont \texttt{null}}$}{\Return{$\rho''$}}
+            }
+          }
+        }
+      }
+      \Return{\normalfont \texttt{null}}\;
+    }
+  }
+  \Fn{\findHistory{$c$, $d$}}{
+    $H \gets \emptyset$\;
+    \While{$d \ne c$ {\bf and} $d \in {\normalfont \dom}(\pi)$}{
+      $H \gets H \cup \{\, \kappa(d) \,\}$\;
+      $d \gets \pi(d)$\;
+    }
+    \lIf{$d = c$}{\Return{$H$}}
+    \Return{\normalfont \texttt{null}}\;
   }
@@
 
+\begin{figure}[t]
+  \centering
+  \begin{tikzpicture}[edge from parent/.style={draw,-latex}]
+    \node[draw,circle,fill=violet!10] (circuit) {} child {
+      node[draw,circle,fill=violet!10] (bmaker) {$\diamondsuit$}
+      child {node[draw,circle,fill=violet!10] {}
+        child {node[draw,circle,fill=violet!10] {}}
+        child {node[draw,circle,fill=violet!10] {}
+          child {node[draw,circle,fill=violet!10] {}}
+          child {node[draw,circle,fill=violet!10] {}
+            child {node[draw,circle,fill=violet!10] {}}
+            child {node[draw,circle,fill=violet!10] (amaker) {$\heartsuit$}
+              child {node[draw,circle,fill=violet!10] (ref) {}
+                child {node[draw,circle,fill=violet!10] {}}
+              }
+            }
+          }
+        }
+      }
+    };
+    \node[below right=1cm and 2cm of circuit] (a) {$a$} child {node (aprime) {$a'$}};
+    \node[right=1 cm of a] (b) {$b$}
+    child {node (btop) {$b^\top$}}
+    child {node (bbot) {$b^\bot$}};
+    \node[draw,fit=(a) (aprime) (b) (btop) (bbot)] {};
+    \draw[-latex] (ref) edge[densely dotted,bend left=90] (circuit);
+    \draw[-latex,color=teal] (aprime) edge[densely dashed] node[xshift=2mm,color=teal] {$0$} (amaker);
+    \draw[-latex,color=teal] (btop) edge[bend left=50,densely dashed] node[xshift=6mm,color=teal] {$0$} (bmaker);
+    \draw[-latex,color=teal] (bbot) edge[bend left=50,densely dashed] node[yshift=-2mm,color=teal] {$1$} (bmaker);
+  \end{tikzpicture}
+  \caption{A circuit (outside the box) and a forest of domains (inside the box).
+The dotted line on the left will be added if \texttt{identifyRecursion} returns a non-\texttt{null} mapping.
+The dashed edges with their labels represent the $\kappa$ function.
+The circuit nodes with symbols in them are the nodes that introduce new (sub)domains.}
+  \label{fig:example}
+\end{figure}
+
+TODO: explain what the second return statement is about and why a third one is not necessary.
+
+TODO: mention which one is the main function, what each function takes and returns.
+
 \begin{example}
-  % TODO: Need a good example.
-  Let...
+  TODO: explain how the algorithm establishes a recursive relationship from
+  % 1. formulas (both the Forclift representation and the more normal way to write down the same thing)
+  % 2. definitions of delta_c, delta_d, kappa, pi
+  \begin{align*}
+    \forall X \in a'. \forall Y \in b^\bot. \forall Z \in b^\bot. Z \ne Y &\implies \neg p(X, Y) \lor \neg p(X, Z) \\
+    \forall X \in a'. \forall Y \in b^\bot. \forall Z \in a'. X \ne Z &\implies \neg p(X, Y) \lor \neg p(Z, Y)
+  \end{align*}
+  to
+  \begin{align*}
+    \forall X \in a. \forall Y \in b. \forall Z \in b. Y \ne Z &\implies \neg p(X, Y) \lor \neg p(X, Z) \\
+    \forall X \in a. \forall Y \in b. \forall Z \in a. X \ne Z &\implies \neg p(X, Y) \lor \neg p(Z, Y)
+  \end{align*}
+  and mention \cref{fig:example}. Solution map (stored as the edge label):
+  \begin{align*}
+    \rho(a') &= (a, \{\, (\diamondsuit, 0) \,\}) \\
+    \rho(b^\bot) &= (b, \{\, (\heartsuit, 1) \,\})
+  \end{align*}
 \end{example}
 
+TODO: conclude with a description of the inference rule and the node/edge type.
+
+\section{New Node Types}
+
+\subsection{Improved Domain Recursion}
+
+The original version of domain recursion is here \cite{DBLP:conf/nips/Broeck11}.
+
+\subsection{Constraint Removal}
+
+\section{Other Topics}
+
+\begin{itemize}
+\item domains, smoothing, and avoiding infinite cycles
+\item new rules that don't create nodes (e.g., duplicate removal, unconditional contradiction detection, etc.)
+\end{itemize}
+
+\section{Circuit Evaluation}
+
+TODO: new node types, their algebraic/graphical representation, what info they hold, and how they're created.
+
+TODO: describe evaluation of: and, counting, constraint removal, ref, unit, contradiction, improved domain recursion. Most of this will be from \cite{DBLP:conf/ijcai/BroeckTMDR11}.
+
+\bibliographystyle{acm}
+\bibliography{notes}
+
 \end{document}

### 2022-01-19 notes/notes.tex
Make code and pseudocode match

@@
 \usepackage{fullpage}
-\usepackage{amsmath}
+
+\usepackage{mathtools}
 \usepackage{amsthm}
 \usepackage{mathrsfs}
-\usepackage{oz}
+
 \usepackage[linesnumbered,ruled,vlined]{algorithm2e}
@@
 
-\usetikzlibrary{arrows,fit,positioning,trees}
+\usetikzlibrary{arrows,fit,positioning,trees,cd}
 
@@
 
+\newcommand\pfun{\mathrel{\ooalign{\hfil$\mapstochar\mkern5mu$\hfil\cr$\to$\cr}}}
+
+\DeclareMathOperator{\dom}{dom}
 \DeclareMathOperator{\Imm}{Im}
@@
 \section{Basic Definitions}
-% TODO (later): maybe mathcal instead of mathscr
+ TODO (later): maybe mathcal instead of mathscr
 
@@
 \item notation: $\Imm$
-\item atom
+\item atom, literal
 \item inequality constraint
@@
 \item substitution
-\item (strict) equality of clauses. It's important to mention that we check the number of variables but not their domains.
-\item size of a domain, how each domain is partitioned into two, and how we iterate over all possible integer partitions of length two.
-\item maybe: notation for partial function, notation for powerset
+\item size of a domain, how each domain is partitioned into two during compilation.
+\item maybe: notation for partial function, notation for powerset, domain size
 \item notation for projection (or avoid it?)
 \item $\WMC$
+\item constraint removal operation
+\item two parts: compilation and inference.
+\item introduce and use arrows for bijections, injections, set inclusions, etc.
+\item $\emptyset$ for an empty partial map.
 \end{itemize}
@@
 
-TODO: merge $\kappa$ and $\iota$ into one.
-
-TODO: maybe $\pi$ and $\kappa$ are global enough to have more unique names.
+TODO: maybe $\pi$ is global enough to have a more unique name.
 
 \begin{definition}
-  A \emph{domain} is a set with elements not used anywhere else.\footnote{In the context of functions, the domain of a function $f$ retains its usual meaning and is denoted $\dom(f)$.} Let $\mathscr{D}$ be the set of all domains (note that this set expands during compilation).
+  A \emph{domain} is a set with elements not used anywhere else.\footnote{In the context of functions, the domain of a function $f$ retains its usual meaning and is denoted $\dom(f)$.} Let $\mathscr{D}$ be the set of all domains and $\mathscr{C} \subset \mathscr{D}$ be the subset of domains introduced as a consequence of constraint removal.
+Note that both sets (can) expand during the compilation phase.
 
-  We now define two partial maps $\pi$ and $\kappa$ with the same domain $\dom(\pi) = \dom(\kappa) \subset \mathscr{D}$.
-First, let $\pi\colon \mathscr{D} \pfun \mathscr{D}$ be a partial endomorphism on $\mathscr{D}$ that denotes the \emph{parent} relation, i.e., if $\pi(d) = e$ for some $d, e \in \mathscr{D}$, then we call $e$ the parent (domain) of $d$, and $e$ a child of $d$.
+Let $\pi\colon \mathscr{D} \pfun \mathscr{D}$ be a partial endomorphism on $\mathscr{D}$ that denotes the \emph{parent} relation, i.e., if $\pi(d) = e$ for some $d, e \in \mathscr{D}$, then we call $e$ the parent (domain) of $d$, and $e$ a child of $d$.
 Intuitively, $\pi$ arranges all domains into a forest---thus, we often use graph theoretical terminology to describe properties of and relationships between domains.
-Second, let $\kappa\colon \mathscr{D} \pfun \mathscr{V}$ be a partial map that assigns a \emph{cause node} to all non-root domains.
-Third, let $\iota\colon \mathscr{D} \pfun \{\, 0, 1 \,\}$ unambiguously order the children of any internal node, i.e., $\iota(d) \ne \iota(e)$ whenever $\pi(d) = \pi(e)$ for any $d, e \in \mathscr{D}$.\footnote{Here, each internal node has at most two children.}
 \end{definition}
@@
   A \emph{clause} is a triple $c = (P, N, C, \delta_c)$, where $P$ and $N$ are sets of atoms interpreted as positive and negative literals respectively, $C$ is a set of inequality constraints, and $\delta_c\colon \Vars(c) \to \mathscr{D}$ is a function that maps all variables in $c$ to their domains.
-Two clauses $c$ and $d = (P', N', C', \delta_d)$ are \emph{equivalent} (written $c \equiv d$) if there is a bijection $\beta\colon \Vars(c) \to \Vars(d)$ such that $c\beta = d\beta$.
+Two clauses $c$ and $d = (P', N', C', \delta_d)$ are \emph{isomorphic} (written $c \cong d$) if there is a bijection $\beta\colon \Vars(c) \to \Vars(d)$ such that $c\beta = d\beta$.
 TODO: we will always use this subscript notation for the $\delta$'s.
+Equality of clauses is defined in the usual way (i.e., all variables, domains, etc.
+must match).
 \end{definition}
@@
 
-%% For succinctness, let $\mathscr{S} = \mathscr{D} \times \mathscr{D} \times 2^{\mathscr{V} \times \{\, 0, 1 \,\}}$.
-
-%% Let $\nu\colon \mathscr{S} \to 2^{\mathscr{S}}$ be a map defined as
-%% \[
-%% \nu(a, b, S) =
-%% \begin{cases}
-%%   \{\,(\pi(a), b, S \cup \{\, \kappa(a) \,\})\,\} & \text{if } a \in \dom(\pi) \\
-%%   \emptyset & \text{if } a \not\in \dom(\pi)
-%% \end{cases}
-%% \]
-%% for all $(a, b, S) \in \mathscr{S}$.
-Furthermore, let $\nu'\colon 2^{\mathscr{S}} \to 2^{\mathscr{S}}$ be an endomorphism defined as $\nu'(S) = \bigcup_{s \in S} \nu(s)$ for all $S \subseteq \mathscr{S}$.
+\begin{definition}[Notation]
+  For any clause $c = (P, N, C, \delta_c)$, bijection $\beta\colon \Vars(c) \to V$ (for some set of variables $V$) and function $\gamma\colon \Doms(c) \to \mathscr{D}$, let $c \ast (\beta, \gamma) = d$ be the clause with all occurrences of any variable $v \in \Vars(c)$ in $P$, $N$, and $C$ replaced with $\beta(v)$ (so $\Vars(d) = V$) and $\delta_d\colon V \to \mathscr{D}$ defined as $\delta_d \coloneqq \gamma \circ \delta_c \circ \beta^{-1}$.
+In other words, $\delta_d$ is the unique function that makes the following diagram commute:
+  \[
+  \begin{tikzcd}
+    \Vars(c) \ar[r, tail, two heads, "\beta"] \arrow{d}{\delta_c} & V = \Vars(d) \ar[d, dashed, "\exists!\delta_d"] \\
+    \Doms(c) \arrow{r}{\gamma} & \mathscr{D}.
+  \end{tikzcd}
+  \]
+\end{definition}
 
@@
   \caption{A recursive function for checking whether one can reuse the circuit for computing $\WMC(\psi)$ to compute $\WMC(\phi)$.
-Both $\phi$ and $\psi$ are formulas, and $\rho\colon \Doms(\phi) \protect\pfun \Doms(\psi) \times 2^{\mathscr{V} \times \{\, 0, 1 \,\}}$ is a partial map.
-TODO: explain more about $\rho$.}
+Both $\phi$ and $\psi$ are formulas, and $\rho\colon \Doms(\phi) \protect\pfun \Doms(\psi)$ is a partial map.}
   \SetKwProg{Fn}{Function}{:}{}
   \SetKwFunction{identifyRecursion}{identifyRecursion}
-  \SetKwFunction{findHistory}{findHistory}
-  \SetKwData{suitable}{suitable}
-  \Fn{\identifyRecursion{$\phi$, $\psi$, $\rho = \emptyset$}}{
-    \lIf{$\phi = \psi = \emptyset$}{\Return{$\rho$}}
+  \SetKwFunction{findHistory}{traceAncestors}
+  \SetKwFunction{generateMaps}{generateMaps}
+  \SetKwFunction{constructDomainMap}{constructDomainMap}
+  \SetKwData{suitable}{suitableBijection}
+  \SetKwData{found}{foundConstraintRemoval}
+  \Fn{\identifyRecursion{$\phi$, $\psi$, $\rho = \emptyset$, $\found = {\normalfont \texttt{false}}$}}{
     \lIf{$|\phi| \ne |\psi|$ {\bf or} $\#\phi \ne \#\psi$}{\Return{\normalfont \texttt{null}}}
+    \If{$\phi = \psi = \emptyset$}{
+      \lIf{$\found$}{\Return{$\rho$}}
+      \Return{\normalfont \texttt{null}}\;
+    }
     \ForEach{clause $c \in \phi$}{
       \ForEach{clause $d \in \psi$ such that $\#d = \#c$} {
-        \ForEach{bijection $\beta\colon \Vars(c) \to \Vars(d)$}{
-          $\suitable \gets {\normalfont \texttt{true}}$\;
-          \If{$\forall v \in \Vars(c). (\delta_c(v) \not\in {\normalfont \dom}(\rho) \lor \pi_1(\rho(\delta_c(v))) = \delta_d(\beta(v)))$ {\bf and} $c\beta = d$}{
-            $\rho' \gets \rho$\;
+        \ForEach{$(\beta, \gamma) \in \generateMaps{$c$, $d$, $\rho$}$ such that $c \ast (\beta, \gamma) = d$}{
+          $\found' \gets \found$\;
+          $\suitable \gets \texttt{true}$\;
           \ForEach{$v \in \Vars(c)$}{
-              $H \gets \findHistory{$\delta_c(v)$, $\delta_d(\beta(v))$}$\;
-              \If{$H = {\normalfont \texttt{null}}$}{
-                $\suitable \gets {\normalfont \texttt{false}}$\;
+            $\found'' \gets \findHistory{$\delta_c(v)$, $\delta_d(\beta(v))$}$\;
+            \If{$\found'' = {\normalfont \texttt{null}}$}{
+              $\suitable \gets \texttt{false}$\;
               break\;
             }
-              $\rho' \gets \rho \cup \{\, \delta_c(v) \mapsto (\delta_d(\beta(v)), H) \,\}$\;
+            \lIf{$\found''$}{$\found' \gets \texttt{true}$}
           }
           \If{\suitable}{
-              $\rho'' \gets \identifyRecursion{$\phi \setminus \{\, c \,\}$, $\psi \setminus \{\, d \,\}$, $\rho'$}$\;
+            $\rho'' \gets \identifyRecursion{$\phi \setminus \{\, c \,\}$, $\psi \setminus \{\, d \,\}$, $\rho \cup \gamma$, $\found'$}$\;
             \lIf{$\rho'' \ne {\normalfont \texttt{null}}$}{\Return{$\rho''$}}
-            }
           }
@@
   }
+  \Fn{\generateMaps{$c$, $d$, $\rho$}}{
+    $M \gets \emptyset$\;
+    \ForEach{bijection $\beta\colon \Vars(c) \to \Vars(d)$}{
+      \If{$\forall v \in \Vars(c). (\delta_c(v) \not\in {\normalfont \dom}(\rho) \lor \rho(\delta_c(v)) = \delta_d(\beta(v)))$}{
+        $\gamma \gets \constructDomainMap{$\Vars(c)$, $\delta_c$, $\delta_d$, $\beta$}$\;
+        \lIf{$\gamma \ne {\normalfont \texttt{null}}$}{$M \gets M \cup \{\, (\beta, \gamma) \,\}$}
+      }
+    }
+    \Return{$M$}\;
+  }
+  \Fn{\constructDomainMap{$V$, $\delta_c$, $\delta_d$, $\beta$}}{
+    $\gamma \gets \emptyset$\;
+    \ForEach{$v \in V$}{
+      \lIf{$\delta_c(v) \not\in \dom(\gamma)$}{$\gamma \gets \gamma \cup \{\, \delta_c(v) \mapsto \delta_d(\beta(v)) \,\}$}
+      \lElseIf{$\gamma(\delta_c(v)) \ne \delta_d(\beta(v))$}{\Return{\normalfont \texttt{null}}}
+    }
+    \Return{$\gamma$}\;
+  }
   \Fn{\findHistory{$c$, $d$}}{
-    $H \gets \emptyset$\;
+    $\found \gets \texttt{false}$\;
     \While{$d \ne c$ {\bf and} $d \in {\normalfont \dom}(\pi)$}{
-      $H \gets H \cup \{\, \kappa(d) \,\}$\;
+      \lIf{$d \in \mathscr{C}$}{$\found \gets \texttt{true}$}
       $d \gets \pi(d)$\;
     }
-    \lIf{$d = c$}{\Return{$H$}}
+    \lIf{$d = c$}{\Return{\found}}
     \Return{\normalfont \texttt{null}}\;
@@
 
+The function \texttt{traceAncestors} returns \texttt{null} if domain $c \in \mathscr{D}$ is not an ancestor of domain $d \in \mathscr{D}$.
+Otherwise, it returns \texttt{true} if the size of $d$ is guaranteed to be strictly smaller than the size of $c$ (i.e., there is domain created by the constraint removal rule on the path from $c$ to $d$) and \texttt{false} if their sizes will be equal at some point during inference.
+
+Notation: For partial functions $\alpha, \beta\colon A \pfun B$ such that $\alpha|_{\dom(\alpha) \cap \dom(\beta)} = \beta|_{\dom(\alpha) \cap \dom(\beta)}$, we write $\alpha \cup \beta$ for the unique partial function such that $\alpha \cup \beta|_{\dom(\alpha)} = \alpha$, and $\alpha \cup \beta|_{\dom(\beta)} = \beta$.
+
+TODO: explain why $\rho \cup \gamma$ is possible.
+
 TODO: explain what the second return statement is about and why a third one is not necessary.
@@
 \begin{example}
-  TODO: explain how the algorithm establishes a recursive relationship from
+  % TODO: explain how the algorithm establishes a recursive relationship from
   % 1. formulas (both the Forclift representation and the more normal way to write down the same thing)

### 2022-01-21 notes/notes.tex
A slight simplification of the algorithm

@@
 \usetikzlibrary{arrows,fit,positioning,trees,cd}
+
+\crefname{algocf}{algorithm}{Algorithms}
+\Crefname{algocf}{Algorithm}{Algorithms}
 
@@
 \section{Basic Definitions}
- TODO (later): maybe mathcal instead of mathscr
 
@@
 \item notation: $\Imm$
-\item atom, literal
+\item atom, literal, constant, predicate, variable
 \item inequality constraint
@@
 \item $\Doms$ on both formulas and clauses. $\Doms(c) = \Imm \delta_c$, and $\Doms(\phi) = \bigcup_{c \in \phi} \Doms(c)$.
-\item the hash codes of clauses and formulas. Introduce the $\#$ notation.
 \item substitution
@@
 
-TODO: maybe $\pi$ is global enough to have a more unique name.
+\paragraph{TODO}
+\begin{itemize}
+\item later: maybe mathcal instead of mathscr
+\item maybe $\pi$ is global enough to have a more unique name
+\item maybe $c[\beta, \gamma]$ is better than $c \ast (\beta, \gamma)$
+\end{itemize}
 
@@
 
+We use hash codes to efficiently check whether a recursive relationship between two formulas is plausible.
+(It is plausible if the formulas are equal up to variables and domains.) The hash code of a clause $c = (P, N, C, \delta_c)$ combines the hash codes of the sets of constants and predicates in $c$, the numbers of positive and negative literals (i.e., $|P|$ and $|N|$), the number of inequality constraints $|C|$, and the number of variables $|\Vars(c)|$.
+The hash code of a formula $\phi$ combines the hash codes of all its clauses and is denoted $\#\phi$.
+
 \section{Identifying Possibilities for Recursion}
@@
 \begin{algorithm}[t]
-  \caption{A recursive function for checking whether one can reuse the circuit for computing $\WMC(\psi)$ to compute $\WMC(\phi)$.
+  \caption{A recursive function for checking whether one can reuse the circuit for computing $\WMC(\phi)$ to compute $\WMC(\psi)$.
 Both $\phi$ and $\psi$ are formulas, and $\rho\colon \Doms(\phi) \protect\pfun \Doms(\psi)$ is a partial map.}
+  \label{alg:recursion}
   \SetKwProg{Fn}{Function}{:}{}
+  \SetKw{KwRet}{yield}
   \SetKwFunction{identifyRecursion}{identifyRecursion}
@@
     \lIf{$|\phi| \ne |\psi|$ {\bf or} $\#\phi \ne \#\psi$}{\Return{\normalfont \texttt{null}}}
-    \If{$\phi = \psi = \emptyset$}{
+    \If{$\phi = \emptyset$}{
       \lIf{$\found$}{\Return{$\rho$}}
@@
     }
-    \ForEach{clause $c \in \phi$}{
-      \ForEach{clause $d \in \psi$ such that $\#d = \#c$} {
-        \ForEach{$(\beta, \gamma) \in \generateMaps{$c$, $d$, $\rho$}$ such that $c \ast (\beta, \gamma) = d$}{
+    \ForEach{clause $c \in \phi$\label{line:for1}}{
+      \ForEach{clause $d \in \psi$ such that $\#d = \#c$\label{line:for2}} {
+        \ForEach{$(\beta, \gamma) \in \generateMaps{$c$, $d$, $\rho$}$ such that $c \ast (\beta, \gamma) = d$\label{line:generateMaps}}{
           $\found' \gets \found$\;
           $\suitable \gets \texttt{true}$\;
-          \ForEach{$v \in \Vars(c)$}{
-            $\found'' \gets \findHistory{$\delta_c(v)$, $\delta_d(\beta(v))$}$\;
+          \ForEach{$e \in \Doms(c)$\label{line:vars}}{
+            $\found'' \gets \findHistory{$e$, $\gamma(e)$}$\;
             \If{$\found'' = {\normalfont \texttt{null}}$}{
@@
   \Fn{\generateMaps{$c$, $d$, $\rho$}}{
-    $M \gets \emptyset$\;
-    \ForEach{bijection $\beta\colon \Vars(c) \to \Vars(d)$}{
-      \If{$\forall v \in \Vars(c). (\delta_c(v) \not\in {\normalfont \dom}(\rho) \lor \rho(\delta_c(v)) = \delta_d(\beta(v)))$}{
-        $\gamma \gets \constructDomainMap{$\Vars(c)$, $\delta_c$, $\delta_d$, $\beta$}$\;
-        \lIf{$\gamma \ne {\normalfont \texttt{null}}$}{$M \gets M \cup \{\, (\beta, \gamma) \,\}$}
+    \ForEach{bijection $\beta\colon \Vars(c) \to \Vars(d)$\label{line:bijection}}{
+      $\gamma \gets \constructDomainMap{$\Vars(c)$, $\delta_c$, $\delta_d$, $\beta$, $\rho$}$\;
+      \lIf{$\gamma \ne {\normalfont \texttt{null}}$}{\KwRet{$(\beta, \gamma)$}}
     }
   }
-    \Return{$M$}\;
-  }
-  \Fn{\constructDomainMap{$V$, $\delta_c$, $\delta_d$, $\beta$}}{
+  \Fn{\constructDomainMap{$V$, $\delta_c$, $\delta_d$, $\beta$, $\rho$}}{
     $\gamma \gets \emptyset$\;
     \ForEach{$v \in V$}{
+      \lIf{$\delta_c(v) \in \dom(\rho)$ {\bf and} $\rho(\delta_c(v)) \ne \delta_d(\beta(v))$}{\Return{\normalfont \texttt{null}}}
       \lIf{$\delta_c(v) \not\in \dom(\gamma)$}{$\gamma \gets \gamma \cup \{\, \delta_c(v) \mapsto \delta_d(\beta(v)) \,\}$}
@@
   }
-  \Fn{\findHistory{$c$, $d$}}{
+  \Fn{\findHistory{$d$, $e$}}{
     $\found \gets \texttt{false}$\;
-    \While{$d \ne c$ {\bf and} $d \in {\normalfont \dom}(\pi)$}{
-      \lIf{$d \in \mathscr{C}$}{$\found \gets \texttt{true}$}
-      $d \gets \pi(d)$\;
+    \While{$e \ne d$ {\bf and} $e \in {\normalfont \dom}(\pi)$}{
+      \lIf{$e \in \mathscr{C}$}{$\found \gets \texttt{true}$}
+      $e \gets \pi(e)$\;
     }
-    \lIf{$d = c$}{\Return{\found}}
+    \lIf{$e = d$}{\Return{\found}}
     \Return{\normalfont \texttt{null}}\;
@@
   \begin{tikzpicture}[edge from parent/.style={draw,-latex}]
-    \node[draw,circle,fill=violet!10] (circuit) {} child {
-      node[draw,circle,fill=violet!10] (bmaker) {$\diamondsuit$}
-      child {node[draw,circle,fill=violet!10] {}
-        child {node[draw,circle,fill=violet!10] {}}
-        child {node[draw,circle,fill=violet!10] {}
-          child {node[draw,circle,fill=violet!10] {}}
-          child {node[draw,circle,fill=violet!10] {}
-            child {node[draw,circle,fill=violet!10] {}}
-            child {node[draw,circle,fill=violet!10] (amaker) {$\heartsuit$}
-              child {node[draw,circle,fill=violet!10] (ref) {}
-                child {node[draw,circle,fill=violet!10] {}}
-              }
-            }
-          }
-        }
-      }
-    };
-    \node[below right=1cm and 2cm of circuit] (a) {$a$} child {node (aprime) {$a'$}};
+    %% \node[draw,circle,fill=violet!10] (circuit) {} child {
+    %%   node[draw,circle,fill=violet!10] (bmaker) {$\diamondsuit$}
+    %%   child {node[draw,circle,fill=violet!10] {}
+    %%     child {node[draw,circle,fill=violet!10] {}}
+    %%     child {node[draw,circle,fill=violet!10] {}
+    %%       child {node[draw,circle,fill=violet!10] {}}
+    %%       child {node[draw,circle,fill=violet!10] {}
+    %%         child {node[draw,circle,fill=violet!10] {}}
+    %%         child {node[draw,circle,fill=violet!10] (amaker) {$\heartsuit$}
+    %%           child {node[draw,circle,fill=violet!10] (ref) {}
+    %%             child {node[draw,circle,fill=violet!10] {}}
+    %%           }
+    %%         }
+    %%       }
+    %%     }
+    %%   }
+    %% };
+    \node (a) {$a$} child {node[draw,rectangle] (aprime) {$a'$}};
     \node[right=1 cm of a] (b) {$b$}
@@
     child {node (bbot) {$b^\bot$}};
-    \node[draw,fit=(a) (aprime) (b) (btop) (bbot)] {};
-    \draw[-latex] (ref) edge[densely dotted,bend left=90] (circuit);
-    \draw[-latex,color=teal] (aprime) edge[densely dashed] node[xshift=2mm,color=teal] {$0$} (amaker);
-    \draw[-latex,color=teal] (btop) edge[bend left=50,densely dashed] node[xshift=6mm,color=teal] {$0$} (bmaker);
-    \draw[-latex,color=teal] (bbot) edge[bend left=50,densely dashed] node[yshift=-2mm,color=teal] {$1$} (bmaker);
+    %% \node[draw,fit=(a) (aprime) (b) (btop) (bbot)] {};
+    %% \draw[-latex] (ref) edge[densely dotted,bend left=90] (circuit);
+    %% \draw[-latex,color=teal] (aprime) edge[densely dashed] node[xshift=2mm,color=teal] {$0$} (amaker);
+    %% \draw[-latex,color=teal] (btop) edge[bend left=50,densely dashed] node[xshift=6mm,color=teal] {$0$} (bmaker);
+    %% \draw[-latex,color=teal] (bbot) edge[bend left=50,densely dashed] node[yshift=-2mm,color=teal] {$1$} (bmaker);
   \end{tikzpicture}
-  \caption{A circuit (outside the box) and a forest of domains (inside the box).
-The dotted line on the left will be added if \texttt{identifyRecursion} returns a non-\texttt{null} mapping.
-The dashed edges with their labels represent the $\kappa$ function.
-The circuit nodes with symbols in them are the nodes that introduce new (sub)domains.}
+  \caption{The forest of domains from \cref{example}.
+The directed edges correspond to the pairs of domains in $\pi$ but in the opposite direction, e.g., $\pi(a') = a$.
+The domain enclosed in a rectangle is the only domain created by constraint removal, i.e., $\mathscr{C} = \{\, a' \,\}$.}
   \label{fig:example}
@@
 
-The function \texttt{traceAncestors} returns \texttt{null} if domain $c \in \mathscr{D}$ is not an ancestor of domain $d \in \mathscr{D}$.
-Otherwise, it returns \texttt{true} if the size of $d$ is guaranteed to be strictly smaller than the size of $c$ (i.e., there is domain created by the constraint removal rule on the path from $c$ to $d$) and \texttt{false} if their sizes will be equal at some point during inference.
+The function \texttt{traceAncestors} returns \texttt{null} if domain $d \in \mathscr{D}$ is not an ancestor of domain $e \in \mathscr{D}$.
+Otherwise, it returns \texttt{true} if the size of $e$ is guaranteed to be strictly smaller than the size of $d$ (i.e., there is domain created by the constraint removal rule on the path from $d$ to $e$) and \texttt{false} if their sizes will be equal at some point during inference.
 
@@
 
-TODO: explain why $\rho \cup \gamma$ is possible.
+\paragraph{TODO}
+\begin{itemize}
+\item explain why $\rho \cup \gamma$ is possible
+\item explain what the second return statement is about and why a third one is not necessary
+\item mention which one is the main function, what each function takes and returns
+\item explain the yield keyword
+\item in the example below: write down both formula using the Forclift format
+\end{itemize}
 
-TODO: explain what the second return statement is about and why a third one is not necessary.
+The algorithm could be improved in two ways:
+\begin{itemize}
+\item by constructing a domain map first and then using it to reduce the number of viable variable bijections.
+\item by similarly using the domain map $\rho$.
+\end{itemize}
+However, it is not clear that this would result in an overall performance improvement, since the number of variables in instances of interest never exceeds three and the identity bijection is typically the right one.
 
-TODO: mention which one is the main function, what each function takes and returns.
+\begin{example} \label{example}
+  Let $\phi$ be the formula
+  \begin{align}
+    \forall X \in a. \forall Y \in b. \forall Z \in b. Y \ne Z &\implies \neg p(X, Y) \lor \neg p(X, Z)\label{phi1} \\
+    \forall X \in a. \forall Y \in b. \forall Z \in a. X \ne Z &\implies \neg p(X, Y) \lor \neg p(Z, Y).\label{phi2}
+  \end{align}
+  and $\psi$ be the formula
+  \begin{align}
+    \forall X \in a'. \forall Y \in b^\bot. \forall Z \in b^\bot. Z \ne Y &\implies \neg p(X, Y) \lor \neg p(X, Z)\label{psi1} \\
+    \forall X \in a'. \forall Y \in b^\bot. \forall Z \in a'. X \ne Z &\implies \neg p(X, Y) \lor \neg p(Z, Y)\label{psi2}
+  \end{align}
 
-\begin{example}
-  % TODO: explain how the algorithm establishes a recursive relationship from
-  % 1. formulas (both the Forclift representation and the more normal way to write down the same thing)
-  % 2. definitions of delta_c, delta_d, kappa, pi
-  \begin{align*}
-    \forall X \in a'. \forall Y \in b^\bot. \forall Z \in b^\bot. Z \ne Y &\implies \neg p(X, Y) \lor \neg p(X, Z) \\
-    \forall X \in a'. \forall Y \in b^\bot. \forall Z \in a'. X \ne Z &\implies \neg p(X, Y) \lor \neg p(Z, Y)
-  \end{align*}
-  to
-  \begin{align*}
-    \forall X \in a. \forall Y \in b. \forall Z \in b. Y \ne Z &\implies \neg p(X, Y) \lor \neg p(X, Z) \\
-    \forall X \in a. \forall Y \in b. \forall Z \in a. X \ne Z &\implies \neg p(X, Y) \lor \neg p(Z, Y)
-  \end{align*}
-  and mention \cref{fig:example}. Solution map (stored as the edge label):
-  \begin{align*}
-    \rho(a') &= (a, \{\, (\diamondsuit, 0) \,\}) \\
-    \rho(b^\bot) &= (b, \{\, (\heartsuit, 1) \,\})
-  \end{align*}
+  The relevant domains and the definition of $\pi$ is in \cref{fig:example}.
+Since $\#\phi = \#\psi$, and the formulas are non-empty, the algorithm proceeds with the for-loops on \cref{line:for1,line:for2,line:generateMaps}.
+Suppose $c$ in the algorithm refers to \cref{phi1}, and $d$ to \cref{psi1}.
+Since both clauses have three variables, function \texttt{generateMaps} has $3!=6$ bijections to check.
+Suppose the identity bijection is picked first.
+Then \texttt{constructDomainMap} is called with the following parameters:
+  \begin{itemize}
+  \item $V = \{\, X, Y, Z \,\}$,
+  \item $\delta_c = \{\, X \mapsto a, Y \mapsto b, Z \mapsto b \,\}$,
+  \item $\delta_d = \{\, X \mapsto a', Y \mapsto b^\bot, Z \mapsto b^\bot \,\}$,
+  \item $\beta = \{\, X \mapsto X, Y \mapsto Y, Z \mapsto Z \,\}$.
+  \end{itemize}
+  Since $\delta_i(Y) = \delta_i(Z)$ for $i \in \{\, c, d \,\}$, \texttt{constructDomainMap} returns $\gamma = \{\, a \mapsto a', b \mapsto b^\bot \,\}$.
+Thus, \texttt{generateMaps} yields its first pair of maps $(\beta, \gamma)$ to \cref{line:generateMaps}.
+Furthermore, the pair satisfies the $c \ast (\beta, \gamma) = d$ condition.
+
+  Suppose \cref{line:vars} selects $e = a$ first.
+Since $\pi(a') = a$, and $a' \in \mathscr{C}$, \texttt{traceAncestors($a$, $a'$)} returns \texttt{true}, and the recursive call to \texttt{identifyRecursion($\phi'$, $\psi'$, $\gamma$, true)} is made, where $\phi'$ and $\psi'$ are new formulas with one clause each: \cref{phi2} and \cref{psi2}, respectively.
+
+  Again we have two non-empty formulas with equal hash codes, so \texttt{generateMaps} is called with $c$ set to \cref{phi2}, $d$ set to \cref{psi2}, and $\rho = \{\, a \mapsto a', b \mapsto b^\bot \,\}$.
+Suppose \cref{line:bijection} picks the identity bijection first again.
+
 \end{example}

### 2022-01-21 notes/notes.tex
First draft of describing Ref

@@
 \usepackage{mathrsfs}
+\usepackage{amsfonts}
 
@@
   \begin{tikzcd}
-    \Vars(c) \ar[r, tail, two heads, "\beta"] \arrow{d}{\delta_c} & V = \Vars(d) \ar[d, dashed, "\exists!\delta_d"] \\
-    \Doms(c) \arrow{r}{\gamma} & \mathscr{D}.
+    \Vars(c) \ar[r, tail, two heads, "\beta"] \arrow[d, swap, "\delta_c"] & V = \Vars(d) \ar[d, dashed, "\exists!\delta_d"] \\
+    \Doms(c) \ar[r, swap, "\gamma"] & \mathscr{D}.
   \end{tikzcd}
@@
           \If{\suitable}{
-            $\rho'' \gets \identifyRecursion{$\phi \setminus \{\, c \,\}$, $\psi \setminus \{\, d \,\}$, $\rho \cup \gamma$, $\found'$}$\;
+            $\rho'' \gets \identifyRecursion{$\phi \setminus \{\, c \,\}$, $\psi \setminus \{\, d \,\}$, $\rho \cup \gamma$, $\found'$}$\;\label{line:recursion}
             \lIf{$\rho'' \ne {\normalfont \texttt{null}}$}{\Return{$\rho''$}}
@@
 
+Diagramatically, \texttt{constructDomainMap} attempts to find $\gamma\colon \Doms(c) \to \Doms(d)$ such that the following diagram commutes (and returns \texttt{null} if such a function does not exist):
+\[
+\begin{tikzcd}
+  \Vars(c) \ar[r, tail, two heads, "\beta"] \arrow[d, swap, "\delta_c"] & \Vars(d) \ar[d, "\delta_d"] \\
+  \Doms(c) \ar[r, dashed, "\gamma"] \ar[d, hookrightarrow] & \Doms(d) \ar[d, hookrightarrow] \\
+  \mathscr{D} \ar[r, swap, "\rho"] & \mathscr{D}.
+\end{tikzcd}
+\]
+
 \begin{example} \label{example}
@@
 Suppose $c$ in the algorithm refers to \cref{phi1}, and $d$ to \cref{psi1}.
-Since both clauses have three variables, function \texttt{generateMaps} has $3!=6$ bijections to check.
+Since both clauses have three variables, in the worst case, function \texttt{generateMaps} would have $3!=6$ bijections to check.
 Suppose the identity bijection is picked first.
@@
   \item $\delta_d = \{\, X \mapsto a', Y \mapsto b^\bot, Z \mapsto b^\bot \,\}$,
-  \item $\beta = \{\, X \mapsto X, Y \mapsto Y, Z \mapsto Z \,\}$.
+  \item $\beta = \{\, X \mapsto X, Y \mapsto Y, Z \mapsto Z \,\}$,
+  \item $\rho = \emptyset$.
   \end{itemize}
@@
 
-  Suppose \cref{line:vars} selects $e = a$ first.
-Since $\pi(a') = a$, and $a' \in \mathscr{C}$, \texttt{traceAncestors($a$, $a'$)} returns \texttt{true}, and the recursive call to \texttt{identifyRecursion($\phi'$, $\psi'$, $\gamma$, true)} is made, where $\phi'$ and $\psi'$ are new formulas with one clause each: \cref{phi2} and \cref{psi2}, respectively.
+  Since $\pi(a') = a$, and $a' \in \mathscr{C}$, \texttt{traceAncestors($a$, $a'$)} returns \texttt{true}, which sets $\textsf{foundConstraintRemoval}'$ to \texttt{true} as well.
+When $e = b$, however, \texttt{traceAncestors}($b$, $b^\bot$) returns \texttt{false} since $b^\bot$ is a descendant of $b$ but not created by the constraint removal compilation rule.
+On \cref{line:recursion}, a recursive call to \texttt{identifyRecursion($\phi'$, $\psi'$, $\gamma$, true)} is made, where $\phi'$ and $\psi'$ are new formulas with one clause each: \cref{phi2} and \cref{psi2}, respectively.
 
@@
 Suppose \cref{line:bijection} picks the identity bijection first again.
-
+Then \texttt{constructDomainMap} is called with the following parameters:
+  \begin{itemize}
+  \item $V = \{\, X, Y, Z \,\}$,
+  \item $\delta_c = \{\, X \mapsto a, Y \mapsto b, Z \mapsto a \,\}$,
+  \item $\delta_d = \{\, X \mapsto a', Y \mapsto b^\bot, Z \mapsto a' \,\}$,
+  \item $\beta = \{\, X \mapsto X, Y \mapsto Y, Z \mapsto Z \,\}$,
+  \item $\rho = \{\, a \mapsto a', b \mapsto b^\bot \,\}$.
+  \end{itemize}
+  Since $\beta$ and $\rho$ `commute' (TODO: as in the diagram above), and there are no new domains in $\Doms(c)$ and $\Doms(d)$, $\gamma$ exists and is equal to $\rho$.
+Again, the returned pair $(\beta, \gamma)$ satisfies the condition $c \ast (\beta, \gamma) = d$.
+This $\gamma$ passes the \texttt{traceAncestors} checks exactly the same way as the one before, and \cref{line:recursion} calls \texttt{identifyRecursion($\emptyset$, $\emptyset$, $\rho$, true)}, which immediately returns $\rho = \{\, a \mapsto a', b \mapsto b^\bot \,\}$ as the final answer.
+This means that one can indeed use a circuit for $\WMC(\phi)$ to compute $\WMC(\psi)$ by replacing every mention of $a$ with $a'$ and every mention of $b$ with $b^\bot$.
 \end{example}
 
-TODO: conclude with a description of the inference rule and the node/edge type.
+\subsection{Evaluation}
 
-\section{New Node Types}
+This $\rho$ is saved as a parameter of the new circuit node. During inference, there is a domain size map $\sigma\colon \mathscr{D} \to \mathbb{N}_0$, which gets updated to
+\[
+\sigma'(x) =
+\begin{cases}
+  \sigma(\rho(x)) & \text{if } x \in \dom(\rho) \\
+  \sigma(x) & \text{otherwise}
+\end{cases}
+\]
+for all $x \in \mathscr{D}$.
+
+\section{New Operations}
+
+TODO: compilation rules, node types, their evaluation during inference.
 

### 2022-01-21 notes/notes.tex
Simplify some stuff in the algorithm

@@
 \item atom, literal, constant, predicate, variable
-\item inequality constraint
+\item inequality constraint. Notation: $[x \ne y]$, where $x$ is a variable (of the clause), and $y$ is either a variable or a constant.
 \item $\Vars$, $\Vars(c) = \Vars(P) \cup \Vars(N) \cup \Vars(C)$
@@
 \item maybe $c[\beta, \gamma]$ is better than $c \ast (\beta, \gamma)$
+\item avoid using lowercase latin letters for everything: capitalise domains and variables
 \end{itemize}
@@
 must match).
+
+  TODO: it's probably enough to say it's a set of literals, a set of constraints, and a $\delta$.
 \end{definition}
@@
 
+\subsection{Constraint Removal}
+
+TODO: introduce the Forclift-style notation (e.g., the compile operator) and the arbitrary formula $\phi$.
+
+\paragraph{Preconditions.} There is a domain $d \in \mathscr{D}$ and an element $e \in d$ such that:
+\begin{itemize}
+\item for each clause $c = (P, N, C, \delta_c) \in \phi$ and variable $v \in \Vars(c)$, either $\delta_c(v) \ne d$ or $[v \ne e] \in C$;
+\item $e$ does not occur in any literal of any clause of $\phi$.
+\end{itemize}
+
+NOTE: we know that
+
+\paragraph{Operator.}
+
 \subsection{Improved Domain Recursion}
@@
 The original version of domain recursion is here \cite{DBLP:conf/nips/Broeck11}.
-
-\subsection{Constraint Removal}
 
@@
 
-TODO: new node types, their algebraic/graphical representation, what info they hold, and how they're created.
+TODO: algebraic/graphical representation, what info they hold, and how they're created
 

### 2022-01-22 notes/notes.tex
A description of constraint removal

@@
 
+\DeclareMathOperator{\Compile}{\textsc{Compile}}
+\DeclareMathOperator{\CR}{\textsc{CR}}
 \DeclareMathOperator{\dom}{dom}
@@
 \item atom, literal, constant, predicate, variable
-\item inequality constraint. Notation: $[x \ne y]$, where $x$ is a variable (of the clause), and $y$ is either a variable or a constant.
-\item $\Vars$, $\Vars(c) = \Vars(P) \cup \Vars(N) \cup \Vars(C)$
+\item inequality constraint. Notation: $(x, y)$, where $x$ is a variable (of the clause), and $y$ is either a variable or a constant.
+\item $\Vars$, $\Vars(c) = \Vars(L) \cup \Vars(C)$
 \item $\Doms$ on both formulas and clauses. $\Doms(c) = \Imm \delta_c$, and $\Doms(\phi) = \bigcup_{c \in \phi} \Doms(c)$.
@@
 \item maybe $c[\beta, \gamma]$ is better than $c \ast (\beta, \gamma)$
-\item avoid using lowercase latin letters for everything: capitalise domains and variables
+\item avoid using lowercase latin letters for everything: capitalise domains and variables.
 \end{itemize}
@@
 \begin{definition}
-  A \emph{clause} is a triple $c = (P, N, C, \delta_c)$, where $P$ and $N$ are sets of atoms interpreted as positive and negative literals respectively, $C$ is a set of inequality constraints, and $\delta_c\colon \Vars(c) \to \mathscr{D}$ is a function that maps all variables in $c$ to their domains.
-Two clauses $c$ and $d = (P', N', C', \delta_d)$ are \emph{isomorphic} (written $c \cong d$) if there is a bijection $\beta\colon \Vars(c) \to \Vars(d)$ such that $c\beta = d\beta$.
+  A \emph{clause} is a triple $c = (L, C, \delta_c)$, where $L$ is the set of literals, $C$ is a set of inequality constraints, and $\delta_c\colon \Vars(c) \to \mathscr{D}$ is a function that maps all variables in $c$ to their domains.
+Two clauses $c$ and $d = (L', C', \delta_d)$ are \emph{isomorphic} (written $c \cong d$) if there is a bijection $\beta\colon \Vars(c) \to \Vars(d)$ such that $c\beta = d\beta$.
 TODO: we will always use this subscript notation for the $\delta$'s.
@@
 must match).
-
-  TODO: it's probably enough to say it's a set of literals, a set of constraints, and a $\delta$.
 \end{definition}
@@
 We use hash codes to efficiently check whether a recursive relationship between two formulas is plausible.
-(It is plausible if the formulas are equal up to variables and domains.) The hash code of a clause $c = (P, N, C, \delta_c)$ combines the hash codes of the sets of constants and predicates in $c$, the numbers of positive and negative literals (i.e., $|P|$ and $|N|$), the number of inequality constraints $|C|$, and the number of variables $|\Vars(c)|$.
+(It is plausible if the formulas are equal up to variables and domains.) The hash code of a clause $c = (L, C, \delta_c)$ combines the hash codes of the sets of constants and predicates in $c$, the numbers of positive and negative literals, the number of inequality constraints $|C|$, and the number of variables $|\Vars(c)|$.
 The hash code of a formula $\phi$ combines the hash codes of all its clauses and is denoted $\#\phi$.
@@
 \begin{definition}[Notation]
-  For any clause $c = (P, N, C, \delta_c)$, bijection $\beta\colon \Vars(c) \to V$ (for some set of variables $V$) and function $\gamma\colon \Doms(c) \to \mathscr{D}$, let $c \ast (\beta, \gamma) = d$ be the clause with all occurrences of any variable $v \in \Vars(c)$ in $P$, $N$, and $C$ replaced with $\beta(v)$ (so $\Vars(d) = V$) and $\delta_d\colon V \to \mathscr{D}$ defined as $\delta_d \coloneqq \gamma \circ \delta_c \circ \beta^{-1}$.
+  For any clause $c = (L, C, \delta_c)$, bijection $\beta\colon \Vars(c) \to V$ (for some set of variables $V$) and function $\gamma\colon \Doms(c) \to \mathscr{D}$, let $c \ast (\beta, \gamma) = d$ be the clause with all occurrences of any variable $v \in \Vars(c)$ in $L$ and $C$ replaced with $\beta(v)$ (so $\Vars(d) = V$) and $\delta_d\colon V \to \mathscr{D}$ defined as $\delta_d \coloneqq \gamma \circ \delta_c \circ \beta^{-1}$.
 In other words, $\delta_d$ is the unique function that makes the following diagram commute:
@@
 
+TODO: still need to connect this to tryCache.
+
 \section{New Operations}
@@
 \begin{itemize}
-\item for each clause $c = (P, N, C, \delta_c) \in \phi$ and variable $v \in \Vars(c)$, either $\delta_c(v) \ne d$ or $[v \ne e] \in C$;
+\item for each clause $c = (L, C, \delta_c) \in \phi$ and variable $v \in \Vars(c)$, either $\delta_c(v) \ne d$ or $(v, e) \in C$;
 \item $e$ does not occur in any literal of any clause of $\phi$.
@@
 
-NOTE: we know that
+\paragraph{Operator.} First, we introduce a new domain (i.e., $\mathscr{D} \coloneqq \mathscr{D} \sqcup \{\, d' \,\}$), add it to $\mathscr{C}$ (i.e., $\mathscr{C} \coloneqq C \sqcup \{\, d' \,\}$), and set $\pi(d') \coloneqq d$.
+Then $\CR(\phi) = \CR_{d \mapsto d'}(\Compile(\phi'))$.
+The new formula $\phi'$ is defined by replacing every clause $(L, C, \delta) \in \phi$ by a clause $c' = (L, C', \delta') \in \phi'$, where
+\[
+C' = \{\, (x, y) \in C \mid y \ne e \,\},
+\]
+and
+\[
+\delta'(x) =
+\begin{cases}
+  d' & \text{if } \delta(x) = d \\
+  \delta(x) & \text{otherwise}
+\end{cases}
+\]
+for all $x \in \Vars(c') \subseteq \Vars(c)$.
 
-\paragraph{Operator.}
+\begin{example}
+  Let $\phi = \{\, c_1, c_2, c_e \,\}$ be a formula with clauses (constants lowercase, variables uppercase)
+  \begin{align*}
+    c_1 &= (\emptyset, \{\, (Y, X) \,\}, \{\, X \mapsto b^\top, Y \mapsto b^\top \,\}), \\
+    c_2 &= (\{\, \neg p(X, Y), \neg p(X, Z) \,\}, \{\, (X, x), (Y, Z) \,\}, \{\, X \mapsto a, Y \mapsto b^\bot, Z \mapsto b^\bot \,\}), \\
+    c_3 &= (\{\, \neg p(X, Y), \neg p(Z, Y) \,\}, \{\, (X, x), (Z, X), (Z, x) \,\}, \{\, X \mapsto a, Y \mapsto b^\bot, Z \mapsto a \,\}).
+  \end{align*}
+  Domain $a$ and with its element $x \in a$ satisfy the preconditions for constraint removal. The operator introduces a new domain $a'$ and transforms $\phi$ to $\phi' = (c_1', c_2', c_3')$, where
+  \begin{align*}
+    c_1' &= c_1 \\
+    c_2' &= (\{\, \neg p(X, Y), \neg p(X, Z) \,\}, \{\, (Y, Z) \,\}, \{\, X \mapsto a', Y \mapsto b^\bot, Z \mapsto b^\bot \,\}) \\
+    c_3' &= (\{\, \neg p(X, Y), \neg p(Z, Y) \,\}, \{\, (Z, X) \,\}, \{\, X \mapsto a', Y \mapsto b^\bot, Z \mapsto a' \,\}).
+  \end{align*}
+\end{example}
 

### 2022-01-23 notes/notes.tex
Support for domain recursion on any domain

@@
 \DeclareMathOperator{\CR}{\textsc{CR}}
+\DeclareMathOperator{\DR}{\textsc{DR}}
+\DeclareMathOperator{\Reff}{\textsc{Ref}}
+
 \DeclareMathOperator{\dom}{dom}
@@
 \DeclareMathOperator{\Doms}{Doms}
+\DeclareMathOperator{\size}{size}
 \DeclareMathOperator{\Vars}{Vars}
@@
 \item notation: $\Imm$
-\item atom, literal, constant, predicate, variable
+\item atom, (positive/negative) literal, constant, predicate, variable, literal variable
 \item inequality constraint. Notation: $(x, y)$, where $x$ is a variable (of the clause), and $y$ is either a variable or a constant.
@@
 \item $\Doms$ on both formulas and clauses. $\Doms(c) = \Imm \delta_c$, and $\Doms(\phi) = \bigcup_{c \in \phi} \Doms(c)$.
-\item substitution
 \item size of a domain, how each domain is partitioned into two during compilation.
@@
 \item $\emptyset$ for an empty partial map.
+\item notation for variable substitution for literal and constraint sets: $S[x/V]$, where $S$ is the set, $V$ is a set of variable, and $x$ is the new constant or variable.
+Note that for constraint sets this could mean that a variable and a constant need to switch places.
+\item During inference, there is a domain size map $\size\colon \mathscr{D} \to \mathbb{N}_0$.
 \end{itemize}
@@
 \item maybe $c[\beta, \gamma]$ is better than $c \ast (\beta, \gamma)$
-\item avoid using lowercase latin letters for everything: capitalise domains and variables.
+\item capitalise variable names.
 \end{itemize}
@@
 
-This $\rho$ is saved as a parameter of the new circuit node. During inference, there is a domain size map $\sigma\colon \mathscr{D} \to \mathbb{N}_0$, which gets updated to
+$\WMC(\Reff_\rho(n), \size) = \WMC(n, \size')$ ($n$ is the target circuit node), where $\size'$ is defined as
 \[
-\sigma'(x) =
+\size'(x) =
 \begin{cases}
-  \sigma(\rho(x)) & \text{if } x \in \dom(\rho) \\
-  \sigma(x) & \text{otherwise}
+  \size(\rho(x)) & \text{if } x \in \dom(\rho) \\
+  \size(x) & \text{otherwise}
 \end{cases}
@@
 \section{New Operations}
-
-TODO: compilation rules, node types, their evaluation during inference.
 
@@
 
-\subsection{Improved Domain Recursion}
+\paragraph{Evaluation.} $\WMC(\CR_{d \mapsto d'}(n), \size) = \WMC(n, \size \cup \{\, d' \mapsto \size(d) - 1 \,\})$.
 
-The original version of domain recursion is here \cite{DBLP:conf/nips/Broeck11}.
+TODO: add an explanation for why the way constraints, domain recursion, and constraint removal interact ensures that domain sizes will never be negative.
+
+\subsection{A Generalisation of Domain Recursion}
+
+\begin{algorithm}[t]
+  \caption{Formula transformation for domain recursion}
+  \label{alg:domainrecursion}
+  \KwIn{formula $\phi$, domain $d \in \mathscr{D}$, and constant $x$}
+  \KwOut{formula $\phi'$}
+  $\phi' \gets \emptyset$\;
+  \ForEach{clause $c = (L, C, \delta) \in \phi$\label{line:forclause}}{
+    $V \gets \{\, v \in \Vars(L) \mid \delta(v) = d \,\}$\;
+    \ForEach{subset $W \subseteq V$ such that $W^2 \cap C = \emptyset$ {\bf and} $W \cap \{\, v \in \Vars(C) \mid (v, y) \in C \text{ for some constant } y \,\} = \emptyset$\label{line:conditions}}{
+      $\phi' \gets \phi' \cup \{\, (L[x/W], C[x/W] \cup \{\, (v, x) \mid (v \in V \setminus W) \,\}, \delta') \,\}$\;
+      \tcc{$\delta'$ is the restriction of $\delta$ to the new set of variables}
+    }
+  }
+\end{algorithm}
+
+TODO: Compare with the original. The original version of domain recursion is here \cite{DBLP:conf/nips/Broeck11}.
+
+TODO: introduce $\phi$.
+
+\paragraph{Precondition.} Domain recursion can be applied to domain $d \in \mathscr{D}$ if there is a clause $c$ with a literal variable $v \in \Vars(L_c)$ such that $\delta_c(v) = d$.
+
+\paragraph{Operator.} First, introduce a new constant $x$. Then $\DR(\phi) = \DR_d(\Compile(\phi'))$, where $\phi'$ is generated by \cref{alg:domainrecursion}.
+
+\begin{example}
+  Let $\phi = \{\, c_1, c_2 \,\}$ be a formula, where
+  \begin{align*}
+    c_1 &= (\{\, \neg p(X, Y), \neg p(X, Z) \,\}, \{\, (Z, Y) \,\}, \{ X \mapsto a, Y \mapsto b, Z \mapsto b \}), \\
+    c_2 &= (\{\, \neg p(X, Y), \neg p(Z, Y) \,\}, \{\, (Z, X) \,\}, \{ X \mapsto a, Y \mapsto b, Z \mapsto a \}).
+  \end{align*}
+  While domain recursion is possible on both domains, here we illustrate how it works on $a$.
+
+  Suppose \cref{line:forclause} picks $c = c_1$ first. Then $V = \{\, X \,\}$. Both subsets of $V$ satisfy the conditions on \cref{line:conditions} and generate new clauses
+  \[
+  (\{\, \neg p(X, Y), \neg p(X, Z) \,\}, \{\, (Z, Y), (X, x) \,\}, \{ X \mapsto a, Y \mapsto b, Z \mapsto b \}),
+  \]
+  (from $W = \emptyset$) and
+  \[
+  (\{\, \neg p(x, Y), \neg p(x, Z) \,\}, \{\, (Z, Y) \,\}, \{ Y \mapsto b, Z \mapsto b \})
+  \]
+  (from $W = V$).
+
+  When $c = c_2$, then $V = \{\, X, Z \,\}$.
+The subset $W = V$ fails to satisfy the first condition because of the $Z \ne X$ constraint; without this condition, the resulting clause would have an unsatisfiable constraint $x \ne x$.
+The other three subsets of $V$ all generate clauses for $\phi'$:
+  \[
+  (\{\, \neg p(X, Y), \neg p(Z, Y) \,\}, \{\, (Z, X), (X, x), (Z, x) \,\}, \{ X \mapsto a, Y \mapsto b, Z \mapsto a \})
+  \]
+  (from $W = \emptyset$),
+  \[
+  (\{\, \neg p(x, Y), \neg p(Z, Y) \,\}, \{\, (Z, x) \,\}, \{ Y \mapsto b, Z \mapsto a \})
+  \]
+  (from $W = \{\, X \,\}$), and
+  \[
+  (\{\, \neg p(X, Y), \neg p(x, Y) \,\}, \{\, (X, x) \,\}, \{ X \mapsto a, Y \mapsto b, \})
+  \]
+  (from $W = \{\, Z \,\}$).
+\end{example}
+
+\paragraph{Evaluation.}
+\[
+\WMC(\DR_d(n), \size) =
+\begin{cases}
+  \WMC(n, \size) & \text{if } \size(d) > 0 \\
+  1 & \text{otherwise.}
+\end{cases}
+\]
+
+One is picked as the multiplicative identity.
 
@@
 
-TODO: algebraic/graphical representation, what info they hold, and how they're created
+TODO: algebraic/graphical representations
 
 TODO: describe evaluation of: and, counting, constraint removal, ref, unit, contradiction, improved domain recursion. Most of this will be from \cite{DBLP:conf/ijcai/BroeckTMDR11}.
+
+\section{Examples}
+
+\subsection{Counting Partial Injections}
 

### 2022-01-27 notes/notes.tex
Add the original version of Forclift
Some writing: definitions and descriptions of operators

@@
 
+\makeatletter
+\newcommand\incircbin
+    {%
+      \mathpalette\@incircbin
+    }
+    \newcommand\@incircbin[2]
+                          {%
+                            \mathbin%
+                                {%
+                                  \ooalign{\hidewidth$#1#2$\hidewidth\crcr$#1\bigcirc$}%
+                                }%
+                          }
+                          \newcommand{\oland}{\incircbin{\land}}
+                          \newcommand{\olor}{\incircbin{\lor}}
+                          \newcommand{\Contradiction}{\incircbin{\bot}}
+                          \newcommand{\Tautology}{\incircbin{\top}}
+                          \newcommand{\Smoothing}{\incircbin{}}
+                          \newcommand{\Unit}{\incircbin{1}}
+                          \makeatother
+
 \newcommand\pfun{\mathrel{\ooalign{\hfil$\mapstochar\mkern5mu$\hfil\cr$\to$\cr}}}
@@
 \DeclareMathOperator{\DR}{\textsc{DR}}
+\DeclareMathOperator{\IE}{\textsc{IE}}
 \DeclareMathOperator{\Reff}{\textsc{Ref}}
+\DeclareMathOperator{\wwp}{w}
+\DeclareMathOperator{\wwn}{\overline{w}}
 
@@
 \DeclareMathOperator{\Doms}{Doms}
-\DeclareMathOperator{\size}{size}
+\DeclareMathOperator{\size}{\sigma}
 \DeclareMathOperator{\Vars}{Vars}
 \DeclareMathOperator{\WMC}{WMC}
+\DeclareMathOperator{\gr}{gr}
 
@@
 \begin{itemize}
-\item notation: $\Imm$
-\item atom, (positive/negative) literal, constant, predicate, variable, literal variable
-\item inequality constraint. Notation: $(x, y)$, where $x$ is a variable (of the clause), and $y$ is either a variable or a constant.
+\item atom, (positive/negative) literal, constant, predicate, variable, literal variable, clause, unit clause
 \item $\Vars$, $\Vars(c) = \Vars(L) \cup \Vars(C)$
 \item $\Doms$ on both formulas and clauses. $\Doms(c) = \Imm \delta_c$, and $\Doms(\phi) = \bigcup_{c \in \phi} \Doms(c)$.
-\item size of a domain, how each domain is partitioned into two during compilation.
-\item maybe: notation for partial function, notation for powerset, domain size
-\item notation for projection (or avoid it?)
-\item $\WMC$
-\item constraint removal operation
+\item maybe: notation for partial function, notation for powerset, notation for disjoint union, domain size
+\item $\WMC$, $\wwp$, $\wwn$, $\Imm$
 \item two parts: compilation and inference.
@@
 \end{itemize}
-
-Let $\mathscr{V}$ be the set of circuit nodes.
 
@@
 
+Most of the definitions here are adaptations/formalisations of \cite{DBLP:conf/ijcai/BroeckTMDR11} and the corresponding code.
+
 \begin{definition}
-  A \emph{domain} is a set with elements not used anywhere else.\footnote{In the context of functions, the domain of a function $f$ retains its usual meaning and is denoted $\dom(f)$.} Let $\mathscr{D}$ be the set of all domains and $\mathscr{C} \subset \mathscr{D}$ be the subset of domains introduced as a consequence of constraint removal.
+  A \emph{domain} is a symbol for a finite set.\footnote{In the context of functions, the domain of a function $f$ retains its usual meaning and is denoted $\dom(f)$.} Let $\mathscr{D}$ be the set of all domains and $\mathscr{C} \subset \mathscr{D}$ be the subset of domains introduced as a consequence of constraint removal.
 Note that both sets (can) expand during the compilation phase.
@@
 \begin{definition}
-  A \emph{clause} is a triple $c = (L, C, \delta_c)$, where $L$ is the set of literals, $C$ is a set of inequality constraints, and $\delta_c\colon \Vars(c) \to \mathscr{D}$ is a function that maps all variables in $c$ to their domains.
+An \emph{(inequality) constraint} is a pair $(a, b)$, where $a$ is a variable, and $b$ is either a variable or a constant.
+\end{definition}
+
+% TODO: so far I'm not using equivalence anywhere
+\begin{definition}
+  A \emph{clause} is a triple $c = (L, C, \delta_c)$, where $L$ is the set of literals, $C$ is a set of inequality constraints, and $\delta_c\colon \Vars(c) \to \mathscr{D}$ is a function that maps all variables in $c$ to their domains such that if $(x, y) \in C$ for some variables $x$ and $y$, then $\delta_c(x) = \delta_c(y)$.
+
   Two clauses $c$ and $d = (L', C', \delta_d)$ are \emph{isomorphic} (written $c \cong d$) if there is a bijection $\beta\colon \Vars(c) \to \Vars(d)$ such that $c\beta = d\beta$.
@@
 The hash code of a formula $\phi$ combines the hash codes of all its clauses and is denoted $\#\phi$.
+
+\begin{definition}
+  Let $\gr(\cdot; \sigma)$ be the function (parameterised by the domain size function $\size$) that takes a clause $c = (L, C, \delta)$ and returns the number of ways the variables in $c$ can be replaced by elements of their respective domains in a way that satisfies the inequality constraints.\footnote{Note that the literals of the clause have no effect on $\gr$.} Formally, for each variable $v \in \Vars(c)$, let $C_v = \{ w \mid (u, w) \in C \setminus \Vars(c)^2 \text{, }u \ne v \}$ be the set of (explicitly named) constants that $v$ is permitted to be equal to.
+Then
+  \[
+  \gr(c; \sigma) \coloneqq \left|\left\{\, (e_v)_{v \in \Vars(c)} \in \prod_{v \in \Vars(c)} C_v \sqcup [\sigma(\delta(v)) - |C_v|] \;\middle|\; \right.\right.
+e_u \ne e_w \text{ for all } (u, w) \in C \cap \Vars(c)^2 \left.\left.
+\vphantom{\prod_{v \in \Vars(c)}} \,\right\}\right|
+  \]
+  for any clause $c$. (Here, $[n] \coloneqq \{\,1, 2, \dots, n\,\}$ for any non-negative integer $n$.)
+\end{definition}
+
+TODO: how does the algorithm prevent the number in $[\cdot]$ from being negative?
 
@@
 
-$\WMC(\Reff_\rho(n), \size) = \WMC(n, \size')$ ($n$ is the target circuit node), where $\size'$ is defined as
+$\WMC(\Reff_\rho(n); \size) = \WMC(n; \size')$ ($n$ is the target circuit node), where $\size'$ is defined as
 \[
@@
 
-\paragraph{Evaluation.} $\WMC(\CR_{d \mapsto d'}(n), \size) = \WMC(n, \size \cup \{\, d' \mapsto \size(d) - 1 \,\})$.
-
-TODO: add an explanation for why the way constraints, domain recursion, and constraint removal interact ensures that domain sizes will never be negative.
+\paragraph{Evaluation.}
+\[
+\WMC(\CR_{d \mapsto d'}(n); \size) =
+\begin{cases}
+  \WMC(n; \size \cup \{\, d' \mapsto \size(d) - 1 \,\}) & \text{if } \size(d) > 0 \\
+  0 & \text{otherwise.}
+\end{cases}
+\]
 
@@
 \[
-\WMC(\DR_d(n), \size) =
+\WMC(\DR_d(n); \size) =
 \begin{cases}
-  \WMC(n, \size) & \text{if } \size(d) > 0 \\
+  \WMC(n; \size) & \text{if } \size(d) > 0 \\
   1 & \text{otherwise.}
@@
 
-\section{Circuit Evaluation}
+\section{Circuit Nodes Types and Their Evaluations}
 
-TODO: algebraic/graphical representations
+Along with the three circuit node types described above, here are all the other ones. This section is mostly just taken from \cite{DBLP:conf/ijcai/BroeckTMDR11} but with some changes in notation.
 
-TODO: describe evaluation of: and, counting, constraint removal, ref, unit, contradiction, improved domain recursion. Most of this will be from \cite{DBLP:conf/ijcai/BroeckTMDR11}.
+TODO: explain that $x, y, z$ refer to nodes, $c$ refers to a clause, and describe each node type in a bit more detail.
+
+\begin{description}
+\item[tautology] $\WMC(\Tautology; \size) = 1$
+\item[contradiction] $\WMC(\Contradiction c; \size) = 0^{\gr(c; \size)}$
+\item[unit clause]
+  \[
+  \WMC(\Unit c; \size) =
+  \begin{cases}
+    \wwp(p)^{\gr(c; \size)} & \text{if the literal is positive} \\
+    \wwn(p)^{\gr(c; \size)} & \text{otherwise,}
+  \end{cases}
+  \]
+  where $p$ is the predicate of the literal.
+\item[smoothing] $\WMC(\Smoothing c; \size) = (\wwp(p) + \wwn(p))^{\gr(c; \size)}$, where $p$ is the predicate of the literal.
+\item[decomposable conjunction] $\WMC(x \oland y; \size) = \WMC(x; \size) \times \WMC(y; \size)$
+\item[deterministic disjunction] $\WMC(x \olor y; \size) = \WMC(x; \size) + \WMC(y; \size)$
+\item[decomposable set-conjunction] $\WMC(\oland_D x; \size) = \WMC(x; \size)^{\size(D)}$
+\item[deterministic set-disjunction] $\WMC(\olor_{D \subseteq S} x; \size) = \sum_{d = 0}^{\size(S)} \binom{\size(S)}{d} \WMC(x; \size \cup \{\, D \mapsto d \,\})$
+\item[inclusion-exclusion] $\WMC(\IE(x, y, z); \size) = \WMC(x; \size) + \WMC(y; \size) - \WMC(z; \size)$
+\end{description}
 

### 2022-01-30 notes/notes.tex
A polynomial-time solution to counting bijections!

@@
 
+\newtheorem{theorem}{Theorem}
 \theoremstyle{definition}
@@
 \newtheorem{example}{Example}
+\newtheorem{observation}{Observation}
+\theoremstyle{remark}
+\newtheorem*{remark}{Remark}
 
@@
 
+TODO: define 'circuit' (or something similar). Note that circuits are rooted.
+
+\subsection{Observations and Theoretical Results}
+
+TODO: explain how circuits and domain sizes connect to functions on integers
+
+\begin{observation}
+  Let $n$ be a positive integer and $d \in \mathscr{D}$ a domain. Then one can construct a circuit $x$ such that
+  \[
+  \WMC(x; \size) =
+  \begin{cases}
+    0 & \text{if } \size(d) \ge n \\
+    \WMC(y; \size) & \text{otherwise,}
+  \end{cases}
+  \]
+  where $y$ is a circuit node of arbitrary type. Indeed, $(\Contradiction c) \oland y$ is such a circuit, where $c = (L, C, \delta)$ is a clause with $n$ variables $(v_i)_{i=1}^n$ such that:
+  \begin{itemize}
+  \item $L$ is unimportant,
+  \item $C = \{\, (v_i, v_j) \mid i = 1, \dots, n - 1\text{, }j = i + 1, \dots, n \,\}$,
+  \item and $\delta(v_i) = d$ for all $i = 1, \dots, n$.
+  \end{itemize}
+  TODO: explain why this works.
+\end{observation}
+
+\begin{remark}
+  Such (sub)circuits can be constructed automatically using compilation rules, although $n$ is upper bounded by the maximum number of variables in any clause of the input formula since there is no rule that would introduce new variables.
+\end{remark}
+
+Intuition: although one can return zero if the size of a domain is too big, there is no way to do the same if the domain size is too small.
+And this turns out to be crucial for computing factorials and constructing recursive subcircuits that compare the sizes of two domains.
+
+\begin{theorem}
+  There is no circuit $x$ such that
+  \[
+  \WMC(x; \size) =
+  \begin{cases}
+    0 & \text{if } \size(d) = 0 \\
+    \WMC(y; \size) & \text{otherwise,}
+  \end{cases}
+  \]
+  where $y$ is a circuit node of arbitrary type.
+\end{theorem}
+\begin{proof}
+  Let us consider all possible root node types.
+\end{proof}
+
 \section{Examples}

### 2022-01-31 notes/notes.tex
Pseudocode for tryCache

@@
 \begin{itemize}
-\item later: maybe mathcal instead of mathscr
+\item should I always say `compilation rule' instead of `operator'?
+\item maybe mathcal instead of mathscr
 \item maybe $\pi$ is global enough to have a more unique name
@@
 
+\begin{algorithm}[t]
+  \caption{A generalised version of the compilation rule that uses \cref{alg:recursion} to add $\Reff$ nodes (i.e., the edges that make the circuit no longer a tree) to the circuit}
+  \label{alg:trycache}
+  \SetKwData{compilationCache}{compilationCache}
+  \KwIn{formula $\phi$}
+  \KwOut{a $\Reff$ circuit node (or \texttt{null})}
+  \ForEach{$(\psi, n) \in \compilationCache{$\#\psi$}$}{
+    $\rho \gets \identifyRecursion{$\phi$, $\psi$}$\;
+    \lIf{$\rho \ne {\normalfont \texttt{null}}$}{\Return{$\Reff_\rho(n)$}}
+  }
+  \Return{\normalfont \texttt{null}}\;
+\end{algorithm}
+
 \begin{figure}[t]
@@
 \begin{itemize}
+\item introduce/describe \cref{alg:recursion} and \cref{alg:trycache} and describe the cache that's being used.
 \item explain why $\rho \cup \gamma$ is possible
@@
 \item new rules that don't create nodes (e.g., duplicate removal, unconditional contradiction detection, etc.)
+\item my search algorithm
+\item some notes on halting
+  \begin{itemize}
+  \item Search is infinite. Some rules increase the size of the formula(s), but most reduc it.
+  \item Inference is guaranteed to terminate if at least one domain shrinks by at least one.
+But note that allowing recursive calls with the same domain sizes (e.g., $f(n) = f(n) + \dots$) could be useful because these problematic terms might cancel out.
+  \item It's impossible for $n \gets n - 1$ and $\texttt{for } n \in \dots$ to combine in a way that results in an infinite loop.
+  \end{itemize}
 \end{itemize}
@@
 
-Intuition: although one can return zero if the size of a domain is too big, there is no way to do the same if the domain size is too small.
-And this turns out to be crucial for computing factorials and constructing recursive subcircuits that compare the sizes of two domains.
-
-\begin{theorem}
-  There is no circuit $x$ such that
-  \[
-  \WMC(x; \size) =
-  \begin{cases}
-    0 & \text{if } \size(d) = 0 \\
-    \WMC(y; \size) & \text{otherwise,}
-  \end{cases}
-  \]
-  where $y$ is a circuit node of arbitrary type.
-\end{theorem}
-\begin{proof}
-  Let us consider all possible root node types.
-\end{proof}
-
 \section{Examples}
 
-\subsection{Counting Partial Injections}
+For both one domain and two domains:
+\begin{itemize}
+\item bijections
+\item injections
+\item partial injections
+\end{itemize}
+
+\section{Conclusions and Future Work}
+
+\begin{itemize}
+\item Transform circuits to definitions of (possibly recursive) functions on integers. Use a computer algebra system to simplify them.
+\item Design an algorithm to infer the necessary base cases. (Note that there can be an infinite amount of them when functions have more than one parameter.)
+\end{itemize}
 

### 2022-02-13 notes/notes.tex
Some writing about search, base cases, etc.

@@
 
-\title{Empowering Domain Recursion in Symmetric Weighted First-Order Model Counting}
+\title{Recursive Solutions to First-Order Model Counting}
 
@@
 
-\section{Basic Definitions}
+\section{Definitions}
 
@@
 \item capitalise variable names.
+\item introduce/use notation for vertices, edges of a graph
 \end{itemize}
@@
 TODO: how does the algorithm prevent the number in $[\cdot]$ from being negative?
+
+\section{Search}
+
+\begin{definition}
+  A \emph{first-order deterministic decomposable negation normal form computational graph} (FCG) is a (weakly connected) directed graph with a a single source, node labels, and ordered direct successors.
+We denote an FCG as $G = (V, s, N^+)$, where $V$ is the set of nodes, $s \in V$ is the source, and $N^+$ is the direct successor function that maps each node in $V$ to a list that contains either other nodes in $V$ or $\star$, which means that the target of the edge is yet to be determined.
+For each $v \in V$, the length of the list $N^+(v)$ is determined by the label of $v$.
+
+\end{definition}
+
+\paragraph{TODO.}
+\begin{itemize}
+\item explain the connection to the algebraic formalism (or just don't use it).
+% We will also use algebraic notation to describe (parts of) circuits: circuittype_parameters(nodes pointed to by the outedges)
+\item define `an FCG for a formula'
+\item need an example
+\item vertex or node, $v$ or $n$?
+\item what notation for lists (a.k.a.
+sequences) am I going to use?
+$\oplus$ for concatenation (of both two lists and an element to a list), $\in$ for (in-order) enumeration, $[]$ for an empty list, and $[x]$ for a list with one element.
+\end{itemize}
+
+\begin{definition}
+  A \emph{state} (of the search for an FCG for a given formula) is a tuple $(G, C, L)$, where:
+  \begin{itemize}
+  \item $G$ is an FCG (can be \texttt{null}),
+  \item $C$ is a compilation cache that maps integers to sets of pairs $(\phi, n)$, where $\phi$ is a formula, and $n$ is a node of $G$ (which is used to identify opportunities for recursion),
+  \item and $L$ is a list of formulas (that are yet to be compiled). (Note that the order is crucial!)
+  \end{itemize}
+\end{definition}
+
+\begin{definition}
+  A (compilation) \emph{rule} is a function that takes a formula and returns a set of $(G, L)$ pairs, where $G$ is a (potentially \texttt{null}) FCG, and $L$ is a list of formulas.
+\end{definition}
 
@@
 \begin{algorithm}[t]
-  \caption{A generalised version of the compilation rule that uses \cref{alg:recursion} to add $\Reff$ nodes (i.e., the edges that make the circuit no longer a tree) to the circuit}
+  \caption{A generalised version of the compilation rule that uses \cref{alg:recursion} to add $\Reff$ nodes (i.e., the edges that make the circuit no longer a tree) to the circuit.
+TODO: refactor to return a set of solutions.}
   \label{alg:trycache}
@@
 
-TODO: still need to connect this to tryCache.
-
 \section{New Operations}
@@
   \begin{itemize}
-  \item Search is infinite. Some rules increase the size of the formula(s), but most reduc it.
+  \item Search is infinite. Some rules increase the size of the formula(s), but most reduce it.
   \item Inference is guaranteed to terminate if at least one domain shrinks by at least one.

### 2022-02-14 notes/notes.tex
Fix a (mostly) inconsequential bug

@@
 \begin{itemize}
+\item maybe add a (vertex) labelling function and its codomain (and use it in the algorithm)? But it's only used once...
 \item explain the connection to the algebraic formalism (or just don't use it).
@@
 sequences) am I going to use?
-$\oplus$ for concatenation (of both two lists and an element to a list), $\in$ for (in-order) enumeration, $[]$ for an empty list, and $[x]$ for a list with one element.
+$\oplus$ for concatenation (of both two lists and an element to a list), $\in$ for (in-order) enumeration, $[]$ for an empty list, $[x]$ for a list with one element, $L$ for the length of the list.
 \end{itemize}
@@
   A (compilation) \emph{rule} is a function that takes a formula and returns a set of $(G, L)$ pairs, where $G$ is a (potentially \texttt{null}) FCG, and $L$ is a list of formulas.
+TODO: add an example showing that it's usually an FCG with one node and a bunch of $\star$'s marking a fixed number of outedges.
 \end{definition}
+
+We assume that if there is a pair $(\texttt{null}, L)$ in the set returned by a rule, then $|L| = 1$, i.e., the rule transformed the formula without creating any nodes.
+
+\begin{algorithm}[t]
+  \caption{The search algorithm}
+  \label{alg:search}
+  \SetKwData{solutions}{solutions}
+  \SetKwProg{Fn}{Function}{:}{}
+  \SetKwFunction{applyGreedyRules}{applyGreedyRules}
+  \SetKwFunction{applyNonGreedyRules}{applyNonGreedyRules}
+  \SetKwFunction{put}{put}
+  \SetKwFunction{get}{get}
+  \SetKwFunction{emptyy}{empty}
+  \SetKwFunction{updateCache}{updateCache}
+  \KwData{a set of greedy rules $\Gamma$}
+  \KwData{a set of non-greedy rules $\Delta$}
+  \KwData{a formula $\phi_0$}
+  \KwResult{all found FCGs for $\phi_0$ are in the set \solutions}
+  $\solutions \gets \emptyset$\;
+  $C_0 \gets \emptyset$\;
+  $(G_0, C_0, L_0) \gets \applyGreedyRules{$\phi_0$, $C_0$}$\;
+  \lIf{$L_0 = []$}{$\solutions \gets \solutions \cup \{\, G_0 \,\}$}
+  \Else{
+    $q \gets \text{an empty queue of states}$\;
+    $q.\put{$(G_0, C_0, L_0)$}$\;
+    \While{{\bf not} $q.\emptyy{}$}{
+      \ForEach{state $(G, C, L) \in \applyNonGreedyRules{$q.\get{}$}$}{
+        \lIf{$L = []$}{$\solutions \gets \solutions \cup \{\, G \,\}$}
+        \lElse{$q.\put{$(G, C, L)$}$}
+      }
+    }
+  }
+  \Fn{\applyGreedyRules{$\phi$, $C$}}{
+    \ForEach{rule $r \in \Gamma$}{
+      $S \gets r(\phi)$\;
+      \If{$S \ne \emptyset$}{
+        $(G, L) \gets \text{any element of } S$\; % TODO: explain why this is valid for greedy rules
+        \lIf{$G = {\normalfont \texttt{null}}$}{\Return{\applyGreedyRules{the only element of $L$, $C$}}}
+        \Else{
+          $(V, s, N^+) \gets G$\;
+          $C \gets \updateCache(C, \phi, s)$\;
+          % TODO: continue here
+        }
+      }
+    }
+    \Return{$({\normalfont \texttt{null}}, C, [\phi])$}\;
+  }
+\end{algorithm}
 

### 2022-02-15 notes/notes.tex
Describe search

@@
 \item During inference, there is a domain size map $\size\colon \mathscr{D} \to \mathbb{N}_0$.
+\item $\sqcup$ for both sets and functions
 \end{itemize}
@@
 \item define `an FCG for a formula'
-\item need an example
 \item vertex or node, $v$ or $n$?
@@
 sequences) am I going to use?
-$\oplus$ for concatenation (of both two lists and an element to a list), $\in$ for (in-order) enumeration, $[]$ for an empty list, $[x]$ for a list with one element, $L$ for the length of the list.
+$\oplus$ for concatenation (of both two lists and an element to a list), $\in$ for (in-order) enumeration, $[]$ for an empty list, $[x]$ for a list with one element, $|L|$ for the length of the list, and $h : t$ to denote a list with first element (a.k.a.
+head) $h$ and remaining list (a.k.a.
+tail) $t$.
+\item use Greek letters for compilation rules
 \end{itemize}
@@
 \begin{algorithm}[t]
-  \caption{The search algorithm}
+  \caption{The (main part of the) search algorithm}
   \label{alg:search}
+  \SetKwProg{Fn}{Function}{:}{}
   \SetKwData{solutions}{solutions}
-  \SetKwProg{Fn}{Function}{:}{}
   \SetKwFunction{applyGreedyRules}{applyGreedyRules}
@@
   \SetKwFunction{emptyy}{empty}
-  \SetKwFunction{updateCache}{updateCache}
-  \KwData{a set of greedy rules $\Gamma$}
-  \KwData{a set of non-greedy rules $\Delta$}
-  \KwData{a formula $\phi_0$}
+  \KwIn{a formula $\phi_0$}
   \KwResult{all found FCGs for $\phi_0$ are in the set \solutions}
@@
   $(G_0, C_0, L_0) \gets \applyGreedyRules{$\phi_0$, $C_0$}$\;
-  \lIf{$L_0 = []$}{$\solutions \gets \solutions \cup \{\, G_0 \,\}$}
+  \lIf{$L_0 = []$}{$\solutions \gets \{\, G_0 \,\}$}
   \Else{
@@
   }
+\end{algorithm}
+
+\begin{algorithm}
+  \caption{Functions used in \cref{alg:search} for applying compilation rules}
+  \label{alg:apply}
+  \SetKwProg{Fn}{Function}{:}{}
+  \SetKwData{newStates}{newStates}
+  \SetKwFunction{applyGreedyRules}{applyGreedyRules}
+  \SetKwFunction{applyNonGreedyRules}{applyNonGreedyRules}
+  \SetKwFunction{applyGreedyRulesToAllFormulas}{applyGreedyRulesToAllFormulas}
+  \SetKwFunction{mergeFcgs}{mergeFcgs}
+  \SetKwFunction{updateCache}{updateCache}
+  \KwData{a set of greedy rules $\Gamma$}
+  \KwData{a set of non-greedy rules $\Delta$}
   \Fn{\applyGreedyRules{$\phi$, $C$}}{
@@
       \If{$S \ne \emptyset$}{
-        $(G, L) \gets \text{any element of } S$\; % TODO: explain why this is valid for greedy rules
+        $(G, L) \gets \text{any element of } S$\;
         \lIf{$G = {\normalfont \texttt{null}}$}{\Return{\applyGreedyRules{the only element of $L$, $C$}}}
@@
           $C \gets \updateCache(C, \phi, s)$\;
-          % TODO: continue here
+          \Return{\applyGreedyRulesToAllFormulas{$G$, $C$, $L$}}\;
         }
@@
   }
+  \Fn{\applyGreedyRulesToAllFormulas{$G$, $C$, $L$}}{
+    $(V, s, N^+) \gets G$\;
+    $N^+(s) \gets []$\;
+    $L' \gets []$\;
+    \ForEach{formula $\phi \in L$}{
+      $(G', C, L'') \gets \applyGreedyRules{$\phi$, $C$}$\;
+      $L' \gets L' \oplus L''$\;
+      \lIf{$G' = {\normalfont \texttt{null}}$}{$N^+(s) \gets N^+(s) \oplus [\star]$}
+      \Else{
+        $(V', s', N') \gets G'$\;
+        $V \gets V \sqcup V'$\;
+        $N^+ \gets N^+ \sqcup N'$\;
+        $N^+(s) \gets N^+(s) \oplus [s']$\;
+      }
+    }
+    \Return{$((V, s, N^+), C, L')$}\;
+  }
+  \Fn{\applyNonGreedyRules{$s$}}{
+    $(G, C, L) \gets s$\;
+    $\phi : T \gets L$\;
+    $(G', C', L') \gets \text{a copy of } s$\;
+    $\newStates \gets []$\;
+    \ForEach{rule $r \in \Delta$}{
+      \ForEach{$(G'', L'') \in r(\phi)$}{
+        \lIf{$G'' = {\normalfont \texttt{null}}$}{$\newStates \gets \newStates \oplus \applyNonGreedyRules{$(G', C', L'')$}$}
+        \Else{
+          $(V, s, N^+) \gets G''$\;
+          $C' \gets \updateCache{$C'$, $\phi$, $s$}$\;
+          $(G'', C', L'') \gets \applyGreedyRulesToAllFormulas{$G''$, $C'$, $L''$}$\;
+          \lIf{$G' = {\normalfont \texttt{null}}$}{$\newStates \gets \newStates \oplus [(G'', C', L'' \oplus T)]$}
+          \lElse{$\newStates \gets \newStates \oplus [(\mergeFcgs{$G'$, $G''$}, C', L'' \oplus T)]$}
+        }
+      }
+      $(G', C', L') \gets \text{a copy of } s$\;
+    }
+    \Return{\newStates}\;
+  }
 \end{algorithm}
+
+\begin{algorithm}
+  \caption{Helper functions used by \cref{alg:apply}}
+  \label{alg:helpers}
+  \SetKwProg{Fn}{Function}{:}{}
+  \SetKwFunction{mergeFcgs}{mergeFcgs}
+  \SetKwFunction{updateCache}{updateCache}
+  \Fn{\updateCache{$C$, $\phi$, $v$}}{
+    \lIf{$\#\phi \not\in \dom(C)$}{\Return{$C \cup \{\, \#\phi \mapsto (\phi, v) \,\}$}}
+    \lIf{there is no $(\phi', v') \in C(\#\phi)$ such that $v' = v$}{$C(\#\phi) \gets (\phi, v) \oplus C(\#\phi)$}
+    \Return{$C$}\;
+  }
+  \Fn{\mergeFcgs{$G = (V, s, N^+)$, $G' = (V', s', N')$, $r = s$}}{
+    \lIf{$r$ has label \textsc{Ref}}{\Return{\normalfont \texttt{null}}}
+    \ForEach{$t \in N^+(r)$}{
+      \If{$t = \star$}{
+        replace $t$ with $s'$ in $N^+(r)$\;
+        \Return{$(V \sqcup V', s, N^+ \sqcup N')$}\;
+      }
+      $G'' \gets \mergeFcgs{$G$, $G'$, $t$}$\;
+      \lIf{$G'' \ne {\normalfont \texttt{null}}$}{\Return{$G''$}}
+    }
+    \Return{\normalfont \texttt{null}}\;
+  }
+\end{algorithm}
+
+\paragraph{TODO}
+\begin{itemize}
+\item maybe `applyAllRules' is a better name
+\item explain the `tail' part of the algorithm
+\end{itemize}
+
+Note: At the end, \texttt{mergeFcgs} will never return \texttt{null} because there is going to be at least one $\star$ in $G$ and the function will find it.
 

### 2022-02-17 notes/notes.tex
Description of smoothing

@@
 
-\usetikzlibrary{arrows,fit,positioning,trees,cd}
+\usetikzlibrary{fit,positioning,trees,cd}
+\usetikzlibrary{shapes}
+\usetikzlibrary{arrows}
+\usetikzlibrary{arrows.meta}
 
@@
 
+\begin{figure}[t]
+  \centering
+  \begin{tikzpicture}[triangle/.style = {regular polygon, regular polygon sides=3}]
+    \node[draw,ellipse] (a) at (0, 0) {$\phi(n)$};
+    \node[draw,ellipse] (b) at (0, -2) {$\psi(n-1)$};
+    \node[draw,ellipse] (c) at (-1, -4) {$\phi(n-1)$};
+    \node[draw,triangle] (d) at (1, -4) {};
+    \draw[-{Latex[length=2mm]}] (a) -- (b) node [midway,xshift=50] {domain recursion};
+    \draw[-{Latex[length=2mm]}] (b) -- (c);
+    \draw[-{Latex[length=2mm]}] (b) -- (d);
+    \draw[-{Latex[length=2mm]}] (c) to [bend left=45] node [midway,xshift=-30] () {$n \mapsto n-1$} (a);
+  \end{tikzpicture}
+  \caption{An illustration of the main idea. TODO: refer to this in the introduction.}
+\end{figure}
+
 \paragraph{Things I might need to explain.}
@@
 \item $\sqcup$ for both sets and functions
+\item mention which rules are in $\Gamma$ and which ones are in $\Delta$ (and why tryCache has to be in $\Delta$).
 \end{itemize}
@@
 \item introduce/use notation for vertices, edges of a graph
+\item maybe `plus-plus' is better than $\oplus$
+\item maybe put each function into its own algorithm environment, using the caption for the function name
 \end{itemize}
@@
 
-\section{Search}
+\section{Search/Compilation}
 
@@
   A \emph{first-order deterministic decomposable negation normal form computational graph} (FCG) is a (weakly connected) directed graph with a a single source, node labels, and ordered direct successors.
-We denote an FCG as $G = (V, s, N^+)$, where $V$ is the set of nodes, $s \in V$ is the source, and $N^+$ is the direct successor function that maps each node in $V$ to a list that contains either other nodes in $V$ or $\star$, which means that the target of the edge is yet to be determined.
-For each $v \in V$, the length of the list $N^+(v)$ is determined by the label of $v$.
+We denote an FCG as $G = (V, s, N^+, \lambda)$, where $V$ is the set of nodes, $s \in V$ is the source, $N^+$ is the direct successor function that maps each node in $V$ to a list that contains either other nodes in $V$ or $\star$, which means that the target of the edge is yet to be determined, and $\lambda\colon V \to \mathscr{L}$ is the vertex-labelling function with some codomain $\mathscr{L}$, which is assumed to be the same for all FCGs.
+For each $v \in V$, the length of the list $N^+(v)$ is determined by $\lambda(v)$.
 
@@
 \begin{itemize}
-\item maybe add a (vertex) labelling function and its codomain (and use it in the algorithm)? But it's only used once...
 \item explain the connection to the algebraic formalism (or just don't use it).
@@
 tail) $t$.
+Also add an example of the list comprehension notation.
 \item use Greek letters for compilation rules
@@
         \Else{
-          $(V, s, N^+) \gets G$\;
+          $(V, s, N^+, \lambda) \gets G$\;
           $C \gets \updateCache(C, \phi, s)$\;
@@
   \Fn{\applyGreedyRulesToAllFormulas{$G$, $C$, $L$}}{
-    $(V, s, N^+) \gets G$\;
+    $(V, s, N^+, \lambda) \gets G$\;
     $N^+(s) \gets []$\;
@@
       \Else{
-        $(V', s', N') \gets G'$\;
+        $(V', s', N', \lambda') \gets G'$\;
         $V \gets V \sqcup V'$\;
@@
         $N^+(s) \gets N^+(s) \oplus [s']$\;
+        $\lambda \gets \lambda \sqcup \lambda'$\;
       }
     }
-    \Return{$((V, s, N^+), C, L')$}\;
+    \Return{$((V, s, N^+, \lambda), C, L')$}\;
   }
@@
         \Else{
-          $(V, s, N^+) \gets G''$\;
+          $(V, s, N^+, \lambda) \gets G''$\;
           $C' \gets \updateCache{$C'$, $\phi$, $s$}$\;
@@
   }
-  \Fn{\mergeFcgs{$G = (V, s, N^+)$, $G' = (V', s', N')$, $r = s$}}{
-    \lIf{$r$ has label \textsc{Ref}}{\Return{\normalfont \texttt{null}}}
+  \Fn{\mergeFcgs{$G = (V, s, N^+, \lambda)$, $G' = (V', s', N', \lambda')$, $r = s$}}{
+    \lIf{$\lambda(r) = \textsc{Ref}$}{\Return{\normalfont \texttt{null}}}
     \ForEach{$t \in N^+(r)$}{
@@
         replace $t$ with $s'$ in $N^+(r)$\;
-        \Return{$(V \sqcup V', s, N^+ \sqcup N')$}\;
+        \Return{$(V \sqcup V', s, N^+ \sqcup N', \lambda \sqcup \lambda')$}\;
       }
@@
 Note: At the end, \texttt{mergeFcgs} will never return \texttt{null} because there is going to be at least one $\star$ in $G$ and the function will find it.
+
+\section{Smoothing}
+
+\begin{algorithm}
+  \SetKwData{changed}{changed}
+  \caption{Propagating atoms for smoothing across the FCG in a way that avoids infinite loops}
+  \label{alg:smoothing}
+  \KwIn{FCG $(V, s, N^+, \lambda)$}
+  \KwIn{function $\iota$ that maps labels in $\mathscr{L}$ to sets of atoms}
+  \KwIn{functions $\{\,f_l\,\}_{l \in \mathscr{L}}$ that take a list of sets of atoms and return a set of atoms}
+  \KwOut{function $S$ that maps vertices in $V$ to sets of atoms}
+  $S \gets \{\, v \mapsto \iota(\lambda(v)) \mid v \in V \,\}$\;
+  $\changed \gets \texttt{true}$\;
+  \While{\changed}{
+    $\changed \gets \texttt{false}$\;
+    \ForEach{vertex $v \in V$}{
+      $S' \gets f_{\lambda(v)}([S(w) \mid w \in N^+(v)])$\;
+      \If{$S' \ne S(v)$}{
+        $\changed \gets \texttt{true}$\;
+        $S(v) \gets S'$\;
+      }
+    }
+  }
+\end{algorithm}
+
+[Insert motivation for smoothing from Section 3.4.
+of the Forclift paper.] Originally, smoothing was (and still is) a two-step process.
+First, atoms that are still accounted for in the circuit are propagated upwards.
+Then, at nodes with certain labels, missing atoms are detected and additional sinks are created to account for them.
+If left unchanged, the first step of this process would result in an infinite loop whenever a cycle is encountered.
+\Cref{alg:smoothing} outlines how the first step can be adapted to an arbitrary directed graph.
 
@@
 \begin{itemize}
-\item domains, smoothing, and avoiding infinite cycles
 \item new rules that don't create nodes (e.g., duplicate removal, unconditional contradiction detection, etc.)
-\item my search algorithm
 \item some notes on halting
@@
 \end{description}
-
-TODO: define 'circuit' (or something similar). Note that circuits are rooted.
 

### 2022-02-17 notes/notes.tex
Some small changes

@@
 \newcommand\pfun{\mathrel{\ooalign{\hfil$\mapstochar\mkern5mu$\hfil\cr$\to$\cr}}}
+\newcommand\mdoubleplus{\mathbin{+\mkern-10mu+}}
 
@@
 \item $\Doms$ on both formulas and clauses. $\Doms(c) = \Imm \delta_c$, and $\Doms(\phi) = \bigcup_{c \in \phi} \Doms(c)$.
-\item maybe: notation for partial function, notation for powerset, notation for disjoint union, domain size
+\item maybe: notation for partial function, notation for powerset, notation for disjoint union
 \item $\WMC$, $\wwp$, $\wwn$, $\Imm$
@@
 Note that for constraint sets this could mean that a variable and a constant need to switch places.
-\item During inference, there is a domain size map $\size\colon \mathscr{D} \to \mathbb{N}_0$.
-\item $\sqcup$ for both sets and functions
+\item During inference, there is a domain size map $\size\colon \mathcal{D} \to \mathbb{N}_0$.
+\item $\sqcup$ for both sets and functions. TODO: I think I use $\cup$ elsewhere.
 \item mention which rules are in $\Gamma$ and which ones are in $\Delta$ (and why tryCache has to be in $\Delta$).
@@
 \item should I always say `compilation rule' instead of `operator'?
-\item maybe mathcal instead of mathscr
 \item maybe $\pi$ is global enough to have a more unique name
-\item maybe $c[\beta, \gamma]$ is better than $c \ast (\beta, \gamma)$
 \item capitalise variable names.
-\item introduce/use notation for vertices, edges of a graph
-\item maybe `plus-plus' is better than $\oplus$
+\item maybe introduce/use notation for vertices, edges of a graph
 \item maybe put each function into its own algorithm environment, using the caption for the function name
@@
 \begin{definition}
-  A \emph{domain} is a symbol for a finite set.\footnote{In the context of functions, the domain of a function $f$ retains its usual meaning and is denoted $\dom(f)$.} Let $\mathscr{D}$ be the set of all domains and $\mathscr{C} \subset \mathscr{D}$ be the subset of domains introduced as a consequence of constraint removal.
+  A \emph{domain} is a symbol for a finite set.\footnote{In the context of functions, the domain of a function $f$ retains its usual meaning and is denoted $\dom(f)$.} Let $\mathcal{D}$ be the set of all domains and $\mathcal{C} \subset \mathcal{D}$ be the subset of domains introduced as a consequence of constraint removal.
 Note that both sets (can) expand during the compilation phase.
 
-Let $\pi\colon \mathscr{D} \pfun \mathscr{D}$ be a partial endomorphism on $\mathscr{D}$ that denotes the \emph{parent} relation, i.e., if $\pi(d) = e$ for some $d, e \in \mathscr{D}$, then we call $e$ the parent (domain) of $d$, and $e$ a child of $d$.
+Let $\pi\colon \mathcal{D} \pfun \mathcal{D}$ be a partial endomorphism on $\mathcal{D}$ that denotes the \emph{parent} relation, i.e., if $\pi(d) = e$ for some $d, e \in \mathcal{D}$, then we call $e$ the parent (domain) of $d$, and $e$ a child of $d$.
 Intuitively, $\pi$ arranges all domains into a forest---thus, we often use graph theoretical terminology to describe properties of and relationships between domains.
@@
 
-% TODO: so far I'm not using equivalence anywhere
 \begin{definition}
-  A \emph{clause} is a triple $c = (L, C, \delta_c)$, where $L$ is the set of literals, $C$ is a set of inequality constraints, and $\delta_c\colon \Vars(c) \to \mathscr{D}$ is a function that maps all variables in $c$ to their domains such that if $(x, y) \in C$ for some variables $x$ and $y$, then $\delta_c(x) = \delta_c(y)$.
-
-  Two clauses $c$ and $d = (L', C', \delta_d)$ are \emph{isomorphic} (written $c \cong d$) if there is a bijection $\beta\colon \Vars(c) \to \Vars(d)$ such that $c\beta = d\beta$.
-TODO: we will always use this subscript notation for the $\delta$'s.
+  A \emph{clause} is a triple $c = (L, C, \delta_c)$, where $L$ is the set of literals, $C$ is a set of inequality constraints, and $\delta_c\colon \Vars(c) \to \mathcal{D}$ is a function that maps all variables in $c$ to their domains such that if $(x, y) \in C$ for some variables $x$ and $y$, then $\delta_c(x) = \delta_c(y)$.
 Equality of clauses is defined in the usual way (i.e., all variables, domains, etc.
 must match).
+TODO: we will always use this subscript notation for the $\delta$'s.
 \end{definition}
@@
 
+TODO: I'm already using the square brackets to denote lists.
+
 TODO: how does the algorithm prevent the number in $[\cdot]$ from being negative?
@@
   A \emph{first-order deterministic decomposable negation normal form computational graph} (FCG) is a (weakly connected) directed graph with a a single source, node labels, and ordered direct successors.
-We denote an FCG as $G = (V, s, N^+, \lambda)$, where $V$ is the set of nodes, $s \in V$ is the source, $N^+$ is the direct successor function that maps each node in $V$ to a list that contains either other nodes in $V$ or $\star$, which means that the target of the edge is yet to be determined, and $\lambda\colon V \to \mathscr{L}$ is the vertex-labelling function with some codomain $\mathscr{L}$, which is assumed to be the same for all FCGs.
+We denote an FCG as $G = (V, s, N^+, \lambda)$, where $V$ is the set of nodes, $s \in V$ is the source, $N^+$ is the direct successor function that maps each node in $V$ to a list that contains either other nodes in $V$ or $\star$, which means that the target of the edge is yet to be determined, and $\lambda\colon V \to \mathcal{L}$ is the vertex-labelling function with some codomain $\mathcal{L}$, which is assumed to be the same for all FCGs.
 For each $v \in V$, the length of the list $N^+(v)$ is determined by $\lambda(v)$.
@@
 sequences) am I going to use?
-$\oplus$ for concatenation (of both two lists and an element to a list), $\in$ for (in-order) enumeration, $[]$ for an empty list, $[x]$ for a list with one element, $|L|$ for the length of the list, and $h : t$ to denote a list with first element (a.k.a.
+$\mdoubleplus$ for concatenation (of both two lists and an element to a list), $\in$ for (in-order) enumeration, $[]$ for an empty list, $[x]$ for a list with one element, $|L|$ for the length of the list, and $h : t$ to denote a list with first element (a.k.a.
 head) $h$ and remaining list (a.k.a.
@@
 Also add an example of the list comprehension notation.
-\item use Greek letters for compilation rules
 \end{itemize}
@@
   \SetKwFunction{applyGreedyRules}{applyGreedyRules}
-  \SetKwFunction{applyNonGreedyRules}{applyNonGreedyRules}
+  \SetKwFunction{applyAllRules}{applyAllRules}
   \SetKwFunction{put}{put}
@@
     \While{{\bf not} $q.\emptyy{}$}{
-      \ForEach{state $(G, C, L) \in \applyNonGreedyRules{$q.\get{}$}$}{
+      \ForEach{state $(G, C, L) \in \applyAllRules{$q.\get{}$}$}{
         \lIf{$L = []$}{$\solutions \gets \solutions \cup \{\, G \,\}$}
@@
   \SetKwFunction{applyGreedyRules}{applyGreedyRules}
-  \SetKwFunction{applyNonGreedyRules}{applyNonGreedyRules}
+  \SetKwFunction{applyAllRules}{applyAllRules}
   \SetKwFunction{applyGreedyRulesToAllFormulas}{applyGreedyRulesToAllFormulas}
@@
       $(G', C, L'') \gets \applyGreedyRules{$\phi$, $C$}$\;
-      $L' \gets L' \oplus L''$\;
-      \lIf{$G' = {\normalfont \texttt{null}}$}{$N^+(s) \gets N^+(s) \oplus [\star]$}
+      $L' \gets L' \mdoubleplus L''$\;
+      \lIf{$G' = {\normalfont \texttt{null}}$}{$N^+(s) \gets N^+(s) \mdoubleplus [\star]$}
       \Else{
@@
         $N^+ \gets N^+ \sqcup N'$\;
-        $N^+(s) \gets N^+(s) \oplus [s']$\;
+        $N^+(s) \gets N^+(s) \mdoubleplus [s']$\;
         $\lambda \gets \lambda \sqcup \lambda'$\;
@@
   }
-  \Fn{\applyNonGreedyRules{$s$}}{
+  \Fn{\applyAllRules{$s$}}{
     $(G, C, L) \gets s$\;
@@
       \ForEach{$(G'', L'') \in r(\phi)$}{
-        \lIf{$G'' = {\normalfont \texttt{null}}$}{$\newStates \gets \newStates \oplus \applyNonGreedyRules{$(G', C', L'')$}$}
+        \lIf{$G'' = {\normalfont \texttt{null}}$}{$\newStates \gets \newStates \mdoubleplus \applyAllRules{$(G', C', L'')$}$}
         \Else{
@@
           $(G'', C', L'') \gets \applyGreedyRulesToAllFormulas{$G''$, $C'$, $L''$}$\;
-          \lIf{$G' = {\normalfont \texttt{null}}$}{$\newStates \gets \newStates \oplus [(G'', C', L'' \oplus T)]$}
-          \lElse{$\newStates \gets \newStates \oplus [(\mergeFcgs{$G'$, $G''$}, C', L'' \oplus T)]$}
+          \lIf{$G' = {\normalfont \texttt{null}}$}{$\newStates \gets \newStates \mdoubleplus [(G'', C', L'' \mdoubleplus T)]$}
+          \lElse{$\newStates \gets \newStates \mdoubleplus [(\mergeFcgs{$G'$, $G''$}, C', L'' \mdoubleplus T)]$}
         }
@@
     \lIf{$\#\phi \not\in \dom(C)$}{\Return{$C \cup \{\, \#\phi \mapsto (\phi, v) \,\}$}}
-    \lIf{there is no $(\phi', v') \in C(\#\phi)$ such that $v' = v$}{$C(\#\phi) \gets (\phi, v) \oplus C(\#\phi)$}
+    \lIf{there is no $(\phi', v') \in C(\#\phi)$ such that $v' = v$}{$C(\#\phi) \gets (\phi, v) \mdoubleplus C(\#\phi)$}
     \Return{$C$}\;
@@
 
-\paragraph{TODO}
-\begin{itemize}
-\item maybe `applyAllRules' is a better name
-\item explain the `tail' part of the algorithm
-\end{itemize}
+TODO: explain the `tail' part of the algorithm, i.e., that the first formula is replaced by some nodes and some formulas.
 
@@
   \KwIn{FCG $(V, s, N^+, \lambda)$}
-  \KwIn{function $\iota$ that maps labels in $\mathscr{L}$ to sets of atoms}
-  \KwIn{functions $\{\,f_l\,\}_{l \in \mathscr{L}}$ that take a list of sets of atoms and return a set of atoms}
+  \KwIn{function $\iota$ that maps labels in $\mathcal{L}$ to sets of atoms}
+  \KwIn{functions $\{\,f_l\,\}_{l \in \mathcal{L}}$ that take a list of sets of atoms and return a set of atoms}
   \KwOut{function $S$ that maps vertices in $V$ to sets of atoms}
@@
 \begin{definition}[Notation]
-  For any clause $c = (L, C, \delta_c)$, bijection $\beta\colon \Vars(c) \to V$ (for some set of variables $V$) and function $\gamma\colon \Doms(c) \to \mathscr{D}$, let $c \ast (\beta, \gamma) = d$ be the clause with all occurrences of any variable $v \in \Vars(c)$ in $L$ and $C$ replaced with $\beta(v)$ (so $\Vars(d) = V$) and $\delta_d\colon V \to \mathscr{D}$ defined as $\delta_d \coloneqq \gamma \circ \delta_c \circ \beta^{-1}$.
+  For any clause $c = (L, C, \delta_c)$, bijection $\beta\colon \Vars(c) \to V$ (for some set of variables $V$) and function $\gamma\colon \Doms(c) \to \mathcal{D}$, let $c[\beta, \gamma] = d$ be the clause with all occurrences of any variable $v \in \Vars(c)$ in $L$ and $C$ replaced with $\beta(v)$ (so $\Vars(d) = V$) and $\delta_d\colon V \to \mathcal{D}$ defined as $\delta_d \coloneqq \gamma \circ \delta_c \circ \beta^{-1}$.
 In other words, $\delta_d$ is the unique function that makes the following diagram commute:
@@
     \Vars(c) \ar[r, tail, two heads, "\beta"] \arrow[d, swap, "\delta_c"] & V = \Vars(d) \ar[d, dashed, "\exists!\delta_d"] \\
-    \Doms(c) \ar[r, swap, "\gamma"] & \mathscr{D}.
+    \Doms(c) \ar[r, swap, "\gamma"] & \mathcal{D}.
   \end{tikzcd}
@@
       \ForEach{clause $d \in \psi$ such that $\#d = \#c$\label{line:for2}} {
-        \ForEach{$(\beta, \gamma) \in \generateMaps{$c$, $d$, $\rho$}$ such that $c \ast (\beta, \gamma) = d$\label{line:generateMaps}}{
+        \ForEach{$(\beta, \gamma) \in \generateMaps{$c$, $d$, $\rho$}$ such that $c[\beta, \gamma] = d$\label{line:generateMaps}}{
           $\found' \gets \found$\;
@@
     \While{$e \ne d$ {\bf and} $e \in {\normalfont \dom}(\pi)$}{
-      \lIf{$e \in \mathscr{C}$}{$\found \gets \texttt{true}$}
+      \lIf{$e \in \mathcal{C}$}{$\found \gets \texttt{true}$}
       $e \gets \pi(e)$\;
@@
 \begin{algorithm}[t]
-  \caption{A generalised version of the compilation rule that uses \cref{alg:recursion} to add $\Reff$ nodes (i.e., the edges that make the circuit no longer a tree) to the circuit.
-TODO: refactor to return a set of solutions.}
+  \caption{A generalised version of the compilation rule that uses \cref{alg:recursion} to add $\Reff$ nodes (i.e., the edges that make the circuit no longer a tree) to the circuit.}
   \label{alg:trycache}
@@
     $\rho \gets \identifyRecursion{$\phi$, $\psi$}$\;
-    \lIf{$\rho \ne {\normalfont \texttt{null}}$}{\Return{$\Reff_\rho(n)$}}
+    \lIf{$\rho \ne {\normalfont \texttt{null}}$}{\Return{$\{\,\Reff_\rho(n)\,\}$}}
   }
@@
 The directed edges correspond to the pairs of domains in $\pi$ but in the opposite direction, e.g., $\pi(a') = a$.
-The domain enclosed in a rectangle is the only domain created by constraint removal, i.e., $\mathscr{C} = \{\, a' \,\}$.}
+The domain enclosed in a rectangle is the only domain created by constraint removal, i.e., $\mathcal{C} = \{\, a' \,\}$.}
   \label{fig:example}
@@
 
-The function \texttt{traceAncestors} returns \texttt{null} if domain $d \in \mathscr{D}$ is not an ancestor of domain $e \in \mathscr{D}$.
+The function \texttt{traceAncestors} returns \texttt{null} if domain $d \in \mathcal{D}$ is not an ancestor of domain $e \in \mathcal{D}$.
 Otherwise, it returns \texttt{true} if the size of $e$ is guaranteed to be strictly smaller than the size of $d$ (i.e., there is domain created by the constraint removal rule on the path from $d$ to $e$) and \texttt{false} if their sizes will be equal at some point during inference.
@@
 \item in the example below: write down both formula using the Forclift format
+\item the parent relation and ancestor tracing is no longer necessary
 \end{itemize}
@@
   \Doms(c) \ar[r, dashed, "\gamma"] \ar[d, hookrightarrow] & \Doms(d) \ar[d, hookrightarrow] \\
-  \mathscr{D} \ar[r, swap, "\rho"] & \mathscr{D}.
+  \mathcal{D} \ar[r, swap, "\rho"] & \mathcal{D}.
 \end{tikzcd}
@@
 Thus, \texttt{generateMaps} yields its first pair of maps $(\beta, \gamma)$ to \cref{line:generateMaps}.
-Furthermore, the pair satisfies the $c \ast (\beta, \gamma) = d$ condition.
+Furthermore, the pair satisfies $c[\beta, \gamma] = d$.
 
-  Since $\pi(a') = a$, and $a' \in \mathscr{C}$, \texttt{traceAncestors($a$, $a'$)} returns \texttt{true}, which sets $\textsf{foundConstraintRemoval}'$ to \texttt{true} as well.
+  Since $\pi(a') = a$, and $a' \in \mathcal{C}$, \texttt{traceAncestors($a$, $a'$)} returns \texttt{true}, which sets $\textsf{foundConstraintRemoval}'$ to \texttt{true} as well.
 When $e = b$, however, \texttt{traceAncestors}($b$, $b^\bot$) returns \texttt{false} since $b^\bot$ is a descendant of $b$ but not created by the constraint removal compilation rule.
@@
   Since $\beta$ and $\rho$ `commute' (TODO: as in the diagram above), and there are no new domains in $\Doms(c)$ and $\Doms(d)$, $\gamma$ exists and is equal to $\rho$.
-Again, the returned pair $(\beta, \gamma)$ satisfies the condition $c \ast (\beta, \gamma) = d$.
+Again, the returned pair $(\beta, \gamma)$ satisfies $c[\beta, \gamma] = d$.
 This $\gamma$ passes the \texttt{traceAncestors} checks exactly the same way as the one before, and \cref{line:recursion} calls \texttt{identifyRecursion($\emptyset$, $\emptyset$, $\rho$, true)}, which immediately returns $\rho = \{\, a \mapsto a', b \mapsto b^\bot \,\}$ as the final answer.
@@
 \]
-for all $x \in \mathscr{D}$.
+for all $x \in \mathcal{D}$.
 
@@
 
-\paragraph{Preconditions.} There is a domain $d \in \mathscr{D}$ and an element $e \in d$ such that:
+\paragraph{Preconditions.} There is a domain $d \in \mathcal{D}$ and an element $e \in d$ such that:
 \begin{itemize}
@@
 
-\paragraph{Operator.} First, we introduce a new domain (i.e., $\mathscr{D} \coloneqq \mathscr{D} \sqcup \{\, d' \,\}$), add it to $\mathscr{C}$ (i.e., $\mathscr{C} \coloneqq C \sqcup \{\, d' \,\}$), and set $\pi(d') \coloneqq d$.
+\paragraph{Operator.} First, we introduce a new domain (i.e., $\mathcal{D} \coloneqq \mathcal{D} \sqcup \{\, d' \,\}$), add it to $\mathcal{C}$ (i.e., $\mathcal{C} \coloneqq C \sqcup \{\, d' \,\}$), and set $\pi(d') \coloneqq d$.
 Then $\CR(\phi) = \CR_{d \mapsto d'}(\Compile(\phi'))$.
@@
   \label{alg:domainrecursion}
-  \KwIn{formula $\phi$, domain $d \in \mathscr{D}$, and constant $x$}
+  \KwIn{formula $\phi$, domain $d \in \mathcal{D}$, and constant $x$}
   \KwOut{formula $\phi'$}
@@
     \ForEach{subset $W \subseteq V$ such that $W^2 \cap C = \emptyset$ {\bf and} $W \cap \{\, v \in \Vars(C) \mid (v, y) \in C \text{ for some constant } y \,\} = \emptyset$\label{line:conditions}}{
+      \tcc{Here, $\delta'$ is the restriction of $\delta$ to the new set of variables}
       $\phi' \gets \phi' \cup \{\, (L[x/W], C[x/W] \cup \{\, (v, x) \mid (v \in V \setminus W) \,\}, \delta') \,\}$\;
-      \tcc{$\delta'$ is the restriction of $\delta$ to the new set of variables}
     }
@@
 
-\paragraph{Precondition.} Domain recursion can be applied to domain $d \in \mathscr{D}$ if there is a clause $c$ with a literal variable $v \in \Vars(L_c)$ such that $\delta_c(v) = d$.
+\paragraph{Precondition.} Domain recursion can be applied to domain $d \in \mathcal{D}$ if there is a clause $c$ with a literal variable $v \in \Vars(L_c)$ such that $\delta_c(v) = d$.
 
@@
 \begin{observation}
-  Let $n$ be a positive integer and $d \in \mathscr{D}$ a domain. Then one can construct a circuit $x$ such that
+  Let $n$ be a positive integer and $d \in \mathcal{D}$ a domain. Then one can construct a circuit $x$ such that
   \[

### 2022-02-18 notes/notes.tex
A bit of writing about notation

@@
 \documentclass{article}
+\usepackage{hyperref}
 \usepackage[UKenglish]{babel}
@@
 \item During inference, there is a domain size map $\size\colon \mathcal{D} \to \mathbb{N}_0$.
-\item $\sqcup$ for both sets and functions. TODO: I think I use $\cup$ elsewhere.
 \item mention which rules are in $\Gamma$ and which ones are in $\Delta$ (and why tryCache has to be in $\Delta$).
+\item \textsc{ForcLift}
 \end{itemize}
@@
 
+\paragraph{Notation for lists.}
+We let $[]$ and $[x]$ denote an empty list and a list with one element $x$, respectively.
+We write $\in$ for (in-order) enumeration, $\mdoubleplus$ for concatenation, and $|\cdot|$ for the length of a list.
+Let $h : t$ denote a list with first element (a.k.a.
+head) $h$ and remaining list (a.k.a.
+tail) $t$.
+We also use list comprehensions written equivalently to set comprehensions.
+For example, let $L \coloneqq [1]$ and $M \coloneqq [2]$ be two lists.
+Then $M = [2x \mid x \in L]$, $L \mdoubleplus M = 1 : [2]$, and $|M| = 1$.
+
 \section{Search/Compilation}
 
-\begin{definition}
-  A \emph{first-order deterministic decomposable negation normal form computational graph} (FCG) is a (weakly connected) directed graph with a a single source, node labels, and ordered direct successors.
-We denote an FCG as $G = (V, s, N^+, \lambda)$, where $V$ is the set of nodes, $s \in V$ is the source, $N^+$ is the direct successor function that maps each node in $V$ to a list that contains either other nodes in $V$ or $\star$, which means that the target of the edge is yet to be determined, and $\lambda\colon V \to \mathcal{L}$ is the vertex-labelling function with some codomain $\mathcal{L}$, which is assumed to be the same for all FCGs.
-For each $v \in V$, the length of the list $N^+(v)$ is determined by $\lambda(v)$.
+\subsection{From Circuits to Labelled Graphs}
 
-\end{definition}
+A \emph{first-order deterministic decomposable negation normal form computational graph} (FCG) is a (weakly connected) directed graph with a a single source, vertex labels, and ordered outgoing edges.\footnote{Note that imposing an ordering on outgoing edges is just a limited version of edge labelling.} We denote an FCG as $G = (V, s, N^+, \tau)$, where $V$ is the set of vertices, and $s \in V$ is the unique source.
+Also, $N^+$ is the direct successor function that maps each vertex in $V$ to a \emph{list} that contains either other vertices in $V$ or a special symbol $\star$.
+This symbol means that the target of the edge is yet to be determined.
+
+Vertex labels consist of two parts: the \emph{type} and the \emph{parameters}.
+For the main definition, we leave the parameters implicit and let $\tau\colon V \to \mathcal{T}$ denote the vertex-labelling function that maps each vertex in $V$ to its type in $\mathcal{T}$.
+Most of our list of types $\mathcal{T} \coloneqq \{\, \Smoothing, \Unit, \Tautology, \Contradiction, \oland, \olor, \CR, \DR, \IE, \Reff \,\}$ is as described in previous work \cite{DBLP:conf/nips/Broeck11,DBLP:conf/ijcai/BroeckTMDR11} as well as the source code of \textsc{ForcLift}\footnote{\url{https://dtai.cs.kuleuven.be/drupal/wfomc}} but with one new type $\CR$ and two revamped types $\DR$ and $\Reff$.
+For each vertex $v \in V$, the length of the list $N^+(v)$ (i.e., the out-degree of $v$) is determined by its type $\tau(v)$.
+
+As in previous work \cite{DBLP:conf/ijcai/BroeckTMDR11}, to describe individual vertices and small (sub)-FCGs, we also use notation of the form, e.g., $\Reff_\rho(v)$.
+Here, the type of the vertex (e.g., $\Reff$) is `applied' to its direct successors (e.g., $v$) using either function or infix notation and provided with its parameter(s) (e.g., $\rho$) in the subscript.
+We say that `$G$ is an FCG for formula $\phi$' if two conditions are satisfied.
+First, the image of $N^+$ contains no $\star$'s.
+Second, $G$ encodes a function that maps the sizes of the domains in $\phi$ to the WMC of $\phi$ (more on this in \cref{sec:evaluation}).
 
@@
 \begin{itemize}
-\item explain the connection to the algebraic formalism (or just don't use it).
-% We will also use algebraic notation to describe (parts of) circuits: circuittype_parameters(nodes pointed to by the outedges)
-\item define `an FCG for a formula'
-\item vertex or node, $v$ or $n$?
-\item what notation for lists (a.k.a.
-sequences) am I going to use?
-$\mdoubleplus$ for concatenation (of both two lists and an element to a list), $\in$ for (in-order) enumeration, $[]$ for an empty list, $[x]$ for a list with one element, $|L|$ for the length of the list, and $h : t$ to denote a list with first element (a.k.a.
-head) $h$ and remaining list (a.k.a.
-tail) $t$.
-Also add an example of the list comprehension notation.
+\item provide a short explanation of the types (emphasising which ones are new/updated).
+%\footnote{The new (as well as significantly renewed) types in \mathcal{T} are described in subsequent (TODO: which ones?) sections.
+The meanings of other types are described...}
+\item have an example of a simple FCG
 \end{itemize}
+
+\subsection{Everything Else}
 
@@
   \begin{itemize}
-  \item $G$ is an FCG (can be \texttt{null}),
-  \item $C$ is a compilation cache that maps integers to sets of pairs $(\phi, n)$, where $\phi$ is a formula, and $n$ is a node of $G$ (which is used to identify opportunities for recursion),
+  \item $G$ is an FCG (or \texttt{null}),
+  \item $C$ is a compilation cache that maps integers to sets of pairs $(\phi, v)$, where $\phi$ is a formula, and $v$ is a vertex of $G$ (which is used to identify opportunities for recursion),
   \item and $L$ is a list of formulas (that are yet to be compiled). (Note that the order is crucial!)
@@
   A (compilation) \emph{rule} is a function that takes a formula and returns a set of $(G, L)$ pairs, where $G$ is a (potentially \texttt{null}) FCG, and $L$ is a list of formulas.
-TODO: add an example showing that it's usually an FCG with one node and a bunch of $\star$'s marking a fixed number of outedges.
+TODO: add an example showing that it's usually an FCG with one vertex and a bunch of $\star$'s marking a fixed number of outgoing edges.
 \end{definition}
 
-We assume that if there is a pair $(\texttt{null}, L)$ in the set returned by a rule, then $|L| = 1$, i.e., the rule transformed the formula without creating any nodes.
+We assume that if there is a pair $(\texttt{null}, L)$ in the set returned by a rule, then $|L| = 1$, i.e., the rule transformed the formula without creating any vertices.
 
@@
         \Else{
-          $(V, s, N^+, \lambda) \gets G$\;
+          $(V, s, N^+, \tau) \gets G$\;
           $C \gets \updateCache(C, \phi, s)$\;
@@
   \Fn{\applyGreedyRulesToAllFormulas{$G$, $C$, $L$}}{
-    $(V, s, N^+, \lambda) \gets G$\;
+    $(V, s, N^+, \tau) \gets G$\;
     $N^+(s) \gets []$\;
@@
       \Else{
-        $(V', s', N', \lambda') \gets G'$\;
+        $(V', s', N', \tau') \gets G'$\;
         $V \gets V \sqcup V'$\;
@@
         $N^+(s) \gets N^+(s) \mdoubleplus [s']$\;
-        $\lambda \gets \lambda \sqcup \lambda'$\;
+        $\tau \gets \tau \sqcup \tau'$\;
       }
     }
-    \Return{$((V, s, N^+, \lambda), C, L')$}\;
+    \Return{$((V, s, N^+, \tau), C, L')$}\;
   }
@@
         \Else{
-          $(V, s, N^+, \lambda) \gets G''$\;
+          $(V, s, N^+, \tau) \gets G''$\;
           $C' \gets \updateCache{$C'$, $\phi$, $s$}$\;
@@
   }
-  \Fn{\mergeFcgs{$G = (V, s, N^+, \lambda)$, $G' = (V', s', N', \lambda')$, $r = s$}}{
-    \lIf{$\lambda(r) = \textsc{Ref}$}{\Return{\normalfont \texttt{null}}}
+  \Fn{\mergeFcgs{$G = (V, s, N^+, \tau)$, $G' = (V', s', N', \tau')$, $r = s$}}{
+    \lIf{$\tau(r) = \textsc{Ref}$}{\Return{\normalfont \texttt{null}}}
     \ForEach{$t \in N^+(r)$}{
@@
         replace $t$ with $s'$ in $N^+(r)$\;
-        \Return{$(V \sqcup V', s, N^+ \sqcup N', \lambda \sqcup \lambda')$}\;
+        \Return{$(V \sqcup V', s, N^+ \sqcup N', \tau \sqcup \tau')$}\;
       }
@@
 
-TODO: explain the `tail' part of the algorithm, i.e., that the first formula is replaced by some nodes and some formulas.
+TODO: explain the `tail' part of the algorithm, i.e., that the first formula is replaced by some vertices and some formulas.
 
@@
   \label{alg:smoothing}
-  \KwIn{FCG $(V, s, N^+, \lambda)$}
-  \KwIn{function $\iota$ that maps labels in $\mathcal{L}$ to sets of atoms}
-  \KwIn{functions $\{\,f_l\,\}_{l \in \mathcal{L}}$ that take a list of sets of atoms and return a set of atoms}
+  \KwIn{FCG $(V, s, N^+, \tau)$}
+  \KwIn{function $\iota$ that maps vertex types in $\mathcal{T}$ to sets of atoms}
+  \KwIn{functions $\{\,f_l\,\}_{l \in \mathcal{T}}$ that take a list of sets of atoms and return a set of atoms}
   \KwOut{function $S$ that maps vertices in $V$ to sets of atoms}
-  $S \gets \{\, v \mapsto \iota(\lambda(v)) \mid v \in V \,\}$\;
+  $S \gets \{\, v \mapsto \iota(\tau(v)) \mid v \in V \,\}$\;
   $\changed \gets \texttt{true}$\;
@@
     \ForEach{vertex $v \in V$}{
-      $S' \gets f_{\lambda(v)}([S(w) \mid w \in N^+(v)])$\;
+      $S' \gets f_{\tau(v)}([S(w) \mid w \in N^+(v)])$\;
       \If{$S' \ne S(v)$}{
@@
 [Insert motivation for smoothing from Section 3.4.
-of the Forclift paper.] Originally, smoothing was (and still is) a two-step process.
+of the ForcLift paper.] Originally, smoothing was (and still is) a two-step process.
 First, atoms that are still accounted for in the circuit are propagated upwards.
-Then, at nodes with certain labels, missing atoms are detected and additional sinks are created to account for them.
+Then, at vertices of certain types, missing atoms are detected and additional sinks are created to account for them.
 If left unchanged, the first step of this process would result in an infinite loop whenever a cycle is encountered.
@@
 \begin{algorithm}[t]
-  \caption{A recursive function for checking whether one can reuse the circuit for computing $\WMC(\phi)$ to compute $\WMC(\psi)$.
+  \caption{A recursive function for checking whether one can reuse the FCG for computing $\WMC(\phi)$ to compute $\WMC(\psi)$.
 Both $\phi$ and $\psi$ are formulas, and $\rho\colon \Doms(\phi) \protect\pfun \Doms(\psi)$ is a partial map.}
@@
 \begin{algorithm}[t]
-  \caption{A generalised version of the compilation rule that uses \cref{alg:recursion} to add $\Reff$ nodes (i.e., the edges that make the circuit no longer a tree) to the circuit.}
+  \caption{A generalised version of the compilation rule that uses \cref{alg:recursion} to add $\Reff$ vertices (i.e., the edges that make the FCG no longer a tree) to the FCG.}
   \label{alg:trycache}
@@
   \KwIn{formula $\phi$}
-  \KwOut{a $\Reff$ circuit node (or \texttt{null})}
-  \ForEach{$(\psi, n) \in \compilationCache{$\#\psi$}$}{
+  \KwOut{a vertex of type $\Reff$ (or \texttt{null})}
+  \ForEach{$(\psi, v) \in \compilationCache{$\#\psi$}$}{
     $\rho \gets \identifyRecursion{$\phi$, $\psi$}$\;
-    \lIf{$\rho \ne {\normalfont \texttt{null}}$}{\Return{$\{\,\Reff_\rho(n)\,\}$}}
+    \lIf{$\rho \ne {\normalfont \texttt{null}}$}{\Return{$\{\,\Reff_\rho(v)\,\}$}}
   }
@@
 Notation: For partial functions $\alpha, \beta\colon A \pfun B$ such that $\alpha|_{\dom(\alpha) \cap \dom(\beta)} = \beta|_{\dom(\alpha) \cap \dom(\beta)}$, we write $\alpha \cup \beta$ for the unique partial function such that $\alpha \cup \beta|_{\dom(\alpha)} = \alpha$, and $\alpha \cup \beta|_{\dom(\beta)} = \beta$.
+TODO: explain $\sqcup$ for both sets and functions.
 
@@
 \item explain the yield keyword
-\item in the example below: write down both formula using the Forclift format
+\item in the example below: write down both formula using the ForcLift format
 \item the parent relation and ancestor tracing is no longer necessary
@@
 This $\gamma$ passes the \texttt{traceAncestors} checks exactly the same way as the one before, and \cref{line:recursion} calls \texttt{identifyRecursion($\emptyset$, $\emptyset$, $\rho$, true)}, which immediately returns $\rho = \{\, a \mapsto a', b \mapsto b^\bot \,\}$ as the final answer.
-This means that one can indeed use a circuit for $\WMC(\phi)$ to compute $\WMC(\psi)$ by replacing every mention of $a$ with $a'$ and every mention of $b$ with $b^\bot$.
+This means that one can indeed use an FCG for $\WMC(\phi)$ to compute $\WMC(\psi)$ by replacing every mention of $a$ with $a'$ and every mention of $b$ with $b^\bot$.
 \end{example}
@@
 
-$\WMC(\Reff_\rho(n); \size) = \WMC(n; \size')$ ($n$ is the target circuit node), where $\size'$ is defined as
+$\WMC(\Reff_\rho(v); \size) = \WMC(v; \size')$ ($n$ is the target vertex), where $\size'$ is defined as
 \[
@@
 
-TODO: introduce the Forclift-style notation (e.g., the compile operator) and the arbitrary formula $\phi$.
+TODO: introduce the ForcLift-style notation (e.g., the compile operator) and the arbitrary formula $\phi$.
 
@@
 \begin{itemize}
-\item new rules that don't create nodes (e.g., duplicate removal, unconditional contradiction detection, etc.)
+\item new rules that don't create vertices (e.g., duplicate removal, unconditional contradiction detection, etc.)
 \item some notes on halting
@@
 
-\section{Circuit Nodes Types and Their Evaluations}
+\section{How to Evaluate an FCG} \label{sec:evaluation}
 
-Along with the three circuit node types described above, here are all the other ones. This section is mostly just taken from \cite{DBLP:conf/ijcai/BroeckTMDR11} but with some changes in notation.
+Along with the three vertex types described above, here are all the other ones. This section is mostly just taken from \cite{DBLP:conf/ijcai/BroeckTMDR11} but with some changes in notation.
 
-TODO: explain that $x, y, z$ refer to nodes, $c$ refers to a clause, and describe each node type in a bit more detail.
+TODO: explain that $x, y, z$ refer to vertices, $c$ refers to a clause, and describe each vertex type in a bit more detail.
 
@@
 
-TODO: explain how circuits and domain sizes connect to functions on integers
+TODO: explain how FCGs and domain sizes connect to functions on integers
 
 \begin{observation}
-  Let $n$ be a positive integer and $d \in \mathcal{D}$ a domain. Then one can construct a circuit $x$ such that
+  Let $n$ be a positive integer and $d \in \mathcal{D}$ a domain. Then one can construct an FCG $x$ such that
   \[
@@
   \]
-  where $y$ is a circuit node of arbitrary type. Indeed, $(\Contradiction c) \oland y$ is such a circuit, where $c = (L, C, \delta)$ is a clause with $n$ variables $(v_i)_{i=1}^n$ such that:
+  where $y$ is a vertex of arbitrary type. Indeed, $(\Contradiction c) \oland y$ is such an FCG, where $c = (L, C, \delta)$ is a clause with $n$ variables $(v_i)_{i=1}^n$ such that:
   \begin{itemize}
@@
 \begin{remark}
-  Such (sub)circuits can be constructed automatically using compilation rules, although $n$ is upper bounded by the maximum number of variables in any clause of the input formula since there is no rule that would introduce new variables.
+  Such FCGs can be constructed automatically using compilation rules, although $n$ is upper bounded by the maximum number of variables in any clause of the input formula since there is no rule that would introduce new variables.
 \end{remark}
@@
 \begin{itemize}
-\item Transform circuits to definitions of (possibly recursive) functions on integers. Use a computer algebra system to simplify them.
+\item Transform FCGs to definitions of (possibly recursive) functions on integers. Use a computer algebra system to simplify them.
 \item Design an algorithm to infer the necessary base cases. (Note that there can be an infinite amount of them when functions have more than one parameter.)

### 2022-02-19 notes/notes.tex
Small changes to the algorithm to make it find more solutions

@@
   \caption{An illustration of the main idea. TODO: refer to this in the introduction.}
+  \label{fig:idea}
 \end{figure}
@@
 \item \textsc{ForcLift}
+\item In a way, we're dividing the idea of domain recursion between the IDR and the Ref nodes, thus also generalising it. [This is good context to refer to \cref{fig:idea}.]
 \end{itemize}
@@
 \item maybe $\pi$ is global enough to have a more unique name
-\item capitalise variable names.
+\item capitalise variable and domain names.
 \item maybe introduce/use notation for vertices, edges of a graph
@@
     \ForEach{rule $r \in \Gamma$}{
-      $S \gets r(\phi)$\;
-      \If{$S \ne \emptyset$}{
-        $(G, L) \gets \text{any element of } S$\;
+      \If{$r(\phi) \ne \emptyset$}{
+        $(G, L) \gets \text{any element of } r(\phi)$\;
         \lIf{$G = {\normalfont \texttt{null}}$}{\Return{\applyGreedyRules{the only element of $L$, $C$}}}
@@
           $(V, s, N^+, \tau) \gets G$\;
-          $C \gets \updateCache(C, \phi, s)$\;
+          $C \gets \updateCache{$C$, $\phi$, $G$}$\;
           \Return{\applyGreedyRulesToAllFormulas{$G$, $C$, $L$}}\;
@@
   }
-  \Fn{\applyGreedyRulesToAllFormulas{$G$, $C$, $L$}}{
-    $(V, s, N^+, \tau) \gets G$\;
+  \Fn{\applyGreedyRulesToAllFormulas{$(V, s, N^+, \tau)$, $C$, $L$}}{
+    \lIf{$L = []$}{\Return{$((V, s, N^+, \tau), C, L)$}}
     $N^+(s) \gets []$\;
@@
           $(V, s, N^+, \tau) \gets G''$\;
-          $C' \gets \updateCache{$C'$, $\phi$, $s$}$\;
+          $C' \gets \updateCache{$C'$, $\phi$, $G''$}$\;
           $(G'', C', L'') \gets \applyGreedyRulesToAllFormulas{$G''$, $C'$, $L''$}$\;
@@
   \SetKwFunction{updateCache}{updateCache}
-  \Fn{\updateCache{$C$, $\phi$, $v$}}{
-    \lIf{$\#\phi \not\in \dom(C)$}{\Return{$C \cup \{\, \#\phi \mapsto (\phi, v) \,\}$}}
-    \lIf{there is no $(\phi', v') \in C(\#\phi)$ such that $v' = v$}{$C(\#\phi) \gets (\phi, v) \mdoubleplus C(\#\phi)$}
+  \Fn{\updateCache{$C$, $\phi$, $(V, s, N^+, \tau)$}}{
+    \lIf{$\tau(s) = \textsc{Ref}$}{\Return{$C$}}
+    \lIf{$\#\phi \not\in \dom(C)$}{\Return{$C \cup \{\, \#\phi \mapsto (\phi, s) \,\}$}}
+    \lIf{there is no $(\phi', v) \in C(\#\phi)$ such that $v = s$}{$C(\#\phi) \gets (\phi, s) \mdoubleplus C(\#\phi)$}
     \Return{$C$}\;
@@
 
-TODO: explain the `tail' part of the algorithm, i.e., that the first formula is replaced by some vertices and some formulas.
+TODO: explain the `tail' part of the algorithm, i.e., that the first formula is replaced by some vertices and some formulas. And explain why we don't want to have \textsc{Ref} vertices in the cache.
 
@@
   \KwIn{function $\iota$ that maps vertex types in $\mathcal{T}$ to sets of atoms}
-  \KwIn{functions $\{\,f_l\,\}_{l \in \mathcal{T}}$ that take a list of sets of atoms and return a set of atoms}
+  \KwIn{functions $\{\,f_t\,\}_{t \in \mathcal{T}}$ that take a list of sets of atoms and return a set of atoms}
   \KwOut{function $S$ that maps vertices in $V$ to sets of atoms}
@@
 
-\section{New Operations}
+\section{New Compilation Rules}
+
+Throughout this section, let $\phi$ be an arbitrary formula.
 
 \subsection{Constraint Removal}
-
-TODO: introduce the ForcLift-style notation (e.g., the compile operator) and the arbitrary formula $\phi$.
 
@@
 
-TODO: Compare with the original. The original version of domain recursion is here \cite{DBLP:conf/nips/Broeck11}.
-
-TODO: introduce $\phi$.
+TODO: Compare with the original \cite{DBLP:conf/nips/Broeck11}.
 
 \paragraph{Precondition.} Domain recursion can be applied to domain $d \in \mathcal{D}$ if there is a clause $c$ with a literal variable $v \in \Vars(L_c)$ such that $\delta_c(v) = d$.
+
+The reason for this precondtion is the same as in the initial version of domain recursion: there must be a variable with that domain featured among the literals because it needs to be replaced by a constant.
+TODO: expand this.
 
@@
   \end{itemize}
+\item care should be taken when cloning to preserve the validity of the cache and avoid infinite cycles (we use a separate (node $\to$ node) cache for this)
+\item No (more) caching during inference.
 \end{itemize}
@@
 
+\paragraph{Conclusions and observations.}
+\begin{itemize}
+\item $\CR$ must be separate from $\DR$ because initially the requirement to not have the newly introduced constant in the literals is not satisfied.
+\end{itemize}
+
+\paragraph{Future work.}
 \begin{itemize}

### 2022-02-21 notes/notes.tex
Prepare for some experiments
Some work towards listing experimental results

@@
 \item maybe put each function into its own algorithm environment, using the caption for the function name
+\item replace the Compile operator with my new definition of a rule. Instead of preconditions, have the rule return a set for all applicable domains.
 \end{itemize}
@@
 
-For both one domain and two domains:
+\textsc{ForcLift} fails on all of these.
+
+\paragraph{TODO.}
 \begin{itemize}
-\item bijections
-\item injections
-\item partial injections
+\item Explain the algebraic notation that I'm using here (e.g., that $f$ is always the main function)
+\item Explain the Knuth's bracket notation (or use something else, since I'm already using brackets for lists)
+\item Explain the importance of comparing domain sizes to 2.
+\item Maybe a big table: name, formula, optimal solution and its complexity, best found solution, its depth, its complexity. Also mention that it only takes a few seconds to find these solutions.
+\item Have at least one example of how an FCG maps to recursive functions
+\item Going beyond depth 6 (or sometimes even completing depth 6) is computationally infeasible with the current implementation.
+\item max time to search through depth 5?
+\end{itemize}
+
+\begin{itemize}
+\item 1d bijections
+  \begin{itemize}
+  \item depth 3 exponential solution:
+    \begin{align*}
+      f(n) &= \sum_{m=0}^n \binom{n}{m} (-1)^{n-m}g(n, m) \\
+      g(n, m) &= \sum_{l=0}^n \binom{n}{l}[l < 2]g(n-l, m-1) \\
+      &= g(n, m - 1) + ng(n - 1, m - 1),
+    \end{align*}
+    which works with base case $g(n, 0) = 1$.
+  \item depth 4 gives 3 more solutions:
+    \begin{enumerate}
+    \item a $\Theta(n^3)$ number of recursive calls (the first definition is exactly as before):
+      \begin{align*}
+        f(n) &= \sum_{m=0}^n \binom{n}{m}(-1)^{n-m}g(n, m) \\
+        g(n, m) &= \sum_{l=0}^m \binom{m}{l}[l < 2](1 + (-1)[l < 1])g(n - 1, m - l) \\
+        &= mg(n - 1, m - 1),
+      \end{align*}
+      which works with base case $g(0, m) = 1$.
+    \item exponential:
+      \begin{align*}
+        f(n) &= \sum_{m=0}^n \binom{n}{m}(-1)^{n-m} \sum_{l=0}^n \binom{n}{l} (-1)^{n-l}g(m, l) \\
+        g(m, l) &= \sum_{k=0}^m \binom{m}{k}[k < 2]g(m - k, l - 1) \\
+        &= g(m, l - 1) + mg(m - 1, l - 1),
+      \end{align*}
+      which works with base case $g(m, 0) = 1$.
+    \item same as the one before but with the parameters of $g$ swapped.
+    \end{enumerate}
+  \item depth 5 gives 2 more solutions:
+    \begin{enumerate}
+    \item a $\Theta(n^2)$ number of recursive calls:
+      \begin{align*}
+        f(n) &= \sum_{m=0}^n \binom{n}{m}(-1)^{n-m}g(n, m) \\
+        g(n, m) &= -g(n-1, m) + \sum_{l=0}^{m}\binom{m}{l}[l < 2]g(n-1, m-l) \\
+        &= mg(n-1, m-1),
+      \end{align*}
+      which works with base case $g(0, m) = 1$.
+    \item essentially the same as the first solution of depth 4 but the same $g$ is expressed differently:
+      \[
+      g(n, m) = -g(n-1, m) + \sum_{l=0}^m \binom{m}{l} [l < 2] g(n-1, m-l).
+      \]
+    \end{enumerate}
+  \end{itemize}
+\item 1d injections (same as 1d bijections, but note that the 2d case is different) (no liftable solutions)
+  \begin{itemize}
+  \item depth 3 gives 2 solutions:
+    \begin{enumerate}
+    \item exponential:
+      \begin{align*}
+        f(n) &= \sum_{m=0}^n \binom{n}{m} (-1)^{n-m} g(n, m) \\
+        g(n, m) &= \sum_{l=0}^m \binom{m}{l}[l < 2]g(n-1, m-l) \\
+        &= g(n-1, m) + mg(n-1, m-1),
+      \end{align*}
+      which works with base case $g(0, m) = 1$.
+    \item same as the one before but with the parameters of $g$ swapped.
+    \end{enumerate}
+  \item depth 5 gives 4 more solutions:
+    \begin{enumerate}
+    \item a very complex exponential solution:
+      \begin{align*}
+        f(n) &= \sum_{m=0}^n \binom{n}{m} (-1)^{n-m} \sum_{l=0}^m \binom{m}{l}[l < 2]g(n-1, m-l) \\
+        &= \sum_{m=0}^n \binom{n}{m} (-1)^{n-m} (g(n-1, m) + mg(n-1, m-1)) \\
+        g(j, k) &= \sum_{i=0}^k \binom{k}{i} [i < 2] g(j-1, k-i) \\
+        &= g(j-1, k) + kg(j-1, k-1),
+      \end{align*}
+      which works with base case $g(0, k) = 1$.
+    \item same as the one before but with the parameters of $g$ swapped.
+    \item exponential:
+      \begin{align*}
+        f(n) &= \sum_{m=0}^n \binom{n}{m} (-1)^{n-m} \sum_{l=0}^n \binom{n}{l} [l < 2] g(m-1, n-l) \\
+        &= \sum_{m=0}^n \binom{n}{m} (-1)^{n-m} (g(m-1, n) + ng(m-1, n-1)) \\
+        g(j, k) &= \sum_{i=0}^j \binom{j}{i} [i < 2] g(j-i, k-1) \\
+        &= g(j, k-1) + jg(j-1, k-1),
+      \end{align*}
+      which works with base case $g(j, 0) = 1$.
+    \item same as the one before but with the parameters of $g$ swapped.
+    \end{enumerate}
+  \item 2 more solutions at depth 6, but who cares?
+  \end{itemize}
+\item 1d partial injections. 2 solutions at depth 6, but they're too complicated to check by hand. A contradiction with $X \ne x$ constraints makes things complicated.
+\item 2d bijections
+  \begin{itemize}
+  \item depth 3 gives 3 solutions:
+    \begin{enumerate}
+    \item linear:
+      \begin{align*}
+        f(m, n) &= \sum_{l=0}^m \binom{m}{l} [l < 2] (1 - [l < 1])f(m-l, n-1) \\
+        &= mf(m-1, n-1),
+      \end{align*}
+      which works with base cases $f(0, 0) = 1$, $f(0, n) = 0$, $f(m, 0) = 0$.
+    \item same but with $m$ and $n$ switched.
+    \item
+      \begin{align*}
+      f(m, n) &= \sum_{l=0}^m \binom{m}{l} (-1)^{m-l} g(l, n) \\
+      g(l, n) &= \sum_{k=0}^n \binom{n}{k} [k < 2] g(l-1, n-k) \\
+      &= g(l-1, n) + ng(l-1, n-1),
+      \end{align*}
+      which works with base cases $g(0, 0) = g(l, 0) = 1$ and $g(0, n) = 0$.
+    \end{enumerate}
+  \end{itemize}
+\item 2d injections
+\item 2d partial injections
 \end{itemize}
@@
 \item Design an algorithm to infer the necessary base cases. (Note that there can be an infinite amount of them when functions have more than one parameter.)
+\item Observation: -1 (and powers thereof) appear in every solution to a formula if and only if the formula has existential quantification.
+That's not very smart!
+By putting unit propagation into $\Gamma$, these powers are pushed to the outer layers of the solution (i.e., `early' in the FCG).
+It's likely that removing this restriction would enable the algorithm to find asymptotically optimal solutions.
 \end{itemize}

### 2022-02-21 notes/notes.tex
All experimental results

--- 2022-02-19 notes/notes.tex
@@
 
-For both one domain and two domains:
+\textsc{ForcLift} fails on all of these.
+
+\paragraph{TODO.}
 \begin{itemize}
-\item bijections
-\item injections
-\item partial injections
+\item Explain the algebraic notation that I'm using here (e.g., that $f$ is always the main function)
+\item Explain the Knuth's bracket notation (or use something else, since I'm already using brackets for lists)
+\item Explain the importance of comparing domain sizes to 2.
+\item Maybe a big table: name, formula, optimal solution and its complexity, best found solution, its depth, its complexity. Also mention that it only takes a few seconds to find these solutions.
+\item Have at least one example of how an FCG maps to recursive functions
+\item Going beyond depth 6 (or sometimes even completing depth 6) is computationally infeasible with the current implementation, but depth at most 5 can be searched within at most a few seconds.
+\end{itemize}
+
+\begin{itemize}
+\item 1d bijections and 1d injections (note that it's the same problem). Depth 3 solution:
+  \begin{align*}
+    f(n) &= \sum_{m=0}^n \binom{n}{m} (-1)^{n-m}g(n, m) \\
+    g(n, m) &= \sum_{l=0}^n \binom{n}{l}[l < 2]g(n-l, m-1) \\
+    &= g(n, m - 1) + ng(n - 1, m - 1),
+  \end{align*}
+  which works with base case $g(n, 0) = 1$.
+\item 1d partial injections. 2 solutions at depth 6, but they're too complicated to check by hand. A contradiction with $X \ne x$ constraints makes things complicated.
+\item 2d bijections. Depth 3:
+  \begin{align*}
+    f(m, n) &= \sum_{l=0}^m \binom{m}{l} [l < 2] (1 - [l < 1])f(m-l, n-1) \\
+    &= mf(m-1, n-1),
+  \end{align*}
+  which works with base cases $f(0, 0) = 1$, $f(0, n) = 0$, $f(m, 0) = 0$.
+\item 2d injections. Depth 2:
+  \begin{align*}
+    f(m, n) &= \sum_{l=0}^m \binom{m}{l}[l<2]f(m-l, n-1) \\
+    &= f(m, n-1) + mf(m-1, n-1),
+  \end{align*}
+  which works with base cases $f(0, 0) = 1$ and $f(m, 0) = 0$.
+\item 2d partial injections, depth 2. Exactly the same circuit as above but with base case $f(m, 0) = 1$.
 \end{itemize}

### 2022-02-21 notes/notes.tex
A graphical representation of one of the FCGs

@@
 
-\textsc{ForcLift} fails on all of these.
+\begin{figure}
+  \centering
+  \begin{tikzpicture}[every node/.style={draw,ellipse},edge from parent/.style={draw,-latex},sibling distance=52mm]
+    \node (dr) {$\DR_{x \in a}$}
+    child {node {$\bigvee_{b^\top \subseteq b}$}
+      child {node {$\wedge$}
+        child {node {$1_{(\{\, p(x, X) \,\}, \emptyset, \{\, X \mapsto b^\top \,\})}$}}
+        child {node {$\wedge$}
+          child {node {$1_{(\{\, \neg p(x, X) \,\}, \emptyset, \{\, X \mapsto b^\bot \,\})}$}}
+          child {node {$\wedge$}
+            child {node {$1_{(\{\, \neg p(X, Y) \,\}, \{\, (X, x) \,\}, \{\, X \mapsto a, Y \mapsto b^\top \,\})}$}}
+            child {node {$\CR_{a \mapsto a'}$}
+              child {node {$\wedge$}
+                child {node {$\bot_{(\emptyset, \{\, (X, Y) \,\}, \{\, X \mapsto b^\top, Y \mapsto b^\top \,\})}$}}
+                child {node (ref) {$\Reff_{\{\, a \mapsto a', b \mapsto b^\bot \,\}}$}}
+              }}}}}};
+    \draw[-latex, bend right] (ref) to (dr);
+  \end{tikzpicture}
+  \caption{A graphical representation of an FCG for injections and partial injections between two domains. TODO: add a reference to a formula?}
+\end{figure}
 
@@
 \begin{itemize}
+\item $b^\bot$ should be part of the notation for counting.
+\item \textsc{ForcLift} fails on all of these.
+\item Mention that functions, surjections, and their partial counterparts are/were already liftable.
+\item Formulas for partial injections, how to add totality, surjectivity.
+\item Describe the figure and connect it to the algebraic formula.
 \item Explain the algebraic notation that I'm using here (e.g., that $f$ is always the main function)
@@
 \item Maybe a big table: name, formula, optimal solution and its complexity, best found solution, its depth, its complexity. Also mention that it only takes a few seconds to find these solutions.
-\item Have at least one example of how an FCG maps to recursive functions
 \item Going beyond depth 6 (or sometimes even completing depth 6) is computationally infeasible with the current implementation, but depth at most 5 can be searched within at most a few seconds.
+\item Notation for domain recursion should include the constant name.
+\item Combine the tikz and the algebraic notation into one, so I don't need to have two versions. But how? Maybe associate a symbol with each type and only to the types that I use?
+\item Partial bijection is the same as partial injection.
 \end{itemize}

### 2022-02-22 notes/notes.tex
Some editing

@@
 \usepackage{amsfonts}
+\usepackage{amssymb}
 
@@
 \newcommand\mdoubleplus{\mathbin{+\mkern-10mu+}}
+\newcommand*{\twoheadrightarrowtail}{\mathrel{\rightarrowtail\kern-1.9ex\twoheadrightarrow}}
 
-\DeclareMathOperator{\Compile}{\textsc{Compile}}
 \DeclareMathOperator{\CR}{\textsc{CR}}
@@
 \item $\Doms$ on both formulas and clauses. $\Doms(c) = \Imm \delta_c$, and $\Doms(\phi) = \bigcup_{c \in \phi} \Doms(c)$.
-\item maybe: notation for partial function, notation for powerset, notation for disjoint union
 \item $\WMC$, $\wwp$, $\wwn$, $\Imm$
 \item two parts: compilation and inference.
-\item introduce and use arrows for bijections, injections, set inclusions, etc.
-\item $\emptyset$ for an empty partial map.
-\item notation for variable substitution for literal and constraint sets: $S[x/V]$, where $S$ is the set, $V$ is a set of variable, and $x$ is the new constant or variable.
-Note that for constraint sets this could mean that a variable and a constant need to switch places.
 \item During inference, there is a domain size map $\size\colon \mathcal{D} \to \mathbb{N}_0$.
@@
 
+\paragraph{Notation.}
+\begin{itemize}
+\item We write $\to$ for functions, $\pfun$ for partial functions, $\twoheadrightarrowtail$ for bijections, and $\hookrightarrow$ for set inclusion.
+\end{itemize}
+
 \paragraph{TODO}
 \begin{itemize}
-\item should I always say `compilation rule' instead of `operator'?
-\item maybe $\pi$ is global enough to have a more unique name
-\item capitalise variable and domain names.
-\item maybe introduce/use notation for vertices, edges of a graph
-\item maybe put each function into its own algorithm environment, using the caption for the function name
-\item replace the Compile operator with my new definition of a rule. Instead of preconditions, have the rule return a set for all applicable domains.
+\item capitalise variable names.
+\item use $\langle\rangle$ for lists. Square brackets are overloaded already.
 \end{itemize}
@@
 \begin{definition}
-  A \emph{domain} is a symbol for a finite set.\footnote{In the context of functions, the domain of a function $f$ retains its usual meaning and is denoted $\dom(f)$.} Let $\mathcal{D}$ be the set of all domains and $\mathcal{C} \subset \mathcal{D}$ be the subset of domains introduced as a consequence of constraint removal.
-Note that both sets (can) expand during the compilation phase.
-
-Let $\pi\colon \mathcal{D} \pfun \mathcal{D}$ be a partial endomorphism on $\mathcal{D}$ that denotes the \emph{parent} relation, i.e., if $\pi(d) = e$ for some $d, e \in \mathcal{D}$, then we call $e$ the parent (domain) of $d$, and $e$ a child of $d$.
-Intuitively, $\pi$ arranges all domains into a forest---thus, we often use graph theoretical terminology to describe properties of and relationships between domains.
+  A \emph{domain} is a symbol for a finite set.\footnote{In the context of functions, the domain of a function $f$ retains its usual meaning and is denoted $\dom(f)$.} Let $\mathcal{D}$ be the set of all domains.
+Note that this set expands during the compilation.
 \end{definition}
@@
 \begin{definition}
-  A \emph{clause} is a triple $c = (L, C, \delta_c)$, where $L$ is the set of literals, $C$ is a set of inequality constraints, and $\delta_c\colon \Vars(c) \to \mathcal{D}$ is a function that maps all variables in $c$ to their domains such that if $(x, y) \in C$ for some variables $x$ and $y$, then $\delta_c(x) = \delta_c(y)$.
+  A \emph{clause} is a triple $c = (L, C, \delta_c)$, where $L$ is the set of literals, $C$ is a set of constraints, and $\delta_c\colon \Vars(c) \to \mathcal{D}$ is a function that maps all variables in $c$ to their domains such that (s.t.) if $(x, y) \in C$ for some variables $x$ and $y$, then $\delta_c(x) = \delta_c(y)$.
 Equality of clauses is defined in the usual way (i.e., all variables, domains, etc.
@@
 \end{definition}
-
-TODO: I'm already using the square brackets to denote lists.
 
@@
   \KwIn{a formula $\phi_0$}
-  \KwResult{all found FCGs for $\phi_0$ are in the set \solutions}
+  \KwOut{all found FCGs for $\phi_0$ are in the set \solutions}
   $\solutions \gets \emptyset$\;
@@
     \lIf{$\#\phi \not\in \dom(C)$}{\Return{$C \cup \{\, \#\phi \mapsto (\phi, s) \,\}$}}
-    \lIf{there is no $(\phi', v) \in C(\#\phi)$ such that $v = s$}{$C(\#\phi) \gets (\phi, s) \mdoubleplus C(\#\phi)$}
+    \lIf{there is no $(\phi', v) \in C(\#\phi)$ s.t. $v = s$}{$C(\#\phi) \gets (\phi, s) \mdoubleplus C(\#\phi)$}
     \Return{$C$}\;
@@
 
-\begin{definition}[Notation]
-  For any clause $c = (L, C, \delta_c)$, bijection $\beta\colon \Vars(c) \to V$ (for some set of variables $V$) and function $\gamma\colon \Doms(c) \to \mathcal{D}$, let $c[\beta, \gamma] = d$ be the clause with all occurrences of any variable $v \in \Vars(c)$ in $L$ and $C$ replaced with $\beta(v)$ (so $\Vars(d) = V$) and $\delta_d\colon V \to \mathcal{D}$ defined as $\delta_d \coloneqq \gamma \circ \delta_c \circ \beta^{-1}$.
-In other words, $\delta_d$ is the unique function that makes the following diagram commute:
+\paragraph{Notation.}
+For any clause $c = (L, C, \delta_c)$, bijection $\beta\colon \Vars(c) \twoheadrightarrowtail V$ (for some set of variables $V$) and function $\gamma\colon \Doms(c) \to \mathcal{D}$, let $c[\beta, \gamma] = d$ be the clause $c$ with all occurrences of any variable $v \in \Vars(c)$ in $L$ and $C$ replaced with $\beta(v)$ (so $\Vars(d) = V$) and $\delta_d\colon V \to \mathcal{D}$ defined as $\delta_d \coloneqq \gamma \circ \delta_c \circ \beta^{-1}$.
+In other words, $\delta_d$ is the unique function that makes
 \[
@@
   \Vars(c) \ar[r, tail, two heads, "\beta"] \arrow[d, swap, "\delta_c"] & V = \Vars(d) \ar[d, dashed, "\exists!\delta_d"] \\
-    \Doms(c) \ar[r, swap, "\gamma"] & \mathcal{D}.
+  \Doms(c) \ar[r, swap, "\gamma"] & \mathcal{D}
 \end{tikzcd}
 \]
-\end{definition}
+commute.
 
 \begin{algorithm}[t]
-  \caption{A recursive function for checking whether one can reuse the FCG for computing $\WMC(\phi)$ to compute $\WMC(\psi)$.
-Both $\phi$ and $\psi$ are formulas, and $\rho\colon \Doms(\phi) \protect\pfun \Doms(\psi)$ is a partial map.}
-  \label{alg:recursion}
+  \caption{The compilation rule for $\Reff$}
+  \label{alg:trycache}
+
   \SetKwProg{Fn}{Function}{:}{}
   \SetKw{KwRet}{yield}
+  \SetKwData{compilationCache}{compilationCache}
   \SetKwFunction{identifyRecursion}{identifyRecursion}
-  \SetKwFunction{findHistory}{traceAncestors}
   \SetKwFunction{generateMaps}{generateMaps}
   \SetKwFunction{constructDomainMap}{constructDomainMap}
-  \SetKwData{suitable}{suitableBijection}
-  \SetKwData{found}{foundConstraintRemoval}
-  \Fn{\identifyRecursion{$\phi$, $\psi$, $\rho = \emptyset$, $\found = {\normalfont \texttt{false}}$}}{
+
+  \KwIn{formula $\phi$}
+  \KwOut{either a singleton with the new $\Reff$ vertex or $\emptyset$}
+
+  \ForEach{$(\psi, v) \in \compilationCache{$\#\phi$}$}{
+    $\rho \gets \identifyRecursion{$\phi$, $\psi$}$\;
+    \lIf{$\rho \ne {\normalfont \texttt{null}}$}{\Return{$\{\, (\Reff_\rho(v), \emptyset) \,\}$}}
+  }
+  \Return{$\emptyset$}\;
+
+  \Fn{\identifyRecursion{$\phi$, $\psi$, $\rho = \emptyset$}}{
     \lIf{$|\phi| \ne |\psi|$ {\bf or} $\#\phi \ne \#\psi$}{\Return{\normalfont \texttt{null}}}
-    \If{$\phi = \emptyset$}{
-      \lIf{$\found$}{\Return{$\rho$}}
-      \Return{\normalfont \texttt{null}}\;
-    }
+    \lIf{$\phi = \emptyset$}{\Return{$\rho$}}
     \ForEach{clause $c \in \phi$\label{line:for1}}{
-      \ForEach{clause $d \in \psi$ such that $\#d = \#c$\label{line:for2}} {
-        \ForEach{$(\beta, \gamma) \in \generateMaps{$c$, $d$, $\rho$}$ such that $c[\beta, \gamma] = d$\label{line:generateMaps}}{
-          $\found' \gets \found$\;
-          $\suitable \gets \texttt{true}$\;
-          \ForEach{$e \in \Doms(c)$\label{line:vars}}{
-            $\found'' \gets \findHistory{$e$, $\gamma(e)$}$\;
-            \If{$\found'' = {\normalfont \texttt{null}}$}{
-              $\suitable \gets \texttt{false}$\;
-              break\;
-            }
-            \lIf{$\found''$}{$\found' \gets \texttt{true}$}
-          }
-          \If{\suitable}{
-            $\rho'' \gets \identifyRecursion{$\phi \setminus \{\, c \,\}$, $\psi \setminus \{\, d \,\}$, $\rho \cup \gamma$, $\found'$}$\;\label{line:recursion}
-            \lIf{$\rho'' \ne {\normalfont \texttt{null}}$}{\Return{$\rho''$}}
-          }
+      \ForEach{clause $d \in \psi$ s.t. $\#d = \#c$\label{line:for2}} {
+        \ForEach{$(\beta, \gamma) \in \generateMaps{$c$, $d$, $\rho$}$ s.t. $c[\beta, \gamma] = d$\label{line:generateMaps}}{
+          $\rho' \gets \identifyRecursion{$\phi \setminus \{\, c \,\}$, $\psi \setminus \{\, d \,\}$, $\rho \cup \gamma$}$\;\label{line:recursion}
+          \lIf{$\rho' \ne {\normalfont \texttt{null}}$}{\Return{$\rho'$}}
         }
@@
   }
+
   \Fn{\generateMaps{$c$, $d$, $\rho$}}{
@@
   }
+
   \Fn{\constructDomainMap{$V$, $\delta_c$, $\delta_d$, $\beta$, $\rho$}}{
@@
   }
-  \Fn{\findHistory{$d$, $e$}}{
-    $\found \gets \texttt{false}$\;
-    \While{$e \ne d$ {\bf and} $e \in {\normalfont \dom}(\pi)$}{
-      \lIf{$e \in \mathcal{C}$}{$\found \gets \texttt{true}$}
-      $e \gets \pi(e)$\;
-    }
-    \lIf{$e = d$}{\Return{\found}}
-    \Return{\normalfont \texttt{null}}\;
-  }
 \end{algorithm}
-
-\begin{algorithm}[t]
-  \caption{A generalised version of the compilation rule that uses \cref{alg:recursion} to add $\Reff$ vertices (i.e., the edges that make the FCG no longer a tree) to the FCG.}
-  \label{alg:trycache}
-  \SetKwData{compilationCache}{compilationCache}
-  \KwIn{formula $\phi$}
-  \KwOut{a vertex of type $\Reff$ (or \texttt{null})}
-  \ForEach{$(\psi, v) \in \compilationCache{$\#\psi$}$}{
-    $\rho \gets \identifyRecursion{$\phi$, $\psi$}$\;
-    \lIf{$\rho \ne {\normalfont \texttt{null}}$}{\Return{$\{\,\Reff_\rho(v)\,\}$}}
-  }
-  \Return{\normalfont \texttt{null}}\;
-\end{algorithm}
-
-\begin{figure}[t]
-  \centering
-  \begin{tikzpicture}[edge from parent/.style={draw,-latex}]
-    %% \node[draw,circle,fill=violet!10] (circuit) {} child {
-    %%   node[draw,circle,fill=violet!10] (bmaker) {$\diamondsuit$}
-    %%   child {node[draw,circle,fill=violet!10] {}
-    %%     child {node[draw,circle,fill=violet!10] {}}
-    %%     child {node[draw,circle,fill=violet!10] {}
-    %%       child {node[draw,circle,fill=violet!10] {}}
-    %%       child {node[draw,circle,fill=violet!10] {}
-    %%         child {node[draw,circle,fill=violet!10] {}}
-    %%         child {node[draw,circle,fill=violet!10] (amaker) {$\heartsuit$}
-    %%           child {node[draw,circle,fill=violet!10] (ref) {}
-    %%             child {node[draw,circle,fill=violet!10] {}}
-    %%           }
-    %%         }
-    %%       }
-    %%     }
-    %%   }
-    %% };
-    \node (a) {$a$} child {node[draw,rectangle] (aprime) {$a'$}};
-    \node[right=1 cm of a] (b) {$b$}
-    child {node (btop) {$b^\top$}}
-    child {node (bbot) {$b^\bot$}};
-    %% \node[draw,fit=(a) (aprime) (b) (btop) (bbot)] {};
-    %% \draw[-latex] (ref) edge[densely dotted,bend left=90] (circuit);
-    %% \draw[-latex,color=teal] (aprime) edge[densely dashed] node[xshift=2mm,color=teal] {$0$} (amaker);
-    %% \draw[-latex,color=teal] (btop) edge[bend left=50,densely dashed] node[xshift=6mm,color=teal] {$0$} (bmaker);
-    %% \draw[-latex,color=teal] (bbot) edge[bend left=50,densely dashed] node[yshift=-2mm,color=teal] {$1$} (bmaker);
-  \end{tikzpicture}
-  \caption{The forest of domains from \cref{example}.
-The directed edges correspond to the pairs of domains in $\pi$ but in the opposite direction, e.g., $\pi(a') = a$.
-The domain enclosed in a rectangle is the only domain created by constraint removal, i.e., $\mathcal{C} = \{\, a' \,\}$.}
-  \label{fig:example}
-\end{figure}
 
@@
 
-Notation: For partial functions $\alpha, \beta\colon A \pfun B$ such that $\alpha|_{\dom(\alpha) \cap \dom(\beta)} = \beta|_{\dom(\alpha) \cap \dom(\beta)}$, we write $\alpha \cup \beta$ for the unique partial function such that $\alpha \cup \beta|_{\dom(\alpha)} = \alpha$, and $\alpha \cup \beta|_{\dom(\beta)} = \beta$.
+Notation: For partial functions $\alpha, \beta\colon A \pfun B$ s.t.
+$\alpha|_{\dom(\alpha) \cap \dom(\beta)} = \beta|_{\dom(\alpha) \cap \dom(\beta)}$, we write $\alpha \cup \beta$ for the unique partial function s.t.
+$\alpha \cup \beta|_{\dom(\alpha)} = \alpha$, and $\alpha \cup \beta|_{\dom(\beta)} = \beta$.
 TODO: explain $\sqcup$ for both sets and functions.
@@
 \begin{itemize}
-\item introduce/describe \cref{alg:recursion} and \cref{alg:trycache} and describe the cache that's being used.
+\item update the example to not refer to things that don't exist anymore
+\item introduce/describe and \cref{alg:trycache} and describe the cache that's being used.
 \item explain why $\rho \cup \gamma$ is possible
 \item explain what the second return statement is about and why a third one is not necessary
-\item mention which one is the main function, what each function takes and returns
 \item explain the yield keyword
 \item in the example below: write down both formula using the ForcLift format
-\item the parent relation and ancestor tracing is no longer necessary
 \end{itemize}
@@
 
-Diagramatically, \texttt{constructDomainMap} attempts to find $\gamma\colon \Doms(c) \to \Doms(d)$ such that the following diagram commutes (and returns \texttt{null} if such a function does not exist):
+Diagramatically, \texttt{constructDomainMap} attempts to find $\gamma\colon \Doms(c) \to \Doms(d)$ s.t. the following diagram commutes (and returns \texttt{null} if such a function does not exist):
 \[
@@
 
-\paragraph{Preconditions.} There is a domain $d \in \mathcal{D}$ and an element $e \in d$ such that:
-\begin{itemize}
-\item for each clause $c = (L, C, \delta_c) \in \phi$ and variable $v \in \Vars(c)$, either $\delta_c(v) \ne d$ or $(v, e) \in C$;
-\item $e$ does not occur in any literal of any clause of $\phi$.
-\end{itemize}
+\begin{algorithm}[t]
+  \caption{The compilation rule for $\CR$}
+  \label{alg:constraintremoval}
+  \KwIn{formula $\phi$, set of domains $\mathcal{D}$}
+  \KwOut{set $S$}
+  $S \gets \emptyset$\;
+  \ForEach{domain $d \in \mathcal{D}$ and element $e \in d$ s.t.
+$e$ does not occur in any literal of any clause of $\phi$ {\bf and} for each clause $ c = (L, C, \delta_c) \in \phi$ and variable $v \in \Vars(c)$, either $\delta_c(v) \ne d$ {\bf or} $(v, e) \in C$}{
+    add a new domain $d'$ to $\mathcal{D}$\;
+    $\phi' \gets \emptyset$\;
+    \ForEach{clause $(L, C, \delta) \in \phi$}{
+      $C' \gets \{\, (x, y) \in C \mid y \ne e \,\}$\;
+      $\delta' \gets \emptyset$\;
+      \ForEach{variable $v \in \Vars(L) \cup \Vars(C')$}{
+        \lIf{$\delta(v) = d$}{$\delta' \gets \delta' \cup \{\, v \mapsto d' \,\}$}
+        \lElse{$\delta' \gets \delta' \cup \{\, v \mapsto \delta(v) \,\}$}
+      }
+      $\phi' \gets \phi' \cup \{\, (L, C', \delta') \,\}$\;
+    }
+    $S \gets S \cup \{\, \CR_{d \mapsto d'}, \phi' \,\}$\;
+  }
+\end{algorithm}
 
-\paragraph{Operator.} First, we introduce a new domain (i.e., $\mathcal{D} \coloneqq \mathcal{D} \sqcup \{\, d' \,\}$), add it to $\mathcal{C}$ (i.e., $\mathcal{C} \coloneqq C \sqcup \{\, d' \,\}$), and set $\pi(d') \coloneqq d$.
-Then $\CR(\phi) = \CR_{d \mapsto d'}(\Compile(\phi'))$.
-The new formula $\phi'$ is defined by replacing every clause $(L, C, \delta) \in \phi$ by a clause $c' = (L, C', \delta') \in \phi'$, where
-\[
-C' = \{\, (x, y) \in C \mid y \ne e \,\},
-\]
-and
-\[
-\delta'(x) =
-\begin{cases}
-  d' & \text{if } \delta(x) = d \\
-  \delta(x) & \text{otherwise}
-\end{cases}
-\]
-for all $x \in \Vars(c') \subseteq \Vars(c)$.
+TODO: describe \cref{alg:constraintremoval} and rewrite the example below.
 
@@
 \begin{algorithm}[t]
-  \caption{Formula transformation for domain recursion}
+  \caption{The compilation rule for $\DR$}
   \label{alg:domainrecursion}
-  \KwIn{formula $\phi$, domain $d \in \mathcal{D}$, and constant $x$}
-  \KwOut{formula $\phi'$}
+  \KwIn{formula $\phi$}
+  \KwOut{set $S$}
+  $S \gets \emptyset$\;
+  \ForEach{domain $d \in \mathcal{D}$ s.t. there is a clause $c \in \phi$ and a variable $v \in \Vars(L_c)$ s.t. $\delta_c(v) = d$}{
     $\phi' \gets \emptyset$\;
+    $x \gets \text{a new constant associated with domain } d$\;
     \ForEach{clause $c = (L, C, \delta) \in \phi$\label{line:forclause}}{
       $V \gets \{\, v \in \Vars(L) \mid \delta(v) = d \,\}$\;
-    \ForEach{subset $W \subseteq V$ such that $W^2 \cap C = \emptyset$ {\bf and} $W \cap \{\, v \in \Vars(C) \mid (v, y) \in C \text{ for some constant } y \,\} = \emptyset$\label{line:conditions}}{
+      \ForEach{subset $W \subseteq V$ s.t. $W^2 \cap C = \emptyset$ {\bf and} $W \cap \{\, v \in \Vars(C) \mid (v, y) \in C \text{ for some constant } y \,\} = \emptyset$\label{line:conditions}}{
         \tcc{Here, $\delta'$ is the restriction of $\delta$ to the new set of variables}
@@
     }
+    $S \gets S \cup \{\, (\DR_d, \phi') \,\}$\;
+  }
 \end{algorithm}
 
+\paragraph{The algorithm uses this notation for substitution.}
+Let $S$ be a set of constraints or literals, $V$ a set of variables, and $x$ either a variable or a constant.
+Then we write $S[x/V]$ to denote $S$ with all occurrences of all variables in $V$ replaced with $x$.\footnote{Note that if $(v, w)$ is a two-variable constraint, substituting a constant $c$ for $v$ would result in $(c, w)$, which would have to be rewritten as $(w, c)$ to fit the definition of a constraint.}
+
 TODO: Compare with the original \cite{DBLP:conf/nips/Broeck11}.
-
-\paragraph{Precondition.} Domain recursion can be applied to domain $d \in \mathcal{D}$ if there is a clause $c$ with a literal variable $v \in \Vars(L_c)$ such that $\delta_c(v) = d$.
 
@@
 
-\paragraph{Operator.} First, introduce a new constant $x$. Then $\DR(\phi) = \DR_d(\Compile(\phi'))$, where $\phi'$ is generated by \cref{alg:domainrecursion}.
+TODO: describe \cref{alg:domainrecursion}.
 
@@
 \item care should be taken when cloning to preserve the validity of the cache and avoid infinite cycles (we use a separate (node $\to$ node) cache for this)
-\item No (more) caching during inference.
+\item another change: one rule can return more than one `continuation of the graph'
 \end{itemize}
@@
 
-\subsection{Observations and Theoretical Results}
-
-TODO: explain how FCGs and domain sizes connect to functions on integers
-
-\begin{observation}
-  Let $n$ be a positive integer and $d \in \mathcal{D}$ a domain. Then one can construct an FCG $x$ such that
-  \[
-  \WMC(x; \size) =
-  \begin{cases}
-    0 & \text{if } \size(d) \ge n \\
-    \WMC(y; \size) & \text{otherwise,}
-  \end{cases}
-  \]
-  where $y$ is a vertex of arbitrary type. Indeed, $(\Contradiction c) \oland y$ is such an FCG, where $c = (L, C, \delta)$ is a clause with $n$ variables $(v_i)_{i=1}^n$ such that:
-  \begin{itemize}
-  \item $L$ is unimportant,
-  \item $C = \{\, (v_i, v_j) \mid i = 1, \dots, n - 1\text{, }j = i + 1, \dots, n \,\}$,
-  \item and $\delta(v_i) = d$ for all $i = 1, \dots, n$.
-  \end{itemize}
-  TODO: explain why this works.
-\end{observation}
-
-\begin{remark}
-  Such FCGs can be constructed automatically using compilation rules, although $n$ is upper bounded by the maximum number of variables in any clause of the input formula since there is no rule that would introduce new variables.
-\end{remark}
-
-\section{Examples}
+\section{Newly Domain-Liftable Formulas}
 
@@
   \centering
-  \begin{tikzpicture}[every node/.style={draw,ellipse},edge from parent/.style={draw,-latex},sibling distance=52mm]
+  \begin{tikzpicture}[every node/.style={draw,ellipse},edge from parent/.style={draw,-latex},sibling distance=48mm]
     \node (dr) {$\DR_{x \in a}$}
@@
 \item Partial bijection is the same as partial injection.
+\item the exponential solutions can be computed in quadratic time with dynamic programming!
 \end{itemize}
+
+\begin{remark}
+  FCGs that compare the size of a domain to an integer can be constructed automatically using compilation rules, although $n$ is upper bounded by the maximum number of variables in any clause of the input formula since there is no rule that would introduce new variables.
+\end{remark}
 

### 2022-02-23 notes/notes.tex
Notation change

@@
 \item capitalise variable names.
-\item use $\langle\rangle$ for lists. Square brackets are overloaded already.
 \end{itemize}
@@
 \paragraph{Notation for lists.}
-We let $[]$ and $[x]$ denote an empty list and a list with one element $x$, respectively.
+Let $\langle\rangle$ and $\langle x \rangle$ denote an empty list and a list with one element $x$, respectively.
 We write $\in$ for (in-order) enumeration, $\mdoubleplus$ for concatenation, and $|\cdot|$ for the length of a list.
@@
 We also use list comprehensions written equivalently to set comprehensions.
-For example, let $L \coloneqq [1]$ and $M \coloneqq [2]$ be two lists.
-Then $M = [2x \mid x \in L]$, $L \mdoubleplus M = 1 : [2]$, and $|M| = 1$.
+For example, let $L \coloneqq \langle 1 \rangle$ and $M \coloneqq \langle 2 \rangle$ be two lists.
+Then $M = \langle 2x \mid x \in L \rangle$, $L \mdoubleplus M = 1 : \langle 2 \rangle$, and $|M| = 1$.
 
@@
   $(G_0, C_0, L_0) \gets \applyGreedyRules{$\phi_0$, $C_0$}$\;
-  \lIf{$L_0 = []$}{$\solutions \gets \{\, G_0 \,\}$}
+  \lIf{$L_0 = \langle\rangle$}{$\solutions \gets \{\, G_0 \,\}$}
   \Else{
@@
       \ForEach{state $(G, C, L) \in \applyAllRules{$q.\get{}$}$}{
-        \lIf{$L = []$}{$\solutions \gets \solutions \cup \{\, G \,\}$}
+        \lIf{$L = \langle\rangle$}{$\solutions \gets \solutions \cup \{\, G \,\}$}
         \lElse{$q.\put{$(G, C, L)$}$}
@@
     }
-    \Return{$({\normalfont \texttt{null}}, C, [\phi])$}\;
+    \Return{$({\normalfont \texttt{null}}, C, \langle\phi\rangle)$}\;
   }
   \Fn{\applyGreedyRulesToAllFormulas{$(V, s, N^+, \tau)$, $C$, $L$}}{
-    \lIf{$L = []$}{\Return{$((V, s, N^+, \tau), C, L)$}}
-    $N^+(s) \gets []$\;
-    $L' \gets []$\;
+    \lIf{$L = \langle\rangle$}{\Return{$((V, s, N^+, \tau), C, L)$}}
+    $N^+(s) \gets \langle\rangle$\;
+    $L' \gets \langle\rangle$\;
     \ForEach{formula $\phi \in L$}{
@@
       $L' \gets L' \mdoubleplus L''$\;
-      \lIf{$G' = {\normalfont \texttt{null}}$}{$N^+(s) \gets N^+(s) \mdoubleplus [\star]$}
+      \lIf{$G' = {\normalfont \texttt{null}}$}{$N^+(s) \gets N^+(s) \mdoubleplus \langle\star\rangle$}
       \Else{
@@
         $N^+ \gets N^+ \sqcup N'$\;
-        $N^+(s) \gets N^+(s) \mdoubleplus [s']$\;
+        $N^+(s) \gets N^+(s) \mdoubleplus \langle s' \rangle$\;
         $\tau \gets \tau \sqcup \tau'$\;
@@
     $(G', C', L') \gets \text{a copy of } s$\;
-    $\newStates \gets []$\;
+    $\newStates \gets \langle\rangle$\;
     \ForEach{rule $r \in \Delta$}{
@@
           $(G'', C', L'') \gets \applyGreedyRulesToAllFormulas{$G''$, $C'$, $L''$}$\;
-          \lIf{$G' = {\normalfont \texttt{null}}$}{$\newStates \gets \newStates \mdoubleplus [(G'', C', L'' \mdoubleplus T)]$}
-          \lElse{$\newStates \gets \newStates \mdoubleplus [(\mergeFcgs{$G'$, $G''$}, C', L'' \mdoubleplus T)]$}
+          \lIf{$G' = {\normalfont \texttt{null}}$}{$\newStates \gets \newStates \mdoubleplus \langle(G'', C', L'' \mdoubleplus T)\rangle$}
+          \lElse{$\newStates \gets \newStates \mdoubleplus \langle(\mergeFcgs{$G'$, $G''$}, C', L'' \mdoubleplus T)\rangle$}
         }
@@
     \ForEach{vertex $v \in V$}{
-      $S' \gets f_{\tau(v)}([S(w) \mid w \in N^+(v)])$\;
+      $S' \gets f_{\tau(v)}(\langle S(w) \mid w \in N^+(v) \rangle)$\;
       \If{$S' \ne S(v)$}{

### 2022-02-25 notes/notes.tex
A table to summarise experimental results

@@
 \usepackage{amssymb}
+\usepackage{pifont}
 
@@
 \usepackage[capitalize]{cleveref}
+\usepackage{booktabs}
+\usepackage{multirow}
+\usepackage{colortbl}
 
@@
 \newcommand*{\twoheadrightarrowtail}{\mathrel{\rightarrowtail\kern-1.9ex\twoheadrightarrow}}
+\newcommand{\cmark}{\ding{51}}%
+\newcommand{\xmark}{\ding{55}}%
 
@@
 
+\section{Introduction}
+
 \section{Definitions}
@@
 \begin{itemize}
-\item atom, (positive/negative) literal, constant, predicate, variable, literal variable, clause, unit clause
+\item atom, (positive/negative) literal, constant, predicate, argument, arity, variable, clause, unit clause, first-order logic
 \item $\Vars$, $\Vars(c) = \Vars(L) \cup \Vars(C)$
@@
 \item We write $\to$ for functions, $\pfun$ for partial functions, $\twoheadrightarrowtail$ for bijections, and $\hookrightarrow$ for set inclusion.
-\end{itemize}
-
-\paragraph{TODO}
-\begin{itemize}
-\item capitalise variable names.
 \end{itemize}
@@
 \end{definition}
+
+TODO: implicit universal quantification.
 
@@
 
-\section{Search/Compilation}
-
-\subsection{From Circuits to Labelled Graphs}
+\section{From Circuits to Labelled Graphs}
 
@@
 For each vertex $v \in V$, the length of the list $N^+(v)$ (i.e., the out-degree of $v$) is determined by its type $\tau(v)$.
+
+TODO: conjunctions and disjunctions should be different from set-conjunctions and set-disjunctions.
 
@@
 The meanings of other types are described...}
-\item have an example of a simple FCG
+\item have an example of a simple FCG. Describe the figure from later.
 \end{itemize}
 
-\subsection{Everything Else}
+\section{Search/Compilation}
 
@@
 
-\section{Smoothing}
+\section{In-Between Compilation and Inference: Smoothing}
 
@@
 
-\section{Identifying Possibilities for Recursion}
+\section{New Compilation Rules}
+
+\subsection{Identifying Possibilities for Recursion}
 
@@
 
-\subsection{Evaluation}
+\subsubsection{Evaluation}
 
@@
 for all $x \in \mathcal{D}$.
-
-\section{New Compilation Rules}
-
-Throughout this section, let $\phi$ be an arbitrary formula.
 
@@
     }
-    $S \gets S \cup \{\, (\DR_d, \phi') \,\}$\;
+    $S \gets S \cup \{\, (\DR_{d \gets d \setminus \{\, x \,\}}, \phi') \,\}$\;
   }
@@
 \[
-\WMC(\DR_d(n); \size) =
+\WMC(\DR_{d \gets d \setminus \{\, x \,\}}(n); \size) =
 \begin{cases}
@@
 
-\section{Newly Domain-Liftable Formulas}
+\section{Examples of Newly Domain-Liftable Formulas}
+
+\begin{table}
+  \centering
+  \begin{tabular}{cccccc}
+    \toprule
+    \multicolumn{3}{c}{Function Class} & \multicolumn{3}{c}{Complexity} \\
+    Partial & Endo & Class & Best Known & With Circuits & With Graphs \\
+    \midrule
+    \rowcolor{lightgray}\cmark/\xmark & \cmark/\xmark & Functions & $\lg m$ & $m$ & $m$ \\
+    \xmark & \xmark & \multirow{4}{*}{Surjections} & $n \lg m$ \cite{30049} & ? & ? \\
+    \xmark & \cmark & & $n \lg m$ \cite{30049} & ? & ? \\
+    \cmark & \xmark & & \multicolumn{3}{c}{Same as injections from $b$ to $a$} \\
+    \cmark & \cmark & & \multicolumn{3}{c}{Same as endo-injections} \\
+    \rowcolor{lightgray}\xmark & \xmark & & $\lg m$ & - & $mn$ \\
+    \rowcolor{lightgray}\xmark & \cmark & & $\lg m$ & - & $m^3$ \\
+    \rowcolor{lightgray}\cmark & \xmark & & $\min\{\, m, n \,\}^2$ & - & $n^2$ \\
+    \rowcolor{lightgray}\cmark & \cmark & \multirow{-4}{*}{Injections} & $m^2$ & - & - \\
+    \xmark & \xmark & \multirow{3}{*}{Bijections} & $\lg m$ & - & $m$ \\
+    \xmark & \cmark & & \multicolumn{3}{c}{\multirow{2}{*}{Same as (partial) (endo-)injections}} \\
+    \cmark & \cmark/\xmark & & \multicolumn{3}{c}{} \\
+    \bottomrule
+  \end{tabular}
+  \caption{Here, $m$ is the size of $a$, and $n$ is the size of $b$.
+All asymptotic complexities are in $\Theta(\cdot)$.
+Logarithm with base two.
+This is for unweighted counting.
+A hyphen means that no solution was found.
+TODO: add shaded rows.
+TODO: explain assumptions for the counts to not be zero.
+TODO: double check.
+TODO: maybe combine more rows/columns.}
+\end{table}
 
@@
   \begin{tikzpicture}[every node/.style={draw,ellipse},edge from parent/.style={draw,-latex},sibling distance=48mm]
-    \node (dr) {$\DR_{x \in a}$}
+    \node (dr) {$\DR_{a \gets a \setminus \{\, x \,\}}$}
     child {node {$\bigvee_{b^\top \subseteq b}$}
@@
   \caption{A graphical representation of an FCG for injections and partial injections between two domains. TODO: add a reference to a formula?}
+  \label{fig:examplefcg}
 \end{figure}
@@
 \item $b^\bot$ should be part of the notation for counting.
-\item \textsc{ForcLift} fails on all of these.
-\item Mention that functions, surjections, and their partial counterparts are/were already liftable.
 \item Formulas for partial injections, how to add totality, surjectivity.
-\item Describe the figure and connect it to the algebraic formula.
+\item Describe \cref{fig:examplefcg} and connect it to the algebraic formula.
 \item Explain the algebraic notation that I'm using here (e.g., that $f$ is always the main function)
-\item Explain the Knuth's bracket notation (or use something else, since I'm already using brackets for lists)
 \item Explain the importance of comparing domain sizes to 2.
-\item Maybe a big table: name, formula, optimal solution and its complexity, best found solution, its depth, its complexity. Also mention that it only takes a few seconds to find these solutions.
+FCGs that compare the size of a domain to an integer can be constructed automatically using compilation rules, although $n$ is upper bounded by the maximum number of variables in any clause of the input formula since there is no rule that would introduce new variables.
+\item Maybe a big table: name, optimal solution and its complexity, best found solution, its depth, its complexity. Also mention that it only takes a few seconds to find these solutions.
 \item Going beyond depth 6 (or sometimes even completing depth 6) is computationally infeasible with the current implementation, but depth at most 5 can be searched within at most a few seconds.
-\item Notation for domain recursion should include the constant name.
 \item Combine the tikz and the algebraic notation into one, so I don't need to have two versions. But how? Maybe associate a symbol with each type and only to the types that I use?
@@
 \item the exponential solutions can be computed in quadratic time with dynamic programming!
+\item Can't explain how formulas are translated into (my definition of) clauses without explaining Skolemization, which is out of scope.
+\item Note that in some cases different descriptions of the same problem lead to different solutions (with different complexities).
+\item Maybe we are actually guaranteed that the solution is always polynomial-time.
 \end{itemize}
 
-\begin{remark}
-  FCGs that compare the size of a domain to an integer can be constructed automatically using compilation rules, although $n$ is upper bounded by the maximum number of variables in any clause of the input formula since there is no rule that would introduce new variables.
-\end{remark}
+Let $p$ be a predicate of arity two s.t.
+the first argument is associated with domain $a$, and the second argument is associated with domain $b$ (i.e., $p$ represents a relation between sets $a$ and $b$).
+Then, to restrict all relations representable by $p$ to just functions from $a$ to $b$, in first-order logic one might write
+\begin{gather}
+  \forall X \in a. \forall Y \in b. \forall Z \in b. p(X, Y) \land p(X, Z) \implies Y = Z \label{eq:def1} \\
+  \forall X \in a. \exists Y \in b. p(X, Y). \label{eq:def2}
+\end{gather}
+The former says that one element of $a$ can map to at \emph{most} one element of $b$, and the latter says that each element of $a$ must map to at \emph{least} one element of $b$. One might add
+\begin{equation} \label{eq:injectivity}
+  \forall W \in a. \forall X \in a. \forall Y \in b. p(W, Y) \land p(X, Y) \implies W = X
+\end{equation}
+to restrict $p$ to injections or
+\begin{equation}
+  \forall Y \in b. \exists X \in a. p(X, Y)
+\end{equation}
+to ensure surjectivity or remove \cref{eq:def2} to consider partial functions. Lastly, one can replace all occurrences of $b$ with $a$ so as to model endofunctions instead.
 
+\paragraph{Notes.}
+\begin{itemize}
+\item \textsc{ForcLift} fails on all of these.
+\item Functions, surjections, and their partial counterparts are/were already liftable.
+It seems like lifting injectivity (which is a fairly general property) is the main accomplishment.
+(But this is just the one I noticed.
+There may be many others as well.)
+\item Here, $[\cdot]$ is the Iverson bracket.
+\end{itemize}
+
+\paragraph{Results.}
 \begin{itemize}

### 2022-03-03 notes/notes.tex
Editing

@@
 \DeclareMathOperator{\dom}{dom}
+\DeclareMathOperator{\id}{id}
 \DeclareMathOperator{\Imm}{Im}
@@
 
-\section{Definitions}
-
 \begin{figure}[t]
@@
   \end{tikzpicture}
-  \caption{An illustration of the main idea. TODO: refer to this in the introduction.}
+  \caption{An illustration of the main idea.}
   \label{fig:idea}
@@
 
+In a way, we're dividing the idea of domain recursion between the IDR and the Ref nodes, thus also generalising it. [TODO: mention \cref{fig:idea}.]
+
+\section{Preliminaries}
+
 \paragraph{Things I might need to explain.}
 \begin{itemize}
-\item atom, (positive/negative) literal, constant, predicate, argument, arity, variable, clause, unit clause, first-order logic
-\item $\Vars$, $\Vars(c) = \Vars(L) \cup \Vars(C)$
-\item $\Doms$ on both formulas and clauses. $\Doms(c) = \Imm \delta_c$, and $\Doms(\phi) = \bigcup_{c \in \phi} \Doms(c)$.
-\item $\WMC$, $\wwp$, $\wwn$, $\Imm$
+\item atom, (positive/negative) literal, constant, predicate, variable, clause, unit clause, first-order logic
+\item $\WMC$, $\wwp$, $\wwn$.
 \item two parts: compilation and inference.
 \item During inference, there is a domain size map $\size\colon \mathcal{D} \to \mathbb{N}_0$.
-\item mention which rules are in $\Gamma$ and which ones are in $\Delta$ (and why tryCache has to be in $\Delta$).
+\item mention which rules are in $\Gamma$ and which ones are in $\Delta$ (and why tryCache has to be in $\Delta$). TODO: having notation for $\Delta$ and $\Gamma$ isn't that necessary
 \item \textsc{ForcLift}
-\item In a way, we're dividing the idea of domain recursion between the IDR and the Ref nodes, thus also generalising it. [This is good context to refer to \cref{fig:idea}.]
+\item $\sqcup$ for both sets and functions
 \end{itemize}
@@
 \item We write $\to$ for functions, $\pfun$ for partial functions, $\twoheadrightarrowtail$ for bijections, and $\hookrightarrow$ for set inclusion.
+Let $\id$ denote the identity function (on any domain).
+For any function $f$, let $\Imm f$ be the image of $f$.
 \end{itemize}
@@
 \begin{definition}
-  A \emph{domain} is a symbol for a finite set.\footnote{In the context of functions, the domain of a function $f$ retains its usual meaning and is denoted $\dom(f)$.} Let $\mathcal{D}$ be the set of all domains.
-Note that this set expands during the compilation.
+  A \emph{domain} is a symbol for a finite set.\footnote{In the context of functions, the domain of a function $f$ retains its usual meaning and is denoted $\dom(f)$.}
 \end{definition}
@@
 \begin{definition}
-  A \emph{clause} is a triple $c = (L, C, \delta_c)$, where $L$ is the set of literals, $C$ is a set of constraints, and $\delta_c\colon \Vars(c) \to \mathcal{D}$ is a function that maps all variables in $c$ to their domains such that (s.t.) if $(x, y) \in C$ for some variables $x$ and $y$, then $\delta_c(x) = \delta_c(y)$.
-Equality of clauses is defined in the usual way (i.e., all variables, domains, etc.
-must match).
-TODO: we will always use this subscript notation for the $\delta$'s.
+  A \emph{clause} is a triple $c = (L, C, \delta_c)$, where $L$ is a set of literals, $C$ is a set of constraints, and $\delta_c$ is a function that maps all variables in $c$ to their domains such that (s.t.) if $(x, y) \in C$ for some variables $x$ and $y$, then $\delta_c(x) = \delta_c(y)$.
+Note that for convenience sometimes we write $\delta_c$ for the domain map of $c$ without unpacking $c$ into its three constituents.
+
+  Also, let $\Vars$ be a function that maps clauses and sets of literals and inequalities to the set of variables contained within. In particular, $\Vars(c) \coloneqq \Vars(L) \cup \Vars(C)$.
 \end{definition}
 
-TODO: implicit universal quantification.
+A \emph{formula} is a set of clauses.
+All variables in a clause are implicitly universally quantified (but note that variables are never shared among clauses), and all clauses in a formula are implicitly linked by conjunction.
+This way, one can read formulas as defined here as sentences in first-order logic.
 
-A \emph{formula} is a set of clauses.
+TODO: Note: we will reuse this several times.
+\begin{example} \label{example:first}
+  Let $\phi \coloneqq \{\, c_1, c_2 \,\}$ be a formula, where
+  \[
+  c_1 \coloneqq (\{\, \neg p(X, Y), \neg p(X, Z) \,\}, \{\, (Y, Z) \,\}, \{\, X \mapsto a, Y \mapsto b, Z \mapsto b \,\}),
+  \]
+  and
+  \[
+  c_2 \coloneqq (\{\, \neg p(X, Y), \neg p(Z, Y) \,\}, \{\, (X, Z) \,\}, \{\, X \mapsto a, Y \mapsto b, Z \mapsto a \,\}),
+  \]
+  for some predicate $p$, variables $X$, $Y$, $Z$, and domains $a$ and $b$. Then in first-order logic $\phi$ could be read as
+  \begin{align*}
+    (\forall X \in a. \forall Y \in b. \forall Z \in b. Y \ne Z &\implies \neg p(X, Y) \lor \neg p(X, Z)) \land \\
+    (\forall X \in a. \forall Y \in b. \forall Z \in a. X \ne Z &\implies \neg p(X, Y) \lor \neg p(Z, Y)).
+  \end{align*}
+\end{example}
 
+\paragraph{Hashing.}
 We use hash codes to efficiently check whether a recursive relationship between two formulas is plausible.
-(It is plausible if the formulas are equal up to variables and domains.) The hash code of a clause $c = (L, C, \delta_c)$ combines the hash codes of the sets of constants and predicates in $c$, the numbers of positive and negative literals, the number of inequality constraints $|C|$, and the number of variables $|\Vars(c)|$.
+(It is plausible if the formulas are equal up to variables and domains.) The hash code of a clause $c = (L, C, \delta)$ combines the hash codes of the sets of constants and predicates in $c$, the numbers of positive and negative literals, the number of inequality constraints $|C|$, and the number of variables $|\Vars(c)|$.
 The hash code of a formula $\phi$ combines the hash codes of all its clauses and is denoted $\#\phi$.
-
-\begin{definition}
-  Let $\gr(\cdot; \sigma)$ be the function (parameterised by the domain size function $\size$) that takes a clause $c = (L, C, \delta)$ and returns the number of ways the variables in $c$ can be replaced by elements of their respective domains in a way that satisfies the inequality constraints.\footnote{Note that the literals of the clause have no effect on $\gr$.} Formally, for each variable $v \in \Vars(c)$, let $C_v = \{ w \mid (u, w) \in C \setminus \Vars(c)^2 \text{, }u \ne v \}$ be the set of (explicitly named) constants that $v$ is permitted to be equal to.
-Then
-  \[
-  \gr(c; \sigma) \coloneqq \left|\left\{\, (e_v)_{v \in \Vars(c)} \in \prod_{v \in \Vars(c)} C_v \sqcup [\sigma(\delta(v)) - |C_v|] \;\middle|\; \right.\right.
-e_u \ne e_w \text{ for all } (u, w) \in C \cap \Vars(c)^2 \left.\left.
-\vphantom{\prod_{v \in \Vars(c)}} \,\right\}\right|
-  \]
-  for any clause $c$. (Here, $[n] \coloneqq \{\,1, 2, \dots, n\,\}$ for any non-negative integer $n$.)
-\end{definition}
-
-TODO: how does the algorithm prevent the number in $[\cdot]$ from being negative?
 
@@
 
-\section{From Circuits to Labelled Graphs}
+\section{Generalising Circuits to Labelled Graphs}
 
@@
 The meanings of other types are described...}
-\item have an example of a simple FCG. Describe the figure from later.
+\item have an example of a simple FCG. Maybe describe the figure from later and move it here.
 \end{itemize}
 
-\section{Search/Compilation}
+\section{Compilation as Search}
 
@@
 
+Let $\mathcal{D}$ be the set of all domains. Note that this set expands during the compilation.
+
 \subsection{Identifying Possibilities for Recursion}
 
-\paragraph{Notation.}
-For any clause $c = (L, C, \delta_c)$, bijection $\beta\colon \Vars(c) \twoheadrightarrowtail V$ (for some set of variables $V$) and function $\gamma\colon \Doms(c) \to \mathcal{D}$, let $c[\beta, \gamma] = d$ be the clause $c$ with all occurrences of any variable $v \in \Vars(c)$ in $L$ and $C$ replaced with $\beta(v)$ (so $\Vars(d) = V$) and $\delta_d\colon V \to \mathcal{D}$ defined as $\delta_d \coloneqq \gamma \circ \delta_c \circ \beta^{-1}$.
+\subsubsection{Notation}
+
+Let $\Doms$ be a function that maps any clause or formula to the set of domains used within.
+Specifically, $\Doms(c) \coloneqq \Imm \delta_c$ for any clause $c$, and $\Doms(\phi) \coloneqq \bigcup_{c \in \phi} \Doms(c)$ for any formula $\phi$.
+
+For partial functions $\alpha, \beta\colon A \pfun B$ s.t.
+$\alpha|_{\dom(\alpha) \cap \dom(\beta)} = \beta|_{\dom(\alpha) \cap \dom(\beta)}$, we write $\alpha \cup \beta$ for the unique partial function s.t.
+$\alpha \cup \beta|_{\dom(\alpha)} = \alpha$, and $\alpha \cup \beta|_{\dom(\beta)} = \beta$.
+
+For any clause $c = (L, C, \delta_c)$, bijection $\beta\colon \Vars(c) \twoheadrightarrowtail V$ (for some set of variables $V$), and function $\gamma\colon \Doms(c) \to \mathcal{D}$, let $c[\beta, \gamma] = d$ be the clause $c$ with all occurrences of any variable $v \in \Vars(c)$ in $L$ and $C$ replaced with $\beta(v)$ (so $\Vars(d) = V$) and $\delta_d\colon V \to \mathcal{D}$ defined as $\delta_d \coloneqq \gamma \circ \delta_c \circ \beta^{-1}$.
 In other words, $\delta_d$ is the unique function that makes
@@
 \]
-commute.
+commute. For example, if clause $c_1$ is as in \cref{example:first}, then
+\begin{multline*}
+  c_1[\{\, X \mapsto A, Y \mapsto B, Z \mapsto C \,\}, \{\, a \mapsto b, b \mapsto c \,\}] = \\
+  (\{\, \neg p(A, B), \neg p(A, C) \,\}, \{\, (B, C) \,\}, \{\, A \mapsto b, B \mapsto c, C \mapsto c \,\}).
+\end{multline*}
+
+\subsubsection{Everything Else}
 
@@
 
-The function \texttt{traceAncestors} returns \texttt{null} if domain $d \in \mathcal{D}$ is not an ancestor of domain $e \in \mathcal{D}$.
-Otherwise, it returns \texttt{true} if the size of $e$ is guaranteed to be strictly smaller than the size of $d$ (i.e., there is domain created by the constraint removal rule on the path from $d$ to $e$) and \texttt{false} if their sizes will be equal at some point during inference.
-
-Notation: For partial functions $\alpha, \beta\colon A \pfun B$ s.t.
-$\alpha|_{\dom(\alpha) \cap \dom(\beta)} = \beta|_{\dom(\alpha) \cap \dom(\beta)}$, we write $\alpha \cup \beta$ for the unique partial function s.t.
-$\alpha \cup \beta|_{\dom(\alpha)} = \alpha$, and $\alpha \cup \beta|_{\dom(\beta)} = \beta$.
-TODO: explain $\sqcup$ for both sets and functions.
-
 \paragraph{TODO}
@@
 
-Diagramatically, \texttt{constructDomainMap} attempts to find $\gamma\colon \Doms(c) \to \Doms(d)$ s.t. the following diagram commutes (and returns \texttt{null} if such a function does not exist):
+Diagramatically, \texttt{constructDomainMap} attempts to find $\gamma\colon \Doms(c) \to \Doms(d)$ s.t.
 \[
@@
 \]
+commutes (and returns \texttt{null} if such a function does not exist).
 
+TODO: update this example. Fix references.
 \begin{example} \label{example}
-  Let $\phi$ be the formula
-  \begin{align}
-    \forall X \in a. \forall Y \in b. \forall Z \in b. Y \ne Z &\implies \neg p(X, Y) \lor \neg p(X, Z)\label{phi1} \\
-    \forall X \in a. \forall Y \in b. \forall Z \in a. X \ne Z &\implies \neg p(X, Y) \lor \neg p(Z, Y).\label{phi2}
-  \end{align}
-  and $\psi$ be the formula
-  \begin{align}
-    \forall X \in a'. \forall Y \in b^\bot. \forall Z \in b^\bot. Z \ne Y &\implies \neg p(X, Y) \lor \neg p(X, Z)\label{psi1} \\
-    \forall X \in a'. \forall Y \in b^\bot. \forall Z \in a'. X \ne Z &\implies \neg p(X, Y) \lor \neg p(Z, Y)\label{psi2}
-  \end{align}
+  Let $\phi$ be the formula from \cref{example:first} and $\psi \coloneqq \phi[\id, \{\, a \mapsto a', b \mapsto b^\bot \,\}]$ (i.e., $\phi$ with both of its domains replaced).
 
-  The relevant domains and the definition of $\pi$ is in \cref{fig:example}.
   Since $\#\phi = \#\psi$, and the formulas are non-empty, the algorithm proceeds with the for-loops on \cref{line:for1,line:for2,line:generateMaps}.
@@
 
-\section{Other Topics}
-
-\begin{itemize}
-\item new rules that don't create vertices (e.g., duplicate removal, unconditional contradiction detection, etc.)
-\item some notes on halting
-  \begin{itemize}
-  \item Search is infinite. Some rules increase the size of the formula(s), but most reduce it.
-  \item Inference is guaranteed to terminate if at least one domain shrinks by at least one.
-But note that allowing recursive calls with the same domain sizes (e.g., $f(n) = f(n) + \dots$) could be useful because these problematic terms might cancel out.
-  \item It's impossible for $n \gets n - 1$ and $\texttt{for } n \in \dots$ to combine in a way that results in an infinite loop.
-  \end{itemize}
-\item care should be taken when cloning to preserve the validity of the cache and avoid infinite cycles (we use a separate (node $\to$ node) cache for this)
-\item another change: one rule can return more than one `continuation of the graph'
-\end{itemize}
-
 \section{How to Evaluate an FCG} \label{sec:evaluation}
@@
 Along with the three vertex types described above, here are all the other ones. This section is mostly just taken from \cite{DBLP:conf/ijcai/BroeckTMDR11} but with some changes in notation.
+
+\begin{definition}
+  Let $\gr(\cdot; \sigma)$ be the function (parameterised by the domain size function $\size$) that takes a clause $c = (L, C, \delta)$ and returns the number of ways the variables in $c$ can be replaced by elements of their respective domains in a way that satisfies the inequality constraints.\footnote{Note that the literals of the clause have no effect on $\gr$.} Formally, for each variable $v \in \Vars(c)$, let $C_v = \{ w \mid (u, w) \in C \setminus \Vars(c)^2 \text{, }u \ne v \}$ be the set of (explicitly named) constants that $v$ is permitted to be equal to.
+Then
+  \[
+  \gr(c; \sigma) \coloneqq \left|\left\{\, (e_v)_{v \in \Vars(c)} \in \prod_{v \in \Vars(c)} C_v \sqcup [\sigma(\delta(v)) - |C_v|] \;\middle|\; \right.\right.
+e_u \ne e_w \text{ for all } (u, w) \in C \cap \Vars(c)^2 \left.\left.
+\vphantom{\prod_{v \in \Vars(c)}} \,\right\}\right|
+  \]
+  for any clause $c$. (Here, $[n] \coloneqq \{\,1, 2, \dots, n\,\}$ for any non-negative integer $n$.)
+\end{definition}
+
+TODO: how does the algorithm prevent the number in $[\cdot]$ from being negative?
 
@@
     \toprule
-    \multicolumn{3}{c}{Function Class} & \multicolumn{3}{c}{Complexity} \\
+    \multicolumn{3}{c}{Function Class} & \multicolumn{3}{c}{Asymptotic Complexity of Counting} \\
     Partial & Endo & Class & Best Known & With Circuits & With Graphs \\
     \midrule
-    \rowcolor{lightgray}\cmark/\xmark & \cmark/\xmark & Functions & $\lg m$ & $m$ & $m$ \\
-    \xmark & \xmark & \multirow{4}{*}{Surjections} & $n \lg m$ \cite{30049} & ? & ? \\
-    \xmark & \cmark & & $n \lg m$ \cite{30049} & ? & ? \\
+    \rowcolor{gray!10}\cmark/\xmark & \cmark/\xmark & Functions & $\log m$ & $m$ & $m$ \\
+    \xmark & \xmark & \multirow{4}{*}{Surjections} & $n \log m$ \cite{30049} & ? & ? \\
+    \xmark & \cmark & & $n \log m$ \cite{30049} & ? & ? \\
     \cmark & \xmark & & \multicolumn{3}{c}{Same as injections from $b$ to $a$} \\
     \cmark & \cmark & & \multicolumn{3}{c}{Same as endo-injections} \\
-    \rowcolor{lightgray}\xmark & \xmark & & $\lg m$ & - & $mn$ \\
-    \rowcolor{lightgray}\xmark & \cmark & & $\lg m$ & - & $m^3$ \\
-    \rowcolor{lightgray}\cmark & \xmark & & $\min\{\, m, n \,\}^2$ & - & $n^2$ \\
-    \rowcolor{lightgray}\cmark & \cmark & \multirow{-4}{*}{Injections} & $m^2$ & - & - \\
-    \xmark & \xmark & \multirow{3}{*}{Bijections} & $\lg m$ & - & $m$ \\
+    \rowcolor{gray!10}\xmark & \xmark & & $\log m$ & - & $mn$ \\
+    \rowcolor{gray!10}\xmark & \cmark & & $\log m$ & - & $m^3$ \\
+    \rowcolor{gray!10}\cmark & \xmark & & $\min\{\, m, n \,\}^2$ & - & $n^2$ \\
+    \rowcolor{gray!10}\cmark & \cmark & \multirow{-4}{*}{Injections} & $m^2$ & - & - \\
+    \xmark & \xmark & \multirow{3}{*}{Bijections} & $\log m$ & - & $m$ \\
     \xmark & \cmark & & \multicolumn{3}{c}{\multirow{2}{*}{Same as (partial) (endo-)injections}} \\
@@
 All asymptotic complexities are in $\Theta(\cdot)$.
-Logarithm with base two.
 This is for unweighted counting.
 A hyphen means that no solution was found.
-TODO: add shaded rows.
+Assuming all arithmetic operations to take constant time.
+Maybe a better solution could be found with more search.
 TODO: explain assumptions for the counts to not be zero.
 TODO: double check.
-TODO: maybe combine more rows/columns.}
+TODO: maybe combine more rows/columns.
+TODO: transfer the citations to text.}
 \end{table}
@@
       child {node {$\wedge$}
-        child {node {$1_{(\{\, p(x, X) \,\}, \emptyset, \{\, X \mapsto b^\top \,\})}$}}
+        child {node[fill=green!10] {$1_{(\{\, p(x, X) \,\}, \emptyset, \{\, X \mapsto b^\top \,\})}$}}
         child {node {$\wedge$}
-          child {node {$1_{(\{\, \neg p(x, X) \,\}, \emptyset, \{\, X \mapsto b^\bot \,\})}$}}
+          child {node[fill=green!10] {$1_{(\{\, \neg p(x, X) \,\}, \emptyset, \{\, X \mapsto b^\bot \,\})}$}}
           child {node {$\wedge$}
-            child {node {$1_{(\{\, \neg p(X, Y) \,\}, \{\, (X, x) \,\}, \{\, X \mapsto a, Y \mapsto b^\top \,\})}$}}
+            child {node[fill=green!10] {$1_{(\{\, \neg p(X, Y) \,\}, \{\, (X, x) \,\}, \{\, X \mapsto a, Y \mapsto b^\top \,\})}$}}
             child {node {$\CR_{a \mapsto a'}$}
               child {node {$\wedge$}
-                child {node {$\bot_{(\emptyset, \{\, (X, Y) \,\}, \{\, X \mapsto b^\top, Y \mapsto b^\top \,\})}$}}
+                child {node[fill=red!10] {$\bot_{(\emptyset, \{\, (X, Y) \,\}, \{\, X \mapsto b^\top, Y \mapsto b^\top \,\})}$}}
                 child {node (ref) {$\Reff_{\{\, a \mapsto a', b \mapsto b^\bot \,\}}$}}
@@
 \begin{itemize}
-\item $b^\bot$ should be part of the notation for counting.
-\item Formulas for partial injections, how to add totality, surjectivity.
 \item Describe \cref{fig:examplefcg} and connect it to the algebraic formula.
@@
 FCGs that compare the size of a domain to an integer can be constructed automatically using compilation rules, although $n$ is upper bounded by the maximum number of variables in any clause of the input formula since there is no rule that would introduce new variables.
-\item Maybe a big table: name, optimal solution and its complexity, best found solution, its depth, its complexity. Also mention that it only takes a few seconds to find these solutions.
-\item Going beyond depth 6 (or sometimes even completing depth 6) is computationally infeasible with the current implementation, but depth at most 5 can be searched within at most a few seconds.
+\item Mention that it only takes a few seconds to find these solutions.
+Going beyond depth 6 (or sometimes even completing depth 6) is computationally infeasible with the current implementation, but depth at most 5 can be searched within at most a few seconds.
 \item Combine the tikz and the algebraic notation into one, so I don't need to have two versions. But how? Maybe associate a symbol with each type and only to the types that I use?
-\item Partial bijection is the same as partial injection.
 \item the exponential solutions can be computed in quadratic time with dynamic programming!
@@
 \item Note that in some cases different descriptions of the same problem lead to different solutions (with different complexities).
-\item Maybe we are actually guaranteed that the solution is always polynomial-time.
+\item Maybe we are actually guaranteed that the solution is always polynomial-time. Except... running time could be infinite?
 \end{itemize}
@@
 
+\section{Discussion}
+
+\begin{itemize}
+\item new rules that don't create vertices (e.g., duplicate removal, unconditional contradiction detection, etc.)
+\item some notes on halting
+  \begin{itemize}
+  \item Search is infinite. Some rules increase the size of the formula(s), but most reduce it.
+  \item Inference is guaranteed to terminate if at least one domain shrinks by at least one.
+But note that allowing recursive calls with the same domain sizes (e.g., $f(n) = f(n) + \dots$) could be useful because these problematic terms might cancel out.
+  \item It's impossible for $n \gets n - 1$ and $\texttt{for } n \in \dots$ to combine in a way that results in an infinite loop.
+  \end{itemize}
+\item care should be taken when cloning to preserve the validity of the cache and avoid infinite cycles (we use a separate (node $\to$ node) cache for this)
+\end{itemize}
+
 \section{Conclusions and Future Work}

### 2022-03-12 aiai_talk/talk.tex
First few slides for the new talk

\documentclass{beamer}
\usepackage[utf8]{inputenc}
\usepackage[UKenglish]{babel}
\usepackage[UKenglish]{isodate}
\usepackage{amsmath}
\usepackage{mathtools}
\usepackage{tikz}

\usetheme{CambridgeUS}

\usetikzlibrary{shapes}
\usetikzlibrary{arrows}
\usetikzlibrary{arrows.meta}
\usetikzlibrary{positioning}

\beamertemplatenavigationsymbolsempty
\DeclareRobustCommand{\stirling}{\genfrac\{\}{0pt}{}}

\author[Paulius Dilkas]{\textbf{Paulius Dilkas}, Vaishak Belle}
\title[Recursive Solutions to FOMC]{Recursive Solutions to First-Order Model Counting}
\date{AIAI Seminar, 28th March 2022}

\begin{document}
\addtobeamertemplate{block begin}{\setlength\abovedisplayskip{0pt}}

\maketitle

\begin{frame}{Some Elementary Counting}
  \begin{block}{A Counting Problem}
    Suppose we were meeting in person, the room had \structure{$n$} seats, and there were \structure{$m \le n$} attendees. How many ways would there be to seat everyone?
  \end{block}

  \pause
  More explicitly, we assume that:
  \begin{itemize}
  \item each attendee gets one seat (i.e., at least one \alert{and} at most one),
  \item and a seat can accommodate at most one person.
  \end{itemize}

  \pause
  \alert{Answer:} \structure{$n^{\underline{m}} = n \cdot (n-1)\cdots(n-m+1)$}.

  Note: this problem is equivalent to counting \structure{$[m] \to [n]$} injections.

\end{frame}
% wouldn't it be nice if we could just describe this problem and have an algorithm solve it for us?

\begin{frame}{Let's Express This Problem in Logic!}
  \centering
  \includegraphics[height=0.8\textheight]{spock.jpg}
\end{frame}

\begin{frame}{Let's Express This Problem in Logic!}
  \begin{itemize}
  \item Let \structure{$M$} and \structure{$N$} be sets (i.e., \alert{domains}) such that \structure{$|M| = m$}, and \structure{$|N| = n$}
  \item Let \structure{$P \subseteq M \times N$} be a relation (i.e., \alert{predicate}) over sets \structure{$M$} and \structure{$N$}
  \item We can describe all of the constraints in first-order logic
    \begin{itemize}
    \item \pause each attendee gets a seat (i.e., at least one seat)
      \[
      \forall x \in M. \exists y \in N. P(x, y)
      \]
    \item \pause one person cannot occupy multiple seats
      \[
      \forall x \in M. \forall y, z \in N. P(x, y) \land P(x, z) \Rightarrow y=z
      \]
    \item \pause one seat cannot accommodate multiple attendees
      \[
      \forall w, x \in M. \forall y \in N. P(w, y) \land P(x, y) \Rightarrow w=x
      \]
    \end{itemize}
  \end{itemize}
  \pause
  The first two sentences constrain \structure{$P$} to be a function, and the last one makes it injective.
  \onslide<6>{
    \begin{tikzpicture}[remember picture,overlay]
      \node at (current page.center) {\includegraphics[height=0.4\textheight]{happy.jpg}};
    \end{tikzpicture}
  }
\end{frame}
% one could also add probabilities to these sentences to say that, e.g., there is a 1% probability of somebody taking up two seats, somebody sitting on somebody else's lap, somebody sitting on the floor, etc.

\begin{frame}{Overview of the Problem}
  \begin{itemize}
  \item \alert{First-order model counting} is the problem of counting the models of a sentence in first-order logic.
  \item The \alert{(symmetric) weighted} variation of the problem adds weights (e.g., probabilities) to predicates.
  \item Thus, SWFOMC can also be used for efficient \alert{probabilistic inference} in relational models.
  \item None of the (implemented) (SW)FOMC algorithms are able to count, e.g., \alert{injective} and \alert{bijective} functions.
  \end{itemize}
\end{frame}

% TODO: this can be fixed via recursion. Add a numerical example, show its complexity.
\begin{frame}{Recursion to the Rescue!}
  \[
  f(m, n) =
  \begin{cases}
    1 & \text{if } m = 0 \text{ and } n = 0 \\
    0 & \text{if } m > 0 \text{ and } n = 0 \\
    f(m, n-1) + mf(m-1, n-1) & \text{otherwise.}
  \end{cases}
  \]
  \begin{itemize}
  \item Optimal time complexity to compute \structure{$n^{\underline{m}}$} is \structure{$\Theta(\log m)$}
  \end{itemize}
\end{frame}

\end{document}

### 2022-03-12 early_talk/talk.tex
First few slides for the new talk

--- 2021-12-27 talk/talk.tex
@@
 
-\begin{frame}{Counting (Unweighted) Functions: Currently Unliftable (1)}
+\begin{frame}{Counting Injections}
   %% \cite{stanley2011enumerative}
@@
   %% \end{block}
-  \begin{block}{Injections}
   Theory:
@@
   Answer: $n^{\underline{m}} = n \cdot (n-1)\cdots(n-m+1)$ if $m \le n$ and $0$ otherwise (for positive $m$ and $n$).
+\end{frame}
 
-    \pause
-    \alert{Answer found by Forclift:}
+\begin{frame}
+  \begin{block}{One answer}
     \[
@@
     \]
-    (exponential...)
+  \end{block}
+  \begin{block}{Another answer (almost found by Forclift)}
+    (The missing parts are highlighted) Same $f$ and...
+    \[
+    g(m, n) =
+    \begin{cases}
+      1 & \text{if } m = 0 \\
+      \alert{n+1} & \alert{\text{if } m = 1} \\
+      \sum_{k=0}^{\min\{n, 1\}} \sum_{l=0}^{\min\{n-k, 1\}} \alert{\frac{n!}{(n-m-l)!}} g(m-2, n-m-l) & \text{otherwise.}
+    \end{cases}
+    \]
   \end{block}
@@
     Answer: $n!\stirling{m}{n} = \sum_{i=0}^n (-1)^i\binom{n}{i}(n-i)^m$.
-  \end{block}
-  \begin{block}{Bijections}
-    Theory:
-    \begin{align*}
-      \forall x \in M. \forall y, z \in N. &P(x, y) \land P(x, z) \Rightarrow y=z \\
-      \forall x \in M. \exists y \in N. &P(x, y) \\
-      \alert{\forall w, x \in M. \forall y \in N.} &\alert{P(w, y) \land P(x, y) \Rightarrow w=x} \\
-      \alert{\forall y \in N. \exists x \in M.} &\alert{P(x, y)}
-    \end{align*}
-    Answer: $n!$ if $m=n$.
   \end{block}
@@
 
+\begin{frame}{Bijections}
+  \begin{align*}
+    \forall x \in M. \forall y, z \in N. &P(x, y) \land P(x, z) \Rightarrow y=z \\
+    \forall x \in M. \exists y \in N. &P(x, y) \\
+    \forall w, x \in M. \forall y \in N. & P(w, y) \land P(x, y) \Rightarrow w=x \\
+    \forall y \in N. \exists x \in M. & P(x, y)
+  \end{align*}
+  Answer: $n!$ if $m=n$ and zero otherwise.
+\end{frame}
+
+\begin{frame}{Bijections: a linear answer found by Forclift}
+  \begin{align*}
+    f(m, n) &= - f(m, n-1) + \sum_{k=0}^m \binom{m}{k}[k < 2]f(m - k, n - 1) \\
+    &= - f(m, n-1) + f(m, n - 1) + m \times f(m - 1, n - 1) \\
+    &= m \times f(m - 1, n - 1)
+  \end{align*}
+  This works if supplied with the right base cases:
+  \begin{align*}
+    f(0, 0) &= 1, \\
+    f(m, 0) &= 0 \text{ (for all $m > 0$),} \\
+    f(0, n) &= 0 \text{ (for all $n > 0$).}
+  \end{align*}
+\end{frame}
+
 \end{document}

### 2022-03-12 notes/notes.tex
First few slides for the new talk

@@
 \item mention which rules are in $\Gamma$ and which ones are in $\Delta$ (and why tryCache has to be in $\Delta$). TODO: having notation for $\Delta$ and $\Gamma$ isn't that necessary
+\item My formalisation of constraints is more restrictive than the original (e.g., in the thesis).
 \item \textsc{ForcLift}
@@
   Let $\phi \coloneqq \{\, c_1, c_2 \,\}$ be a formula, where
-  \[
+  \begin{equation} \label{phi1}
     c_1 \coloneqq (\{\, \neg p(X, Y), \neg p(X, Z) \,\}, \{\, (Y, Z) \,\}, \{\, X \mapsto a, Y \mapsto b, Z \mapsto b \,\}),
-  \]
+  \end{equation}
   and
-  \[
+  \begin{equation} \label{phi2}
     c_2 \coloneqq (\{\, \neg p(X, Y), \neg p(Z, Y) \,\}, \{\, (X, Z) \,\}, \{\, X \mapsto a, Y \mapsto b, Z \mapsto a \,\}),
-  \]
+  \end{equation}
   for some predicate $p$, variables $X$, $Y$, $Z$, and domains $a$ and $b$. Then in first-order logic $\phi$ could be read as
@@
 \begin{itemize}
-\item update the example to not refer to things that don't exist anymore
-\item introduce/describe and \cref{alg:trycache} and describe the cache that's being used.
+\item introduce/describe \cref{alg:trycache} and describe the cache that's being used.
 \item explain why $\rho \cup \gamma$ is possible
@@
 Diagramatically, \texttt{constructDomainMap} attempts to find $\gamma\colon \Doms(c) \to \Doms(d)$ s.t.
-\[
+\begin{equation} \label{eq:commute}
 \begin{tikzcd}
@@
 \end{tikzcd}
-\]
+\end{equation}
 commutes (and returns \texttt{null} if such a function does not exist).
@@
   Let $\phi$ be the formula from \cref{example:first} and $\psi \coloneqq \phi[\id, \{\, a \mapsto a', b \mapsto b^\bot \,\}]$ (i.e., $\phi$ with both of its domains replaced).
-
-  Since $\#\phi = \#\psi$, and the formulas are non-empty, the algorithm proceeds with the for-loops on \cref{line:for1,line:for2,line:generateMaps}.
+Since $\#\phi = \#\psi$, and both formulas are non-empty, the algorithm proceeds with the for-loops on \cref{line:for1,line:for2,line:generateMaps}.
 Suppose $c$ in the algorithm refers to \cref{phi1}, and $d$ to \cref{psi1}.
@@
   \end{itemize}
-  Since $\beta$ and $\rho$ `commute' (TODO: as in the diagram above), and there are no new domains in $\Doms(c)$ and $\Doms(d)$, $\gamma$ exists and is equal to $\rho$.
+  Since $\beta$ and $\rho$ commute (as in \cref{eq:commute}), and there are no new domains in $\Doms(c)$ and $\Doms(d)$, $\gamma$ exists and is equal to $\rho$.
 Again, the returned pair $(\beta, \gamma)$ satisfies $c[\beta, \gamma] = d$.
-This $\gamma$ passes the \texttt{traceAncestors} checks exactly the same way as the one before, and \cref{line:recursion} calls \texttt{identifyRecursion($\emptyset$, $\emptyset$, $\rho$, true)}, which immediately returns $\rho = \{\, a \mapsto a', b \mapsto b^\bot \,\}$ as the final answer.
+\Cref{line:recursion} calls \texttt{identifyRecursion($\emptyset$, $\emptyset$, $\rho$, true)}, which immediately returns $\rho = \{\, a \mapsto a', b \mapsto b^\bot \,\}$ as the final answer.
 This means that one can indeed use an FCG for $\WMC(\phi)$ to compute $\WMC(\psi)$ by replacing every mention of $a$ with $a'$ and every mention of $b$ with $b^\bot$.

### 2022-03-16 aiai_talk/talk.tex
First draft of a full talk

@@
 \usepackage{tikz}
+\usepackage{complexity}
 
@@
 \usetikzlibrary{positioning}
+\usetikzlibrary{overlay-beamer-styles}
 
@@
 \DeclareRobustCommand{\stirling}{\genfrac\{\}{0pt}{}}
+
+\definecolor{color1}{HTML}{1B9E77}
+\definecolor{color2}{HTML}{D95F02}
 
@@
 
+\section{A Motivating Example}
+
 \begin{frame}{Some Elementary Counting}
-  \begin{block}{A Counting Problem}
+  \begin{exampleblock}{A Counting Problem}
     Suppose we were meeting in person, the room had \structure{$n$} seats, and there were \structure{$m \le n$} attendees. How many ways would there be to seat everyone?
-  \end{block}
+  \end{exampleblock}
 
@@
   \end{itemize}
+  \begin{block}{Claim}
+    This shortcoming can be addressed via support for (almost arbitrary) \alert{recursive functions}.
+  \end{block}
 \end{frame}
 
-% TODO: this can be fixed via recursion. Add a numerical example, show its complexity.
-\begin{frame}{Recursion to the Rescue!}
+\begin{frame}{Back to Our Example}
+  For instance, the following function counts injections
   \[
@@
   \]
+  \pause
   \begin{itemize}
-  \item Optimal time complexity to compute \structure{$n^{\underline{m}}$} is \structure{$\Theta(\log m)$}
+  \item \structure{$f$} can be computed in \structure{$\Theta(mn)$} time (via dynamic programming).
+  \item Optimal time complexity to compute \structure{$n^{\underline{m}}$} is \structure{$\Theta(\log m)$}.
+  \item But \structure{$\Theta(mn)$} is still much better than solving an equivalent \alert{$\#\P$-complete} problem in propositional logic.
+  \item The rest of this talk is about how such functions can be found automatically.
   \end{itemize}
@@
 
+\section{Graphs and Their Role in Knowledge Compilation}
+
+\begin{frame}{First-Order Knowledge Compilation}
+  \begin{columns}
+    \begin{column}{0.25\textwidth}
+      \centering
+      \begin{tikzpicture}[every node/.style={draw,ellipse},edge from parent/.style={draw,-latex},sibling distance=10mm,level distance=10mm]
+        \node[fill=red!50,fill on=<2>] (dr) {}
+        child {node {}
+          child {node {}
+            child {node {}}
+            child {node {}
+              child {node {}}
+              child {node {}
+                child {node {}}
+                child {node[fill=red!50,fill on=<2>] {}
+                  child {node {}
+                    child {node {}}
+                    child {node[fill=red!50,fill on=<2>] (ref) {}}
+        }}}}}};
+        \draw[-latex, bend right,alt=<2>{red}{black}] (ref) to (dr);
+      \end{tikzpicture}
+    \end{column}
+    \begin{column}{0.75\textwidth}
+      \begin{block}{Workflow Before}
+        \begin{enumerate}
+        \item Compile the formula to a \alert{circuit}
+        \item Evaluate to get the answer
+        \end{enumerate}
+      \end{block}
+      \pause
+      \begin{block}{Workflow After}
+        \begin{enumerate}
+        \item Compile the formula to a \alert{graph}
+        \item Extract the definitions of functions
+        \item Simplify
+        \item Supplement with \alert{base cases}
+        \item Evaluate to get the answer
+        \end{enumerate}
+      \end{block}
+    \end{column}
+  \end{columns}
+\end{frame}
+% Only Step 1 is fully automated at this point. The other steps are executed by hand.
+% Two parts: compilation and inference/evaluation.
+
+\begin{frame}{More Formally...}
+  \begin{definition}
+    A \alert{first-order deterministic decomposable negation normal form computational graph} (FCG) is a
+    \begin{itemize}
+    \item directed graph
+    \item (which is weakly connected)
+    \item with a single source,
+    \item labelled vertices,
+    \item and ordered outgoing edges.
+    \end{itemize}
+  \end{definition}
+\end{frame}
+
+\begin{frame}{How to Interpret an FCG}
+  \begin{columns}
+    \begin{column}{0.25\textwidth}
+      \centering
+      \begin{tikzpicture}[every node/.style={draw,ellipse},edge from parent/.style={draw,-latex},sibling distance=10mm,level distance=10mm]
+        \node[fill=red!50,fill on=<2>] (dr) {}
+        child {node[fill=red!50,fill on=<3>] {}
+          child {node[fill=red!50, fill on=<4>] {}
+            child {node[fill=red!50, fill on=<5>] {}}
+            child {node[fill=red!50, fill on=<6>] {}
+              child {node[fill=red!50, fill on=<7>] {}}
+              child {node[fill=red!50, fill on=<8>] {}
+                child {node[fill=red!50, fill on=<9>] {}}
+                child {node[fill=red!50, fill on=<10>] {}
+                  child {node[fill=red!50, fill on=<11>] {}
+                    child {node[fill=red!50, fill on=<12>] {}}
+                    child {node[fill=red!50, fill on=<13>] (ref) {}}
+        }}}}}};
+        \draw[-latex, bend right] (ref) to (dr);
+      \end{tikzpicture}
+    \end{column}
+    \begin{column}{0.75\textwidth}
+      \begin{align*}
+        f(m, n) &= \onslide<3->{\sum_{l=0}^m \binom{m}{l}} \onslide<5->{1} \onslide<4->{\times} \onslide<7->{1} \onslide<6->{\times} \onslide<9->{1} \onslide<8->{\times} \onslide<12->{[l<2]} \onslide<11->{\times} \onslide<13->{f(m-l, n-1)}\\
+        \onslide<14>{&= f(m, n-1) + mf(m-1, n-1)}
+      \end{align*}
+      \onslide<12>{
+        \[
+          [\phi] =
+          \begin{cases}
+            1 & \text{if } \phi \\
+            0 & \text{if } \neg\phi
+          \end{cases}
+          \]
+      }
+    \end{column}
+  \end{columns}
+\end{frame} % Things get more interesting if you do some computations before encountering a cycle or if you have several cycles.
+
+%% \section{Compilation: How to Construct an FCG}
+\section{Compilation: How to Construct an FCG}
+
+\begin{frame}{Compilation Rules}
+  \begin{definition}
+    A \alert{(compilation) rule} is a function that takes a \alert{formula} and returns a set of \structure{$(G, L)$} pairs, where
+    \begin{itemize}
+    \item \structure{$G$} is a (potentially \texttt{null}) FCG,
+    \item and \structure{$L$} is a list of formulas.
+    \end{itemize}
+  \end{definition}
+\end{frame}
+
+\begin{frame}{Example Rule: Independence}
+  Input formula:
+  \begin{gather}
+    ({\color{color1} \forall x, y \in L. x=y}) \land \label{eq:1} \tag{{\color{color1} 1}} \\
+    ({\color{color2} \forall x \in M. \forall y, z \in N. P(x, y) \land P(x, z) \Rightarrow y=z}) \land \label{eq:2} \tag{{\color{color2} 2}} \\
+    ({\color{color2} \forall w, x \in M. \forall y \in N. P(w, y) \land P(x, y) \Rightarrow w=x}) \label{eq:3} \tag{{\color{color2} 3}}
+  \end{gather}
+  \pause
+  Only one \structure{(G, L)} pair:
+  \[
+  G = 
+  \begin{tikzpicture}[edge from parent/.style={draw,-latex},baseline=(current bounding box.center)]
+    \node[draw,circle] {$\land$}
+    child {node {\color{color1} $\star$}}
+    child {node {\color{color2} $\star$}}
+    ;
+  \end{tikzpicture},
+  \qquad
+  L = \langle {\color{color1} \eqref{eq:1}}, {\color{color2} \eqref{eq:2} \land \eqref{eq:3}} \rangle
+  \]
+  Later, both \structure{$G$} and \structure{$L$} are incorporated into a larger \alert{search state}.
+\end{frame}
+% stars mark edges to nowhere and they are associated with the formulas in L via a certain order
+
+\begin{frame}{New Rule 1: (Generalised) Domain Recursion}
+  \begin{columns}
+    \begin{column}{0.20\textwidth}
+      \centering
+      \begin{tikzpicture}[every node/.style={draw,ellipse},edge from parent/.style={draw,-latex},sibling distance=10mm,level distance=10mm]
+        \node[fill=red!50] (dr) {}
+        child {node {}
+          child {node {}
+            child {node {}}
+            child {node {}
+              child {node {}}
+              child {node {}
+                child {node {}}
+                child {node {}
+                  child {node {}
+                    child {node {}}
+                    child {node (ref) {}}
+        }}}}}};
+        \draw[-latex, bend right] (ref) to (dr);
+      \end{tikzpicture}
+    \end{column}
+    \begin{column}{0.8\textwidth}
+      \begin{example}
+        Input formula:
+        \[
+        \forall x \in M. \forall y, z \in N. y \ne z \Rightarrow \neg P(x, y) \lor \neg P(x, z)
+        \]
+        Output formula (with a new constant \structure{$c \in M$}):
+        \begin{gather*}
+          \forall y, z \in N. y \ne z \Rightarrow \neg P(\alert{c}, y) \lor \neg P(\alert{c}, z) \\
+          \forall x \in M. \forall y, z \in N. \alert{x \ne c} \land y \ne z \Rightarrow \neg P(x, y) \lor \neg P(x, z)
+        \end{gather*}
+        %% Output FCG:
+        %% \begin{tikzpicture}[edge from parent/.style={draw,-latex}]
+        %%   \node[draw,circle] {$\textsc{DR}$}
+        %%   child {node {$\star$}}
+        %%   ;
+        %% \end{tikzpicture}
+        Here, domain recursion is applied to domain \structure{$M$}. It could similarly be applied to \structure{$N$} as well.
+      \end{example}
+    \end{column}
+  \end{columns}
+\end{frame}
+% We're still creating a vertex in a graph with one outgoing edge.
+
+\begin{frame}{New Rule 2: Constraint Removal}
+  \begin{columns}
+    \begin{column}{0.20\textwidth}
+      \centering
+      \begin{tikzpicture}[every node/.style={draw,ellipse},edge from parent/.style={draw,-latex},sibling distance=10mm,level distance=10mm]
+        \node (dr) {}
+        child {node {}
+          child {node {}
+            child {node {}}
+            child {node {}
+              child {node {}}
+              child {node {}
+                child {node {}}
+                child {node[fill=red!50] {}
+                  child {node {}
+                    child {node {}}
+                    child {node (ref) {}}
+        }}}}}};
+        \draw[-latex, bend right] (ref) to (dr);
+      \end{tikzpicture}
+    \end{column}
+    \begin{column}{0.8\textwidth}
+      \begin{example}
+        Input formula (with a constant \structure{$c \in M$}):
+        \begin{gather*}
+        \forall x \in \alert{M}. \forall y, z \in N. \alert{x \ne c} \land y \ne z \Rightarrow \neg P(x, y) \lor \neg P(x, z) \\
+        \begin{multlined}
+          \forall w,x \in \alert{M}. \forall y \in N. \alert{w \ne c} \land \alert{x \ne c} \land w \ne x \Rightarrow \\
+          \neg P(w, y) \lor \neg P(x, y)
+        \end{multlined}
+        \end{gather*}
+        Output formula (with a new domain \structure{$M' \coloneqq M \setminus \{\, c \,\}$}):
+        \begin{gather*}
+          \forall x \in \alert{M'}. \forall y, z \in N. y \ne z \Rightarrow \neg P(x, y) \lor \neg P(x, z) \\
+          \forall w,x \in \alert{M'}. \forall y \in N. w \ne x \Rightarrow \neg P(w, y) \lor \neg P(x, y)
+        \end{gather*}
+      \end{example}
+    \end{column}
+  \end{columns}
+\end{frame}
+% Requirement: all variables from M are != c.
+% Necessary because later we want to compare formulas and identify that they are isomorphic up to domains.
+
+\begin{frame}{New Rule 3: Identifying Possibilities for Recursion}
+  \begin{columns}
+    \begin{column}{0.25\textwidth}
+      \centering
+      \begin{tikzpicture}[every node/.style={draw,ellipse},edge from parent/.style={draw,-latex},sibling distance=10mm,level distance=10mm]
+        \node (dr) {}
+        child {node {}
+          child {node {}
+            child {node {}}
+            child {node {}
+              child {node {}}
+              child {node {}
+                child {node {}}
+                child {node {}
+                  child {node {}
+                    child {node {}}
+                    child {node[fill=red!50] (ref) {}}
+        }}}}}};
+        \draw[-latex, bend right, red] (ref) to (dr);
+      \end{tikzpicture}
+    \end{column}
+    \begin{column}{0.75\textwidth}
+      \begin{block}{Goal}
+      Check if the input formula is isomorphic (up to domains) to a previously encountered formula.
+      \end{block}
+      \begin{block}{Rough Outline}
+        \begin{enumerate}
+        \item Consider pairs of `similar' clauses.
+        \item Consider bijections between their sets of variables.
+        \item Extend each such bijection to a map between sets of domains.
+        \item If the bijection makes the clauses equal, and the domain map is compatible with previous domain maps, move on to another pair of clauses.
+        \end{enumerate}
+      \end{block}
+    \end{column}
+  \end{columns}
+\end{frame}
+
+%% \begin{frame}{Compilation as Search}
+%%   \begin{definition}
+%%     A \alert{(search) state} is a tuple \structure{$(G, C, L)$}, where:
+%%     \begin{itemize}
+%%     \item \structure{$G$} is an FCG (or \texttt{null}),
+%%     \item \structure{$C$} is a compilation cache that maps integers to sets of pairs $(\phi, v)$, where $\phi$ is a formula, and $v$ is a vertex of $G$ (which is used to identify opportunities for recursion),
+%%     \item and \structure{$L$} is a list of formulas (that are yet to be compiled). (Note that the order is crucial!)
+%%     \end{itemize}
+%%   \end{definition}
+%%   The search algorithm combines greedy and breadth-first search:
+%% \end{frame}
+
+\section{Summary}
+
+\begin{frame}{Summary \& Future Work}
+  \begin{block}{Summary}
+    The circuits hitherto used for FOMC become more powerful with:
+    \begin{itemize}
+    \item cycles,
+    \item generalised domain recursion,
+    \item and some more new compilation rules that support domain recursion.
+    \end{itemize}
+  \end{block}
+  \begin{block}{Future Work}
+    \begin{itemize}
+    \item Automate:
+      \begin{itemize}
+      \item extracting and simplifying the definitions of functions,
+      \item finding all base cases.
+      \end{itemize}
+    \item Open questions:
+      \begin{itemize}
+      \item What kind of \alert{sequences} are computable in this way?
+      \item Would using a \alert{different logic} extend the capabilities of FOMC further?
+      \end{itemize}
+    \end{itemize}
+  \end{block}
+\end{frame}
+
 \end{document}

### 2022-04-29 abstract/extended_abstract.tex
Add a short summary

\documentclass{article}
\usepackage[capitalise]{cleveref}
\usepackage[UKenglish]{babel}
\usepackage[UKenglish]{isodate}
\usepackage[utf8]{inputenc}
\usepackage{microtype}
\usepackage{tikz}
\usepackage{amsfonts}
\usepackage[affil-it]{authblk}

\usetikzlibrary{arrows}
\usetikzlibrary{arrows.meta}
\usetikzlibrary{shapes}

\usepackage{natbib}
\bibliographystyle{abbrvnat}

\title{Recursive Solutions to First-Order Model Counting}
\author{Paulius Dilkas}
\author{Vaishak Belle}
\affil{University of Edinburgh, Edinburgh, UK}

\begin{document}
\maketitle

% Definition and scope of the topic: FOMC

\emph{First-order model counting} (FOMC) is the problem of computing the number of models of a sentence in first-order logic given the size(s) of its domain(s) \citep{DBLP:conf/ijcai/BroeckTMDR11}. The main application of FOMC (or, rather, its \emph{weighted} variant WFOMC) is in probabilistic inference, particularly for statistical relational models such as Markov logic networks that define probabilities over sets of objects and relations thereof \citep{DBLP:conf/ijcai/BroeckTMDR11,DBLP:journals/cacm/GogateD16}.

Over slightly more than a decade, research on (W)FOMC advanced on both theoretical and empirical fronts. Several WFOMC algorithms such as ForcLift \citep{DBLP:conf/ijcai/BroeckTMDR11}, probabilistic theorem proving \citep{DBLP:journals/cacm/GogateD16}, and L2C \citep{DBLP:conf/kr/KazemiP16} were developed. More and more classes of formulas were shown to be \emph{liftable}, i.e., solvable in polynomial time with respect to the size(s) of the domain(s) \citep{DBLP:conf/kr/BremenK21,DBLP:conf/nips/KazemiKBP16,DBLP:conf/lics/KuusistoL18,DBLP:journals/jair/Kuzelka21}. Much of the researchers' attention was devoted to developing efficient solutions to formulas with up to two variables \citep{DBLP:conf/uai/BremenK21,DBLP:journals/corr/abs-2110-05992}.

% The problem you are to focus on the topic: recursion

However, none of the publicly available (W)FOMC algorithms can efficiently compute functions as simple as a factorial.\footnote{The problem of computing the factorial can be described using two variables and counting quantifiers, so it belongs to a fragment of first-order logic which is known to be liftable \citep{DBLP:journals/jair/Kuzelka21}.} We claim that this shortcoming is due to the inability of these algorithms to construct recursive solutions.

% If the problem was faced before, describe the state of the art.

The topic of recursion in the context of WFOMC has been studied before but in very limited ways. \Citet{DBLP:conf/ilp/BarvinekB0ZK21} use WFOMC to generate numerical data which is then used to conjecture recurrence relations that explain that data. \Citet{DBLP:conf/nips/Broeck11} introduced the idea of \emph{domain recursion}. Intuitively, domain recursion partitions a domain of size $n$ into a single explicitly named constant and the remaining domain of size $n-1$. However, many stringent conditions are enforced to ensure that the search for a tractable solution always terminates.

%1) But their code only conjectures stuff on data. My conjectures are guaranteed always true.
%2) everything has to be expressible in $\mathbf{C}^2$, i.e., the two-variable fragment of first-order logic with counting quantifiers on one domain.
%3) They only consider P-recursive functions, which means that, e.g., $f(n) = f(n-1)f(n-2)$ would not be allowed.

% Discuss the methods and novel techniques to be employed

\begin{figure}[t]
  \centering
  \begin{tikzpicture}[triangle/.style = {regular polygon, regular polygon sides=3}]
    \node[draw,ellipse] (a) at (0, 0) {$\phi(n)$};
    \node[draw,ellipse] (b) at (0, -2) {$\psi(n-1)$};
    \node[draw,ellipse] (c) at (-1, -4) {$\phi(n-1)$};
    \node[draw,triangle] (d) at (1, -4) {};
    \draw[-{Latex[length=2mm]}] (a) -- (b) node [midway,xshift=50] {Domain recursion};
    \draw[-{Latex[length=2mm]}] (b) -- (c);
    \draw[-{Latex[length=2mm]}] (b) -- (d);
    \draw[-{Latex[length=2mm]}] (c) to [bend left=45] node [midway,xshift=-30] () {$n \mapsto n-1$} (a);
  \end{tikzpicture}
  \caption{A conceptual illustration of the main idea}
  \label{fig:idea}
\end{figure}

In this work, we show how new tractable solutions can be found by dispensing with these restrictions. With additional compilation rules and an algorithm for checking whether a `recursive call' is possible, ForcLift \citep{DBLP:conf/ijcai/BroeckTMDR11} can construct recursive functions that efficiently solve counting problems that used to be beyond its reach. The main conceptual difference from the original algorithm is that the input formula is now compiled to a labelled directed graph rather than a circuit (i.e., cycles are allowed). This idea is illustrated in \cref{fig:idea}. Suppose the original formula $\phi$ depended on a domain of size $n \in \mathbb{N}$. Domain recursion transforms $\phi$ into a different formula $\psi$ that depends on a domain of size $n-1$. After some number of subsequent transformations, the algorithm identifies that a solution to $\psi$ can be constructed in part by finding a solution to a version of $\phi$ where the domain of size $n$ is replaced by a domain of size $n-1$. Recognising $\phi$ from before, we can add a cycle-forming edge to the graph, which can be interpreted as function $f$ relying on $f(n-1)$ to compute $f(n)$.

%% \begin{itemize}
%% \item one can then extract the (potentially recursive) definitions of functions from the graph
%% \item simplify the algebraic expressions, e.g.:
%%   \begin{itemize}
%%   \item adding and subtracting the same thing
%%   \item $\sum_{i=0}^n[i < 2]f(i) = f(0) + f(1)$
%%   \end{itemize}
%% \item evaluate the functions
%% \item definition of an FCG
%% \item maybe example of an FCG for injections
%% \item new compilation rules
%%   \begin{itemize}
%%   \item (generalised) domain recursion (via example)
%%   \item constraint removal (via example)
%%   \item recursion checking algorithm (sketch it)
%%   \end{itemize}
%% \item combining BFS and greedy search
%% \item smoothing needs to be adapted so as to not get stuck in an infinite loop
%% \item dynamic programming may be necessary to compute in polynomial time
%% \end{itemize}

% Highlights of the results obtained

In our experiments, we consider variations of the function-counting problem. These functions vary in:
\begin{itemize}
\item whether they are full or partial,
\item whether they are injective/surjective/bijective or not,
\item and whether the domain and the codomain are the same.
\end{itemize}
Many versions of this problem were previously unsolvable by any available (W)FOMC algorithm, whereas we can find recursive solutions (that can be evaluated in polynomial time) to all except one of these problems.

%% \begin{itemize}
%% \item $\Theta(mn)$ for $[m] \to [n]$ injections (optimal: $\Theta(\log m)$)
%% \item $\Theta(m)$ for $[m] \to [n]$ bijections (optimal: $\Theta(\log m)$)
%% \item TODO: add/explain the formulas as well
%% \end{itemize}

% Possible future enhancements and further work in progress

Further work is necessary to fully automate this new way of computing the (W)FOMC of a formula. The new version of ForcLift produces a graph which then needs to be transformed to definitions of (potentially recursive) functions. In some cases, it is necessary to simplify the algebraic expressions in these definitions (e.g., reducing $x-x$ to zero for some expression $x$). Most importantly, the algorithm only gives us the recursive calls but not the base cases. What makes the problem of finding these base cases non-trivial is that the number of base cases is not constant for functions of arity greater than one (i.e., formulas that mention more than one domain). Nonetheless, these remaining challenges are minuscule compared to the broader goal of expanding the capabilities of (W)FOMC to new classes of instances.

%% \begin{itemize}
%% \item open questions:
%%   \begin{itemize}
%%     \item what kind of sequences are computable in this way?
%%     \item would using a different logic extend the capabilities of FOMC even further?
%%   \end{itemize}
%% \end{itemize}

\bibliography{extended_abstract}

\end{document}

### 2022-04-29 aiai_talk/talk.tex
Add a short summary

@@
   \item Let \structure{$P \subseteq M \times N$} be a relation (i.e., \alert{predicate}) over sets \structure{$M$} and \structure{$N$}
-  \item We can describe all of the constraints in first-order logic
+  \item We can describe all of the constraints in first-order logic:
     \begin{itemize}
@@
   \]
-  Later, both \structure{$G$} and \structure{$L$} are incorporated into a larger \alert{search state}.
+  %% Later, both \structure{$G$} and \structure{$L$} are incorporated into a larger \alert{search state}.
 \end{frame}
@@
         %% \end{tikzpicture}
-        Here, domain recursion is applied to domain \structure{$M$}. It could similarly be applied to \structure{$N$} as well.
+        %% Here, domain recursion is applied to domain \structure{$M$}. It could similarly be applied to \structure{$N$} as well.
       \end{example}

### 2022-05-16 abstract/extended_abstract.tex
Final version of the extended abstract

@@
-\documentclass{article}
+\documentclass[runningheads]{llncs}
+\usepackage[T1]{fontenc}
+
 \usepackage[capitalise]{cleveref}
-\usepackage[UKenglish]{babel}
-\usepackage[UKenglish]{isodate}
-\usepackage[utf8]{inputenc}
 \usepackage{microtype}
@@
 \usepackage{amsfonts}
-\usepackage[affil-it]{authblk}
 
@@
 
-\usepackage{natbib}
-\bibliographystyle{abbrvnat}
+\begin{document}
 
 \title{Recursive Solutions to First-Order Model Counting}
-\author{Paulius Dilkas}
-\author{Vaishak Belle}
-\affil{University of Edinburgh, Edinburgh, UK}
+\author{Paulius Dilkas \and Vaishak Belle}
+\authorrunning{P. Dilkas and V. Belle}
+\institute{University of Edinburgh, Edinburgh, UK\\
+  \email{p.dilkas@sms.ed.ac.uk}, \email{vbelle@ed.ac.uk}}
 
-\begin{document}
 \maketitle
+
+\begin{abstract}
+  First-order model counting (FOMC) is a computational problem that asks to count the models of a sentence in first-order logic.
+Despite being around for more than a decade, practical FOMC algorithms are still unable to compute functions as simple as a factorial.
+We argue that the capabilities of FOMC algorithms are severely limited by their inability to express arbitrary recursive computations.
+To enable arbitrary recursion, we relax the restrictions that typically accompany domain recursion and generalise circuits used to express a solution to an FOMC problem to graphs that may contain cycles.
+To this end, we enhance the most well-established (weighted) FOMC algorithm ForcLift with new compilation rules and an algorithm to check whether a recursive call is feasible.
+These improvements allow us to find efficient solutions to counting fundamental structures such as injections and bijections.
+\end{abstract}
 
@@
 
-\emph{First-order model counting} (FOMC) is the problem of computing the number of models of a sentence in first-order logic given the size(s) of its domain(s) \citep{DBLP:conf/ijcai/BroeckTMDR11}.
-The main application of FOMC (or, rather, its \emph{weighted} variant WFOMC) is in probabilistic inference, particularly for statistical relational models such as Markov logic networks that define probabilities over sets of objects and relations thereof \citep{DBLP:conf/ijcai/BroeckTMDR11,DBLP:journals/cacm/GogateD16}.
+\emph{First-order model counting} (FOMC) is the problem of computing the number of models of a sentence in first-order logic given the size(s) of its domain(s) \cite{DBLP:conf/ijcai/BroeckTMDR11}.
+The main application of FOMC (or, rather, its \emph{weighted} variant WFOMC) is in probabilistic inference, particularly for statistical relational models such as Markov logic networks that define probabilities over sets of objects and relations thereof \cite{DBLP:journals/cacm/GogateD16,DBLP:conf/ijcai/BroeckTMDR11}.
 
 Over slightly more than a decade, research on (W)FOMC advanced on both theoretical and empirical fronts.
-Several WFOMC algorithms such as ForcLift \citep{DBLP:conf/ijcai/BroeckTMDR11}, probabilistic theorem proving \citep{DBLP:journals/cacm/GogateD16}, and L2C \citep{DBLP:conf/kr/KazemiP16} were developed.
-More and more classes of formulas were shown to be \emph{liftable}, i.e., solvable in polynomial time with respect to the size(s) of the domain(s) \citep{DBLP:conf/kr/BremenK21,DBLP:conf/nips/KazemiKBP16,DBLP:conf/lics/KuusistoL18,DBLP:journals/jair/Kuzelka21}.
-Much of the researchers' attention was devoted to developing efficient solutions to formulas with up to two variables \citep{DBLP:conf/uai/BremenK21,DBLP:journals/corr/abs-2110-05992}.
+Several WFOMC algorithms such as ForcLift \cite{DBLP:conf/ijcai/BroeckTMDR11}, probabilistic theorem proving \cite{DBLP:journals/cacm/GogateD16}, and L2C \cite{DBLP:conf/kr/KazemiP16} were developed.
+More and more classes of formulas were shown to be \emph{liftable}, i.e., solvable in polynomial time with respect to the size(s) of the domain(s) \cite{DBLP:conf/nips/KazemiKBP16,DBLP:conf/lics/KuusistoL18,DBLP:journals/jair/Kuzelka21,DBLP:conf/kr/BremenK21}.
+Much of the researchers' attention was devoted to developing efficient solutions to formulas with up to two variables \cite{DBLP:journals/corr/abs-2110-05992,DBLP:conf/uai/BremenK21}.
 
@@
 
-However, none of the publicly available (W)FOMC algorithms can efficiently compute functions as simple as a factorial.\footnote{The problem of computing the factorial can be described using two variables and counting quantifiers, so it belongs to a fragment of first-order logic which is known to be liftable \citep{DBLP:journals/jair/Kuzelka21}.} We claim that this shortcoming is due to the inability of these algorithms to construct recursive solutions.
+However, none of the publicly available (W)FOMC algorithms can efficiently compute functions as simple as a factorial.\footnote{The problem of computing the factorial can be described using two variables and counting quantifiers, so it belongs to a fragment of first-order logic which is known to be liftable \cite{DBLP:journals/jair/Kuzelka21}.} We claim that this shortcoming is due to the inability of these algorithms to construct recursive solutions.
 
@@
 The topic of recursion in the context of WFOMC has been studied before but in very limited ways.
-\Citet{DBLP:conf/ilp/BarvinekB0ZK21} use WFOMC to generate numerical data which is then used to conjecture recurrence relations that explain that data.
-\Citet{DBLP:conf/nips/Broeck11} introduced the idea of \emph{domain recursion}.
+Barv{\'{\i}}nek et al.~\cite{DBLP:conf/ilp/BarvinekB0ZK21} use WFOMC to generate numerical data which is then used to conjecture recurrence relations that explain that data.
+Van den Broeck~\cite{DBLP:conf/nips/Broeck11} introduced the idea of \emph{domain recursion}.
 Intuitively, domain recursion partitions a domain of size $n$ into a single explicitly named constant and the remaining domain of size $n-1$.
@@
 In this work, we show how new tractable solutions can be found by dispensing with these restrictions.
-With additional compilation rules and an algorithm for checking whether a `recursive call' is possible, ForcLift \citep{DBLP:conf/ijcai/BroeckTMDR11} can construct recursive functions that efficiently solve counting problems that used to be beyond its reach.
+With additional compilation rules and an algorithm for checking whether a `recursive call' is possible, ForcLift \cite{DBLP:conf/ijcai/BroeckTMDR11} can construct recursive functions that efficiently solve counting problems that used to be beyond its reach.
 The main conceptual difference from the original algorithm is that the input formula is now compiled to a labelled directed graph rather than a circuit (i.e., cycles are allowed).
@@
 
+\bibliographystyle{splncs04}
 \bibliography{extended_abstract}

### 2022-06-09 doc/notes/notes.tex
Reorganise the repo

--- 2022-03-12 notes/notes.tex
@@
 
+\paragraph{Abstract.} First-order model counting (FOMC) is a #P-complete computational problem that asks to count the models of a sentence in first-order logic.
+Despite being around for more than a decade, practical FOMC algorithms are still unable to compute functions as simple as a factorial.
+We argue that the capabilities of FOMC algorithms are severely limited by their inability to express arbitrary recursive computations.
+To enable arbitrary recursion, we relax the restrictions that typically accompany domain recursion and generalise circuits used to express a solution to an FOMC problem to graphs that may contain cycles.
+To this end, we enhance the most well-established (weighted) FOMC algorithm ForcLift with new compilation rules and an algorithm to check whether a recursive call is feasible.
+These improvements allow us to find efficient solutions to counting fundamental structures such as injections and bijections.
+
 \begin{figure}[t]
@@
 
+\section{First-Order Logic}
+
+In this section, we describe a variation of function-free first-order logic with equality. For a more complete exposition of first-order logic, see the book by \cite{DBLP:books/daglib/0023546}.
+
+In first-order logic, an \emph{atom} (i.e., an atomic formula) is either $t_1 = t_2$ or $P(t_1, \dots, t_n)$ for some predicate $P$ and terms $(t_i)_{i=1}^n$.
+Here, $n \in \mathbb{N}_0$ is the \emph{arity} of $P$.
+A \emph{term} is either a constant or a variable (we also call terms \emph{arguments}).
+An atom is \emph{ground} if all of its terms are constants.
+
+A \emph{formula} is a well-formed expression that connects atoms using the previously described logical operators as well as universal ($\forall x \in D.
+\phi$) and existential ($\exists x \in D.
+\phi$) quantifiers.
+Here, $x$ is a variable, $D$ is a domain, and $\phi$ is a formula.
+A variable occurrence is \emph{bound} if it is within the scope of a quantifier for that variable, otherwise it is \emph{free}.
+A formula is a \emph{sentence} if all of its variable occurrences are bound.\footnote{In the rest of this chapter, all formulas in first-order logic are assumed to be sentences.}
+
+\subsection{How to Interpret a Sentence}
+
+Let $\phi$ be a sentence.
+Since each variable in $\phi$ is introduced by a quantifier, each variable is linked to a unique domain.
+As is done implicitly in previous work \citep{DBLP:phd/basesearch/VandenBroeck13}, we make the following assumption.
+
+\begin{assumption}
+  Each constant can be mapped to a domain, and each $n$-ary predicate can be mapped to a sequence of $n$ domains such that:
+  \begin{enumerate}
+  \item ...
+  \item ...
+  \end{enumerate}
+\end{assumption}
+
+First, we assume that each $n$-ary predicate can be associated with a sequence of $n$ domains, one for each of its terms.
+Second, we assume that each constant can be similarly linked to a unique domain.
+Third, we assume that equality is only checked between terms that have the same domain.
+
+TODO: describe this more formally. Maybe just two rules: whenever two terms are compared, they have the same domain, the domain of a term is always the same as the $k$-th domain of the predicate.
+
+\begin{itemize}
+\item Interpretation
+  \begin{itemize}
+  \item domains as sets
+  \item constants as specific elements of domains (different constant implies different element. If the domain is not big enough, then the formula is unsat.)
+  \item variables (indicated during quantification)
+  \item predicates are interpreted as relations
+  \end{itemize}
+\item models are defined very differently: all combinations of relations that satisfy the sentence.
+\item (multiple) (finite) domains (of discourse). This makes, e.g., satisfiability decidable and a FO formula can always be expanded to a propositional one.
+\end{itemize}
+
+more on first-order logic: \citep{DBLP:books/daglib/0023546}. The MLN paper also has a description
+
 \section{Preliminaries}
@@
 \end{itemize}
+
+TODO: reorder Section 6 to introduce DR before CR before Ref.
 
@@
   A (compilation) \emph{rule} is a function that takes a formula and returns a set of $(G, L)$ pairs, where $G$ is a (potentially \texttt{null}) FCG, and $L$ is a list of formulas.
-TODO: add an example showing that it's usually an FCG with one vertex and a bunch of $\star$'s marking a fixed number of outgoing edges.
+
+  TODO: Take the example from the AIAI talk.
 \end{definition}

### 2022-06-09 src/encoding.cc

@@ -1,97 +1,0 @@
-#include "encoding.h"
-
-#include <assert.h>
-
-#include <map>
-#include <sstream>
-
-#include <boost/log/trivial.hpp>
-
-void Encoding::Set(const VariablePositions& positions) {
-  representation_.clear();
-  std::map<char, int> variable_encodings;
-  int next_int = 1;
-  for (char variable : positions.string_representation()) {
-    if (positions.OccursOnlyOnce(std::string(1, variable))) {
-      representation_.push_back(0);
-      continue;
-    }
-    auto it = variable_encodings.find(variable);
-    if (it == variable_encodings.end()) {
-      variable_encodings[variable] = next_int;
-      representation_.push_back(next_int++);
-    } else {
-      representation_.push_back(it->second);
-    }
-  }
-}
-
-Match Encoding::IsSubsetOf(Encoding other) const {
-  BOOST_LOG_TRIVIAL(debug) << "Encoding::IsSubsetOf: this = " << AsString()
-                           << ", other = " << other.AsString();
-  assert(representation_.size() == other.representation_.size());
-
-  std::map<int, int> translation;
-  Match match = {Match::Quality::kEqual, 0};
-  int max_var_this = 0, max_var_other = 0;
-  for (std::vector<int>::size_type i = 0; i < representation_.size(); ++i) {
-    if (representation_[i] > max_var_this) max_var_this = representation_[i];
-    if (other.representation_[i] > max_var_other)
-      max_var_other = other.representation_[i];
-
-    if (representation_[i] == 0) {
-      if (other.representation_[i] != 0)
-        match.quality = Match::Quality::kSubset;
-      continue;
-    }
-    auto it = translation.find(representation_[i]);
-    if (it != translation.end()) {
-      if (other.representation_[i] != it->second)
-        return {Match::Quality::kNotASubset, 0};
-    } else {
-      if (other.representation_[i] == 0)
-        return {Match::Quality::kNotASubset, 0};
-      translation[representation_[i]] = other.representation_[i];
-    }
-  }
-  match.diff_in_variables = max_var_other - max_var_this;
-  return match;
-}
-
-int Encoding::CountRedundantPositions() {
-  std::set<int> seen;
-  int count = 0;
-  for (auto v : representation_) {
-    if (seen.find(v) != seen.end()) ++count;
-    seen.insert(v);
-  }
-  return count;
-}
-
-std::map<int, std::set<std::string>>
[…]

### 2022-06-09 src/hasse_diagram.cc

@@ -1,255 +1,0 @@
-#include "hasse_diagram.h"
-
-#include <assert.h>
-#include <math.h>
-
-#include <map>
-#include <vector>
-
-#include <boost/graph/copy.hpp>
-#include <boost/graph/topological_sort.hpp>
-#include <boost/log/trivial.hpp>
-
-#include "misc.h"
-#include "visitors/multiplicity_subtractor.h"
-#include "visitors/parent_finder.h"
-#include "visitors/source_visitor.h"
-
-HasseDiagram::HasseDiagram(Gfodd gfodd, int predicate_arity) :
-    predicate_(&diagram_), predicate_arity_(predicate_arity),
-    skeleton_(diagram_, predicate_), gfodd_(gfodd),
-    edge_counts_(gfodd.NumInternalEdges()) {
-  auto vertex = boost::add_vertex(diagram_);
-  diagram_[vertex].set_positions(predicate_arity);
-  tops_.insert(vertex);
-}
-
-void HasseDiagram::UpdatePathCounts(HasseDiagram::Vertex from,
-                                    HasseDiagram::Vertex to) {
-  for (auto from_edge :
-           boost::make_iterator_range(boost::out_edges(from, diagram_))) {
-    if (diagram_[from_edge].edge_of_gfodd == kPredecessor) {
-      HasseDiagram::Vertex predecessor = boost::target(from_edge, diagram_);
-      bool skip = false;
-      auto edges = boost::edge_range(to, predecessor, diagram_);
-      for (auto to_edge : boost::make_iterator_range(edges)) {
-        if (diagram_[to_edge].edge_of_gfodd == kPredecessor) {
-          diagram_[to_edge].multiplicity += diagram_[from_edge].multiplicity;
-          skip = true;
-          break;
-        }
-      }
-      if (!skip) {
-        auto edge = boost::add_edge(to, predecessor, diagram_).first;
-        diagram_[edge].edge_of_gfodd = kPredecessor;
-        diagram_[edge].multiplicity = diagram_[from_edge].multiplicity;
-      }
-    }
-  }
-}
-
-HasseDiagram::Vertex
-HasseDiagram::AddVertexClass(VariablePositions variable_positions,
-                             Gfodd::VertexDescriptor gfodd_vertex_id,
-                             Gfodd::VertexDescriptor null_vertex) {
-  std::set<HasseDiagram::Vertex> excluded;
[…]

### 2022-06-09 src/variable_positions.cc

@@ -1,59 +1,0 @@
-#include "variable_positions.h"
-
-#include <boost/log/trivial.hpp>
-
-VariablePositions::VariablePositions(std::string variables) :
-    string_representation_(variables) {
-  for (std::string::size_type i = 0; i < variables.length(); ++i)
-    map_[std::string(1, variables[i])].insert(i);
-}
-
-// TODO: should probably test this
-VariablePositions::VariablePositions(const VariablePositions &other) :
-    string_representation_(other.string_representation_) {
-  for (auto [variable, positions] : other.map_) map_[variable] = positions;
-}
-
-// TODO: test (and make sure that this is the right thing to do)
-void VariablePositions::Insert(VariablePositions other) {
-  for (auto [variable, positions] : other.map_) {
-    auto it = map_.find(variable);
-    if (it == map_.end()) {
-      map_[variable] = positions;
-    } else {
-      it->second.insert(positions.begin(), positions.end());
-    }
-  }
-}
-
-// TODO: should this be a constructor that accepts an instance of
-// VariablePositions and a decoding map?
-VariablePositions
-VariablePositions::RespectTheMap(std::map<int, std::set<std::string>> decoding)
-    const {
-  // TODO: do I actually need the '0' cell?
-  BOOST_LOG_TRIVIAL(debug) << "VariablePositions::RespectTheMap: this = "
-                           << string_representation();
-  VariablePositions new_version(*this);
-
-  for (auto& [cell_name, cell] : decoding) {
-    if (cell_name != 0) {
-      BOOST_LOG_TRIVIAL(debug) << "VariablePositions::RespectTheMap: The "
-                               << "following variables are getting merged:";
-      std::set<int> positions;
-      std::string variable_name;
-      for (auto variable : cell) {
-        auto it = new_version.map_.find(variable);
-        if (it != new_version.map_.end()) {
-          BOOST_LOG_TRIVIAL(debug) << "VariablePositions::RespectTheMap: "
-                                   << variable;
-          variable_name = variable;
-          positions.insert(it->second.begin(), it->second.end());
-        }
-        new_version.map_.erase(it);
-      }
-      new_version.map_[variable_name] = positions;
-    }
-  }
-  return new_version;
-}

### 2022-06-09 src/vertex.cc

@@ -1,16 +1,0 @@
-#include "vertex.h"
-
-int Vertex::new_variables() {
-  assert(!sink_);
-  return new_variables_;
-}
-
-VariablePositions Vertex::positions() {
-  assert(!sink_);
-  return positions_;
-}
-
-double Vertex::weight() {
-  assert(sink_);
-  return weight_;
-}

### 2022-06-09 src/vertex_class.cc

@@ -1,14 +1,0 @@
-#include "vertex_class.h"
-
-#include "math.h"
-
-int VertexClass::FullSize(int domain_size, int predicate_arity) {
-  return std::pow(static_cast<double>(domain_size),
-                  predicate_arity - positions_.CountRedundantPositions());
-}
-
-Match VertexClass::IsSubsetOf(VariablePositions other) const {
-  Encoding encoding;
-  encoding.Set(other);
-  return IsSubsetOf(encoding);
-}

### 2022-06-09 src/visitors/multiplicity_subtractor.cc

@@ -1,23 +1,0 @@
-#include "visitors/multiplicity_subtractor.h"
-
-#include "hasse_diagram.h"
-
-namespace visitors {
-
-template <typename Vertex, typename Graph>
-void MultiplicitySubtractor<Vertex, Graph>::
-finish_vertex(Vertex vertex, const Graph& graph) const {
-  to_subtract_[vertex] = 0;
-  if (boost::out_degree(vertex, graph) == 0) return;
-  for (auto out_edge :
-           boost::make_iterator_range(boost::out_edges(vertex, graph))) {
-    auto target = boost::target(out_edge, graph);
-    to_subtract_[vertex] += to_subtract_[target] +
-                            changes_[target].multiplicity;
-  }
-}
-
-template class MultiplicitySubtractor<HasseDiagram::Vertex,
-                                      HasseDiagram::FilteredGraph>;
-
-}  // namespace visitors

### 2022-06-09 src/visitors/multiplicity_subtractor.h

@@ -1,27 +1,0 @@
-#ifndef MULTIPLICITY_SUBTRACTOR_H
-#define MULTIPLICITY_SUBTRACTOR_H
-
-#include <map>
-
-#include <boost/graph/depth_first_search.hpp>
-
-#include "misc.h"
-
-namespace visitors {
-
-template <typename Vertex, typename Graph>
-class MultiplicitySubtractor : public boost::default_dfs_visitor {
- public:
-  MultiplicitySubtractor(std::map<Vertex, Change>& changes,
-                         std::map<Vertex, int>& to_subtract) :
-      changes_(changes), to_subtract_(to_subtract) {}
-  void finish_vertex(Vertex vertex, const Graph& graph) const;
-
- private:
-  std::map<Vertex, Change>& changes_;
-  std::map<Vertex, int>& to_subtract_;
-};
-
-}  // namespace visitors
-
-#endif

### 2022-06-09 src/visitors/path_enumerator.cc

@@ -1,24 +1,0 @@
-#include "visitors/path_enumerator.h"
-
-#include "gfodd.h"
-
-namespace visitors {
-
-template <typename Vertex, typename Edge, typename Graph>
-void PathEnumerator<Vertex, Edge, Graph>::
-finish_vertex(Vertex vertex, const Graph& graph) const {
-  paths_[vertex] = {};
-  if (boost::out_degree(vertex, graph) == 0) return;
-  for (auto out_edge :
-           boost::make_iterator_range(boost::out_edges(vertex, graph))) {
-    for (auto path : paths_[boost::target(out_edge, graph)]) {
-      path.push_back(out_edge);
-      paths_[vertex].push_back(path);
-    }
-  }
-}
-
-template class PathEnumerator<Gfodd::VertexDescriptor, Gfodd::EdgeDescriptor,
-                              Gfodd::Graph>;
-
-}  // namespace visitors

### 2022-06-09 src/visitors/source_visitor.cc

@@ -1,59 +1,0 @@
-#include "source_visitor.h"
-
-#include <boost/log/trivial.hpp>
-
-#include "encoding.h"
-#include "hasse_diagram.h"
-#include "visitors/encoding_finder.h"
-#include "visitors/target_visitor.h"
-
-namespace visitors {
-
-template <typename Vertex, typename Graph>
-void SourceVisitor<Vertex, Graph>::discover_vertex(Vertex source,
-                                                   const Graph& graph) const {
-  // Identify matching variables from source_variables and source_vertex
-  auto decoding = graph[source].
-                  MatchAString(source_variables_.string_representation());
-
-  // Transform target_variables to match these constraints
-  auto new_variables = target_variables_.RespectTheMap(decoding);
-
-  // Encode them
-  Encoding encoding;
-  encoding.Set(new_variables);
-  BOOST_LOG_TRIVIAL(debug) << "SourceVisitor: encoding = "
-                           << encoding.AsString();
-
-  // Find the descendant of parent_of_target_ that matches the encoding, i.e.,
-  // find the target
-  Match::Quality last_match;
-  Vertex target = boost::graph_traits<Graph>::null_vertex();
-  visitors::EncodingFinder<Vertex, Graph> encoding_finder(encoding, target,
-                                                          last_match);
-  std::vector<boost::default_color_type> colors(boost::num_vertices(graph));
-
-  const auto terminator = [last_match](Vertex, const Graph&) {
-    return last_match == Match::Quality::kNotASubset;
-  };
-
-  try {
-    boost::depth_first_visit(graph, parent_of_target_,
-                             encoding_finder, colors.data(),
-                             terminator);
-  } catch (EndSearchException& exception) {}
-  assert(target != boost::graph_traits<Graph>::null_vertex());
-  top_target_[source] = target;
-  changes_[source] = {};
-
-  // Run the second half the edge construction algorithm
-  visitors::TargetVisitor<Vertex, Graph>
-      visitor(edge_of_gfodd_, total_multiplicity_, changes_[source]);
-  boost::depth_first_search(graph,
-                            boost::visitor(visitor).root_vertex(target));
-}
-
-template class SourceVisitor<HasseDiagram::Vertex,
-                             HasseDiagram::FilteredGraph>;
-
-}  // namespace visitors

### 2022-06-09 test/variable_positions_test.cc

@@ -1,21 +1,0 @@
-#define BOOST_TEST_MODULE VariablePositionsTest
-
-#include "variable_positions.h"
-
-#include <boost/test/unit_test.hpp>
-
-BOOST_AUTO_TEST_CASE(test_OccursOnlyOnce) {
-  VariablePositions positions("xyx");
-  BOOST_CHECK(!positions.OccursOnlyOnce("x"));
-  BOOST_CHECK(positions.OccursOnlyOnce("y"));
-}
-
-BOOST_AUTO_TEST_CASE(test_RespectTheMap) {
-  VariablePositions positions("wxyz");
-  VariablePositions updated = positions.RespectTheMap({{0, {"a", "y"}},
-                                                       {1, {"x", "z"}}});
-  BOOST_CHECK(updated.OccursOnlyOnce("w"));
-  BOOST_CHECK(updated.OccursOnlyOnce("y"));
-  BOOST_CHECK(!updated.OccursOnlyOnce("z"));
-  // and x is no longer there as it's replaced by z
-}

### 2022-07-25 doc/paper/paper.tex
First draft of the AAAI submission

%File: anonymous-submission-latex-2023.tex
\documentclass[letterpaper]{article} % DO NOT CHANGE THIS
\usepackage[submission]{aaai23}  % DO NOT CHANGE THIS
\usepackage{times}  % DO NOT CHANGE THIS
\usepackage{helvet}  % DO NOT CHANGE THIS
\usepackage{courier}  % DO NOT CHANGE THIS
\usepackage[hyphens]{url}  % DO NOT CHANGE THIS
\usepackage{graphicx} % DO NOT CHANGE THIS
\urlstyle{rm} % DO NOT CHANGE THIS
\def\UrlFont{\rm}  % DO NOT CHANGE THIS
\usepackage{natbib}  % DO NOT CHANGE THIS AND DO NOT ADD ANY OPTIONS TO IT
\usepackage{caption} % DO NOT CHANGE THIS AND DO NOT ADD ANY OPTIONS TO IT
\frenchspacing  % DO NOT CHANGE THIS
\setlength{\pdfpagewidth}{8.5in} % DO NOT CHANGE THIS
\setlength{\pdfpageheight}{11in} % DO NOT CHANGE THIS

\usepackage{mathtools}
\usepackage{amsthm}
\usepackage{mathrsfs}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{pifont}
\usepackage[linesnumbered,ruled,vlined]{algorithm2e}
\usepackage{tikz}
\usepackage[capitalize]{cleveref}
\usepackage{booktabs}
\usepackage{multirow}
\usepackage{colortbl}
\usepackage{subcaption}
\usepackage[inline,shortlabels]{enumitem}
\usepackage{complexity}

% These are recommended to typeset algorithms but not required. See the subsubsection on algorithms. Remove them if you don't have algorithms in your paper.
% \usepackage{algorithm}
% \usepackage{algorithmic}

% These are recommended to typeset listings but not required. See the subsubsection on listing. Remove this block if you don't have listings in your paper.
% \usepackage{newfloat}
% \usepackage{listings}
% \DeclareCaptionStyle{ruled}{labelfont=normalfont,labelsep=colon,strut=off} % DO NOT CHANGE THIS
% \lstset{%
% 	basicstyle={\footnotesize\ttfamily},% footnotesize acceptable for monospace
% 	numbers=left,numberstyle=\footnotesize,xleftmargin=2em,% show line numbers, remove this entire line if you don't want the numbers.
% 	aboveskip=0pt,belowskip=0pt,%
% 	showstringspaces=false,tabsize=2,breaklines=true}
% \floatstyle{ruled}
% \newfloat{listing}{tb}{lst}{}
% \floatname{listing}{Listing}

% Keep the \pdfinfo as shown here. There's no need
% for you to add the /Title and /Author tags.
\pdfinfo{
/TemplateVersion (2023.1)
}

% DISALLOWED PACKAGES
% \usepackage{authblk} -- This package is specifically forbidden
% \usepackage{balance} -- This package is specifically forbidden
% \usepackage{color (if used in text)
% \usepackage{CJK} -- This package is specifically forbidden
% \usepackage{float} -- This package is specifically forbidden
% \usepackage{flushend} -- This package is specifically forbidden
% \usepackage{fontenc} -- This package is specifically forbidden
% \usepackage{fullpage} -- This package is specifically forbidden
% \usepackage{geometry} -- This package is specifically forbidden
% \usepackage{grffile} -- This package is specifically forbidden
% \usepackage{hyperref} -- This package is specifically forbidden
% \usepackage{navigator} -- This package is specifically forbidden
% (or any other package that embeds links such as navigator or hyperref)
% \indentfirst} -- This package is specifically forbidden
% \layout} -- This package is specifically forbidden
% \multicol} -- This package is specifically forbidden
% \nameref} -- This package is specifically forbidden
% \usepackage{savetrees} -- This package is specifically forbidden
% \usepackage{setspace} -- This package is specifically forbidden
% \usepackage{stfloats} -- This package is specifically forbidden
% \usepackage{tabu} -- This package is specifically forbidden
% \usepackage{titlesec} -- This package is specifically forbidden
% \usepackage{tocbibind} -- This package is specifically forbidden
% \usepackage{ulem} -- This package is specifically forbidden
% \usepackage{wrapfig} -- This package is specifically forbidden
% DISALLOWED COMMANDS
% \nocopyright -- Your paper will not be published if you use this command
% \addtolength -- This command may not be used
% \balance -- This command may not be used
% \baselinestretch -- Your paper will not be published if you use this command
% \clearpage -- No page breaks of any kind may be used for the final version of your paper
% \columnsep -- This command may not be used
% \newpage -- No page breaks of any kind may be used for the final version of your paper
% \pagebreak -- No page breaks of any kind may be used for the final version of your paperr
% \pagestyle -- This command may not be used
% \tiny -- This is not an acceptable font size.
% \vspace{- -- No negative value may be used in proximity of a caption, figure, table, section, subsection, subsubsection, or reference
% \vskip{- -- No negative value may be used to alter spacing above or below a caption, figure, table, section, subsection, subsubsection, or reference

\setcounter{secnumdepth}{2} %May be changed to 1 or 2 if section numbers are desired.

% Title

% Your title must be in mixed case, not sentence case.
% That means all verbs (including short verbs like be, is, using,and go),
% nouns, adverbs, adjectives should be capitalized, including both words in hyphenated terms, while
% articles, conjunctions, and prepositions are lower case unless they
% directly follow a colon or long dash
\title{Recursive Solutions to First-Order Model Counting}
\author{Anonymous Submission}
\affiliations{}

\captionsetup[subfigure]{width=\linewidth}
\usetikzlibrary{fit,positioning,trees,cd}
\usetikzlibrary{shapes}
\usetikzlibrary{arrows}
\usetikzlibrary{arrows.meta}
\newcommand{\crefrangeconjunction}{--}
\crefname{algocf}{algorithm}{Algorithms}
\Crefname{algocf}{Algorithm}{Algorithms}
\newcommand\pfun{\mathrel{\ooalign{\hfil$\mapstochar\mkern5mu$\hfil\cr$\to$\cr}}}
\newcommand\mdoubleplus{\mathbin{+\mkern-10mu+}}
\newcommand*{\twoheadrightarrowtail}{\mathrel{\rightarrowtail\kern-1.9ex\twoheadrightarrow}}
\newcommand{\cmark}{\ding{51}}%
\newcommand{\xmark}{\ding{55}}%
\newcommand{\FOtwo}{$\mathsf{FO}^{2}$}
\newcommand{\FOthree}{$\mathsf{FO}^{3}$}
\newcommand{\SFO}{$\mathsf{S}^{2}\mathsf{FO}^{2}$}
\newcommand{\SRU}{$\mathsf{S}^{2}\mathsf{RU}$}
\newcommand{\Uone}{$\mathsf{U}_{1}$}
\newcommand{\Ctwo}{$\mathsf{C}^{2}$}
\DeclareMathOperator{\CR}{\textsc{CR}}
\DeclareMathOperator{\GDR}{\textsc{GDR}}
\DeclareMathOperator{\IE}{\textsc{IE}}
\DeclareMathOperator{\Reff}{\textsc{Ref}}
\DeclareMathOperator{\wwp}{w}
\DeclareMathOperator{\wwn}{\overline{w}}
\DeclareMathOperator{\dom}{dom}
\DeclareMathOperator{\id}{id}
\DeclareMathOperator{\Imm}{Im}
\DeclareMathOperator{\Doms}{Doms}
\DeclareMathOperator{\size}{\sigma}
\DeclareMathOperator{\Vars}{Vars}
\DeclareMathOperator{\WMC}{WMC}
\DeclareMathOperator{\gr}{gr}
\DeclareMathOperator{\leftlsquigarrow}{\text{\reflectbox{$\rightsquigarrow$}}}
\SetKw{KwRet}{yield}
\SetKwProg{Fn}{Function}{:}{}
\SetKwFunction{applyAllRules}{applyAllRules}
\SetKwFunction{applyGreedyRules}{applyGreedyRules}
\SetKwFunction{applyGreedyRulesToFormulas}{applyGreedyRulesToFormulas}
\SetKwFunction{emptyy}{empty}
\SetKwFunction{get}{get}
\SetKwFunction{put}{put}
\SetKwFunction{constructDomainMap}{constructDomainMap}
\SetKwFunction{identifyRecursion}{identifyRecursion}
\SetKwFunction{generateMaps}{generateMaps}
\SetKwFunction{mergeFcgs}{mergeFcgs}
\SetKwFunction{updateCache}{updCache}
\newtheorem{assumption}{Assumption}
\newtheorem{conjecture}{Conjecture}
\newtheorem{constraint}{Constraint}
\newtheorem{fact}{Fact}
\newtheorem{proposition}{Proposition}
\newtheorem{theorem}{Theorem}
\newtheorem{lemma}{Lemma}
\theoremstyle{definition}
\newtheorem{definition}{Definition}
\newtheorem{example}{Example}
\newtheorem{experiment}{Experiment}
\theoremstyle{remark}
\newtheorem*{remark}{Remark}
\makeatletter
\newcommand{\nosemic}{\renewcommand{\@endalgocfline}{\relax}}% Drop semi-colon ;
\newcommand{\dosemic}{\renewcommand{\@endalgocfline}{\algocf@endline}}% Reinstate semi-colon ;
\newcommand{\pushline}{\Indp}% Indent
\newcommand{\popline}{\Indm\dosemic}% Undent
\makeatother
\Crefname{algocf}{Algorithm}{Algorithms}
\Crefname{constraint}{Constraint}{Constraints}
\Crefname{experiment}{Experiment}{Experiments}
\Crefname{clause}{Clause}{Clauses}
\Crefname{diagram}{Diagram}{Diagrams}
\crefname{line}{line}{lines}

\begin{document}

\maketitle

\begin{abstract}
  First-order model counting (FOMC) is a computational problem that asks to
  count the models of a sentence in first-order logic. Despite being around for
  more than a decade, practical FOMC algorithms are still unable to compute
  functions as simple as a factorial. We argue that the capabilities of FOMC
  algorithms are severely limited by their inability to express arbitrary
  recursive computations. To enable arbitrary recursion, we relax the
  restrictions that typically accompany domain recursion and generalise circuits
  used to express a solution to an FOMC problem to graphs that may contain
  cycles. To this end, we enhance the most well-established (weighted) FOMC
  algorithm ForcLift with new compilation rules and an algorithm to check
  whether a recursive call is feasible. These improvements allow us to find
  efficient solutions to counting fundamental structures such as injections and
  bijections.
\end{abstract}

\section{Introduction}

% 1. What is the problem?
% 2. Why is it interesting and important?
% 1) the latest first-order variable elimination algorithm \citep{DBLP:journals/jair/TaghipourFDB13}
% 2) other approaches to lifted inference  \citep{DBLP:conf/uai/BrazO17,DBLP:conf/nips/JhaGMS10,DBLP:journals/ijar/RiguzziBZCL17}
% 3) Unlike most early algorithms for lifted inference that were adaptations of probabilistic inference algorithms such as AND/OR search \citep{DBLP:conf/aaai/GogateD10} and variable elimination \citep{DBLP:conf/ijcai/BrazAR05,DBLP:conf/aaai/MilchZKHK08}, WFOMC is an approach grounded in logic.

\emph{First-order model counting} (FOMC) is the problem of computing the number
of models of a sentence in first-order logic (FOL) given the size(s) of its
domain(s) \citep{DBLP:conf/pods/BeameBGS15}. \emph{Symmetric weighted FOMC}
(WFOMC) extends FOMC with (pairs of) weights on predicates and asks for a
weighted sum across all models instead. WFOMC emerged as the dominant approach
to \emph{lifted (probabilistic) inference}. Lifted inference techniques exploit
symmetries in probabilistic models by reasoning about sets rather than
individuals \citep{DBLP:conf/ecai/Kersting12}. By doing so, many instances
become solvable in polynomial time \citep{DBLP:conf/nips/Broeck11}. Lifted
inference algorithms are typically used on probabilistic models such as
probabilistic programming languages
\citep{DBLP:journals/ml/RaedtK15,DBLP:journals/ijar/RiguzziBZCL17}, Markov logic
networks
\citep{DBLP:conf/ijcai/BroeckTMDR11,DBLP:journals/cacm/GogateD16,DBLP:journals/ml/RichardsonD06},
and other lifted graphical \citep{DBLP:journals/ml/KimmigMG15} and statistical
relational \citep{DBLP:series/synthesis/2016Raedt} models. Lifted inference
techniques for probabilistic databases, while developed somewhat independently,
have also been inspired by WFOMC
\citep{DBLP:journals/pvldb/GatterbauerS15,DBLP:journals/debu/GribkoffSB14}.

% 3. Why is it hard? (E.g., why do naive approaches fail?)
% complexity/liftability -> murky boundary

Traditionally in computational complexity theory, a problem is \emph{tractable}
if it can be solved in time polynomial in the size of the instance. The
equivalent notion in (W)FOMC is liftability. A (W)FOMC instance is
\emph{(domain-)liftable} if it can be solved in time polynomial in the size(s)
of the domain(s) \citep{jaeger2012liftability}. Over more than a decade, more
and more classes of instances were shown to be liftable
\citep{DBLP:conf/kr/BremenK21,DBLP:conf/nips/KazemiKBP16,DBLP:conf/lics/KuusistoL18,DBLP:journals/jair/Kuzelka21}.
First, \citet{DBLP:conf/nips/Broeck11} showed that the class of all sentences of
FOL with up to two variables (denoted \FOtwo{}) is liftable. Then
\citet{DBLP:conf/pods/BeameBGS15} proved that there exists a sentence with three
variables for which FOMC is $\#\P_{1}$-complete (i.e., \FOthree{} is not
liftable). Since these two results came out, most of the research on (W)FOMC
focused on developing faster solutions for the \FOtwo{} fragment
\citep{DBLP:conf/uai/BremenK21,DBLP:conf/aaai/MalhotraS22} and defining
new liftable fragments. These fragments include \SFO{} and \SRU{}
\citep{DBLP:conf/nips/KazemiKBP16}, \Uone{} \citep{DBLP:conf/lics/KuusistoL18},
\FOtwo{} with tree axioms \citep{DBLP:conf/kr/BremenK21}, and \Ctwo{} (i.e., the
two variable fragment with counting quantifiers)
\citep{DBLP:journals/jair/Kuzelka21,DBLP:conf/aaai/MalhotraS22}. On the
empirical front, there are several open-source implementations of exact WFOMC
algorithms: \textsc{ForcLift} \citep{DBLP:conf/ijcai/BroeckTMDR11},
probabilistic theorem proving \citep{DBLP:journals/cacm/GogateD16}, and
\textsc{L2C} \citep{DBLP:conf/kr/KazemiP16}. Approximate counting is supported
by \textsc{ApproxWFOMC} \citep{DBLP:conf/ijcai/BremenK20} as well as
\textsc{ForcLift} \citep{DBLP:conf/uai/BroeckCD12} and probabilistic theorem
proving \citep{DBLP:journals/cacm/GogateD16}.

% 4. Why hasn't it been solved before? (Or, what's wrong with previous proposed
% solutions? How does mine differ?)
% simple unliftable instances -> recursion

However, none of the publicly available exact (W)FOMC algorithms can efficiently
compute functions as simple as a factorial.\footnote{The problem of computing
  the factorial can be described using two variables and counting quantifiers,
  so it is known to be liftable in theory \citep{DBLP:journals/jair/Kuzelka21}.}
We claim that this shortcoming is due to the inability of these algorithms to
construct recursive solutions. The topic of recursion in the context of WFOMC
has been studied before but in limited ways.
\Citet{DBLP:conf/ilp/BarvinekB0ZK21} use WFOMC to generate numerical data which
is then used to conjecture recurrence relations that explain that data.
\Citet{DBLP:conf/nips/Broeck11} introduced the idea of \emph{domain recursion}.
Intuitively, domain recursion partitions a domain of size $n$ into a single
explicitly named constant and the remaining domain of size $n-1$. However, many
stringent conditions are enforced to ensure that the search for a tractable
solution always terminates.

% \begin{itemize}
%   \item But their code only conjectures stuff on data. My conjectures are
%         guaranteed to always be true.
%   \item everything has to be expressible in \Ctwo{}, i.e., the two-variable
%         fragment of FOL with counting quantifiers on one domain.
%   \item They only consider P-recursive functions, which means that, e.g.,
%         $f(n) = f(n-1)f(n-2)$ would not be allowed.
% \end{itemize}

% 5. What are the key components of my approach and results? Also include any
% specific limitations.

% 5.1) An overview of how ForcLift/Crane work.

In this work, we show how to relax these restrictions in a way that results in a
stronger (W)FOMC algorithm, capable of handling more instances in a lifted
manner. The ideas presented in this paper are implemented in
\textsc{Crane}---an extension of the arguably most well-known WFOMC algorithm
\textsc{ForcLift} written in Scala. \textsc{ForcLift} works in two stages:
compilation and evaluation/propagation.\footnote{There is also an intermediate
  stage called \emph{smoothing} that takes place between compilation and
  evaluation. As our changes to smoothing are quite elementary, we do not
  discuss them to not distract the reader from the main contributions of this
  paper.} In the first part, various \emph{(compilation) rules} are applied to
the input (or some derivative) formula, gradually constructing a circuit. In the
second part, the weights of the instance (and sometimes constants) are
propagated through the circuit, computing the WMC\@.

% 5.2) The main idea: cycles that represent recursive calls.

TODO: improve the wording of the paragraph below.

The main conceptual difference between \textsc{Crane} and \textsc{ForcLift} is
that we utilise labelled directed graphs instead of circuits. The cycles in
these graphs represent recursive calls. Suppose the original formula $\phi$
depends on a domain of size $n \in \mathbb{N}$. Our generalised version of
domain recursion transforms $\phi$ into a different formula $\psi$ that depends
on a domain of size $n-1$. After some number of subsequent transformations, the
algorithm identifies that a solution to $\psi$ can be constructed in part by
finding a solution to a version of $\phi$ where the domain of size $n$ is
replaced by a domain of size $n-1$. Recognising $\phi$ from before, we can add a
cycle-forming edge to the graph, which can be interpreted as function $f$
relying on $f(n-1)$ to compute $f(n)$.

% 5.3) contributions, references to sections, shortcomings

To construct such graphs, we introduce a novel search algorithm that replaces
greedy search used by \textsc{ForcLift} and three compilation rules that work
together to construct cyclic graphs. We begin with \cref{sec:recprelims} where
we define the representation used for sentences in FOL as well as discuss
caching and some notational conventions. Then, at the beginning of
\cref{sec:methods} we formally define the graphs that replace circuits in
representing a solution to a (W)FOMC problem and discuss some related notions.
\Cref{sec:rules} introduces the new compilation rules:
\begin{itemize}
  \item a generalisation of domain recursion by \citet{DBLP:conf/nips/Broeck11},
  \item \emph{constraint removal}---a formula transformation rule that removes
        the constraints introduced by generalised domain recursion (GDR),
        introducing a new (smaller) domain instead,
  \item and a rule for creating recursive calls.
\end{itemize}
In a typical solution produced by \textsc{Crane}, these rules are executed in
exactly this order (interspersed with some other rules), with the edge that
represents a recursive call pointing back to the node introduced by GDR\@. In
\cref{sec:interpret}, we informally discuss how a graph can be interpreted as a
collection of (potentially recursive) functions. Finally, in \cref{sec:results}
we compare \textsc{ForcLift} and \textsc{Crane} on a range of function-counting
problems. We show that \textsc{Crane} performs as well as \textsc{ForcLift} on
the instances that were already solvable by \textsc{ForcLift} but is also able
to handle most instances that \textsc{ForcLift} fails on as well.

% \Cref{sec:search} then describes our new search algorithm that makes fewer
% assumptions than \textsc{ForcLift} about the right order in which compilation
% rules should be applied.

% \begin{itemize}
%   \item What we do with the compilation result is different (see below)
%   \item evaluation/interpretation: algebraic simplification, dynamic programming
%   \item limitation: function extraction and simplification need to be automated,
%         same for finding base cases
% \end{itemize}

% Leftovers
% \begin{itemize}
%   \item compilation works by always having a formula as input and
%         adding nodes to the circuit/FCG that constitute the solution the that
%         formula.
%   \item Workflow after
%   \begin{itemize}
%     \item Compile the formula to a graph
%     \item Extract the definitions of functions
%     \item Simplify
%     \item Supplement with base cases
%     \item Evaluate to get the answer
%   \end{itemize}
% \end{itemize}

\section{Preliminaries}\label{sec:recprelims}

In this section, we describe our format for FOMC instances, introduce some
notation, and discuss our caching scheme, which is used to identify
possibilities for a recursive call. Note that although the focus of this paper
is on unweighted model counting, \textsc{ForcLift}'s
\citep{DBLP:conf/ijcai/BroeckTMDR11} support for weights trivially transfers to
\textsc{Crane} as well.

Our representation of FOMC instances is heavily based on the format used
internally by \textsc{ForcLift}, some aspects of which are described by
\citet{DBLP:conf/ijcai/BroeckTMDR11}. \textsc{ForcLift} is able to translate
sentences in a variant of function-free many-sorted FOL with equality to this
internal format. An \emph{atom} is $p(t_1, \dots, t_n)$ for some predicate $p$
and terms $t_{1}, \dots, t_{n}$. Here, $n \in \mathbb{N}_0$ is the \emph{arity}
of $p$. A \emph{term} is either a constant or a variable. A \emph{literal} is
either an atom or the negation of an atom (denoted by
$\neg p(t_1, \dots, t_n)$). Let $\mathcal{D}$ be the set of all domains; note
that this set expands during compilation.

\begin{definition}[Constraint]\label{def:constraint}
  An \emph{(inequality) constraint} is a pair $(a, b)$, where $a$ is a variable,
  and $b$ is either a variable or a constant.
\end{definition}

\begin{definition}[Clause]\label{def:clause}
  A \emph{clause}\footnote{\citet{DBLP:conf/ijcai/BroeckTMDR11} refer to clauses
    as c-clauses.} is a triple $c = (L, C, \delta_c)$, where $L$ is a set of
  literals, $C$ is a set of constraints, and $\delta_c$ is the domain map of
  $c$. Let $\Vars$ be the function that maps clauses and sets of either literals
  or constraints to the set of variables contained within. In particular,
  $\Vars(c) \coloneqq \Vars(L) \cup \Vars(C)$. \emph{Domain map}
  $\delta_{c}\colon \Vars(c) \to \mathcal{D}$ is a function that maps all
  variables in $c$ to their domains such that (s.t.) if $(X, Y) \in C$ for some
  variables $X$ and $Y$, then $\delta_c(X) = \delta_c(Y)$. For convenience, we
  sometimes write $\delta_c$ for the domain map of $c$ without unpacking $c$
  into its three constituents.
\end{definition}

Similarly to variables in \cref{def:clause}, all constants are (implicitly)
mapped to domains, and each $n$-ary predicate is implicitly mapped to a sequence
of $n$ domains. For constant $x$, predicate $p$, and domains $a$ and $b$, we
write, e.g., $x \in a$ and $p \in a \times b$ to denote that $x$ is associated
with $a$, and $p$ is associated with $a$ and $b$ (in that order).

\begin{definition}[Formula]\label{def:formula}
  A \emph{formula} (called a c-theory by \citet{DBLP:conf/ijcai/BroeckTMDR11})
  is a set of clauses such that all constraints and atoms `type check' with
  respect to domains.
\end{definition}

\begin{example}\label{example:first}
  Let $\phi \coloneqq \{\, c_1, c_2 \,\}$ be a formula with clauses
  \begin{align*}
    c_1 &\coloneqq
          \begin{multlined}[t]
            (\{\, \neg p(X, Y), \neg p(X, Z) \,\}, \{\, (Y, Z) \,\}, \\
            \{\, X \mapsto a, Y \mapsto b, Z \mapsto b \,\}),
          \end{multlined}\\
    c_2 &\coloneqq
          \begin{multlined}[t]
            (\{\, \neg p(X, Y), \neg p(Z, Y) \,\}, \{\, (X, Z) \,\}, \\
            \{\, X \mapsto a, Y \mapsto b, Z \mapsto a \,\})
          \end{multlined}
  \end{align*}
  for some predicate $p$, variables $X$, $Y$, $Z$, and domains $a$ and $b$. Then
  $\Vars(\{\, (Y, Z) \,\}) = \{\, Y, Z \,\}$, and
  $\Vars(c_{1}) = \Vars(c_{2}) = \{\, X, Y, Z \,\}$. Based on the domain maps of
  $c_{1}$ and $c_{2}$, we can infer that $p \in a \times b$. All variables (in
  both clauses) that occur as the first argument to $p$ are in $a$, and likewise
  all variables that occur as the second argument to $p$ are in $b$. Therefore,
  $\phi$ `type checks' as a valid formula.
\end{example}

There are two major differences between
\cref{def:constraint,def:clause,def:formula} and the corresponding concepts
introduced by \citet{DBLP:conf/ijcai/BroeckTMDR11}. First, we decouple
variable-to-domain assignments from constraints and move them to a separate
function $\delta_{c}$ in \cref{def:clause}. Formalising these assignments as a
function unveils the (previously implicit) assumption that each variable must be
assigned to a domain. Second, while \citet{DBLP:conf/ijcai/BroeckTMDR11} allow
for equality constraints and constraints of the form $X \not\in d$ for some
variable $X$ and domain $d$, we exclude such constraints simply because they are
not needed.

One can read a formula as in \cref{def:formula} as a sentence in a FOL\@.
All variables in a
clause are implicitly universally quantified (but note that variables are never
shared among clauses), and all clauses in a formula are implicitly linked by
conjunction. Thus, formula $\phi$ from \cref{example:first} reads as
\begin{align*}
  &\begin{multlined}[t]
    (\forall X \in a\text{. }\forall Y, Z \in b\text{. }\\
    Y \ne Z \implies \neg p(X, Y) \lor \neg p(X, Z)) \land
    \end{multlined}\\
  &\begin{multlined}[t]
    (\forall X, Z \in a\text{. }\forall Y \in b\text{. }\\
    X \ne Z \implies \neg p(X, Y) \lor \neg p(Z, Y)).
    \end{multlined}
\end{align*}

Once domains are mapped to finite sets and constants to specific (and different)
elements in those sets, a formula can be viewed as a set of conditions that the
predicates (interpreted as relations) have to satisfy.\footnote{If some domain
  is not big enough to contain all of its constants, the formula is
  unsatisfiable.} Hence, FOMC is the problem of counting the number of
combinations of relations that satisfy these conditions.

\begin{example}
  Let $\phi$ be as in \cref{example:first} and let $|a| = |b| = 2$. There are
  $2^{2 \times 2} = 16$ possible relations between $a$ and $b$. Let us count how
  many of them satisfy the conditions imposed on predicate $p$. The empty
  relation does. All four relations of cardinality one do too. Finally, there
  are two relations of cardinality two that satisfy the conditions as well.
  Thus, the FOMC of $\phi$ (when $|a| = |b| = 2$) is 7. Incidentally, the FOMC
  of $\phi$ counts partial injections. We will continue to use the problem of
  counting partial injections (and the formula from \cref{example:first}
  specifically) as the main running example throughout the paper.
\end{example}

\paragraph*{Notation.}
We write $\langle\rangle$ and $\langle x \rangle$ to denote an empty list and a
list with one element $x$, respectively, and $|l|$ to denote the length of list
$l$. Let $S$ be a set of constraints or literals, $V$ a set of variables, and
$x$ either a variable or a constant. We write $S[x/V]$ to denote $S$ with all
occurrences of all variables in $V$ replaced with $x$.\footnote{Note that if
  $(X, Y)$ is a two-variable constraint, substituting a constant $c$ for $X$
  would result in $(c, Y)$, which would have to be rewritten as $(Y, c)$ to fit
  the definition of a constraint.}

\section{From Circuits to Graphs}\label{sec:methods}

% , and \cref{sec:search} outlines the hybrid search algorithm
% that replaces the greedy search used by \textsc{ForcLift}
% \citep{DBLP:conf/ijcai/BroeckTMDR11}.

% TODO: update (and other references to sections, i.e., the beginning of each
% section and the end of the introduction)
We begin this section by formally defining the graphs that \textsc{Crane} uses
as a generalisation of circuits. Then, \cref{sec:rules} describes three new
compilation rules.

\begin{figure}[t]
  \centering
  \begin{tikzpicture}[every node/.style={draw,ellipse},edge from
    parent/.style={draw,-Latex},sibling distance=3cm]
    \node (dr) {$\GDR_{a \gets a \setminus \{\, x \,\}}$}
    child {node {$\bigvee_{b^\top \subseteq b}$}
      child {node {$\CR_{a \mapsto a'}$}
        child {
          node[circle] {$\wedge$}
          child {node {$\bot$}}
          % _{(\emptyset, \{\, (X, Y) \,\}, \{\, X \mapsto b^\top, Y \mapsto b^\top \,\})}
          child {node (ref) {$\Reff_{\{\, a \mapsto a', b \mapsto b^{\bot} \,\}}$}}
        }}};
    \draw[-Latex, bend right] (ref) to (dr);
  \end{tikzpicture}
  \caption{A simplified version of an FCG constructed by \textsc{Crane} for the
    problem of counting partial injections from \cref{example:first}. Label
    $\bigvee_{b^\top \subseteq b}$ denotes set-disjunction, $\land$ denotes
    conjunction, and $\bot$ denotes a contradiction---see the work by
    \citet{DBLP:conf/ijcai/BroeckTMDR11} for the descriptions of these node
    types. Here we omit nodes whose only arithmetic effect is multiplication by
    one. Some of these nodes play an important role in the weighted version of
    the problem whereas others are remnants of the interaction between
    compilation rules and the way in which \textsc{ForcLift} handles existential
    quantifiers.}\label{fig:examplefcg}
\end{figure}

% From circuits to graphs.
A \emph{first-order deterministic decomposable negation normal form
  computational graph} (FCG) is a (weakly connected) directed graph with a
single source, node labels, and ordered outgoing edges.\footnote{Note that
  imposing an ordering on outgoing edges is just a limited version of edge
  labelling.} We denote an FCG as $G = (V, s, N^+, \tau)$, where $V$ is the set
of nodes, and $s \in V$ is the unique source. Function $N^+$ maps each node in
$V$ to a \emph{list} of its direct successors. Node labels consist of two parts:
the \emph{type} and the \emph{parameters}. To avoid clutter, we leave the
parameters implicit and let $\tau$ denote the node-labelling function that maps
each node in $V$ to its type. For each node $v \in V$, the length of list
$N^+(v)$ (i.e., the out-degree of $v$) is determined by its type $\tau(v)$. Most
of the types are as in previous work
\citep{DBLP:conf/nips/Broeck11,DBLP:conf/ijcai/BroeckTMDR11}. The type for
non-tree-like edges (denoted by $\Reff$), while used before, is extended to
contain the information necessary to support recursive calls. We also add three
new types:
\begin{itemize}
  \item a type for \emph{constraint removal} denoted by $\CR$,
  \item a type for \emph{generalised domain recursion} denoted by $\GDR$ (both
        with out-degree one),
  \item and $\star$---a placeholder type (with out-degree zero) for nodes that
        are going to be replaced.
\end{itemize}
When drawing an FCG, we order outgoing edges from left to right, write node
labels directly on the nodes, and omit irrelevant labels and/or parameters. See
\cref{fig:examplefcg} for an example FCG\@. Its source node has out-degree 1
(i.e., $|N^+(s)| = 1$), label $\GDR_{a \gets a \setminus \{\, x \,\}}$, and type
$\GDR$ (i.e., $\tau(s) = \GDR$).

%\paragraph*{Notation.}
Similarly to \citet{DBLP:conf/ijcai/BroeckTMDR11}, we write $T_p$ for an FCG
that has a node with label $T_p$ (i.e., type $T$ and parameter(s) $p$) and
$\star$'s as all of its direct successors. In particular, as an FCG, $\star$
denotes
$(\{\, s \,\}, s, \{\, s \mapsto \langle\rangle \,\}, \{\, s \mapsto \star \,\})$,
i.e., an FCG with just one node of type $\star$ and no edges. We write $T_p(v)$
for an FCG with one edge from a node labelled $T_{p}$ to some other node $v$
(and no other nodes or edges).

\begin{figure}[t]
  \centering
  \begin{subfigure}{0.49\linewidth}
    \centering
    \begin{tikzpicture}[edge from parent/.style={draw,-Latex}]
      \node[draw,circle,label={[text=blue]1}] (top) {}
      child {
        node[draw,circle,label={[text=blue,xshift=-1mm]2}] {}
        child {node[draw,ellipse] (ref) {$\Reff$}}
        child {node[draw,circle,label={[text=blue,xshift=1mm,yshift=-1mm]3}] {$\star$}}
      }
      child {node[draw,circle,label={[text=blue,xshift=1mm,yshift=-1mm]4}] {$\star$}};
      \draw[-Latex] (ref) to [bend left=45] (top);
    \end{tikzpicture}
    \caption{An example FCG}\label{fig:smallexample1}
  \end{subfigure}
  \begin{subfigure}{0.49\linewidth}
    \centering
    \begin{tikzpicture}[edge from parent/.style={draw,-Latex}]
      \node[draw,circle,label={[text=blue]1}] (top) {}
      child {
        node[draw,circle,label={[text=blue,xshift=-1mm]2}] {}
        child {node[draw,circle,label={[text=blue,xshift=2mm,yshift=-1mm]3}] {$\star$}}
      }
      child {node[draw,circle,label={[text=blue,xshift=1mm,yshift=-1mm]4}] {$\star$}};
    \end{tikzpicture}
    \caption{The underlying tree of
      \cref{fig:smallexample1}}\label{fig:smallexample2}
  \end{subfigure}
  \caption{An FCG and its underlying tree. The integers in blue denote the
    pre-order traversal of the underlying tree.}\label{fig:ordering}
\end{figure}

%\paragraph*{Connecting FCGs with formulas.}
Finally, we introduce a structure that represents a solution to a (W)FOMC
problem while it is still being built. A \emph{chip} is a pair $(G, L)$, where
$G$ is an FCG, and $L$ is a list of formulas, such that $|L|$ is equal to the
number of $\star$'s in $G$. The intuition behind this definition is that $L$
contains formulas that still need to be compiled. Once a formula is compiled, it
replaced one of the $\star$'s in $G$. We say that an FCG is \emph{complete}
(i.e., it represents a \emph{complete solution}) if it has no $\star$'s.
Similarly, a chip is complete if its FCG is complete (or, equivalently, the list
of formulas is empty). Let the \emph{underlying tree} of $G$ be the induced
subgraph of $G$ that omits all $\Reff$ nodes.\footnote{Subsequently presented
  algorithms ensure that the underlying tree is guaranteed to be a tree.} Then
we can define an implicit bijection between the formulas in $L$ and the
$\star$'s in $G$ according to the order in which elements of $L$ are listed and
the pre-order traversal of the underlying tree of $G$. For example, if $G$ is as
in \cref{fig:smallexample1} (with its underlying tree in
\cref{fig:smallexample2}), then $|L| = 2$. Moreover, the first element of $L$ is
associated with the $\star$ labelled 3, and the second with the one labelled 4.

\section{New Compilation Rules}\label{sec:rules}

A \emph{(compilation) rule} takes a formula and returns a set of chips. The
cardinality of this set is the number of different ways in which the rule can be
applied to the input formula. While \textsc{ForcLift}
\citep{DBLP:conf/ijcai/BroeckTMDR11} heuristically chooses one of them, in an
attempt to not miss a solution, \textsc{Crane} returns them all. In particular,
if a rule returns an empty set, then that rule is not applicable to the formula,
and the algorithm continues with the next rule.

\subsection{Generalised Domain Recursion}\label{sec:dr}
% 1. Note that the total number of such possibilities is not necessarily
% exponential: some combinations produce clearly unsatisfiable formulas that can
% be immediately discarded.
% 2. We can combine all of these possibilities into a single formula equivalent
% to the original one.
% 3. \begin{itemize}
%   \item the formula is shattered,
%   \item the formula has no independent subformulas,
%   \item and there exists a root binding class.
% \end{itemize}
% 4. During evaluation, $v$ is ignored, and the WMCs of $x$ and $r$ can be
% computed independently. Note that the WMC of $x$ is independent of the size of
% $D$---this further simplifies the matters.

% Main idea
The main idea behind domain recursion (both the original version by
\citet{DBLP:conf/nips/Broeck11} and the one presented here) is as follows. Let
$d \in \mathcal{D}$ be a domain. Assuming that $d \ne \emptyset$, pick some
$x \in d$. Then, for every variable $X$ associated with domain $d$ that occurs
in a literal, consider two possibilities: $X = x$ and $X \ne x$.

\begin{example}\label{example:dr}
  Let $\phi$ be a formula with a single clause
  \begin{multline*}
    (\{\, \neg p(X, Y), \neg p(X, Z) \,\}, \{\, (Y, Z) \,\}, \\
    \{\, X \mapsto a, Y \mapsto b, Z \mapsto b \,\}).
  \end{multline*}
  Then we can introduce constant $x \in a$ and rewrite $\phi$ as
  $\phi' = \{\, c_{1}, c_{2} \,\}$, where
  \begin{align*}
    c_{1} &= \begin{multlined}[t]
      (\{\, \neg p(x, Y), \neg p(x, Z) \,\}, \{\, (Y, Z) \,\}, \\
      \{\, Y \mapsto b, Z \mapsto b \,\}),
      \end{multlined}\\
    c_{2} &= \begin{multlined}[t]
      (\{\, \neg p(X, Y), \neg p(X, Z) \,\}, \{\, (X, x), (Y, Z) \,\}, \\
      \{\, X \mapsto a', Y \mapsto b, Z \mapsto b \,\}),
      \end{multlined}
  \end{align*}
  and $a' = a \setminus \{\, x \,\}$.
\end{example}

% Original domain recursion
\citet{DBLP:conf/nips/Broeck11} imposes stringent preconditions on the input
formula to ensure that the expanded version of the formula (as in
\cref{example:dr}) can be handled efficiently. The clauses in this expanded
formula are then partitioned into three parts based on whether the transformation
introduced constants or constraints or both. The aforementioned conditions
ensure that these parts can be treated independently.

\begin{algorithm}[t]
  \caption{The compilation rule for $\GDR$ nodes.}\label{alg:domainrecursion}
  \KwIn{formula $\phi$}
  \KwOut{set of chips $S$}
  $S \gets \emptyset$\;
  \ForEach{domain $d \in \mathcal{D}$ s.t.\ there is $c \in \phi$ and $v \in \Vars(L_c)$ s.t. $\delta_c(v) = d$\label{line:condition}}{
    $\phi' \gets \emptyset$\;
    $x \gets \text{a new constant in domain } d$\;
    \ForEach{clause $c = (L, C, \delta) \in \phi$\label{line:forclause}}{
      $V \gets \{\, v \in \Vars(L) \mid \delta(v) = d \,\}$\;
      \ForEach{subset $W \subseteq V$ s.t. $W^2 \cap C = \emptyset$ {\bf and} $W \cap \{\, v \in \Vars(C) \mid (v, y) \in C \text{ for some constant } y \,\} = \emptyset$\label{line:conditions}}{
        \tcc{$\delta'$ restricts $\delta$ to the new set of variables}
        $\phi' \gets \phi' \cup \{\, (L[x/W], C[x/W] \cup \{\, (v, x) \mid (v \in V \setminus W) \,\}, \delta') \,\}$\;\label{line:generation}
      }
    }
    $S \gets S \cup \{\, (\GDR_{d \gets d \setminus \{\, x \,\}}, \langle\phi'\rangle) \,\}$\;
  }
\end{algorithm}

% Description of GDR, in contrast to DR
In contrast, GDR has only one precondition: for GDR to be applicable on domain
$d \in \mathcal{D}$, there must be at least one variable with domain $d$ that is
featured in a literal (and not just in constraints). Without such variables, GDR
would have no effect on the formula. GDR is also simpler in that the expanded
formula is left as-is to be handled by other compilation rules. Typically, after
a few more rules are applied, a combination of $\CR$ and $\Reff$ nodes
introduces a loop back to the $\GDR$ node, thus completing the definition of a
recursive function. The GDR compilation rule is summarised as
\cref{alg:domainrecursion} and explained in more detail using the example below.

\begin{example}
  Let $\phi \coloneqq \{\, c_1, c_2 \,\}$ be the formula from
  \cref{example:first}. While GDR is possible on both domains, here we
  illustrate how it works on $a$. Having chosen a domain, the algorithm iterates
  over the clauses of $\phi$. Suppose \cref{line:forclause} picks $c = c_1$ as
  the first clause. Then, set $V$ is constructed to contain all variables with
  domain $d = a$ that occur in the literals of clause $c$. In this case,
  $V = \{\, X \,\}$.

  \Cref{line:conditions} iterates over all subsets $W \subseteq V$ of variables
  that can be replaced by a constant without resulting in formulas that are
  evidently unsatisfiable. We impose two restrictions on $W$. First,
  $W^2 \cap C = \emptyset$ ensures that there are no pairs of variables in $W$
  that are constrained to be distinct, since that would result in a $x \ne x$
  constraint after substitution. Similarly, we want to avoid variables in $W$
  that have inequality constraints with constants: after substitution, such
  constraints would transform into inequality constraints between two constants.
  In this case, both subsets of $V$ satisfy these conditions, and
  \cref{line:generation} generates two clauses for the output formula:
  \begin{multline*}
    (\{\, \neg p(X, Y), \neg p(X, Z) \,\}, \{\, (Y, Z), (X, x) \,\}, \\
    \{\, X \mapsto a, Y \mapsto b, Z \mapsto b \,\}),
  \end{multline*}
  from $W = \emptyset$ and
  \[
    (\{\, \neg p(x, Y), \neg p(x, Z) \,\}, \{\, (Y, Z) \,\}, \{\, Y \mapsto b, Z \mapsto b \,\})
  \]
  from $W = V$.

  When \cref{line:forclause} picks $c = c_2$, then $V = \{\, X, Z \,\}$. The
  subset $W = V$ fails to satisfy the conditions on \cref{line:conditions}
  because of the $X \ne Z$ constraint. The other three subsets of $V$ all
  generate clauses for $\phi'$. Indeed, $W = \emptyset$ generates
  \begin{multline*}
    (\{\, \neg p(X, Y), \neg p(Z, Y) \,\}, \{\, (X, Z), (X, x), (Z, x) \,\}, \\
    \{\, X \mapsto a, Y \mapsto b, Z \mapsto a \,\}),
  \end{multline*}
  $W = \{\, X \,\}$ generates
  \[
    (\{\, \neg p(x, Y), \neg p(Z, Y) \,\}, \{\, (Z, x) \,\}, \{\, Y \mapsto b, Z \mapsto a \,\}),
  \]
  and $W = \{\, Z \,\}$ generates
  \[
    (\{\, \neg p(X, Y), \neg p(x, Y) \,\}, \{\, (X, x) \,\}, \{\, X \mapsto a, Y \mapsto b \,\}).
  \]
\end{example}

\subsection{Constraint Removal}\label{sec:cr}

\begin{algorithm}[t]
  \caption{The compilation rule for $\CR$ nodes.}\label{alg:constraintremoval}
  \KwIn{formula $\phi$, set of domains $\mathcal{D}$}
  \KwOut{set of chips $S$}
  $S \gets \emptyset$\;
  \ForEach{domain $d \in \mathcal{D}$ and element $x \in d$ s.t. $x$ does not occur in any literal of any clause of $\phi$ {\bf and} for each clause $c = (L, C, \delta_c) \in \phi$ and variable $v \in \Vars(c)$, either $\delta_c(v) \ne d$ or $(v, x) \in C$\label{line:crconditions}}{
    add a new domain $d'$ to $\mathcal{D}$\;
    $\phi' \gets \emptyset$\;
    \ForEach{clause $(L, C, \delta) \in \phi$}{
      $C' \gets \{\, (a, b) \in C \mid b \ne x \,\}$\;\label{line:constraintremoval}
      \nosemic$\delta' \gets v \mapsto \begin{cases} d' & \text{if} \delta(v) = d\\ \delta(v) & \text{otherwise;} \end{cases}$\;\label{line:newdelta}
      $\phi' \gets \phi' \cup \{\, (L, C', \delta') \,\}$\;
    }
    $S \gets S \cup \{\, (\CR_{d \mapsto d'}, \langle\phi'\rangle) \,\}$\;
  }
\end{algorithm}

Recall that GDR on a domain $d$ creates constraints of the form $X_i \ne x$ for
some constant $x \in d$ and family of variables $X_i \in d$. Once certain
conditions are satisfied, \cref{alg:constraintremoval} can eliminate these
constraints and replace $d$ with a new domain $d'$, which can be interpreted as
$d \setminus \{\, x \,\}$. These conditions (on \cref{line:crconditions} of the
algorithm) are that a constraint of the form $X \ne e$ exists for all variables
$X \in d$ across all clauses, and such constraints are the only place where $e$
occurs. The algorithm then proceeds to construct the new formula by removing
constraints (on \cref{line:constraintremoval}) and constructing a new domain map
$\delta'$ that replaces $d$ with $d'$ (on \cref{line:newdelta}).

\begin{example}
  Let $\phi = \{\, c_1, c_2, c_3 \,\}$ be a formula with clauses
  \begin{align*}
    c_1 &= (\emptyset, \{\, (Y, X) \,\}, \{\, X \mapsto b^\top, Y \mapsto b^\top \,\}), \\
    c_2 &=
          \begin{multlined}[t]
            (\{\, \neg p(X, Y), \neg p(X, Z) \,\}, \{\, (X, x), (Y, Z) \,\}, \\
            \{\, X \mapsto a, Y \mapsto b^\bot, Z \mapsto b^\bot \,\}),
          \end{multlined}\\
    c_3 &=
          \begin{multlined}[t]
            (\{\, \neg p(X, Y), \neg p(Z, Y) \,\}, \{\, (X, x), (Z, X), (Z, x) \,\}, \\
            \{\, X \mapsto a, Y \mapsto b^\bot, Z \mapsto a \,\}).
          \end{multlined}
  \end{align*}
  Domain $a$ and with its element $x \in a$ satisfy the preconditions for
  constraint removal. The rule introduces a new domain $a'$ and transforms
  $\phi$ to $\phi' = (c_1', c_2', c_3')$, where
  \begin{align*}
    c_1' &= c_1, \\
    c_2' &=
           \begin{multlined}[t]
             (\{\, \neg p(X, Y), \neg p(X, Z) \,\}, \{\, (Y, Z) \,\}, \\
             \{\, X \mapsto a', Y \mapsto b^\bot, Z \mapsto b^\bot \,\}),
           \end{multlined} \\
    c_3' &=
           \begin{multlined}[t]
             (\{\, \neg p(X, Y), \neg p(Z, Y) \,\}, \{\, (Z, X) \,\}, \\
             \{\, X \mapsto a', Y \mapsto b^\bot, Z \mapsto a' \,\}).
           \end{multlined}
  \end{align*}
\end{example}

\subsection{Identifying Opportunities for Recursion}\label{sec:ref}

TODO: write a short informal summary. Add the full info as an appendix and
reference it.

\section{How to Interpret an FCG}\label{sec:interpret}

When \textsc{ForcLift} \citep{DBLP:conf/ijcai/BroeckTMDR11} compiles a WFOMC
instance into a circuit, each gate type encodes an arithmetic operation on its
inputs and parameters. These operations are then immediately performed while
traversing the circuit and using domain sizes and weights as the initial inputs.
With \textsc{Crane}, the interpretation of an FCG is a collection of functions.
Each function has (some) domain sizes as parameters and may contain recursive
calls to other functions, including itself. While there may be any number of
subsidiary functions, there is always one main function that can be called with
the sizes of the domains of the input formula as arguments. Henceforth, this
function is always called $f$, and it is defined by the source node.

The interpretation of a node is decided by its type. Here we describe the
interpretations of new (or significantly changed) types and refer the reader to
previous work \citep{DBLP:conf/ijcai/BroeckTMDR11} for information on other
types. Both $\CR$ and $\GDR$ nodes do not contribute anything to the definitions
of functions---the interpretation of such a node is simply the interpretation of
its only direct successor. Obviously, $\star$ nodes also have no interpretation,
although for a different reason: incomplete FCGs are not meant to be
interpreted. The interpretation of a $\Reff$ node is a function call. The direct
successor of the $\Reff$ node (say, $v$) then must introduce a function. The
parameters of this function are the sizes of all domains used by nodes reachable
from $v$.

\begin{example}\label{example:interpretation}
  Let us use the FCG from \cref{fig:examplefcg} as an example. The input formula
  (i.e., the formula in \cref{example:first}) has two domains: $a$ and $b$.
  Thus, the interpretation of the FCG is a function
  $f\colon \mathbb{N}_{0} \times \mathbb{N}_{0} \to \mathbb{R}_{\ge 0}$. Let
  $m \coloneqq |a|$, and $n \coloneqq |b|$. The node labelled
  $\bigvee_{b^{\top} \subseteq b}$ tells us that
  $f(m, n) = \sum_{l = 0}^{n} \binom{n}{l} \square$, where $\square$ is the
  interpretation of the remaining subgraph, and $l$ iterates over all possible
  sizes of $b^{\top}$. It also creates two subdomains
  $b^{\top}, b^{\bot} \subseteq b$ that partition $b$, i.e., as the size of
  $b^{\top}$ increases, the size of $b^{\bot}$ correspondingly decreases. Nodes
  labelled $\land$ correspond to multiplication. Therefore,
  $f(m, n) = \sum_{l = 0}^{n} \binom{n}{l} \diamondsuit \times \heartsuit$,
  where $\diamondsuit$ is the interpretation of the contradiction (i.e., $\bot$)
  node, and $\heartsuit$ is the interpretation of the $\Reff$ node.

  A contradiction node with clause $c$ as a parameter is interpreted as one if
  the clause has groundings and zero otherwise. In this case, the parameter is
  $c = (\emptyset, \{\, (X, Y) \,\}, \{\, X \mapsto b^\top, Y \mapsto b^\top \,\})$
  (not shown in \cref{fig:examplefcg}), which can be read as
  $\forall X, Y \in b^{\top}\text{. }X \ne Y \implies \bot$, i.e.,
  $\forall X, Y \in b^{\top}\text{, }X = Y$. This latter sentence is true if and
  only if $|b^{\top}| < 2$. Therefore, we can use the Iverson bracket notation
  to write
  \[
    \diamondsuit = [l < 2] \coloneqq
    \begin{cases}
      1 & \text{if } l < 2 \\
      0 & \text{otherwise.}
    \end{cases}
  \]

  It remains to interpret the $\Reff$ node. Parameter
  $\{\, a \mapsto a', b \mapsto b^\bot \,\}$ tells us that the interpretation of
  the $\Reff$ node should be the same as that of the source node, but with
  domains $a$ and $b$ replaced with $a'$ and $b^{\bot}$, respectively. Domain
  $a'$ was created by a constraint removal rule applied on $a$, so
  $|a'| = m - 1$. Now $b^{\bot} = b \setminus b^{\top}$, and $|b^{\top}| = l$,
  so $|b^{\bot}| = n - l$. Thus, the interpretation of the $\Reff$ node is a
  recursive call to $f(m - 1, n - l)$. Therefore,
  \begin{align}
    f(m, n) &= \sum_{l = 0}^{n} \binom{n}{l} [l < 2] f(m-1, n-l)\nonumber \\
            &= f(m-1, n) + n f(m-1, n-1).\label{eq:solution}
  \end{align}
  In order to use this recursive function to compute the model count of the
  input formula for any domain sizes, one just needs to find the base cases
  $f(0, n)$ and $f(m, 0)$ for all $m, n \in \mathbb{N}_{0}$.
\end{example}

\section{Empirical Results}\label{sec:results} % Newly Domain-Liftable Formulas

\begin{table*}[t]
  \centering
  \begin{tabular}{cccccc}
    \toprule
    \multicolumn{3}{c}{Function Class} & \multicolumn{3}{c}{Asymptotic Complexity of Counting} \\
    Partial & Endo- & Class & Best Known & With \textsc{ForcLift} & With \textsc{Crane} \\
    \midrule
    \rowcolor{gray!10}\cmark/\xmark & \cmark/\xmark & Functions & $\log m$ & $m$ & $m$ \\
    \xmark & \xmark & \multirow{4}{*}{Surjections} & $n \log m$ & $m^{3}+n^{3}$ & $m^{3}+n^{3}$ \\
    \xmark & \cmark & & $m \log m$ & $m^{3}$ & $m^{3}$ \\
    \cmark & \xmark & & \multicolumn{3}{c}{Same as injections from $b$ to $a$} \\
    \cmark & \cmark & & \multicolumn{3}{c}{Same as endo-injections} \\
    \rowcolor{gray!10}\xmark & \xmark & & $m$ & --- & $mn$ \\
    \rowcolor{gray!10}\xmark & \cmark & & $m$ & --- & $m^3$ \\
    \rowcolor{gray!10}\cmark & \xmark & & $\min\{\, m, n \,\}^2$ & --- & $mn$ \\
    \rowcolor{gray!10}\cmark & \cmark & \multirow{-4}{*}{Injections} & $m^2$ & --- & --- \\
    \xmark & \xmark & \multirow{3}{*}{Bijections} & $m$ & --- & $m$ \\
    \xmark & \cmark & & \multicolumn{3}{c}{\multirow{2}{*}{Same as (partial) (endo-)injections}} \\
    \cmark & \cmark/\xmark & & \multicolumn{3}{c}{} \\
    \bottomrule
  \end{tabular}
  \caption{The worst-case complexity of counting various types of functions.
    Here, $m$ is the size of domain $a$, and $n$ is the size of domain $b$. All
    asymptotic complexities are in $\Theta(\cdot)$. A dash means that no
    complete solution was found.}\label{tbl:results}
\end{table*}

In this section, we compare \textsc{Crane} and \textsc{ForcLift}
\citep{DBLP:conf/ijcai/BroeckTMDR11} on their ability to count various kinds of
functions. (Other WFOMC algorithms such as \textsc{L2C}
\citep{DBLP:conf/kr/KazemiP16} and probabilistic theorem proving
\citep{DBLP:journals/cacm/GogateD16} are unable to solve any of the instances
that \textsc{ForcLift} fails on.) We begin by describing how such functions can
be expressed in FOL\@. \textsc{ForcLift} then translates these sentences in FOL
to formulas as defined in \cref{def:formula}.

% Describe what kind of instances we're investigating
Let $p \in a \times b$ be a predicate. To restrict all relations representable
by $p$ to just functions from $a$ to $b$, in FOL one might write
\[
  \forall X \in a\text{. }\forall Y, Z \in b\text{. }p(X, Y) \land p(X, Z) \implies Y = Z
\]
and
\begin{equation}\label{eq:def2}
  \forall X \in a\text{. }\exists Y \in b\text{. }p(X, Y).
\end{equation}
The former sentence says that one element of $a$ can map to at \emph{most} one
element of $b$, and the latter sentence says that each element of $a$ must map
to at \emph{least} one element of $b$. One can then add
\[
  \forall W, X \in a\text{. }\forall Y \in b\text{. }p(W, Y) \land p(X, Y) \implies W = X
\]
to restrict $p$ to injections or
\[
  \forall Y \in b\text{. }\exists X \in a\text{. }p(X, Y)
\]
to ensure surjectivity or remove \cref{eq:def2} to consider partial functions.
Lastly, one can replace all occurrences of $b$ with $a$ to model endofunctions
(i.e., functions with the same domain and codomain) instead.

% the process: both for running algorithms and for determining complexities
In our experiments, we consider all sixteen combinations of these properties,
i.e., injectivity, surjectivity, partiality, and endo-. \textsc{ForcLift} is
always run until it terminates. \textsc{Crane} is run until either five
solutions are found or the search tree reaches height 6.\footnote{The search
  tree has a high branching factor, so exploring all nodes at depth 5 takes at
  most a few seconds whereas doing the same for depth 6 can be computationally
  infeasible in some cases.} If successful, \textsc{ForcLift} generates a
circuit, and \textsc{Crane} generates one or more (complete) FCGs. In both
cases, we manually convert the resulting graphs into definitions of functions as
described in \cref{sec:interpret}. We then assess the complexity of each
solution and pick the best if \textsc{Crane} returns several solutions of
varying complexities. When assessing the complexity of each such definition, we
make two assumptions. First, we can compute the binomial coefficient
$\binom{n}{k}$ in $\Theta(nk)$ time. Second, techniques such as dynamic
programming and memoization are used to avoid recomputing the same binomial
coefficient or function call multiple times.

The experimental results are summarised in \cref{tbl:results}. The best-known
asymptotic complexity for computing total surjections is by \citet{30049}. All
other best-known complexity results are inferred from the formulas and programs
on the on-line encyclopedia of integer sequences \citep{oeis}. On instances that
could already be solved by \textsc{ForcLift}, the two algorithms perform equally
well. However, \textsc{Crane} is also able to solve all but one instances that
\textsc{ForcLift} fails on in at most cubic time.

Let us examine the case of counting partial (non-endomorphic) injections more
closely. The FCG in \cref{fig:examplefcg,example:interpretation} counts partial
injections and is responsible for the $mn$ entry in the table. For a complete
solution, \cref{eq:solution} must be combined with the base case $f(0, n) = 1$
for all $n \in \mathbb{N}_{0}$. In other words, the base case says that the
empty partial map is the only partial injection with an empty domain, regardless
of the codomain. Finally, note that $f(m, n)$ can be evaluated in $\Theta(mn)$
time by a dynamic programming algorithm that computes $f(i, j)$ for all
$i = 0, \dots, m$ and $j = 0, \dots, n$.

  % \item The complexities assume that arithmetic operations on number such as
  %       addition and multiplication take constant time.
  % \item In some cases (e.g., when counting injections from... to...), we might
  %       immediately recognize that the answer must be zero. Whether such cases
  %       can be handled efficiently or not by our approach depends on the
  %       definitions of functions and the order of evaluation. (We still get the
  %       right answer, though.)
  % \item All complexity results are for the worst case. In particular, optimal
  %       best-case complexity is usually $\Theta(1)$ (see above for why).

% Other results
% \begin{itemize}
%   \item 1d bijections and 1d injections (note that it's the same problem). Depth
%         3 solution:
%         \begin{align*}
%           f(n) &= \sum_{m=0}^n \binom{n}{m} (-1)^{n-m}g(n, m) \\
%           g(n, m) &= \sum_{l=0}^n \binom{n}{l}[l < 2]g(n-l, m-1) \\
%                &= g(n, m - 1) + ng(n - 1, m - 1),
%         \end{align*}
%         which works with base case $g(n, 0) = 1$.
%   \item 1d partial injections. 2 solutions at depth 6, but they're too
%         complicated to check by hand. A contradiction with $X \ne x$ constraints
%         makes things complicated.
%   \item 2d bijections. Depth 3:
%         \begin{align*}
%           f(m, n) &= \sum_{l=0}^m \binom{m}{l} [l < 2] (1 - [l < 1])f(m-l, n-1) \\
%                   &= mf(m-1, n-1),
%         \end{align*}
%         which works with base cases $f(0, 0) = 1$, $f(0, n) = 0$, $f(m, 0) = 0$.
%   \item 2d partial injections, depth 2. Exactly the same circuit as for injections but with base case $f(m, 0) = 1$.
% \end{itemize}

\section{Conclusion and Future Work}

% A summary of what's been done/achieved and how

In this paper, we showed how a state-of-the-art (W)FOMC algorithm can be
empowered by generalising domain recursion and adding support for cycles in the
graph that encodes a solution. To construct such graphs, \textsc{Crane}
supplements \textsc{ForcLift} \citep{DBLP:conf/ijcai/BroeckTMDR11} with three
new compilation rules and a hybrid search algorithm. In \cref{sec:results}, we
saw examples of instances that become liftable not just in theory
\citep{DBLP:journals/jair/Kuzelka21} but with an implemented algorithm as well.
However, our experiments cover only a small set of instances since some parts of
\textsc{Crane} are yet to be fully automated. Specifically, our experiments
focus on various function-counting problems---it remains to be seen what other
types of instances become liftable as a result.

% An idea pivotal to our work is the generalisation of circuits to graphs. Despite
% the wide variety of circuits that are used in artificial intelligence
% \citep{DBLP:series/faia/Darwiche21}, this is the first time that the addition of
% cycles is shown to make a class of circuits more powerful. An important strand
% for future work is in developing an algorithm that learns FCGs from data
% similarly to the way \textsc{ForcLift} has been utilised in learning Markov
% logic networks \citep{DBLP:conf/aaai/BroeckMD13,DBLP:journals/ml/HaarenBMD16}.
% One could also consider whether some of the many recent applications of circuits
% are suitable for FCGs as well. These applications include the verification and
% explainability of neural networks \citep{DBLP:conf/pods/Darwiche20}, causal
% inference \citep{https://doi.org/10.48550/arxiv.2202.02891}, computing the
% expectations of kernel functions \citep{DBLP:conf/uai/LiZVB21}, and variational
% inference in discrete graphical models \citep{DBLP:conf/nips/ShihE20}.

However, the most important direction for future work is in fully automating
this new way of computing the (W)FOMC of a formula. First, we need an algorithm
that transforms FCGs into definitions of functions. Formalising this process
would also allow us to prove the correctness of the new compilation rules in
constructing FCGs that indeed compute the right WMC\@. Second, these definitions
must be simplified before they can be used, perhaps by a computer algebra
system. Third, most importantly, we need a way to find the base cases for the
recursive definitions provided by \textsc{Crane}. What makes this problem
non-trivial is that the number of base cases is not constant for functions of
arity greater than one (i.e., formulas that mention more than one domain). On
the other hand, assuming that a domain is empty can greatly simplify a problem.
Fourth, since the first solution found by \textsc{Crane} is not always optimal
in terms of its complexity, an automated way to determine the asymptotic
complexity of a solution would be helpful as well. Achieving these goals would
make \textsc{Crane} capable of automatically constructing efficient ways to
compute a function (e.g., a sequence) of interest. In addition to the potential
impact to areas of artificial intelligence (AI) such as statistical relational
AI \citep{DBLP:series/synthesis/2016Raedt}, \textsc{Crane} could be beneficial
to research in combinatorics as well \citep{DBLP:conf/ilp/BarvinekB0ZK21}.

\bibliography{paper}
\end{document}

### 2022-07-30 doc/paper/paper.tex
Transfer changes from the thesis

@@
 \newcommand{\Ctwo}{$\mathsf{C}^{2}$}
+\newcommand{\IFO}{$\mathsf{I}\mathsf{FO}^{2}$}
 \DeclareMathOperator{\CR}{\textsc{CR}}
@@
 (WFOMC) extends FOMC with (pairs of) weights on predicates and asks for a
-weighted sum across all models instead. WFOMC emerged as the dominant approach
-to \emph{lifted (probabilistic) inference}. Lifted inference techniques exploit
+weighted sum across all models instead. By fixing the sizes of the domains, a
+WFOMC instance can be rewritten as a WMC instance---in fact, the WFOMC algorithm
+by \citet{DBLP:conf/ijcai/BroeckTMDR11} can do so when it is unable to solve the
+instance in a lifted manner. WFOMC emerged as the dominant approach to
+\emph{lifted (probabilistic) inference}. Lifted inference techniques exploit
 symmetries in probabilistic models by reasoning about sets rather than
@@
   the factorial can be described using two variables and counting quantifiers,
-  so it is known to be liftable in theory \citep{DBLP:journals/jair/Kuzelka21}.}
-We claim that this shortcoming is due to the inability of these algorithms to
-construct recursive solutions. The topic of recursion in the context of WFOMC
-has been studied before but in limited ways.
-\Citet{DBLP:conf/ilp/BarvinekB0ZK21} use WFOMC to generate numerical data which
-is then used to conjecture recurrence relations that explain that data.
+  so it is known to be liftable in principle
+  \citep{DBLP:journals/jair/Kuzelka21}.} We claim that this shortcoming is due
+to the inability of these algorithms to construct recursive solutions. The topic
+of recursion in the context of WFOMC has been studied before but in limited
+ways. \Citet{DBLP:conf/ilp/BarvinekB0ZK21} use WFOMC to generate numerical data
+which is then used to conjecture recurrence relations that explain that data.
 \Citet{DBLP:conf/nips/Broeck11} introduced the idea of \emph{domain recursion}.
@@
 
-% \begin{itemize}
-%   \item But their code only conjectures stuff on data. My conjectures are
-%         guaranteed to always be true.
-%   \item everything has to be expressible in \Ctwo{}, i.e., the two-variable
-%         fragment of FOL with counting quantifiers on one domain.
-%   \item They only consider P-recursive functions, which means that, e.g.,
-%         $f(n) = f(n-1)f(n-2)$ would not be allowed.
-% \end{itemize}
-
 % 5. What are the key components of my approach and results? Also include any
@@
 In this work, we show how to relax these restrictions in a way that results in a
-stronger (W)FOMC algorithm, capable of handling more instances in a lifted
-manner. The ideas presented in this paper are implemented in
-\textsc{Crane}---an extension of the arguably most well-known WFOMC algorithm
-\textsc{ForcLift} written in Scala. \textsc{ForcLift} works in two stages:
-compilation and evaluation/propagation.\footnote{There is also an intermediate
-  stage called \emph{smoothing} that takes place between compilation and
-  evaluation. As our changes to smoothing are quite elementary, we do not
-  discuss them to not distract the reader from the main contributions of this
-  paper.} In the first part, various \emph{(compilation) rules} are applied to
-the input (or some derivative) formula, gradually constructing a circuit. In the
-second part, the weights of the instance (and sometimes constants) are
-propagated through the circuit, computing the WMC\@.
+stronger (W)FOMC algorithm, capable of handling more instances (e.g., counting
+various injective mappings) in a lifted manner. The ideas presented in this
+paper are implemented in \textsc{Crane}---an extension of the arguably most
+well-known WFOMC algorithm \textsc{ForcLift} written in Scala. \textsc{ForcLift}
+works in two stages: compilation and evaluation/propagation.\footnote{There is
+  also an intermediate stage called \emph{smoothing} that takes place between
+  compilation and evaluation. As our changes to smoothing are quite elementary,
+  we do not discuss them to not distract the reader from the main contributions
+  of this paper.} In the first part, various \emph{(compilation) rules} are
+applied to the input (or some derivative) formula, gradually constructing a
+circuit. In the second part, the weights of the instance (and sometimes
+constants) are propagated through the circuit, computing the WMC\@.
 
@@
 
-TODO: improve the wording of the paragraph below.
+TODO: remove the references to the figure.
 
@@
 that we utilise labelled directed graphs instead of circuits. The cycles in
-these graphs represent recursive calls. Suppose the original formula $\phi$
-depends on a domain of size $n \in \mathbb{N}$. Our generalised version of
-domain recursion transforms $\phi$ into a different formula $\psi$ that depends
-on a domain of size $n-1$. After some number of subsequent transformations, the
-algorithm identifies that a solution to $\psi$ can be constructed in part by
-finding a solution to a version of $\phi$ where the domain of size $n$ is
-replaced by a domain of size $n-1$. Recognising $\phi$ from before, we can add a
-cycle-forming edge to the graph, which can be interpreted as function $f$
-relying on $f(n-1)$ to compute $f(n)$.
+these graphs represent recursive calls. See \cref{fig:after} for an illustration
+of an example scenario. Suppose the original formula $\phi$ depends on a domain
+of size $n \in \mathbb{N}$. \emph{Generalised domain recursion} (GDR), one of
+the new compilation rules, transforms $\phi$ into a different formula $\psi$
+that has an additional constant and some new \emph{constraints}. After some
+additional transformations, the constraints in $\psi$ become `uniform' and can
+be removed, replacing the domain of size $n$ with a new domain of size
+$n-1$---this is the responsibility of the \emph{constraint removal} (CR)
+compilation rule. Afterwards, another new compilation rule recognizes that the
+resulting formula $\phi(n-1)$ is just like the input formula $\phi(n)$ except it
+refers to a different domain. This observation allows us to add a cycle-forming
+edge to the graph (highlighted in blue in \cref{fig:after}), which can be
+interpreted as function $f$ relying on $f(n-1)$ to compute $f(n)$. To construct
+such graphs, we also introduce a novel search algorithm that replaces the greedy
+search used by \textsc{ForcLift}.
 
@@
 
-To construct such graphs, we introduce a novel search algorithm that replaces
-greedy search used by \textsc{ForcLift} and three compilation rules that work
-together to construct cyclic graphs. We begin with \cref{sec:recprelims} where
-we define the representation used for sentences in FOL as well as discuss
-caching and some notational conventions. Then, at the beginning of
-\cref{sec:methods} we formally define the graphs that replace circuits in
+\Cref{sec:recprelims} defines the representation used for sentences in FOL as
+well as discuss caching and some notational conventions. At the beginning of
+\cref{sec:methods}, we formally define the graphs that replace circuits in
 representing a solution to a (W)FOMC problem and discuss some related notions.
-\Cref{sec:rules} introduces the new compilation rules:
-\begin{itemize}
-  \item a generalisation of domain recursion by \citet{DBLP:conf/nips/Broeck11},
-  \item \emph{constraint removal}---a formula transformation rule that removes
-        the constraints introduced by generalised domain recursion (GDR),
-        introducing a new (smaller) domain instead,
-  \item and a rule for creating recursive calls.
-\end{itemize}
-In a typical solution produced by \textsc{Crane}, these rules are executed in
-exactly this order (interspersed with some other rules), with the edge that
-represents a recursive call pointing back to the node introduced by GDR\@. In
-\cref{sec:interpret}, we informally discuss how a graph can be interpreted as a
+\Cref{sec:rules} introduces the new compilation rules. \Cref{sec:search} then
+describes our new search algorithm that makes fewer assumptions than
+\textsc{ForcLift} about the right order in which compilation rules should be
+applied. In \cref{sec:interpret}, we discuss how a graph can be interpreted as a
 collection of (potentially recursive) functions. Finally, in \cref{sec:results}
@@
 the instances that were already solvable by \textsc{ForcLift} but is also able
-to handle most instances that \textsc{ForcLift} fails on as well.
-
-% \Cref{sec:search} then describes our new search algorithm that makes fewer
-% assumptions than \textsc{ForcLift} about the right order in which compilation
-% rules should be applied.
-
-% \begin{itemize}
-%   \item What we do with the compilation result is different (see below)
-%   \item evaluation/interpretation: algebraic simplification, dynamic programming
-%   \item limitation: function extraction and simplification need to be automated,
-%         same for finding base cases
-% \end{itemize}
-
-% Leftovers
-% \begin{itemize}
-%   \item compilation works by always having a formula as input and
-%         adding nodes to the circuit/FCG that constitute the solution the that
-%         formula.
-%   \item Workflow after
-%   \begin{itemize}
-%     \item Compile the formula to a graph
-%     \item Extract the definitions of functions
-%     \item Simplify
-%     \item Supplement with base cases
-%     \item Evaluate to get the answer
-%   \end{itemize}
-% \end{itemize}
+to handle most of the instances that \textsc{ForcLift} fails on.
 
@@
 
-Our representation of FOMC instances is heavily based on the format used
+Our representation of FOMC instances is largely based on the format used
 internally by \textsc{ForcLift}, some aspects of which are described by
@@
 either an atom or the negation of an atom (denoted by
-$\neg p(t_1, \dots, t_n)$). Let $\mathcal{D}$ be the set of all domains; note
-that this set expands during compilation.
+$\neg p(t_1, \dots, t_n)$). Let $\mathcal{D}$ be the set of all domains.
+Initially, $\mathcal{D}$ contains all domains mentioned by the input (W)FOMC
+instance. During compilation, new domains added to $\mathcal{D}$ by some of the
+compilation rules.
 
@@
 mapped to domains, and each $n$-ary predicate is implicitly mapped to a sequence
-of $n$ domains. For constant $x$, predicate $p$, and domains $a$ and $b$, we
-write, e.g., $x \in a$ and $p \in a \times b$ to denote that $x$ is associated
-with $a$, and $p$ is associated with $a$ and $b$ (in that order).
+of $n$ domains. For constant or variable $x$, predicate $p$, and domains
+$\Gamma$ and $\Delta$, we write, e.g., $x \in \Gamma$ and
+$p \in \Gamma \times \Delta$ to denote that $x$ is associated with $\Gamma$, and
+$p$ is associated with $\Gamma$ and $\Delta$ (in that order).
 
@@
             (\{\, \neg p(X, Y), \neg p(X, Z) \,\}, \{\, (Y, Z) \,\}, \\
-            \{\, X \mapsto a, Y \mapsto b, Z \mapsto b \,\}),
+            \{\, X \mapsto \Gamma, Y \mapsto \Delta, Z \mapsto \Delta \,\}),
           \end{multlined}\\
@@
             (\{\, \neg p(X, Y), \neg p(Z, Y) \,\}, \{\, (X, Z) \,\}, \\
-            \{\, X \mapsto a, Y \mapsto b, Z \mapsto a \,\})
+            \{\, X \mapsto \Gamma, Y \mapsto \Delta, Z \mapsto \Gamma \,\})
           \end{multlined}
   \end{align*}
-  for some predicate $p$, variables $X$, $Y$, $Z$, and domains $a$ and $b$. Then
-  $\Vars(\{\, (Y, Z) \,\}) = \{\, Y, Z \,\}$, and
+  for some predicate $p$, variables $X$, $Y$, $Z$, and domains $\Gamma$ and
+  $\Delta$. Then $\Vars(\{\, (Y, Z) \,\}) = \{\, Y, Z \,\}$, and
   $\Vars(c_{1}) = \Vars(c_{2}) = \{\, X, Y, Z \,\}$. Based on the domain maps of
-  $c_{1}$ and $c_{2}$, we can infer that $p \in a \times b$. All variables (in
-  both clauses) that occur as the first argument to $p$ are in $a$, and likewise
-  all variables that occur as the second argument to $p$ are in $b$. Therefore,
-  $\phi$ `type checks' as a valid formula.
+  $c_{1}$ and $c_{2}$, we can infer that $p \in \Gamma \times \Delta$. All
+  variables (in both clauses) that occur as the first argument to $p$ are in
+  $\Gamma$, and likewise all variables that occur as the second argument to $p$
+  are in $\Delta$. Therefore, $\phi$ `type checks' as a valid formula.
 \end{example}
@@
 assigned to a domain. Second, while \citet{DBLP:conf/ijcai/BroeckTMDR11} allow
-for equality constraints and constraints of the form $X \not\in d$ for some
-variable $X$ and domain $d$, we exclude such constraints simply because they are
-not needed.
-
-One can read a formula as in \cref{def:formula} as a sentence in a FOL\@.
-All variables in a
-clause are implicitly universally quantified (but note that variables are never
-shared among clauses), and all clauses in a formula are implicitly linked by
-conjunction. Thus, formula $\phi$ from \cref{example:first} reads as
+for equality constraints and constraints of the form $X \not\in \Delta$ for some
+variable $X$ and domain $\Delta$, we exclude such constraints simply because
+they are not needed.
+
+One can read a formula as in \cref{def:formula} as a sentence in a FOL\@. All
+variables in a clause are implicitly universally quantified (but note that
+variables are never shared among clauses), and all clauses in a formula are
+implicitly linked by conjunction. Thus, formula $\phi$ from \cref{example:first}
+reads as
 \begin{align*}
   &\begin{multlined}[t]
-    (\forall X \in a\text{. }\forall Y, Z \in b\text{. }\\
+    (\forall X \in \Gamma\text{. }\forall Y, Z \in \Delta\text{. }\\
     Y \ne Z \implies \neg p(X, Y) \lor \neg p(X, Z)) \land
@@
   &\begin{multlined}[t]
-    (\forall X, Z \in a\text{. }\forall Y \in b\text{. }\\
+    (\forall X, Z \in \Gamma\text{. }\forall Y \in \Delta\text{. }\\
     X \ne Z \implies \neg p(X, Y) \lor \neg p(Z, Y)).
@@
 \begin{example}
-  Let $\phi$ be as in \cref{example:first} and let $|a| = |b| = 2$. There are
-  $2^{2 \times 2} = 16$ possible relations between $a$ and $b$. Let us count how
-  many of them satisfy the conditions imposed on predicate $p$. The empty
-  relation does. All four relations of cardinality one do too. Finally, there
-  are two relations of cardinality two that satisfy the conditions as well.
-  Thus, the FOMC of $\phi$ (when $|a| = |b| = 2$) is 7. Incidentally, the FOMC
-  of $\phi$ counts partial injections. We will continue to use the problem of
-  counting partial injections (and the formula from \cref{example:first}
-  specifically) as the main running example throughout the paper.
+  Let $\phi$ be as in \cref{example:first} and let $|\Gamma| = |\Delta| = 2$.
+  There are $2^{2 \times 2} = 16$ possible relations between $\Gamma$ and
+  $\Delta$. Let us count how many of them satisfy the conditions imposed on
+  predicate $p$. The empty relation does. All four relations of cardinality one
+  do too. Finally, there are two relations of cardinality two that satisfy the
+  conditions as well. Thus, the FOMC of $\phi$ (when $|\Gamma| = |\Delta| = 2$)
+  is 7. Incidentally, the FOMC of $\phi$ counts partial injections. We will
+  continue to use the problem of counting partial injections (and the formula
+  from \cref{example:first} specifically) as the main running example throughout
+  the paper.
 \end{example}
@@
     parent/.style={draw,-Latex},sibling distance=3cm]
-    \node (dr) {$\GDR_{a \gets a \setminus \{\, x \,\}}$}
-    child {node {$\bigvee_{b^\top \subseteq b}$}
-      child {node {$\CR_{a \mapsto a'}$}
+    \node (dr) {$\GDR_{\Gamma \gets \Gamma \setminus \{\, x \,\}}$}
+    child {node {$\bigvee_{\Delta^\top \subseteq \Delta}$}
+      child {node {$\CR_{\Gamma \mapsto \Gamma'}$}
         child {
@@
           child {node {$\bot$}}
-          % _{(\emptyset, \{\, (X, Y) \,\}, \{\, X \mapsto b^\top, Y \mapsto b^\top \,\})}
-          child {node (ref) {$\Reff_{\{\, a \mapsto a', b \mapsto b^{\bot} \,\}}$}}
+          child {node (ref) {$\Reff_{\{\, \Gamma \mapsto \Gamma', \Delta \mapsto \Delta^{\bot} \,\}}$}}
         }}};
@@
     problem of counting partial injections from \cref{example:first}. Label
-    $\bigvee_{b^\top \subseteq b}$ denotes set-disjunction, $\land$ denotes
-    conjunction, and $\bot$ denotes a contradiction---see the work by
+    $\bigvee_{\Delta^\top \subseteq \Delta}$ denotes set-disjunction, $\land$
+    denotes conjunction, and $\bot$ denotes a contradiction---see the work by
     \citet{DBLP:conf/ijcai/BroeckTMDR11} for the descriptions of these node
@@
 \begin{itemize}
-  \item a type for \emph{constraint removal} denoted by $\CR$,
-  \item a type for \emph{generalised domain recursion} denoted by $\GDR$ (both
-        with out-degree one),
+  \item a type for constraint removal denoted by $\CR$,
+  \item a type for generalised domain recursion denoted by $\GDR$ (both with
+        out-degree one),
   \item and $\star$---a placeholder type (with out-degree zero) for nodes that
@@
 \cref{fig:examplefcg} for an example FCG\@. Its source node has out-degree 1
-(i.e., $|N^+(s)| = 1$), label $\GDR_{a \gets a \setminus \{\, x \,\}}$, and type
-$\GDR$ (i.e., $\tau(s) = \GDR$).
+(i.e., $|N^+(s)| = 1$), label
+$\GDR_{\Gamma \gets \Gamma \setminus \{\, x \,\}}$, and type $\GDR$ (i.e.,
+$\tau(s) = \GDR$).
 
@@
 \subsection{Generalised Domain Recursion}\label{sec:dr}
-% 1. Note that the total number of such possibilities is not necessarily
-% exponential: some combinations produce clearly unsatisfiable formulas that can
-% be immediately discarded.
-% 2. We can combine all of these possibilities into a single formula equivalent
-% to the original one.
-% 3. \begin{itemize}
-%   \item the formula is shattered,
-%   \item the formula has no independent subformulas,
-%   \item and there exists a root binding class.
-% \end{itemize}
-% 4. During evaluation, $v$ is ignored, and the WMCs of $x$ and $r$ can be
-% computed independently. Note that the WMC of $x$ is independent of the size of
-% $D$---this further simplifies the matters.
 
@@
 \citet{DBLP:conf/nips/Broeck11} and the one presented here) is as follows. Let
-$d \in \mathcal{D}$ be a domain. Assuming that $d \ne \emptyset$, pick some
-$x \in d$. Then, for every variable $X$ associated with domain $d$ that occurs
-in a literal, consider two possibilities: $X = x$ and $X \ne x$.
+$\Omega \in \mathcal{D}$ be a domain. Assuming that $\Omega \ne \emptyset$, pick
+some $x \in \Omega$. Then, for every variable $X \in \Omega$ that occurs in a
+literal, consider two possibilities: $X = x$ and $X \ne x$.
 
@@
     (\{\, \neg p(X, Y), \neg p(X, Z) \,\}, \{\, (Y, Z) \,\}, \\
-    \{\, X \mapsto a, Y \mapsto b, Z \mapsto b \,\}).
+    \{\, X \mapsto \Gamma, Y \mapsto \Delta, Z \mapsto \Delta \,\}).
   \end{multline*}
-  Then we can introduce constant $x \in a$ and rewrite $\phi$ as
+  Then we can introduce constant $x \in \Gamma$ and rewrite $\phi$ as
   $\phi' = \{\, c_{1}, c_{2} \,\}$, where
@@
       (\{\, \neg p(x, Y), \neg p(x, Z) \,\}, \{\, (Y, Z) \,\}, \\
-      \{\, Y \mapsto b, Z \mapsto b \,\}),
+      \{\, Y \mapsto \Delta, Z \mapsto \Delta \,\}),
       \end{multlined}\\
@@
       (\{\, \neg p(X, Y), \neg p(X, Z) \,\}, \{\, (X, x), (Y, Z) \,\}, \\
-      \{\, X \mapsto a', Y \mapsto b, Z \mapsto b \,\}),
+      \{\, X \mapsto \Gamma', Y \mapsto \Delta, Z \mapsto \Delta \,\}),
       \end{multlined}
   \end{align*}
-  and $a' = a \setminus \{\, x \,\}$.
+    and $\Gamma' = \Gamma \setminus \{\, x \,\}$.
 \end{example}
@@
 \cref{example:dr}) can be handled efficiently. The clauses in this expanded
-formula are then partitioned into three parts based on whether the transformation
-introduced constants or constraints or both. The aforementioned conditions
-ensure that these parts can be treated independently.
+formula are then partitioned into three parts based on whether the
+transformation introduced constants or constraints or both. The aforementioned
+conditions ensure that these parts can be treated independently.
 
@@
   \caption{The compilation rule for $\GDR$ nodes.}\label{alg:domainrecursion}
-  \KwIn{formula $\phi$}
+  \KwIn{formula $\phi$, set of all relevant domains $\mathcal{D}$}
   \KwOut{set of chips $S$}
   $S \gets \emptyset$\;
-  \ForEach{domain $d \in \mathcal{D}$ s.t.\ there is $c \in \phi$ and $v \in \Vars(L_c)$ s.t. $\delta_c(v) = d$\label{line:condition}}{
+  \ForEach{domain $\Omega \in \mathcal{D}$ s.t.\ there is $c \in \phi$ and $X \in \Vars(L_c)$ s.t. $\delta_c(X) = \Omega$\label{line:condition}}{
     $\phi' \gets \emptyset$\;
-    $x \gets \text{a new constant in domain } d$\;
+    $x \gets \text{a new constant in domain } \Omega$\;
     \ForEach{clause $c = (L, C, \delta) \in \phi$\label{line:forclause}}{
-      $V \gets \{\, v \in \Vars(L) \mid \delta(v) = d \,\}$\;
-      \ForEach{subset $W \subseteq V$ s.t. $W^2 \cap C = \emptyset$ {\bf and} $W \cap \{\, v \in \Vars(C) \mid (v, y) \in C \text{ for some constant } y \,\} = \emptyset$\label{line:conditions}}{
+      $V \gets \{\, X \in \Vars(L) \mid \delta(X) = \Omega \,\}$\;
+      \ForEach{subset $W \subseteq V$ s.t. $W^2 \cap C = \emptyset$ {\bf and} $W \cap \{\, X \in \Vars(C) \mid (X, y) \in C \text{ for some constant } y \,\} = \emptyset$\label{line:conditions}}{
         \tcc{$\delta'$ restricts $\delta$ to the new set of variables}
-        $\phi' \gets \phi' \cup \{\, (L[x/W], C[x/W] \cup \{\, (v, x) \mid (v \in V \setminus W) \,\}, \delta') \,\}$\;\label{line:generation}
+        $\phi' \gets \phi' \cup \{\, (L[x/W], C[x/W] \cup \{\, (X, x) \mid (X \in V \setminus W) \,\}, \delta') \,\}$\;\label{line:generation}
       }
     }
-    $S \gets S \cup \{\, (\GDR_{d \gets d \setminus \{\, x \,\}}, \langle\phi'\rangle) \,\}$\;
+    $S \gets S \cup \{\, (\GDR_{\Omega \gets \Omega \setminus \{\, x \,\}}, \langle\phi'\rangle) \,\}$\;
   }
@@
 In contrast, GDR has only one precondition: for GDR to be applicable on domain
-$d \in \mathcal{D}$, there must be at least one variable with domain $d$ that is
-featured in a literal (and not just in constraints). Without such variables, GDR
-would have no effect on the formula. GDR is also simpler in that the expanded
-formula is left as-is to be handled by other compilation rules. Typically, after
-a few more rules are applied, a combination of $\CR$ and $\Reff$ nodes
-introduces a loop back to the $\GDR$ node, thus completing the definition of a
-recursive function. The GDR compilation rule is summarised as
+$\Omega \in \mathcal{D}$, there must be at least one variable with domain
+$\Omega$ that is featured in a literal (and not just in constraints). Without
+such variables, GDR would have no effect on the formula. GDR is also simpler in
+that the expanded formula is left as-is to be handled by other compilation
+rules. Typically, after a few more rules are applied, a combination of $\CR$ and
+$\Reff$ nodes introduces a loop back to the $\GDR$ node, thus completing the
+definition of a recursive function. The GDR compilation rule is summarised as
 \cref{alg:domainrecursion} and explained in more detail using the example below.
@@
   \cref{example:first}. While GDR is possible on both domains, here we
-  illustrate how it works on $a$. Having chosen a domain, the algorithm iterates
-  over the clauses of $\phi$. Suppose \cref{line:forclause} picks $c = c_1$ as
-  the first clause. Then, set $V$ is constructed to contain all variables with
-  domain $d = a$ that occur in the literals of clause $c$. In this case,
-  $V = \{\, X \,\}$.
+  illustrate how it works on $\Gamma$. Having chosen a domain, the algorithm
+  iterates over the clauses of $\phi$. Suppose \cref{line:forclause} picks
+  $c = c_1$ as the first clause. Then, set $V$ is constructed to contain all
+  variables with domain $\Omega = \Gamma$ that occur in the literals of clause
+  $c$. In this case, $V = \{\, X \,\}$.
 
@@
     (\{\, \neg p(X, Y), \neg p(X, Z) \,\}, \{\, (Y, Z), (X, x) \,\}, \\
-    \{\, X \mapsto a, Y \mapsto b, Z \mapsto b \,\}),
+    \{\, X \mapsto \Gamma, Y \mapsto \Delta, Z \mapsto \Delta \,\}),
   \end{multline*}
@@
   \[
-    (\{\, \neg p(x, Y), \neg p(x, Z) \,\}, \{\, (Y, Z) \,\}, \{\, Y \mapsto b, Z \mapsto b \,\})
+    (\{\, \neg p(x, Y), \neg p(x, Z) \,\}, \{\, (Y, Z) \,\}, \{\, Y \mapsto \Delta, Z \mapsto \Delta \,\})
   \]
@@
     (\{\, \neg p(X, Y), \neg p(Z, Y) \,\}, \{\, (X, Z), (X, x), (Z, x) \,\}, \\
-    \{\, X \mapsto a, Y \mapsto b, Z \mapsto a \,\}),
+    \{\, X \mapsto \Gamma, Y \mapsto \Delta, Z \mapsto \Gamma \,\}),
   \end{multline*}
@@
   \[
-    (\{\, \neg p(x, Y), \neg p(Z, Y) \,\}, \{\, (Z, x) \,\}, \{\, Y \mapsto b, Z \mapsto a \,\}),
+    (\{\, \neg p(x, Y), \neg p(Z, Y) \,\}, \{\, (Z, x) \,\}, \{\, Y \mapsto \Delta, Z \mapsto \Gamma \,\}),
   \]
@@
   \[
-    (\{\, \neg p(X, Y), \neg p(x, Y) \,\}, \{\, (X, x) \,\}, \{\, X \mapsto a, Y \mapsto b \,\}).
+    (\{\, \neg p(X, Y), \neg p(x, Y) \,\}, \{\, (X, x) \,\}, \{\, X \mapsto \Gamma, Y \mapsto \Delta \,\}).
   \]
@@
   \caption{The compilation rule for $\CR$ nodes.}\label{alg:constraintremoval}
-  \KwIn{formula $\phi$, set of domains $\mathcal{D}$}
+  \KwIn{formula $\phi$, set of all relevant domains $\mathcal{D}$}
   \KwOut{set of chips $S$}
   $S \gets \emptyset$\;
-  \ForEach{domain $d \in \mathcal{D}$ and element $x \in d$ s.t.
-$x$ does not occur in any literal of any clause of $\phi$ {\bf and} for each clause $c = (L, C, \delta_c) \in \phi$ and variable $v \in \Vars(c)$, either $\delta_c(v) \ne d$ or $(v, x) \in C$\label{line:crconditions}}{
-    add a new domain $d'$ to $\mathcal{D}$\;
+  \ForEach{domain $\Omega \in \mathcal{D}$ and element $x \in \Omega$ s.t.
+$x$ does not occur in any literal of any clause of $\phi$ {\bf and} for each clause $c = (L, C, \delta_c) \in \phi$ and variable $X \in \Vars(c)$, either $\delta_c(X) \ne \Omega$ or $(X, x) \in C$\label{line:crconditions}}{
+    add a new domain $\Omega'$ to $\mathcal{D}$\;
     $\phi' \gets \emptyset$\;
@@
       $C' \gets \{\, (a, b) \in C \mid b \ne x \,\}$\;\label{line:constraintremoval}
-      \nosemic$\delta' \gets v \mapsto \begin{cases} d' & \text{if} \delta(v) = d\\ \delta(v) & \text{otherwise;} \end{cases}$\;\label{line:newdelta}
+      \nosemic$\delta' \gets X \mapsto
+      \begin{cases}
+        \Omega' & \text{if } \delta(X) = \Omega\\
+        \delta(X) & \text{otherwise;}
+      \end{cases}$\;\label{line:newdelta}
       $\phi' \gets \phi' \cup \{\, (L, C', \delta') \,\}$\;
     }
-    $S \gets S \cup \{\, (\CR_{d \mapsto d'}, \langle\phi'\rangle) \,\}$\;
+    $S \gets S \cup \{\, (\CR_{\Omega \mapsto \Omega'}, \langle\phi'\rangle) \,\}$\;
   }
@@
 
-Recall that GDR on a domain $d$ creates constraints of the form $X_i \ne x$ for
-some constant $x \in d$ and family of variables $X_i \in d$. Once certain
-conditions are satisfied, \cref{alg:constraintremoval} can eliminate these
-constraints and replace $d$ with a new domain $d'$, which can be interpreted as
-$d \setminus \{\, x \,\}$. These conditions (on \cref{line:crconditions} of the
-algorithm) are that a constraint of the form $X \ne e$ exists for all variables
-$X \in d$ across all clauses, and such constraints are the only place where $e$
-occurs. The algorithm then proceeds to construct the new formula by removing
-constraints (on \cref{line:constraintremoval}) and constructing a new domain map
-$\delta'$ that replaces $d$ with $d'$ (on \cref{line:newdelta}).
+Recall that GDR on a domain $\Omega$ creates constraints of the form $X_i \ne x$
+for some constant $x \in \Omega$ and family of variables $X_i \in \Omega$. Once
+certain conditions are satisfied, \cref{alg:constraintremoval} can eliminate
+these constraints and replace $\Omega$ with a new domain $\Omega'$, which can be
+interpreted as $\Omega \setminus \{\, x \,\}$. These conditions (on
+\cref{line:crconditions} of the algorithm) are that a constraint of the form
+$X \ne x$ exists for all variables $X \in \Omega$ across all clauses, and such
+constraints are the only place where $x$ occurs. The algorithm then proceeds to
+construct the new formula by removing constraints (on
+\cref{line:constraintremoval}) and constructing a new domain map $\delta'$ that
+replaces $\Omega$ with $\Omega'$ (on \cref{line:newdelta}).
 
@@
   \begin{align*}
-    c_1 &= (\emptyset, \{\, (Y, X) \,\}, \{\, X \mapsto b^\top, Y \mapsto b^\top \,\}), \\
+    c_1 &= (\emptyset, \{\, (Y, X) \,\}, \{\, X \mapsto \Delta^\top, Y \mapsto \Delta^\top \,\}), \\
     c_2 &=
@@
             (\{\, \neg p(X, Y), \neg p(X, Z) \,\}, \{\, (X, x), (Y, Z) \,\}, \\
-            \{\, X \mapsto a, Y \mapsto b^\bot, Z \mapsto b^\bot \,\}),
+            \{\, X \mapsto \Gamma, Y \mapsto \Delta^\bot, Z \mapsto \Delta^\bot \,\}),
           \end{multlined}\\
@@
             (\{\, \neg p(X, Y), \neg p(Z, Y) \,\}, \{\, (X, x), (Z, X), (Z, x) \,\}, \\
-            \{\, X \mapsto a, Y \mapsto b^\bot, Z \mapsto a \,\}).
+            \{\, X \mapsto \Gamma, Y \mapsto \Delta^\bot, Z \mapsto \Gamma \,\}).
           \end{multlined}
   \end{align*}
-  Domain $a$ and with its element $x \in a$ satisfy the preconditions for
-  constraint removal. The rule introduces a new domain $a'$ and transforms
-  $\phi$ to $\phi' = (c_1', c_2', c_3')$, where
+  Domain $\Gamma$ and with its element $x \in \Gamma$ satisfy the preconditions
+  for CR\@. The rule introduces a new domain $\Gamma'$ and transforms $\phi$ to
+  $\phi' = (c_1', c_2', c_3')$, where
   \begin{align*}
@@
              (\{\, \neg p(X, Y), \neg p(X, Z) \,\}, \{\, (Y, Z) \,\}, \\
-             \{\, X \mapsto a', Y \mapsto b^\bot, Z \mapsto b^\bot \,\}),
+             \{\, X \mapsto \Gamma', Y \mapsto \Delta^\bot, Z \mapsto \Delta^\bot \,\}),
            \end{multlined} \\
@@
              (\{\, \neg p(X, Y), \neg p(Z, Y) \,\}, \{\, (Z, X) \,\}, \\
-             \{\, X \mapsto a', Y \mapsto b^\bot, Z \mapsto a' \,\}).
+             \{\, X \mapsto \Gamma', Y \mapsto \Delta^\bot, Z \mapsto \Gamma' \,\}).
            \end{multlined}
@@
 reference it.
+
+% TODO: do I still need the definition of a chip? What about tau?
 
@@
   Let us use the FCG from \cref{fig:examplefcg} as an example. The input formula
-  (i.e., the formula in \cref{example:first}) has two domains: $a$ and $b$.
-  Thus, the interpretation of the FCG is a function
+  (i.e., the formula in \cref{example:first}) has two domains: $\Gamma$ and
+  $\Delta$. Thus, the interpretation of the FCG is a function
   $f\colon \mathbb{N}_{0} \times \mathbb{N}_{0} \to \mathbb{R}_{\ge 0}$. Let
-  $m \coloneqq |a|$, and $n \coloneqq |b|$. The node labelled
-  $\bigvee_{b^{\top} \subseteq b}$ tells us that
+  $m \coloneqq |\Gamma|$, and $n \coloneqq |\Delta|$. The node labelled
+  $\bigvee_{\Delta^{\top} \subseteq \Delta}$ tells us that
   $f(m, n) = \sum_{l = 0}^{n} \binom{n}{l} \square$, where $\square$ is the
   interpretation of the remaining subgraph, and $l$ iterates over all possible
-  sizes of $b^{\top}$. It also creates two subdomains
-  $b^{\top}, b^{\bot} \subseteq b$ that partition $b$, i.e., as the size of
-  $b^{\top}$ increases, the size of $b^{\bot}$ correspondingly decreases. Nodes
-  labelled $\land$ correspond to multiplication. Therefore,
+  sizes of $\Delta^{\top}$. It also creates two subdomains
+  $\Delta^{\top}, \Delta^{\bot} \subseteq b$ that partition $\Delta$, i.e., as
+  the size of $\Delta^{\top}$ increases, the size of $\Delta^{\bot}$
+  correspondingly decreases. Nodes labelled $\land$ correspond to
+  multiplication. Therefore,
   $f(m, n) = \sum_{l = 0}^{n} \binom{n}{l} \diamondsuit \times \heartsuit$,
@@
   the clause has groundings and zero otherwise. In this case, the parameter is
-  $c = (\emptyset, \{\, (X, Y) \,\}, \{\, X \mapsto b^\top, Y \mapsto b^\top \,\})$
+  $c = (\emptyset, \{\, (X, Y) \,\}, \{\, X \mapsto \Delta^\top, Y \mapsto \Delta^\top \,\})$
   (not shown in \cref{fig:examplefcg}), which can be read as
-  $\forall X, Y \in b^{\top}\text{. }X \ne Y \implies \bot$, i.e.,
-  $\forall X, Y \in b^{\top}\text{, }X = Y$. This latter sentence is true if and
-  only if $|b^{\top}| < 2$. Therefore, we can use the Iverson bracket notation
-  to write
+  $\forall X, Y \in \Delta^{\top}\text{. }X \ne Y \implies \bot$, i.e.,
+  $\forall X, Y \in \Delta^{\top}\text{. }X = Y$. This latter sentence is true
+  if and only if $|\Delta^{\top}| < 2$. Therefore, we can use the Iverson
+  bracket notation to write
   \[
@@
   It remains to interpret the $\Reff$ node. Parameter
-  $\{\, a \mapsto a', b \mapsto b^\bot \,\}$ tells us that the interpretation of
-  the $\Reff$ node should be the same as that of the source node, but with
-  domains $a$ and $b$ replaced with $a'$ and $b^{\bot}$, respectively. Domain
-  $a'$ was created by a constraint removal rule applied on $a$, so
-  $|a'| = m - 1$. Now $b^{\bot} = b \setminus b^{\top}$, and $|b^{\top}| = l$,
-  so $|b^{\bot}| = n - l$. Thus, the interpretation of the $\Reff$ node is a
-  recursive call to $f(m - 1, n - l)$. Therefore,
+  $\{\, \Gamma \mapsto \Gamma', \Delta \mapsto \Delta^\bot \,\}$ tells us that
+  the interpretation of the $\Reff$ node should be the same as that of the
+  source node, but with domains $\Gamma$ and $\Delta$ replaced with $\Gamma'$
+  and $\Delta^{\bot}$, respectively. Domain $\Gamma'$ was created by the CR rule
+  applied on $\Gamma$, so $|\Gamma'| = m - 1$. Now
+  $\Delta^{\bot} = \Delta \setminus \Delta^{\top}$, and $|\Delta^{\top}| = l$,
+  so $|\Delta^{\bot}| = n - l$. Thus, the interpretation of the $\Reff$ node is
+  a recursive call to $f(m - 1, n - l)$. Therefore,
   \begin{align}
@@
     \xmark & \cmark & & $m \log m$ & $m^{3}$ & $m^{3}$ \\
-    \cmark & \xmark & & \multicolumn{3}{c}{Same as injections from $b$ to $a$} \\
+    \cmark & \xmark & & \multicolumn{3}{c}{Same as injections from $\Delta$ to $\Gamma$} \\
     \cmark & \cmark & & \multicolumn{3}{c}{Same as endo-injections} \\
@@
   \caption{The worst-case complexity of counting various types of functions.
-    Here, $m$ is the size of domain $a$, and $n$ is the size of domain $b$. All
-    asymptotic complexities are in $\Theta(\cdot)$. A dash means that no
-    complete solution was found.}\label{tbl:results}
+    Here, $m$ is the size of domain $\Gamma$, and $n$ is the size of domain
+    $\Delta$. All asymptotic complexities are in $\Theta(\cdot)$. A dash means
+    that no complete solution was found.}\label{tbl:results}
 \end{table*}
@@
 % Describe what kind of instances we're investigating
-Let $p \in a \times b$ be a predicate. To restrict all relations representable
-by $p$ to just functions from $a$ to $b$, in FOL one might write
+Let $p \in \Gamma \times \Delta$ be a predicate. To restrict all relations
+representable by $p$ to just functions from $\Gamma$ to $\Delta$, in FOL one
+might write
 \[
-  \forall X \in a\text{. }\forall Y, Z \in b\text{. }p(X, Y) \land p(X, Z) \implies Y = Z
+  \forall X \in \Gamma\text{. }\forall Y, Z \in \Delta\text{. }p(X, Y) \land p(X, Z) \implies Y = Z
 \]
@@
 \begin{equation}\label{eq:def2}
-  \forall X \in a\text{. }\exists Y \in b\text{. }p(X, Y).
+  \forall X \in \Gamma\text{. }\exists Y \in \Delta\text{. }p(X, Y).
 \end{equation}
-The former sentence says that one element of $a$ can map to at \emph{most} one
-element of $b$, and the latter sentence says that each element of $a$ must map
-to at \emph{least} one element of $b$. One can then add
+The former sentence says that one element of $\Gamma$ can map to at \emph{most}
+one element of $\Delta$, and the latter sentence says that each element of
+$\Gamma$ must map to at \emph{least} one element of $\Delta$. One can then add
 \[
-  \forall W, X \in a\text{. }\forall Y \in b\text{. }p(W, Y) \land p(X, Y) \implies W = X
+  \forall X,Z \in \Gamma\text{. }\forall Y \in \Delta\text{. }p(X, Y) \land p(Z, Y) \implies X = Z
 \]
@@
 \[
-  \forall Y \in b\text{. }\exists X \in a\text{. }p(X, Y)
+  \forall Y \in \Delta\text{. }\exists X \in \Gamma\text{. }p(X, Y)
 \]
 to ensure surjectivity or remove \cref{eq:def2} to consider partial functions.
-Lastly, one can replace all occurrences of $b$ with $a$ to model endofunctions
-(i.e., functions with the same domain and codomain) instead.
+Lastly, one can replace all occurrences of $\Delta$ with $\Gamma$ to model
+endofunctions (i.e., functions with the same domain and codomain) instead.
 
@@
 
-  % \item The complexities assume that arithmetic operations on number such as
-  %       addition and multiplication take constant time.
-  % \item In some cases (e.g., when counting injections from... to...), we might
-  %       immediately recognize that the answer must be zero. Whether such cases
-  %       can be handled efficiently or not by our approach depends on the
-  %       definitions of functions and the order of evaluation. (We still get the
-  %       right answer, though.)
-  % \item All complexity results are for the worst case. In particular, optimal
-  %       best-case complexity is usually $\Theta(1)$ (see above for why).
-
-% Other results
-% \begin{itemize}
-%   \item 1d bijections and 1d injections (note that it's the same problem). Depth
-%         3 solution:
-%         \begin{align*}
-%           f(n) &= \sum_{m=0}^n \binom{n}{m} (-1)^{n-m}g(n, m) \\
-%           g(n, m) &= \sum_{l=0}^n \binom{n}{l}[l < 2]g(n-l, m-1) \\
-%                &= g(n, m - 1) + ng(n - 1, m - 1),
-%         \end{align*}
-%         which works with base case $g(n, 0) = 1$.
-%   \item 1d partial injections. 2 solutions at depth 6, but they're too
-%         complicated to check by hand. A contradiction with $X \ne x$ constraints
-%         makes things complicated.
-%   \item 2d bijections. Depth 3:
-%         \begin{align*}
-%           f(m, n) &= \sum_{l=0}^m \binom{m}{l} [l < 2] (1 - [l < 1])f(m-l, n-1) \\
-%                   &= mf(m-1, n-1),
-%         \end{align*}
-%         which works with base cases $f(0, 0) = 1$, $f(0, n) = 0$, $f(m, 0) = 0$.
-%   \item 2d partial injections, depth 2. Exactly the same circuit as for injections but with base case $f(m, 0) = 1$.
-% \end{itemize}
-
 \section{Conclusion and Future Work}
@@
 supplements \textsc{ForcLift} \citep{DBLP:conf/ijcai/BroeckTMDR11} with three
-new compilation rules and a hybrid search algorithm. In \cref{sec:results}, we
-saw examples of instances that become liftable not just in theory
-\citep{DBLP:journals/jair/Kuzelka21} but with an implemented algorithm as well.
-However, our experiments cover only a small set of instances since some parts of
-\textsc{Crane} are yet to be fully automated. Specifically, our experiments
-focus on various function-counting problems---it remains to be seen what other
-types of instances become liftable as a result.
-
-% An idea pivotal to our work is the generalisation of circuits to graphs. Despite
-% the wide variety of circuits that are used in artificial intelligence
-% \citep{DBLP:series/faia/Darwiche21}, this is the first time that the addition of
-% cycles is shown to make a class of circuits more powerful. An important strand
-% for future work is in developing an algorithm that learns FCGs from data
-% similarly to the way \textsc{ForcLift} has been utilised in learning Markov
-% logic networks \citep{DBLP:conf/aaai/BroeckMD13,DBLP:journals/ml/HaarenBMD16}.
-% One could also consider whether some of the many recent applications of circuits
-% are suitable for FCGs as well. These applications include the verification and
-% explainability of neural networks \citep{DBLP:conf/pods/Darwiche20}, causal
-% inference \citep{https://doi.org/10.48550/arxiv.2202.02891}, computing the
-% expectations of kernel functions \citep{DBLP:conf/uai/LiZVB21}, and variational
-% inference in discrete graphical models \citep{DBLP:conf/nips/ShihE20}.
+new compilation rules and a hybrid search algorithm. The experiments in
+\cref{sec:results} revealed a range of counting problems that are liftable to
+\textsc{Crane} but not to any other (W)FOMC algorithm. The common thread across
+these newly liftable problems is (partial) injectivity. Thus, we can formulate
+the following conjecture.
+
+\begin{conjecture}
+  Let \IFO{} be the class of formulas in FOL that contain clauses with at most
+  two variables as well as any number of copies
+  \begin{align*}
+    &\begin{multlined}[t]
+      (\forall X \in \Gamma\text{. }\forall Y, Z \in \Delta\text{. }\\
+      Y \ne Z \implies \neg p(X, Y) \lor \neg p(X, Z)) \land
+    \end{multlined}\\
+    &\begin{multlined}[t]
+      (\forall X, Z \in \Gamma\text{. }\forall Y \in \Delta\text{. }\\
+      X \ne Z \implies \neg p(X, Y) \lor \neg p(Z, Y)).
+    \end{multlined}
+  \end{align*}
+  for some predicate $p$ and domains $\Gamma$ and $\Delta$. Then \IFO{} is
+  liftable by \textsc{Crane}.
+\end{conjecture}
+
+Since the tasks of counting injections and bijections fall into the \Ctwo{}
+fragment as well, we can formulate an even stronger conjecture.
+
+\begin{conjecture}
+  \Ctwo{} is liftable by \textsc{Crane} by either reformulating formulas in
+  \Ctwo{} to avoid counting quantifiers or extending \textsc{Crane} to support
+  them.
+\end{conjecture}
 
@@
 system. Third, most importantly, we need a way to find the base cases for the
-recursive definitions provided by \textsc{Crane}. What makes this problem
-non-trivial is that the number of base cases is not constant for functions of
-arity greater than one (i.e., formulas that mention more than one domain). On
-the other hand, assuming that a domain is empty can greatly simplify a problem.
-Fourth, since the first solution found by \textsc{Crane} is not always optimal
-in terms of its complexity, an automated way to determine the asymptotic
-complexity of a solution would be helpful as well. Achieving these goals would
-make \textsc{Crane} capable of automatically constructing efficient ways to
-compute a function (e.g., a sequence) of interest. In addition to the potential
-impact to areas of artificial intelligence (AI) such as statistical relational
-AI \citep{DBLP:series/synthesis/2016Raedt}, \textsc{Crane} could be beneficial
-to research in combinatorics as well \citep{DBLP:conf/ilp/BarvinekB0ZK21}.
+recursive definitions provided by \textsc{Crane}. Fourth, since the first
+solution found by \textsc{Crane} is not always optimal in terms of its
+complexity, an automated way to determine the asymptotic complexity of a
+solution would be helpful as well. Achieving these goals would make
+\textsc{Crane} capable of automatically constructing efficient ways to compute a
+function (e.g., a sequence) of interest. In addition to the potential impact to
+areas of artificial intelligence (AI) such as statistical relational AI
+\citep{DBLP:series/synthesis/2016Raedt}, \textsc{Crane} could be beneficial to
+research in combinatorics as well \citep{DBLP:conf/ilp/BarvinekB0ZK21}.
 

### 2022-07-30 doc/paper/paper.tex
Some changes

@@
 
-\captionsetup[subfigure]{width=\linewidth}
 \usetikzlibrary{fit,positioning,trees,cd}
@@
 % 2. Why is it interesting and important?
-% 1) the latest first-order variable elimination algorithm \citep{DBLP:journals/jair/TaghipourFDB13}
-% 2) other approaches to lifted inference  \citep{DBLP:conf/uai/BrazO17,DBLP:conf/nips/JhaGMS10,DBLP:journals/ijar/RiguzziBZCL17}
-% 3) Unlike most early algorithms for lifted inference that were adaptations of probabilistic inference algorithms such as AND/OR search \citep{DBLP:conf/aaai/GogateD10} and variable elimination \citep{DBLP:conf/ijcai/BrazAR05,DBLP:conf/aaai/MilchZKHK08}, WFOMC is an approach grounded in logic.
 
@@
 
-TODO: remove the references to the figure.
-
 The main conceptual difference between \textsc{Crane} and \textsc{ForcLift} is
 that we utilise labelled directed graphs instead of circuits. The cycles in
-these graphs represent recursive calls. See \cref{fig:after} for an illustration
-of an example scenario. Suppose the original formula $\phi$ depends on a domain
-of size $n \in \mathbb{N}$. \emph{Generalised domain recursion} (GDR), one of
-the new compilation rules, transforms $\phi$ into a different formula $\psi$
-that has an additional constant and some new \emph{constraints}. After some
-additional transformations, the constraints in $\psi$ become `uniform' and can
-be removed, replacing the domain of size $n$ with a new domain of size
-$n-1$---this is the responsibility of the \emph{constraint removal} (CR)
+these graphs represent recursive calls. Suppose the input formula $\phi$ depends
+on a domain of size $n \in \mathbb{N}$. \emph{Generalised domain recursion}
+(GDR), one of the new compilation rules, transforms $\phi$ into a different
+formula $\psi$ that has an additional constant and some new \emph{constraints}.
+After some additional transformations, the constraints in $\psi$ become
+`uniform' and can be removed, replacing the domain of size $n$ with a new domain
+of size $n-1$---this is the responsibility of the \emph{constraint removal} (CR)
 compilation rule. Afterwards, another new compilation rule recognizes that the
@@
 refers to a different domain. This observation allows us to add a cycle-forming
-edge to the graph (highlighted in blue in \cref{fig:after}), which can be
-interpreted as function $f$ relying on $f(n-1)$ to compute $f(n)$. To construct
-such graphs, we also introduce a novel search algorithm that replaces the greedy
-search used by \textsc{ForcLift}.
+edge to the graph, which can be interpreted as function $f$ relying on $f(n-1)$
+to compute $f(n)$.
 
@@
 
-\Cref{sec:recprelims} defines the representation used for sentences in FOL as
-well as discuss caching and some notational conventions. At the beginning of
-\cref{sec:methods}, we formally define the graphs that replace circuits in
-representing a solution to a (W)FOMC problem and discuss some related notions.
-\Cref{sec:rules} introduces the new compilation rules. \Cref{sec:search} then
-describes our new search algorithm that makes fewer assumptions than
-\textsc{ForcLift} about the right order in which compilation rules should be
-applied. In \cref{sec:interpret}, we discuss how a graph can be interpreted as a
-collection of (potentially recursive) functions. Finally, in \cref{sec:results}
-we compare \textsc{ForcLift} and \textsc{Crane} on a range of function-counting
-problems. We show that \textsc{Crane} performs as well as \textsc{ForcLift} on
-the instances that were already solvable by \textsc{ForcLift} but is also able
-to handle most of the instances that \textsc{ForcLift} fails on.
+We begin by defining the representation used for sentences in FOL in
+\cref{sec:recprelims}. Then, in \cref{sec:methods}, we define the graphs that
+replace circuits in representing a solution to a (W)FOMC problem.
+\Cref{sec:rules} introduces the new compilation rules. In \cref{sec:interpret},
+we discuss how a graph can be interpreted as a collection of (potentially
+recursive) functions. In \cref{sec:results}, we compare \textsc{ForcLift} and
+\textsc{Crane} on a range of function-counting problems. We show that
+\textsc{Crane} performs as well as \textsc{ForcLift} on the instances that were
+already solvable by \textsc{ForcLift} but is also able to handle most of the
+instances that \textsc{ForcLift} fails on. Finally, in \cref{sec:conclusion}, we
+conclude by outlining some conjectures and directions for future work.
 
 \section{Preliminaries}\label{sec:recprelims}
-
-In this section, we describe our format for FOMC instances, introduce some
-notation, and discuss our caching scheme, which is used to identify
-possibilities for a recursive call. Note that although the focus of this paper
-is on unweighted model counting, \textsc{ForcLift}'s
-\citep{DBLP:conf/ijcai/BroeckTMDR11} support for weights trivially transfers to
-\textsc{Crane} as well.
 
@@
 
-% , and \cref{sec:search} outlines the hybrid search algorithm
-% that replaces the greedy search used by \textsc{ForcLift}
-% \citep{DBLP:conf/ijcai/BroeckTMDR11}.
-
-% TODO: update (and other references to sections, i.e., the beginning of each
-% section and the end of the introduction)
-We begin this section by formally defining the graphs that \textsc{Crane} uses
-as a generalisation of circuits. Then, \cref{sec:rules} describes three new
-compilation rules.
-
 \begin{figure}[t]
@@
   imposing an ordering on outgoing edges is just a limited version of edge
-  labelling.} We denote an FCG as $G = (V, s, N^+, \tau)$, where $V$ is the set
-of nodes, and $s \in V$ is the unique source. Function $N^+$ maps each node in
-$V$ to a \emph{list} of its direct successors. Node labels consist of two parts:
-the \emph{type} and the \emph{parameters}. To avoid clutter, we leave the
-parameters implicit and let $\tau$ denote the node-labelling function that maps
-each node in $V$ to its type. For each node $v \in V$, the length of list
-$N^+(v)$ (i.e., the out-degree of $v$) is determined by its type $\tau(v)$. Most
-of the types are as in previous work
+  labelling.} Node labels consist of two parts: the \emph{type} and the
+\emph{parameters}. The out-degree of each node is determined by its type.
+Similarly to \citet{DBLP:conf/ijcai/BroeckTMDR11}, we write $T_p$ for an FCG
+that has a node with label $T_p$ (i.e., type $T$ and parameter(s) $p$) and
+$\star$'s as all of its direct successors.
+
+Most of the types are as in previous work
 \citep{DBLP:conf/nips/Broeck11,DBLP:conf/ijcai/BroeckTMDR11}. The type for
@@
 labels directly on the nodes, and omit irrelevant labels and/or parameters. See
-\cref{fig:examplefcg} for an example FCG\@. Its source node has out-degree 1
-(i.e., $|N^+(s)| = 1$), label
-$\GDR_{\Gamma \gets \Gamma \setminus \{\, x \,\}}$, and type $\GDR$ (i.e.,
-$\tau(s) = \GDR$).
+\cref{fig:examplefcg} for an example FCG\@. Its source node has out-degree 1,
+label $\GDR_{\Gamma \gets \Gamma \setminus \{\, x \,\}}$, and type $\GDR$.
 
-%\paragraph*{Notation.}
-Similarly to \citet{DBLP:conf/ijcai/BroeckTMDR11}, we write $T_p$ for an FCG
-that has a node with label $T_p$ (i.e., type $T$ and parameter(s) $p$) and
-$\star$'s as all of its direct successors. In particular, as an FCG, $\star$
-denotes
-$(\{\, s \,\}, s, \{\, s \mapsto \langle\rangle \,\}, \{\, s \mapsto \star \,\})$,
-i.e., an FCG with just one node of type $\star$ and no edges. We write $T_p(v)$
-for an FCG with one edge from a node labelled $T_{p}$ to some other node $v$
-(and no other nodes or edges).
-
-\begin{figure}[t]
-  \centering
-  \begin{subfigure}{0.49\linewidth}
-    \centering
-    \begin{tikzpicture}[edge from parent/.style={draw,-Latex}]
-      \node[draw,circle,label={[text=blue]1}] (top) {}
-      child {
-        node[draw,circle,label={[text=blue,xshift=-1mm]2}] {}
-        child {node[draw,ellipse] (ref) {$\Reff$}}
-        child {node[draw,circle,label={[text=blue,xshift=1mm,yshift=-1mm]3}] {$\star$}}
-      }
-      child {node[draw,circle,label={[text=blue,xshift=1mm,yshift=-1mm]4}] {$\star$}};
-      \draw[-Latex] (ref) to [bend left=45] (top);
-    \end{tikzpicture}
-    \caption{An example FCG}\label{fig:smallexample1}
-  \end{subfigure}
-  \begin{subfigure}{0.49\linewidth}
-    \centering
-    \begin{tikzpicture}[edge from parent/.style={draw,-Latex}]
-      \node[draw,circle,label={[text=blue]1}] (top) {}
-      child {
-        node[draw,circle,label={[text=blue,xshift=-1mm]2}] {}
-        child {node[draw,circle,label={[text=blue,xshift=2mm,yshift=-1mm]3}] {$\star$}}
-      }
-      child {node[draw,circle,label={[text=blue,xshift=1mm,yshift=-1mm]4}] {$\star$}};
-    \end{tikzpicture}
-    \caption{The underlying tree of
-      \cref{fig:smallexample1}}\label{fig:smallexample2}
-  \end{subfigure}
-  \caption{An FCG and its underlying tree. The integers in blue denote the
-    pre-order traversal of the underlying tree.}\label{fig:ordering}
-\end{figure}
-
-%\paragraph*{Connecting FCGs with formulas.}
+% Connecting FCGs with formulas
 Finally, we introduce a structure that represents a solution to a (W)FOMC
@@
 contains formulas that still need to be compiled. Once a formula is compiled, it
-replaced one of the $\star$'s in $G$. We say that an FCG is \emph{complete}
-(i.e., it represents a \emph{complete solution}) if it has no $\star$'s.
-Similarly, a chip is complete if its FCG is complete (or, equivalently, the list
-of formulas is empty). Let the \emph{underlying tree} of $G$ be the induced
-subgraph of $G$ that omits all $\Reff$ nodes.\footnote{Subsequently presented
-  algorithms ensure that the underlying tree is guaranteed to be a tree.} Then
-we can define an implicit bijection between the formulas in $L$ and the
-$\star$'s in $G$ according to the order in which elements of $L$ are listed and
-the pre-order traversal of the underlying tree of $G$. For example, if $G$ is as
-in \cref{fig:smallexample1} (with its underlying tree in
-\cref{fig:smallexample2}), then $|L| = 2$. Moreover, the first element of $L$ is
-associated with the $\star$ labelled 3, and the second with the one labelled 4.
+replaced one of the $\star$'s in $G$ according to a set order. We say that an
+FCG is \emph{complete} (i.e., it represents a \emph{complete solution}) if it
+has no $\star$'s. Similarly, a chip is complete if its FCG is complete (or,
+equivalently, the list of formulas is empty).
 
@@
 
-% TODO: do I still need the definition of a chip? What about tau?
-
 \section{How to Interpret an FCG}\label{sec:interpret}
@@
 
-\section{Conclusion and Future Work}
+\section{Conclusion and Future Work}\label{sec:conclusion}
 
@@
 supplements \textsc{ForcLift} \citep{DBLP:conf/ijcai/BroeckTMDR11} with three
-new compilation rules and a hybrid search algorithm. The experiments in
-\cref{sec:results} revealed a range of counting problems that are liftable to
-\textsc{Crane} but not to any other (W)FOMC algorithm. The common thread across
-these newly liftable problems is (partial) injectivity. Thus, we can formulate
-the following conjecture.
+new compilation rules. The experiments in \cref{sec:results} revealed a range of
+counting problems that are liftable to \textsc{Crane} but not to any other
+(W)FOMC algorithm. Although here we focused on FOMC problems,
+\textsc{ForcLift}'s support for weights trivially transfers to \textsc{Crane} as
+well. The common thread across these newly liftable problems is (partial)
+injectivity. Thus, we can formulate the following conjecture.
 

### 2022-07-31 doc/paper/paper.tex
Initial version of a truncated section

@@
 \SetKwFunction{constructDomainMap}{constructDomainMap}
-\SetKwFunction{identifyRecursion}{identifyRecursion}
-\SetKwFunction{generateMaps}{generateMaps}
+\SetKwFunction{identifyRecursion}{r}
+\SetKwFunction{generateMaps}{genMaps}
 \SetKwFunction{mergeFcgs}{mergeFcgs}
@@
   cycles. To this end, we enhance the most well-established (weighted) FOMC
-  algorithm ForcLift with new compilation rules and an algorithm to check
-  whether a recursive call is feasible. These improvements allow us to find
-  efficient solutions to counting fundamental structures such as injections and
-  bijections.
+  algorithm \textsc{ForcLift} with new compilation rules and an algorithm to
+  check whether a recursive call is feasible. These improvements allow us to
+  find efficient solutions to counting fundamental structures such as injections
+  and bijections.
 \end{abstract}
@@
 
-TODO: write a short informal summary. Add the full info as an appendix and
-reference it.
+% TODO: will need to explain: hashing, caching, how the output of genMaps is filtered
+
+\paragraph*{Notation.}
+First, for partial functions $\alpha, \beta\colon A \pfun B$ s.t.
+$\alpha|_{\dom(\alpha) \cap \dom(\beta)} = \beta|_{\dom(\alpha) \cap \dom(\beta)}$,
+we write $\alpha \cup \beta$ for the unique partial function s.t.
+$\alpha \cup \beta|_{\dom(\alpha)} = \alpha$, and
+$\alpha \cup \beta|_{\dom(\beta)} = \beta$. Second, let $\Doms$ be a function
+that maps any clause or formula to the set of domains used within. Specifically,
+$\Doms(c) \coloneqq \Imm \delta_c$ for any clause $c$, and
+$\Doms(\phi) \coloneqq \bigcup_{c \in \phi} \Doms(c)$ for any formula $\phi$.
+
+\begin{algorithm}[t]
+  \caption{The compilation rule for $\Reff$ nodes.}\label{alg:trycache}
+  \KwIn{formula $\phi$, cache $C$}
+  \KwOut{a set of chips}
+
+  \ForEach{formula and node $(\psi, v) \in C(\#\phi)$}{
+    $\rho \gets \identifyRecursion{$\phi$, $\psi$}$\;
+    \lIf{$\rho \ne {\normalfont \texttt{null}}$}{\Return{$\{\, (\Reff_\rho(v), \langle\rangle) \,\}$}}
+  }
+  \Return{$\emptyset$}\;
+
+  \Fn{\identifyRecursion{$\phi$, $\psi$, $\rho = \emptyset$}}{
+    \lIf{$|\phi| \ne |\psi|$ {\bf or} $\#\phi \ne \#\psi$}{\Return{\normalfont\texttt{null}}}
+    \lIf{$\phi = \emptyset$}{\Return{$\rho$}}
+    \ForEach{clause $c \in \psi$\label{line:for1}}{
+      \ForEach{clause $d \in \phi$ s.t. $\#d=\#c$\label{line:for2}}{
+        \ForAll{$(\beta, \gamma) \in \generateMaps{$c$, $d$, $\rho$}$\label{line:generateMaps}}{
+          $\rho' \gets \identifyRecursion{$\phi\setminus\{\, d \,\}$, $\psi\setminus\{\, c \,\}$, $\rho\cup\gamma$}$\;\label{line:recursion}
+          \lIf{$\rho' \ne {\normalfont \texttt{null}}$}{\Return{$\rho'$}}
+        }
+      }
+      \Return{\normalfont\texttt{null}}\;
+    }
+  }
+\end{algorithm}
+
+% Cache $C$ is used to partition all previously-encountered formulas based on
+% their hash codes.
+\Cref{alg:trycache} describes the compilation rule for creating $\Reff$ nodes.
+For every formula $\psi$ s.t. $\#\psi = \#\phi$ that we have encountered so far,
+function \texttt{r} is called to check whether a recursive call
+is actually feasible. If it is, the function returns a (total) map
+$\rho\colon \Doms(\psi) \to \Doms(\phi)$ that shows how $\psi$ can be
+transformed into $\phi$ by replacing each domain $\Omega \in \Doms(\psi)$ with
+$\rho(\Omega) \in \Doms(\phi)$. Otherwise, \texttt{r} returns
+\texttt{null} to signify that $\phi$ and $\psi$ are too different for recursion
+to work. This happens if $\phi$ and $\psi$ (or their subformulas explored in
+recursive calls) are structurally different (i.e., the numbers of clauses or the
+hash codes fail to match) or if a clause of $\psi$ cannot be paired with a
+sufficiently similar clause of $\phi$.
+
+Function \texttt{r} iterates over pairs of clauses of $\phi$ and
+$\psi$ that have the same hash codes. It uses function \texttt{genMaps} to
+check whether the two clauses are sufficiently similar. If so, the function
+calls itself on the remaining clauses until the map
+$\rho\colon \Doms(\psi) \pfun \Doms(\phi)$ becomes total, and all clauses are
+successfully coupled.
+
+Given two clauses $c \in \psi$ and $d \in \phi$, \texttt{genMaps} considers
+all possible bijections\footnote{Although the number of bijections between two
+  sets of cardinality $n$ is $n!$, this part of the algorithm is unlikely to
+  cause performance issues for two reasons. First, in practice, $n$ is usually
+  at most two or three. Second, due to the manner in which formulas are modified
+  by compilation rules, if any bijection results in a successfully identified
+  recursive relationship, it is almost always the identity bijection.}
+$\beta\colon \Vars(c) \twoheadrightarrowtail \Vars(d)$ and calls
+\texttt{constructDomainMap}, which then attempts to construct a map
+$\gamma\colon \Doms(c) \to \Doms(d)$ consistent with both $\beta$ and (the as
+yet partial map) $\rho\colon \Doms(\psi) \pfun \Doms(\phi)$. The \textbf{yield}
+keyword in \texttt{genMaps} works as in programming languages such as C\#,
+JavaScript, and Python, and lazily returns a sequence of values, computing each
+element of the sequence as needed.
+
+Diagrammatically, \texttt{constructDomainMap} attempts to find a
+$\gamma\colon \Doms(c) \to \Doms(d)$ s.t.
+\begin{equation}\label[diagram]{eq:commute}
+  \begin{tikzcd}
+    V = \Vars(c) \ar[r, tail, two heads, "\beta"] \arrow[d, swap, "\delta_c"] & \Vars(d) \ar[d, "\delta_d"] \\
+    \Doms(c) \ar[r, dashed, "\gamma"] \ar[d, hookrightarrow] & \Doms(d) \ar[d, hookrightarrow] \\
+    \Doms(\psi) \ar[r, swap, "\rho", "|" marking, outer sep=5pt] & \Doms(\phi).
+  \end{tikzcd}
+\end{equation}
+commutes (and returns \texttt{null} if such a function does not exist). Indeed,
+for every variable in $V = \Vars(c)$, the function returns \texttt{null} if
+either the top rectangle from $V$ to $\Doms(d)$ or the outer rectangle from $V$
+to $\Doms(\phi)$ fails to commute. These checks also ensure that
+$\rho \cup \gamma$ is possible on \cref{line:recursion} of the algorithm, i.e.,
+$\rho|_{\dom(\rho)\cap\dom(\gamma)} = \gamma|_{\dom(\rho)\cap\dom(\gamma)}$.
+
+% \begin{example}\label{example}
+
+%   % definitions of formulas and intro
+%   As in \cref{example:first}, let $\psi \coloneqq \{\, c_1, c_2 \,\}$ be a
+%   formula with clauses
+%   \begin{align*}
+%     c_1 &= (\{\, \neg p(X, Y), \neg p(X, Z) \,\}, \{\, (Y, Z) \,\}, \{\, X \mapsto \Gamma, Y \mapsto \Delta, Z \mapsto \Delta \,\}), \\
+%     c_2 &= (\{\, \neg p(X, Y), \neg p(Z, Y) \,\}, \{\, (X, Z) \,\}, \{\, X \mapsto \Gamma, Y \mapsto \Delta, Z \mapsto \Gamma \,\}).
+%   \end{align*}
+%   Let formula
+%   $\phi \coloneqq \psi[\id, \{\, \Gamma \mapsto \Gamma', \Delta \mapsto \Delta^\bot \,\}]$
+%   be just like $\psi$ but with different domains. In other words,
+%   $\phi = \{\, d_1, d_2 \,\}$, where
+%   \begin{align*}
+%     d_1 &\coloneqq (\{\, \neg p(X, Y), \neg p(X, Z) \,\}, \{\, (Y, Z) \,\}, \{\, X \mapsto \Gamma', Y \mapsto \Delta^\bot, Z \mapsto \Delta^\bot \,\}),\\
+%     d_2 &\coloneqq (\{\, \neg p(X, Y), \neg p(Z, Y) \,\}, \{\, (X, Z) \,\}, \{\, X \mapsto \Gamma', Y \mapsto \Delta^\bot, Z \mapsto \Gamma' \,\}).
+%   \end{align*}
+%   Note that $\#\phi = \#\psi$ and assume that $(\psi, v) \in C(\#\phi)$ for some
+%   node $v$. We shall see how \cref{alg:trycache} identifies that the FCG for
+%   $\psi$ can be reused for $\phi$ as well.
+
+%   Since both formulas are non-empty, the algorithm proceeds with the for-loops
+%   on \cref{line:for1,line:for2,line:generateMaps}. Suppose $c = c_1$ and
+%   $d = d_1$ get picked. Since both clauses have three variables, in the worst
+%   case, function \texttt{genMaps} would have $3!=6$ bijections to check.
+%   Suppose the identity bijection is picked first. Then
+%   \texttt{constructDomainMap} is called with the following parameters:
+%   \begin{itemize}
+%     \item $V = \{\, X, Y, Z \,\}$,
+%     \item
+%           $\delta_c = \{\, X \mapsto \Gamma, Y \mapsto \Delta, Z \mapsto \Delta \,\}$,
+%     \item
+%           $\delta_d = \{\, X \mapsto \Gamma', Y \mapsto \Delta^\bot, Z \mapsto \Delta^\bot \,\}$,
+%     \item $\beta = \id = \{\, X \mapsto X, Y \mapsto Y, Z \mapsto Z \,\}$,
+%     \item $\rho = \emptyset$.
+%   \end{itemize}
+%   Since $\delta_c(Y) = \delta_c(Z)$, and $\delta_d(Y) = \delta_d(Z)$,
+%   \texttt{constructDomainMap} returns
+%   $\gamma = \{\, \Gamma \mapsto \Gamma', \Delta \mapsto \Delta^\bot \,\}$. Thus,
+%   \texttt{genMaps} yields its first pair of maps $(\beta, \gamma)$ to
+%   \cref{line:generateMaps}. Furthermore, this pair satisfies
+%   $c[\beta, \gamma] = d$. On \cref{line:recursion}, a recursive call to
+%   \texttt{r($\{\,c_2\,\}$, $\{\,d_2\,\}$, $\gamma$)} is made.
+
+%   In this subproblem where both formulas are left with a single clause each,
+%   again we have two non-empty formulas with equal hash codes. Thus
+%   \texttt{genMaps} is called with $c = c_2$, $d = d_2$, and
+%   $\rho = \{\, \Gamma \mapsto \Gamma', \Delta \mapsto \Delta^\bot \,\}$. Suppose
+%   \cref{line:bijection} picks the identity bijection gain. Then
+%   \texttt{constructDomainMap} is called with the following parameters:
+%   \begin{itemize}
+%     \item $V = \{\, X, Y, Z \,\}$,
+%     \item
+%           $\delta_c = \{\, X \mapsto \Gamma, Y \mapsto \Delta, Z \mapsto \Gamma \,\}$,
+%     \item
+%           $\delta_d = \{\, X \mapsto \Gamma', Y \mapsto \Delta^\bot, Z \mapsto \Gamma' \,\}$,
+%     \item $\beta = \id = \{\, X \mapsto X, Y \mapsto Y, Z \mapsto Z \,\}$,
+%     \item $\rho = \{\, \Gamma \mapsto \Gamma', \Delta \mapsto \Delta^\bot \,\}$.
+%   \end{itemize}
+%   Since $\beta$ and $\rho$ commute (as in \cref{eq:commute}), and there are no
+%   new domains in $\Doms(c)$ and $\Doms(d)$, $\gamma$ exists and is equal to
+%   $\rho$. Again, the returned pair $(\beta, \gamma)$ satisfies
+%   $c[\beta, \gamma] = d$. \Cref{line:recursion} calls
+%   \texttt{r($\emptyset$, $\emptyset$, $\rho$)}, which
+%   immediately returns
+%   $\rho = \{\, \Gamma \mapsto \Gamma', \Delta \mapsto \Delta^\bot \,\}$ as the
+%   final answer. Therefore, one can indeed reuse an FCG for $\psi$ to compute the
+%   model count of $\phi$.
+% \end{example}
 

### 2022-07-31 doc/paper/paper.tex
First draft of the complete paper

--- 2022-07-30 doc/paper/paper.tex
@@
   A \emph{formula} (called a c-theory by \citet{DBLP:conf/ijcai/BroeckTMDR11})
-  is a set of clauses such that all constraints and atoms `type check' with
-  respect to domains.
+  is a set of clauses s.t.\ all constraints and atoms `type check' with respect
+  to domains.
 \end{definition}
@@
 list with one element $x$, respectively, and $|l|$ to denote the length of list
-$l$. Let $S$ be a set of constraints or literals, $V$ a set of variables, and
-$x$ either a variable or a constant. We write $S[x/V]$ to denote $S$ with all
-occurrences of all variables in $V$ replaced with $x$.\footnote{Note that if
-  $(X, Y)$ is a two-variable constraint, substituting a constant $c$ for $X$
-  would result in $(c, Y)$, which would have to be rewritten as $(Y, c)$ to fit
-  the definition of a constraint.}
+$l$. We write $\pfun$ for partial functions. Let $S$ be a set of constraints or
+literals, $V$ a set of variables, and $x$ either a variable or a constant. We
+write $S[x/V]$ to denote $S$ with all occurrences of all variables in $V$
+replaced with $x$.\footnote{Note that if $(X, Y)$ is a two-variable constraint,
+  substituting a constant $c$ for $X$ would result in $(c, Y)$, which would have
+  to be rewritten as $(Y, c)$ to fit the definition of a constraint.}
 
@@
 problem while it is still being built. A \emph{chip} is a pair $(G, L)$, where
-$G$ is an FCG, and $L$ is a list of formulas, such that $|L|$ is equal to the
-number of $\star$'s in $G$. The intuition behind this definition is that $L$
-contains formulas that still need to be compiled. Once a formula is compiled, it
-replaced one of the $\star$'s in $G$ according to a set order. We say that an
-FCG is \emph{complete} (i.e., it represents a \emph{complete solution}) if it
-has no $\star$'s. Similarly, a chip is complete if its FCG is complete (or,
+$G$ is an FCG, and $L$ is a list of formulas, s.t. $|L|$ is equal to the number
+of $\star$'s in $G$. The intuition behind this definition is that $L$ contains
+formulas that still need to be compiled. Once a formula is compiled, it replaced
+one of the $\star$'s in $G$ according to a set order. We say that an FCG is
+\emph{complete} (i.e., it represents a \emph{complete solution}) if it has no
+$\star$'s. Similarly, a chip is complete if its FCG is complete (or,
 equivalently, the list of formulas is empty).
@@
           \begin{multlined}[t]
-            (\{\, \neg p(X, Y), \neg p(Z, Y) \,\}, \{\, (X, x), (Z, X), (Z, x) \,\}, \\
+            (\{\, \neg p(X, Y), \neg p(Z, Y) \,\}, \\
+            \{\, (X, x), (Z, X), (Z, x) \,\}, \\
             \{\, X \mapsto \Gamma, Y \mapsto \Delta^\bot, Z \mapsto \Gamma \,\}).
@@
 
-TODO: write a short informal summary. Add the full info as an appendix and
-reference it.
+Let $\Doms$ be a function that maps any clause or formula to the set of domains
+used within, and let $\dom(f)$ denote the domain of function $f$.
+
+We use (integer-valued) hash functions to efficiently discard pairs of formulas
+that are too different for recursion to be established. The hash code of a
+clause $c = (L, C, \delta_{c})$ (denoted by $\# c$) combines the hash codes of
+the sets of constants and predicates in $c$, the numbers of positive and
+negative literals, the number of inequality constraints $|C|$, and the number of
+variables $|\Vars(c)|$. The hash code of a formula $\phi$ combines the hash
+codes of all its clauses and is denoted by $\#\phi$.
+
+\citet{DBLP:conf/ijcai/BroeckTMDR11} use a cache to check if a formula is
+identical to one of the formulas that have already been fully compiled. In
+\textsc{Crane}, to facilitate recursion, we extend the caching scheme to include
+formulas that have been encountered but not fully compiled yet. Formally, we
+define a \emph{cache} to be a map from integers (e.g., hash codes) to sets of
+pairs of the form $(\phi, v)$, where $\phi$ is a formula, and $v$ is an FCG
+node.
+
+\begin{algorithm}[t]
+  \caption{The compilation rule for $\Reff$ nodes.}\label{alg:trycache}
+  \KwIn{formula $\phi$, cache $C$}
+  \KwOut{a set of chips}
+
+  \ForEach{formula and node $(\psi, v) \in C(\#\phi)$}{
+    $\rho \gets \identifyRecursion{$\phi$, $\psi$}$\;
+    \lIf{$\rho \ne {\normalfont \texttt{null}}$}{\Return{$\{\, (\Reff_\rho(v), \langle\rangle) \,\}$}}
+  }
+  \Return{$\emptyset$}\;
+
+  \Fn{\identifyRecursion{formula $\phi$, formula $\psi$, map $\rho = \emptyset$}}{
+    \lIf{$|\phi| \ne |\psi|$ {\bf or} $\#\phi \ne \#\psi$}{\Return{\normalfont\texttt{null}}}
+    \lIf{$\phi = \emptyset$}{\Return{$\rho$}}
+    \ForEach{clause $c \in \psi$\label{line:for1}}{
+      \ForEach{clause $d \in \phi$ s.t. $\#d=\#c$\label{line:for2}}{
+        \ForAll{$\gamma \in \generateMaps{$c$, $d$, $\rho$}$\label{line:generateMaps}}{
+          $\rho' \gets \identifyRecursion{$\phi\setminus\{\, d \,\}$, $\psi\setminus\{\, c \,\}$, $\rho\cup\gamma$}$\;\label{line:recursion}
+          \lIf{$\rho' \ne {\normalfont \texttt{null}}$}{\Return{$\rho'$}}
+        }
+      }
+      \Return{\normalfont\texttt{null}}\;
+    }
+  }
+\end{algorithm}
+
+% Cache $C$ is used to partition all previously-encountered formulas based on
+% their hash codes.
+\Cref{alg:trycache} describes the compilation rule for creating $\Reff$ nodes.
+For every formula $\psi$ in the cache s.t. $\#\psi = \#\phi$, function
+\texttt{r} is called to check whether a recursive call is feasible. If it is,
+\texttt{r} returns a (total) map $\rho\colon \Doms(\psi) \to \Doms(\phi)$ that
+shows how $\psi$ can be transformed into $\phi$ by replacing each domain
+$\Omega \in \Doms(\psi)$ with $\rho(\Omega) \in \Doms(\phi)$. Otherwise,
+\texttt{r} returns \texttt{null} to signify that $\phi$ and $\psi$ are too
+different for recursion to work. This happens if $\phi$ and $\psi$ (or their
+subformulas explored in recursive calls) are structurally different (i.e., the
+numbers of clauses or the hash codes fail to match) or if a clause of $\psi$
+cannot be paired with a sufficiently similar clause of $\phi$. Function
+\texttt{r} works by iterating over pairs of clauses of $\phi$ and $\psi$ that
+have the same hash codes. For every pair of clauses that are sufficiently
+similar, \texttt{r} calls itself on the remaining clauses until the map
+$\rho\colon \Doms(\psi) \pfun \Doms(\phi)$ becomes total, and all clauses are
+successfully coupled.
+
+The compatibility of two clauses is checked by function \texttt{genMaps}. It
+considers every possible bijection $\beta\colon \Vars(c) \to \Vars(d)$ and map
+$\gamma\colon \Doms(c) \to \Doms(d)$ s.t.
+\[
+  \begin{tikzcd}
+    \Vars(c) \ar[r, dashed, "\beta"] \arrow[d, swap, "\delta_c"] & \Vars(d) \ar[d, "\delta_d"] \\
+    \Doms(c) \ar[r, dashed, "\gamma"] \ar[d, hookrightarrow] & \Doms(d) \ar[d, hookrightarrow] \\
+    \Doms(\psi) \ar[r, swap, "\rho", "|" marking, outer sep=5pt] & \Doms(\phi).
+  \end{tikzcd}
+\]
+commutes, and $c$ becomes equal to $d$ when its variables are replaced according
+to $\beta$ and its domains replaced according to $\gamma$. The function then
+returns each such $\gamma$ as soon as possible. The commutativity check also
+ensures that $\rho \cup \gamma$ is possible on \cref{line:recursion} of
+\cref{alg:trycache}. The resulting (partial) function $\rho \cup \gamma$ is the
+unique function s.t. $\rho \cup \gamma|_{\dom(\rho)} = \rho$, and
+$\rho \cup \gamma|_{\dom(\gamma)} = \gamma$. The operation is defined when
+$\rho|_{\dom(\rho)\cap\dom(\gamma)} = \gamma|_{\dom(\rho)\cap\dom(\gamma)}$.
 

### 2022-08-01 doc/paper/paper.tex
Clean up packages & commands
Improve wording

@@
 \usepackage{amsthm}
-\usepackage{mathrsfs}
-\usepackage{amsfonts}
 \usepackage{amssymb}
@@
 \usepackage{colortbl}
-\usepackage{subcaption}
-\usepackage[inline,shortlabels]{enumitem}
 \usepackage{complexity}
@@
 
-\usetikzlibrary{fit,positioning,trees,cd}
+\usetikzlibrary{cd}
 \usetikzlibrary{shapes}
-\usetikzlibrary{arrows}
-\usetikzlibrary{arrows.meta}
-\newcommand{\crefrangeconjunction}{--}
+
 \crefname{algocf}{algorithm}{Algorithms}
 \Crefname{algocf}{Algorithm}{Algorithms}
+
+\newcommand{\crefrangeconjunction}{--}
 \newcommand\pfun{\mathrel{\ooalign{\hfil$\mapstochar\mkern5mu$\hfil\cr$\to$\cr}}}
-\newcommand\mdoubleplus{\mathbin{+\mkern-10mu+}}
-\newcommand*{\twoheadrightarrowtail}{\mathrel{\rightarrowtail\kern-1.9ex\twoheadrightarrow}}
 \newcommand{\cmark}{\ding{51}}%
@@
 \DeclareMathOperator{\GDR}{\textsc{GDR}}
-\DeclareMathOperator{\IE}{\textsc{IE}}
 \DeclareMathOperator{\Reff}{\textsc{Ref}}
-\DeclareMathOperator{\wwp}{w}
-\DeclareMathOperator{\wwn}{\overline{w}}
 \DeclareMathOperator{\dom}{dom}
-\DeclareMathOperator{\id}{id}
-\DeclareMathOperator{\Imm}{Im}
 \DeclareMathOperator{\Doms}{Doms}
-\DeclareMathOperator{\size}{\sigma}
 \DeclareMathOperator{\Vars}{Vars}
-\DeclareMathOperator{\WMC}{WMC}
-\DeclareMathOperator{\gr}{gr}
-\DeclareMathOperator{\leftlsquigarrow}{\text{\reflectbox{$\rightsquigarrow$}}}
-\SetKw{KwRet}{yield}
 \SetKwProg{Fn}{Function}{:}{}
-\SetKwFunction{applyAllRules}{applyAllRules}
-\SetKwFunction{applyGreedyRules}{applyGreedyRules}
-\SetKwFunction{applyGreedyRulesToFormulas}{applyGreedyRulesToFormulas}
-\SetKwFunction{emptyy}{empty}
-\SetKwFunction{get}{get}
-\SetKwFunction{put}{put}
-\SetKwFunction{constructDomainMap}{constructDomainMap}
 \SetKwFunction{identifyRecursion}{r}
 \SetKwFunction{generateMaps}{genMaps}
-\SetKwFunction{mergeFcgs}{mergeFcgs}
-\SetKwFunction{updateCache}{updCache}
-\newtheorem{assumption}{Assumption}
 \newtheorem{conjecture}{Conjecture}
-\newtheorem{constraint}{Constraint}
-\newtheorem{fact}{Fact}
-\newtheorem{proposition}{Proposition}
-\newtheorem{theorem}{Theorem}
-\newtheorem{lemma}{Lemma}
 \theoremstyle{definition}
@@
 \newtheorem{example}{Example}
-\newtheorem{experiment}{Experiment}
-\theoremstyle{remark}
-\newtheorem*{remark}{Remark}
 \makeatletter
@@
 \Crefname{algocf}{Algorithm}{Algorithms}
-\Crefname{constraint}{Constraint}{Constraints}
-\Crefname{experiment}{Experiment}{Experiments}
-\Crefname{clause}{Clause}{Clauses}
-\Crefname{diagram}{Diagram}{Diagrams}
 \crefname{line}{line}{lines}
@@
 ways. \Citet{DBLP:conf/ilp/BarvinekB0ZK21} use WFOMC to generate numerical data
-which is then used to conjecture recurrence relations that explain that data.
+that is then used to conjecture recurrence relations that explain that data.
 \Citet{DBLP:conf/nips/Broeck11} introduced the idea of \emph{domain recursion}.
@@
   also an intermediate stage called \emph{smoothing} that takes place between
-  compilation and evaluation. As our changes to smoothing are quite elementary,
+  compilation and evaluation. As our changes to smoothing are rather elementary,
   we do not discuss them to not distract the reader from the main contributions
@@
 internally by \textsc{ForcLift}, some aspects of which are described by
-\citet{DBLP:conf/ijcai/BroeckTMDR11}. \textsc{ForcLift} is able to translate
-sentences in a variant of function-free many-sorted FOL with equality to this
-internal format. An \emph{atom} is $p(t_1, \dots, t_n)$ for some predicate $p$
-and terms $t_{1}, \dots, t_{n}$. Here, $n \in \mathbb{N}_0$ is the \emph{arity}
-of $p$. A \emph{term} is either a constant or a variable. A \emph{literal} is
-either an atom or the negation of an atom (denoted by
-$\neg p(t_1, \dots, t_n)$). Let $\mathcal{D}$ be the set of all domains.
-Initially, $\mathcal{D}$ contains all domains mentioned by the input (W)FOMC
-instance. During compilation, new domains added to $\mathcal{D}$ by some of the
-compilation rules.
+\citet{DBLP:conf/ijcai/BroeckTMDR11}. \textsc{ForcLift} can translate sentences
+in a variant of function-free many-sorted FOL with equality to this internal
+format. An \emph{atom} is $p(t_1, \dots, t_n)$ for some predicate $p$ and terms
+$t_{1}, \dots, t_{n}$. Here, $n \in \mathbb{N}_0$ is the \emph{arity} of $p$. A
+\emph{term} is either a constant or a variable. A \emph{literal} is either an
+atom or the negation of an atom (denoted by $\neg p(t_1, \dots, t_n)$). Let
+$\mathcal{D}$ be the set of all domains. Initially, $\mathcal{D}$ contains all
+domains mentioned by the input (W)FOMC instance. During compilation, new domains
+are added to $\mathcal{D}$ by some of the compilation rules.
 
@@
   variables (in both clauses) that occur as the first argument to $p$ are in
-  $\Gamma$, and likewise all variables that occur as the second argument to $p$
-  are in $\Delta$. Therefore, $\phi$ `type checks' as a valid formula.
+  $\Gamma$, and, likewise, all variables that occur as the second argument to
+  $p$ are in $\Delta$. Therefore, $\phi$ `type checks' as a valid formula.
 \end{example}
@@
 
-One can read a formula as in \cref{def:formula} as a sentence in a FOL\@. All
+One can read a formula from \cref{def:formula} as a sentence in a FOL\@. All
 variables in a clause are implicitly universally quantified (but note that
 variables are never shared among clauses), and all clauses in a formula are
-implicitly linked by conjunction. Thus, formula $\phi$ from \cref{example:first}
-reads as
+implicitly linked by a conjunction. Thus, formula $\phi$ from
+\cref{example:first} reads as
 \begin{align*}
@@
 We write $\langle\rangle$ and $\langle x \rangle$ to denote an empty list and a
-list with one element $x$, respectively, and $|l|$ to denote the length of list
-$l$. We write $\pfun$ for partial functions. Let $S$ be a set of constraints or
-literals, $V$ a set of variables, and $x$ either a variable or a constant. We
-write $S[x/V]$ to denote $S$ with all occurrences of all variables in $V$
-replaced with $x$.\footnote{Note that if $(X, Y)$ is a two-variable constraint,
+list with one element $x$, respectively, and $|l|$ for the length of list $l$.
+We write $\pfun$ for partial functions. Let $S$ be a set of constraints or
+literals, $V$ a set of variables, and $x$ a variable or a constant. We write
+$S[x/V]$ to denote $S$ with all occurrences of all variables in $V$ replaced
+with $x$.\footnote{Note that if $(X, Y)$ is a two-variable constraint,
   substituting a constant $c$ for $X$ would result in $(c, Y)$, which would have
@@
     one. Some of these nodes play an important role in the weighted version of
-    the problem whereas others are remnants of the interaction between
+    the problem, whereas others are remnants of the interaction between
     compilation rules and the way in which \textsc{ForcLift} handles existential
@@
   labelling.} Node labels consist of two parts: the \emph{type} and the
-\emph{parameters}. The out-degree of each node is determined by its type.
-Similarly to \citet{DBLP:conf/ijcai/BroeckTMDR11}, we write $T_p$ for an FCG
-that has a node with label $T_p$ (i.e., type $T$ and parameter(s) $p$) and
-$\star$'s as all of its direct successors.
-
-Most of the types are as in previous work
+\emph{parameters}. The type of a node determines its out-degree. Similarly to
+\citet{DBLP:conf/ijcai/BroeckTMDR11}, we write $T_p$ for an FCG that has a node
+with the label $T_p$ (i.e., type $T$ and parameter(s) $p$) and $\star$'s as all
+of its direct successors.
+
+Most node types are as in previous work
 \citep{DBLP:conf/nips/Broeck11,DBLP:conf/ijcai/BroeckTMDR11}. The type for
@@
 of $\star$'s in $G$. The intuition behind this definition is that $L$ contains
-formulas that still need to be compiled. Once a formula is compiled, it replaced
+formulas that still need to be compiled. Once a formula is compiled, it replaces
 one of the $\star$'s in $G$ according to a set order. We say that an FCG is
@@
 attempt to not miss a solution, \textsc{Crane} returns them all. In particular,
-if a rule returns an empty set, then that rule is not applicable to the formula,
+if a rule returns an empty set, then that rule does not apply to the formula,
 and the algorithm continues with the next rule.
@@
   \Cref{line:conditions} iterates over all subsets $W \subseteq V$ of variables
-  that can be replaced by a constant without resulting in formulas that are
-  evidently unsatisfiable. We impose two restrictions on $W$. First,
+  that can be replaced by a constant without resulting in evidently
+  unsatisfiable formulas. We impose two restrictions on $W$. First,
   $W^2 \cap C = \emptyset$ ensures that there are no pairs of variables in $W$
-  that are constrained to be distinct, since that would result in a $x \ne x$
+  that are constrained to be distinct, since that would result in an $x \ne x$
   constraint after substitution. Similarly, we want to avoid variables in $W$
-  that have inequality constraints with constants: after substitution, such
+  that have inequality constraints with constants: after the substitution, such
   constraints would transform into inequality constraints between two constants.
@@
   \end{align*}
-  Domain $\Gamma$ and with its element $x \in \Gamma$ satisfy the preconditions
-  for CR\@. The rule introduces a new domain $\Gamma'$ and transforms $\phi$ to
+  Domain $\Gamma$ and its element $x \in \Gamma$ satisfy the preconditions for
+  CR\@. The rule introduces a new domain $\Gamma'$ and transforms $\phi$ to
   $\phi' = (c_1', c_2', c_3')$, where
@@
 \citet{DBLP:conf/ijcai/BroeckTMDR11} use a cache to check if a formula is
-identical to one of the formulas that have already been fully compiled. In
-\textsc{Crane}, to facilitate recursion, we extend the caching scheme to include
-formulas that have been encountered but not fully compiled yet. Formally, we
-define a \emph{cache} to be a map from integers (e.g., hash codes) to sets of
-pairs of the form $(\phi, v)$, where $\phi$ is a formula, and $v$ is an FCG
-node.
+identical to one of the formulas that have already been fully compiled. To
+facilitate recursion, we extend the caching scheme to include formulas that have
+been encountered but not fully compiled yet. Formally, we define a \emph{cache}
+to be a map from integers (e.g., hash codes) to sets of pairs of the form
+$(\phi, v)$, where $\phi$ is a formula, and $v$ is an FCG node.
 
@@
 \texttt{r} works by iterating over pairs of clauses of $\phi$ and $\psi$ that
-have the same hash codes. For every pair of clauses that are sufficiently
-similar, \texttt{r} calls itself on the remaining clauses until the map
+have the same hash codes. For every pair of sufficiently similar clauses,
+\texttt{r} calls itself on the remaining clauses until the map
 $\rho\colon \Doms(\psi) \pfun \Doms(\phi)$ becomes total, and all clauses are
@@
 
-The compatibility of two clauses is checked by function \texttt{genMaps}. It
-considers every possible bijection $\beta\colon \Vars(c) \to \Vars(d)$ and map
-$\gamma\colon \Doms(c) \to \Doms(d)$ s.t.
+The compatibility of a pair of clauses is checked by function \texttt{genMaps}.
+It considers every possible bijection $\beta\colon \Vars(c) \to \Vars(d)$ and
+map $\gamma\colon \Doms(c) \to \Doms(d)$ s.t.
 \[
@@
   \end{align}
-  In order to use this recursive function to compute the model count of the
-  input formula for any domain sizes, one just needs to find the base cases
-  $f(0, n)$ and $f(m, 0)$ for all $m, n \in \mathbb{N}_{0}$.
+  To use this recursive function to compute the model count of the input formula
+  for any domain sizes, one just needs to find the base cases $f(0, n)$ and
+  $f(m, 0)$ for all $m, n \in \mathbb{N}_{0}$.
 \end{example}
@@
   tree has a high branching factor, so exploring all nodes at depth 5 takes at
-  most a few seconds whereas doing the same for depth 6 can be computationally
+  most a few seconds, whereas doing the same for depth 6 can be computationally
   infeasible in some cases.} If successful, \textsc{ForcLift} generates a
@@
 could already be solved by \textsc{ForcLift}, the two algorithms perform equally
-well. However, \textsc{Crane} is also able to solve all but one instances that
+well. However, \textsc{Crane} can also solve all but one instances that
 \textsc{ForcLift} fails on in at most cubic time.
@@
 
-However, the most important direction for future work is in fully automating
-this new way of computing the (W)FOMC of a formula. First, we need an algorithm
-that transforms FCGs into definitions of functions. Formalising this process
-would also allow us to prove the correctness of the new compilation rules in
+However, the most important direction for future work is to fully automate this
+new way of computing the (W)FOMC of a formula. First, we need an algorithm that
+transforms FCGs into definitions of functions. Formalising this process would
+also allow us to prove the correctness of the new compilation rules in
 constructing FCGs that indeed compute the right WMC\@. Second, these definitions
@@
 \textsc{Crane} capable of automatically constructing efficient ways to compute a
-function (e.g., a sequence) of interest. In addition to the potential impact to
+function (e.g., a sequence) of interest. In addition to the potential impact on
 areas of artificial intelligence (AI) such as statistical relational AI

### 2022-08-02 doc/paper/paper.tex
Minor changes

@@
 
+% in fact, the WFOMC algorithm by \citet{DBLP:conf/ijcai/BroeckTMDR11} can do so when it is unable to solve the instance in a lifted manner.
+
 \emph{First-order model counting} (FOMC) is the problem of computing the number
@@
 weighted sum across all models instead. By fixing the sizes of the domains, a
-WFOMC instance can be rewritten as a WMC instance---in fact, the WFOMC algorithm
-by \citet{DBLP:conf/ijcai/BroeckTMDR11} can do so when it is unable to solve the
-instance in a lifted manner. WFOMC emerged as the dominant approach to
-\emph{lifted (probabilistic) inference}. Lifted inference techniques exploit
-symmetries in probabilistic models by reasoning about sets rather than
+WFOMC instance can be rewritten as an instance of (propositional) weighted model
+counting \citep{DBLP:journals/ai/ChaviraD08}. WFOMC emerged as the dominant
+approach to \emph{lifted (probabilistic) inference}. Lifted inference techniques
+exploit symmetries in probabilistic models by reasoning about sets rather than
 individuals \citep{DBLP:conf/ecai/Kersting12}. By doing so, many instances
@@
 \emph{(domain-)liftable} if it can be solved in time polynomial in the size(s)
-of the domain(s) \citep{jaeger2012liftability}. Over more than a decade, more
-and more classes of instances were shown to be liftable
+of the domain(s) \citep{jaeger2012liftability}. Over more than a decade, many
+classes of instances were shown to be liftable
 \citep{DBLP:conf/kr/BremenK21,DBLP:conf/nips/KazemiKBP16,DBLP:conf/lics/KuusistoL18,DBLP:journals/jair/Kuzelka21}.
@@
 focused on developing faster solutions for the \FOtwo{} fragment
-\citep{DBLP:conf/uai/BremenK21,DBLP:conf/aaai/MalhotraS22} and defining
-new liftable fragments. These fragments include \SFO{} and \SRU{}
+\citep{DBLP:conf/uai/BremenK21,DBLP:conf/aaai/MalhotraS22} and defining new
+liftable fragments. These fragments include \SFO{} and \SRU{}
 \citep{DBLP:conf/nips/KazemiKBP16}, \Uone{} \citep{DBLP:conf/lics/KuusistoL18},
 \FOtwo{} with tree axioms \citep{DBLP:conf/kr/BremenK21}, and \Ctwo{} (i.e., the
-two variable fragment with counting quantifiers)
+two-variable fragment with counting quantifiers)
 \citep{DBLP:journals/jair/Kuzelka21,DBLP:conf/aaai/MalhotraS22}. On the
@@
 paper are implemented in \textsc{Crane}---an extension of the arguably most
-well-known WFOMC algorithm \textsc{ForcLift} written in Scala. \textsc{ForcLift}
-works in two stages: compilation and evaluation/propagation.\footnote{There is
-  also an intermediate stage called \emph{smoothing} that takes place between
+well-known WFOMC algorithm \textsc{ForcLift}. \textsc{ForcLift} works in two
+stages: compilation and evaluation/propagation.\footnote{There is also an
+  intermediate stage called \emph{smoothing} that takes place between
   compilation and evaluation. As our changes to smoothing are rather elementary,
   we do not discuss them to not distract the reader from the main contributions
-  of this paper.} In the first part, various \emph{(compilation) rules} are
+  of this paper.} In the first stage, various \emph{(compilation) rules} are
 applied to the input (or some derivative) formula, gradually constructing a
-circuit. In the second part, the weights of the instance (and sometimes
-constants) are propagated through the circuit, computing the WMC\@.
+circuit. In the second stage, the weights of the instance are propagated through
+the circuit, computing the weighted model count. Along with new compilation
+rules, \textsc{Crane} introduces changes to both stages of the process. First,
+while \textsc{ForcLift} applies compilation rules via greedy\footnote{The
+  algorithm is not described in any paper on \textsc{ForcLift} but can be found
+  in its source code at \url{https://dtai.cs.kuleuven.be/drupal/wfomc}} search,
+\textsc{Crane} uses a hybrid search algorithm that applies some rules greedily
+and some using breadth-first search. Second, the product of compilation is not
+directly evaluated but rather interpreted as a collection of functions on domain
+sizes.
 
@@
 The main conceptual difference between \textsc{Crane} and \textsc{ForcLift} is
-that we utilise labelled directed graphs instead of circuits. The cycles in
-these graphs represent recursive calls. Suppose the input formula $\phi$ depends
-on a domain of size $n \in \mathbb{N}$. \emph{Generalised domain recursion}
-(GDR), one of the new compilation rules, transforms $\phi$ into a different
-formula $\psi$ that has an additional constant and some new \emph{constraints}.
-After some additional transformations, the constraints in $\psi$ become
-`uniform' and can be removed, replacing the domain of size $n$ with a new domain
-of size $n-1$---this is the responsibility of the \emph{constraint removal} (CR)
-compilation rule. Afterwards, another new compilation rule recognizes that the
-resulting formula $\phi(n-1)$ is just like the input formula $\phi(n)$ except it
-refers to a different domain. This observation allows us to add a cycle-forming
-edge to the graph, which can be interpreted as function $f$ relying on $f(n-1)$
-to compute $f(n)$.
+that we utilise labelled directed graphs instead of circuits, where cycles
+represent recursive calls. Suppose the input formula $\phi$ depends on a domain
+of size $n \in \mathbb{N}$. \emph{Generalised domain recursion} (GDR)---one of
+the new compilation rules---transforms $\phi$ into a different formula $\psi$
+that has an additional constant and some new \emph{constraints}. After some
+additional transformations, the constraints in $\psi$ become `uniform' and can
+be removed, replacing the domain of size $n$ with a new domain of size
+$n-1$---this is the responsibility of the \emph{constraint removal} (CR)
+compilation rule. Afterwards, another compilation rule recognizes that the
+resulting formula is just like the input formula $\phi$ except it refers to a
+different domain. This observation allows us to add a cycle-forming edge to the
+graph, which can be interpreted as function $f$ relying on $f(n-1)$ to compute
+$f(n)$.
+
+% search
+% interpretation
 
@@
 format. An \emph{atom} is $p(t_1, \dots, t_n)$ for some predicate $p$ and terms
-$t_{1}, \dots, t_{n}$. Here, $n \in \mathbb{N}_0$ is the \emph{arity} of $p$. A
-\emph{term} is either a constant or a variable. A \emph{literal} is either an
-atom or the negation of an atom (denoted by $\neg p(t_1, \dots, t_n)$). Let
-$\mathcal{D}$ be the set of all domains. Initially, $\mathcal{D}$ contains all
-domains mentioned by the input (W)FOMC instance. During compilation, new domains
-are added to $\mathcal{D}$ by some of the compilation rules.
+$t_{1}, \dots, t_{n}$. A \emph{term} is either a constant or a variable. A
+\emph{literal} is either an atom or the negation of an atom (denoted by
+$\neg p(t_1, \dots, t_n)$). Let $\mathcal{D}$ be the set of all domains.
+Initially, $\mathcal{D}$ contains all domains mentioned by the input (W)FOMC
+instance. During compilation, new domains are added to $\mathcal{D}$ by some of
+the compilation rules.
 
@@
 elements in those sets, a formula can be viewed as a set of conditions that the
-predicates (interpreted as relations) have to satisfy.\footnote{If some domain
-  is not big enough to contain all of its constants, the formula is
-  unsatisfiable.} Hence, FOMC is the problem of counting the number of
-combinations of relations that satisfy these conditions.
+predicates (interpreted as relations) have to satisfy. Hence, FOMC is the
+problem of counting the number of combinations of relations that satisfy these
+conditions.
+
+% \footnote{If some domain is not big enough to contain all of its constants,
+% the formula is unsatisfiable.}
 
@@
 $S[x/V]$ to denote $S$ with all occurrences of all variables in $V$ replaced
-with $x$.\footnote{Note that if $(X, Y)$ is a two-variable constraint,
-  substituting a constant $c$ for $X$ would result in $(c, Y)$, which would have
-  to be rewritten as $(Y, c)$ to fit the definition of a constraint.}
+with $x$.\footnote{If $(X, Y)$ is a two-variable constraint, substituting a
+  constant $c$ for $X$ would result in $(c, Y)$, which would have to be
+  rewritten as $(Y, c)$ to fit the definition of a constraint.}
 
@@
     \citet{DBLP:conf/ijcai/BroeckTMDR11} for the descriptions of these node
-    types. Here we omit nodes whose only arithmetic effect is multiplication by
-    one. Some of these nodes play an important role in the weighted version of
-    the problem, whereas others are remnants of the interaction between
-    compilation rules and the way in which \textsc{ForcLift} handles existential
-    quantifiers.}\label{fig:examplefcg}
+    types. Here we omit some parameters as well as nodes whose only arithmetic
+    effect is multiplication by one. Some of these nodes play an important role
+    in the weighted version of the problem, whereas others are remnants of the
+    interaction between compilation rules and the way in which \textsc{ForcLift}
+    handles existential quantifiers.}\label{fig:examplefcg}
 \end{figure}
@@
   computational graph} (FCG) is a (weakly connected) directed graph with a
-single source, node labels, and ordered outgoing edges.\footnote{Note that
-  imposing an ordering on outgoing edges is just a limited version of edge
-  labelling.} Node labels consist of two parts: the \emph{type} and the
-\emph{parameters}. The type of a node determines its out-degree. Similarly to
-\citet{DBLP:conf/ijcai/BroeckTMDR11}, we write $T_p$ for an FCG that has a node
-with the label $T_p$ (i.e., type $T$ and parameter(s) $p$) and $\star$'s as all
-of its direct successors.
-
-Most node types are as in previous work
-\citep{DBLP:conf/nips/Broeck11,DBLP:conf/ijcai/BroeckTMDR11}. The type for
-non-tree-like edges (denoted by $\Reff$), while used before, is extended to
-contain the information necessary to support recursive calls. We also add three
-new types:
+single source, node labels, and ordered outgoing edges.\footnote{Imposing an
+  ordering on outgoing edges is just a limited version of edge labelling.} Node
+labels consist of two parts: the \emph{type} and the \emph{parameters}. The type
+of a node determines its out-degree.
+
+Along with many node types defined previously
+\citep{DBLP:conf/nips/Broeck11,DBLP:conf/ijcai/BroeckTMDR11}, \textsc{Crane}
+uses three more:
 \begin{itemize}
@@
 \end{itemize}
-When drawing an FCG, we order outgoing edges from left to right, write node
-labels directly on the nodes, and omit irrelevant labels and/or parameters. See
-\cref{fig:examplefcg} for an example FCG\@. Its source node has out-degree 1,
-label $\GDR_{\Gamma \gets \Gamma \setminus \{\, x \,\}}$, and type $\GDR$.
+Similarly to \citet{DBLP:conf/ijcai/BroeckTMDR11}, we write $T_p$ for an FCG
+that has a node with the label $T_p$ (i.e., type $T$ and parameter(s) $p$) and
+$\star$'s as all of its direct successors. See \cref{fig:examplefcg} for an
+example FCG\@. Its source node has out-degree 1, label
+$\GDR_{\Gamma \gets \Gamma \setminus \{\, x \,\}}$, and type $\GDR$.
 
@@
 $G$ is an FCG, and $L$ is a list of formulas, s.t. $|L|$ is equal to the number
-of $\star$'s in $G$. The intuition behind this definition is that $L$ contains
-formulas that still need to be compiled. Once a formula is compiled, it replaces
-one of the $\star$'s in $G$ according to a set order. We say that an FCG is
-\emph{complete} (i.e., it represents a \emph{complete solution}) if it has no
-$\star$'s. Similarly, a chip is complete if its FCG is complete (or,
-equivalently, the list of formulas is empty).
+of $\star$'s in $G$. $L$ contains formulas that still need to be compiled. Once
+a formula is compiled, it replaces one of the $\star$'s in $G$ according to a
+set order. We say that an FCG is \emph{complete} (i.e., it represents a
+\emph{complete solution}) if it has no $\star$'s. Similarly, a chip is complete
+if its FCG is complete (or, equivalently, the list of formulas is empty).
 
@@
 attempt to not miss a solution, \textsc{Crane} returns them all. In particular,
-if a rule returns an empty set, then that rule does not apply to the formula,
-and the algorithm continues with the next rule.
+if a rule returns an empty set, then that rule does not apply to the formula.
 
@@
 rules. Typically, after a few more rules are applied, a combination of $\CR$ and
-$\Reff$ nodes introduces a loop back to the $\GDR$ node, thus completing the
-definition of a recursive function. The GDR compilation rule is summarised as
-\cref{alg:domainrecursion} and explained in more detail using the example below.
+$\Reff$ nodes introduces a cycle-inducing edge back to the $\GDR$ node, thus
+completing the definition of a recursive function. The GDR compilation rule is
+summarised as \cref{alg:domainrecursion} and explained in more detail using the
+example below.
 
@@
 \begin{example}
-  Let $\phi = \{\, c_1, c_2, c_3 \,\}$ be a formula with clauses
+  Let $\phi = \{\, c_1, c_2 \,\}$ be a formula with clauses
   \begin{align*}
-    c_1 &= (\emptyset, \{\, (Y, X) \,\}, \{\, X \mapsto \Delta^\top, Y \mapsto \Delta^\top \,\}), \\
-    c_2 &=
+    c_1 &=
           \begin{multlined}[t]
@@
           \end{multlined}\\
-    c_3 &=
+    c_2 &=
           \begin{multlined}[t]
@@
   CR\@. The rule introduces a new domain $\Gamma'$ and transforms $\phi$ to
-  $\phi' = (c_1', c_2', c_3')$, where
+  $\phi' = (c_1', c_2')$, where
   \begin{align*}
-    c_1' &= c_1, \\
-    c_2' &=
+    c_1' &=
            \begin{multlined}[t]
@@
            \end{multlined} \\
-    c_3' &=
+    c_2' &=
            \begin{multlined}[t]
@@
 
+\paragraph{Notation.}
 Let $\Doms$ be a function that maps any clause or formula to the set of domains
@@
 
+\paragraph{Hashing.}
 We use (integer-valued) hash functions to efficiently discard pairs of formulas
@@
 
-\citet{DBLP:conf/ijcai/BroeckTMDR11} use a cache to check if a formula is
-identical to one of the formulas that have already been fully compiled. To
-facilitate recursion, we extend the caching scheme to include formulas that have
-been encountered but not fully compiled yet. Formally, we define a \emph{cache}
-to be a map from integers (e.g., hash codes) to sets of pairs of the form
-$(\phi, v)$, where $\phi$ is a formula, and $v$ is an FCG node.
+\paragraph{Caching.}
+\textsc{ForcLift} \citep{DBLP:conf/ijcai/BroeckTMDR11} uses a cache to check if
+a formula is identical to one of the formulas that have already been fully
+compiled. To facilitate recursion, we extend the caching scheme to include
+formulas that have been encountered but not fully compiled yet. Formally, we
+define a \emph{cache} to be a map from integers (e.g., hash codes) to sets of
+pairs of the form $(\phi, v)$, where $\phi$ is a formula, and $v$ is an FCG
+node.
 
@@
 When \textsc{ForcLift} \citep{DBLP:conf/ijcai/BroeckTMDR11} compiles a WFOMC
-instance into a circuit, each gate type encodes an arithmetic operation on its
+instance into a circuit, each node type encodes an arithmetic operation on its
 inputs and parameters. These operations are then immediately performed while
@@
 \begin{example}\label{example:interpretation}
-  Let us use the FCG from \cref{fig:examplefcg} as an example. The input formula
-  (i.e., the formula in \cref{example:first}) has two domains: $\Gamma$ and
-  $\Delta$. Thus, the interpretation of the FCG is a function
+  Consider the FCG from \cref{fig:examplefcg}. The input formula (i.e., the
+  formula from \cref{example:first}) has two domains: $\Gamma$ and $\Delta$.
+  Thus, the interpretation of the FCG is a function
   $f\colon \mathbb{N}_{0} \times \mathbb{N}_{0} \to \mathbb{R}_{\ge 0}$. Let
@@
 
-In this section, we compare \textsc{Crane} and \textsc{ForcLift}
+We compare \textsc{Crane} and \textsc{ForcLift}
 \citep{DBLP:conf/ijcai/BroeckTMDR11} on their ability to count various kinds of
@@
 
-% the process: both for running algorithms and for determining complexities
 In our experiments, we consider all sixteen combinations of these properties,
@@
 always run until it terminates. \textsc{Crane} is run until either five
-solutions are found or the search tree reaches height 6.\footnote{The search
-  tree has a high branching factor, so exploring all nodes at depth 5 takes at
-  most a few seconds, whereas doing the same for depth 6 can be computationally
-  infeasible in some cases.} If successful, \textsc{ForcLift} generates a
-circuit, and \textsc{Crane} generates one or more (complete) FCGs. In both
-cases, we manually convert the resulting graphs into definitions of functions as
-described in \cref{sec:interpret}. We then assess the complexity of each
-solution and pick the best if \textsc{Crane} returns several solutions of
-varying complexities. When assessing the complexity of each such definition, we
-make two assumptions. First, we can compute the binomial coefficient
-$\binom{n}{k}$ in $\Theta(nk)$ time. Second, techniques such as dynamic
-programming and memoization are used to avoid recomputing the same binomial
-coefficient or function call multiple times.
+solutions are found or the search tree reaches height 6 (which happens in at
+most a few seconds). If successful, \textsc{ForcLift} generates a circuit, and
+\textsc{Crane} generates one or more (complete) FCGs. In both cases, we manually
+convert the resulting graphs into definitions of functions as described in
+\cref{sec:interpret}. We then assess the complexity of each solution and pick
+the best if \textsc{Crane} returns several solutions of varying complexities.
+When assessing the complexity of each such definition, we make two assumptions.
+First, we can compute the binomial coefficient $\binom{n}{k}$ in $\Theta(nk)$
+time. Second, techniques such as dynamic programming and memoization are used to
+avoid recomputing the same binomial coefficient or function call multiple times.
 
@@
 supplements \textsc{ForcLift} \citep{DBLP:conf/ijcai/BroeckTMDR11} with three
-new compilation rules. The experiments in \cref{sec:results} revealed a range of
-counting problems that are liftable to \textsc{Crane} but not to any other
-(W)FOMC algorithm. Although here we focused on FOMC problems,
-\textsc{ForcLift}'s support for weights trivially transfers to \textsc{Crane} as
-well. The common thread across these newly liftable problems is (partial)
-injectivity. Thus, we can formulate the following conjecture.
+new compilation rules. Our experiments revealed a range of counting problems
+that are liftable to \textsc{Crane} but not to any other (W)FOMC algorithm.
+Although in this paper we focus on unweighted counting, \textsc{ForcLift}'s
+support for weights trivially transfers to \textsc{Crane} as well. The common
+thread across these newly liftable problems is (partial) injectivity. Thus, we
+can formulate the following conjecture.
 
@@
 also allow us to prove the correctness of the new compilation rules in
-constructing FCGs that indeed compute the right WMC\@. Second, these definitions
-must be simplified before they can be used, perhaps by a computer algebra
-system. Third, most importantly, we need a way to find the base cases for the
-recursive definitions provided by \textsc{Crane}. Fourth, since the first
-solution found by \textsc{Crane} is not always optimal in terms of its
+constructing FCGs that indeed compute the right (weighted) model counts. Second,
+these definitions must be simplified before they can be used, perhaps by a
+computer algebra system. Third, most importantly, we need a way to find the base
+cases for the recursive definitions provided by \textsc{Crane}. Fourth, since
+the first solution found by \textsc{Crane} is not always optimal in terms of its
 complexity, an automated way to determine the asymptotic complexity of a

### 2022-08-07 doc/paper/paper.tex
Feedback

@@
 
+% TODO: FOMC algorithms -> of most algorithms to date
 \begin{abstract}
   First-order model counting (FOMC) is a computational problem that asks to
-  count the models of a sentence in first-order logic. Despite being around for
-  more than a decade, practical FOMC algorithms are still unable to compute
-  functions as simple as a factorial. We argue that the capabilities of FOMC
-  algorithms are severely limited by their inability to express arbitrary
-  recursive computations. To enable arbitrary recursion, we relax the
-  restrictions that typically accompany domain recursion and generalise circuits
-  used to express a solution to an FOMC problem to graphs that may contain
-  cycles. To this end, we enhance the most well-established (weighted) FOMC
-  algorithm \textsc{ForcLift} with new compilation rules and an algorithm to
-  check whether a recursive call is feasible. These improvements allow us to
-  find efficient solutions to counting fundamental structures such as injections
-  and bijections.
+  count the models of a sentence in finite-domain first-order logic. Despite
+  being around for more than a decade, practical FOMC algorithms are still
+  unable to compute functions as simple as a factorial. We argue that the
+  capabilities of FOMC algorithms are severely limited by their inability to
+  express arbitrary recursive computations. To enable arbitrary recursion, we
+  relax the restrictions that typically accompany domain recursion and
+  generalise circuits used to express a solution to an FOMC problem to graphs
+  that may contain cycles. To this end, we enhance the most well-established
+  (weighted) FOMC algorithm \textsc{ForcLift} with new compilation rules and an
+  algorithm to check whether a recursive call is feasible. These improvements
+  allow us to find efficient solutions to counting fundamental structures such
+  as injections and bijections.
 \end{abstract}
+% TODO: We conclude after report on empirical results and discuss a few
+% conjectures on what correctness might look like.
 
 \section{Introduction}
+
+% TODO: It might be worth remarking either in the abstract or in the intro that
+% generally the weighted version is what is studied but the nonweighted version
+% is also still interesting because of its connections to finite model theory.
+% You could make a reference to the work of Paul Beam on symmetric weighted
+% model counting.
 
@@
 Traditionally in computational complexity theory, a problem is \emph{tractable}
-if it can be solved in time polynomial in the size of the instance. The
-equivalent notion in (W)FOMC is liftability. A (W)FOMC instance is
-\emph{(domain-)liftable} if it can be solved in time polynomial in the size(s)
-of the domain(s) \citep{jaeger2012liftability}. Over more than a decade, many
-classes of instances were shown to be liftable
+if it can be solved in time polynomial in the instance size. The equivalent
+notion in (W)FOMC is liftability. A (W)FOMC instance is \emph{(domain-)liftable}
+if it can be solved in time polynomial in the size(s) of the domain(s)
+\citep{jaeger2012liftability}. Over more than a decade, many classes of
+instances were shown to be liftable
 \citep{DBLP:conf/kr/BremenK21,DBLP:conf/nips/KazemiKBP16,DBLP:conf/lics/KuusistoL18,DBLP:journals/jair/Kuzelka21}.
@@
 
+% TODO (footnote): You need to explain this a little bit more. You say that it
+% is liftable in principle but you should clarif ythat factorial has never been
+% shown empirically and there is no correctness theorem claiming that a
+% factorial can be computed in a lifted manner. Or something like that.
 However, none of the publicly available exact (W)FOMC algorithms can efficiently
@@
 solution always terminates.
+% TODO: Because this is the focus of your work you might want to give at least
+% one example of such a stringent condition
 
@@
 the compilation rules.
+% TODO ('Let D... all domains'): You need to state explicitly or implicitly that
+% to set of domains is constructed from a finite set of constants. Either you
+% can define the set of constants in the langoage or you can say that in the
+% interest of simplicity the set of constants is a set of nullary functions
+% mentioned in the sentence, which only mentions relations or nullary functions.
+% Function that take arguments are not allowed.
 
@@
 
+% TODO: You should mention that somewhat unusually, first order variables are in
+% capital letters, similar to the convention of logic programming. They are not
+% to be confused with second order qualification.
 One can read a formula from \cref{def:formula} as a sentence in a FOL\@. All
@@
 
-% \footnote{If some domain is not big enough to contain all of its constants,
-% the formula is unsatisfiable.}
-
 \begin{example}
@@
 \end{example}
+% TODO: It might be useful to give one or two readable examples with interesting
+% model counts. For example Px v Qx over domain n has 3^n/4^n solutions. I think
+% The Frends smokers example has a more complicated solution you can find in one
+% of the papers. It might motivate the framework generally speaking better
+% although of course you can continue to use the same running example for the
+% rest of your paper. Such examples are especially useful for readers who are
+% not familiar but still need to get excited by the problem
 
@@
 $S[x/V]$ to denote $S$ with all occurrences of all variables in $V$ replaced
-with $x$.\footnote{If $(X, Y)$ is a two-variable constraint, substituting a
-  constant $c$ for $X$ would result in $(c, Y)$, which would have to be
-  rewritten as $(Y, c)$ to fit the definition of a constraint.}
+with $x$.
 
@@
 
+% TODO: Again for the reader who is not very familiar with this area it might be
+% good to at least give the circuit for one of the examples such as a
+% disjunction just to show them how it is usually done.
+
 % From circuits to graphs.
@@
 of a node determines its out-degree.
+
+% TODO: I think there is a point of confusion here. Firstly the work of guy
+% introduce circuits and I presume that you want to say that the node types are
+% present in both the circuits as well as your structure. Given that I think you
+% should start of the paragraph by saying that like with circuit introduced by
+% Guy, there are node type such as XYZN. In addition to those you will be
+% introducing the following new ones.
+%
+% I think the other point that is not made very clear is that you have no
+% formally defined circuits. So perhaps if you could introduce a quick
+% definition and then say that we have the same building blocks as those, ie
+% nodes, but with a different graphical structure it will become clearer
 
@@
 
+% TODO: explain notation (i.e., remove the bot)
 \begin{example}
@@
 \end{table*}
+% TODO: This is very neat but readers from the community will expect to see some
+% plots of time. Can you also give a few of those that reflect or mirror the
+% conclusions from the table? Also it is a standard to discuss a few lifted
+% theories like the smokers and friends example. Can you also include some
+% empirical results with plots of time on such theories as well to appeal to the
+% sanity of the reader that it actually works for problems in frameworks such
+% as Markov log networks
 
@@
 
+% TODO: You previously mentioned this class being discussed in another paper.
+% You will need to remind the reader what you are doing differently to that and
+% how you are improving to previous work.
+
 However, the most important direction for future work is to fully automate this

### 2022-08-09 doc/talks/workshop_talk/talk.tex
A new talk

--- 2022-04-29 aiai_talk/talk.tex
@@
 
-\usetheme{CambridgeUS}
-
 \usetikzlibrary{shapes}
@@
 \beamertemplatenavigationsymbolsempty
-\DeclareRobustCommand{\stirling}{\genfrac\{\}{0pt}{}}
+\usetheme{default}
+\usecolortheme{rose}
 
@@
 
-\author[Paulius Dilkas]{\textbf{Paulius Dilkas}, Vaishak Belle}
-\title[Recursive Solutions to FOMC]{Recursive Solutions to First-Order Model Counting}
-\date{AIAI Seminar, 28th March 2022}
+\author{\textbf{Paulius Dilkas}, Vaishak Belle}
+\title{Recursive Solutions to First-Order Model Counting}
+\institute{University of Edinburgh, UK}
+\date{Workshop on Counting and Sampling 2022}
 
@@
 
-\maketitle
-
-\section{A Motivating Example}
+\begin{frame}[noframenumbering,plain]
+  \tikz[remember picture,overlay]{
+    \node at ([yshift=25pt,xshift=30pt]current page.south)
+    {\includegraphics[height=40pt]{inf.png}};
+    \node at ([yshift=25pt,xshift=75pt]current page.south)
+    {\includegraphics[height=40pt]{ecr.jpg}};
+    \node at ([yshift=20pt,xshift=140pt]current page.south)
+    {\includegraphics[height=20pt]{epsrc.png}};
+  }
+  \titlepage
+\end{frame}
 
@@
   \begin{exampleblock}{A Counting Problem}
-    Suppose we were meeting in person, the room had \structure{$n$} seats, and there were \structure{$m \le n$} attendees. How many ways would there be to seat everyone?
+    Suppose this room has \structure{$n$} seats, and there are
+    \structure{$m \le n$} people in the audience. How many ways are there to
+    seat everyone?
   \end{exampleblock}
@@
   \begin{itemize}
-  \item each attendee gets one seat (i.e., at least one \alert{and} at most one),
+  \item each attendee gets exactly one seat,
   \item and a seat can accommodate at most one person.
@@
 \begin{frame}{Let's Express This Problem in Logic!}
-  \centering
-  \includegraphics[height=0.8\textheight]{spock.jpg}
-\end{frame}
-
-\begin{frame}{Let's Express This Problem in Logic!}
   \begin{itemize}
@@
       \[
-      \forall x \in M. \exists y \in N. P(x, y)
+      \forall x \in M\text{. }\exists y \in N\text{. }P(x, y)
       \]
@@
       \[
-      \forall x \in M. \forall y, z \in N. P(x, y) \land P(x, z) \Rightarrow y=z
+      \forall x \in M\text{. }\forall y, z \in N\text{. }P(x, y) \land P(x, z) \Rightarrow y=z
       \]
@@
       \[
-      \forall w, x \in M. \forall y \in N. P(w, y) \land P(x, y) \Rightarrow w=x
+      \forall w, x \in M\text{. }\forall y \in N\text{. }P(w, y) \land P(x, y) \Rightarrow w=x
       \]
@@
   The first two sentences constrain \structure{$P$} to be a function, and the last one makes it injective.
-  \onslide<6>{
-    \begin{tikzpicture}[remember picture,overlay]
-      \node at (current page.center) {\includegraphics[height=0.4\textheight]{happy.jpg}};
-    \end{tikzpicture}
-  }
 \end{frame}
@@
   \begin{itemize}
-  \item \alert{First-order model counting} is the problem of counting the models of a sentence in first-order logic.
-  \item The \alert{(symmetric) weighted} variation of the problem adds weights (e.g., probabilities) to predicates.
-  \item Thus, SWFOMC can also be used for efficient \alert{probabilistic inference} in relational models.
-  \item None of the (implemented) (SW)FOMC algorithms are able to count, e.g., \alert{injective} and \alert{bijective} functions.
+    \item \alert{First-order model counting} (FOMC) is the problem of counting
+          the models of a sentence in first-order logic.
+    \item The \alert{(symmetric) weighted} variation of the problem adds weights
+          (e.g., probabilities) to predicates.
+          \begin{itemize}
+            \item It is used for efficient \alert{probabilistic inference} in
+                  relational models such as Markov logic networks.
+          \end{itemize}
+    \item None of the (implemented) (W)FOMC algorithms are able to count, e.g.,
+          \alert{injective} and \alert{bijective} functions.
   \end{itemize}
   \begin{block}{Claim}
-    This shortcoming can be addressed via support for (almost arbitrary) \alert{recursive functions}.
+    This shortcoming can be addressed via support for (almost arbitrary)
+    \alert{recursive functions}.
   \end{block}
@@
 
-\section{Graphs and Their Role in Knowledge Compilation}
-
-\begin{frame}{First-Order Knowledge Compilation}
+\begin{frame}{First-Order Knowledge Compilation with \textsc{ForcLift}}
   \begin{columns}
@@
         child {node {}
-          child {node {}
-            child {node {}}
-            child {node {}
-              child {node {}}
-              child {node {}
-                child {node {}}
           child {node[fill=red!50,fill on=<2>] {}
@@
               child {node[fill=red!50,fill on=<2>] (ref) {}}
-        }}}}}};
+            }}};
         \draw[-latex, bend right,alt=<2>{red}{black}] (ref) to (dr);
@@
 
-\begin{frame}{More Formally...}
+\begin{frame}{More Formally\ldots}
   \begin{definition}
@@
                 child {node[fill=red!50, fill on=<4>] {}
-            child {node[fill=red!50, fill on=<5>] {}}
-            child {node[fill=red!50, fill on=<6>] {}
-              child {node[fill=red!50, fill on=<7>] {}}
-              child {node[fill=red!50, fill on=<8>] {}
-                child {node[fill=red!50, fill on=<9>] {}}
-                child {node[fill=red!50, fill on=<10>] {}
-                  child {node[fill=red!50, fill on=<11>] {}
-                    child {node[fill=red!50, fill on=<12>] {}}
-                    child {node[fill=red!50, fill on=<13>] (ref) {}}
-        }}}}}};
+                  child {node[fill=red!50, fill on=<5>] {}
+                    child {node[fill=red!50, fill on=<6>] {}}
+                    child {node[fill=red!50, fill on=<7>] (ref) {}}
+        }}};
         \draw[-latex, bend right] (ref) to (dr);
@@
       \begin{align*}
-        f(m, n) &= \onslide<3->{\sum_{l=0}^m \binom{m}{l}} \onslide<5->{1} \onslide<4->{\times} \onslide<7->{1} \onslide<6->{\times} \onslide<9->{1} \onslide<8->{\times} \onslide<12->{[l<2]} \onslide<11->{\times} \onslide<13->{f(m-l, n-1)}\\
-        \onslide<14>{&= f(m, n-1) + mf(m-1, n-1)}
+        f(m, n) &= \onslide<3->{\sum_{l=0}^m \binom{m}{l}} \onslide<6->{[l<2]} \onslide<5->{\times} \onslide<7->{f(m-l, n-1)}\\
+        \onslide<8>{&= f(m, n-1) + mf(m-1, n-1)}
       \end{align*}
-      \onslide<12>{
+      \onslide<6>{
         \[
@@
   \end{columns}
-\end{frame} % Things get more interesting if you do some computations before encountering a cycle or if you have several cycles.
-
-%% \section{Compilation: How to Construct an FCG}
-\section{Compilation: How to Construct an FCG}
+\end{frame}
 
@@
     \begin{itemize}
-    \item \structure{$G$} is a (potentially \texttt{null}) FCG,
+    \item \structure{$G$} is an FCG,
     \item and \structure{$L$} is a list of formulas.
@@
   \begin{gather}
-    ({\color{color1} \forall x, y \in L. x=y}) \land \label{eq:1} \tag{{\color{color1} 1}} \\
-    ({\color{color2} \forall x \in M. \forall y, z \in N. P(x, y) \land P(x, z) \Rightarrow y=z}) \land \label{eq:2} \tag{{\color{color2} 2}} \\
-    ({\color{color2} \forall w, x \in M. \forall y \in N. P(w, y) \land P(x, y) \Rightarrow w=x}) \label{eq:3} \tag{{\color{color2} 3}}
+    ({\color{color1} \forall x, y \in L\text{. }x=y}) \land \label{eq:1} \tag{{\color{color1} 1}} \\
+    ({\color{color2} \forall x \in M\text{. }\forall y, z \in N\text{. }P(x, y) \land P(x, z) \Rightarrow y=z}) \land \label{eq:2} \tag{{\color{color2} 2}} \\
+    ({\color{color2} \forall w, x \in M\text{. }\forall y \in N\text{. }P(w, y) \land P(x, y) \Rightarrow w=x}) \label{eq:3} \tag{{\color{color2} 3}}
   \end{gather}
@@
 
-\begin{frame}{New Rule 1: (Generalised) Domain Recursion}
+\begin{frame}
+  \frametitle<1>{New Rule 1: Generalised Domain Recursion}
+  \frametitle<2>{New Rule 2: Constraint Removal}
+  \frametitle<3>{New Rule 3: Identifying Possibilities for Recursion}
   \begin{columns}
-    \begin{column}{0.20\textwidth}
+    \begin{column}{0.15\textwidth}
       \centering
       \begin{tikzpicture}[every node/.style={draw,ellipse},edge from parent/.style={draw,-latex},sibling distance=10mm,level distance=10mm]
-        \node[fill=red!50] (dr) {}
+        \node[fill=red!50, fill on=<1>] (dr) {}
         child {node {}
+          child {node[fill=red!50, fill on=<2>] {}
             child {node {}
               child {node {}}
-            child {node {}
-              child {node {}}
-              child {node {}
-                child {node {}}
-                child {node {}
-                  child {node {}
-                    child {node {}}
-                    child {node (ref) {}}
-        }}}}}};
-        \draw[-latex, bend right] (ref) to (dr);
+              child {node[fill=red!50, fill on=<3>] (ref) {}}
+            }}};
+        \draw[-latex, bend right,alt=<3>{red}{black}] (ref) to (dr);
       \end{tikzpicture}
     \end{column}
-    \begin{column}{0.8\textwidth}
+    \begin{column}{0.85\textwidth}
+      \begin{overprint}
+        \onslide<1>
           \begin{example}
@@
             \[
-        \forall x \in M. \forall y, z \in N. y \ne z \Rightarrow \neg P(x, y) \lor \neg P(x, z)
+              \forall x \in M\text{. }\forall y, z \in N\text{. }y \ne z \Rightarrow \neg P(x, y) \lor \neg P(x, z)
             \]
@@
             \begin{gather*}
-          \forall y, z \in N. y \ne z \Rightarrow \neg P(\alert{c}, y) \lor \neg P(\alert{c}, z) \\
-          \forall x \in M. \forall y, z \in N. \alert{x \ne c} \land y \ne z \Rightarrow \neg P(x, y) \lor \neg P(x, z)
+              \forall y, z \in N\text{. }y \ne z \Rightarrow \neg P(\alert{c}, y) \lor \neg P(\alert{c}, z) \\
+              \begin{multlined}
+                \forall x \in M\text{. }\forall y, z \in N\text{. }\alert{x \ne c} \land y \ne z \Rightarrow \\
+                \neg P(x, y) \lor \neg P(x, z)
+              \end{multlined}
             \end{gather*}
@@
           \end{example}
-    \end{column}
-  \end{columns}
-\end{frame}
-% We're still creating a vertex in a graph with one outgoing edge.
-
-\begin{frame}{New Rule 2: Constraint Removal}
-  \begin{columns}
-    \begin{column}{0.20\textwidth}
-      \centering
-      \begin{tikzpicture}[every node/.style={draw,ellipse},edge from parent/.style={draw,-latex},sibling distance=10mm,level distance=10mm]
-        \node (dr) {}
-        child {node {}
-          child {node {}
-            child {node {}}
-            child {node {}
-              child {node {}}
-              child {node {}
-                child {node {}}
-                child {node[fill=red!50] {}
-                  child {node {}
-                    child {node {}}
-                    child {node (ref) {}}
-        }}}}}};
-        \draw[-latex, bend right] (ref) to (dr);
-      \end{tikzpicture}
-    \end{column}
-    \begin{column}{0.8\textwidth}
+        \onslide<2>
           \begin{example}
@@
             \begin{gather*}
-        \forall x \in \alert{M}. \forall y, z \in N. \alert{x \ne c} \land y \ne z \Rightarrow \neg P(x, y) \lor \neg P(x, z) \\
               \begin{multlined}
-          \forall w,x \in \alert{M}. \forall y \in N. \alert{w \ne c} \land \alert{x \ne c} \land w \ne x \Rightarrow \\
+                \forall x \in \alert{M}\text{. }\forall y, z \in N\text{. }\alert{x \ne c} \land y \ne z \Rightarrow \\
+                \neg P(x, y) \lor \neg P(x, z)
+              \end{multlined} \\
+              \begin{multlined}
+                \forall w,x \in \alert{M}\text{. }\forall y \in N\text{. }\alert{w \ne c} \land \alert{x \ne c} \land w \ne x \Rightarrow \\
                 \neg P(w, y) \lor \neg P(x, y)
@@
             \begin{gather*}
-          \forall x \in \alert{M'}. \forall y, z \in N. y \ne z \Rightarrow \neg P(x, y) \lor \neg P(x, z) \\
-          \forall w,x \in \alert{M'}. \forall y \in N. w \ne x \Rightarrow \neg P(w, y) \lor \neg P(x, y)
+              \forall x \in \alert{M'}\text{. }\forall y, z \in N\text{. }y \ne z \Rightarrow \neg P(x, y) \lor \neg P(x, z) \\
+              \forall w,x \in \alert{M'}\text{. }\forall y \in N\text{. }w \ne x \Rightarrow \neg P(w, y) \lor \neg P(x, y)
             \end{gather*}
           \end{example}
-    \end{column}
-  \end{columns}
-\end{frame}
-% Requirement: all variables from M are != c.
-% Necessary because later we want to compare formulas and identify that they are isomorphic up to domains.
-
-\begin{frame}{New Rule 3: Identifying Possibilities for Recursion}
-  \begin{columns}
-    \begin{column}{0.25\textwidth}
-      \centering
-      \begin{tikzpicture}[every node/.style={draw,ellipse},edge from parent/.style={draw,-latex},sibling distance=10mm,level distance=10mm]
-        \node (dr) {}
-        child {node {}
-          child {node {}
-            child {node {}}
-            child {node {}
-              child {node {}}
-              child {node {}
-                child {node {}}
-                child {node {}
-                  child {node {}
-                    child {node {}}
-                    child {node[fill=red!50] (ref) {}}
-        }}}}}};
-        \draw[-latex, bend right, red] (ref) to (dr);
-      \end{tikzpicture}
-    \end{column}
-    \begin{column}{0.75\textwidth}
+        \onslide<3>
           \begin{block}{Goal}
-      Check if the input formula is isomorphic (up to domains) to a previously encountered formula.
+            Check if the input formula is isomorphic (up to domains) to a
+            previously encountered formula.
           \end{block}
@@
               \item Extend each such bijection to a map between sets of domains.
-        \item If the bijection makes the clauses equal, and the domain map is compatible with previous domain maps, move on to another pair of clauses.
+              \item If the bijection makes the clauses equal, and the domain map
+                    is compatible with previous domain maps, move on to another
+                    pair of clauses.
             \end{enumerate}
           \end{block}
+      \end{overprint}
     \end{column}
@@
 \end{frame}
+% We're still creating a vertex in a graph with one outgoing edge.
 
@@
 
-\section{Summary}
+\begin{frame}{Resulting Improvements to Counting Functions}
+  Let \structure{$M$} and \structure{$N$} be two sets with cardinalities
+  \structure{$|M| = m$} and \structure{$|N| = n$}.
+
+  Our new rules enable \textsc{ForcLift} to efficiently count
+  \structure{$M \to N$} functions such as:
+  \begin{itemize}
+    \item injections in \structure{$\Theta(mn)$} time
+          \begin{itemize}
+            \item best: \structure{$\Theta(m)$}
+          \end{itemize}
+    \item partial injections in \structure{$\Theta(mn)$} time
+          \begin{itemize}
+            \item best: \structure{$\Theta({\min\{\, m, n \,\}}^2)$}
+          \end{itemize}
+          \item bijections in \structure{$\Theta(m)$} time
+          \begin{itemize}
+            \item \alert{optimal!}
+          \end{itemize}
+  \end{itemize}
+\end{frame}
 

### 2022-08-16 doc/paper/paper.tex
Small changes

@@
 
-% TODO: FOMC algorithms -> of most algorithms to date
 \begin{abstract}
@@
   unable to compute functions as simple as a factorial. We argue that the
-  capabilities of FOMC algorithms are severely limited by their inability to
+  capabilities of FOMC algorithms to date are limited by their inability to
   express arbitrary recursive computations. To enable arbitrary recursion, we
@@
   algorithm to check whether a recursive call is feasible. These improvements
-  allow us to find efficient solutions to counting fundamental structures such
-  as injections and bijections.
+  allow the algorithm to construct efficient solutions to counting fundamental
+  structures such as injections and bijections. We end with a few conjectures on
+  what classes of instances could be liftable as a result.
 \end{abstract}
-% TODO: We conclude after report on empirical results and discuss a few
-% conjectures on what correctness might look like.
 
 \section{Introduction}
-
-% TODO: It might be worth remarking either in the abstract or in the intro that
-% generally the weighted version is what is studied but the nonweighted version
-% is also still interesting because of its connections to finite model theory.
-% You could make a reference to the work of Paul Beam on symmetric weighted
-% model counting.
 
@@
 % 2. Why is it interesting and important?
-
-% in fact, the WFOMC algorithm by \citet{DBLP:conf/ijcai/BroeckTMDR11} can do so when it is unable to solve the instance in a lifted manner.
 
@@
 \citep{DBLP:journals/pvldb/GatterbauerS15,DBLP:journals/debu/GribkoffSB14}.
+While WFOMC tends to receive more attention in the literature, FOMC is an
+interesting problem in an of itself because of its connections to finite model
+theory \citep{DBLP:conf/kr/BremenK21} and applications in enumerative
+combinatorics \citep{DBLP:conf/ilp/BarvinekB0ZK21}.
 
@@
 
-% TODO (footnote): You need to explain this a little bit more. You say that it
-% is liftable in principle but you should clarif ythat factorial has never been
-% shown empirically and there is no correctness theorem claiming that a
-% factorial can be computed in a lifted manner. Or something like that.
 However, none of the publicly available exact (W)FOMC algorithms can efficiently
@@
   so it is known to be liftable in principle
-  \citep{DBLP:journals/jair/Kuzelka21}.} We claim that this shortcoming is due
-to the inability of these algorithms to construct recursive solutions. The topic
-of recursion in the context of WFOMC has been studied before but in limited
-ways. \Citet{DBLP:conf/ilp/BarvinekB0ZK21} use WFOMC to generate numerical data
-that is then used to conjecture recurrence relations that explain that data.
+  \citep{DBLP:journals/jair/Kuzelka21}, but an algorithm that can lift such an
+  instance in practice does not exist.} We claim that this shortcoming is due to
+the inability of these algorithms to construct recursive solutions. The topic of
+recursion in the context of WFOMC has been studied before but in limited ways.
+\Citet{DBLP:conf/ilp/BarvinekB0ZK21} use WFOMC to generate numerical data that
+is then used to conjecture recurrence relations that explain that data.
 \Citet{DBLP:conf/nips/Broeck11} introduced the idea of \emph{domain recursion}.
@@
 solution always terminates.
-% TODO: Because this is the focus of your work you might want to give at least
-% one example of such a stringent condition
 
@@
 well-known WFOMC algorithm \textsc{ForcLift}. \textsc{ForcLift} works in two
-stages: compilation and evaluation/propagation.\footnote{There is also an
-  intermediate stage called \emph{smoothing} that takes place between
-  compilation and evaluation. As our changes to smoothing are rather elementary,
-  we do not discuss them to not distract the reader from the main contributions
-  of this paper.} In the first stage, various \emph{(compilation) rules} are
-applied to the input (or some derivative) formula, gradually constructing a
-circuit. In the second stage, the weights of the instance are propagated through
-the circuit, computing the weighted model count. Along with new compilation
-rules, \textsc{Crane} introduces changes to both stages of the process. First,
-while \textsc{ForcLift} applies compilation rules via greedy\footnote{The
-  algorithm is not described in any paper on \textsc{ForcLift} but can be found
-  in its source code at \url{https://dtai.cs.kuleuven.be/drupal/wfomc}} search,
-\textsc{Crane} uses a hybrid search algorithm that applies some rules greedily
-and some using breadth-first search. Second, the product of compilation is not
-directly evaluated but rather interpreted as a collection of functions on domain
-sizes.
+stages: compilation and evaluation/propagation. In the first stage, various
+\emph{(compilation) rules} are applied to the input (or some derivative)
+formula, gradually constructing a circuit. In the second stage, the weights of
+the instance are propagated through the circuit, computing the weighted model
+count. Along with new compilation rules, \textsc{Crane} introduces changes to
+both stages of the process. First, while \textsc{ForcLift} applies compilation
+rules via greedy\footnote{The algorithm is not described in any paper but can be
+  found in its source code at \url{https://dtai.cs.kuleuven.be/drupal/wfomc}}
+search, \textsc{Crane} uses a hybrid search algorithm that applies some rules
+greedily and some using breadth-first search. Second, the product of compilation
+is not directly evaluated but rather interpreted as a collection of functions on
+domain sizes.
+
+% \footnote{There is also an intermediate stage called \emph{smoothing} that takes
+%   place between compilation and evaluation. As our changes to smoothing are
+%   rather elementary, we do not discuss them to not distract the reader from the
+%   main contributions of this paper.}
 
@@
 compilation rule. Afterwards, another compilation rule recognizes that the
-resulting formula is just like the input formula $\phi$ except it refers to a
-different domain. This observation allows us to add a cycle-forming edge to the
-graph, which can be interpreted as function $f$ relying on $f(n-1)$ to compute
-$f(n)$.
+resulting formula is just like the input formula $\phi$ but with a different
+domain. This observation allows us to add a cycle-forming edge to the graph,
+which can be interpreted as function $f$ relying on $f(n-1)$ to compute $f(n)$.
 
@@
 in a variant of function-free many-sorted FOL with equality to this internal
-format. An \emph{atom} is $p(t_1, \dots, t_n)$ for some predicate $p$ and terms
+format. We use lowercase Latin letters for predicates and constants, uppercase
+Latin letters for variables, and uppercase Greek letters for domains. An
+\emph{atom} is $p(t_1, \dots, t_n)$ for some predicate $p$ and terms
 $t_{1}, \dots, t_{n}$. A \emph{term} is either a constant or a variable. A
 \emph{literal} is either an atom or the negation of an atom (denoted by
-$\neg p(t_1, \dots, t_n)$). Let $\mathcal{D}$ be the set of all domains.
-Initially, $\mathcal{D}$ contains all domains mentioned by the input (W)FOMC
-instance. During compilation, new domains are added to $\mathcal{D}$ by some of
-the compilation rules.
-% TODO ('Let D... all domains'): You need to state explicitly or implicitly that
-% to set of domains is constructed from a finite set of constants. Either you
-% can define the set of constants in the langoage or you can say that in the
-% interest of simplicity the set of constants is a set of nullary functions
-% mentioned in the sentence, which only mentions relations or nullary functions.
-% Function that take arguments are not allowed.
+$\neg p(t_1, \dots, t_n)$). Let $\mathcal{D}$ be the set of all (finite)
+domains. Initially, $\mathcal{D}$ contains all domains mentioned by the input
+(W)FOMC instance. During compilation, new domains are added to $\mathcal{D}$ by
+some of the compilation rules. Each such new domain is interpreted as a subset
+of some element of $\mathcal{D}$.
 
@@
 
-% TODO: You should mention that somewhat unusually, first order variables are in
-% capital letters, similar to the convention of logic programming. They are not
-% to be confused with second order qualification.
 One can read a formula from \cref{def:formula} as a sentence in a FOL\@. All
@@
     types. Here we omit some parameters as well as nodes whose only arithmetic
-    effect is multiplication by one. Some of these nodes play an important role
-    in the weighted version of the problem, whereas others are remnants of the
-    interaction between compilation rules and the way in which \textsc{ForcLift}
-    handles existential quantifiers.}\label{fig:examplefcg}
+    effect is multiplication by one.}\label{fig:examplefcg}
 \end{figure}
+% Some of these nodes play an important role in the weighted version of the
+% problem, whereas others are remnants of the interaction between compilation
+% rules and the way in which \textsc{ForcLift} handles existential quantifiers.
 
@@
 
+% \footnote{Imposing an ordering on outgoing edges is just a limited version of
+% edge labelling.}
+
 % From circuits to graphs.
@@
   computational graph} (FCG) is a (weakly connected) directed graph with a
-single source, node labels, and ordered outgoing edges.\footnote{Imposing an
-  ordering on outgoing edges is just a limited version of edge labelling.} Node
+single source, node labels, and ordered outgoing edges. Node
 labels consist of two parts: the \emph{type} and the \emph{parameters}. The type
@@
 formula to ensure that the expanded version of the formula (as in
-\cref{example:dr}) can be handled efficiently. The clauses in this expanded
-formula are then partitioned into three parts based on whether the
-transformation introduced constants or constraints or both. The aforementioned
-conditions ensure that these parts can be treated independently.
+\cref{example:dr}) can be handled efficiently. For example, at least one clause
+must contain a variable that occurs in all of its atoms. The clauses in this
+expanded formula are then partitioned into three parts based on whether the
+transformation introduced constants or constraints or both. The preconditions
+ensure that these parts can be treated independently.
 
@@
 
-% TODO: explain notation (i.e., remove the bot)
 \begin{example}
@@
             (\{\, \neg p(X, Y), \neg p(X, Z) \,\}, \{\, (X, x), (Y, Z) \,\}, \\
-            \{\, X \mapsto \Gamma, Y \mapsto \Delta^\bot, Z \mapsto \Delta^\bot \,\}),
+            \{\, X \mapsto \Gamma, Y \mapsto \Delta, Z \mapsto \Delta \,\}),
           \end{multlined}\\
@@
             \{\, (X, x), (Z, X), (Z, x) \,\}, \\
-            \{\, X \mapsto \Gamma, Y \mapsto \Delta^\bot, Z \mapsto \Gamma \,\}).
+            \{\, X \mapsto \Gamma, Y \mapsto \Delta, Z \mapsto \Gamma \,\}).
           \end{multlined}
@@
              (\{\, \neg p(X, Y), \neg p(X, Z) \,\}, \{\, (Y, Z) \,\}, \\
-             \{\, X \mapsto \Gamma', Y \mapsto \Delta^\bot, Z \mapsto \Delta^\bot \,\}),
+             \{\, X \mapsto \Gamma', Y \mapsto \Delta, Z \mapsto \Delta \,\}),
            \end{multlined} \\
@@
              (\{\, \neg p(X, Y), \neg p(Z, Y) \,\}, \{\, (Z, X) \,\}, \\
-             \{\, X \mapsto \Gamma', Y \mapsto \Delta^\bot, Z \mapsto \Gamma' \,\}).
+             \{\, X \mapsto \Gamma', Y \mapsto \Delta, Z \mapsto \Gamma' \,\}).
            \end{multlined}
@@
 \paragraph{Hashing.}
-We use (integer-valued) hash functions to efficiently discard pairs of formulas
-that are too different for recursion to be established. The hash code of a
-clause $c = (L, C, \delta_{c})$ (denoted by $\# c$) combines the hash codes of
-the sets of constants and predicates in $c$, the numbers of positive and
-negative literals, the number of inequality constraints $|C|$, and the number of
+We use (integer-valued) hash functions to discard pairs of formulas that are too
+different for recursion to work. The hash code of a clause
+$c = (L, C, \delta_{c})$ (denoted by $\# c$) combines the hash codes of the sets
+of constants and predicates in $c$, the numbers of positive and negative
+literals, the number of inequality constraints $|C|$, and the number of
 variables $|\Vars(c)|$. The hash code of a formula $\phi$ combines the hash
@@
 
-The compatibility of a pair of clauses is checked by function \texttt{genMaps}.
-It considers every possible bijection $\beta\colon \Vars(c) \to \Vars(d)$ and
-map $\gamma\colon \Doms(c) \to \Doms(d)$ s.t.
+Function \texttt{genMaps} checks the compatibility of a pair of clauses. It
+considers every possible bijection $\beta\colon \Vars(c) \to \Vars(d)$ and map
+$\gamma\colon \Doms(c) \to \Doms(d)$ s.t.
 \[
@@
 inputs and parameters. These operations are then immediately performed while
-traversing the circuit and using domain sizes and weights as the initial inputs.
-With \textsc{Crane}, the interpretation of an FCG is a collection of functions.
-Each function has (some) domain sizes as parameters and may contain recursive
-calls to other functions, including itself. While there may be any number of
-subsidiary functions, there is always one main function that can be called with
-the sizes of the domains of the input formula as arguments. Henceforth, this
-function is always called $f$, and it is defined by the source node.
+traversing the circuit. With \textsc{Crane}, the interpretation of an FCG is a
+collection of functions. Each function has (some) domain sizes as parameters and
+may contain recursive calls to other functions, including itself. While there
+may be any number of subsidiary functions, there is always one main function
+that can be called with the sizes of the domains of the input formula as
+arguments. Henceforth, this function is always called $f$, and it is defined by
+the source node.
 
@@
 previous work \citep{DBLP:conf/ijcai/BroeckTMDR11} for information on other
-types. Both $\CR$ and $\GDR$ nodes do not contribute anything to the definitions
-of functions---the interpretation of such a node is simply the interpretation of
-its only direct successor. Obviously, $\star$ nodes also have no interpretation,
-although for a different reason: incomplete FCGs are not meant to be
-interpreted. The interpretation of a $\Reff$ node is a function call. The direct
-successor of the $\Reff$ node (say, $v$) then must introduce a function. The
-parameters of this function are the sizes of all domains used by nodes reachable
-from $v$.
+types. The interpretation of a $\CR$ or a $\GDR$ node is simply the
+interpretation of its only direct successor. Obviously, $\star$ nodes have no
+interpretation as incomplete FCGs are not meant to be interpreted. The
+interpretation of a $\Reff$ node is a function call. The direct successor of the
+$\Reff$ node (say, $v$) then must introduce a function. The parameters of this
+function are the sizes of all domains used by nodes reachable from $v$.
 
@@
 \end{table*}
-% TODO: This is very neat but readers from the community will expect to see some
-% plots of time. Can you also give a few of those that reflect or mirror the
-% conclusions from the table? Also it is a standard to discuss a few lifted
-% theories like the smokers and friends example. Can you also include some
-% empirical results with plots of time on such theories as well to appeal to the
-% sanity of the reader that it actually works for problems in frameworks such
-% as Markov log networks
+% TODO: It is a standard to discuss a few lifted theories like the smokers and
+% friends example. Can you also include some empirical results on such theories
+% as well to appeal to the sanity of the reader that it actually works for
+% problems in frameworks such as Markov log networks
 
@@
 \citep{DBLP:conf/ijcai/BroeckTMDR11} on their ability to count various kinds of
-functions. (Other WFOMC algorithms such as \textsc{L2C}
+functions. This class of instances is chosen because of its simplicity and
+ubiquity and the inability of state-of-the-art WFOMC algorithms to solve many
+such instances. Note that other WFOMC algorithms---\textsc{L2C}
 \citep{DBLP:conf/kr/KazemiP16} and probabilistic theorem proving
-\citep{DBLP:journals/cacm/GogateD16} are unable to solve any of the instances
-that \textsc{ForcLift} fails on.) We begin by describing how such functions can
-be expressed in FOL\@. \textsc{ForcLift} then translates these sentences in FOL
-to formulas as defined in \cref{def:formula}.
+\citep{DBLP:journals/cacm/GogateD16}---are unable to solve any of the instances
+that \textsc{ForcLift} fails on. We begin by describing how such
+function-counting problems can be expressed in FOL\@. \textsc{ForcLift} then
+translates these sentences in FOL to formulas as defined in \cref{def:formula}.
 
@@
 
-The experimental results are summarised in \cref{tbl:results}. The best-known
-asymptotic complexity for computing total surjections is by \citet{30049}. All
-other best-known complexity results are inferred from the formulas and programs
-on the on-line encyclopedia of integer sequences \citep{oeis}. On instances that
-could already be solved by \textsc{ForcLift}, the two algorithms perform equally
-well. However, \textsc{Crane} can also solve all but one instances that
-\textsc{ForcLift} fails on in at most cubic time.
+The experimental results are in \cref{tbl:results}. Previous work often compares
+WFOMC algorithms by running them on a few instances with increasing domain sizes
+and measuring runtime
+\citep{DBLP:conf/nips/Broeck11,DBLP:conf/ijcai/BroeckTMDR11,DBLP:conf/aaai/BroeckD12}.
+However, we can do better than that and identify the exact worst-case asymptotic
+complexity of a solution produced by either \textsc{Crane} or \textsc{ForcLift}.
+The best-known asymptotic complexity for computing total surjections is by
+\citet{30049}. All other best-known complexity results are inferred from the
+formulas and programs on the on-line encyclopedia of integer sequences
+\citep{oeis}. On instances that could already be solved by \textsc{ForcLift},
+the two algorithms perform equally well. However, \textsc{Crane} can also solve
+all but one instances that \textsc{ForcLift} fails on in at most cubic time.
 
@@
 solution, \cref{eq:solution} must be combined with the base case $f(0, n) = 1$
-for all $n \in \mathbb{N}_{0}$. In other words, the base case says that the
-empty partial map is the only partial injection with an empty domain, regardless
-of the codomain. Finally, note that $f(m, n)$ can be evaluated in $\Theta(mn)$
-time by a dynamic programming algorithm that computes $f(i, j)$ for all
-$i = 0, \dots, m$ and $j = 0, \dots, n$.
+for all $n \in \mathbb{N}_{0}$. This base case says that the empty partial map
+is the only partial injection with an empty domain. Finally, note that $f(m, n)$
+can be evaluated in $\Theta(mn)$ time by a dynamic programming algorithm that
+computes $f(i, j)$ for all $i = 0, \dots, m$ and $j = 0, \dots, n$.
 
@@
   Let \IFO{} be the class of formulas in FOL that contain clauses with at most
-  two variables as well as any number of copies
+  two variables as well as any number of copies of
   \begin{align*}
@@
       (\forall X, Z \in \Gamma\text{. }\forall Y \in \Delta\text{. }\\
-      X \ne Z \implies \neg p(X, Y) \lor \neg p(Z, Y)).
+      X \ne Z \implies \neg p(X, Y) \lor \neg p(Z, Y))
     \end{multlined}
@@
 
-Since the tasks of counting injections and bijections fall into the \Ctwo{}
-fragment as well, we can formulate an even stronger conjecture.
+Recall that \Ctwo{} is the class of formulas with counting quantifiers and at
+most two variables. \Ctwo{} was recently shown to be liftable
+\citep{DBLP:journals/jair/Kuzelka21} but without providing a usable (W)FOMC
+algorithm. Since the tasks of counting injections and bijections fall into the
+\Ctwo{} fragment, we can conjecture the following.
 
@@
 
-% TODO: You previously mentioned this class being discussed in another paper.
-% You will need to remind the reader what you are doing differently to that and
-% how you are improving to previous work.
-
 However, the most important direction for future work is to fully automate this
-new way of computing the (W)FOMC of a formula. First, we need an algorithm that
-transforms FCGs into definitions of functions. Formalising this process would
-also allow us to prove the correctness of the new compilation rules in
-constructing FCGs that indeed compute the right (weighted) model counts. Second,
-these definitions must be simplified before they can be used, perhaps by a
-computer algebra system. Third, most importantly, we need a way to find the base
-cases for the recursive definitions provided by \textsc{Crane}. Fourth, since
-the first solution found by \textsc{Crane} is not always optimal in terms of its
-complexity, an automated way to determine the asymptotic complexity of a
-solution would be helpful as well. Achieving these goals would make
-\textsc{Crane} capable of automatically constructing efficient ways to compute a
-function (e.g., a sequence) of interest. In addition to the potential impact on
-areas of artificial intelligence (AI) such as statistical relational AI
+new process. First, we need an algorithm that transforms FCGs into definitions
+of functions. Formalising this process would also allow us to prove the
+correctness of the new compilation rules in constructing FCGs that indeed
+compute the right (weighted) model counts. Second, these definitions must be
+simplified before they can be used, perhaps by a computer algebra system. Third,
+we need a way to find the base cases for the recursive definitions provided by
+\textsc{Crane}. Fourth, since the first solution found by \textsc{Crane} is not
+always optimal in terms of its complexity, an automated way to determine the
+asymptotic complexity of a solution would be helpful as well. Achieving these
+goals would enable \textsc{Crane} to automatically constructing efficient ways
+to compute various functions and sequences. In addition to the potential impact
+on areas of artificial intelligence (AI) such as statistical relational AI
 \citep{DBLP:series/synthesis/2016Raedt}, \textsc{Crane} could be beneficial to

### 2022-08-16 doc/talks/workshop_talk/talk.tex
Small changes

@@
   \begin{itemize}
-  \item \structure{$f$} can be computed in \structure{$\Theta(mn)$} time (via dynamic programming).
-  \item Optimal time complexity to compute \structure{$n^{\underline{m}}$} is \structure{$\Theta(\log m)$}.
-  \item But \structure{$\Theta(mn)$} is still much better than solving an equivalent \alert{$\#\P$-complete} problem in propositional logic.
-  \item The rest of this talk is about how such functions can be found automatically.
+    \item \structure{$f$} can be computed in \structure{$\Theta(mn)$} time (via
+          dynamic programming).
+    \item Optimal time complexity to compute \structure{$n^{\underline{m}}$} is
+          \structure{$\Theta(m)$}.
+    \item But \structure{$\Theta(mn)$} is still much better than translating to
+          propositional logic and running a WMC algorithm.
+    \item The rest of this talk is about how such functions can be found
+          automatically.
   \end{itemize}

### 2022-11-22 doc/paper/paper.tex
Small changes

@@
   sizes of $\Delta^{\top}$. It also creates two subdomains
-  $\Delta^{\top}, \Delta^{\bot} \subseteq b$ that partition $\Delta$, i.e., as
-  the size of $\Delta^{\top}$ increases, the size of $\Delta^{\bot}$
+  $\Delta^{\top}, \Delta^{\bot} \subseteq \Delta$ that partition $\Delta$, i.e.,
+  as the size of $\Delta^{\top}$ increases, the size of $\Delta^{\bot}$
   correspondingly decreases. Nodes labelled $\land$ correspond to

### 2022-11-22 solvers/Crane/src/main/scala/edu/ucla/cs/starai/forclift/nnf/visitors/OutputVisitor.scala

@@ -1,0 +1,95 @@
+package edu.ucla.cs.starai.forclift.nnf.visitors
+
+import scala.collection.mutable.ListBuffer
+import scala.collection.mutable.Set
+
+import edu.ucla.cs.starai.forclift.nnf._
+
+class OutputVisitor extends NnfVisitor[Unit, (String, List[String])] {
+
+  var nextFunctionIndex = 1
+  var nesxtVariableIndex = 1 // TODO: maybe replace with the number of input domains (+1?)
+
+  def visit(node: NNFNode): (String, List[String]) =
+    if (/* TODO: indegree > 1 */) {
+      // TODO: add function arguments
+      val functionName = "f_{" + nextFunctionIndex + "}"
+      nextFunctionIndex++
+      val (main, additional) = super.visit(node, ())
+      (functionName, [functionName + " = " + main] + additional)
+    } else {
+      super.visit(node, ())
+    }
+
+  // ========================= NON-SINK NODES =================================
+
+  protected def visitAndNode(and: And, u: Unit): (String, List[String]) = {
+    val (main1, additional1) = visit(and.l.get)
+    val (main2, additional2) = visit(and.r.get)
+    (main1 + " * " + main2, additional1 + additional2)
+  }
+
+  protected def visitConstraintRemovalNode(
+    cr: ConstraintRemovalNode,
+    u: Unit
+  ): (String, List[String]) = visit(cr.child.get)
+
+  // TODO: remove domain recursion
+  protected def visitDomainRecursion(dr: DomainRecursionNode, u: Unit): (String, List[String]) = {
+    visit(dr.mixedChild.get)
+    visit(dr.groundChild.get)
+  }
+
+  protected def visitExists(exists: CountingNode, u: Unit): (String, List[String]) = {
+    val variableName = "v_{" + nesxtVariableIndex + "}"
+    nesxtVariableIndex++
+    val (main, additional) = visit(exists.child.get)
+    ("sum_{" + variableName + " = 0}^{" + domain??? + "} " + main, additional)
+  }
+
+  protected def visitForallNode(
+      forall: IndependentPartialGroundingNode,
+      u: Unit
+  ): (String, List[String]) = {
+    // TODO: multiplication?
+    visit(forall.child.get)
+  }
+
+  protected def visitImprovedDomainRecursion(
+      idr: ImprovedDomainRecursionNode,
+      u: Unit
[…]

### 2023-01-05 doc/paper/paper.tex
An implementation of the algorithm that constructs the definitions of functions from an FCG

@@
 
+% TODO: when describing experimental results, say that a solution for the last
+% (unsolved) instance can be found, but is too complicated to evaluate by hand.
+% Add that the linear order axiom is also liftable. Cite the same paper in the
+% introduction as well.
+
 \begin{abstract}
@@
 However, none of the publicly available exact (W)FOMC algorithms can efficiently
-compute functions as simple as a factorial.\footnote{The problem of computing
-  the factorial can be described using two variables and counting quantifiers,
-  so it is known to be liftable in principle
-  \citep{DBLP:journals/jair/Kuzelka21}, but an algorithm that can lift such an
+compute functions as simple as a factorial.\footnote{There is previous work
+  \citep{DBLP:journals/jair/Kuzelka21,DBLP:conf/ijcai/Broeck16} showing how FOMC
+  can compute factorials in principle, but an algorithm that can lift such an
   instance in practice does not exist.} We claim that this shortcoming is due to
@@
 \subsection{Generalised Domain Recursion}\label{sec:dr}
+% TODO: the thesis has some improvements to this section
 
@@
 \subsection{Constraint Removal}\label{sec:cr}
+% TODO: the thesis has an improved version of this section
 
@@
 \section{Empirical Results}\label{sec:results} % Newly Domain-Liftable Formulas
+% TODO: the thesis has an improved version of this section
+% TODO: add the sample solutions as an appendix (they're already in the thesis)
 
@@
     $\Delta$. All asymptotic complexities are in $\Theta(\cdot)$. A dash means
-    that no complete solution was found.}\label{tbl:results}
+    that the algorithm was not able to find a solution.}\label{tbl:results}
 \end{table*}

### 2023-01-05 solutions.py

@@ -46,13 +46,13 @@ def one_dimensional_bijections4(n):
     return sum(math.comb(n, m) * (-1) ** (n - m) * g(n, m) for m in range(n + 1))
 
 
-def one_dimensional_injections1(n):
-    def g(n, m):
-        if n == 0:
+def one_dimensional_injections1(m):
+    def g(m, l):
+        if m == 0:
             return 1
-        return g(n - 1, m) + m * g(n - 1, m - 1)
+        return g(m - 1, l) + l * g(m - 1, l - 1)
 
-    return sum(math.comb(n, m) * (-1) ** (n - m) * g(n, m) for m in range(n + 1))
+    return sum(math.comb(m, l) * (-1) ** (m - l) * g(m, l) for l in range(m + 1))
 
 
 def one_dimensional_injections2(n):
@@ -169,6 +169,19 @@ def crane_one_dimensional_surjections2(l, m):
     return (l + 1) * crane_one_dimensional_surjections2(l, m - 1)
 
 
+def crane_two_dimensional_surjections(m, n):
+    return sum(
+        math.comb(m, l)
+        * (-1) ** (m - l)
+        * sum(math.comb(n, k) * (-1) ** (n - k) * (k + 1) ** l for k in range(n + 1))
+        for l in range(m + 1)
+    )
+
+
+def my_two_dimensional_surjections(m, n):
+    return sum((-1) ** i * math.comb(n, i) * (n - i) ** m for i in range(n + 1))
+
+
 # ================================= MISC =================================
 
 
@@ -235,8 +248,10 @@ def partial_injections_final(m, n):
         m - 1, n - 1
     )
 
+def factorial(n):
+    return sum(math.comb(n, k) * sum(math.comb(n, l) * (l + 1) ** k * (-1) ** (2 * n - k - l) for l in range(n + 1)) for k in range(n + 1))
 
-MAX = 5
+MAX = 6
 
 # for m in range(1, MAX):
 #     for n in range(1, MAX):
@@ -247,22 +262,22 @@ MAX = 5
 #     for n in range(1, MAX):
 #         print("f({}, {}) = {}".format(m, n, forclift2_injections(m, n)))
 
-for m in range(0, MAX):
-    for n in range(0, MAX):
-        print(
-            "f({}, {}) = {} ({})".format(
-                m,
-                n,
-                partial_injections_final(m, n),
-                my_partial_injections(m, n),
-            )
-        )
-
[…]

### 2023-01-05 solvers/Crane/src/main/scala/edu/ucla/cs/starai/forclift/inference/WeightedCNF.scala

@@ -23,9 +23,7 @@ import edu.ucla.cs.starai.forclift.compiler._
 import edu.ucla.cs.starai.forclift.conditioning._
 import edu.ucla.cs.starai.forclift.propositional._
 import edu.ucla.cs.starai.forclift.util._
-import edu.ucla.cs.starai.forclift.nnf.visitors.SignLogDoubleWmc
-import edu.ucla.cs.starai.forclift.nnf.visitors.VerifyWmcVisitor
-import edu.ucla.cs.starai.forclift.nnf.visitors.WmcVisitor
+import edu.ucla.cs.starai.forclift.nnf.visitors._
 
 case class WeightedCNF(
   cnf: CNF,
@@ -80,6 +78,12 @@ case class WeightedCNF(
     val c2d = new LogC2D
     c2d.weightedModelCount(propCnf)
   }
+
+  lazy val toLatex: List[String] = smoothNnfs.map{ nnf =>
+    val functionIntroductionFinder = new FunctionIntroductionFinder
+      functionIntroductionFinder.visit(nnf)
+    LatexOutputVisitor(domainSizes.domains, functionIntroductionFinder.nodes, nnf)
+  }.flatten
 
   def verifyLogWmc {
 	VerifyWmcVisitor.verify(smoothNnfs, domainSizes, predicateWeights)

### 2023-01-05 solvers/Crane/src/main/scala/edu/ucla/cs/starai/forclift/nnf/FONodes.scala

@@ -41,8 +41,12 @@ class IndependentPartialGroundingNode(
 
   lazy val evalOrder = child.get.evalOrder
 
-  def simpleClone(): NNFNode =
-    new IndependentPartialGroundingNode(cnf, None, c, ineqs, d, explanation)
+  def simpleClone(): NNFNode = {
+    val n =
+      new IndependentPartialGroundingNode(cnf, None, c, ineqs, d, explanation)
+    n.domains = domains
+    n
+  }
 
   def size = child.get.size + 1
 
@@ -68,6 +72,7 @@ class IndependentPartialGroundingNode(
       d,
       explanation
     )
+    returnValue.domains = domains
     NNFNode.conditionCache((this, pos, neg)) = returnValue
     returnValue
   }
@@ -78,6 +83,7 @@ class IndependentPartialGroundingNode(
     } else {
       val newNode =
         new IndependentPartialGroundingNode(cnf, None, c, ineqs, d, explanation)
+      newNode.domains = domains
       NNFNode.smoothingCache(this) = newNode
       newNode.update(List(Some(child.get.smooth)))
       newNode
@@ -113,8 +119,8 @@ class IndependentPartialGroundingNode(
         "  " + getName(nameSpace) + """ [texlbl="""" + fontsize + """ """ + cnf
           .toLatex() + """"];""" + "\n" +
           "  " + "exp" + getName(
-          nameSpace
-        ) + """ [texlbl="""" + fontsize + """ $\displaystyle\bigforall{""" + c + """}{""" + subscript + """}$", shape=circle];""" + "\n"
+            nameSpace
+          ) + """ [texlbl="""" + fontsize + """ $\displaystyle\bigforall{""" + c + """}{""" + subscript + """}$", shape=circle];""" + "\n"
       }
       val myEdges = if (compact) {
         "  " + getName(nameSpace) + " -> " + child.get.getName(
@@ -130,10 +136,10 @@ class IndependentPartialGroundingNode(
           nameSpace
         ) + """ [""" + edgeLabel(explanation) + """];""" + "\n" +
           "  " + "exp" + getName(nameSpace) + " -> " + child.get.getName(
-          nameSpace
-        ) + """ [""" + edgeLabel(
-          " $ " + childlwmc.exp + " $ "
-        ) + """];""" + "\n"
+            nameSpace
+          ) + """ [""" + edgeLabel(
+            " $ " + childlwmc.exp + " $ "
[…]

### 2023-01-05 solvers/Crane/src/main/scala/edu/ucla/cs/starai/forclift/nnf/visitors/DomainsVisitor.scala

@@ -6,10 +6,11 @@ import scala.collection.mutable.Set
 import edu.ucla.cs.starai.forclift.nnf._
 import edu.ucla.cs.starai.forclift.PositiveUnitClause
 
-/** Updates the 'domains' field of all nodes in a way that avoids infinite
-  * loops caused by cycles in the circuit.
+/** Updates the 'domains' field of all nodes in a way that avoids infinite loops
+  * caused by cycles in the circuit.
   *
-  * @param nodes all circuit nodes (as returned by PostOrderVisitor)
+  * @param nodes
+  *   all circuit nodes (as returned by PostOrderVisitor)
   *
   * Each visitor method returns 'true' if the 'domains' field of the input node
   * was updated and 'false' otherwise.
@@ -63,7 +64,7 @@ class DomainsVisitor(val nodes: ListBuffer[NNFNode])
       cr: ConstraintRemovalNode,
       u: Unit
   ): Boolean = {
-    val newDomains = cr.child.get.domains + cr.domain
+    val newDomains = cr.child.get.domains + cr.domain - cr.subdomain
     val returnValue = cr.domains != newDomains
     cr.domains = newDomains
     returnValue

### 2023-01-23 doc/paper/paper.tex
(Messy) preparation for submission

@@
-%File: anonymous-submission-latex-2023.tex
-\documentclass[letterpaper]{article} % DO NOT CHANGE THIS
-\usepackage[submission]{aaai23}  % DO NOT CHANGE THIS
-\usepackage{times}  % DO NOT CHANGE THIS
-\usepackage{helvet}  % DO NOT CHANGE THIS
-\usepackage{courier}  % DO NOT CHANGE THIS
-\usepackage[hyphens]{url}  % DO NOT CHANGE THIS
-\usepackage{graphicx} % DO NOT CHANGE THIS
-\urlstyle{rm} % DO NOT CHANGE THIS
-\def\UrlFont{\rm}  % DO NOT CHANGE THIS
-\usepackage{natbib}  % DO NOT CHANGE THIS AND DO NOT ADD ANY OPTIONS TO IT
-\usepackage{caption} % DO NOT CHANGE THIS AND DO NOT ADD ANY OPTIONS TO IT
-\frenchspacing  % DO NOT CHANGE THIS
-\setlength{\pdfpagewidth}{8.5in} % DO NOT CHANGE THIS
-\setlength{\pdfpageheight}{11in} % DO NOT CHANGE THIS
+\documentclass{article}
+\pdfpagewidth=8.5in
+\pdfpageheight=11in
+
+\usepackage{kr}
+
+% Use the postscript times font!
+\usepackage{times}
+\usepackage{soul}
+\usepackage{url}
+\usepackage[hidelinks]{hyperref}
+\usepackage[utf8]{inputenc}
+\usepackage[small]{caption}
+\usepackage{graphicx}
+\usepackage{amsmath}
+\usepackage{amsthm}
+\usepackage{booktabs}
+% \usepackage{algorithm}
+% \usepackage{algorithmic}
+\urlstyle{same}
 
 \usepackage{mathtools}
-\usepackage{amsthm}
 \usepackage{amssymb}
@@
 \usepackage[capitalize]{cleveref}
-\usepackage{booktabs}
 \usepackage{multirow}
@@
 \usepackage{complexity}
-
-% These are recommended to typeset algorithms but not required. See the subsubsection on algorithms. Remove them if you don't have algorithms in your paper.
-% \usepackage{algorithm}
-% \usepackage{algorithmic}
-
-% These are recommended to typeset listings but not required. See the subsubsection on listing. Remove this block if you don't have listings in your paper.
-% \usepackage{newfloat}
-% \usepackage{listings}
-% \DeclareCaptionStyle{ruled}{labelfont=normalfont,labelsep=colon,strut=off} % DO NOT CHANGE THIS
-% \lstset{%
-% 	basicstyle={\footnotesize\ttfamily},% footnotesize acceptable for monospace
-% 	numbers=left,numberstyle=\footnotesize,xleftmargin=2em,% show line numbers, remove this entire line if you don't want the numbers.
-% 	aboveskip=0pt,belowskip=0pt,%
-% 	showstringspaces=false,tabsize=2,breaklines=true}
-% \floatstyle{ruled}
-% \newfloat{listing}{tb}{lst}{}
-% \floatname{listing}{Listing}
-
-% Keep the \pdfinfo as shown here. There's no need
-% for you to add the /Title and /Author tags.
-\pdfinfo{
-/TemplateVersion (2023.1)
-}
-
-% DISALLOWED PACKAGES
-% \usepackage{authblk} -- This package is specifically forbidden
-% \usepackage{balance} -- This package is specifically forbidden
-% \usepackage{color (if used in text)
-% \usepackage{CJK} -- This package is specifically forbidden
-% \usepackage{float} -- This package is specifically forbidden
-% \usepackage{flushend} -- This package is specifically forbidden
-% \usepackage{fontenc} -- This package is specifically forbidden
-% \usepackage{fullpage} -- This package is specifically forbidden
-% \usepackage{geometry} -- This package is specifically forbidden
-% \usepackage{grffile} -- This package is specifically forbidden
-% \usepackage{hyperref} -- This package is specifically forbidden
-% \usepackage{navigator} -- This package is specifically forbidden
-% (or any other package that embeds links such as navigator or hyperref)
-% \indentfirst} -- This package is specifically forbidden
-% \layout} -- This package is specifically forbidden
-% \multicol} -- This package is specifically forbidden
-% \nameref} -- This package is specifically forbidden
-% \usepackage{savetrees} -- This package is specifically forbidden
-% \usepackage{setspace} -- This package is specifically forbidden
-% \usepackage{stfloats} -- This package is specifically forbidden
-% \usepackage{tabu} -- This package is specifically forbidden
-% \usepackage{titlesec} -- This package is specifically forbidden
-% \usepackage{tocbibind} -- This package is specifically forbidden
-% \usepackage{ulem} -- This package is specifically forbidden
-% \usepackage{wrapfig} -- This package is specifically forbidden
-% DISALLOWED COMMANDS
-% \nocopyright -- Your paper will not be published if you use this command
-% \addtolength -- This command may not be used
-% \balance -- This command may not be used
-% \baselinestretch -- Your paper will not be published if you use this command
-% \clearpage -- No page breaks of any kind may be used for the final version of your paper
-% \columnsep -- This command may not be used
-% \newpage -- No page breaks of any kind may be used for the final version of your paper
-% \pagebreak -- No page breaks of any kind may be used for the final version of your paperr
-% \pagestyle -- This command may not be used
-% \tiny -- This is not an acceptable font size.
-% \vspace{- -- No negative value may be used in proximity of a caption, figure, table, section, subsection, subsubsection, or reference
-% \vskip{- -- No negative value may be used to alter spacing above or below a caption, figure, table, section, subsection, subsubsection, or reference
-
-\setcounter{secnumdepth}{2} %May be changed to 1 or 2 if section numbers are desired.
-
-% Title
-
-% Your title must be in mixed case, not sentence case.
-% That means all verbs (including short verbs like be, is, using,and go),
-% nouns, adverbs, adjectives should be capitalized, including both words in hyphenated terms, while
-% articles, conjunctions, and prepositions are lower case unless they
-% directly follow a colon or long dash
-\title{Recursive Solutions to First-Order Model Counting}
-\author{Anonymous Submission}
-\affiliations{}
-
 \usetikzlibrary{cd}
 \usetikzlibrary{shapes}
+
+% the following package is optional:
+%\usepackage{latexsym}
+
+% See https://www.overleaf.com/learn/latex/theorems_and_proofs
+% for a nice explanation of how to define new theorems, but keep
+% in mind that the amsthm package is already included in this
+% template and that you must *not* alter the styling.
+% \newtheorem{example}{Example}
+% \newtheorem{theorem}{Theorem}
+\newtheorem{conjecture}{Conjecture}
+\theoremstyle{definition}
+\newtheorem{definition}{Definition}
+\newtheorem{example}{Example}
+
+\pdfinfo{
+/TemplateVersion (KR.2022.0, KR.2023.0)
+}
+
+\title{Recursive Solutions to First-Order Model Counting}
+
+% TODO: double check how the university names should be formatted and the emails
+% TODO: read the formatting instructions and their LaTeX source
+\author{%
+Paulius Dilkas$^1$\and
+Vaishak Belle$^2$\\
+\affiliations
+$^1$National University of Singapore, Singapore\\
+$^2$University of Edinburgh, UK\\
+\emails
+paulius.dilkas@nus.edu.sg,
+vbelle@ed.ac.uk
+}
 
@@
 \SetKwFunction{generateMaps}{genMaps}
-\newtheorem{conjecture}{Conjecture}
-\theoremstyle{definition}
-\newtheorem{definition}{Definition}
-\newtheorem{example}{Example}
 \makeatletter
@@
 \maketitle
-
-% TODO: when describing experimental results, say that a solution for the last
-% (unsolved) instance can be found, but is too complicated to evaluate by hand.
-% Add that the linear order axiom is also liftable. Cite the same paper in the
-% introduction as well.
 
@@
 of models of a sentence in first-order logic (FOL) given the size(s) of its
-domain(s) \citep{DBLP:conf/pods/BeameBGS15}. \emph{Symmetric weighted FOMC}
+domain(s) \cite{DBLP:conf/pods/BeameBGS15}. \emph{Symmetric weighted FOMC}
 (WFOMC) extends FOMC with (pairs of) weights on predicates and asks for a
@@
 WFOMC instance can be rewritten as an instance of (propositional) weighted model
-counting \citep{DBLP:journals/ai/ChaviraD08}. WFOMC emerged as the dominant
+counting \cite{DBLP:journals/ai/ChaviraD08}. WFOMC emerged as the dominant
 approach to \emph{lifted (probabilistic) inference}. Lifted inference techniques
 exploit symmetries in probabilistic models by reasoning about sets rather than
-individuals \citep{DBLP:conf/ecai/Kersting12}. By doing so, many instances
-become solvable in polynomial time \citep{DBLP:conf/nips/Broeck11}. Lifted
+individuals \cite{DBLP:conf/ecai/Kersting12}. By doing so, many instances
+become solvable in polynomial time \cite{DBLP:conf/nips/Broeck11}. Lifted
 inference algorithms are typically used on probabilistic models such as
 probabilistic programming languages
-\citep{DBLP:journals/ml/RaedtK15,DBLP:journals/ijar/RiguzziBZCL17}, Markov logic
+\cite{DBLP:journals/ml/RaedtK15,DBLP:journals/ijar/RiguzziBZCL17}, Markov logic
 networks
-\citep{DBLP:conf/ijcai/BroeckTMDR11,DBLP:journals/cacm/GogateD16,DBLP:journals/ml/RichardsonD06},
-and other lifted graphical \citep{DBLP:journals/ml/KimmigMG15} and statistical
-relational \citep{DBLP:series/synthesis/2016Raedt} models. Lifted inference
+\cite{DBLP:conf/ijcai/BroeckTMDR11,DBLP:journals/cacm/GogateD16,DBLP:journals/ml/RichardsonD06},
+and other lifted graphical \cite{DBLP:journals/ml/KimmigMG15} and statistical
+relational \cite{DBLP:series/synthesis/2016Raedt} models. Lifted inference
 techniques for probabilistic databases, while developed somewhat independently,
 have also been inspired by WFOMC
-\citep{DBLP:journals/pvldb/GatterbauerS15,DBLP:journals/debu/GribkoffSB14}.
+\cite{DBLP:journals/pvldb/GatterbauerS15,DBLP:journals/debu/GribkoffSB14}.
 While WFOMC tends to receive more attention in the literature, FOMC is an
 interesting problem in an of itself because of its connections to finite model
-theory \citep{DBLP:conf/kr/BremenK21} and applications in enumerative
-combinatorics \citep{DBLP:conf/ilp/BarvinekB0ZK21}.
+theory \cite{DBLP:conf/kr/BremenK21} and applications in enumerative
+combinatorics \cite{DBLP:conf/ilp/BarvinekB0ZK21}.
 
@@
 
+% TODO: have ~ in front of every \cite
+% TODO: fix doom emacs warnings
 Traditionally in computational complexity theory, a problem is \emph{tractable}
@@
 if it can be solved in time polynomial in the size(s) of the domain(s)
-\citep{jaeger2012liftability}. Over more than a decade, many classes of
-instances were shown to be liftable
-\citep{DBLP:conf/kr/BremenK21,DBLP:conf/nips/KazemiKBP16,DBLP:conf/lics/KuusistoL18,DBLP:journals/jair/Kuzelka21}.
-First, \citet{DBLP:conf/nips/Broeck11} showed that the class of all sentences of
-FOL with up to two variables (denoted \FOtwo{}) is liftable. Then
-\citet{DBLP:conf/pods/BeameBGS15} proved that there exists a sentence with three
-variables for which FOMC is $\#\P_{1}$-complete (i.e., \FOthree{} is not
-liftable). Since these two results came out, most of the research on (W)FOMC
-focused on developing faster solutions for the \FOtwo{} fragment
-\citep{DBLP:conf/uai/BremenK21,DBLP:conf/aaai/MalhotraS22} and defining new
-liftable fragments. These fragments include \SFO{} and \SRU{}
-\citep{DBLP:conf/nips/KazemiKBP16}, \Uone{} \citep{DBLP:conf/lics/KuusistoL18},
-\FOtwo{} with tree axioms \citep{DBLP:conf/kr/BremenK21}, and \Ctwo{} (i.e., the
+\cite{jaeger2012liftability}. Over more than a decade, many classes of instances
+were shown to be liftable
+\cite{DBLP:conf/kr/BremenK21,DBLP:conf/nips/KazemiKBP16,DBLP:conf/lics/KuusistoL18,DBLP:journals/jair/Kuzelka21}.
+First, Van den Broeck~\shortcite{DBLP:conf/nips/Broeck11} showed that the class
+of all sentences of FOL with up to two variables (denoted \FOtwo{}) is liftable.
+Then Beame et al.~\shortcite{DBLP:conf/pods/BeameBGS15} proved that there exists
+a sentence with three variables for which FOMC is $\#\P_{1}$-complete (i.e.,
+\FOthree{} is not liftable). Since these two results came out, most of the
+research on (W)FOMC focused on developing faster solutions for the \FOtwo{}
+fragment \cite{DBLP:conf/uai/BremenK21,DBLP:conf/aaai/MalhotraS22} and defining
+new liftable fragments. These fragments include \SFO{} and \SRU{}
+\cite{DBLP:conf/nips/KazemiKBP16}, \Uone{} \cite{DBLP:conf/lics/KuusistoL18},
+\FOtwo{} with tree axioms \cite{DBLP:conf/kr/BremenK21}, and \Ctwo{} (i.e., the
 two-variable fragment with counting quantifiers)
-\citep{DBLP:journals/jair/Kuzelka21,DBLP:conf/aaai/MalhotraS22}. On the
-empirical front, there are several open-source implementations of exact WFOMC
-algorithms: \textsc{ForcLift} \citep{DBLP:conf/ijcai/BroeckTMDR11},
-probabilistic theorem proving \citep{DBLP:journals/cacm/GogateD16}, and
-\textsc{L2C} \citep{DBLP:conf/kr/KazemiP16}. Approximate counting is supported
-by \textsc{ApproxWFOMC} \citep{DBLP:conf/ijcai/BremenK20} as well as
-\textsc{ForcLift} \citep{DBLP:conf/uai/BroeckCD12} and probabilistic theorem
-proving \citep{DBLP:journals/cacm/GogateD16}.
+\cite{DBLP:journals/jair/Kuzelka21,DBLP:conf/aaai/MalhotraS22}. On the empirical
+front, there are several open-source implementations of exact WFOMC algorithms:
+\textsc{ForcLift} \cite{DBLP:conf/ijcai/BroeckTMDR11}, probabilistic theorem
+proving \cite{DBLP:journals/cacm/GogateD16}, and \textsc{L2C}
+\cite{DBLP:conf/kr/KazemiP16}. Approximate counting is supported by
+\textsc{ApproxWFOMC} \cite{DBLP:conf/ijcai/BremenK20} as well as
+\textsc{ForcLift} \cite{DBLP:conf/uai/BroeckCD12} and probabilistic theorem
+proving \cite{DBLP:journals/cacm/GogateD16}.
 
@@
 compute functions as simple as a factorial.\footnote{There is previous work
-  \citep{DBLP:journals/jair/Kuzelka21,DBLP:conf/ijcai/Broeck16} showing how FOMC
+  \cite{DBLP:journals/jair/Kuzelka21,DBLP:conf/ijcai/Broeck16} showing how FOMC
   can compute factorials in principle, but an algorithm that can lift such an
@@
 recursion in the context of WFOMC has been studied before but in limited ways.
-\Citet{DBLP:conf/ilp/BarvinekB0ZK21} use WFOMC to generate numerical data that
-is then used to conjecture recurrence relations that explain that data.
-\Citet{DBLP:conf/nips/Broeck11} introduced the idea of \emph{domain recursion}.
-Intuitively, domain recursion partitions a domain of size $n$ into a single
-explicitly named constant and the remaining domain of size $n-1$. However, many
-stringent conditions are enforced to ensure that the search for a tractable
-solution always terminates.
+Barv{\'{\i}}nek et al.~\shortcite{DBLP:conf/ilp/BarvinekB0ZK21} use WFOMC to
+generate numerical data that is then used to conjecture recurrence relations
+that explain that data. Van den Broeck~\shortcite{DBLP:conf/nips/Broeck11}
+introduced the idea of \emph{domain recursion}. Intuitively, domain recursion
+partitions a domain of size $n$ into a single explicitly named constant and the
+remaining domain of size $n-1$. However, many stringent conditions are enforced
+to ensure that the search for a tractable solution always terminates.
 
@@
 
-% search
-% interpretation
-
 % 5.3) contributions, references to sections, shortcomings
@@
 Our representation of FOMC instances is largely based on the format used
-internally by \textsc{ForcLift}, some aspects of which are described by
-\citet{DBLP:conf/ijcai/BroeckTMDR11}. \textsc{ForcLift} can translate sentences
-in a variant of function-free many-sorted FOL with equality to this internal
-format. We use lowercase Latin letters for predicates and constants, uppercase
-Latin letters for variables, and uppercase Greek letters for domains. An
-\emph{atom} is $p(t_1, \dots, t_n)$ for some predicate $p$ and terms
-$t_{1}, \dots, t_{n}$. A \emph{term} is either a constant or a variable. A
+internally by \textsc{ForcLift}, some aspects of which are described by Van den
+Broeck et al.~\shortcite{DBLP:conf/ijcai/BroeckTMDR11}. \textsc{ForcLift} can
+translate sentences in a variant of function-free many-sorted FOL with equality
+to this internal format. We use lowercase Latin letters for predicates and
+constants, uppercase Latin letters for variables, and uppercase Greek letters
+for domains. An \emph{atom} is $p(t_1, \dots, t_n)$ for some predicate $p$ and
+terms $t_{1}, \dots, t_{n}$. A \emph{term} is either a constant or a variable. A
 \emph{literal} is either an atom or the negation of an atom (denoted by
@@
 \begin{definition}[Clause]\label{def:clause}
-  A \emph{clause}\footnote{\citet{DBLP:conf/ijcai/BroeckTMDR11} refer to clauses
-    as c-clauses.} is a triple $c = (L, C, \delta_c)$, where $L$ is a set of
-  literals, $C$ is a set of constraints, and $\delta_c$ is the domain map of
-  $c$. Let $\Vars$ be the function that maps clauses and sets of either literals
-  or constraints to the set of variables contained within. In particular,
+  A \emph{clause}\footnote{Van den Broeck et
+    al.~\shortcite{DBLP:conf/ijcai/BroeckTMDR11} refer to clauses as c-clauses.}
+  is a triple $c = (L, C, \delta_c)$, where $L$ is a set of literals, $C$ is a
+  set of constraints, and $\delta_c$ is the domain map of $c$. Let $\Vars$ be
+  the function that maps clauses and sets of either literals or constraints to
+  the set of variables contained within. In particular,
   $\Vars(c) \coloneqq \Vars(L) \cup \Vars(C)$. \emph{Domain map}
@@
 \begin{definition}[Formula]\label{def:formula}
-  A \emph{formula} (called a c-theory by \citet{DBLP:conf/ijcai/BroeckTMDR11})
-  is a set of clauses s.t.\ all constraints and atoms `type check' with respect
-  to domains.
+  A \emph{formula} (called a c-theory by Van den Broeck et
+  al.~\shortcite{DBLP:conf/ijcai/BroeckTMDR11}) is a set of clauses s.t.\ all
+  constraints and atoms `type check' with respect to domains.
 \end{definition}
@@
 \cref{def:constraint,def:clause,def:formula} and the corresponding concepts
-introduced by \citet{DBLP:conf/ijcai/BroeckTMDR11}. First, we decouple
-variable-to-domain assignments from constraints and move them to a separate
-function $\delta_{c}$ in \cref{def:clause}. Formalising these assignments as a
-function unveils the (previously implicit) assumption that each variable must be
-assigned to a domain. Second, while \citet{DBLP:conf/ijcai/BroeckTMDR11} allow
-for equality constraints and constraints of the form $X \not\in \Delta$ for some
-variable $X$ and domain $\Delta$, we exclude such constraints simply because
-they are not needed.
+introduced by Van den Broeck et al.~\shortcite{DBLP:conf/ijcai/BroeckTMDR11}.
+First, we decouple variable-to-domain assignments from constraints and move them
+to a separate function $\delta_{c}$ in \cref{def:clause}. Formalising these
+assignments as a function unveils the (previously implicit) assumption that each
+variable must be assigned to a domain. Second, while Van den Broeck et
+al.~\shortcite{DBLP:conf/ijcai/BroeckTMDR11} allow for equality constraints and
+constraints of the form $X \not\in \Delta$ for some variable $X$ and domain
+$\Delta$, we exclude such constraints simply because they are not needed.
 
@@
 % TODO: It might be useful to give one or two readable examples with interesting
-% model counts. For example Px v Qx over domain n has 3^n/4^n solutions. I think
+% model counts. For example Px v Qx over domain n has 3^n solutions. I think
 % The Frends smokers example has a more complicated solution you can find in one
@@
     denotes conjunction, and $\bot$ denotes a contradiction---see the work by
-    \citet{DBLP:conf/ijcai/BroeckTMDR11} for the descriptions of these node
-    types. Here we omit some parameters as well as nodes whose only arithmetic
-    effect is multiplication by one.}\label{fig:examplefcg}
+    Van den Broeck et al.~\protect\shortcite{DBLP:conf/ijcai/BroeckTMDR11} for
+    the descriptions of these node types. Here we omit some parameters as well
+    as nodes whose only arithmetic effect is multiplication by
+    one.}\label{fig:examplefcg}
 \end{figure}
-% Some of these nodes play an important role in the weighted version of the
-% problem, whereas others are remnants of the interaction between compilation
-% rules and the way in which \textsc{ForcLift} handles existential quantifiers.
 
@@
 
-% \footnote{Imposing an ordering on outgoing edges is just a limited version of
-% edge labelling.}
-
-% From circuits to graphs.
 A \emph{first-order deterministic decomposable negation normal form
@@
 Along with many node types defined previously
-\citep{DBLP:conf/nips/Broeck11,DBLP:conf/ijcai/BroeckTMDR11}, \textsc{Crane}
+\cite{DBLP:conf/nips/Broeck11,DBLP:conf/ijcai/BroeckTMDR11}, \textsc{Crane}
 uses three more:
@@
 \end{itemize}
-Similarly to \citet{DBLP:conf/ijcai/BroeckTMDR11}, we write $T_p$ for an FCG
-that has a node with the label $T_p$ (i.e., type $T$ and parameter(s) $p$) and
-$\star$'s as all of its direct successors. See \cref{fig:examplefcg} for an
-example FCG\@. Its source node has out-degree 1, label
-$\GDR_{\Gamma \gets \Gamma \setminus \{\, x \,\}}$, and type $\GDR$.
+Similarly to Van den Broeck et al.~\shortcite{DBLP:conf/ijcai/BroeckTMDR11}, we
+write $T_p$ for an FCG that has a node with the label $T_p$ (i.e., type $T$ and
+parameter(s) $p$) and $\star$'s as all of its direct successors. See
+\cref{fig:examplefcg} for an example FCG\@. Its source node has out-degree 1,
+label $\GDR_{\Gamma \gets \Gamma \setminus \{\, x \,\}}$, and type $\GDR$.
 
@@
 applied to the input formula. While \textsc{ForcLift}
-\citep{DBLP:conf/ijcai/BroeckTMDR11} heuristically chooses one of them, in an
+\cite{DBLP:conf/ijcai/BroeckTMDR11} heuristically chooses one of them, in an
 attempt to not miss a solution, \textsc{Crane} returns them all. In particular,
@@
 % Main idea
-The main idea behind domain recursion (both the original version by
-\citet{DBLP:conf/nips/Broeck11} and the one presented here) is as follows. Let
-$\Omega \in \mathcal{D}$ be a domain. Assuming that $\Omega \ne \emptyset$, pick
-some $x \in \Omega$. Then, for every variable $X \in \Omega$ that occurs in a
-literal, consider two possibilities: $X = x$ and $X \ne x$.
+The main idea behind domain recursion (both the original version by Van den
+Broeck~\shortcite{DBLP:conf/nips/Broeck11} and the one presented here) is as
+follows. Let $\Omega \in \mathcal{D}$ be a domain. Assuming that
+$\Omega \ne \emptyset$, pick some $x \in \Omega$. Then, for every variable
+$X \in \Omega$ that occurs in a literal, consider two possibilities: $X = x$ and
+$X \ne x$.
 
@@
 % Original domain recursion
-\citet{DBLP:conf/nips/Broeck11} imposes stringent preconditions on the input
-formula to ensure that the expanded version of the formula (as in
-\cref{example:dr}) can be handled efficiently. For example, at least one clause
-must contain a variable that occurs in all of its atoms. The clauses in this
-expanded formula are then partitioned into three parts based on whether the
-transformation introduced constants or constraints or both. The preconditions
-ensure that these parts can be treated independently.
+Van den Broeck~\shortcite{DBLP:conf/nips/Broeck11} imposes stringent
+preconditions on the input formula to ensure that the expanded version of the
+formula (as in \cref{example:dr}) can be handled efficiently. For example, at
+least one clause must contain a variable that occurs in all of its atoms. The
+clauses in this expanded formula are then partitioned into three parts based on
+whether the transformation introduced constants or constraints or both. The
+preconditions ensure that these parts can be treated independently.
 
@@
 \paragraph{Caching.}
-\textsc{ForcLift} \citep{DBLP:conf/ijcai/BroeckTMDR11} uses a cache to check if
+\textsc{ForcLift} \cite{DBLP:conf/ijcai/BroeckTMDR11} uses a cache to check if
 a formula is identical to one of the formulas that have already been fully
@@
 
-When \textsc{ForcLift} \citep{DBLP:conf/ijcai/BroeckTMDR11} compiles a WFOMC
+When \textsc{ForcLift} \cite{DBLP:conf/ijcai/BroeckTMDR11} compiles a WFOMC
 instance into a circuit, each node type encodes an arithmetic operation on its
@@
 interpretations of new (or significantly changed) types and refer the reader to
-previous work \citep{DBLP:conf/ijcai/BroeckTMDR11} for information on other
+previous work \cite{DBLP:conf/ijcai/BroeckTMDR11} for information on other
 types. The interpretation of a $\CR$ or a $\GDR$ node is simply the
@@
 
-\section{Empirical Results}\label{sec:results} % Newly Domain-Liftable Formulas
+\section{Experimental Results}\label{sec:results}
 % TODO: the thesis has an improved version of this section
-% TODO: add the sample solutions as an appendix (they're already in the thesis)
+% TODO: when describing experimental results, say that a solution for the last
+% (unsolved) instance can be found, but is too complicated to evaluate by hand.
+% Add that the linear order axiom is also liftable. Cite the same paper in the
+% introduction as well.
 
@@
 We compare \textsc{Crane} and \textsc{ForcLift}
-\citep{DBLP:conf/ijcai/BroeckTMDR11} on their ability to count various kinds of
+\cite{DBLP:conf/ijcai/BroeckTMDR11} on their ability to count various kinds of
 functions. This class of instances is chosen because of its simplicity and
@@
 such instances. Note that other WFOMC algorithms---\textsc{L2C}
-\citep{DBLP:conf/kr/KazemiP16} and probabilistic theorem proving
-\citep{DBLP:journals/cacm/GogateD16}---are unable to solve any of the instances
+\cite{DBLP:conf/kr/KazemiP16} and probabilistic theorem proving
+\cite{DBLP:journals/cacm/GogateD16}---are unable to solve any of the instances
 that \textsc{ForcLift} fails on. We begin by describing how such
@@
 and measuring runtime
-\citep{DBLP:conf/nips/Broeck11,DBLP:conf/ijcai/BroeckTMDR11,DBLP:conf/aaai/BroeckD12}.
+\cite{DBLP:conf/nips/Broeck11,DBLP:conf/ijcai/BroeckTMDR11,DBLP:conf/aaai/BroeckD12}.
 However, we can do better than that and identify the exact worst-case asymptotic
@@
 The best-known asymptotic complexity for computing total surjections is by
-\citet{30049}. All other best-known complexity results are inferred from the
-formulas and programs on the on-line encyclopedia of integer sequences
-\citep{oeis}. On instances that could already be solved by \textsc{ForcLift},
-the two algorithms perform equally well. However, \textsc{Crane} can also solve
-all but one instances that \textsc{ForcLift} fails on in at most cubic time.
+Earnest~\shortcite{30049}. All other best-known complexity results are inferred
+from the formulas and programs on the on-line encyclopedia of integer sequences
+\cite{oeis}. On instances that could already be solved by \textsc{ForcLift}, the
+two algorithms perform equally well. However, \textsc{Crane} can also solve all
+but one instances that \textsc{ForcLift} fails on in at most cubic time.
 
@@
 graph that encodes a solution. To construct such graphs, \textsc{Crane}
-supplements \textsc{ForcLift} \citep{DBLP:conf/ijcai/BroeckTMDR11} with three
+supplements \textsc{ForcLift} \cite{DBLP:conf/ijcai/BroeckTMDR11} with three
 new compilation rules. Our experiments revealed a range of counting problems
@@
 most two variables. \Ctwo{} was recently shown to be liftable
-\citep{DBLP:journals/jair/Kuzelka21} but without providing a usable (W)FOMC
+\cite{DBLP:journals/jair/Kuzelka21} but without providing a usable (W)FOMC
 algorithm. Since the tasks of counting injections and bijections fall into the
@@
 on areas of artificial intelligence (AI) such as statistical relational AI
-\citep{DBLP:series/synthesis/2016Raedt}, \textsc{Crane} could be beneficial to
-research in combinatorics as well \citep{DBLP:conf/ilp/BarvinekB0ZK21}.
-
+\cite{DBLP:series/synthesis/2016Raedt}, \textsc{Crane} could be beneficial to
+research in combinatorics as well \cite{DBLP:conf/ilp/BarvinekB0ZK21}.
+
+% TODO: cite Lifted Reasoning for Combinatorial Counting
+
+\appendix
+\section{Solutions Found by \textsc{Crane}}
+
+whose complexity is in \cref{tbl:results} (including those findable by
+\textsc{ForcLift} \cite{DBLP:conf/ijcai/BroeckTMDR11}). Both before and after
+algebraic simplification, excluding multiplication by one. All of these
+solutions have been checked to be correct when combined with suitable base
+cases.
+
+\begin{enumerate}
+  \item $\Theta(m)$ solution for counting $\Gamma \to \Gamma$ functions:
+  \[
+    f(m) = {\left(-1 + \sum_{l=0}^{m} \binom{m}{l} [l < 2]\right)}^{m} = m^{m}.
+  \]
+  \item $\Theta(m^3 + n^3)$ solution for counting $\Gamma \to \Delta$
+  surjections:
+  \begin{align*}
+    \begin{split}
+      f(m, n) ={}& \sum_{l=0}^{m} \binom{m}{l}{(-1)}^{m-l} \sum_{k=0}^{n} \binom{n}{k} {(-1)}^{n-k}\\
+                 &{\left( \sum_{j=0}^{k} \binom{k}{j} [j < 2] \right)}^{l}
+    \end{split}\\
+    ={}& \sum_{l=0}^{m} \binom{m}{l}{(-1)}^{m-l} \sum_{k=0}^{n} \binom{n}{k} {(-1)}^{n-k} {(k+1)}^{l}.
+  \end{align*}
+  \item $\Theta(m^{3})$ solution for counting $\Gamma \to \Gamma$ surjections:
+  \begin{align*}
+    \begin{split}
+      f(m) ={}& \sum_{l=0}^{m} \binom{m}{l}{(-1)}^{m-l} \sum_{k=0}^{m} \binom{m}{k} {(-1)}^{m-k}\\
+              &{\left( \sum_{j=0}^{k} \binom{k}{j} [j < 2] \right)}^{l}
+    \end{split}\\
+    ={}& \sum_{l=0}^{m} \binom{m}{l}{(-1)}^{m-l} \sum_{k=0}^{m} \binom{m}{k} {(-1)}^{m-k} {(k+1)}^{l}.
+  \end{align*}
+  \item $\Theta(mn)$ solution for counting $\Gamma \to \Delta$ injections and
+  partial injections (with different base cases):
+  \begin{align*}
+    f(m, n) ={}& \sum_{l=0}^m \binom{m}{l} [l<2] f(m-l, n-1)\\
+    ={}& f(m, n-1) + mf(m-1, n-1).
+  \end{align*}
+  \item $\Theta(m^{3})$ solution for counting $\Gamma \to \Gamma$ injections:
+  \begin{align*}
+    f(m) ={}& \sum_{l=0}^{m} \binom{m}{l} {(-1)}^{m-l} g(m, l); \\
+    \begin{split}
+      g(m, l) ={}& \sum_{k=0}^{l} \binom{l}{k} [k < 2] g(m - 1, l - k)\\
+      ={}& g(m - 1, l) + lg(m - 1, l - 1).
+    \end{split}
+  \end{align*}
+  \item $\Theta(m)$ solution for counting $\Gamma \to \Delta$ bijections:
+  \[
+    f(m, n) = mf(m-1, n-1).
+  \]
+\end{enumerate}
+
+% TODO: the correctness of all of these was confirmed by finding the right base
+% cases and checking whether the function definitions produce the right values
+% for a sufficiently high number of domain sizes.
+
+% TODO: in the acknowledgements, mention that most of the work was done at UoE
+
+\bibliographystyle{kr}
 \bibliography{paper}
+
 \end{document}

### 2023-01-23 solvers/Crane/src/main/scala/edu/ucla/cs/starai/forclift/inference/WeightedCNF.scala

@@ -82,7 +82,7 @@ case class WeightedCNF(
   lazy val toLatex: List[String] = smoothNnfs.map{ nnf =>
     val functionIntroductionFinder = new FunctionIntroductionFinder
       functionIntroductionFinder.visit(nnf)
-    LatexOutputVisitor(domainSizes.domains, functionIntroductionFinder.nodes, nnf)
+    LatexOutputVisitor(domainSizes.domains, functionIntroductionFinder.nodes, predicateWeights, nnf)
   }.flatten
 
   def verifyLogWmc {

### 2023-01-23 doc/paper/paper.tex
Copy over some improvements from the thesis

@@
 % TODO: read the formatting instructions and their LaTeX source
+% TODO: make sure there are no overflow errors
 \author{%
@@
 of models of a sentence in first-order logic (FOL) given the size(s) of its
-domain(s) \cite{DBLP:conf/pods/BeameBGS15}. \emph{Symmetric weighted FOMC}
+domain(s)~\cite{DBLP:conf/pods/BeameBGS15}. \emph{Symmetric weighted FOMC}
 (WFOMC) extends FOMC with (pairs of) weights on predicates and asks for a
@@
 WFOMC instance can be rewritten as an instance of (propositional) weighted model
-counting \cite{DBLP:journals/ai/ChaviraD08}. WFOMC emerged as the dominant
+counting~\cite{DBLP:journals/ai/ChaviraD08}. WFOMC emerged as the dominant
 approach to \emph{lifted (probabilistic) inference}. Lifted inference techniques
 exploit symmetries in probabilistic models by reasoning about sets rather than
-individuals \cite{DBLP:conf/ecai/Kersting12}. By doing so, many instances
-become solvable in polynomial time \cite{DBLP:conf/nips/Broeck11}. Lifted
+individuals~\cite{DBLP:conf/ecai/Kersting12}. By doing so, many instances
+become solvable in polynomial time~\cite{DBLP:conf/nips/Broeck11}. Lifted
 inference algorithms are typically used on probabilistic models such as
@@
 \cite{DBLP:conf/ijcai/BroeckTMDR11,DBLP:journals/cacm/GogateD16,DBLP:journals/ml/RichardsonD06},
-and other lifted graphical \cite{DBLP:journals/ml/KimmigMG15} and statistical
-relational \cite{DBLP:series/synthesis/2016Raedt} models. Lifted inference
+and other lifted graphical~\cite{DBLP:journals/ml/KimmigMG15} and statistical
+relational~\cite{DBLP:series/synthesis/2016Raedt} models. Lifted inference
 techniques for probabilistic databases, while developed somewhat independently,
@@
 interesting problem in an of itself because of its connections to finite model
-theory \cite{DBLP:conf/kr/BremenK21} and applications in enumerative
-combinatorics \cite{DBLP:conf/ilp/BarvinekB0ZK21}.
+theory~\cite{DBLP:conf/kr/BremenK21} and applications in enumerative
+combinatorics~\cite{DBLP:conf/ilp/BarvinekB0ZK21}.
 
@@
 
-% TODO: have ~ in front of every \cite
+% TODO: have ~ in front of every~\cite
 % TODO: fix doom emacs warnings
@@
 research on (W)FOMC focused on developing faster solutions for the \FOtwo{}
-fragment \cite{DBLP:conf/uai/BremenK21,DBLP:conf/aaai/MalhotraS22} and defining
+fragment~\cite{DBLP:conf/uai/BremenK21,DBLP:conf/aaai/MalhotraS22} and defining
 new liftable fragments. These fragments include \SFO{} and \SRU{}
-\cite{DBLP:conf/nips/KazemiKBP16}, \Uone{} \cite{DBLP:conf/lics/KuusistoL18},
-\FOtwo{} with tree axioms \cite{DBLP:conf/kr/BremenK21}, and \Ctwo{} (i.e., the
+\cite{DBLP:conf/nips/KazemiKBP16}, \Uone{}~\cite{DBLP:conf/lics/KuusistoL18},
+\FOtwo{} with tree axioms~\cite{DBLP:conf/kr/BremenK21}, and \Ctwo{} (i.e., the
 two-variable fragment with counting quantifiers)
@@
 front, there are several open-source implementations of exact WFOMC algorithms:
-\textsc{ForcLift} \cite{DBLP:conf/ijcai/BroeckTMDR11}, probabilistic theorem
-proving \cite{DBLP:journals/cacm/GogateD16}, and \textsc{L2C}
+\textsc{ForcLift}~\cite{DBLP:conf/ijcai/BroeckTMDR11}, probabilistic theorem
+proving~\cite{DBLP:journals/cacm/GogateD16}, and \textsc{L2C}
 \cite{DBLP:conf/kr/KazemiP16}. Approximate counting is supported by
-\textsc{ApproxWFOMC} \cite{DBLP:conf/ijcai/BremenK20} as well as
-\textsc{ForcLift} \cite{DBLP:conf/uai/BroeckCD12} and probabilistic theorem
-proving \cite{DBLP:journals/cacm/GogateD16}.
+\textsc{ApproxWFOMC}~\cite{DBLP:conf/ijcai/BremenK20} as well as
+\textsc{ForcLift}~\cite{DBLP:conf/uai/BroeckCD12} and probabilistic theorem
+proving~\cite{DBLP:journals/cacm/GogateD16}.
 
@@
 compute functions as simple as a factorial.\footnote{There is previous work
-  \cite{DBLP:journals/jair/Kuzelka21,DBLP:conf/ijcai/Broeck16} showing how FOMC
+ ~\cite{DBLP:journals/jair/Kuzelka21,DBLP:conf/ijcai/Broeck16} showing how FOMC
   can compute factorials in principle, but an algorithm that can lift such an
@@
 \subsection{Generalised Domain Recursion}\label{sec:dr}
-% TODO: the thesis has some improvements to this section
 
@@
 % Original domain recursion
-Van den Broeck~\shortcite{DBLP:conf/nips/Broeck11} imposes stringent
-preconditions on the input formula to ensure that the expanded version of the
-formula (as in \cref{example:dr}) can be handled efficiently. For example, at
-least one clause must contain a variable that occurs in all of its atoms. The
-clauses in this expanded formula are then partitioned into three parts based on
-whether the transformation introduced constants or constraints or both. The
-preconditions ensure that these parts can be treated independently.
+Van den Broeck~\shortcite{DBLP:conf/nips/Broeck11} imposes stringent conditions
+on the input formula to ensure that the expanded version of the formula (as in
+\cref{example:dr}) can be handled efficiently. For instance,
+\cref{example:first} cannot be handled by \textsc{ForcLift} because there is no
+root binding class, i.e., the two root variables belong to different equivalence
+classes with respect to the binding relationship. The clauses in this expanded
+formula are then partitioned into three parts based on whether the
+transformation introduced constants or constraints or both. The aforementioned
+conditions ensure that these parts can be treated independently.
 
@@
 \paragraph{Caching.}
-\textsc{ForcLift} \cite{DBLP:conf/ijcai/BroeckTMDR11} uses a cache to check if
+\textsc{ForcLift}~\cite{DBLP:conf/ijcai/BroeckTMDR11} uses a cache to check if
 a formula is identical to one of the formulas that have already been fully
@@
 
-When \textsc{ForcLift} \cite{DBLP:conf/ijcai/BroeckTMDR11} compiles a WFOMC
+When \textsc{ForcLift}~\cite{DBLP:conf/ijcai/BroeckTMDR11} compiles a WFOMC
 instance into a circuit, each node type encodes an arithmetic operation on its
@@
 interpretations of new (or significantly changed) types and refer the reader to
-previous work \cite{DBLP:conf/ijcai/BroeckTMDR11} for information on other
+previous work~\cite{DBLP:conf/ijcai/BroeckTMDR11} for information on other
 types. The interpretation of a $\CR$ or a $\GDR$ node is simply the
@@
 graph that encodes a solution. To construct such graphs, \textsc{Crane}
-supplements \textsc{ForcLift} \cite{DBLP:conf/ijcai/BroeckTMDR11} with three
+supplements \textsc{ForcLift}~\cite{DBLP:conf/ijcai/BroeckTMDR11} with three
 new compilation rules. Our experiments revealed a range of counting problems
@@
 \cite{DBLP:series/synthesis/2016Raedt}, \textsc{Crane} could be beneficial to
-research in combinatorics as well \cite{DBLP:conf/ilp/BarvinekB0ZK21}.
+research in combinatorics as well~\cite{DBLP:conf/ilp/BarvinekB0ZK21}.
 
@@
 whose complexity is in \cref{tbl:results} (including those findable by
-\textsc{ForcLift} \cite{DBLP:conf/ijcai/BroeckTMDR11}). Both before and after
+\textsc{ForcLift}~\cite{DBLP:conf/ijcai/BroeckTMDR11}). Both before and after
 algebraic simplification, excluding multiplication by one. All of these

### 2023-01-23 doc/paper/paper.tex
Ditto

@@
 \subsection{Constraint Removal}\label{sec:cr}
-% TODO: the thesis has an improved version of this section
+
+Recall that GDR on a domain $\Omega$ creates constraints of the form $X_i \ne x$
+for some constant $x \in \Omega$ and family of variables $X_i \in \Omega$. Once
+certain conditions are satisfied, we can eliminate these constraints and replace
+$\Omega$ with a new domain $\Omega'$, which can be interpreted as
+$\Omega \setminus \{\, x \,\}$. These conditions are that a constraint of the
+form $X \ne x$ exists for all variables $X \in \Omega$ across all clauses, and
+such constraints are the only place where $x$ occurs. We formalise the
+conditions as \cref{def:replaceable}.
+
+\begin{definition}\label{def:replaceable}
+  With respect to a formula $\phi$, a pair $(\Omega, x)$ of a domain
+  $\Omega \in \mathcal{D}$ and its element $x \in \Omega$ is called
+  \emph{replaceable} if
+  \begin{itemize}
+    \item $x$ does not occur in any literal of any clause of $\phi$,
+    \item and for each clause $c = (L, C, \delta_c) \in \phi$ and variable
+          $X \in \Vars(c)$, either $\delta_c(X) \ne \Omega$ or $(X, x) \in C$.
+  \end{itemize}
+\end{definition}
 
@@
   $S \gets \emptyset$\;
-  \ForEach{domain $\Omega \in \mathcal{D}$ and element $x \in \Omega$ s.t.
-$x$ does not occur in any literal of any clause of $\phi$ {\bf and} for each clause $c = (L, C, \delta_c) \in \phi$ and variable $X \in \Vars(c)$, either $\delta_c(X) \ne \Omega$ or $(X, x) \in C$\label{line:crconditions}}{
+  \ForEach{replaceable pair $(\Omega \in \mathcal{D}, x \in \Omega)$\label{line:crconditions}}{
     add a new domain $\Omega'$ to $\mathcal{D}$\;
@@
 
-Recall that GDR on a domain $\Omega$ creates constraints of the form $X_i \ne x$
-for some constant $x \in \Omega$ and family of variables $X_i \in \Omega$. Once
-certain conditions are satisfied, \cref{alg:constraintremoval} can eliminate
-these constraints and replace $\Omega$ with a new domain $\Omega'$, which can be
-interpreted as $\Omega \setminus \{\, x \,\}$. These conditions (on
-\cref{line:crconditions} of the algorithm) are that a constraint of the form
-$X \ne x$ exists for all variables $X \in \Omega$ across all clauses, and such
-constraints are the only place where $x$ occurs. The algorithm then proceeds to
+Once a replaceable pair is found, \cref{alg:constraintremoval} proceeds to
 construct the new formula by removing constraints (on

### 2023-01-25 doc/paper/paper.tex
Start writing a longer talk

@@
 \newtheorem{conjecture}{Conjecture}
+\newtheorem{proposition}{Proposition}
 \theoremstyle{definition}
@@
 % TODO: make sure there are no overflow errors
+% TODO: for arbitrary instances of '2022' (e.g., in citations), make it '2023'
 \author{%
@@
 exploit symmetries in probabilistic models by reasoning about sets rather than
-individuals~\cite{DBLP:conf/ecai/Kersting12}. By doing so, many instances
-become solvable in polynomial time~\cite{DBLP:conf/nips/Broeck11}. Lifted
-inference algorithms are typically used on probabilistic models such as
-probabilistic programming languages
-\cite{DBLP:journals/ml/RaedtK15,DBLP:journals/ijar/RiguzziBZCL17}, Markov logic
-networks
-\cite{DBLP:conf/ijcai/BroeckTMDR11,DBLP:journals/cacm/GogateD16,DBLP:journals/ml/RichardsonD06},
+individuals~\cite{DBLP:conf/ecai/Kersting12}. By doing so, many instances become
+solvable in polynomial time~\cite{DBLP:conf/nips/Broeck11}. Lifted inference
+algorithms are typically used on probabilistic models such as probabilistic
+programming
+languages~\cite{DBLP:journals/ml/RaedtK15,DBLP:journals/ijar/RiguzziBZCL17},
+Markov logic
+networks~\cite{DBLP:conf/ijcai/BroeckTMDR11,DBLP:journals/cacm/GogateD16,DBLP:journals/ml/RichardsonD06},
 and other lifted graphical~\cite{DBLP:journals/ml/KimmigMG15} and statistical
@@
 techniques for probabilistic databases, while developed somewhat independently,
-have also been inspired by WFOMC
-\cite{DBLP:journals/pvldb/GatterbauerS15,DBLP:journals/debu/GribkoffSB14}.
+have also been inspired by
+WFOMC~\cite{DBLP:journals/pvldb/GatterbauerS15,DBLP:journals/debu/GribkoffSB14}.
 While WFOMC tends to receive more attention in the literature, FOMC is an
@@
 
-% TODO: have ~ in front of every~\cite
 % TODO: fix doom emacs warnings
@@
 notion in (W)FOMC is liftability. A (W)FOMC instance is \emph{(domain-)liftable}
-if it can be solved in time polynomial in the size(s) of the domain(s)
-\cite{jaeger2012liftability}. Over more than a decade, many classes of instances
-were shown to be liftable
-\cite{DBLP:conf/kr/BremenK21,DBLP:conf/nips/KazemiKBP16,DBLP:conf/lics/KuusistoL18,DBLP:journals/jair/Kuzelka21}.
+if it can be solved in time polynomial in the size(s) of the
+domain(s)~\cite{jaeger2012liftability}. Over more than a decade, many classes of
+instances were shown to be
+liftable~\cite{DBLP:conf/kr/BremenK21,DBLP:conf/nips/KazemiKBP16,DBLP:conf/lics/KuusistoL18,DBLP:journals/jair/Kuzelka21}.
 First, Van den Broeck~\shortcite{DBLP:conf/nips/Broeck11} showed that the class
@@
 fragment~\cite{DBLP:conf/uai/BremenK21,DBLP:conf/aaai/MalhotraS22} and defining
-new liftable fragments. These fragments include \SFO{} and \SRU{}
-\cite{DBLP:conf/nips/KazemiKBP16}, \Uone{}~\cite{DBLP:conf/lics/KuusistoL18},
-\FOtwo{} with tree axioms~\cite{DBLP:conf/kr/BremenK21}, and \Ctwo{} (i.e., the
-two-variable fragment with counting quantifiers)
-\cite{DBLP:journals/jair/Kuzelka21,DBLP:conf/aaai/MalhotraS22}. On the empirical
-front, there are several open-source implementations of exact WFOMC algorithms:
-\textsc{ForcLift}~\cite{DBLP:conf/ijcai/BroeckTMDR11}, probabilistic theorem
-proving~\cite{DBLP:journals/cacm/GogateD16}, and \textsc{L2C}
-\cite{DBLP:conf/kr/KazemiP16}. Approximate counting is supported by
+new liftable fragments. These fragments include \SFO{} and
+\SRU{}~\cite{DBLP:conf/nips/KazemiKBP16},
+\Uone{}~\cite{DBLP:conf/lics/KuusistoL18}, \FOtwo{} with tree
+axioms~\cite{DBLP:conf/kr/BremenK21}, and \Ctwo{} (i.e., the two-variable
+fragment with counting
+quantifiers)~\cite{DBLP:journals/jair/Kuzelka21,DBLP:conf/aaai/MalhotraS22}. On
+the empirical front, there are several open-source implementations of exact
+WFOMC algorithms: \textsc{ForcLift}~\cite{DBLP:conf/ijcai/BroeckTMDR11},
+probabilistic theorem proving~\cite{DBLP:journals/cacm/GogateD16}, and
+\textsc{L2C}~\cite{DBLP:conf/kr/KazemiP16}. Approximate counting is supported by
 \textsc{ApproxWFOMC}~\cite{DBLP:conf/ijcai/BremenK20} as well as
@@
 However, none of the publicly available exact (W)FOMC algorithms can efficiently
-compute functions as simple as a factorial.\footnote{There is previous work
- ~\cite{DBLP:journals/jair/Kuzelka21,DBLP:conf/ijcai/Broeck16} showing how FOMC
-  can compute factorials in principle, but an algorithm that can lift such an
-  instance in practice does not exist.} We claim that this shortcoming is due to
-the inability of these algorithms to construct recursive solutions. The topic of
-recursion in the context of WFOMC has been studied before but in limited ways.
-Barv{\'{\i}}nek et al.~\shortcite{DBLP:conf/ilp/BarvinekB0ZK21} use WFOMC to
-generate numerical data that is then used to conjecture recurrence relations
+compute functions as simple as a factorial.\footnote{There is previous
+  work~\cite{DBLP:journals/jair/Kuzelka21,DBLP:conf/ijcai/Broeck16} showing how
+  FOMC can compute factorials in principle, but an algorithm that can lift such
+  an instance in practice does not exist.} We claim that this shortcoming is due
+to the inability of these algorithms to construct recursive solutions. The topic
+of recursion in the context of WFOMC has been studied before but in limited
+ways. Barv{\'{\i}}nek et al.~\shortcite{DBLP:conf/ilp/BarvinekB0ZK21} use WFOMC
+to generate numerical data that is then used to conjecture recurrence relations
 that explain that data. Van den Broeck~\shortcite{DBLP:conf/nips/Broeck11}
@@
 
-Along with many node types defined previously
-\cite{DBLP:conf/nips/Broeck11,DBLP:conf/ijcai/BroeckTMDR11}, \textsc{Crane}
-uses three more:
+Along with many node types defined
+previously~\cite{DBLP:conf/nips/Broeck11,DBLP:conf/ijcai/BroeckTMDR11},
+\textsc{Crane} uses three more:
 \begin{itemize}
@@
 cardinality of this set is the number of different ways in which the rule can be
-applied to the input formula. While \textsc{ForcLift}
-\cite{DBLP:conf/ijcai/BroeckTMDR11} heuristically chooses one of them, in an
-attempt to not miss a solution, \textsc{Crane} returns them all. In particular,
-if a rule returns an empty set, then that rule does not apply to the formula.
+applied to the input formula. While
+\textsc{ForcLift}~\cite{DBLP:conf/ijcai/BroeckTMDR11} heuristically chooses one
+of them, in an attempt to not miss a solution, \textsc{Crane} returns them all.
+In particular, if a rule returns an empty set, then that rule does not apply to
+the formula.
 
@@
 \end{example}
+
+TODO: connecting sentence?
+
+\begin{proposition}[Correctness of GDR]
+  Let $\phi$ be the formula used as input to \cref{alg:domainrecursion} and
+  $\phi'$ be one of the formulas constructed by the algorithm. Then
+  $\phi \equiv \phi'$.
+\end{proposition}
+\begin{proof}
+  TODO
+  Assume that \cref{line:condition} selects domain $\Omega \in \mathcal{D}$.
+  \[
+    \forall X \in \Omega\text{. } \psi \equiv \psi[x/\{\, X \,\}] \land \forall X \in \Omega\text{. } X \ne x \implies \psi
+  \]
+\end{proof}
 
@@
 
-\section{Experimental Results}\label{sec:results}
-% TODO: the thesis has an improved version of this section
+\section{Empirical Results}\label{sec:results}
 % TODO: when describing experimental results, say that a solution for the last
@@
 
+% TODO: make sure this table floats to the right page and look at other floating
+% objects too (e.g., is [t] on?)
 \begin{table*}[t]
@@
     \midrule
-    \rowcolor{gray!10}\cmark/\xmark & \cmark/\xmark & Functions & $\log m$ & $m$ & $m$ \\
+    \rowcolor{gray!25}\cmark/\xmark & \cmark/\xmark & Functions & $\log m$ & $m$ & $m$ \\
     \xmark & \xmark & \multirow{4}{*}{Surjections} & $n \log m$ & $m^{3}+n^{3}$ & $m^{3}+n^{3}$ \\
@@
     \cmark & \cmark & & \multicolumn{3}{c}{Same as endo-injections} \\
-    \rowcolor{gray!10}\xmark & \xmark & & $m$ & --- & $mn$ \\
-    \rowcolor{gray!10}\xmark & \cmark & & $m$ & --- & $m^3$ \\
-    \rowcolor{gray!10}\cmark & \xmark & & $\min\{\, m, n \,\}^2$ & --- & $mn$ \\
-    \rowcolor{gray!10}\cmark & \cmark & \multirow{-4}{*}{Injections} & $m^2$ & --- & --- \\
+    \rowcolor{gray!25}\xmark & \xmark & & $m$ & --- & $mn$ \\
+    \rowcolor{gray!25}\xmark & \cmark & & $m$ & --- & $m^3$ \\
+    \rowcolor{gray!25}\cmark & \xmark & & ${\min\{\, m, n \,\}}^2$ & --- & $mn$ \\
+    \rowcolor{gray!25}\cmark & \cmark & \multirow{-4}{*}{Injections} & $m^2$ & --- & --- \\
     \xmark & \xmark & \multirow{3}{*}{Bijections} & $m$ & --- & $m$ \\
@@
   \end{tabular}
-  \caption{The worst-case complexity of counting various types of functions.
-    Here, $m$ is the size of domain $\Gamma$, and $n$ is the size of domain
+  \caption{The worst-case complexity of counting various types of functions,
+    where $m$ is the size of domain $\Gamma$, and $n$ is the size of domain
     $\Delta$. All asymptotic complexities are in $\Theta(\cdot)$. A dash means
@@
 
-We compare \textsc{Crane} and \textsc{ForcLift}
-\cite{DBLP:conf/ijcai/BroeckTMDR11} on their ability to count various kinds of
-functions. This class of instances is chosen because of its simplicity and
-ubiquity and the inability of state-of-the-art WFOMC algorithms to solve many
-such instances. Note that other WFOMC algorithms---\textsc{L2C}
-\cite{DBLP:conf/kr/KazemiP16} and probabilistic theorem proving
-\cite{DBLP:journals/cacm/GogateD16}---are unable to solve any of the instances
-that \textsc{ForcLift} fails on. We begin by describing how such
+We compare \textsc{Crane} and
+\textsc{ForcLift}~\cite{DBLP:conf/ijcai/BroeckTMDR11} on their ability to count
+various kinds of functions. This class of instances is chosen because of its
+simplicity and ubiquity and the inability of state-of-the-art WFOMC algorithms
+to solve many such instances. Note that other WFOMC
+algorithms---\textsc{L2C}~\cite{DBLP:conf/kr/KazemiP16} and probabilistic
+theorem proving~\cite{DBLP:journals/cacm/GogateD16}---are unable to solve any of
+the instances that \textsc{ForcLift} fails on. We begin by describing how such
 function-counting problems can be expressed in FOL\@. \textsc{ForcLift} then
@@
 \[
-  \forall X \in \Gamma\text{. }\forall Y, Z \in \Delta\text{. }p(X, Y) \land p(X, Z) \implies Y = Z
+  \forall X \in \Gamma\text{. }\forall Y,Z \in \Delta\text{. }p(X, Y) \land p(X, Z) \implies Y = Z
 \]
@@
 
+% the process: both for running algorithms and for determining complexities
 In our experiments, we consider all sixteen combinations of these properties,
-i.e., injectivity, surjectivity, partiality, and endo-. \textsc{ForcLift} is
-always run until it terminates. \textsc{Crane} is run until either five
-solutions are found or the search tree reaches height 6 (which happens in at
-most a few seconds). If successful, \textsc{ForcLift} generates a circuit, and
-\textsc{Crane} generates one or more (complete) FCGs. In both cases, we manually
-convert the resulting graphs into definitions of functions as described in
-\cref{sec:interpret}. We then assess the complexity of each solution and pick
-the best if \textsc{Crane} returns several solutions of varying complexities.
-When assessing the complexity of each such definition, we make two assumptions.
-First, we can compute the binomial coefficient $\binom{n}{k}$ in $\Theta(nk)$
-time. Second, techniques such as dynamic programming and memoization are used to
-avoid recomputing the same binomial coefficient or function call multiple times.
-
-The experimental results are in \cref{tbl:results}. Previous work often compares
-WFOMC algorithms by running them on a few instances with increasing domain sizes
-and measuring runtime
-\cite{DBLP:conf/nips/Broeck11,DBLP:conf/ijcai/BroeckTMDR11,DBLP:conf/aaai/BroeckD12}.
-However, we can do better than that and identify the exact worst-case asymptotic
+i.e., injectivity, surjectivity, partiality, and endo-. We run each algorithm
+once on each of the sixteen instances.\footnote{While domain sizes have to be
+  specified as part of the input, they are immaterial to the search procedure.}
+\textsc{ForcLift} is always run until it terminates; \textsc{Crane} is run until
+either five solutions are found or the search tree reaches height
+six.\footnote{The search tree has a high branching factor, so exploring all
+  nodes at depth five takes at most a few seconds, whereas doing the same for
+  depth six can be computationally infeasible in some cases.} If successful,
+\textsc{ForcLift} generates a circuit, and \textsc{Crane} generates one or more
+(complete) FCGs. In both cases, we manually convert the resulting graphs into
+definitions of functions as described in \cref{sec:interpret}. We then assess
+the complexity of each solution by hand and pick the best in case \textsc{Crane}
+returns several solutions of varying complexities.
+
+% how the complexity of a solution is determined
+Previous work often compares WFOMC algorithms by running them on a few instances
+with increasing domain sizes and measuring
+runtime~\cite{DBLP:conf/nips/Broeck11,DBLP:conf/ijcai/BroeckTMDR11,DBLP:conf/aaai/BroeckD12}.
+However, we can do much better and identify the exact worst-case asymptotic
 complexity of a solution produced by either \textsc{Crane} or \textsc{ForcLift}.
-The best-known asymptotic complexity for computing total surjections is by
-Earnest~\shortcite{30049}. All other best-known complexity results are inferred
-from the formulas and programs on the on-line encyclopedia of integer sequences
-\cite{oeis}. On instances that could already be solved by \textsc{ForcLift}, the
-two algorithms perform equally well. However, \textsc{Crane} can also solve all
-but one instances that \textsc{ForcLift} fails on in at most cubic time.
-
-Let us examine the case of counting partial (non-endomorphic) injections more
-closely. The FCG in \cref{fig:examplefcg,example:interpretation} counts partial
-injections and is responsible for the $mn$ entry in the table. For a complete
-solution, \cref{eq:solution} must be combined with the base case $f(0, n) = 1$
-for all $n \in \mathbb{N}_{0}$. This base case says that the empty partial map
-is the only partial injection with an empty domain. Finally, note that $f(m, n)$
-can be evaluated in $\Theta(mn)$ time by a dynamic programming algorithm that
-computes $f(i, j)$ for all $i = 0, \dots, m$ and $j = 0, \dots, n$.
+The asymptotic complexity of a solution can be determined by considering the
+total number of arithmetic operations needed to follow the definitions of
+constituent functions without recomputing the same quantity multiple times. In
+particular, we assume that each function call and binomial coefficient is
+computed at most once. We also assume that computing $\binom{n}{k}$ takes
+$\Theta(nk)$ time. For example, the complexity of \cref{eq:solution} is
+$\Theta(mn)$ since $f(m, n)$ can be computed by a dynamic programming algorithm
+that computes $f(i, j)$ for all $i = 0, \dots, m$ and $j = 0, \dots, n$, taking
+a constant amount of time on the computation of each $f(i, j)$.
+
+These results are summarised in \cref{tbl:results}, where we compare the
+solutions found by both algorithms to the best known ways of computing the same
+quantities. The best-known asymptotic complexity for computing total surjections
+is by Earnest~\shortcite{30049}. All other best-known complexity results are
+inferred from the formulas and programs on the on-line encyclopedia of integer
+sequences~\cite{oeis}. On instances that could already be solved by
+\textsc{ForcLift}, the two algorithms perform equally well. However,
+\textsc{Crane} can also solve all but one instances that \textsc{ForcLift} fails
+on in at most cubic time. See \cref{app:solutions} for the exact solutions
+produced by \textsc{Crane} that correspond to the complexity results in
+\cref{tbl:results}.
 
@@
 Recall that \Ctwo{} is the class of formulas with counting quantifiers and at
-most two variables. \Ctwo{} was recently shown to be liftable
-\cite{DBLP:journals/jair/Kuzelka21} but without providing a usable (W)FOMC
-algorithm. Since the tasks of counting injections and bijections fall into the
-\Ctwo{} fragment, we can conjecture the following.
+most two variables. \Ctwo{} was recently shown to be
+liftable~\cite{DBLP:journals/jair/Kuzelka21} but without providing a usable
+(W)FOMC algorithm. Since the tasks of counting injections and bijections fall
+into the \Ctwo{} fragment, we can conjecture the following.
 
@@
 to compute various functions and sequences. In addition to the potential impact
-on areas of artificial intelligence (AI) such as statistical relational AI
-\cite{DBLP:series/synthesis/2016Raedt}, \textsc{Crane} could be beneficial to
+on areas of artificial intelligence (AI) such as statistical relational
+AI~\cite{DBLP:series/synthesis/2016Raedt}, \textsc{Crane} could be beneficial to
 research in combinatorics as well~\cite{DBLP:conf/ilp/BarvinekB0ZK21}.
@@
 \appendix
-\section{Solutions Found by \textsc{Crane}}
+\section{Solutions Found by \textsc{Crane}}\label{app:solutions}
+
+% TODO: fix the introductory description
 
@@
 % TODO: in the acknowledgements, mention that most of the work was done at UoE
+% TODO: should the appendix be in the same file or not?
 

### 2023-01-25 doc/talks/3_long/talk.tex
Start writing a longer talk

--- 2022-08-16 doc/talks/workshop_talk/talk.tex
@@
 \usetikzlibrary{overlay-beamer-styles}
+\usetikzlibrary{shapes.callouts}
 
 \beamertemplatenavigationsymbolsempty
-\usetheme{default}
-\usecolortheme{rose}
+\usetheme{metropolis}
+\setbeamercolor{background canvas}{bg=white}
+%\usecolortheme{rose}
 
@@
 
-\author{\textbf{Paulius Dilkas}, Vaishak Belle}
-\title{Recursive Solutions to First-Order Model Counting}
-\institute{University of Edinburgh, UK}
-\date{Workshop on Counting and Sampling 2022}
+% 15 min introduction
+% 25 min presentation
+% 5 min summary
+% 20-25 slides
+% right now it's 15 slides and 20 min
+% TODO: use \alert instead of \structure
+
+\author{\textbf{Paulius Dilkas} \inst{1} \and Vaishak Belle \inst{2}}
+\title{Recursive Solutions to \\First-Order Model Counting}
+\institute{\inst{1} National University of Singapore, Singapore \and \inst{2} University of Edinburgh, UK}
+\date{TODO}
 
@@
   \tikz[remember picture,overlay]{
+    \node at ([yshift=20pt,xshift=-20pt]current page.south)
+    {\includegraphics[height=40pt]{nus.jpg}};
     \node at ([yshift=25pt,xshift=30pt]current page.south)
@@
   \titlepage
+\end{frame}
+
+% TODO: must attribute vecteezy
+\begin{frame}{What Computers Can and Cannot Do}
+  \begin{tikzpicture}[remember picture,overlay]
+    \node[right=0.7cm] at (current page.west) (stickman) {\includegraphics[height=0.5\textheight]{stickman.png}};
+    \node<-4>[left,shift=({0, -2})] at (current page.east) (computer) {\includegraphics[height=0.5\textheight]{happy_computer}};
+    \node<2>[ellipse callout, draw, right=0cm, callout relative pointer={(-1, -0.5)}] at (stickman.north east) {$\int_{-\infty}^{\infty} e^{-t^{2}}\,\mathrm{d}t$};
+    \node<2>[ellipse callout, draw, left=-0.5cm, below=0.5cm] at (computer.north west) {$\sqrt{\pi}$};
+    \node<3>[ellipse callout, draw, right=-1cm, callout relative pointer={(-2.5, -0.5)}] at (stickman.north east) {Produce a schedule for the nurses at NUH.};
+    \node<3>[ellipse callout, draw, below=0.5cm, shift=({-0.5,0}), callout relative pointer={(0.5, -0.25)}] at (computer.north west) {\includegraphics[width=0.1\textwidth]{schedule}};
+    \node<4>[ellipse callout, draw, right=0cm, callout relative pointer={(-1, -0.15)}] at (stickman.north east) {Describe this picture. \includegraphics[width=0.25\textwidth]{cat.jpg}};
+    \node<4>[ellipse callout, draw, below=0.5cm, shift=({-0.5,0.5}), callout relative pointer={(0.5, -0.5)}] at (computer.north west) {It's a cat with its eyes closed.};
+    \node<5>[ellipse callout, draw, right=0cm, callout relative pointer={(-1, -0.15)}, text width=5cm] at (stickman.north east) {If I shuffle a deck of \alert{$n$} cards, how many possible outcomes are there?};
+    \node<5>[left,shift=({-1, -1})] at (current page.east) (computer2) {\includegraphics[height=0.5\textheight]{overheating_computer}};
+  \end{tikzpicture}
+  % 1. compute the integral
+  % 2. job scheduling
+  % 3. picture description
+  % 4. count matchings
+\end{frame}
+
+\begin{frame}{Flavours of Counting}
 \end{frame}
@@
 \end{frame}
+
+\section{Main Content (TODO: remove later)}
 
@@
 
+\section{Summary (TODO: remove later)}
+
 \begin{frame}{Summary \& Future Work}

### 2023-01-30 doc/paper/paper.tex
A new short talk (and some other things)

@@
 \newtheorem{proposition}{Proposition}
+\newtheorem{claim}{Claim}
 \theoremstyle{definition}
@@
 % TODO: for arbitrary instances of '2022' (e.g., in citations), make it '2023'
+% TODO: maybe mention the term 'data complexity'
+% TODO: fix doom emacs warnings
 \author{%
@@
 \DeclareMathOperator{\Doms}{Doms}
+\DeclareMathOperator{\MC}{MC}
 \DeclareMathOperator{\Vars}{Vars}
@@
 
-% TODO: fix doom emacs warnings
 Traditionally in computational complexity theory, a problem is \emph{tractable}
@@
 proving~\cite{DBLP:journals/cacm/GogateD16}.
+% TODO: add FastWFOMC (only for \FOtwo{})
 
@@
 However, none of the publicly available exact (W)FOMC algorithms can efficiently
-compute functions as simple as a factorial.\footnote{There is previous
-  work~\cite{DBLP:journals/jair/Kuzelka21,DBLP:conf/ijcai/Broeck16} showing how
-  FOMC can compute factorials in principle, but an algorithm that can lift such
-  an instance in practice does not exist.} We claim that this shortcoming is due
-to the inability of these algorithms to construct recursive solutions. The topic
-of recursion in the context of WFOMC has been studied before but in limited
-ways. Barv{\'{\i}}nek et al.~\shortcite{DBLP:conf/ilp/BarvinekB0ZK21} use WFOMC
-to generate numerical data that is then used to conjecture recurrence relations
-that explain that data. Van den Broeck~\shortcite{DBLP:conf/nips/Broeck11}
-introduced the idea of \emph{domain recursion}. Intuitively, domain recursion
-partitions a domain of size $n$ into a single explicitly named constant and the
-remaining domain of size $n-1$. However, many stringent conditions are enforced
-to ensure that the search for a tractable solution always terminates.
+compute functions as simple as a factorial.\footnote{There is some previous work
+  showing how FOMC can compute
+  factorials~\cite{DBLP:journals/jair/Kuzelka21,DBLP:conf/kr/BremenK21,DBLP:conf/ijcai/Broeck16}.
+  One of them~\cite{DBLP:conf/ijcai/Broeck16} is an example `by hand' that does
+  not directly correspond to any algorithm.
+  Another~\cite{DBLP:journals/jair/Kuzelka21} proves that the problem is
+  liftable but contains no experimental results. The
+  third~\cite{DBLP:conf/kr/BremenK21} contains experimental results performed
+  with an algorithm, which is not publicly available.} We claim that this
+shortcoming is due to the inability of these algorithms to construct recursive
+solutions. The topic of recursion in the context of WFOMC has been studied
+before but in limited ways. Barv{\'{\i}}nek et
+al.~\shortcite{DBLP:conf/ilp/BarvinekB0ZK21} use WFOMC to generate numerical
+data that is then used to conjecture recurrence relations that explain that
+data. Van den Broeck~\shortcite{DBLP:conf/nips/Broeck11} introduced the idea of
+\emph{domain recursion}. Intuitively, domain recursion partitions a domain of
+size $n$ into a single explicitly named constant and the remaining domain of
+size $n-1$. However, many stringent conditions are enforced to ensure that the
+search for a tractable solution always terminates.
 
@@
 
-TODO: connecting sentence?
-
-\begin{proposition}[Correctness of GDR]
+\begin{proposition}[Correctness of $\GDR$]
   Let $\phi$ be the formula used as input to \cref{alg:domainrecursion} and
@@
 \end{proposition}
-\begin{proof}
-  TODO
-  Assume that \cref{line:condition} selects domain $\Omega \in \mathcal{D}$.
+\begin{proof} % TODO: finish (Proof technique: if one is true then the other one will be true and vice versa)
+  Let $\Omega \in \mathcal{D}$ be the domain selected by
+  \cref{line:condition} of the algorithm.
+  \begin{claim}\label{claim:logic}
   \[
@@
   \]
+  \end{claim}
+  \begin{claim}
+    Iteration of \cref{claim:logic} for all variables in some set of variables
+    $V$ produces the same clauses as subset enumeration on
+    \cref{line:conditions}.
+  \end{claim}
 \end{proof}
@@
 
+\begin{proposition}[Correctness of $\CR$]
+\end{proposition}
+\begin{proof} % TODO: finish (Proof technique: if one is true then the other one will be true and vice versa)
+  \[
+    \forall X \in \Omega \ni x\text{. } X \ne x \implies \psi \equiv \forall X \in \Omega \setminus \{\, x \,\}\text{. } \psi
+  \]
+\end{proof}
+
 \subsection{Identifying Opportunities for Recursion}\label{sec:ref}
@@
 $\rho|_{\dom(\rho)\cap\dom(\gamma)} = \gamma|_{\dom(\rho)\cap\dom(\gamma)}$.
+
+% TODO: maybe something other than MC? Introduce the notation and the role of \sigma.
+% TODO: add an argument about why this recursion is (or can easily be made) finite
+\begin{proposition}[Correctness of $\Reff$]
+\end{proposition}
+\begin{proof} % TODO: finish (Proof technique: show a bijection between the sets of models)
+  For a given formula $\phi$, \cref{alg:trycache} attempts to find a formula
+  $\psi$ and a map $\rho\colon \Doms(\psi) \to \Doms(\phi)$ such that
+  $\MC(\psi, \sigma \circ \rho\colon \Doms(\psi) \to \mathbb{N}_{0}) = \MC(\phi, \sigma\colon \Doms(\phi) \to \mathbb{N}_{0})$.
+\end{proof}
 
@@
 % TODO: should the appendix be in the same file or not?
+% TODO: also mention that most of the work for this paper was done at UoE
 

### 2023-01-30 doc/talks/3_long/talk.tex
A new short talk (and some other things)

@@
 \usetikzlibrary{shapes.callouts}
+\usetikzlibrary{cd}
 
@@
 
+\newcommand{\WMC}{\textup{WMC}}
+\newcommand{\WFOMC}{\textup{(W)FOMC}}
+\newcommand{\WMI}{\textup{WMI}}
+\newcommand{\WFOMI}{\textup{WFOMI}}
+\newcommand{\AMC}{\textup{AMC}}
+\newcommand{\pbp}{\textup{PBP}}
+\newcommand{\SPPP}{\textup{SP}}
+
 % 15 min introduction
-% 25 min presentation
-% 5 min summary
+% 20-25 min presentation
+% 5-10 min summary
 % 20-25 slides
-% right now it's 15 slides and 20 min
+% before it was 15 slides and 20 min
 % TODO: use \alert instead of \structure
+% TODO: replace capital latin letters with capital Greek letters
 
@@
 
-% TODO: must attribute vecteezy
 \begin{frame}{What Computers Can and Cannot Do}
@@
     \node<5>[left,shift=({-1, -1})] at (current page.east) (computer2) {\includegraphics[height=0.5\textheight]{overheating_computer}};
+    \node[shift=({1.3, 0.1})] at (current page.south west) {\tiny \color{lightgray}{Vector art by Vecteezy.com}};
   \end{tikzpicture}
-  % 1. compute the integral
-  % 2. job scheduling
-  % 3. picture description
-  % 4. count matchings
 \end{frame}
+% TODO: replace cat with 'Generate a picture of a monkey with a funny hat'
 
-\begin{frame}{Flavours of Counting}
+\begin{frame}[fragile]{Many Ways to Count}
+  \begin{center}
+    \begin{tikzcd}
+      \WMI{} & \WFOMI{} \\
+      \#\SAT{}/\WMC{} & \WFOMC{} \\
+      \AMC{}, \pbp{} & \SPPP{}
+    \end{tikzcd}
+  \end{center}
 \end{frame}
+% maybe mention #CSP and other non-SAT ways of counting
 
@@
   \begin{exampleblock}{A Counting Problem}
-    Suppose this room has \structure{$n$} seats, and there are
-    \structure{$m \le n$} people in the audience. How many ways are there to
-    seat everyone?
+    Suppose this room has \alert{$n$} seats, and there are \alert{$m \le n$}
+    people in the audience. How many ways are there to seat everyone?
   \end{exampleblock}
@@
   \pause
-  \alert{Answer:} \structure{$n^{\underline{m}} = n \cdot (n-1)\cdots(n-m+1)$}.
+  \alert{Answer:} $n^{\underline{m}} = n \cdot (n-1)\cdots(n-m+1)$.
 
-  Note: this problem is equivalent to counting \structure{$[m] \to [n]$} injections.
+  Note: this problem is equivalent to counting \alert{$[m] \to [n]$} injections.
 
@@
   \begin{itemize}
-  \item Let \structure{$M$} and \structure{$N$} be sets (i.e., \alert{domains}) such that \structure{$|M| = m$}, and \structure{$|N| = n$}
-  \item Let \structure{$P \subseteq M \times N$} be a relation (i.e., \alert{predicate}) over sets \structure{$M$} and \structure{$N$}
+    \item Let \alert{$M$} and \alert{$N$} be sets (i.e., domains)
+    \begin{itemize}
+      \item such that \alert{$|M| = m$}, and \alert{$|N| = n$}.
+    \end{itemize}
+    \item Let \alert{$P \subseteq M \times N$} be a relation (i.e., predicate)
+          over \alert{$M$} and \alert{$N$}.
     \item We can describe all of the constraints in first-order logic:
@@
   \end{itemize}
-  \pause
-  The first two sentences constrain \structure{$P$} to be a function, and the last one makes it injective.
+  \pause The first two sentences constrain \alert{$P$} to be a function, and the
+  last one makes it injective.
 \end{frame}
@@
   \begin{block}{Claim}
-    This shortcoming can be addressed via support for (almost arbitrary)
-    \alert{recursive functions}.
+    This shortcoming can be addressed via support for \alert{recursive functions}.
   \end{block}
@@
 
-\section{Main Content (TODO: remove later)}
+% TODO: maybe meat makes more sense than sandwich? Or a picture of recursion, e.g., fractals?
+{ % all template changes are local to this group.
+    \setbeamertemplate{navigation symbols}{}
+    \begin{frame}<article:0>[plain]
+        \begin{tikzpicture}[remember picture,overlay]
+            \node[at=(current page.center)] {
+                \includegraphics[keepaspectratio, width=\paperwidth]{sandwich.jpg}
+            };
+        \end{tikzpicture}
+     \end{frame}
+}
 
@@
 
-\section{Summary (TODO: remove later)}
+{ % all template changes are local to this group.
+    \setbeamertemplate{navigation symbols}{}
+    \begin{frame}<article:0>[plain]
+        \begin{tikzpicture}[remember picture,overlay]
+            \node[at=(current page.center)] {
+                \includegraphics[keepaspectratio, height=\paperheight]{zoom.jpg}
+            };
+        \end{tikzpicture}
+     \end{frame}
+}
 

### 2023-01-31 doc/paper/paper.tex
1/4 proofs complete

@@
 \usepackage{complexity}
+\usepackage{siunitx}
 \usetikzlibrary{cd}
@@
 % \newtheorem{theorem}{Theorem}
+\newtheorem{theorem}{Theorem}
 \newtheorem{conjecture}{Conjecture}
-\newtheorem{proposition}{Proposition}
 \newtheorem{claim}{Claim}
@@
 WFOMC~\cite{DBLP:journals/pvldb/GatterbauerS15,DBLP:journals/debu/GribkoffSB14}.
-While WFOMC tends to receive more attention in the literature, FOMC is an
+While WFOMC has received more attention in the literature, FOMC is an
 interesting problem in an of itself because of its connections to finite model
 theory~\cite{DBLP:conf/kr/BremenK21} and applications in enumerative
-combinatorics~\cite{DBLP:conf/ilp/BarvinekB0ZK21}.
+combinatorics~\cite{DBLP:conf/ilp/BarvinekB0ZK21}. There is also a recent line
+of work that uses FOMC-based methods to count solutions to constraint
+satisfaction problems~\cite{DBLP:journals/jair/TotisDRK23}.
 
@@
 WFOMC algorithms: \textsc{ForcLift}~\cite{DBLP:conf/ijcai/BroeckTMDR11},
-probabilistic theorem proving~\cite{DBLP:journals/cacm/GogateD16}, and
-\textsc{L2C}~\cite{DBLP:conf/kr/KazemiP16}. Approximate counting is supported by
-\textsc{ApproxWFOMC}~\cite{DBLP:conf/ijcai/BremenK20} as well as
+probabilistic theorem proving~\cite{DBLP:journals/cacm/GogateD16},
+\textsc{L2C}~\cite{DBLP:conf/kr/KazemiP16}, and
+\textsc{FastWFOMC}~\cite{DBLP:conf/uai/BremenK21}. Approximate counting is
+supported by \textsc{ApproxWFOMC}~\cite{DBLP:conf/ijcai/BremenK20} as well as
 \textsc{ForcLift}~\cite{DBLP:conf/uai/BroeckCD12} and probabilistic theorem
 proving~\cite{DBLP:journals/cacm/GogateD16}.
-% TODO: add FastWFOMC (only for \FOtwo{})
 
@@
   found in its source code at \url{https://dtai.cs.kuleuven.be/drupal/wfomc}}
-search, \textsc{Crane} uses a hybrid search algorithm that applies some rules
-greedily and some using breadth-first search. Second, the product of compilation
-is not directly evaluated but rather interpreted as a collection of functions on
-domain sizes.
+search, \textsc{Crane} also supports a hybrid search algorithm that applies some
+rules greedily and some using breadth-first search. Second, the product of
+compilation is not directly evaluated but rather interpreted as a collection of
+functions on domain sizes.
 
@@
 
-\begin{proposition}[Correctness of $\GDR$]
+\begin{theorem}[Correctness of $\GDR$]
   Let $\phi$ be the formula used as input to \cref{alg:domainrecursion} and
@@
   $\phi \equiv \phi'$.
-\end{proposition}
+\end{theorem}
 \begin{proof} % TODO: finish (Proof technique: if one is true then the other one will be true and vice versa)
@@
   \ForEach{replaceable pair $(\Omega \in \mathcal{D}, x \in \Omega)$\label{line:crconditions}}{
-    add a new domain $\Omega'$ to $\mathcal{D}$\;
+    add a new domain $\Omega'$ to $\mathcal{D}$\;\label{line:newdomain}
     $\phi' \gets \emptyset$\;
@@
 
-\begin{proposition}[Correctness of $\CR$]
-\end{proposition}
-\begin{proof} % TODO: finish (Proof technique: if one is true then the other one will be true and vice versa)
-  \[
-    \forall X \in \Omega \ni x\text{. } X \ne x \implies \psi \equiv \forall X \in \Omega \setminus \{\, x \,\}\text{. } \psi
-  \]
+\begin{theorem}[Correctness of $\CR$]
+  Let $\phi$ be the input formula of \cref{alg:constraintremoval}, $(\Omega, x)$
+  a replaceable pair, and $\phi'$ the formula constructed by the algorithm, when
+  $(\Omega, x)$ is selected on \cref{line:crconditions}. Then
+  $\phi \equiv \phi'$, where the domain $\Omega'$ introduced on
+  \cref{line:newdomain} is interpreted as $\Omega \setminus \{\, x \,\}$.
+\end{theorem}
+\begin{proof}
+  Since there is a natural bijection between the clauses of $\phi$ and $\phi'$,
+  we shall argue about the equivalence of each pair of clauses. Let $c$ be an
+  arbitrary clause of $\phi$ and $c'$ its corresponding clause of $\phi'$.
+
+  If $c$ has no variables with domain $\Omega$, then it cannot have any
+  constraints involving $x$, so $c' = c$. Otherwise, for notational simplicity,
+  let us assume that $X$ is the only variable in $c$ with domain $\Omega$ (the
+  proof for an arbitrary number of variables is virtually the same). By
+  \cref{def:replaceable}, we can rewrite $c$ as $\forall X \in \Omega\text{.
+  } X \ne x \implies \psi$, where $\psi$ is a formula with $X$ as the only free
+  variable and with no mention of either $x$ or $\Omega$. Then
+  $c' \equiv \forall X \in \Omega'\text{. } \psi$. Since
+  $\Omega' \coloneqq \Omega \setminus \{\, x \,\}$, we have that $c \equiv c'$.
+  Since $c$ was an arbitrary clause of $\phi$, this completes the proof that
+  $\phi \equiv \phi'$.
 \end{proof}
@@
 % TODO: add an argument about why this recursion is (or can easily be made) finite
-\begin{proposition}[Correctness of $\Reff$]
-\end{proposition}
+\begin{theorem}[Correctness of $\Reff$]
+\end{theorem}
 \begin{proof} % TODO: finish (Proof technique: show a bijection between the sets of models)
@@
 
+\begin{theorem}
+  Any collection of functions returned by \textsc{Crane} can be evaluated in
+  time polynomial in domain sizes.
+\end{theorem}
+\begin{proof}% TODO (I have some handwritten notes)
+  % prove that all functions output by Crane can be computed in polytime (must, should be easy: 1) bound the number of possible arguments that any function can have, 2) prove that the computation time of any dynamic programming cell is always polytime (what about functions depending on other functions?))
+\end{proof}
+
 \section{Empirical Results}\label{sec:results}
-% TODO: when describing experimental results, say that a solution for the last
-% (unsolved) instance can be found, but is too complicated to evaluate by hand.
-% Add that the linear order axiom is also liftable. Cite the same paper in the
+% TODO: Add that the linear order axiom is also liftable. Cite the same paper in the
 % introduction as well.
 
-% TODO: make sure this table floats to the right page and look at other floating
-% objects too (e.g., is [t] on?)
+% TODO: make sure this table (as well as other floating objects) is on the right page
 \begin{table*}[t]
@@
 to solve many such instances. Note that other WFOMC
-algorithms---\textsc{L2C}~\cite{DBLP:conf/kr/KazemiP16} and probabilistic
-theorem proving~\cite{DBLP:journals/cacm/GogateD16}---are unable to solve any of
+algorithms---\textsc{L2C}~\cite{DBLP:conf/kr/KazemiP16}, probabilistic theorem
+proving~\cite{DBLP:journals/cacm/GogateD16}, and
+\textsc{FastWFOMC}~\cite{DBLP:conf/uai/BremenK21}---are unable to solve any of
 the instances that \textsc{ForcLift} fails on. We begin by describing how such
@@
   specified as part of the input, they are immaterial to the search procedure.}
-\textsc{ForcLift} is always run until it terminates; \textsc{Crane} is run until
-either five solutions are found or the search tree reaches height
-six.\footnote{The search tree has a high branching factor, so exploring all
-  nodes at depth five takes at most a few seconds, whereas doing the same for
-  depth six can be computationally infeasible in some cases.} If successful,
-\textsc{ForcLift} generates a circuit, and \textsc{Crane} generates one or more
-(complete) FCGs. In both cases, we manually convert the resulting graphs into
-definitions of functions as described in \cref{sec:interpret}. We then assess
-the complexity of each solution by hand and pick the best in case \textsc{Crane}
-returns several solutions of varying complexities.
+\textsc{Crane} is run in hybrid search mode until either five solutions are
+found or the search tree reaches height six.\footnote{The search tree has a high
+  branching factor, so exploring all nodes at depth five takes at most a few
+  seconds, whereas doing the same for depth six can be computationally
+  infeasible in some cases.} \textsc{ForcLift} is always run until it
+terminates. If successful, \textsc{ForcLift} generates a circuit, and
+\textsc{Crane} generates one or more (complete) FCGs. In both cases, we manually
+convert the resulting graphs into definitions of functions as described in
+\cref{sec:interpret}. We then assess the complexity of each solution by hand and
+pick the best in case \textsc{Crane} returns several solutions of varying
+complexities.
 
@@
 \textsc{ForcLift}, the two algorithms perform equally well. However,
-\textsc{Crane} can also solve all but one instances that \textsc{ForcLift} fails
-on in at most cubic time. See \cref{app:solutions} for the exact solutions
-produced by \textsc{Crane} that correspond to the complexity results in
-\cref{tbl:results}.
+\textsc{Crane} can also solve all but one of the instances that
+\textsc{ForcLift} fails on in at most cubic time. See \cref{app:solutions} for
+the exact solutions produced by \textsc{Crane} that correspond to the complexity
+results in \cref{tbl:results}.
 
 \section{Conclusion and Future Work}\label{sec:conclusion}
-
-% A summary of what's been done/achieved and how
 
@@
 
-% TODO: cite Lifted Reasoning for Combinatorial Counting
-
 \appendix
@@
 
-% TODO: fix the introductory description
-
-whose complexity is in \cref{tbl:results} (including those findable by
-\textsc{ForcLift}~\cite{DBLP:conf/ijcai/BroeckTMDR11}). Both before and after
-algebraic simplification, excluding multiplication by one. All of these
-solutions have been checked to be correct when combined with suitable base
-cases.
+In this appendix, we list the exact function definitions produced by
+\textsc{Crane} for all of the problem instances in \cref{sec:results} both
+before and after algebraic simplification (excluding multiplications by one).
+The correctness of all of them has been checked by identifying suitable base
+cases and verifying the numerical answers across a range of domain sizes.
 
@@
   \begin{align*}
-    \begin{split}
     f(m, n) ={}& \sum_{l=0}^{m} \binom{m}{l}{(-1)}^{m-l} \sum_{k=0}^{n} \binom{n}{k} {(-1)}^{n-k}\\
-                 &{\left( \sum_{j=0}^{k} \binom{k}{j} [j < 2] \right)}^{l}
-    \end{split}\\
+               &{\left( \sum_{j=0}^{k} \binom{k}{j} [j < 2] \right)}^{l} \\
     ={}& \sum_{l=0}^{m} \binom{m}{l}{(-1)}^{m-l} \sum_{k=0}^{n} \binom{n}{k} {(-1)}^{n-k} {(k+1)}^{l}.
@@
   \begin{align*}
-    \begin{split}
     f(m) ={}& \sum_{l=0}^{m} \binom{m}{l}{(-1)}^{m-l} \sum_{k=0}^{m} \binom{m}{k} {(-1)}^{m-k}\\
-              &{\left( \sum_{j=0}^{k} \binom{k}{j} [j < 2] \right)}^{l}
-    \end{split}\\
+            &{\left( \sum_{j=0}^{k} \binom{k}{j} [j < 2] \right)}^{l} \\
     ={}& \sum_{l=0}^{m} \binom{m}{l}{(-1)}^{m-l} \sum_{k=0}^{m} \binom{m}{k} {(-1)}^{m-k} {(k+1)}^{l}.
@@
     f(m) ={}& \sum_{l=0}^{m} \binom{m}{l} {(-1)}^{m-l} g(m, l); \\
-    \begin{split}
     g(m, l) ={}& \sum_{k=0}^{l} \binom{l}{k} [k < 2] g(m - 1, l - k)\\
     ={}& g(m - 1, l) + lg(m - 1, l - 1).
-    \end{split}
   \end{align*}
+  % \item $\Theta(m^{2})$ solution for counting $\Gamma \to \Gamma$ partial
+  %       injections:
+  % \begin{align*}
+  %   f(m) ={}& f(m - 1) + \sum_{l = 0}^{m} \binom{m}{l} \sum_{k = 0}^{m} \binom{m}{k}\\
+  %           &[1 \le l < 3] [k < 2] 2^{m - l} g(m - l, m - k - 1)\\
+  %   ={}& f(m - 1) + m2^{m-1}g(m-1, m-1)\\
+  %   +{}& m^{2}2^{m-1}g(m-1, m-2)\\
+  %   +{}& \binom{m}{2}2^{m-2}g(m-2, m-1) \\
+  %   +{}& \binom{m}{2}m2^{m-2}g(m-2, m-2)\\
+  %   g(i, j) ={}& \sum_{h = 0}^{j} \binom{j}{h} [h < 2] g(i - 1, j - h)\\
+  %   ={}& g(i-1, j) + jg(i-1, j-1).
+  %   \end{align*}
   \item $\Theta(m)$ solution for counting $\Gamma \to \Delta$ bijections:

### 2023-02-05 doc/paper/paper.tex
2/4 proofs complete (an overhaul of Preliminaries)

@@
 
-\title{Recursive Solutions to First-Order Model Counting}
-
-% TODO: double check how the university names should be formatted and the emails
-% TODO: read the formatting instructions and their LaTeX source
+\title{Synthesising Recursive Functions for First-Order Model Counting}
+
+% TODO: read the formatting instructions and their LaTeX source (email font?)
 % TODO: make sure there are no overflow errors
-% TODO: for arbitrary instances of '2022' (e.g., in citations), make it '2023'
 % TODO: maybe mention the term 'data complexity'
-% TODO: fix doom emacs warnings
+% TODO: make claim numbers subordinate to theorem numbers
+% TODO: mention that most of the work for this paper was done at UoE
+% TODO: the appendix should be in a separate file
+% TODO: cite some works about synthesis
+% TODO: clean up unnecessary things from the header (e.g., packages and definitions)
+% TODO: don't use the '\in' syntax for predicates
+% TODO: make sure I'm using \sigma instead of || everywhere
+% TODO: (at the end): grammarly the whole thing, put the appendix in a separate file
 \author{%
@@
 \affiliations
-$^1$National University of Singapore, Singapore\\
-$^2$University of Edinburgh, UK\\
+$^1$National University of Singapore, Singapore, Singapore\\
+$^2$University of Edinburgh, Edinburgh, UK\\
 \emails
@@
 
-\crefname{algocf}{algorithm}{Algorithms}
+\crefalias{diagram}{equation}
+\crefname{diagram}{Diagram}{Diagrams}
+\Crefname{diagram}{Diagram}{Diagrams}
+\creflabelformat{diagram}{#2\textup{(#1)}#3}
+
+\crefname{algocf}{Algorithm}{Algorithms}
 \Crefname{algocf}{Algorithm}{Algorithms}
+\crefname{condition}{Condition}{Conditions}
+\Crefname{condition}{Condition}{Conditions}
 
@@
 \DeclareMathOperator{\Doms}{Doms}
-\DeclareMathOperator{\MC}{MC}
 \DeclareMathOperator{\Vars}{Vars}
+\DeclareMathOperator{\Preds}{Preds}
 \SetKwProg{Fn}{Function}{:}{}
@@
 \section{Introduction}
+
+% TODO: In the introduction it is written: "Crane uses a hybrid search algorithm
+% that applies some rules greedily and some using breadth-first search". Which
+% rules are applied greedily and which are not? What is the reason for parting
+% from the usual greedy method?
+
+TODO: cite \textsc{Magician}~\cite{DBLP:conf/aaai/VenugopalSG15} and
+\textsc{Tuffy}~\cite{DBLP:journals/pvldb/NiuRDS11} (read the abstracts first,
+look at the code)
 
@@
 
+% TODO: I am not sure the statement of note 2 is correct since, in [van den
+% Broeck, IJCAI 2011], the compilation is described as follows: "Compiling a set
+% of c-clauses C to Fo d-DNNF is performed by the Compile(C) function, which
+% tries to recursively apply the compilation rules in the order we present
+% here". But then maybe the algorithm was not yet ForcLift.
+
 In this work, we show how to relax these restrictions in a way that results in a
@@
 rules via greedy\footnote{The algorithm is not described in any paper but can be
-  found in its source code at \url{https://dtai.cs.kuleuven.be/drupal/wfomc}}
+  found in its source code at \url{https://dtaid.cs.kuleuven.be/wfomc}}
 search, \textsc{Crane} also supports a hybrid search algorithm that applies some
@@
 represent recursive calls. Suppose the input formula $\phi$ depends on a domain
-of size $n \in \mathbb{N}$. \emph{Generalised domain recursion} (GDR)---one of
-the new compilation rules---transforms $\phi$ into a different formula $\psi$
+of size $n \in \mathbb{N}_{0}$. \emph{Generalised domain recursion} (GDR)---one
+of the new compilation rules---transforms $\phi$ into a different formula $\psi$
 that has an additional constant and some new \emph{constraints}. After some
@@
 constants, uppercase Latin letters for variables, and uppercase Greek letters
-for domains. An \emph{atom} is $p(t_1, \dots, t_n)$ for some predicate $p$ and
-terms $t_{1}, \dots, t_{n}$. A \emph{term} is either a constant or a variable. A
-\emph{literal} is either an atom or the negation of an atom (denoted by
-$\neg p(t_1, \dots, t_n)$). Let $\mathcal{D}$ be the set of all (finite)
-domains. Initially, $\mathcal{D}$ contains all domains mentioned by the input
-(W)FOMC instance. During compilation, new domains are added to $\mathcal{D}$ by
-some of the compilation rules. Each such new domain is interpreted as a subset
-of some element of $\mathcal{D}$.
+for domains. Sometimes we write predicate $p$ as $p/n$, where
+$n \in \mathbb{N}^{+}$ is the \emph{arity} of $p$. An \emph{atom} is
+$p(t_1, \dots, t_n)$ for some predicate $p/n$ and terms $t_{1}, \dots, t_{n}$. A
+\emph{term} is either a constant or a variable. A \emph{literal} is either an
+atom or the negation of an atom (denoted by $\neg p(t_1, \dots, t_n)$). Let
+$\mathcal{D}$ be the set of all relevant (finite) domains. Initially,
+$\mathcal{D}$ contains all domains mentioned by the input formula. During
+compilation, new domains are added to $\mathcal{D}$ by some of the compilation
+rules. Each such new domain is interpreted as a subset of some other domain in
+$\mathcal{D}$.
 
@@
 
-Similarly to variables in \cref{def:clause}, all constants are (implicitly)
-mapped to domains, and each $n$-ary predicate is implicitly mapped to a sequence
-of $n$ domains. For constant or variable $x$, predicate $p$, and domains
-$\Gamma$ and $\Delta$, we write, e.g., $x \in \Gamma$ and
-$p \in \Gamma \times \Delta$ to denote that $x$ is associated with $\Gamma$, and
-$p$ is associated with $\Gamma$ and $\Delta$ (in that order).
+\paragraph{Notation.}
+For any set $S$, let $2^{S}$ denote its power set and
+$S^{\ast} \coloneqq \bigcup_{i=0}^{\infty} S^{i}$ the set of tuples of any
+finite length of elements of $S$. For any $n \in \mathbb{N}_{0}$, let
+$[n] \coloneqq \{\, 1, \dots, n \,\}$. For example, $[0] = \emptyset$, and
+$[2] = \{\, 1, 2 \,\}$. We write $\langle\rangle$ for an empty list,
+$\langle x \rangle$ for a list with one element $x$, $|l|$ for the length of
+list $l$, and $\pfun$ to denote partial functions. Let $S$ be a set of
+constraints or literals, $V$ a set of variables, and $x$ a variable or a
+constant. We write $S[x/V]$ to denote $S$ with all occurrences of all variables
+in $V$ replaced with $x$. Let $\Doms$ (respectively, $\Preds$) be the function
+that maps any clause or formula to the set of domains (respectively, predicates)
+used within, and let $\dom(f)$ denote the domain of function $f$.
 
@@
   al.~\shortcite{DBLP:conf/ijcai/BroeckTMDR11}) is a set of clauses s.t.\ all
-  constraints and atoms `type check' with respect to domains.
+  constraints and atoms `type check' with respect to domains. Each formula
+  $\phi$ has a map $\pi_{\phi}\colon \Preds(\phi) \to {\Doms(\phi)}^{\ast}$ such
+  that, for each predicate $p/n \in \Preds(\phi)$, we have that
+  $\pi_{\phi}(p) \in {\Doms(\phi)}^{n}$.\footnote{Similarly to variables and
+    predicates, constants are also mapped to domains, although we keep this
+    mapping implicit.}
 \end{definition}
@@
   \end{align*}
-  for some predicate $p$, variables $X$, $Y$, $Z$, and domains $\Gamma$ and
-  $\Delta$. Then $\Vars(\{\, (Y, Z) \,\}) = \{\, Y, Z \,\}$, and
-  $\Vars(c_{1}) = \Vars(c_{2}) = \{\, X, Y, Z \,\}$. Based on the domain maps of
-  $c_{1}$ and $c_{2}$, we can infer that $p \in \Gamma \times \Delta$. All
-  variables (in both clauses) that occur as the first argument to $p$ are in
-  $\Gamma$, and, likewise, all variables that occur as the second argument to
-  $p$ are in $\Delta$. Therefore, $\phi$ `type checks' as a valid formula.
+  for some predicate $p/2$, variables $X$, $Y$, $Z$, and domains $\Gamma$ and
+  $\Delta$. Based on $\delta_{c_{1}}$ and $\delta_{c_{2}}$, we can infer that
+  $\pi_{\phi} = \{\, p \mapsto (\Gamma, \Delta) \,\}$. All variables that occur
+  as the first argument to $p$ are in $\Gamma$, and, likewise, all variables
+  that occur as the second argument to $p$ are in $\Delta$. Therefore, $\phi$
+  `type checks' as a valid formula.
 \end{example}
@@
 First, we decouple variable-to-domain assignments from constraints and move them
-to a separate function $\delta_{c}$ in \cref{def:clause}. Formalising these
-assignments as a function unveils the (previously implicit) assumption that each
-variable must be assigned to a domain. Second, while Van den Broeck et
-al.~\shortcite{DBLP:conf/ijcai/BroeckTMDR11} allow for equality constraints and
-constraints of the form $X \not\in \Delta$ for some variable $X$ and domain
-$\Delta$, we exclude such constraints simply because they are not needed.
-
-One can read a formula from \cref{def:formula} as a sentence in a FOL\@. All
-variables in a clause are implicitly universally quantified (but note that
-variables are never shared among clauses), and all clauses in a formula are
-implicitly linked by a conjunction. Thus, formula $\phi$ from
-\cref{example:first} reads as
+to a separate function $\delta_{c}$ in \cref{def:clause}. Second, while Van den
+Broeck et al.~\shortcite{DBLP:conf/ijcai/BroeckTMDR11} allow for equality
+constraints and constraints of the form $X \not\in \Delta$ for some variable $X$
+and domain $\Delta$, we exclude such constraints simply because they are not
+needed.
+
+One can read a formula in our format as a sentence in FOL\@. All variables in a
+clause are implicitly universally quantified (but note that variables are never
+shared among clauses), and all clauses in a formula are implicitly linked by a
+conjunction. Thus, formula $\phi$ from \cref{example:first} reads as
 \begin{align*}
@@
 
-Once domains are mapped to finite sets and constants to specific (and different)
-elements in those sets, a formula can be viewed as a set of conditions that the
-predicates (interpreted as relations) have to satisfy. Hence, FOMC is the
-problem of counting the number of combinations of relations that satisfy these
-conditions.
+Once domains are mapped to finite sets and constants to elements in those sets,
+a formula can be viewed as a set of conditions that the predicates (interpreted
+as relations) have to satisfy. Hence, FOMC is the problem of counting the number
+of combinations of relations that satisfy these conditions. To formalise this
+idea, let $\sigma\colon \mathcal{D} \to \mathbb{N}_{0}$ be the \emph{domain size
+  function} that maps each domain to a non-negative integer.
+
+\begin{definition}\label{def:model}
+  Let $\phi$ be a formula and $\sigma$ a domain size function. A \emph{model} of
+  $(\phi, \sigma)$ is a map
+  $\mathfrak{M}\colon \Preds(\phi) \to 2^{\mathbb{N}_{0}^{\ast}}$ such that the
+  following two conditions are satisfied.
+  \begin{enumerate}
+    \item Let $p/n \in \Preds(\phi)$ be a predicate and let
+          $\pi_{\phi}(p) = {(d_{i})}_{i=1}^{n}$ for some domains
+          $d_{i} \in \Doms(\phi)$. Then
+          \begin{equation}\label{eq:subset}
+            \mathfrak{M}(p) \subseteq \prod_{i=1}^{n}[\sigma(d_{i})].\footnote{For simplicity, \cref{def:model} ignores constants.
+To include constants, one would replace $[\sigma(d_{i})]$ with a set that contains all constants associated with domain $d_{i}$, extended with enough new elements to make its cardinality $\sigma(d_{i})$.}
+          \end{equation}
+    \item As a collection of relations, $\mathfrak{M}$ satisfies
+          $\phi$.
+  \end{enumerate}
+\end{definition}
 
 \begin{example}
-  Let $\phi$ be as in \cref{example:first} and let $|\Gamma| = |\Delta| = 2$.
-  There are $2^{2 \times 2} = 16$ possible relations between $\Gamma$ and
-  $\Delta$. Let us count how many of them satisfy the conditions imposed on
-  predicate $p$. The empty relation does. All four relations of cardinality one
-  do too. Finally, there are two relations of cardinality two that satisfy the
-  conditions as well. Thus, the FOMC of $\phi$ (when $|\Gamma| = |\Delta| = 2$)
-  is 7. Incidentally, the FOMC of $\phi$ counts partial injections. We will
-  continue to use the problem of counting partial injections (and the formula
-  from \cref{example:first} specifically) as the main running example throughout
-  the paper.
+  Let $\phi$ be as in \cref{example:first} and let
+  $\sigma(\Gamma) = \sigma(\Delta) = 2$. Then the right-hand side of
+  \cref{eq:subset} becomes
+  \[
+    [\sigma(\Gamma)] \times [\sigma(\Delta)] = [2] \times [2] = \{\,(1, 1), (1, 2), (2, 1), (2, 2)\,\}
+  \]
+  There are $2^{4} = 16$ possible relations between $\Gamma$ and $\Delta$. Let
+  us count how many of them satisfy the conditions imposed on predicate $p$. The
+  empty relation does. All four relations of cardinality one do too. Finally,
+  there are two relations of cardinality two that satisfy the conditions as
+  well. Thus, the FOMC of $(\phi, \sigma)$ is 7. Incidentally, it counts partial
+  injections. We will continue to use the problem of counting partial injections
+  (and the formula from \cref{example:first} specifically) as the main running
+  example throughout the paper.
 \end{example}
@@
 % not familiar but still need to get excited by the problem
-
-\paragraph*{Notation.}
-We write $\langle\rangle$ and $\langle x \rangle$ to denote an empty list and a
-list with one element $x$, respectively, and $|l|$ for the length of list $l$.
-We write $\pfun$ for partial functions. Let $S$ be a set of constraints or
-literals, $V$ a set of variables, and $x$ a variable or a constant. We write
-$S[x/V]$ to denote $S$ with all occurrences of all variables in $V$ replaced
-with $x$.
 
@@
 
-\paragraph{Notation.}
-Let $\Doms$ be a function that maps any clause or formula to the set of domains
-used within, and let $\dom(f)$ denote the domain of function $f$.
-
 \paragraph{Hashing.}
@@
 
-  \ForEach{formula and node $(\psi, v) \in C(\#\phi)$}{
+  \ForEach{formula and node $(\psi, v) \in C(\#\phi)$}{\label{line:selectformula}
     $\rho \gets \identifyRecursion{$\phi$, $\psi$}$\;
-    \lIf{$\rho \ne {\normalfont \texttt{null}}$}{\Return{$\{\, (\Reff_\rho(v), \langle\rangle) \,\}$}}
+    \lIf{$\rho \ne {\normalfont \texttt{null}}$}{\Return{$\{\, (\Reff_\rho(v), \langle\rangle) \,\}$}}\label{line:rho}
   }
@@
 
-% TODO: maybe something other than MC? Introduce the notation and the role of \sigma.
-% TODO: add an argument about why this recursion is (or can easily be made) finite
 \begin{theorem}[Correctness of $\Reff$]
+  Let $\phi$ be the formula used as input to \cref{alg:trycache}. Let $\psi$ be
+  any formula selected on \cref{line:selectformula} of the algorithm such that
+  $\rho \ne {\normalfont\texttt{null}}$ on \cref{line:rho}. Then the set of
+  models of $(\psi, \sigma \circ \rho)$ is equal to the set of models of
+  $(\phi, \sigma)$.
 \end{theorem}
-\begin{proof} % TODO: finish (Proof technique: show a bijection between the sets of models)
-  For a given formula $\phi$, \cref{alg:trycache} attempts to find a formula
-  $\psi$ and a map $\rho\colon \Doms(\psi) \to \Doms(\phi)$ such that
-  $\MC(\psi, \sigma \circ \rho\colon \Doms(\psi) \to \mathbb{N}_{0}) = \MC(\phi, \sigma\colon \Doms(\phi) \to \mathbb{N}_{0})$.
+\begin{proof}
+  We first show that the right-hand side of \cref{eq:subset} is the same for
+  models of both $(\phi, \sigma)$ and $(\psi, \sigma \circ \rho)$.
+  \Cref{alg:trycache} ensures that $\psi \equiv \phi$ up to domains. In
+  particular, this means that $\Preds(\psi) = \Preds(\phi)$. The square in
+  \begin{equation}\label[diagram]{diagram:ref}
+    \begin{tikzcd}
+      \Preds(\psi) \ar[equal]{r} \ar[d, swap, "\pi_{\psi}"] & \Preds(\phi) \ar[d, "\pi_{\phi}"] \\
+      {\Doms(\psi)}^{\ast} \ar[r, "\rho"] & {\Doms(\phi)}^{\ast} \ar[r, "\sigma"] & \mathbb{N}_{0}^{\ast}
+    \end{tikzcd}
+  \end{equation}
+  commutes by \cref{def:formula} and the definition of $\rho$. In other words,
+  for any predicate $p/n \in \Preds(\psi) = \Preds(\phi)$, function $\rho$
+  translates the domains associated with $p$ in $\psi$ to the domains associated
+  with $p$ in $\phi$. Let $\pi_{\phi}(p) = {(d_{i})}_{i=1}^{n}$ and
+  $\pi_{\psi}(p) = {(e_{i})}_{i=1}^{n}$ for some domains $d_{i} \in \Doms(\phi)$
+  and $e_{i} \in \Doms(\psi)$. Since $\rho(e_{i}) = d_{i}$ for all
+  $i = 1, \dots, n$ by the commutativity in \cref{diagram:ref}, we get that
+  \begin{equation}\label{eq:equality}
+    \prod_{i=1}^{n}[\sigma(d_{i})] = \prod_{i=1}^{n}[\sigma \circ \rho(e_{i})]
+  \end{equation}
+  as required. Certainly, any subset of the left-hand side of \cref{eq:equality}
+  (e.g., $\mathfrak{M}(p)$, where $\mathfrak{M}$ is a model of $(\phi, \sigma)$)
+  is a subset of the right-hand side and vice versa. Since $\phi$ and $\psi$
+  semantically only differ in what domains they refer to, every model of $\phi$
+  satisfies $\psi$ and vice versa, completing the proof.
 \end{proof}
@@
 \end{theorem}
-\begin{proof}% TODO (I have some handwritten notes)
-  % prove that all functions output by Crane can be computed in polytime (must, should be easy: 1) bound the number of possible arguments that any function can have, 2) prove that the computation time of any dynamic programming cell is always polytime (what about functions depending on other functions?))
+\begin{proof}
+  % 1) bound the number of possible arguments that any function can have
+  % 2) prove that the computation time of any dynamic programming cell is always polytime (what about functions depending on other functions?))
+  \begin{claim}
+    Infinite recursion is impossible because that would necessitate a sequence
+    of compilation rule applications that start with $\phi$ and end up with
+    exactly $\phi$ as one of the outcomes. This is impossible because... [argue
+    about formula length and the necessity to preserve domains and constants].
+  \end{claim}
+  \begin{claim}
+    Argument values cannot increase from one function call to another.
+  \end{claim}
+  \begin{claim}
+    Excluding functions, time to evaluate a function definition is polynomial
+    (e.g., binomials, linear sums, powers, multiplication, addition). The number
+    of operations within a definition is a constant that does not depend on
+    domain sizes.
+  \end{claim}
+  \begin{claim}
+    Describe a dynamic programming algorithm that:
+    \begin{itemize}
+      \item Gradually increases the sum of all domain sizes
+      \item Computes and stores the values of all function calls whose arguments
+            have that sum. Argue that there will always be an order in which
+            that's possible.
+    \end{itemize}
+  \end{claim}
+  NOTE: For proving that each cell is evaluated in polynomial time, I can just
+  cite the ForcLift completeness (and domain recursion) paper.
 \end{proof}
@@
 \section{Empirical Results}\label{sec:results}
-% TODO: Add that the linear order axiom is also liftable. Cite the same paper in the
-% introduction as well.
+
+TODO: Incidentally, the linear order axiom is also liftable. Cite the same
+paper~\cite{DBLP:journals/corr/abs-2211-01164} in the introduction as well.
 
@@
 
-% TODO: the correctness of all of these was confirmed by finding the right base
-% cases and checking whether the function definitions produce the right values
-% for a sufficiently high number of domain sizes.
-
-% TODO: in the acknowledgements, mention that most of the work was done at UoE
-% TODO: should the appendix be in the same file or not?
-% TODO: also mention that most of the work for this paper was done at UoE
-
 \bibliographystyle{kr}

### 2023-02-05 doc/talks/3_long/talk.tex
2/4 proofs complete (an overhaul of Preliminaries)

@@
 \usetikzlibrary{shapes}
-\usetikzlibrary{arrows}
-\usetikzlibrary{arrows.meta}
 \usetikzlibrary{positioning}
@@
 \usetikzlibrary{cd}
+\usetikzlibrary{calc}
 
@@
 \definecolor{color2}{HTML}{D95F02}
+\definecolor{highlightcolor}{HTML}{22373A}
 
@@
 % before it was 15 slides and 20 min
+% make sure there's a clear and coherent storyline
 % TODO: use \alert instead of \structure
 % TODO: replace capital latin letters with capital Greek letters
+% TODO: add a very clear example of what a model is
+% TODO: could add the step-by-step walkthrough of what FOKC looks like
 
@@
 \end{frame}
-% TODO: replace cat with 'Generate a picture of a monkey with a funny hat'
+% TODO: replace cat with 'Generate a picture of a monkey with a funny hat' (make sure it's legal to use)
 
-\begin{frame}[fragile]{Many Ways to Count}
+\begin{frame}[fragile]{There Are Many Ways to Count}
   \begin{center}
-    \begin{tikzcd}
-      \WMI{} & \WFOMI{} \\
-      \#\SAT{}/\WMC{} & \WFOMC{} \\
-      \AMC{}, \pbp{} & \SPPP{}
+    \begin{tikzcd}[remember picture]
+      |[alias=WMI]|\WMI{} & \WFOMI{} \\
+      |[alias=WMC]|\#\SAT{}/\WMC{} \ar[u] \ar[d] \ar[r] & \WFOMC{} \ar[u] \ar[d] \\
+      |[alias=PBP]|\AMC{}, \pbp{} & |[alias=SP]|\SPPP{}
     \end{tikzcd}
   \end{center}
+  \begin{overprint}
+    foo
+  \end{overprint}
+  \begin{tikzpicture}[overlay,remember picture]
+    \begin{scope}[transform canvas={xshift=-3em}]
+      \draw[->,draw=gray] ($(WMC)+(0,0.1)$)--($(WMI)+(0,0.5)$) node[midway,left] {\color{gray}{$\sum \to \int$}};
+      \draw[->,draw=gray] ($(WMC)-(0,0.1)$)--($(PBP)-(0,0.5)$) node[midway,left] {\color{gray}{Generalising weights}};
+    \end{scope}
+    \begin{scope}[transform canvas={yshift=-2em}]
+      \draw[->,draw=gray] ($(PBP)-(1,0)$)--($(SP)+(1,0)$) node[midway,below] {\color{gray}{From propositional to first-order logic}};
+    \end{scope}
+  \end{tikzpicture}
 \end{frame}
-% maybe mention #CSP and other non-SAT ways of counting
+% maybe mention #CSP and other non-SAT ways of counting (SMT?, counting paths in automata and directed graphs)
+% TODO: gradually reveal parts of this diagram (1. axes + #SAT + WMC, 2. extension to FOL (with bottom label), 3. integration 4. bottom row)
+% TODO: at the same time, show the full name and the reference for each at the bottom
+% TODO: for future work, come back to this slide and add more arrows (e.g., beyond FOL)
+
+% TODO: a big chunk of the introduction should provide motivation to my work (e.g., mention applications)
 

### 2023-02-06 doc/paper/paper.tex
3/4 proofs complete

@@
 \newtheorem{conjecture}{Conjecture}
-\newtheorem{claim}{Claim}
+\newtheorem{claim}{Claim}[theorem]
 \theoremstyle{definition}
@@
 
-% TODO: read the formatting instructions and their LaTeX source (email font?)
-% TODO: make sure there are no overflow errors
-% TODO: maybe mention the term 'data complexity'
-% TODO: make claim numbers subordinate to theorem numbers
-% TODO: mention that most of the work for this paper was done at UoE
-% TODO: the appendix should be in a separate file
-% TODO: cite some works about synthesis
-% TODO: clean up unnecessary things from the header (e.g., packages and definitions)
-% TODO: don't use the '\in' syntax for predicates
-% TODO: make sure I'm using \sigma instead of || everywhere
-% TODO: (at the end): grammarly the whole thing, put the appendix in a separate file
+% TODO (at the very end)
+% put the appendix in a separate file
+% grammarly the whole thing
+% read the formatting instructions and their LaTeX source (email font?)
+% make sure there are no overflow errors
+% clean up unnecessary things from the header (e.g., packages and definitions)
+
 \author{%
@@
 
+% TODO: maybe mention the term 'data complexity'
+% TODO: cite some works about synthesis
+
 % TODO: In the introduction it is written: "Crane uses a hybrid search algorithm
@@
     (\forall X \in \Gamma\text{. }\forall Y, Z \in \Delta\text{. }\\
-    Y \ne Z \implies \neg p(X, Y) \lor \neg p(X, Z)) \land
+    Y \ne Z \Rightarrow \neg p(X, Y) \lor \neg p(X, Z)) \land
     \end{multlined}\\
@@
     (\forall X, Z \in \Gamma\text{. }\forall Y \in \Delta\text{. }\\
-    X \ne Z \implies \neg p(X, Y) \lor \neg p(Z, Y)).
+    X \ne Z \Rightarrow \neg p(X, Y) \lor \neg p(Z, Y)).
     \end{multlined}
@@
     $\phi' \gets \emptyset$\;
-    $x \gets \text{a new constant in domain } \Omega$\;
+    $x \gets \text{a new constant in domain } \Omega$\;\label{line:constant}
     \ForEach{clause $c = (L, C, \delta) \in \phi$\label{line:forclause}}{
-      $V \gets \{\, X \in \Vars(L) \mid \delta(X) = \Omega \,\}$\;
-      \ForEach{subset $W \subseteq V$ s.t. $W^2 \cap C = \emptyset$ {\bf and} $W \cap \{\, X \in \Vars(C) \mid (X, y) \in C \text{ for some constant } y \,\} = \emptyset$\label{line:conditions}}{
+      $V \gets \{\, X \in \Vars(L) \mid \delta(X) = \Omega \,\}$\;\label{line:V}
+      \ForEach{$W \subseteq V$ s.t. $W^2 \cap C = \emptyset$ {\bf and} $W \cap \{\, X \in \Vars(C) \mid (X, y) \in C \text{ for some constant } y \,\} = \emptyset$\label{line:conditions}}{
         \tcc{$\delta'$ restricts $\delta$ to the new set of variables}
@@
 
-\begin{theorem}[Correctness of $\GDR$]
-  Let $\phi$ be the formula used as input to \cref{alg:domainrecursion} and
-  $\phi'$ be one of the formulas constructed by the algorithm. Then
-  $\phi \equiv \phi'$.
+\begin{theorem}[Correctness of $\GDR$\footnote{\Cref{thm:correctness1} is equivalent to
+    Proposition~3 by~\cite{DBLP:conf/nips/Broeck11}.}]\label{thm:correctness1}
+  Let $\phi$ be the formula used as input to \cref{alg:domainrecursion},
+  $\Omega \in \mathcal{D}$ the domain selected on \cref{line:condition}, and
+  $\phi'$ the formula constructed by the algorithm for $\Omega$. Assume that
+  $\Omega \ne \emptyset$. Then $\phi \equiv \phi'$.
 \end{theorem}
-\begin{proof} % TODO: finish (Proof technique: if one is true then the other one will be true and vice versa)
-  Let $\Omega \in \mathcal{D}$ be the domain selected by
-  \cref{line:condition} of the algorithm.
-  \begin{claim}\label{claim:logic}
+\begin{proof}
+  Let $x$ be the constant introduced on \cref{line:constant} and $c$ a clause of
+  $\phi$ selected on \cref{line:forclause} of the algorithm. We will show that
+  $c$ is equivalent to the conjunction of clauses added to $\phi'$ on
+  \cref{line:conditions,line:generation}.
+
+  If $c$ has no variables with domain $\Omega$, then
+  \cref{line:conditions,line:generation} simply add a copy of $c$ to $\phi'$. If
+  $c$ has one variable with domain $\Omega$, say, $X$, then
+  $c \equiv \forall X \in \Omega\text{. } \psi$ for some formula $\psi$ with one
+  free variable $X$. In this case, \cref{line:conditions,line:generation} create
+  two clauses: $\psi[x/\{\, X \,\}]$ and $\forall X \in \Omega\text{.
+  } X \ne x \Rightarrow \psi$. It is easy to see that their conjunction is
+  equivalent to $c$ provided that $\Omega \ne \emptyset$ and so $x$ is a
+  well-defined constant.
+
+  Let $V$ be the set of variables introduced on \cref{line:V}. It remains to
+  show that repeating the transformation
   \[
-    \forall X \in \Omega\text{. } \psi \equiv \psi[x/\{\, X \,\}] \land \forall X \in \Omega\text{. } X \ne x \implies \psi
+    \forall X \in \Omega\text{. } \psi \mapsto \{\, \psi[x/\{\, X \,\}], \forall X \in \Omega\text{. } X \ne x \Rightarrow \psi \,\}
   \]
-  \end{claim}
-  \begin{claim}
-    Iteration of \cref{claim:logic} for all variables in some set of variables
-    $V$ produces the same clauses as subset enumeration on
-    \cref{line:conditions}.
-  \end{claim}
+  for all variables $X \in V$ produces the same clauses as
+  \cref{line:conditions,line:generation} (except for some tautologies that the
+  latter method skips). Note that the order in which these operations are
+  applied is immaterial. In other words, if we add inequality constraints for
+  variables ${\{\, X_{i} \,\}}_{i=1}^{n}$, and apply substitution for variables
+  $V \setminus {\{\, X_{i} \,\}}_{i=1}^{n}$, then---regardless of the order of
+  operations---we get
+  \[
+    \forall X_{1}, \dots, X_{n} \in \Omega\text{.} \bigwedge_{i=1}^{n} X_{i} \ne x \Rightarrow \psi\left[x / \left(V \setminus {\{\, X_{i} \,\}}_{i=1}^{n}\right)\right].
+  \]
+  This formula is equivalent to the clause generated on \cref{line:generation}
+  with $W = V \setminus {\{\, X_{i} \,\}}_{i=1}^{n}$. Thus, for every clause $c$
+  of $\phi$, the new formula $\phi'$ gets a set of clauses whose conjunction is
+  equivalent to $c$. Hence, the two formulas are equivalent.
 \end{proof}
@@
   \cref{def:replaceable}, we can rewrite $c$ as $\forall X \in \Omega\text{.
-  } X \ne x \implies \psi$, where $\psi$ is a formula with $X$ as the only free
+  } X \ne x \Rightarrow \psi$, where $\psi$ is a formula with $X$ as the only free
   variable and with no mention of either $x$ or $\Omega$. Then
@@
 \section{How to Interpret an FCG}\label{sec:interpret}
+% TODO: make sure I'm using \sigma instead of || in this section
 
@@
   (not shown in \cref{fig:examplefcg}), which can be read as
-  $\forall X, Y \in \Delta^{\top}\text{. }X \ne Y \implies \bot$, i.e.,
+  $\forall X, Y \in \Delta^{\top}\text{. }X \ne Y \Rightarrow \bot$, i.e.,
   $\forall X, Y \in \Delta^{\top}\text{. }X = Y$. This latter sentence is true
@@
 
+% TODO: don't use the \in syntax
 % Describe what kind of instances we're investigating
@@
 \[
-  \forall X \in \Gamma\text{. }\forall Y,Z \in \Delta\text{. }p(X, Y) \land p(X, Z) \implies Y = Z
+  \forall X \in \Gamma\text{. }\forall Y,Z \in \Delta\text{. }p(X, Y) \land p(X, Z) \Rightarrow Y = Z
 \]
@@
 \[
-  \forall X,Z \in \Gamma\text{. }\forall Y \in \Delta\text{. }p(X, Y) \land p(Z, Y) \implies X = Z
+  \forall X,Z \in \Gamma\text{. }\forall Y \in \Delta\text{. }p(X, Y) \land p(Z, Y) \Rightarrow X = Z
 \]
@@
       (\forall X \in \Gamma\text{. }\forall Y, Z \in \Delta\text{. }\\
-      Y \ne Z \implies \neg p(X, Y) \lor \neg p(X, Z)) \land
+      Y \ne Z \Rightarrow \neg p(X, Y) \lor \neg p(X, Z)) \land
     \end{multlined}\\
@@
       (\forall X, Z \in \Gamma\text{. }\forall Y \in \Delta\text{. }\\
-      X \ne Z \implies \neg p(X, Y) \lor \neg p(Z, Y))
+      X \ne Z \Rightarrow \neg p(X, Y) \lor \neg p(Z, Y))
     \end{multlined}

### 2023-02-08 doc/paper/paper.tex
Some slides

@@
 \usepackage{siunitx}
+\usepackage{forest}
 \usetikzlibrary{cd}
@@
 % clean up unnecessary things from the header (e.g., packages and definitions)
+%  make sure the result table (as well as other floating objects) are on the right pages
 
@@
 
+\forestset{
+sn edges/.style={for tree={edge={-Latex}}}
+}
+
 \begin{document}
@@
 
-% TODO: I am not sure the statement of note 2 is correct since, in [van den
-% Broeck, IJCAI 2011], the compilation is described as follows: "Compiling a set
-% of c-clauses C to Fo d-DNNF is performed by the Compile(C) function, which
-% tries to recursively apply the compilation rules in the order we present
-% here". But then maybe the algorithm was not yet ForcLift.
-
 In this work, we show how to relax these restrictions in a way that results in a
@@
 both stages of the process. First, while \textsc{ForcLift} applies compilation
-rules via greedy\footnote{The algorithm is not described in any paper but can be
-  found in its source code at \url{https://dtaid.cs.kuleuven.be/wfomc}}
-search, \textsc{Crane} also supports a hybrid search algorithm that applies some
-rules greedily and some using breadth-first search. Second, the product of
-compilation is not directly evaluated but rather interpreted as a collection of
-functions on domain sizes.
+rules via greedy search, \textsc{Crane} also supports a hybrid search algorithm
+that applies some rules greedily and some using breadth-first search. Second,
+the product of compilation is not directly evaluated but rather interpreted as a
+collection of functions on domain sizes.
 
@@
 
+\begin{figure}
+  \centering
+  \begin{forest}
+    for tree={s sep=10mm, sn edges}
+    [$\bigwedge_{x \in \Delta}$,ellipse,draw,label=right:{\color{blue}{$3^{|\Delta|}$}}
+    [$\lor$,ellipse,draw,label=right:{\color{blue}{$2 + 1 = 3$}}
+    [$\land$,ellipse,draw,label=left:{\color{blue}{$2 \times 1 = 2$}}
+    [$p(x) \lor \neg p(x)$,rectangle,draw,fill=gray!25,label=below:{\color{blue}{2}}]
+    [$\land$,ellipse,draw,label={[label distance=0cm,text=blue]87:$1 \times 1 = 1$}
+    [$q(x)$,rectangle,draw,fill=gray!25,label=below:{\color{blue}{1}}]
+    [$\top$,rectangle,draw,fill=gray!25,label=below:{\color{blue}{1}}]
+    ]
+    ]
+    [$\land$,ellipse,draw,label=right:{\color{blue}{$1 \times 1 = 1$}}
+    [$\neg q(x)$,rectangle,draw,fill=gray!25,label=below:{\color{blue}{1}}]
+    [$p(x)$,rectangle,draw,fill=gray!25,label=below:{\color{blue}{1}}]
+    ]
+    ]
+    ]
+  \end{forest}
+  \caption{A circuit produced by \textsc{ForcLift} for the sentence
+    $\forall X \in \Delta\text{. } p(X) \lor q(X)$. Values and computations in
+    blue show how a bottom-up evaluation of the circuit computes the model
+    count of the sentence.}
+\end{figure}
+% TODO: integrate this figure into the text
+
 \begin{figure}[t]
   \centering
-  \begin{tikzpicture}[every node/.style={draw,ellipse},edge from
-    parent/.style={draw,-Latex},sibling distance=3cm]
-    \node (dr) {$\GDR_{\Gamma \gets \Gamma \setminus \{\, x \,\}}$}
-    child {node {$\bigvee_{\Delta^\top \subseteq \Delta}$}
-      child {node {$\CR_{\Gamma \mapsto \Gamma'}$}
-        child {
-          node[circle] {$\wedge$}
-          child {node {$\bot$}}
-          child {node (ref) {$\Reff_{\{\, \Gamma \mapsto \Gamma', \Delta \mapsto \Delta^{\bot} \,\}}$}}
-        }}};
-    \draw[-Latex, bend right] (ref) to (dr);
-  \end{tikzpicture}
+  \begin{forest}
+    for tree={sn edges}
+    [$\GDR_{\Gamma \gets \Gamma \setminus \{\, x \,\}}$,ellipse,draw,name=gdr
+    [$\bigvee_{\Delta^\top \subseteq \Delta}$,ellipse,draw
+    [$\CR_{\Gamma \mapsto \Gamma'}$,ellipse,draw
+    [$\land$,ellipse,draw
+    [$\bot$,rectangle,draw,fill=gray!25]
+    [$\Reff_{\{\, \Gamma \mapsto \Gamma', \Delta \mapsto \Delta^{\bot} \,\}}$,ellipse,draw,name=ref]
+    ]
+    ]
+    ]
+    ]
+    \draw[-Latex,bend right=45] (ref) to (gdr);
+  \end{forest}
   \caption{A simplified version of an FCG constructed by \textsc{Crane} for the
@@
 \end{figure}
-
-% TODO: Again for the reader who is not very familiar with this area it might be
-% good to at least give the circuit for one of the examples such as a
-% disjunction just to show them how it is usually done.
 
@@
   any formula selected on \cref{line:selectformula} of the algorithm such that
-  $\rho \ne {\normalfont\texttt{null}}$ on \cref{line:rho}. Then the set of
-  models of $(\psi, \sigma \circ \rho)$ is equal to the set of models of
-  $(\phi, \sigma)$.
+  $\rho \ne {\normalfont\texttt{null}}$ on \cref{line:rho}. Let $\sigma$ be a
+  domain size function. Then the set of models of $(\psi, \sigma \circ \rho)$ is
+  equal to the set of models of $(\phi, \sigma)$.
 \end{theorem}
@@
 \section{How to Interpret an FCG}\label{sec:interpret}
-% TODO: make sure I'm using \sigma instead of || in this section
 
@@
 
-\section{Empirical Results}\label{sec:results}
+\section{Experimental Results}\label{sec:results}
 
@@
 
-% TODO: make sure this table (as well as other floating objects) is on the right page
 \begin{table*}[t]
@@
 We compare \textsc{Crane} and
-\textsc{ForcLift}~\cite{DBLP:conf/ijcai/BroeckTMDR11} on their ability to count
-various kinds of functions. This class of instances is chosen because of its
-simplicity and ubiquity and the inability of state-of-the-art WFOMC algorithms
-to solve many such instances. Note that other WFOMC
-algorithms---\textsc{L2C}~\cite{DBLP:conf/kr/KazemiP16}, probabilistic theorem
-proving~\cite{DBLP:journals/cacm/GogateD16}, and
+\textsc{ForcLift}\footnote{\url{https://dtaid.cs.kuleuven.be/wfomc}}~\cite{DBLP:conf/ijcai/BroeckTMDR11}
+on their ability to count various kinds of functions. This class of instances is
+chosen because of its simplicity and ubiquity and the inability of
+state-of-the-art WFOMC algorithms to solve many such instances. Note that other
+WFOMC algorithms---\textsc{L2C}~\cite{DBLP:conf/kr/KazemiP16}, probabilistic
+theorem proving~\cite{DBLP:journals/cacm/GogateD16}, and
 \textsc{FastWFOMC}~\cite{DBLP:conf/uai/BremenK21}---are unable to solve any of
@@
 
-% TODO: don't use the \in syntax
-% Describe what kind of instances we're investigating
-Let $p \in \Gamma \times \Delta$ be a predicate. To restrict all relations
-representable by $p$ to just functions from $\Gamma$ to $\Delta$, in FOL one
+Let $p$ be a predicate that models relations between sets $\Gamma$ and $\Delta$.
+To restrict all such relations to just $\Gamma \to \Delta$ functions, in FOL one
 might write

### 2023-02-08 doc/talks/3_long/talk.tex
Some slides

--- 2023-01-30 doc/talks/3_long/talk.tex
@@
 \usepackage{complexity}
+\usepackage[style=authoryear]{biblatex}
 
 \usetikzlibrary{shapes}
-\usetikzlibrary{arrows}
-\usetikzlibrary{arrows.meta}
 \usetikzlibrary{positioning}
@@
 \setbeamercolor{background canvas}{bg=white}
+\addbibresource{talk.bib}
 %\usecolortheme{rose}
@@
 \definecolor{color2}{HTML}{D95F02}
+\definecolor{color3}{HTML}{7570b3}
+\definecolor{color4}{HTML}{e7298a}
+
+\newcommand{\x}{\textcolor{color1}{x}}
+\newcommand{\y}{\textcolor{color3}{y}}
+\newcommand{\pP}{\textcolor{color3}{P}}
+\newcommand{\dDelta}{\textcolor{color2}{\Delta}}
 
@@
 % before it was 15 slides and 20 min
+% make sure there's a clear and coherent storyline
 % TODO: use \alert instead of \structure
-% TODO: replace capital latin letters with capital Greek letters
+% TODO: add a very clear example of what a model is
+% TODO: could add the step-by-step walkthrough of what FOKC looks like
 
@@
 \institute{\inst{1} National University of Singapore, Singapore \and \inst{2} University of Edinburgh, UK}
-\date{TODO}
+\date{TODO: date}
 
@@
 \end{frame}
-% TODO: replace cat with 'Generate a picture of a monkey with a funny hat'
 
-\begin{frame}[fragile]{Many Ways to Count}
+\begin{frame}[fragile]{(Some of the) Many Ways to Count}
   \begin{center}
-    \begin{tikzcd}
-      \WMI{} & \WFOMI{} \\
-      \#\SAT{}/\WMC{} & \WFOMC{} \\
-      \AMC{}, \pbp{} & \SPPP{}
+    \begin{tikzcd}[remember picture]
+      |[alias=WMI,visible on=<7->]|\WMI{} & |[visible on=<7->]|\WFOMI{} \\
+      |[alias=WMC]|\#\SAT{}/\WMC{} \arrow[u,visible on=<7->] \ar[d,visible on=<8->] \ar[r,visible on=<5->] & |[visible on=<5->]|\WFOMC{} \arrow[u,visible on=<7->] \ar[d,visible on=<8->] \\
+      |[alias=PBP,visible on=<8->]|\AMC{}, \pbp{} & |[alias=SP,visible on=<8->]|\SPPP{}
     \end{tikzcd}
   \end{center}
+  \begin{tikzpicture}[overlay,remember picture]
+    \begin{scope}[transform canvas={xshift=-3em}]
+      \draw[->,draw=gray] ($(WMC)+(0,0.1)$)--($(WMI)+(0,0.5)$) node[midway,left,visible on=<7->] {\color{gray}{$\sum \to \int$}};
+      \draw[->,draw=gray] ($(WMC)-(0,0.1)$)--($(PBP)-(0,0.5)$) node[midway,left,visible on=<8->] {\color{gray}{Generalising weights}};
+    \end{scope}
+    \begin{scope}[transform canvas={yshift=-2em}]
+      \draw[->,draw=gray] ($(PBP)-(1,0)$)--($(SP)+(1,0)$) node[midway,below,visible on=<5->] {\color{gray}{From propositional to first-order logic}};
+    \end{scope}
+  \end{tikzpicture}
+  \vfill
+    \begin{overprint}
+      \onslide<1,2>
+      \begin{block}{\#SAT~\color{gray}{\parencite{DBLP:journals/tcs/Valiant79}}}
+        \begin{itemize}
+          \item Input formula: $\x \lor \y$
+          \item Interpretations: $\emptyset$, $\{\, \x \,\}$, $\{\, \y \,\}$,
+                $\{\, \x, \y \,\}$
+          \item Models: $\{\, \x \,\}$, $\{\, \y \,\}$, $\{\, \x, \y \,\}$
+          \item<2-> Answer (model count): 3
+        \end{itemize}
+      \end{block}
+      \onslide<3,4>
+      \begin{block}{Weighted Model Counting~\color{gray}{\parencite{DBLP:journals/ai/ChaviraD08}}}
+        \begin{itemize}
+          \item Input formula: $\x \lor \y$
+          \item Input weights: $\begin{aligned}[t]
+                                  &w(\x) = 0.3\text{, }w(\neg \x) = 0.7,\\
+                                  &w(\y) = 0.2\text{, }w(\neg \y) = 0.8
+                                \end{aligned}$
+          \item<4-> Answer (weighted model count):
+                $w(\x)w(\y) + w(\x)w(\neg \y) + w(\neg \x)w(\y) = 0.44$
+        \end{itemize}
+      \end{block}
+      \onslide<5,6>
+      \begin{block}{(Weighted) (Symmetric) First-Order Model Counting\\
+          \color{gray}{\parencite{DBLP:conf/ijcai/BroeckTMDR11}}}
+        \begin{itemize}
+          \item Input formula: $\forall \x \in \Delta\text{. }\pP(\x)$
+          \item Input weights: $w^{+}(\pP) = 0.3$, $w^{-}(\pP) = 0.7$
+          \item Input domain size(s): $|\dDelta| = 2$
+          \item<6-> Answer: ${(w^{+}(\pP))}^{|\dDelta|} = 0.09$
+        \end{itemize}
+      \end{block}
+      \onslide<7>
+      \begin{block}{Extensions to Continuous Domains}
+        \begin{itemize}
+          \item Weighted model integration
+          \begin{itemize}
+            \item \color{gray}{\parencite{DBLP:conf/ijcai/BellePB15}}
+          \end{itemize}
+          \item Weighted first-order model integration
+          \begin{itemize}
+            \item \color{gray}{\parencite{DBLP:conf/uai/FeldsteinB21}}
+          \end{itemize}
+        \end{itemize}
+      \end{block}
+      \onslide<8>
+      \begin{block}{Generalisations of the weight function}
+        \begin{itemize}
+          \item Algebraic model counting
+          \begin{itemize}
+            \item \textcolor{gray}{\parencite{DBLP:journals/japll/KimmigBR17}}
+            \item From $\mathbb{R}_{\ge 0}$ to commutative semirings
+          \end{itemize}
+          \item Pseudo-Boolean projection~\textcolor{gray}{\parencite{DBLP:conf/sat/DilkasB21}}
+          \begin{itemize}
+            \item Weights not necessarily on literals
+          \end{itemize}
+          \item Semiring programming~\color{gray}{\parencite{DBLP:journals/ijar/BelleR20}}
+        \end{itemize}
+      \end{block}
+    \end{overprint}
 \end{frame}
-% maybe mention #CSP and other non-SAT ways of counting
+% maybe mention #CSP and other non-SAT ways of counting (SMT?, counting paths in automata and directed graphs)
+
+% TODO: for future work, come back to this slide and add more arrows (e.g., beyond FOL)
+
+% TODO: a big chunk of the introduction should provide motivation to my work (e.g., mention applications) (maybe before this slide?)
 
@@
   \begin{itemize}
-    \item Let \alert{$M$} and \alert{$N$} be sets (i.e., domains)
+    \item Let \alert{$\Gamma$} and \alert{$\Delta$} be sets (i.e., domains)
     \begin{itemize}
-      \item such that \alert{$|M| = m$}, and \alert{$|N| = n$}.
+      \item such that \alert{$|\Gamma| = m$}, and \alert{$|\Delta| = n$}.
     \end{itemize}
-    \item Let \alert{$P \subseteq M \times N$} be a relation (i.e., predicate)
-          over \alert{$M$} and \alert{$N$}.
+    \item Let \alert{$P \subseteq \Gamma \times \Delta$} be a relation (i.e.,
+          predicate) over \alert{$\Gamma$} and \alert{$\Delta$}.
     \item We can describe all of the constraints in first-order logic:
@@
       \[
-        \forall x \in M\text{. }\exists y \in N\text{. }P(x, y)
+        \forall x \in \Gamma\text{. }\exists y \in \Delta\text{. }P(x, y)
       \]
@@
       \[
-        \forall x \in M\text{. }\forall y, z \in N\text{. }P(x, y) \land P(x, z) \Rightarrow y=z
+        \forall x \in \Gamma\text{. }\forall y, z \in \Delta\text{. }P(x, y) \land P(x, z) \Rightarrow y=z
       \]
@@
       \[
-        \forall w, x \in M\text{. }\forall y \in N\text{. }P(w, y) \land P(x, y) \Rightarrow w=x
+        \forall w, x \in \Gamma\text{. }\forall y \in \Delta\text{. }P(w, y) \land P(x, y) \Rightarrow w=x
       \]
@@
 
-% TODO: maybe meat makes more sense than sandwich? Or a picture of recursion, e.g., fractals?
-{ % all template changes are local to this group.
-    \setbeamertemplate{navigation symbols}{}
-    \begin{frame}<article:0>[plain]
-        \begin{tikzpicture}[remember picture,overlay]
-            \node[at=(current page.center)] {
-                \includegraphics[keepaspectratio, width=\paperwidth]{sandwich.jpg}
-            };
-        \end{tikzpicture}
+{
+  \usebackgroundtemplate{\includegraphics[keepaspectratio,width=\paperwidth]{matryoshka.jpg}}
+  \begin{frame}{Recursion}
   \end{frame}
@@
   \begin{gather}
-    ({\color{color1} \forall x, y \in L\text{. }x=y}) \land \label{eq:1} \tag{{\color{color1} 1}} \\
-    ({\color{color2} \forall x \in M\text{. }\forall y, z \in N\text{. }P(x, y) \land P(x, z) \Rightarrow y=z}) \land \label{eq:2} \tag{{\color{color2} 2}} \\
-    ({\color{color2} \forall w, x \in M\text{. }\forall y \in N\text{. }P(w, y) \land P(x, y) \Rightarrow w=x}) \label{eq:3} \tag{{\color{color2} 3}}
+    ({\color{color1} \forall x, y \in \Omega\text{. }x=y}) \land \label{eq:1} \tag{{\color{color1} 1}} \\
+    ({\color{color2} \forall x \in \Gamma\text{. }\forall y, z \in \Delta\text{. }P(x, y) \land P(x, z) \Rightarrow y=z}) \land \label{eq:2} \tag{{\color{color2} 2}} \\
+    ({\color{color2} \forall w, x \in \Gamma\text{. }\forall y \in \Delta\text{. }P(w, y) \land P(x, y) \Rightarrow w=x}) \label{eq:3} \tag{{\color{color2} 3}}
   \end{gather}
@@
             \[
-              \forall x \in M\text{. }\forall y, z \in N\text{. }y \ne z \Rightarrow \neg P(x, y) \lor \neg P(x, z)
+              \forall x \in \Gamma\text{. }\forall y, z \in \Delta\text{. }y \ne z \Rightarrow \neg P(x, y) \lor \neg P(x, z)
             \]
-            Output formula (with a new constant \structure{$c \in M$}):
+            Output formula (with a new constant \structure{$c \in \Gamma$}):
             \begin{gather*}
-              \forall y, z \in N\text{. }y \ne z \Rightarrow \neg P(\alert{c}, y) \lor \neg P(\alert{c}, z) \\
+              \forall y, z \in \Delta\text{. }y \ne z \Rightarrow \neg P(\alert{c}, y) \lor \neg P(\alert{c}, z) \\
               \begin{multlined}
-                \forall x \in M\text{. }\forall y, z \in N\text{. }\alert{x \ne c} \land y \ne z \Rightarrow \\
+                \forall x \in \Gamma\text{. }\forall y, z \in \Delta\text{. }\alert{x \ne c} \land y \ne z \Rightarrow \\
                 \neg P(x, y) \lor \neg P(x, z)
@@
             %% \end{tikzpicture}
-            %% Here, domain recursion is applied to domain \structure{$M$}. It could similarly be applied to \structure{$N$} as well.
           \end{example}
@@
           \begin{example}
-            Input formula (with a constant \structure{$c \in M$}):
+            Input formula (with a constant \structure{$c \in \Gamma$}):
             \begin{gather*}
               \begin{multlined}
-                \forall x \in \alert{M}\text{. }\forall y, z \in N\text{. }\alert{x \ne c} \land y \ne z \Rightarrow \\
+                \forall x \in \alert{\Gamma}\text{. }\forall y, z \in \Delta\text{. }\alert{x \ne c} \land y \ne z \Rightarrow \\
                 \neg P(x, y) \lor \neg P(x, z)
@@
               \begin{multlined}
-                \forall w,x \in \alert{M}\text{. }\forall y \in N\text{. }\alert{w \ne c} \land \alert{x \ne c} \land w \ne x \Rightarrow \\
+                \forall w,x \in \alert{\Gamma}\text{. }\forall y \in \Delta\text{. }\alert{w \ne c} \land \alert{x \ne c} \land w \ne x \Rightarrow \\
                 \neg P(w, y) \lor \neg P(x, y)
@@
             \end{gather*}
-            Output formula (with a new domain \structure{$M' \coloneqq M \setminus \{\, c \,\}$}):
+            Output formula (with a new domain \structure{$\Gamma' \coloneqq \Gamma \setminus \{\, c \,\}$}):
             \begin{gather*}
-              \forall x \in \alert{M'}\text{. }\forall y, z \in N\text{. }y \ne z \Rightarrow \neg P(x, y) \lor \neg P(x, z) \\
-              \forall w,x \in \alert{M'}\text{. }\forall y \in N\text{. }w \ne x \Rightarrow \neg P(w, y) \lor \neg P(x, y)
+              \forall x \in \alert{\Gamma'}\text{. }\forall y, z \in \Delta\text{. }y \ne z \Rightarrow \neg P(x, y) \lor \neg P(x, z) \\
+              \forall w,x \in \alert{\Gamma'}\text{. }\forall y \in \Delta\text{. }w \ne x \Rightarrow \neg P(w, y) \lor \neg P(x, y)
             \end{gather*}
@@
 \begin{frame}{Resulting Improvements to Counting Functions}
-  Let \structure{$M$} and \structure{$N$} be two sets with cardinalities
-  \structure{$|M| = m$} and \structure{$|N| = n$}.
+  Let \structure{$\Gamma$} and \structure{$\Delta$} be two sets with
+  cardinalities \structure{$|\Gamma| = m$} and \structure{$|\Delta| = n$}.
 
   Our new rules enable \textsc{ForcLift} to efficiently count
-  \structure{$M \to N$} functions such as:
+  \structure{$\Gamma \to \Delta$} functions such as:
   \begin{itemize}
@@
 \end{frame}
+% TODO: mention Crane
+% TODO: mention that everything used to be unliftable (by any algorithm with a publicly available implementation)
 

### 2023-02-13 doc/paper/paper.tex
Improvements to the paper and more slides

@@
 % \newtheorem{example}{Example}
-% \newtheorem{theorem}{Theorem}
 \newtheorem{theorem}{Theorem}
+\newtheorem{fact}{Fact}
+\newtheorem{proposition}{Proposition}
 \newtheorem{conjecture}{Conjecture}
@@
 %  make sure the result table (as well as other floating objects) are on the right pages
+
+% TODO: use \textt for predicates (e.g., p, q), introduce the notation, use DeclareMathOperator
 
@@
 \newcommand{\IFO}{$\mathsf{I}\mathsf{FO}^{2}$}
+
+\DeclareMathOperator{\friends}{\texttt{friends}}
+\DeclareMathOperator{\smokes}{\texttt{smokes}}
 \DeclareMathOperator{\CR}{\textsc{CR}}
@@
 \SetKwFunction{generateMaps}{genMaps}
+
 \makeatletter
@@
 
-\section{Introduction}
-
-% TODO: maybe mention the term 'data complexity'
+\section{Introduction}\label{sec:introduction}
+
 % TODO: cite some works about synthesis
@@
 % from the usual greedy method?
-
-TODO: cite \textsc{Magician}~\cite{DBLP:conf/aaai/VenugopalSG15} and
-\textsc{Tuffy}~\cite{DBLP:journals/pvldb/NiuRDS11} (read the abstracts first,
-look at the code)
 
@@
 a sentence with three variables for which FOMC is $\#\P_{1}$-complete (i.e.,
-\FOthree{} is not liftable). Since these two results came out, most of the
+\FOthree{} is not liftable). Since these two seminal results, most of the
 research on (W)FOMC focused on developing faster solutions for the \FOtwo{}
@@
 quantifiers)~\cite{DBLP:journals/jair/Kuzelka21,DBLP:conf/aaai/MalhotraS22}. On
-the empirical front, there are several open-source implementations of exact
-WFOMC algorithms: \textsc{ForcLift}~\cite{DBLP:conf/ijcai/BroeckTMDR11},
-probabilistic theorem proving~\cite{DBLP:journals/cacm/GogateD16},
-\textsc{L2C}~\cite{DBLP:conf/kr/KazemiP16}, and
-\textsc{FastWFOMC}~\cite{DBLP:conf/uai/BremenK21}. Approximate counting is
-supported by \textsc{ApproxWFOMC}~\cite{DBLP:conf/ijcai/BremenK20} as well as
-\textsc{ForcLift}~\cite{DBLP:conf/uai/BroeckCD12} and probabilistic theorem
-proving~\cite{DBLP:journals/cacm/GogateD16}.
+the empirical front, there are several implementations of exact WFOMC
+algorithms: \textsc{Alchemy}~\cite{DBLP:journals/cacm/GogateD16},
+\textsc{FastWFOMC}~\cite{DBLP:conf/uai/BremenK21},
+\textsc{ForcLift}~\cite{DBLP:conf/ijcai/BroeckTMDR11}, and
+\textsc{L2C}~\cite{DBLP:conf/kr/KazemiP16}. Approximate counting is
+supported by \textsc{Alchemy}~\cite{DBLP:journals/cacm/GogateD16},
+\textsc{ApproxWFOMC}~\cite{DBLP:conf/ijcai/BremenK20},
+\textsc{ForcLift}~\cite{DBLP:conf/uai/BroeckCD12},
+\textsc{Magician}~\cite{DBLP:conf/aaai/VenugopalSG15}, and
+\textsc{Tuffy}~\cite{DBLP:journals/pvldb/NiuRDS11}.
+
+% Magician: an approach to improve the efficiency of sampling and local search
+% based MLN inference algorithms by utilising \#CSP algorithms. Tuffy: grounding
+% and stochastic local search.
 
@@
 as relations) have to satisfy. Hence, FOMC is the problem of counting the number
-of combinations of relations that satisfy these conditions. To formalise this
-idea, let $\sigma\colon \mathcal{D} \to \mathbb{N}_{0}$ be the \emph{domain size
-  function} that maps each domain to a non-negative integer.
+of combinations of relations that satisfy these conditions.
+
+\begin{example}\label{example:simple}
+  Let $\Delta$ be a domain of size $n \in \mathbb{N}_{0}$. The model count of
+  $\forall X \in \Delta\text{. } p(X) \lor q(X)$ is then $3^{n}$. Intuitively,
+  since both predicates are of arity one, they can be interpreted as subsets of
+  $\Delta$. Thus, the formula says that each element of $\Delta$ has to be
+  included in $p$ or in $q$ or in both, i.e., there are three possibilities.
+\end{example}
+
+\begin{example}
+  Consider a variant of the well-known `friends and smokers' example
+  $\forall X, Y \in \Delta\text{.
+  } \smokes(X) \land \friends(X, Y) \Rightarrow \smokes(Y)$. Letting
+  $n \coloneqq |\Delta|$ as in \cref{example:simple}, the model count can be
+  expressed as
+  $\sum_{k=0}^{n} \binom{n}{k}2^{n^{2} - k(n-k)}$~\cite{DBLP:conf/kr/BroeckMD14}.
+\end{example}
+
+To formalise the idea of a model, let
+$\sigma\colon \mathcal{D} \to \mathbb{N}_{0}$ be the \emph{domain size function}
+that maps each domain to a non-negative integer.
 
@@
 \end{example}
-% TODO: It might be useful to give one or two readable examples with interesting
-% model counts. For example Px v Qx over domain n has 3^n solutions. I think
-% The Frends smokers example has a more complicated solution you can find in one
-% of the papers. It might motivate the framework generally speaking better
-% although of course you can continue to use the same running example for the
-% rest of your paper. Such examples are especially useful for readers who are
-% not familiar but still need to get excited by the problem
 
@@
 
-\begin{theorem}
-  Any collection of functions returned by \textsc{Crane} can be evaluated in
-  time polynomial in domain sizes.
-\end{theorem}
-\begin{proof}
-  % 1) bound the number of possible arguments that any function can have
-  % 2) prove that the computation time of any dynamic programming cell is always polytime (what about functions depending on other functions?))
-  \begin{claim}
-    Infinite recursion is impossible because that would necessitate a sequence
-    of compilation rule applications that start with $\phi$ and end up with
-    exactly $\phi$ as one of the outcomes. This is impossible because... [argue
-    about formula length and the necessity to preserve domains and constants].
-  \end{claim}
-  \begin{claim}
-    Argument values cannot increase from one function call to another.
-  \end{claim}
-  \begin{claim}
-    Excluding functions, time to evaluate a function definition is polynomial
-    (e.g., binomials, linear sums, powers, multiplication, addition). The number
-    of operations within a definition is a constant that does not depend on
-    domain sizes.
-  \end{claim}
-  \begin{claim}
-    Describe a dynamic programming algorithm that:
-    \begin{itemize}
-      \item Gradually increases the sum of all domain sizes
-      \item Computes and stores the values of all function calls whose arguments
-            have that sum. Argue that there will always be an order in which
-            that's possible.
-    \end{itemize}
-  \end{claim}
-  NOTE: For proving that each cell is evaluated in polynomial time, I can just
-  cite the ForcLift completeness (and domain recursion) paper.
-\end{proof}
-
 \section{Experimental Results}\label{sec:results}
@@
 state-of-the-art WFOMC algorithms to solve many such instances. Note that other
-WFOMC algorithms---\textsc{L2C}~\cite{DBLP:conf/kr/KazemiP16}, probabilistic
-theorem proving~\cite{DBLP:journals/cacm/GogateD16}, and
-\textsc{FastWFOMC}~\cite{DBLP:conf/uai/BremenK21}---are unable to solve any of
+WFOMC algorithms mentioned in \cref{sec:introduction} are unable to solve any of
 the instances that \textsc{ForcLift} fails on. We begin by describing how such

### 2023-02-13 solutions.py

@@ -267,9 +267,9 @@ def factorial(n):
     return sum(math.comb(n, k) * sum(math.comb(n, l) * (l + 1) ** k * (-1) ** (2 * n - k - l) for l in range(n + 1)) for k in range(n + 1))
 
 def friendsmoker(n):
-    return 2**n * sum(math.comb(n, m) * 2**((n-m)*n*m) for m in range(n + 1))
+    return 2**n * sum(math.comb(n, m) * 2**((n-m)*(n-m-1) + (n-m)*m + m*(m-1)) for m in range(n + 1))
 
-MAX = 6
+MAX = 10
 
 # for m in range(1, MAX):
 #     for n in range(1, MAX):
@@ -291,20 +291,20 @@ MAX = 6
 #             )
 #         )
 
-for n in range(0, MAX):
-    print(
-        "f({}) = {} ({}, {})".format(
-            n,
-            crane_one_dimensional_partial_injections(n),
-            two_dimensional_partial_injections(n, n),
-            partial_injections_final(n, n)
-        )
-    )
-
 # for n in range(0, MAX):
 #     print(
-#         "f({}) = {}".format(
+#         "f({}) = {} ({}, {})".format(
 #             n,
-#             friendsmoker(n)
+#             crane_one_dimensional_partial_injections(n),
+#             two_dimensional_partial_injections(n, n),
+#             partial_injections_final(n, n)
 #         )
 #     )
+
+for n in range(0, MAX):
+    print(
+        "f({}) = {}".format(
+            n,
+            friendsmoker(n)
+        )
+    )

### 2023-02-13 doc/paper/paper.tex
Improvements to Section 3

@@
 \usepackage{forest}
+\usepackage[inline]{enumitem}
+
 \usetikzlibrary{cd}
@@
 \textsc{ForcLift}~\cite{DBLP:conf/ijcai/BroeckTMDR11}, and
-\textsc{L2C}~\cite{DBLP:conf/kr/KazemiP16}. Approximate counting is
-supported by \textsc{Alchemy}~\cite{DBLP:journals/cacm/GogateD16},
-\textsc{ApproxWFOMC}~\cite{DBLP:conf/ijcai/BremenK20},
+\textsc{L2C}~\cite{DBLP:conf/kr/KazemiP16}. Approximate counting is supported by
+\textsc{Alchemy}, \textsc{ApproxWFOMC}~\cite{DBLP:conf/ijcai/BremenK20},
 \textsc{ForcLift}~\cite{DBLP:conf/uai/BroeckCD12},
@@
     for tree={s sep=10mm, sn edges}
-    [$\bigwedge_{x \in \Delta}$,ellipse,draw,label=right:{\color{blue}{$3^{|\Delta|}$}}
+    [$\bigwedge_{x \in \Delta}$,ellipse,draw,label=right:{\color{blue}{$3^{n}$}}
     [$\lor$,ellipse,draw,label=right:{\color{blue}{$2 + 1 = 3$}}
@@
   \end{forest}
-  \caption{A circuit produced by \textsc{ForcLift} for the sentence
-    $\forall X \in \Delta\text{. } p(X) \lor q(X)$. Values and computations in
-    blue show how a bottom-up evaluation of the circuit computes the model
-    count of the sentence.}
+  \caption{A circuit produced by \textsc{ForcLift} for \cref{example:simple}.
+    Values and computations in blue (on the outside of each node) show how a
+    bottom-up evaluation of the circuit computes the model
+    count.}\label{fig:simplecircuit}
 \end{figure}
-% TODO: integrate this figure into the text
+
+Darwiche~\shortcite{DBLP:journals/jancl/Darwiche01} introduced
+\emph{deterministic decomposable negation normal form} (d-DNNF) circuits for
+propositional knowledge compilation and showed that the model count of a
+propositional formula can be computed in time linear in the size of the circuit.
+Van den Broeck et al.~\shortcite{DBLP:conf/ijcai/BroeckTMDR11} generalised them
+to FOL via \emph{first-order d-DNNF (FO d-DNNF) circuits}. FO d-DNNF circuits
+(hereafter simply called \emph{circuits}) are directed acyclic graphs with nodes
+corresponding to formulas in FOL---see \cref{fig:simplecircuit} for an example.
+The following types of nodes are supported by \textsc{ForcLift}: caching
+($\Reff$), contradiction ($\bot$), tautology ($\top$), decomposable conjunction
+($\land$), decomposable set-conjunction ($\bigwedge$), deterministic disjunction
+($\lor$), deterministic set-disjunction ($\bigvee$), domain recursion,
+grounding, inclusion-exclusion, smoothing, and unit clause. We refer the reader
+to previous work~\cite{DBLP:conf/nips/Broeck11,DBLP:conf/ijcai/BroeckTMDR11} for
+more information about node types and their interpretations for computing the
+(W)FOMC\@.
 
@@
   \end{forest}
-  \caption{A simplified version of an FCG constructed by \textsc{Crane} for the
-    problem of counting partial injections from \cref{example:first}. Label
-    $\bigvee_{\Delta^\top \subseteq \Delta}$ denotes set-disjunction, $\land$
-    denotes conjunction, and $\bot$ denotes a contradiction---see the work by
-    Van den Broeck et al.~\protect\shortcite{DBLP:conf/ijcai/BroeckTMDR11} for
-    the descriptions of these node types. Here we omit some parameters as well
-    as nodes whose only arithmetic effect is multiplication by
-    one.}\label{fig:examplefcg}
+  \caption{A simplified version of the FCG constructed by \textsc{Crane} for the
+    problem of counting partial injections from \cref{example:first}. Here we
+    omit some parameters as well as nodes whose only arithmetic effect is
+    multiplication by one.}\label{fig:examplefcg}
 \end{figure}
 
-A \emph{first-order deterministic decomposable negation normal form
-  computational graph} (FCG) is a (weakly connected) directed graph with a
-single source, node labels, and ordered outgoing edges. Node
-labels consist of two parts: the \emph{type} and the \emph{parameters}. The type
-of a node determines its out-degree.
-
-% TODO: I think there is a point of confusion here. Firstly the work of guy
-% introduce circuits and I presume that you want to say that the node types are
-% present in both the circuits as well as your structure. Given that I think you
-% should start of the paragraph by saying that like with circuit introduced by
-% Guy, there are node type such as XYZN. In addition to those you will be
-% introducing the following new ones.
-%
-% I think the other point that is not made very clear is that you have no
-% formally defined circuits. So perhaps if you could introduce a quick
-% definition and then say that we have the same building blocks as those, ie
-% nodes, but with a different graphical structure it will become clearer
-
-Along with many node types defined
-previously~\cite{DBLP:conf/nips/Broeck11,DBLP:conf/ijcai/BroeckTMDR11},
-\textsc{Crane} uses three more:
-\begin{itemize}
-  \item a type for constraint removal denoted by $\CR$,
-  \item a type for generalised domain recursion denoted by $\GDR$ (both with
-        out-degree one),
-  \item and $\star$---a placeholder type (with out-degree zero) for nodes that
-        are going to be replaced.
-\end{itemize}
-Similarly to Van den Broeck et al.~\shortcite{DBLP:conf/ijcai/BroeckTMDR11}, we
-write $T_p$ for an FCG that has a node with the label $T_p$ (i.e., type $T$ and
-parameter(s) $p$) and $\star$'s as all of its direct successors. See
-\cref{fig:examplefcg} for an example FCG\@. Its source node has out-degree 1,
-label $\GDR_{\Gamma \gets \Gamma \setminus \{\, x \,\}}$, and type $\GDR$.
+In this paper, we introduce \emph{FO d-DNNF computational graphs} (FCGs) that
+generalise circuits by dispensing with acyclicity. Formally, an FCG is a (weakly
+connected) directed graph with a single source, node labels, and ordered
+outgoing edges. Node labels consist of two parts: the \emph{type} and the
+\emph{parameters}. The type of a node determines its out-degree. We make the
+following changes and additions to the node types already supported by
+\textsc{ForcLift}. First, we introduce a new node type for constraint removal
+($\CR$). Second, we replace domain recursion with generalised domain recursion
+($\GDR$). And third, for reasoning about partially-constructed FCGs, we write
+$\star$ for a placeholder type that is yet to be replaced. Similarly to Van den
+Broeck et al.~\shortcite{DBLP:conf/ijcai/BroeckTMDR11}, we write $T_p$ for an
+FCG that has a node with the label $T_p$ (i.e., type $T$ and parameter(s) $p$)
+and $\star$'s as all of its direct successors. See \cref{fig:examplefcg} for an
+example FCG\@. Its source node has out-degree 1, label
+$\GDR_{\Gamma \gets \Gamma \setminus \{\, x \,\}}$, and type $\GDR$.
 

### 2023-02-14 doc/paper/paper.tex
Formatting changes

@@
 % TODO: use \textt for predicates (e.g., p, q), introduce the notation, use DeclareMathOperator
+% TODO: cite the linear order axiom paper \cite{DBLP:journals/corr/abs-2211-01164} in the introduction
+% TODO: introduction: move the huge footnote to the main text
 
@@
 translate sentences in a variant of function-free many-sorted FOL with equality
-to this internal format. We use lowercase Latin letters for predicates and
-constants, uppercase Latin letters for variables, and uppercase Greek letters
-for domains. Sometimes we write predicate $p$ as $p/n$, where
-$n \in \mathbb{N}^{+}$ is the \emph{arity} of $p$. An \emph{atom} is
-$p(t_1, \dots, t_n)$ for some predicate $p/n$ and terms $t_{1}, \dots, t_{n}$. A
-\emph{term} is either a constant or a variable. A \emph{literal} is either an
-atom or the negation of an atom (denoted by $\neg p(t_1, \dots, t_n)$). Let
-$\mathcal{D}$ be the set of all relevant (finite) domains. Initially,
-$\mathcal{D}$ contains all domains mentioned by the input formula. During
-compilation, new domains are added to $\mathcal{D}$ by some of the compilation
-rules. Each such new domain is interpreted as a subset of some other domain in
-$\mathcal{D}$.
+to this internal format. We use lowercase Latin letters for predicates (e.g.,
+$\texttt{p}$) and constants (e.g., $x$), uppercase Latin letters for variables
+(e.g., $X$), and uppercase Greek letters for domains (e.g., $\Delta$). Sometimes
+we write predicate $\texttt{p}$ as $\texttt{p}/n$, where $n \in \mathbb{N}^{+}$
+is the \emph{arity} of $\texttt{p}$. An \emph{atom} is
+$\texttt{p}(t_1, \dots, t_n)$ for some predicate $\texttt{p}/n$ and terms
+$t_{1}, \dots, t_{n}$. A \emph{term} is either a constant or a variable. A
+\emph{literal} is either an atom or the negation of an atom (denoted by
+$\neg \texttt{p}(t_1, \dots, t_n)$). Let $\mathcal{D}$ be the set of all
+relevant (finite) domains. Initially, $\mathcal{D}$ contains all domains
+mentioned by the input formula. During compilation, new domains are added to
+$\mathcal{D}$ by some of the compilation rules. Each such new domain is
+interpreted as a subset of some other domain in $\mathcal{D}$.
 
@@
   $\phi$ has a map $\pi_{\phi}\colon \Preds(\phi) \to {\Doms(\phi)}^{\ast}$ such
-  that, for each predicate $p/n \in \Preds(\phi)$, we have that
-  $\pi_{\phi}(p) \in {\Doms(\phi)}^{n}$.\footnote{Similarly to variables and
-    predicates, constants are also mapped to domains, although we keep this
-    mapping implicit.}
+  that, for each predicate $\texttt{p}/n \in \Preds(\phi)$, we have that
+  $\pi_{\phi}(\texttt{p}) \in {\Doms(\phi)}^{n}$.\footnote{Similarly to
+    variables and predicates, constants are also mapped to domains, although we
+    keep this mapping implicit.}
 \end{definition}
@@
           \begin{multlined}[t]
-            (\{\, \neg p(X, Y), \neg p(X, Z) \,\}, \{\, (Y, Z) \,\}, \\
+            (\{\, \neg \texttt{p}(X, Y), \neg \texttt{p}(X, Z) \,\}, \{\, (Y, Z) \,\}, \\
             \{\, X \mapsto \Gamma, Y \mapsto \Delta, Z \mapsto \Delta \,\}),
@@
           \begin{multlined}[t]
-            (\{\, \neg p(X, Y), \neg p(Z, Y) \,\}, \{\, (X, Z) \,\}, \\
+            (\{\, \neg \texttt{p}(X, Y), \neg \texttt{p}(Z, Y) \,\}, \{\, (X, Z) \,\}, \\
             \{\, X \mapsto \Gamma, Y \mapsto \Delta, Z \mapsto \Gamma \,\})
@@
   \end{align*}
-  for some predicate $p/2$, variables $X$, $Y$, $Z$, and domains $\Gamma$ and
-  $\Delta$. Based on $\delta_{c_{1}}$ and $\delta_{c_{2}}$, we can infer that
-  $\pi_{\phi} = \{\, p \mapsto (\Gamma, \Delta) \,\}$. All variables that occur
-  as the first argument to $p$ are in $\Gamma$, and, likewise, all variables
-  that occur as the second argument to $p$ are in $\Delta$. Therefore, $\phi$
-  `type checks' as a valid formula.
+  for some predicate $\texttt{p}/2$, variables $X$, $Y$, $Z$, and domains
+  $\Gamma$ and $\Delta$. Based on $\delta_{c_{1}}$ and $\delta_{c_{2}}$, we can
+  infer that $\pi_{\phi} = \{\, \texttt{p} \mapsto (\Gamma, \Delta) \,\}$. All
+  variables that occur as the first argument to $\texttt{p}$ are in $\Gamma$,
+  and, likewise, all variables that occur as the second argument to $\texttt{p}$
+  are in $\Delta$. Therefore, $\phi$ `type checks' as a valid formula.
 \end{example}
@@
     (\forall X \in \Gamma\text{. }\forall Y, Z \in \Delta\text{. }\\
-    Y \ne Z \Rightarrow \neg p(X, Y) \lor \neg p(X, Z)) \land
+    Y \ne Z \Rightarrow \neg \texttt{p}(X, Y) \lor \neg \texttt{p}(X, Z)) \land
     \end{multlined}\\
@@
     (\forall X, Z \in \Gamma\text{. }\forall Y \in \Delta\text{. }\\
-    X \ne Z \Rightarrow \neg p(X, Y) \lor \neg p(Z, Y)).
+    X \ne Z \Rightarrow \neg \texttt{p}(X, Y) \lor \neg \texttt{p}(Z, Y)).
     \end{multlined}
@@
   Let $\Delta$ be a domain of size $n \in \mathbb{N}_{0}$. The model count of
-  $\forall X \in \Delta\text{. } p(X) \lor q(X)$ is then $3^{n}$. Intuitively,
-  since both predicates are of arity one, they can be interpreted as subsets of
-  $\Delta$. Thus, the formula says that each element of $\Delta$ has to be
-  included in $p$ or in $q$ or in both, i.e., there are three possibilities.
+  $\forall X \in \Delta\text{. } \texttt{p}(X) \lor \texttt{q}(X)$ is then
+  $3^{n}$. Intuitively, since both predicates are of arity one, they can be
+  interpreted as subsets of $\Delta$. Thus, the formula says that each element
+  of $\Delta$ has to be included in $\texttt{p}$ or in $\texttt{q}$ or in both,
+  i.e., there are three possibilities.
 \end{example}
 
-\begin{example}
+\begin{example}\label{example:smokers}
   Consider a variant of the well-known `friends and smokers' example
@@
 \end{example}
+% TODO: maybe add an extra sentence to explain what the formula means
 
@@
   \begin{enumerate}
-    \item Let $p/n \in \Preds(\phi)$ be a predicate and let
-          $\pi_{\phi}(p) = {(d_{i})}_{i=1}^{n}$ for some domains
+    \item Let $\texttt{p}/n \in \Preds(\phi)$ be a predicate and let
+          $\pi_{\phi}(\texttt{p}) = {(d_{i})}_{i=1}^{n}$ for some domains
           $d_{i} \in \Doms(\phi)$. Then
           \begin{equation}\label{eq:subset}
-            \mathfrak{M}(p) \subseteq \prod_{i=1}^{n}[\sigma(d_{i})].\footnote{For simplicity, \cref{def:model} ignores constants.
+            \mathfrak{M}(\texttt{p}) \subseteq \prod_{i=1}^{n}[\sigma(d_{i})].\footnote{For simplicity, \cref{def:model} ignores constants.
 To include constants, one would replace $[\sigma(d_{i})]$ with a set that contains all constants associated with domain $d_{i}$, extended with enough new elements to make its cardinality $\sigma(d_{i})$.}
           \end{equation}
-    \item As a collection of relations, $\mathfrak{M}$ satisfies
-          $\phi$.
+    \item As a collection of relations, $\mathfrak{M}$ satisfies $\phi$.
   \end{enumerate}
@@
   There are $2^{4} = 16$ possible relations between $\Gamma$ and $\Delta$. Let
-  us count how many of them satisfy the conditions imposed on predicate $p$. The
-  empty relation does. All four relations of cardinality one do too. Finally,
-  there are two relations of cardinality two that satisfy the conditions as
-  well. Thus, the FOMC of $(\phi, \sigma)$ is 7. Incidentally, it counts partial
-  injections. We will continue to use the problem of counting partial injections
-  (and the formula from \cref{example:first} specifically) as the main running
-  example throughout the paper.
+  us count how many of them satisfy the conditions imposed on predicate
+  $\texttt{p}$. The empty relation does. All four relations of cardinality one
+  do too. Finally, there are two relations of cardinality two that satisfy the
+  conditions as well. Thus, the FOMC of $(\phi, \sigma)$ is 7. Incidentally, it
+  counts partial injections. We will continue to use the problem of counting
+  partial injections (and the formula from \cref{example:first} specifically) as
+  the main running example throughout the paper.
 \end{example}
@@
   \begin{multline*}
-    (\{\, \neg p(X, Y), \neg p(X, Z) \,\}, \{\, (Y, Z) \,\}, \\
+    (\{\, \neg \texttt{p}(X, Y), \neg \texttt{p}(X, Z) \,\}, \{\, (Y, Z) \,\}, \\
     \{\, X \mapsto \Gamma, Y \mapsto \Delta, Z \mapsto \Delta \,\}).
@@
     c_{1} &= \begin{multlined}[t]
-      (\{\, \neg p(x, Y), \neg p(x, Z) \,\}, \{\, (Y, Z) \,\}, \\
+      (\{\, \neg \texttt{p}(x, Y), \neg \texttt{p}(x, Z) \,\}, \{\, (Y, Z) \,\}, \\
       \{\, Y \mapsto \Delta, Z \mapsto \Delta \,\}),
@@
     c_{2} &= \begin{multlined}[t]
-      (\{\, \neg p(X, Y), \neg p(X, Z) \,\}, \{\, (X, x), (Y, Z) \,\}, \\
+      (\{\, \neg \texttt{p}(X, Y), \neg \texttt{p}(X, Z) \,\}, \{\, (X, x), (Y, Z) \,\}, \\
       \{\, X \mapsto \Gamma', Y \mapsto \Delta, Z \mapsto \Delta \,\}),
@@
   \begin{multline*}
-    (\{\, \neg p(X, Y), \neg p(X, Z) \,\}, \{\, (Y, Z), (X, x) \,\}, \\
+    (\{\, \neg \texttt{p}(X, Y), \neg \texttt{p}(X, Z) \,\}, \{\, (Y, Z), (X, x) \,\}, \\
     \{\, X \mapsto \Gamma, Y \mapsto \Delta, Z \mapsto \Delta \,\}),
@@
   \[
-    (\{\, \neg p(x, Y), \neg p(x, Z) \,\}, \{\, (Y, Z) \,\}, \{\, Y \mapsto \Delta, Z \mapsto \Delta \,\})
+    (\{\, \neg \texttt{p}(x, Y), \neg \texttt{p}(x, Z) \,\}, \{\, (Y, Z) \,\}, \{\, Y \mapsto \Delta, Z \mapsto \Delta \,\})
   \]
@@
   \begin{multline*}
-    (\{\, \neg p(X, Y), \neg p(Z, Y) \,\}, \{\, (X, Z), (X, x), (Z, x) \,\}, \\
+    (\{\, \neg \texttt{p}(X, Y), \neg \texttt{p}(Z, Y) \,\}, \{\, (X, Z), (X, x), (Z, x) \,\}, \\
     \{\, X \mapsto \Gamma, Y \mapsto \Delta, Z \mapsto \Gamma \,\}),
@@
   \[
-    (\{\, \neg p(x, Y), \neg p(Z, Y) \,\}, \{\, (Z, x) \,\}, \{\, Y \mapsto \Delta, Z \mapsto \Gamma \,\}),
+    (\{\, \neg \texttt{p}(x, Y), \neg \texttt{p}(Z, Y) \,\}, \{\, (Z, x) \,\}, \{\, Y \mapsto \Delta, Z \mapsto \Gamma \,\}),
   \]
@@
   \[
-    (\{\, \neg p(X, Y), \neg p(x, Y) \,\}, \{\, (X, x) \,\}, \{\, X \mapsto \Gamma, Y \mapsto \Delta \,\}).
+    (\{\, \neg \texttt{p}(X, Y), \neg \texttt{p}(x, Y) \,\}, \{\, (X, x) \,\}, \{\, X \mapsto \Gamma, Y \mapsto \Delta \,\}).
   \]
@@
           \begin{multlined}[t]
-            (\{\, \neg p(X, Y), \neg p(X, Z) \,\}, \{\, (X, x), (Y, Z) \,\}, \\
+            (\{\, \neg \texttt{p}(X, Y), \neg \texttt{p}(X, Z) \,\}, \{\, (X, x), (Y, Z) \,\}, \\
             \{\, X \mapsto \Gamma, Y \mapsto \Delta, Z \mapsto \Delta \,\}),
@@
           \begin{multlined}[t]
-            (\{\, \neg p(X, Y), \neg p(Z, Y) \,\}, \\
+            (\{\, \neg \texttt{p}(X, Y), \neg \texttt{p}(Z, Y) \,\}, \\
             \{\, (X, x), (Z, X), (Z, x) \,\}, \\
@@
            \begin{multlined}[t]
-             (\{\, \neg p(X, Y), \neg p(X, Z) \,\}, \{\, (Y, Z) \,\}, \\
+             (\{\, \neg \texttt{p}(X, Y), \neg \texttt{p}(X, Z) \,\}, \{\, (Y, Z) \,\}, \\
              \{\, X \mapsto \Gamma', Y \mapsto \Delta, Z \mapsto \Delta \,\}),
@@
            \begin{multlined}[t]
-             (\{\, \neg p(X, Y), \neg p(Z, Y) \,\}, \{\, (Z, X) \,\}, \\
+             (\{\, \neg \texttt{p}(X, Y), \neg \texttt{p}(Z, Y) \,\}, \{\, (Z, X) \,\}, \\
              \{\, X \mapsto \Gamma', Y \mapsto \Delta, Z \mapsto \Gamma' \,\}).
@@
   commutes by \cref{def:formula} and the definition of $\rho$. In other words,
-  for any predicate $p/n \in \Preds(\psi) = \Preds(\phi)$, function $\rho$
-  translates the domains associated with $p$ in $\psi$ to the domains associated
-  with $p$ in $\phi$. Let $\pi_{\phi}(p) = {(d_{i})}_{i=1}^{n}$ and
-  $\pi_{\psi}(p) = {(e_{i})}_{i=1}^{n}$ for some domains $d_{i} \in \Doms(\phi)$
-  and $e_{i} \in \Doms(\psi)$. Since $\rho(e_{i}) = d_{i}$ for all
-  $i = 1, \dots, n$ by the commutativity in \cref{diagram:ref}, we get that
+  for any predicate $\texttt{p}/n \in \Preds(\psi) = \Preds(\phi)$, function
+  $\rho$ translates the domains associated with $\texttt{p}$ in $\psi$ to the
+  domains associated with $\texttt{p}$ in $\phi$. Let
+  $\pi_{\phi}(\texttt{p}) = {(d_{i})}_{i=1}^{n}$ and
+  $\pi_{\psi}(\texttt{p}) = {(e_{i})}_{i=1}^{n}$ for some domains
+  $d_{i} \in \Doms(\phi)$ and $e_{i} \in \Doms(\psi)$. Since
+  $\rho(e_{i}) = d_{i}$ for all $i = 1, \dots, n$ by the commutativity in
+  \cref{diagram:ref}, we get that
   \begin{equation}\label{eq:equality}
@@
   as required. Certainly, any subset of the left-hand side of \cref{eq:equality}
-  (e.g., $\mathfrak{M}(p)$, where $\mathfrak{M}$ is a model of $(\phi, \sigma)$)
-  is a subset of the right-hand side and vice versa. Since $\phi$ and $\psi$
-  semantically only differ in what domains they refer to, every model of $\phi$
-  satisfies $\psi$ and vice versa, completing the proof.
+  (e.g., $\mathfrak{M}(\texttt{p})$, where $\mathfrak{M}$ is a model of
+  $(\phi, \sigma)$) is a subset of the right-hand side and vice versa. Since
+  $\phi$ and $\psi$ semantically only differ in what domains they refer to,
+  every model of $\phi$ satisfies $\psi$ and vice versa, completing the proof.
 \end{proof}
@@
 \section{Experimental Results}\label{sec:results}
-
-TODO: Incidentally, the linear order axiom is also liftable. Cite the same
-paper~\cite{DBLP:journals/corr/abs-2211-01164} in the introduction as well.
 
@@
 \end{table*}
-% TODO: It is a standard to discuss a few lifted theories like the smokers and
-% friends example. Can you also include some empirical results on such theories
-% as well to appeal to the sanity of the reader that it actually works for
-% problems in frameworks such as Markov log networks
 
@@
 
-Let $p$ be a predicate that models relations between sets $\Gamma$ and $\Delta$.
-To restrict all such relations to just $\Gamma \to \Delta$ functions, in FOL one
-might write
+Let $\texttt{p}$ be a predicate that models relations between sets $\Gamma$ and
+$\Delta$. To restrict all such relations to just $\Gamma \to \Delta$ functions,
+in FOL one might write
 \[
-  \forall X \in \Gamma\text{. }\forall Y,Z \in \Delta\text{. }p(X, Y) \land p(X, Z) \Rightarrow Y = Z
+  \forall X \in \Gamma\text{. }\forall Y,Z \in \Delta\text{. }\texttt{p}(X, Y) \land \texttt{p}(X, Z) \Rightarrow Y = Z
 \]
@@
 \begin{equation}\label{eq:def2}
-  \forall X \in \Gamma\text{. }\exists Y \in \Delta\text{. }p(X, Y).
+  \forall X \in \Gamma\text{. }\exists Y \in \Delta\text{. }\texttt{p}(X, Y).
 \end{equation}
@@
 \[
-  \forall X,Z \in \Gamma\text{. }\forall Y \in \Delta\text{. }p(X, Y) \land p(Z, Y) \Rightarrow X = Z
+  \forall X,Z \in \Gamma\text{. }\forall Y \in \Delta\text{. }\texttt{p}(X, Y) \land \texttt{p}(Z, Y) \Rightarrow X = Z
 \]
-to restrict $p$ to injections or
+to restrict $\texttt{p}$ to injections or
 \[
-  \forall Y \in \Delta\text{. }\exists X \in \Gamma\text{. }p(X, Y)
+  \forall Y \in \Delta\text{. }\exists X \in \Gamma\text{. }\texttt{p}(X, Y)
 \]
@@
 \textsc{Crane} is run in hybrid search mode until either five solutions are
-found or the search tree reaches height six.\footnote{The search tree has a high
-  branching factor, so exploring all nodes at depth five takes at most a few
-  seconds, whereas doing the same for depth six can be computationally
-  infeasible in some cases.} \textsc{ForcLift} is always run until it
-terminates. If successful, \textsc{ForcLift} generates a circuit, and
+found or the search tree reaches height six. \textsc{ForcLift} is always run
+until it terminates. If successful, \textsc{ForcLift} generates a circuit, and
 \textsc{Crane} generates one or more (complete) FCGs. In both cases, we manually
@@
 complexities.
+
+% \footnote{The search tree has a high
+%   branching factor, so exploring all nodes at depth five takes at most a few
+%   seconds, whereas doing the same for depth six can be computationally
+%   infeasible in some cases.}
 
@@
 
-These results are summarised in \cref{tbl:results}, where we compare the
-solutions found by both algorithms to the best known ways of computing the same
-quantities. The best-known asymptotic complexity for computing total surjections
-is by Earnest~\shortcite{30049}. All other best-known complexity results are
-inferred from the formulas and programs on the on-line encyclopedia of integer
-sequences~\cite{oeis}. On instances that could already be solved by
+The experimental results are summarised in \cref{tbl:results}, where we compare
+the solutions found by both algorithms to the best known ways of computing the
+same quantities. The best-known asymptotic complexity for computing total
+surjections is by Earnest~\shortcite{30049}. All other best-known complexity
+results are inferred from the formulas and programs on the on-line encyclopedia
+of integer sequences~\cite{oeis}. On instances that could already be solved by
 \textsc{ForcLift}, the two algorithms perform equally well. However,
@@
 the exact solutions produced by \textsc{Crane} that correspond to the complexity
-results in \cref{tbl:results}.
+results in \cref{tbl:results}. We also note that standard (W)FOMC benchmarks
+such as \cref{example:smokers} that are already supported by \textsc{ForcLift}
+remain feasible for \textsc{Crane} as well. Moreover, our algorithm can also
+handle the linear order axiom, for which a bespoke algorithm was recently
+proposed by T{\'{o}}th and
+Ku\v{z}elka~\shortcite{DBLP:journals/corr/abs-2211-01164}.
 
@@
       (\forall X \in \Gamma\text{. }\forall Y, Z \in \Delta\text{. }\\
-      Y \ne Z \Rightarrow \neg p(X, Y) \lor \neg p(X, Z)) \land
+      Y \ne Z \Rightarrow \neg \texttt{\textup{p}}(X, Y) \lor \neg \texttt{\textup{p}}(X, Z)) \land
     \end{multlined}\\
@@
       (\forall X, Z \in \Gamma\text{. }\forall Y \in \Delta\text{. }\\
-      X \ne Z \Rightarrow \neg p(X, Y) \lor \neg p(Z, Y))
+      X \ne Z \Rightarrow \neg \texttt{\textup{p}}(X, Y) \lor \neg \texttt{\textup{p}}(Z, Y))
     \end{multlined}
   \end{align*}
-  for some predicate $p$ and domains $\Gamma$ and $\Delta$. Then \IFO{} is
-  liftable by \textsc{Crane}.
+  for some predicate $\texttt{\textup{p}}/2$ and domains $\Gamma$ and $\Delta$.
+  Then \IFO{} is liftable by \textsc{Crane}.
 \end{conjecture}

### 2023-02-14 doc/paper/paper.tex
Fix references

@@
 %  make sure the result table (as well as other floating objects) are on the right pages
-
-% TODO: use \textt for predicates (e.g., p, q), introduce the notation, use DeclareMathOperator
-% TODO: cite the linear order axiom paper \cite{DBLP:journals/corr/abs-2211-01164} in the introduction
-% TODO: introduction: move the huge footnote to the main text
 
@@
 \section{Introduction}\label{sec:introduction}
-
-% TODO: cite some works about synthesis
 
@@
 \SRU{}~\cite{DBLP:conf/nips/KazemiKBP16},
-\Uone{}~\cite{DBLP:conf/lics/KuusistoL18}, \FOtwo{} with tree
-axioms~\cite{DBLP:conf/kr/BremenK21}, and \Ctwo{} (i.e., the two-variable
+\Uone{}~\cite{DBLP:conf/lics/KuusistoL18}, \Ctwo{} (i.e., the two-variable
 fragment with counting
-quantifiers)~\cite{DBLP:journals/jair/Kuzelka21,DBLP:conf/aaai/MalhotraS22}. On
-the empirical front, there are several implementations of exact WFOMC
-algorithms: \textsc{Alchemy}~\cite{DBLP:journals/cacm/GogateD16},
+quantifiers)~\cite{DBLP:journals/jair/Kuzelka21,DBLP:conf/aaai/MalhotraS22}, and
+\Ctwo{} extended with tree axioms~\cite{DBLP:conf/kr/BremenK21} and linear order
+axiom~\cite{DBLP:journals/corr/abs-2211-01164}. On the empirical front, there
+are several implementations of exact WFOMC algorithms:
+\textsc{Alchemy}~\cite{DBLP:journals/cacm/GogateD16},
 \textsc{FastWFOMC}~\cite{DBLP:conf/uai/BremenK21},
@@
   third~\cite{DBLP:conf/kr/BremenK21} contains experimental results performed
-  with an algorithm, which is not publicly available.} We claim that this
-shortcoming is due to the inability of these algorithms to construct recursive
-solutions. The topic of recursion in the context of WFOMC has been studied
-before but in limited ways. Barv{\'{\i}}nek et
-al.~\shortcite{DBLP:conf/ilp/BarvinekB0ZK21} use WFOMC to generate numerical
-data that is then used to conjecture recurrence relations that explain that
-data. Van den Broeck~\shortcite{DBLP:conf/nips/Broeck11} introduced the idea of
-\emph{domain recursion}. Intuitively, domain recursion partitions a domain of
-size $n$ into a single explicitly named constant and the remaining domain of
-size $n-1$. However, many stringent conditions are enforced to ensure that the
-search for a tractable solution always terminates.
+  with an algorithm, which is not publicly available.} We claim that the
+capabilities of (W)FOMC algorithms can be significantly extended by empowering
+them with the ability to construct recursive solutions. The topic of recursion
+in the context of WFOMC has been studied before but in limited ways.
+Barv{\'{\i}}nek et al.~\shortcite{DBLP:conf/ilp/BarvinekB0ZK21} use WFOMC to
+generate numerical data that is then used to conjecture recurrence relations
+that explain that data. Van den Broeck~\shortcite{DBLP:conf/nips/Broeck11}
+introduced the idea of \emph{domain recursion}. Intuitively, domain recursion
+partitions a domain of size $n$ into a single explicitly named constant and the
+remaining domain of size $n-1$. However, many stringent conditions are enforced
+to ensure that the search for a tractable solution always terminates.
 
@@
 the product of compilation is not directly evaluated but rather interpreted as a
-collection of functions on domain sizes.
+collection of functions on domain sizes. Hence, our approach is reminiscent of
+previous work on lifted inference via compilation to C++
+programs~\cite{DBLP:conf/kr/KazemiP16} and the broader area of functional
+synthesis~\cite{DBLP:conf/cav/GoliaRM20,DBLP:conf/pldi/KuncakMPS10,sanathanan1963transfer}.
+
+% similarly to the other domains, there are many functions that fit the
+% specification, i.e., can correctly count the number of models as a function of
+% domain size(s). Whereas in [...] one typically wants to select the smallest
+% definition of a function, we are primarily concerned with its worst-case
+% complexity as measured by the number of arithmetic operations needed for an
+% arbitrary function call
+% \begin{itemize}
+%   \item Boolean functions~\cite{DBLP:conf/cav/GoliaRM20}
+%   \item dynamical systems~\cite{sanathanan1963transfer}
+%   \item program fragments~\cite{DBLP:conf/pldi/KuncakMPS10}
+% \end{itemize}
 
@@
 \end{example}
-% TODO: maybe add an extra sentence to explain what the formula means
 

### 2023-02-14 doc/paper/paper.tex
Move things around

@@
 % TODO (at the very end)
-% put the appendix in a separate file
 % grammarly the whole thing
@@
 % make sure there are no overflow errors
-% clean up unnecessary things from the header (e.g., packages and definitions)
 %  make sure the result table (as well as other floating objects) are on the right pages
@@
 \section{Introduction}\label{sec:introduction}
-
-% TODO: In the introduction it is written: "Crane uses a hybrid search algorithm
-% that applies some rules greedily and some using breadth-first search". Which
-% rules are applied greedily and which are not? What is the reason for parting
-% from the usual greedy method?
 
@@
 rules via greedy search, \textsc{Crane} also supports a hybrid search algorithm
-that applies some rules greedily and some using breadth-first search. Second,
-the product of compilation is not directly evaluated but rather interpreted as a
-collection of functions on domain sizes. Hence, our approach is reminiscent of
-previous work on lifted inference via compilation to C++
-programs~\cite{DBLP:conf/kr/KazemiP16} and the broader area of functional
+that applies some rules greedily and some using breadth-first
+search.\footnote{In the current implementation, the rules that are applied in a
+  non-greedy fashion are: atom counting, inclusion-exclusion, independent
+  partial groundings, Shannon decomposition, shattering, and two of our new
+  rules introduced in \cref{sec:dr,sec:ref}---see previous
+  work~\cite{DBLP:conf/ijcai/BroeckTMDR11} for more information about the
+  rules.} This alternative was introduced since there is no reason to expect
+greedy search to be optimal. Second, the product of compilation is not directly
+evaluated but rather interpreted as a collection of functions on domain sizes.
+Hence, our approach is reminiscent of previous work on lifted inference via
+compilation to C++ programs~\cite{DBLP:conf/kr/KazemiP16} and the broader area
+of functional
 synthesis~\cite{DBLP:conf/cav/GoliaRM20,DBLP:conf/pldi/KuncakMPS10,sanathanan1963transfer}.
@@
 
-\begin{figure}
+\begin{figure}[t]
   \centering
@@
 \begin{theorem}[Correctness of $\GDR$\footnote{\Cref{thm:correctness1} is equivalent to
-    Proposition~3 by~\cite{DBLP:conf/nips/Broeck11}.}]\label{thm:correctness1}
+    Proposition~3 by Van den Broeck~\shortcite{DBLP:conf/nips/Broeck11}.}]\label{thm:correctness1}
   Let $\phi$ be the formula used as input to \cref{alg:domainrecursion},
@@
 
+We compare \textsc{Crane} and
+\textsc{ForcLift}\footnote{\url{https://dtaid.cs.kuleuven.be/wfomc}}~\cite{DBLP:conf/ijcai/BroeckTMDR11}
+on their ability to count various kinds of functions. This class of instances is
+chosen because of its simplicity and ubiquity and the inability of
+state-of-the-art WFOMC algorithms to solve many such instances. Note that other
+WFOMC algorithms mentioned in \cref{sec:introduction} are unable to solve any of
+the instances that \textsc{ForcLift} fails on. We begin by describing how such
+function-counting problems can be expressed in FOL\@. \textsc{ForcLift} then
+translates these sentences in FOL to formulas as defined in \cref{def:formula}.
+
+Let $\texttt{p}$ be a predicate that models relations between sets $\Gamma$ and
+$\Delta$. To restrict all such relations to just $\Gamma \to \Delta$ functions,
+in FOL one might write
+\[
+  \forall X \in \Gamma\text{. }\forall Y,Z \in \Delta\text{. }\texttt{p}(X, Y) \land \texttt{p}(X, Z) \Rightarrow Y = Z
+\]
+and
+\begin{equation}\label{eq:def2}
+  \forall X \in \Gamma\text{. }\exists Y \in \Delta\text{. }\texttt{p}(X, Y).
+\end{equation}
+The former sentence says that one element of $\Gamma$ can map to at \emph{most}
+one element of $\Delta$, and the latter sentence says that each element of
+$\Gamma$ must map to at \emph{least} one element of $\Delta$. One can then add
+\[
+  \forall X,Z \in \Gamma\text{. }\forall Y \in \Delta\text{. }\texttt{p}(X, Y) \land \texttt{p}(Z, Y) \Rightarrow X = Z
+\]
+to restrict $\texttt{p}$ to injections or
+\[
+  \forall Y \in \Delta\text{. }\exists X \in \Gamma\text{. }\texttt{p}(X, Y)
+\]
+to ensure surjectivity or remove \cref{eq:def2} to consider partial functions.
+Lastly, one can replace all occurrences of $\Delta$ with $\Gamma$ to model
+endofunctions (i.e., functions with the same domain and codomain) instead.
+
+% the process: both for running algorithms and for determining complexities
+In our experiments, we consider all sixteen combinations of these properties,
+i.e., injectivity, surjectivity, partiality, and endo-. We run each algorithm
+once on each of the sixteen instances.\footnote{While domain sizes have to be
+  specified as part of the input, they are immaterial to the search procedure.}
+\textsc{Crane} is run in hybrid search mode until either five solutions are
+found or the search tree reaches height six. \textsc{ForcLift} is always run
+until it terminates. If successful, \textsc{ForcLift} generates a circuit, and
+\textsc{Crane} generates one or more (complete) FCGs. In both cases, we manually
+convert the resulting graphs into definitions of functions as described in
+\cref{sec:interpret}. We then assess the complexity of each solution by hand and
+pick the best in case \textsc{Crane} returns several solutions of varying
+complexities.
+
+% \footnote{The search tree has a high
+%   branching factor, so exploring all nodes at depth five takes at most a few
+%   seconds, whereas doing the same for depth six can be computationally
+%   infeasible in some cases.}
+
+% how the complexity of a solution is determined
+Previous work often compares WFOMC algorithms by running them on a few instances
+with increasing domain sizes and measuring
+runtime~\cite{DBLP:conf/nips/Broeck11,DBLP:conf/ijcai/BroeckTMDR11,DBLP:conf/aaai/BroeckD12}.
+However, we can do much better and identify the exact worst-case asymptotic
+complexity of a solution produced by either \textsc{Crane} or \textsc{ForcLift}.
+The asymptotic complexity of a solution can be determined by considering the
+total number of arithmetic operations needed to follow the definitions of
+constituent functions without recomputing the same quantity multiple times. In
+particular, we assume that each function call and binomial coefficient is
+computed at most once. We also assume that computing $\binom{n}{k}$ takes
+$\Theta(nk)$ time. For example, the complexity of \cref{eq:solution} is
+$\Theta(mn)$ since $f(m, n)$ can be computed by a dynamic programming algorithm
+that computes $f(i, j)$ for all $i = 0, \dots, m$ and $j = 0, \dots, n$, taking
+a constant amount of time on the computation of each $f(i, j)$.
+
 \begin{table*}[t]
@@
 
-We compare \textsc{Crane} and
-\textsc{ForcLift}\footnote{\url{https://dtaid.cs.kuleuven.be/wfomc}}~\cite{DBLP:conf/ijcai/BroeckTMDR11}
-on their ability to count various kinds of functions. This class of instances is
-chosen because of its simplicity and ubiquity and the inability of
-state-of-the-art WFOMC algorithms to solve many such instances. Note that other
-WFOMC algorithms mentioned in \cref{sec:introduction} are unable to solve any of
-the instances that \textsc{ForcLift} fails on. We begin by describing how such
-function-counting problems can be expressed in FOL\@. \textsc{ForcLift} then
-translates these sentences in FOL to formulas as defined in \cref{def:formula}.
-
-Let $\texttt{p}$ be a predicate that models relations between sets $\Gamma$ and
-$\Delta$. To restrict all such relations to just $\Gamma \to \Delta$ functions,
-in FOL one might write
-\[
-  \forall X \in \Gamma\text{. }\forall Y,Z \in \Delta\text{. }\texttt{p}(X, Y) \land \texttt{p}(X, Z) \Rightarrow Y = Z
-\]
-and
-\begin{equation}\label{eq:def2}
-  \forall X \in \Gamma\text{. }\exists Y \in \Delta\text{. }\texttt{p}(X, Y).
-\end{equation}
-The former sentence says that one element of $\Gamma$ can map to at \emph{most}
-one element of $\Delta$, and the latter sentence says that each element of
-$\Gamma$ must map to at \emph{least} one element of $\Delta$. One can then add
-\[
-  \forall X,Z \in \Gamma\text{. }\forall Y \in \Delta\text{. }\texttt{p}(X, Y) \land \texttt{p}(Z, Y) \Rightarrow X = Z
-\]
-to restrict $\texttt{p}$ to injections or
-\[
-  \forall Y \in \Delta\text{. }\exists X \in \Gamma\text{. }\texttt{p}(X, Y)
-\]
-to ensure surjectivity or remove \cref{eq:def2} to consider partial functions.
-Lastly, one can replace all occurrences of $\Delta$ with $\Gamma$ to model
-endofunctions (i.e., functions with the same domain and codomain) instead.
-
-% the process: both for running algorithms and for determining complexities
-In our experiments, we consider all sixteen combinations of these properties,
-i.e., injectivity, surjectivity, partiality, and endo-. We run each algorithm
-once on each of the sixteen instances.\footnote{While domain sizes have to be
-  specified as part of the input, they are immaterial to the search procedure.}
-\textsc{Crane} is run in hybrid search mode until either five solutions are
-found or the search tree reaches height six. \textsc{ForcLift} is always run
-until it terminates. If successful, \textsc{ForcLift} generates a circuit, and
-\textsc{Crane} generates one or more (complete) FCGs. In both cases, we manually
-convert the resulting graphs into definitions of functions as described in
-\cref{sec:interpret}. We then assess the complexity of each solution by hand and
-pick the best in case \textsc{Crane} returns several solutions of varying
-complexities.
-
-% \footnote{The search tree has a high
-%   branching factor, so exploring all nodes at depth five takes at most a few
-%   seconds, whereas doing the same for depth six can be computationally
-%   infeasible in some cases.}
-
-% how the complexity of a solution is determined
-Previous work often compares WFOMC algorithms by running them on a few instances
-with increasing domain sizes and measuring
-runtime~\cite{DBLP:conf/nips/Broeck11,DBLP:conf/ijcai/BroeckTMDR11,DBLP:conf/aaai/BroeckD12}.
-However, we can do much better and identify the exact worst-case asymptotic
-complexity of a solution produced by either \textsc{Crane} or \textsc{ForcLift}.
-The asymptotic complexity of a solution can be determined by considering the
-total number of arithmetic operations needed to follow the definitions of
-constituent functions without recomputing the same quantity multiple times. In
-particular, we assume that each function call and binomial coefficient is
-computed at most once. We also assume that computing $\binom{n}{k}$ takes
-$\Theta(nk)$ time. For example, the complexity of \cref{eq:solution} is
-$\Theta(mn)$ since $f(m, n)$ can be computed by a dynamic programming algorithm
-that computes $f(i, j)$ for all $i = 0, \dots, m$ and $j = 0, \dots, n$, taking
-a constant amount of time on the computation of each $f(i, j)$.
-
 The experimental results are summarised in \cref{tbl:results}, where we compare
@@
 \textsc{Crane} can also solve all but one of the instances that
-\textsc{ForcLift} fails on in at most cubic time. See \cref{app:solutions} for
+\textsc{ForcLift} fails on in at most cubic time. See supplementary material for
 the exact solutions produced by \textsc{Crane} that correspond to the complexity
@@
 
-\appendix
-\section{Solutions Found by \textsc{Crane}}\label{app:solutions}
-
-In this appendix, we list the exact function definitions produced by
-\textsc{Crane} for all of the problem instances in \cref{sec:results} both
-before and after algebraic simplification (excluding multiplications by one).
-The correctness of all of them has been checked by identifying suitable base
-cases and verifying the numerical answers across a range of domain sizes.
-
-\begin{enumerate}
-  \item $\Theta(m)$ solution for counting $\Gamma \to \Gamma$ functions:
-  \[
-    f(m) = {\left(-1 + \sum_{l=0}^{m} \binom{m}{l} [l < 2]\right)}^{m} = m^{m}.
-  \]
-  \item $\Theta(m^3 + n^3)$ solution for counting $\Gamma \to \Delta$
-  surjections:
-  \begin{align*}
-    f(m, n) ={}& \sum_{l=0}^{m} \binom{m}{l}{(-1)}^{m-l} \sum_{k=0}^{n} \binom{n}{k} {(-1)}^{n-k}\\
-               &{\left( \sum_{j=0}^{k} \binom{k}{j} [j < 2] \right)}^{l} \\
-    ={}& \sum_{l=0}^{m} \binom{m}{l}{(-1)}^{m-l} \sum_{k=0}^{n} \binom{n}{k} {(-1)}^{n-k} {(k+1)}^{l}.
-  \end{align*}
-  \item $\Theta(m^{3})$ solution for counting $\Gamma \to \Gamma$ surjections:
-  \begin{align*}
-    f(m) ={}& \sum_{l=0}^{m} \binom{m}{l}{(-1)}^{m-l} \sum_{k=0}^{m} \binom{m}{k} {(-1)}^{m-k}\\
-            &{\left( \sum_{j=0}^{k} \binom{k}{j} [j < 2] \right)}^{l} \\
-    ={}& \sum_{l=0}^{m} \binom{m}{l}{(-1)}^{m-l} \sum_{k=0}^{m} \binom{m}{k} {(-1)}^{m-k} {(k+1)}^{l}.
-  \end{align*}
-  \item $\Theta(mn)$ solution for counting $\Gamma \to \Delta$ injections and
-  partial injections (with different base cases):
-  \begin{align*}
-    f(m, n) ={}& \sum_{l=0}^m \binom{m}{l} [l<2] f(m-l, n-1)\\
-    ={}& f(m, n-1) + mf(m-1, n-1).
-  \end{align*}
-  \item $\Theta(m^{3})$ solution for counting $\Gamma \to \Gamma$ injections:
-  \begin{align*}
-    f(m) ={}& \sum_{l=0}^{m} \binom{m}{l} {(-1)}^{m-l} g(m, l); \\
-    g(m, l) ={}& \sum_{k=0}^{l} \binom{l}{k} [k < 2] g(m - 1, l - k)\\
-    ={}& g(m - 1, l) + lg(m - 1, l - 1).
-  \end{align*}
-  % \item $\Theta(m^{2})$ solution for counting $\Gamma \to \Gamma$ partial
-  %       injections:
-  % \begin{align*}
-  %   f(m) ={}& f(m - 1) + \sum_{l = 0}^{m} \binom{m}{l} \sum_{k = 0}^{m} \binom{m}{k}\\
-  %           &[1 \le l < 3] [k < 2] 2^{m - l} g(m - l, m - k - 1)\\
-  %   ={}& f(m - 1) + m2^{m-1}g(m-1, m-1)\\
-  %   +{}& m^{2}2^{m-1}g(m-1, m-2)\\
-  %   +{}& \binom{m}{2}2^{m-2}g(m-2, m-1) \\
-  %   +{}& \binom{m}{2}m2^{m-2}g(m-2, m-2)\\
-  %   g(i, j) ={}& \sum_{h = 0}^{j} \binom{j}{h} [h < 2] g(i - 1, j - h)\\
-  %   ={}& g(i-1, j) + jg(i-1, j-1).
-  %   \end{align*}
-  \item $\Theta(m)$ solution for counting $\Gamma \to \Delta$ bijections:
-  \[
-    f(m, n) = mf(m-1, n-1).
-  \]
-\end{enumerate}
-
 \bibliographystyle{kr}

### 2023-02-14 doc/paper/supplementary_material.tex
Move things around

--- 2023-02-14 doc/paper/paper.tex
@@
 
-% TODO: use \textt for predicates (e.g., p, q), introduce the notation, use DeclareMathOperator
-% TODO: cite the linear order axiom paper \cite{DBLP:journals/corr/abs-2211-01164} in the introduction
-% TODO: introduction: move the huge footnote to the main text
-
 \author{%
@@
 
-\maketitle
-
-\begin{abstract}
-  First-order model counting (FOMC) is a computational problem that asks to
-  count the models of a sentence in finite-domain first-order logic. Despite
-  being around for more than a decade, practical FOMC algorithms are still
-  unable to compute functions as simple as a factorial. We argue that the
-  capabilities of FOMC algorithms to date are limited by their inability to
-  express arbitrary recursive computations. To enable arbitrary recursion, we
-  relax the restrictions that typically accompany domain recursion and
-  generalise circuits used to express a solution to an FOMC problem to graphs
-  that may contain cycles. To this end, we enhance the most well-established
-  (weighted) FOMC algorithm \textsc{ForcLift} with new compilation rules and an
-  algorithm to check whether a recursive call is feasible. These improvements
-  allow the algorithm to construct efficient solutions to counting fundamental
-  structures such as injections and bijections. We end with a few conjectures on
-  what classes of instances could be liftable as a result.
-\end{abstract}
-
-\section{Introduction}\label{sec:introduction}
-
-% TODO: cite some works about synthesis
-
-% TODO: In the introduction it is written: "Crane uses a hybrid search algorithm
-% that applies some rules greedily and some using breadth-first search". Which
-% rules are applied greedily and which are not? What is the reason for parting
-% from the usual greedy method?
-
-% 1. What is the problem?
-% 2. Why is it interesting and important?
-
-\emph{First-order model counting} (FOMC) is the problem of computing the number
-of models of a sentence in first-order logic (FOL) given the size(s) of its
-domain(s)~\cite{DBLP:conf/pods/BeameBGS15}. \emph{Symmetric weighted FOMC}
-(WFOMC) extends FOMC with (pairs of) weights on predicates and asks for a
-weighted sum across all models instead. By fixing the sizes of the domains, a
-WFOMC instance can be rewritten as an instance of (propositional) weighted model
-counting~\cite{DBLP:journals/ai/ChaviraD08}. WFOMC emerged as the dominant
-approach to \emph{lifted (probabilistic) inference}. Lifted inference techniques
-exploit symmetries in probabilistic models by reasoning about sets rather than
-individuals~\cite{DBLP:conf/ecai/Kersting12}. By doing so, many instances become
-solvable in polynomial time~\cite{DBLP:conf/nips/Broeck11}. Lifted inference
-algorithms are typically used on probabilistic models such as probabilistic
-programming
-languages~\cite{DBLP:journals/ml/RaedtK15,DBLP:journals/ijar/RiguzziBZCL17},
-Markov logic
-networks~\cite{DBLP:conf/ijcai/BroeckTMDR11,DBLP:journals/cacm/GogateD16,DBLP:journals/ml/RichardsonD06},
-and other lifted graphical~\cite{DBLP:journals/ml/KimmigMG15} and statistical
-relational~\cite{DBLP:series/synthesis/2016Raedt} models. Lifted inference
-techniques for probabilistic databases, while developed somewhat independently,
-have also been inspired by
-WFOMC~\cite{DBLP:journals/pvldb/GatterbauerS15,DBLP:journals/debu/GribkoffSB14}.
-While WFOMC has received more attention in the literature, FOMC is an
-interesting problem in an of itself because of its connections to finite model
-theory~\cite{DBLP:conf/kr/BremenK21} and applications in enumerative
-combinatorics~\cite{DBLP:conf/ilp/BarvinekB0ZK21}. There is also a recent line
-of work that uses FOMC-based methods to count solutions to constraint
-satisfaction problems~\cite{DBLP:journals/jair/TotisDRK23}.
-
-% 3. Why is it hard? (E.g., why do naive approaches fail?)
-% complexity/liftability -> murky boundary
-
-Traditionally in computational complexity theory, a problem is \emph{tractable}
-if it can be solved in time polynomial in the instance size. The equivalent
-notion in (W)FOMC is liftability. A (W)FOMC instance is \emph{(domain-)liftable}
-if it can be solved in time polynomial in the size(s) of the
-domain(s)~\cite{jaeger2012liftability}. Over more than a decade, many classes of
-instances were shown to be
-liftable~\cite{DBLP:conf/kr/BremenK21,DBLP:conf/nips/KazemiKBP16,DBLP:conf/lics/KuusistoL18,DBLP:journals/jair/Kuzelka21}.
-First, Van den Broeck~\shortcite{DBLP:conf/nips/Broeck11} showed that the class
-of all sentences of FOL with up to two variables (denoted \FOtwo{}) is liftable.
-Then Beame et al.~\shortcite{DBLP:conf/pods/BeameBGS15} proved that there exists
-a sentence with three variables for which FOMC is $\#\P_{1}$-complete (i.e.,
-\FOthree{} is not liftable). Since these two seminal results, most of the
-research on (W)FOMC focused on developing faster solutions for the \FOtwo{}
-fragment~\cite{DBLP:conf/uai/BremenK21,DBLP:conf/aaai/MalhotraS22} and defining
-new liftable fragments. These fragments include \SFO{} and
-\SRU{}~\cite{DBLP:conf/nips/KazemiKBP16},
-\Uone{}~\cite{DBLP:conf/lics/KuusistoL18}, \FOtwo{} with tree
-axioms~\cite{DBLP:conf/kr/BremenK21}, and \Ctwo{} (i.e., the two-variable
-fragment with counting
-quantifiers)~\cite{DBLP:journals/jair/Kuzelka21,DBLP:conf/aaai/MalhotraS22}. On
-the empirical front, there are several implementations of exact WFOMC
-algorithms: \textsc{Alchemy}~\cite{DBLP:journals/cacm/GogateD16},
-\textsc{FastWFOMC}~\cite{DBLP:conf/uai/BremenK21},
-\textsc{ForcLift}~\cite{DBLP:conf/ijcai/BroeckTMDR11}, and
-\textsc{L2C}~\cite{DBLP:conf/kr/KazemiP16}. Approximate counting is supported by
-\textsc{Alchemy}, \textsc{ApproxWFOMC}~\cite{DBLP:conf/ijcai/BremenK20},
-\textsc{ForcLift}~\cite{DBLP:conf/uai/BroeckCD12},
-\textsc{Magician}~\cite{DBLP:conf/aaai/VenugopalSG15}, and
-\textsc{Tuffy}~\cite{DBLP:journals/pvldb/NiuRDS11}.
-
-% Magician: an approach to improve the efficiency of sampling and local search
-% based MLN inference algorithms by utilising \#CSP algorithms. Tuffy: grounding
-% and stochastic local search.
-
-% 4. Why hasn't it been solved before? (Or, what's wrong with previous proposed
-% solutions? How does mine differ?)
-% simple unliftable instances -> recursion
-
-However, none of the publicly available exact (W)FOMC algorithms can efficiently
-compute functions as simple as a factorial.\footnote{There is some previous work
-  showing how FOMC can compute
-  factorials~\cite{DBLP:journals/jair/Kuzelka21,DBLP:conf/kr/BremenK21,DBLP:conf/ijcai/Broeck16}.
-  One of them~\cite{DBLP:conf/ijcai/Broeck16} is an example `by hand' that does
-  not directly correspond to any algorithm.
-  Another~\cite{DBLP:journals/jair/Kuzelka21} proves that the problem is
-  liftable but contains no experimental results. The
-  third~\cite{DBLP:conf/kr/BremenK21} contains experimental results performed
-  with an algorithm, which is not publicly available.} We claim that this
-shortcoming is due to the inability of these algorithms to construct recursive
-solutions. The topic of recursion in the context of WFOMC has been studied
-before but in limited ways. Barv{\'{\i}}nek et
-al.~\shortcite{DBLP:conf/ilp/BarvinekB0ZK21} use WFOMC to generate numerical
-data that is then used to conjecture recurrence relations that explain that
-data. Van den Broeck~\shortcite{DBLP:conf/nips/Broeck11} introduced the idea of
-\emph{domain recursion}. Intuitively, domain recursion partitions a domain of
-size $n$ into a single explicitly named constant and the remaining domain of
-size $n-1$. However, many stringent conditions are enforced to ensure that the
-search for a tractable solution always terminates.
-
-% 5. What are the key components of my approach and results? Also include any
-% specific limitations.
-
-% 5.1) An overview of how ForcLift/Crane work.
-
-In this work, we show how to relax these restrictions in a way that results in a
-stronger (W)FOMC algorithm, capable of handling more instances (e.g., counting
-various injective mappings) in a lifted manner. The ideas presented in this
-paper are implemented in \textsc{Crane}---an extension of the arguably most
-well-known WFOMC algorithm \textsc{ForcLift}. \textsc{ForcLift} works in two
-stages: compilation and evaluation/propagation. In the first stage, various
-\emph{(compilation) rules} are applied to the input (or some derivative)
-formula, gradually constructing a circuit. In the second stage, the weights of
-the instance are propagated through the circuit, computing the weighted model
-count. Along with new compilation rules, \textsc{Crane} introduces changes to
-both stages of the process. First, while \textsc{ForcLift} applies compilation
-rules via greedy search, \textsc{Crane} also supports a hybrid search algorithm
-that applies some rules greedily and some using breadth-first search. Second,
-the product of compilation is not directly evaluated but rather interpreted as a
-collection of functions on domain sizes.
-
-% \footnote{There is also an intermediate stage called \emph{smoothing} that takes
-%   place between compilation and evaluation. As our changes to smoothing are
-%   rather elementary, we do not discuss them to not distract the reader from the
-%   main contributions of this paper.}
-
-% 5.2) The main idea: cycles that represent recursive calls.
-
-The main conceptual difference between \textsc{Crane} and \textsc{ForcLift} is
-that we utilise labelled directed graphs instead of circuits, where cycles
-represent recursive calls. Suppose the input formula $\phi$ depends on a domain
-of size $n \in \mathbb{N}_{0}$. \emph{Generalised domain recursion} (GDR)---one
-of the new compilation rules---transforms $\phi$ into a different formula $\psi$
-that has an additional constant and some new \emph{constraints}. After some
-additional transformations, the constraints in $\psi$ become `uniform' and can
-be removed, replacing the domain of size $n$ with a new domain of size
-$n-1$---this is the responsibility of the \emph{constraint removal} (CR)
-compilation rule. Afterwards, another compilation rule recognizes that the
-resulting formula is just like the input formula $\phi$ but with a different
-domain. This observation allows us to add a cycle-forming edge to the graph,
-which can be interpreted as function $f$ relying on $f(n-1)$ to compute $f(n)$.
-
-% 5.3) contributions, references to sections, shortcomings
-
-We begin by defining the representation used for sentences in FOL in
-\cref{sec:recprelims}. Then, in \cref{sec:methods}, we define the graphs that
-replace circuits in representing a solution to a (W)FOMC problem.
-\Cref{sec:rules} introduces the new compilation rules. In \cref{sec:interpret},
-we discuss how a graph can be interpreted as a collection of (potentially
-recursive) functions. In \cref{sec:results}, we compare \textsc{ForcLift} and
-\textsc{Crane} on a range of function-counting problems. We show that
-\textsc{Crane} performs as well as \textsc{ForcLift} on the instances that were
-already solvable by \textsc{ForcLift} but is also able to handle most of the
-instances that \textsc{ForcLift} fails on. Finally, in \cref{sec:conclusion}, we
-conclude by outlining some conjectures and directions for future work.
-
-\section{Preliminaries}\label{sec:recprelims}
-
-Our representation of FOMC instances is largely based on the format used
-internally by \textsc{ForcLift}, some aspects of which are described by Van den
-Broeck et al.~\shortcite{DBLP:conf/ijcai/BroeckTMDR11}. \textsc{ForcLift} can
-translate sentences in a variant of function-free many-sorted FOL with equality
-to this internal format. We use lowercase Latin letters for predicates (e.g.,
-$\texttt{p}$) and constants (e.g., $x$), uppercase Latin letters for variables
-(e.g., $X$), and uppercase Greek letters for domains (e.g., $\Delta$). Sometimes
-we write predicate $\texttt{p}$ as $\texttt{p}/n$, where $n \in \mathbb{N}^{+}$
-is the \emph{arity} of $\texttt{p}$. An \emph{atom} is
-$\texttt{p}(t_1, \dots, t_n)$ for some predicate $\texttt{p}/n$ and terms
-$t_{1}, \dots, t_{n}$. A \emph{term} is either a constant or a variable. A
-\emph{literal} is either an atom or the negation of an atom (denoted by
-$\neg \texttt{p}(t_1, \dots, t_n)$). Let $\mathcal{D}$ be the set of all
-relevant (finite) domains. Initially, $\mathcal{D}$ contains all domains
-mentioned by the input formula. During compilation, new domains are added to
-$\mathcal{D}$ by some of the compilation rules. Each such new domain is
-interpreted as a subset of some other domain in $\mathcal{D}$.
-
-\begin{definition}[Constraint]\label{def:constraint}
-  An \emph{(inequality) constraint} is a pair $(a, b)$, where $a$ is a variable,
-  and $b$ is either a variable or a constant.
-\end{definition}
-
-\begin{definition}[Clause]\label{def:clause}
-  A \emph{clause}\footnote{Van den Broeck et
-    al.~\shortcite{DBLP:conf/ijcai/BroeckTMDR11} refer to clauses as c-clauses.}
-  is a triple $c = (L, C, \delta_c)$, where $L$ is a set of literals, $C$ is a
-  set of constraints, and $\delta_c$ is the domain map of $c$. Let $\Vars$ be
-  the function that maps clauses and sets of either literals or constraints to
-  the set of variables contained within. In particular,
-  $\Vars(c) \coloneqq \Vars(L) \cup \Vars(C)$. \emph{Domain map}
-  $\delta_{c}\colon \Vars(c) \to \mathcal{D}$ is a function that maps all
-  variables in $c$ to their domains such that (s.t.) if $(X, Y) \in C$ for some
-  variables $X$ and $Y$, then $\delta_c(X) = \delta_c(Y)$. For convenience, we
-  sometimes write $\delta_c$ for the domain map of $c$ without unpacking $c$
-  into its three constituents.
-\end{definition}
-
-\paragraph{Notation.}
-For any set $S$, let $2^{S}$ denote its power set and
-$S^{\ast} \coloneqq \bigcup_{i=0}^{\infty} S^{i}$ the set of tuples of any
-finite length of elements of $S$. For any $n \in \mathbb{N}_{0}$, let
-$[n] \coloneqq \{\, 1, \dots, n \,\}$. For example, $[0] = \emptyset$, and
-$[2] = \{\, 1, 2 \,\}$. We write $\langle\rangle$ for an empty list,
-$\langle x \rangle$ for a list with one element $x$, $|l|$ for the length of
-list $l$, and $\pfun$ to denote partial functions. Let $S$ be a set of
-constraints or literals, $V$ a set of variables, and $x$ a variable or a
-constant. We write $S[x/V]$ to denote $S$ with all occurrences of all variables
-in $V$ replaced with $x$. Let $\Doms$ (respectively, $\Preds$) be the function
-that maps any clause or formula to the set of domains (respectively, predicates)
-used within, and let $\dom(f)$ denote the domain of function $f$.
-
-\begin{definition}[Formula]\label{def:formula}
-  A \emph{formula} (called a c-theory by Van den Broeck et
-  al.~\shortcite{DBLP:conf/ijcai/BroeckTMDR11}) is a set of clauses s.t.\ all
-  constraints and atoms `type check' with respect to domains. Each formula
-  $\phi$ has a map $\pi_{\phi}\colon \Preds(\phi) \to {\Doms(\phi)}^{\ast}$ such
-  that, for each predicate $\texttt{p}/n \in \Preds(\phi)$, we have that
-  $\pi_{\phi}(\texttt{p}) \in {\Doms(\phi)}^{n}$.\footnote{Similarly to
-    variables and predicates, constants are also mapped to domains, although we
-    keep this mapping implicit.}
-\end{definition}
-
-\begin{example}\label{example:first}
-  Let $\phi \coloneqq \{\, c_1, c_2 \,\}$ be a formula with clauses
-  \begin{align*}
-    c_1 &\coloneqq
-          \begin{multlined}[t]
-            (\{\, \neg \texttt{p}(X, Y), \neg \texttt{p}(X, Z) \,\}, \{\, (Y, Z) \,\}, \\
-            \{\, X \mapsto \Gamma, Y \mapsto \Delta, Z \mapsto \Delta \,\}),
-          \end{multlined}\\
-    c_2 &\coloneqq
-          \begin{multlined}[t]
-            (\{\, \neg \texttt{p}(X, Y), \neg \texttt{p}(Z, Y) \,\}, \{\, (X, Z) \,\}, \\
-            \{\, X \mapsto \Gamma, Y \mapsto \Delta, Z \mapsto \Gamma \,\})
-          \end{multlined}
-  \end{align*}
-  for some predicate $\texttt{p}/2$, variables $X$, $Y$, $Z$, and domains
-  $\Gamma$ and $\Delta$. Based on $\delta_{c_{1}}$ and $\delta_{c_{2}}$, we can
-  infer that $\pi_{\phi} = \{\, \texttt{p} \mapsto (\Gamma, \Delta) \,\}$. All
-  variables that occur as the first argument to $\texttt{p}$ are in $\Gamma$,
-  and, likewise, all variables that occur as the second argument to $\texttt{p}$
-  are in $\Delta$. Therefore, $\phi$ `type checks' as a valid formula.
-\end{example}
-
-There are two major differences between
-\cref{def:constraint,def:clause,def:formula} and the corresponding concepts
-introduced by Van den Broeck et al.~\shortcite{DBLP:conf/ijcai/BroeckTMDR11}.
-First, we decouple variable-to-domain assignments from constraints and move them
-to a separate function $\delta_{c}$ in \cref{def:clause}. Second, while Van den
-Broeck et al.~\shortcite{DBLP:conf/ijcai/BroeckTMDR11} allow for equality
-constraints and constraints of the form $X \not\in \Delta$ for some variable $X$
-and domain $\Delta$, we exclude such constraints simply because they are not
-needed.
-
-One can read a formula in our format as a sentence in FOL\@. All variables in a
-clause are implicitly universally quantified (but note that variables are never
-shared among clauses), and all clauses in a formula are implicitly linked by a
-conjunction. Thus, formula $\phi$ from \cref{example:first} reads as
-\begin{align*}
-  &\begin{multlined}[t]
-    (\forall X \in \Gamma\text{. }\forall Y, Z \in \Delta\text{. }\\
-    Y \ne Z \Rightarrow \neg \texttt{p}(X, Y) \lor \neg \texttt{p}(X, Z)) \land
-    \end{multlined}\\
-  &\begin{multlined}[t]
-    (\forall X, Z \in \Gamma\text{. }\forall Y \in \Delta\text{. }\\
-    X \ne Z \Rightarrow \neg \texttt{p}(X, Y) \lor \neg \texttt{p}(Z, Y)).
-    \end{multlined}
-\end{align*}
-
-Once domains are mapped to finite sets and constants to elements in those sets,
-a formula can be viewed as a set of conditions that the predicates (interpreted
-as relations) have to satisfy. Hence, FOMC is the problem of counting the number
-of combinations of relations that satisfy these conditions.
-
-\begin{example}\label{example:simple}
-  Let $\Delta$ be a domain of size $n \in \mathbb{N}_{0}$. The model count of
-  $\forall X \in \Delta\text{. } \texttt{p}(X) \lor \texttt{q}(X)$ is then
-  $3^{n}$. Intuitively, since both predicates are of arity one, they can be
-  interpreted as subsets of $\Delta$. Thus, the formula says that each element
-  of $\Delta$ has to be included in $\texttt{p}$ or in $\texttt{q}$ or in both,
-  i.e., there are three possibilities.
-\end{example}
-
-\begin{example}\label{example:smokers}
-  Consider a variant of the well-known `friends and smokers' example
-  $\forall X, Y \in \Delta\text{.
-  } \smokes(X) \land \friends(X, Y) \Rightarrow \smokes(Y)$. Letting
-  $n \coloneqq |\Delta|$ as in \cref{example:simple}, the model count can be
-  expressed as
-  $\sum_{k=0}^{n} \binom{n}{k}2^{n^{2} - k(n-k)}$~\cite{DBLP:conf/kr/BroeckMD14}.
-\end{example}
-% TODO: maybe add an extra sentence to explain what the formula means
-
-To formalise the idea of a model, let
-$\sigma\colon \mathcal{D} \to \mathbb{N}_{0}$ be the \emph{domain size function}
-that maps each domain to a non-negative integer.
-
-\begin{definition}\label{def:model}
-  Let $\phi$ be a formula and $\sigma$ a domain size function. A \emph{model} of
-  $(\phi, \sigma)$ is a map
-  $\mathfrak{M}\colon \Preds(\phi) \to 2^{\mathbb{N}_{0}^{\ast}}$ such that the
-  following two conditions are satisfied.
-  \begin{enumerate}
-    \item Let $\texttt{p}/n \in \Preds(\phi)$ be a predicate and let
-          $\pi_{\phi}(\texttt{p}) = {(d_{i})}_{i=1}^{n}$ for some domains
-          $d_{i} \in \Doms(\phi)$. Then
-          \begin{equation}\label{eq:subset}
-            \mathfrak{M}(\texttt{p}) \subseteq \prod_{i=1}^{n}[\sigma(d_{i})].\footnote{For simplicity, \cref{def:model} ignores constants.
-To include constants, one would replace $[\sigma(d_{i})]$ with a set that contains all constants associated with domain $d_{i}$, extended with enough new elements to make its cardinality $\sigma(d_{i})$.}
-          \end{equation}
-    \item As a collection of relations, $\mathfrak{M}$ satisfies $\phi$.
-  \end{enumerate}
-\end{definition}
-
-\begin{example}
-  Let $\phi$ be as in \cref{example:first} and let
-  $\sigma(\Gamma) = \sigma(\Delta) = 2$. Then the right-hand side of
-  \cref{eq:subset} becomes
-  \[
-    [\sigma(\Gamma)] \times [\sigma(\Delta)] = [2] \times [2] = \{\,(1, 1), (1, 2), (2, 1), (2, 2)\,\}
-  \]
-  There are $2^{4} = 16$ possible relations between $\Gamma$ and $\Delta$. Let
-  us count how many of them satisfy the conditions imposed on predicate
-  $\texttt{p}$. The empty relation does. All four relations of cardinality one
-  do too. Finally, there are two relations of cardinality two that satisfy the
-  conditions as well. Thus, the FOMC of $(\phi, \sigma)$ is 7. Incidentally, it
-  counts partial injections. We will continue to use the problem of counting
-  partial injections (and the formula from \cref{example:first} specifically) as
-  the main running example throughout the paper.
-\end{example}
-
-\section{From Circuits to Graphs}\label{sec:methods}
-
-\begin{figure}
-  \centering
-  \begin{forest}
-    for tree={s sep=10mm, sn edges}
-    [$\bigwedge_{x \in \Delta}$,ellipse,draw,label=right:{\color{blue}{$3^{n}$}}
-    [$\lor$,ellipse,draw,label=right:{\color{blue}{$2 + 1 = 3$}}
-    [$\land$,ellipse,draw,label=left:{\color{blue}{$2 \times 1 = 2$}}
-    [$p(x) \lor \neg p(x)$,rectangle,draw,fill=gray!25,label=below:{\color{blue}{2}}]
-    [$\land$,ellipse,draw,label={[label distance=0cm,text=blue]87:$1 \times 1 = 1$}
-    [$q(x)$,rectangle,draw,fill=gray!25,label=below:{\color{blue}{1}}]
-    [$\top$,rectangle,draw,fill=gray!25,label=below:{\color{blue}{1}}]
-    ]
-    ]
-    [$\land$,ellipse,draw,label=right:{\color{blue}{$1 \times 1 = 1$}}
-    [$\neg q(x)$,rectangle,draw,fill=gray!25,label=below:{\color{blue}{1}}]
-    [$p(x)$,rectangle,draw,fill=gray!25,label=below:{\color{blue}{1}}]
-    ]
-    ]
-    ]
-  \end{forest}
-  \caption{A circuit produced by \textsc{ForcLift} for \cref{example:simple}.
-    Values and computations in blue (on the outside of each node) show how a
-    bottom-up evaluation of the circuit computes the model
-    count.}\label{fig:simplecircuit}
-\end{figure}
-
-Darwiche~\shortcite{DBLP:journals/jancl/Darwiche01} introduced
-\emph{deterministic decomposable negation normal form} (d-DNNF) circuits for
-propositional knowledge compilation and showed that the model count of a
-propositional formula can be computed in time linear in the size of the circuit.
-Van den Broeck et al.~\shortcite{DBLP:conf/ijcai/BroeckTMDR11} generalised them
-to FOL via \emph{first-order d-DNNF (FO d-DNNF) circuits}. FO d-DNNF circuits
-(hereafter simply called \emph{circuits}) are directed acyclic graphs with nodes
-corresponding to formulas in FOL---see \cref{fig:simplecircuit} for an example.
-The following types of nodes are supported by \textsc{ForcLift}: caching
-($\Reff$), contradiction ($\bot$), tautology ($\top$), decomposable conjunction
-($\land$), decomposable set-conjunction ($\bigwedge$), deterministic disjunction
-($\lor$), deterministic set-disjunction ($\bigvee$), domain recursion,
-grounding, inclusion-exclusion, smoothing, and unit clause. We refer the reader
-to previous work~\cite{DBLP:conf/nips/Broeck11,DBLP:conf/ijcai/BroeckTMDR11} for
-more information about node types and their interpretations for computing the
-(W)FOMC\@.
-
-\begin{figure}[t]
-  \centering
-  \begin{forest}
-    for tree={sn edges}
-    [$\GDR_{\Gamma \gets \Gamma \setminus \{\, x \,\}}$,ellipse,draw,name=gdr
-    [$\bigvee_{\Delta^\top \subseteq \Delta}$,ellipse,draw
-    [$\CR_{\Gamma \mapsto \Gamma'}$,ellipse,draw
-    [$\land$,ellipse,draw
-    [$\bot$,rectangle,draw,fill=gray!25]
-    [$\Reff_{\{\, \Gamma \mapsto \Gamma', \Delta \mapsto \Delta^{\bot} \,\}}$,ellipse,draw,name=ref]
-    ]
-    ]
-    ]
-    ]
-    \draw[-Latex,bend right=45] (ref) to (gdr);
-  \end{forest}
-  \caption{A simplified version of the FCG constructed by \textsc{Crane} for the
-    problem of counting partial injections from \cref{example:first}. Here we
-    omit some parameters as well as nodes whose only arithmetic effect is
-    multiplication by one.}\label{fig:examplefcg}
-\end{figure}
-
-In this paper, we introduce \emph{FO d-DNNF computational graphs} (FCGs) that
-generalise circuits by dispensing with acyclicity. Formally, an FCG is a (weakly
-connected) directed graph with a single source, node labels, and ordered
-outgoing edges. Node labels consist of two parts: the \emph{type} and the
-\emph{parameters}. The type of a node determines its out-degree. We make the
-following changes and additions to the node types already supported by
-\textsc{ForcLift}. First, we introduce a new node type for constraint removal
-($\CR$). Second, we replace domain recursion with generalised domain recursion
-($\GDR$). And third, for reasoning about partially-constructed FCGs, we write
-$\star$ for a placeholder type that is yet to be replaced. Similarly to Van den
-Broeck et al.~\shortcite{DBLP:conf/ijcai/BroeckTMDR11}, we write $T_p$ for an
-FCG that has a node with the label $T_p$ (i.e., type $T$ and parameter(s) $p$)
-and $\star$'s as all of its direct successors. See \cref{fig:examplefcg} for an
-example FCG\@. Its source node has out-degree 1, label
-$\GDR_{\Gamma \gets \Gamma \setminus \{\, x \,\}}$, and type $\GDR$.
-
-% Connecting FCGs with formulas
-Finally, we introduce a structure that represents a solution to a (W)FOMC
-problem while it is still being built. A \emph{chip} is a pair $(G, L)$, where
-$G$ is an FCG, and $L$ is a list of formulas, s.t. $|L|$ is equal to the number
-of $\star$'s in $G$. $L$ contains formulas that still need to be compiled. Once
-a formula is compiled, it replaces one of the $\star$'s in $G$ according to a
-set order. We say that an FCG is \emph{complete} (i.e., it represents a
-\emph{complete solution}) if it has no $\star$'s. Similarly, a chip is complete
-if its FCG is complete (or, equivalently, the list of formulas is empty).
-
-\section{New Compilation Rules}\label{sec:rules}
-
-A \emph{(compilation) rule} takes a formula and returns a set of chips. The
-cardinality of this set is the number of different ways in which the rule can be
-applied to the input formula. While
-\textsc{ForcLift}~\cite{DBLP:conf/ijcai/BroeckTMDR11} heuristically chooses one
-of them, in an attempt to not miss a solution, \textsc{Crane} returns them all.
-In particular, if a rule returns an empty set, then that rule does not apply to
-the formula.
-
-\subsection{Generalised Domain Recursion}\label{sec:dr}
-
-% Main idea
-The main idea behind domain recursion (both the original version by Van den
-Broeck~\shortcite{DBLP:conf/nips/Broeck11} and the one presented here) is as
-follows. Let $\Omega \in \mathcal{D}$ be a domain. Assuming that
-$\Omega \ne \emptyset$, pick some $x \in \Omega$. Then, for every variable
-$X \in \Omega$ that occurs in a literal, consider two possibilities: $X = x$ and
-$X \ne x$.
-
-\begin{example}\label{example:dr}
-  Let $\phi$ be a formula with a single clause
-  \begin{multline*}
-    (\{\, \neg \texttt{p}(X, Y), \neg \texttt{p}(X, Z) \,\}, \{\, (Y, Z) \,\}, \\
-    \{\, X \mapsto \Gamma, Y \mapsto \Delta, Z \mapsto \Delta \,\}).
-  \end{multline*}
-  Then we can introduce constant $x \in \Gamma$ and rewrite $\phi$ as
-  $\phi' = \{\, c_{1}, c_{2} \,\}$, where
-  \begin{align*}
-    c_{1} &= \begin{multlined}[t]
-      (\{\, \neg \texttt{p}(x, Y), \neg \texttt{p}(x, Z) \,\}, \{\, (Y, Z) \,\}, \\
-      \{\, Y \mapsto \Delta, Z \mapsto \Delta \,\}),
-      \end{multlined}\\
-    c_{2} &= \begin{multlined}[t]
-      (\{\, \neg \texttt{p}(X, Y), \neg \texttt{p}(X, Z) \,\}, \{\, (X, x), (Y, Z) \,\}, \\
-      \{\, X \mapsto \Gamma', Y \mapsto \Delta, Z \mapsto \Delta \,\}),
-      \end{multlined}
-  \end{align*}
-  and $\Gamma' = \Gamma \setminus \{\, x \,\}$.
-\end{example}
-
-% Original domain recursion
-Van den Broeck~\shortcite{DBLP:conf/nips/Broeck11} imposes stringent conditions
-on the input formula to ensure that the expanded version of the formula (as in
-\cref{example:dr}) can be handled efficiently. For instance,
-\cref{example:first} cannot be handled by \textsc{ForcLift} because there is no
-root binding class, i.e., the two root variables belong to different equivalence
-classes with respect to the binding relationship. The clauses in this expanded
-formula are then partitioned into three parts based on whether the
-transformation introduced constants or constraints or both. The aforementioned
-conditions ensure that these parts can be treated independently.
-
-\begin{algorithm}[t]
-  \caption{The compilation rule for $\GDR$ nodes.}\label{alg:domainrecursion}
-  \KwIn{formula $\phi$, set of all relevant domains $\mathcal{D}$}
-  \KwOut{set of chips $S$}
-  $S \gets \emptyset$\;
-  \ForEach{domain $\Omega \in \mathcal{D}$ s.t.\ there is $c \in \phi$ and $X \in \Vars(L_c)$ s.t. $\delta_c(X) = \Omega$\label{line:condition}}{
-    $\phi' \gets \emptyset$\;
-    $x \gets \text{a new constant in domain } \Omega$\;\label{line:constant}
-    \ForEach{clause $c = (L, C, \delta) \in \phi$\label{line:forclause}}{
-      $V \gets \{\, X \in \Vars(L) \mid \delta(X) = \Omega \,\}$\;\label{line:V}
-      \ForEach{$W \subseteq V$ s.t. $W^2 \cap C = \emptyset$ {\bf and} $W \cap \{\, X \in \Vars(C) \mid (X, y) \in C \text{ for some constant } y \,\} = \emptyset$\label{line:conditions}}{
-        \tcc{$\delta'$ restricts $\delta$ to the new set of variables}
-        $\phi' \gets \phi' \cup \{\, (L[x/W], C[x/W] \cup \{\, (X, x) \mid (X \in V \setminus W) \,\}, \delta') \,\}$\;\label{line:generation}
-      }
-    }
-    $S \gets S \cup \{\, (\GDR_{\Omega \gets \Omega \setminus \{\, x \,\}}, \langle\phi'\rangle) \,\}$\;
-  }
-\end{algorithm}
-
-% Description of GDR, in contrast to DR
-In contrast, GDR has only one precondition: for GDR to be applicable on domain
-$\Omega \in \mathcal{D}$, there must be at least one variable with domain
-$\Omega$ that is featured in a literal (and not just in constraints). Without
-such variables, GDR would have no effect on the formula. GDR is also simpler in
-that the expanded formula is left as-is to be handled by other compilation
-rules. Typically, after a few more rules are applied, a combination of $\CR$ and
-$\Reff$ nodes introduces a cycle-inducing edge back to the $\GDR$ node, thus
-completing the definition of a recursive function. The GDR compilation rule is
-summarised as \cref{alg:domainrecursion} and explained in more detail using the
-example below.
-
-\begin{example}
-  Let $\phi \coloneqq \{\, c_1, c_2 \,\}$ be the formula from
-  \cref{example:first}. While GDR is possible on both domains, here we
-  illustrate how it works on $\Gamma$. Having chosen a domain, the algorithm
-  iterates over the clauses of $\phi$. Suppose \cref{line:forclause} picks
-  $c = c_1$ as the first clause. Then, set $V$ is constructed to contain all
-  variables with domain $\Omega = \Gamma$ that occur in the literals of clause
-  $c$. In this case, $V = \{\, X \,\}$.
-
-  \Cref{line:conditions} iterates over all subsets $W \subseteq V$ of variables
-  that can be replaced by a constant without resulting in evidently
-  unsatisfiable formulas. We impose two restrictions on $W$. First,
-  $W^2 \cap C = \emptyset$ ensures that there are no pairs of variables in $W$
-  that are constrained to be distinct, since that would result in an $x \ne x$
-  constraint after substitution. Similarly, we want to avoid variables in $W$
-  that have inequality constraints with constants: after the substitution, such
-  constraints would transform into inequality constraints between two constants.
-  In this case, both subsets of $V$ satisfy these conditions, and
-  \cref{line:generation} generates two clauses for the output formula:
-  \begin{multline*}
-    (\{\, \neg \texttt{p}(X, Y), \neg \texttt{p}(X, Z) \,\}, \{\, (Y, Z), (X, x) \,\}, \\
-    \{\, X \mapsto \Gamma, Y \mapsto \Delta, Z \mapsto \Delta \,\}),
-  \end{multline*}
-  from $W = \emptyset$ and
-  \[
-    (\{\, \neg \texttt{p}(x, Y), \neg \texttt{p}(x, Z) \,\}, \{\, (Y, Z) \,\}, \{\, Y \mapsto \Delta, Z \mapsto \Delta \,\})
-  \]
-  from $W = V$.
-
-  When \cref{line:forclause} picks $c = c_2$, then $V = \{\, X, Z \,\}$. The
-  subset $W = V$ fails to satisfy the conditions on \cref{line:conditions}
-  because of the $X \ne Z$ constraint. The other three subsets of $V$ all
-  generate clauses for $\phi'$. Indeed, $W = \emptyset$ generates
-  \begin{multline*}
-    (\{\, \neg \texttt{p}(X, Y), \neg \texttt{p}(Z, Y) \,\}, \{\, (X, Z), (X, x), (Z, x) \,\}, \\
-    \{\, X \mapsto \Gamma, Y \mapsto \Delta, Z \mapsto \Gamma \,\}),
-  \end{multline*}
-  $W = \{\, X \,\}$ generates
-  \[
-    (\{\, \neg \texttt{p}(x, Y), \neg \texttt{p}(Z, Y) \,\}, \{\, (Z, x) \,\}, \{\, Y \mapsto \Delta, Z \mapsto \Gamma \,\}),
-  \]
-  and $W = \{\, Z \,\}$ generates
-  \[
-    (\{\, \neg \texttt{p}(X, Y), \neg \texttt{p}(x, Y) \,\}, \{\, (X, x) \,\}, \{\, X \mapsto \Gamma, Y \mapsto \Delta \,\}).
-  \]
-\end{example}
-
-\begin{theorem}[Correctness of $\GDR$\footnote{\Cref{thm:correctness1} is equivalent to
-    Proposition~3 by~\cite{DBLP:conf/nips/Broeck11}.}]\label{thm:correctness1}
-  Let $\phi$ be the formula used as input to \cref{alg:domainrecursion},
-  $\Omega \in \mathcal{D}$ the domain selected on \cref{line:condition}, and
-  $\phi'$ the formula constructed by the algorithm for $\Omega$. Assume that
-  $\Omega \ne \emptyset$. Then $\phi \equiv \phi'$.
-\end{theorem}
-\begin{proof}
-  Let $x$ be the constant introduced on \cref{line:constant} and $c$ a clause of
-  $\phi$ selected on \cref{line:forclause} of the algorithm. We will show that
-  $c$ is equivalent to the conjunction of clauses added to $\phi'$ on
-  \cref{line:conditions,line:generation}.
-
-  If $c$ has no variables with domain $\Omega$, then
-  \cref{line:conditions,line:generation} simply add a copy of $c$ to $\phi'$. If
-  $c$ has one variable with domain $\Omega$, say, $X$, then
-  $c \equiv \forall X \in \Omega\text{. } \psi$ for some formula $\psi$ with one
-  free variable $X$. In this case, \cref{line:conditions,line:generation} create
-  two clauses: $\psi[x/\{\, X \,\}]$ and $\forall X \in \Omega\text{.
-  } X \ne x \Rightarrow \psi$. It is easy to see that their conjunction is
-  equivalent to $c$ provided that $\Omega \ne \emptyset$ and so $x$ is a
-  well-defined constant.
-
-  Let $V$ be the set of variables introduced on \cref{line:V}. It remains to
-  show that repeating the transformation
-  \[
-    \forall X \in \Omega\text{. } \psi \mapsto \{\, \psi[x/\{\, X \,\}], \forall X \in \Omega\text{. } X \ne x \Rightarrow \psi \,\}
-  \]
-  for all variables $X \in V$ produces the same clauses as
-  \cref{line:conditions,line:generation} (except for some tautologies that the
-  latter method skips). Note that the order in which these operations are
-  applied is immaterial. In other words, if we add inequality constraints for
-  variables ${\{\, X_{i} \,\}}_{i=1}^{n}$, and apply substitution for variables
-  $V \setminus {\{\, X_{i} \,\}}_{i=1}^{n}$, then---regardless of the order of
-  operations---we get
-  \[
-    \forall X_{1}, \dots, X_{n} \in \Omega\text{.} \bigwedge_{i=1}^{n} X_{i} \ne x \Rightarrow \psi\left[x / \left(V \setminus {\{\, X_{i} \,\}}_{i=1}^{n}\right)\right].
-  \]
-  This formula is equivalent to the clause generated on \cref{line:generation}
-  with $W = V \setminus {\{\, X_{i} \,\}}_{i=1}^{n}$. Thus, for every clause $c$
-  of $\phi$, the new formula $\phi'$ gets a set of clauses whose conjunction is
-  equivalent to $c$. Hence, the two formulas are equivalent.
-\end{proof}
-
-\subsection{Constraint Removal}\label{sec:cr}
-
-Recall that GDR on a domain $\Omega$ creates constraints of the form $X_i \ne x$
-for some constant $x \in \Omega$ and family of variables $X_i \in \Omega$. Once
-certain conditions are satisfied, we can eliminate these constraints and replace
-$\Omega$ with a new domain $\Omega'$, which can be interpreted as
-$\Omega \setminus \{\, x \,\}$. These conditions are that a constraint of the
-form $X \ne x$ exists for all variables $X \in \Omega$ across all clauses, and
-such constraints are the only place where $x$ occurs. We formalise the
-conditions as \cref{def:replaceable}.
-
-\begin{definition}\label{def:replaceable}
-  With respect to a formula $\phi$, a pair $(\Omega, x)$ of a domain
-  $\Omega \in \mathcal{D}$ and its element $x \in \Omega$ is called
-  \emph{replaceable} if
-  \begin{itemize}
-    \item $x$ does not occur in any literal of any clause of $\phi$,
-    \item and for each clause $c = (L, C, \delta_c) \in \phi$ and variable
-          $X \in \Vars(c)$, either $\delta_c(X) \ne \Omega$ or $(X, x) \in C$.
-  \end{itemize}
-\end{definition}
-
-\begin{algorithm}[t]
-  \caption{The compilation rule for $\CR$ nodes.}\label{alg:constraintremoval}
-  \KwIn{formula $\phi$, set of all relevant domains $\mathcal{D}$}
-  \KwOut{set of chips $S$}
-  $S \gets \emptyset$\;
-  \ForEach{replaceable pair $(\Omega \in \mathcal{D}, x \in \Omega)$\label{line:crconditions}}{
-    add a new domain $\Omega'$ to $\mathcal{D}$\;\label{line:newdomain}
-    $\phi' \gets \emptyset$\;
-    \ForEach{clause $(L, C, \delta) \in \phi$}{
-      $C' \gets \{\, (a, b) \in C \mid b \ne x \,\}$\;\label{line:constraintremoval}
-      \nosemic$\delta' \gets X \mapsto
-      \begin{cases}
-        \Omega' & \text{if } \delta(X) = \Omega\\
-        \delta(X) & \text{otherwise;}
-      \end{cases}$\;\label{line:newdelta}
-      $\phi' \gets \phi' \cup \{\, (L, C', \delta') \,\}$\;
-    }
-    $S \gets S \cup \{\, (\CR_{\Omega \mapsto \Omega'}, \langle\phi'\rangle) \,\}$\;
-  }
-\end{algorithm}
-
-Once a replaceable pair is found, \cref{alg:constraintremoval} proceeds to
-construct the new formula by removing constraints (on
-\cref{line:constraintremoval}) and constructing a new domain map $\delta'$ that
-replaces $\Omega$ with $\Omega'$ (on \cref{line:newdelta}).
-
-\begin{example}
-  Let $\phi = \{\, c_1, c_2 \,\}$ be a formula with clauses
-  \begin{align*}
-    c_1 &=
-          \begin{multlined}[t]
-            (\{\, \neg \texttt{p}(X, Y), \neg \texttt{p}(X, Z) \,\}, \{\, (X, x), (Y, Z) \,\}, \\
-            \{\, X \mapsto \Gamma, Y \mapsto \Delta, Z \mapsto \Delta \,\}),
-          \end{multlined}\\
-    c_2 &=
-          \begin{multlined}[t]
-            (\{\, \neg \texttt{p}(X, Y), \neg \texttt{p}(Z, Y) \,\}, \\
-            \{\, (X, x), (Z, X), (Z, x) \,\}, \\
-            \{\, X \mapsto \Gamma, Y \mapsto \Delta, Z \mapsto \Gamma \,\}).
-          \end{multlined}
-  \end{align*}
-  Domain $\Gamma$ and its element $x \in \Gamma$ satisfy the preconditions for
-  CR\@. The rule introduces a new domain $\Gamma'$ and transforms $\phi$ to
-  $\phi' = (c_1', c_2')$, where
-  \begin{align*}
-    c_1' &=
-           \begin{multlined}[t]
-             (\{\, \neg \texttt{p}(X, Y), \neg \texttt{p}(X, Z) \,\}, \{\, (Y, Z) \,\}, \\
-             \{\, X \mapsto \Gamma', Y \mapsto \Delta, Z \mapsto \Delta \,\}),
-           \end{multlined} \\
-    c_2' &=
-           \begin{multlined}[t]
-             (\{\, \neg \texttt{p}(X, Y), \neg \texttt{p}(Z, Y) \,\}, \{\, (Z, X) \,\}, \\
-             \{\, X \mapsto \Gamma', Y \mapsto \Delta, Z \mapsto \Gamma' \,\}).
-           \end{multlined}
-  \end{align*}
-\end{example}
-
-\begin{theorem}[Correctness of $\CR$]
-  Let $\phi$ be the input formula of \cref{alg:constraintremoval}, $(\Omega, x)$
-  a replaceable pair, and $\phi'$ the formula constructed by the algorithm, when
-  $(\Omega, x)$ is selected on \cref{line:crconditions}. Then
-  $\phi \equiv \phi'$, where the domain $\Omega'$ introduced on
-  \cref{line:newdomain} is interpreted as $\Omega \setminus \{\, x \,\}$.
-\end{theorem}
-\begin{proof}
-  Since there is a natural bijection between the clauses of $\phi$ and $\phi'$,
-  we shall argue about the equivalence of each pair of clauses. Let $c$ be an
-  arbitrary clause of $\phi$ and $c'$ its corresponding clause of $\phi'$.
-
-  If $c$ has no variables with domain $\Omega$, then it cannot have any
-  constraints involving $x$, so $c' = c$. Otherwise, for notational simplicity,
-  let us assume that $X$ is the only variable in $c$ with domain $\Omega$ (the
-  proof for an arbitrary number of variables is virtually the same). By
-  \cref{def:replaceable}, we can rewrite $c$ as $\forall X \in \Omega\text{.
-  } X \ne x \Rightarrow \psi$, where $\psi$ is a formula with $X$ as the only free
-  variable and with no mention of either $x$ or $\Omega$. Then
-  $c' \equiv \forall X \in \Omega'\text{. } \psi$. Since
-  $\Omega' \coloneqq \Omega \setminus \{\, x \,\}$, we have that $c \equiv c'$.
-  Since $c$ was an arbitrary clause of $\phi$, this completes the proof that
-  $\phi \equiv \phi'$.
-\end{proof}
-
-\subsection{Identifying Opportunities for Recursion}\label{sec:ref}
-
-\paragraph{Hashing.}
-We use (integer-valued) hash functions to discard pairs of formulas that are too
-different for recursion to work. The hash code of a clause
-$c = (L, C, \delta_{c})$ (denoted by $\# c$) combines the hash codes of the sets
-of constants and predicates in $c$, the numbers of positive and negative
-literals, the number of inequality constraints $|C|$, and the number of
-variables $|\Vars(c)|$. The hash code of a formula $\phi$ combines the hash
-codes of all its clauses and is denoted by $\#\phi$.
-
-\paragraph{Caching.}
-\textsc{ForcLift}~\cite{DBLP:conf/ijcai/BroeckTMDR11} uses a cache to check if
-a formula is identical to one of the formulas that have already been fully
-compiled. To facilitate recursion, we extend the caching scheme to include
-formulas that have been encountered but not fully compiled yet. Formally, we
-define a \emph{cache} to be a map from integers (e.g., hash codes) to sets of
-pairs of the form $(\phi, v)$, where $\phi$ is a formula, and $v$ is an FCG
-node.
-
-\begin{algorithm}[t]
-  \caption{The compilation rule for $\Reff$ nodes.}\label{alg:trycache}
-  \KwIn{formula $\phi$, cache $C$}
-  \KwOut{a set of chips}
-
-  \ForEach{formula and node $(\psi, v) \in C(\#\phi)$}{\label{line:selectformula}
-    $\rho \gets \identifyRecursion{$\phi$, $\psi$}$\;
-    \lIf{$\rho \ne {\normalfont \texttt{null}}$}{\Return{$\{\, (\Reff_\rho(v), \langle\rangle) \,\}$}}\label{line:rho}
-  }
-  \Return{$\emptyset$}\;
-
-  \Fn{\identifyRecursion{formula $\phi$, formula $\psi$, map $\rho = \emptyset$}}{
-    \lIf{$|\phi| \ne |\psi|$ {\bf or} $\#\phi \ne \#\psi$}{\Return{\normalfont\texttt{null}}}
-    \lIf{$\phi = \emptyset$}{\Return{$\rho$}}
-    \ForEach{clause $c \in \psi$\label{line:for1}}{
-      \ForEach{clause $d \in \phi$ s.t. $\#d=\#c$\label{line:for2}}{
-        \ForAll{$\gamma \in \generateMaps{$c$, $d$, $\rho$}$\label{line:generateMaps}}{
-          $\rho' \gets \identifyRecursion{$\phi\setminus\{\, d \,\}$, $\psi\setminus\{\, c \,\}$, $\rho\cup\gamma$}$\;\label{line:recursion}
-          \lIf{$\rho' \ne {\normalfont \texttt{null}}$}{\Return{$\rho'$}}
-        }
-      }
-      \Return{\normalfont\texttt{null}}\;
-    }
-  }
-\end{algorithm}
-
-% Cache $C$ is used to partition all previously-encountered formulas based on
-% their hash codes.
-\Cref{alg:trycache} describes the compilation rule for creating $\Reff$ nodes.
-For every formula $\psi$ in the cache s.t. $\#\psi = \#\phi$, function
-\texttt{r} is called to check whether a recursive call is feasible. If it is,
-\texttt{r} returns a (total) map $\rho\colon \Doms(\psi) \to \Doms(\phi)$ that
-shows how $\psi$ can be transformed into $\phi$ by replacing each domain
-$\Omega \in \Doms(\psi)$ with $\rho(\Omega) \in \Doms(\phi)$. Otherwise,
-\texttt{r} returns \texttt{null} to signify that $\phi$ and $\psi$ are too
-different for recursion to work. This happens if $\phi$ and $\psi$ (or their
-subformulas explored in recursive calls) are structurally different (i.e., the
-numbers of clauses or the hash codes fail to match) or if a clause of $\psi$
-cannot be paired with a sufficiently similar clause of $\phi$. Function
-\texttt{r} works by iterating over pairs of clauses of $\phi$ and $\psi$ that
-have the same hash codes. For every pair of sufficiently similar clauses,
-\texttt{r} calls itself on the remaining clauses until the map
-$\rho\colon \Doms(\psi) \pfun \Doms(\phi)$ becomes total, and all clauses are
-successfully coupled.
-
-Function \texttt{genMaps} checks the compatibility of a pair of clauses. It
-considers every possible bijection $\beta\colon \Vars(c) \to \Vars(d)$ and map
-$\gamma\colon \Doms(c) \to \Doms(d)$ s.t.
-\[
-  \begin{tikzcd}
-    \Vars(c) \ar[r, dashed, "\beta"] \arrow[d, swap, "\delta_c"] & \Vars(d) \ar[d, "\delta_d"] \\
-    \Doms(c) \ar[r, dashed, "\gamma"] \ar[d, hookrightarrow] & \Doms(d) \ar[d, hookrightarrow] \\
-    \Doms(\psi) \ar[r, swap, "\rho", "|" marking, outer sep=5pt] & \Doms(\phi).
-  \end{tikzcd}
-\]
-commutes, and $c$ becomes equal to $d$ when its variables are replaced according
-to $\beta$ and its domains replaced according to $\gamma$. The function then
-returns each such $\gamma$ as soon as possible. The commutativity check also
-ensures that $\rho \cup \gamma$ is possible on \cref{line:recursion} of
-\cref{alg:trycache}. The resulting (partial) function $\rho \cup \gamma$ is the
-unique function s.t. $\rho \cup \gamma|_{\dom(\rho)} = \rho$, and
-$\rho \cup \gamma|_{\dom(\gamma)} = \gamma$. The operation is defined when
-$\rho|_{\dom(\rho)\cap\dom(\gamma)} = \gamma|_{\dom(\rho)\cap\dom(\gamma)}$.
-
-\begin{theorem}[Correctness of $\Reff$]
-  Let $\phi$ be the formula used as input to \cref{alg:trycache}. Let $\psi$ be
-  any formula selected on \cref{line:selectformula} of the algorithm such that
-  $\rho \ne {\normalfont\texttt{null}}$ on \cref{line:rho}. Let $\sigma$ be a
-  domain size function. Then the set of models of $(\psi, \sigma \circ \rho)$ is
-  equal to the set of models of $(\phi, \sigma)$.
-\end{theorem}
-\begin{proof}
-  We first show that the right-hand side of \cref{eq:subset} is the same for
-  models of both $(\phi, \sigma)$ and $(\psi, \sigma \circ \rho)$.
-  \Cref{alg:trycache} ensures that $\psi \equiv \phi$ up to domains. In
-  particular, this means that $\Preds(\psi) = \Preds(\phi)$. The square in
-  \begin{equation}\label[diagram]{diagram:ref}
-    \begin{tikzcd}
-      \Preds(\psi) \ar[equal]{r} \ar[d, swap, "\pi_{\psi}"] & \Preds(\phi) \ar[d, "\pi_{\phi}"] \\
-      {\Doms(\psi)}^{\ast} \ar[r, "\rho"] & {\Doms(\phi)}^{\ast} \ar[r, "\sigma"] & \mathbb{N}_{0}^{\ast}
-    \end{tikzcd}
-  \end{equation}
-  commutes by \cref{def:formula} and the definition of $\rho$. In other words,
-  for any predicate $\texttt{p}/n \in \Preds(\psi) = \Preds(\phi)$, function
-  $\rho$ translates the domains associated with $\texttt{p}$ in $\psi$ to the
-  domains associated with $\texttt{p}$ in $\phi$. Let
-  $\pi_{\phi}(\texttt{p}) = {(d_{i})}_{i=1}^{n}$ and
-  $\pi_{\psi}(\texttt{p}) = {(e_{i})}_{i=1}^{n}$ for some domains
-  $d_{i} \in \Doms(\phi)$ and $e_{i} \in \Doms(\psi)$. Since
-  $\rho(e_{i}) = d_{i}$ for all $i = 1, \dots, n$ by the commutativity in
-  \cref{diagram:ref}, we get that
-  \begin{equation}\label{eq:equality}
-    \prod_{i=1}^{n}[\sigma(d_{i})] = \prod_{i=1}^{n}[\sigma \circ \rho(e_{i})]
-  \end{equation}
-  as required. Certainly, any subset of the left-hand side of \cref{eq:equality}
-  (e.g., $\mathfrak{M}(\texttt{p})$, where $\mathfrak{M}$ is a model of
-  $(\phi, \sigma)$) is a subset of the right-hand side and vice versa. Since
-  $\phi$ and $\psi$ semantically only differ in what domains they refer to,
-  every model of $\phi$ satisfies $\psi$ and vice versa, completing the proof.
-\end{proof}
-
-\section{How to Interpret an FCG}\label{sec:interpret}
-
-When \textsc{ForcLift}~\cite{DBLP:conf/ijcai/BroeckTMDR11} compiles a WFOMC
-instance into a circuit, each node type encodes an arithmetic operation on its
-inputs and parameters. These operations are then immediately performed while
-traversing the circuit. With \textsc{Crane}, the interpretation of an FCG is a
-collection of functions. Each function has (some) domain sizes as parameters and
-may contain recursive calls to other functions, including itself. While there
-may be any number of subsidiary functions, there is always one main function
-that can be called with the sizes of the domains of the input formula as
-arguments. Henceforth, this function is always called $f$, and it is defined by
-the source node.
-
-The interpretation of a node is decided by its type. Here we describe the
-interpretations of new (or significantly changed) types and refer the reader to
-previous work~\cite{DBLP:conf/ijcai/BroeckTMDR11} for information on other
-types. The interpretation of a $\CR$ or a $\GDR$ node is simply the
-interpretation of its only direct successor. Obviously, $\star$ nodes have no
-interpretation as incomplete FCGs are not meant to be interpreted. The
-interpretation of a $\Reff$ node is a function call. The direct successor of the
-$\Reff$ node (say, $v$) then must introduce a function. The parameters of this
-function are the sizes of all domains used by nodes reachable from $v$.
-
-\begin{example}\label{example:interpretation}
-  Consider the FCG from \cref{fig:examplefcg}. The input formula (i.e., the
-  formula from \cref{example:first}) has two domains: $\Gamma$ and $\Delta$.
-  Thus, the interpretation of the FCG is a function
-  $f\colon \mathbb{N}_{0} \times \mathbb{N}_{0} \to \mathbb{R}_{\ge 0}$. Let
-  $m \coloneqq |\Gamma|$, and $n \coloneqq |\Delta|$. The node labelled
-  $\bigvee_{\Delta^{\top} \subseteq \Delta}$ tells us that
-  $f(m, n) = \sum_{l = 0}^{n} \binom{n}{l} \square$, where $\square$ is the
-  interpretation of the remaining subgraph, and $l$ iterates over all possible
-  sizes of $\Delta^{\top}$. It also creates two subdomains
-  $\Delta^{\top}, \Delta^{\bot} \subseteq \Delta$ that partition $\Delta$, i.e.,
-  as the size of $\Delta^{\top}$ increases, the size of $\Delta^{\bot}$
-  correspondingly decreases. Nodes labelled $\land$ correspond to
-  multiplication. Therefore,
-  $f(m, n) = \sum_{l = 0}^{n} \binom{n}{l} \diamondsuit \times \heartsuit$,
-  where $\diamondsuit$ is the interpretation of the contradiction (i.e., $\bot$)
-  node, and $\heartsuit$ is the interpretation of the $\Reff$ node.
-
-  A contradiction node with clause $c$ as a parameter is interpreted as one if
-  the clause has groundings and zero otherwise. In this case, the parameter is
-  $c = (\emptyset, \{\, (X, Y) \,\}, \{\, X \mapsto \Delta^\top, Y \mapsto \Delta^\top \,\})$
-  (not shown in \cref{fig:examplefcg}), which can be read as
-  $\forall X, Y \in \Delta^{\top}\text{. }X \ne Y \Rightarrow \bot$, i.e.,
-  $\forall X, Y \in \Delta^{\top}\text{. }X = Y$. This latter sentence is true
-  if and only if $|\Delta^{\top}| < 2$. Therefore, we can use the Iverson
-  bracket notation to write
-  \[
-    \diamondsuit = [l < 2] \coloneqq
-    \begin{cases}
-      1 & \text{if } l < 2 \\
-      0 & \text{otherwise.}
-    \end{cases}
-  \]
-
-  It remains to interpret the $\Reff$ node. Parameter
-  $\{\, \Gamma \mapsto \Gamma', \Delta \mapsto \Delta^\bot \,\}$ tells us that
-  the interpretation of the $\Reff$ node should be the same as that of the
-  source node, but with domains $\Gamma$ and $\Delta$ replaced with $\Gamma'$
-  and $\Delta^{\bot}$, respectively. Domain $\Gamma'$ was created by the CR rule
-  applied on $\Gamma$, so $|\Gamma'| = m - 1$. Now
-  $\Delta^{\bot} = \Delta \setminus \Delta^{\top}$, and $|\Delta^{\top}| = l$,
-  so $|\Delta^{\bot}| = n - l$. Thus, the interpretation of the $\Reff$ node is
-  a recursive call to $f(m - 1, n - l)$. Therefore,
-  \begin{align}
-    f(m, n) &= \sum_{l = 0}^{n} \binom{n}{l} [l < 2] f(m-1, n-l)\nonumber \\
-            &= f(m-1, n) + n f(m-1, n-1).\label{eq:solution}
-  \end{align}
-  To use this recursive function to compute the model count of the input formula
-  for any domain sizes, one just needs to find the base cases $f(0, n)$ and
-  $f(m, 0)$ for all $m, n \in \mathbb{N}_{0}$.
-\end{example}
-
-\section{Experimental Results}\label{sec:results}
-
-\begin{table*}[t]
-  \centering
-  \begin{tabular}{cccccc}
-    \toprule
-    \multicolumn{3}{c}{Function Class} & \multicolumn{3}{c}{Asymptotic Complexity of Counting} \\
-    Partial & Endo- & Class & Best Known & With \textsc{ForcLift} & With \textsc{Crane} \\
-    \midrule
-    \rowcolor{gray!25}\cmark/\xmark & \cmark/\xmark & Functions & $\log m$ & $m$ & $m$ \\
-    \xmark & \xmark & \multirow{4}{*}{Surjections} & $n \log m$ & $m^{3}+n^{3}$ & $m^{3}+n^{3}$ \\
-    \xmark & \cmark & & $m \log m$ & $m^{3}$ & $m^{3}$ \\
-    \cmark & \xmark & & \multicolumn{3}{c}{Same as injections from $\Delta$ to $\Gamma$} \\
-    \cmark & \cmark & & \multicolumn{3}{c}{Same as endo-injections} \\
-    \rowcolor{gray!25}\xmark & \xmark & & $m$ & --- & $mn$ \\
-    \rowcolor{gray!25}\xmark & \cmark & & $m$ & --- & $m^3$ \\
-    \rowcolor{gray!25}\cmark & \xmark & & ${\min\{\, m, n \,\}}^2$ & --- & $mn$ \\
-    \rowcolor{gray!25}\cmark & \cmark & \multirow{-4}{*}{Injections} & $m^2$ & --- & --- \\
-    \xmark & \xmark & \multirow{3}{*}{Bijections} & $m$ & --- & $m$ \\
-    \xmark & \cmark & & \multicolumn{3}{c}{\multirow{2}{*}{Same as (partial) (endo-)injections}} \\
-    \cmark & \cmark/\xmark & & \multicolumn{3}{c}{} \\
-    \bottomrule
-  \end{tabular}
-  \caption{The worst-case complexity of counting various types of functions,
-    where $m$ is the size of domain $\Gamma$, and $n$ is the size of domain
-    $\Delta$. All asymptotic complexities are in $\Theta(\cdot)$. A dash means
-    that the algorithm was not able to find a solution.}\label{tbl:results}
-\end{table*}
-
-We compare \textsc{Crane} and
-\textsc{ForcLift}\footnote{\url{https://dtaid.cs.kuleuven.be/wfomc}}~\cite{DBLP:conf/ijcai/BroeckTMDR11}
-on their ability to count various kinds of functions. This class of instances is
-chosen because of its simplicity and ubiquity and the inability of
-state-of-the-art WFOMC algorithms to solve many such instances. Note that other
-WFOMC algorithms mentioned in \cref{sec:introduction} are unable to solve any of
-the instances that \textsc{ForcLift} fails on. We begin by describing how such
-function-counting problems can be expressed in FOL\@. \textsc{ForcLift} then
-translates these sentences in FOL to formulas as defined in \cref{def:formula}.
-
-Let $\texttt{p}$ be a predicate that models relations between sets $\Gamma$ and
-$\Delta$. To restrict all such relations to just $\Gamma \to \Delta$ functions,
-in FOL one might write
-\[
-  \forall X \in \Gamma\text{. }\forall Y,Z \in \Delta\text{. }\texttt{p}(X, Y) \land \texttt{p}(X, Z) \Rightarrow Y = Z
-\]
-and
-\begin{equation}\label{eq:def2}
-  \forall X \in \Gamma\text{. }\exists Y \in \Delta\text{. }\texttt{p}(X, Y).
-\end{equation}
-The former sentence says that one element of $\Gamma$ can map to at \emph{most}
-one element of $\Delta$, and the latter sentence says that each element of
-$\Gamma$ must map to at \emph{least} one element of $\Delta$. One can then add
-\[
-  \forall X,Z \in \Gamma\text{. }\forall Y \in \Delta\text{. }\texttt{p}(X, Y) \land \texttt{p}(Z, Y) \Rightarrow X = Z
-\]
-to restrict $\texttt{p}$ to injections or
-\[
-  \forall Y \in \Delta\text{. }\exists X \in \Gamma\text{. }\texttt{p}(X, Y)
-\]
-to ensure surjectivity or remove \cref{eq:def2} to consider partial functions.
-Lastly, one can replace all occurrences of $\Delta$ with $\Gamma$ to model
-endofunctions (i.e., functions with the same domain and codomain) instead.
-
-% the process: both for running algorithms and for determining complexities
-In our experiments, we consider all sixteen combinations of these properties,
-i.e., injectivity, surjectivity, partiality, and endo-. We run each algorithm
-once on each of the sixteen instances.\footnote{While domain sizes have to be
-  specified as part of the input, they are immaterial to the search procedure.}
-\textsc{Crane} is run in hybrid search mode until either five solutions are
-found or the search tree reaches height six. \textsc{ForcLift} is always run
-until it terminates. If successful, \textsc{ForcLift} generates a circuit, and
-\textsc{Crane} generates one or more (complete) FCGs. In both cases, we manually
-convert the resulting graphs into definitions of functions as described in
-\cref{sec:interpret}. We then assess the complexity of each solution by hand and
-pick the best in case \textsc{Crane} returns several solutions of varying
-complexities.
-
-% \footnote{The search tree has a high
-%   branching factor, so exploring all nodes at depth five takes at most a few
-%   seconds, whereas doing the same for depth six can be computationally
-%   infeasible in some cases.}
-
-% how the complexity of a solution is determined
-Previous work often compares WFOMC algorithms by running them on a few instances
-with increasing domain sizes and measuring
-runtime~\cite{DBLP:conf/nips/Broeck11,DBLP:conf/ijcai/BroeckTMDR11,DBLP:conf/aaai/BroeckD12}.
-However, we can do much better and identify the exact worst-case asymptotic
-complexity of a solution produced by either \textsc{Crane} or \textsc{ForcLift}.
-The asymptotic complexity of a solution can be determined by considering the
-total number of arithmetic operations needed to follow the definitions of
-constituent functions without recomputing the same quantity multiple times. In
-particular, we assume that each function call and binomial coefficient is
-computed at most once. We also assume that computing $\binom{n}{k}$ takes
-$\Theta(nk)$ time. For example, the complexity of \cref{eq:solution} is
-$\Theta(mn)$ since $f(m, n)$ can be computed by a dynamic programming algorithm
-that computes $f(i, j)$ for all $i = 0, \dots, m$ and $j = 0, \dots, n$, taking
-a constant amount of time on the computation of each $f(i, j)$.
-
-The experimental results are summarised in \cref{tbl:results}, where we compare
-the solutions found by both algorithms to the best known ways of computing the
-same quantities. The best-known asymptotic complexity for computing total
-surjections is by Earnest~\shortcite{30049}. All other best-known complexity
-results are inferred from the formulas and programs on the on-line encyclopedia
-of integer sequences~\cite{oeis}. On instances that could already be solved by
-\textsc{ForcLift}, the two algorithms perform equally well. However,
-\textsc{Crane} can also solve all but one of the instances that
-\textsc{ForcLift} fails on in at most cubic time. See \cref{app:solutions} for
-the exact solutions produced by \textsc{Crane} that correspond to the complexity
-results in \cref{tbl:results}. We also note that standard (W)FOMC benchmarks
-such as \cref{example:smokers} that are already supported by \textsc{ForcLift}
-remain feasible for \textsc{Crane} as well. Moreover, our algorithm can also
-handle the linear order axiom, for which a bespoke algorithm was recently
-proposed by T{\'{o}}th and
-Ku\v{z}elka~\shortcite{DBLP:journals/corr/abs-2211-01164}.
-
-\section{Conclusion and Future Work}\label{sec:conclusion}
-
-In this paper, we showed how a state-of-the-art (W)FOMC algorithm can be
-empowered by generalising domain recursion and adding support for cycles in the
-graph that encodes a solution. To construct such graphs, \textsc{Crane}
-supplements \textsc{ForcLift}~\cite{DBLP:conf/ijcai/BroeckTMDR11} with three
-new compilation rules. Our experiments revealed a range of counting problems
-that are liftable to \textsc{Crane} but not to any other (W)FOMC algorithm.
-Although in this paper we focus on unweighted counting, \textsc{ForcLift}'s
-support for weights trivially transfers to \textsc{Crane} as well. The common
-thread across these newly liftable problems is (partial) injectivity. Thus, we
-can formulate the following conjecture.
-
-\begin{conjecture}
-  Let \IFO{} be the class of formulas in FOL that contain clauses with at most
-  two variables as well as any number of copies of
-  \begin{align*}
-    &\begin{multlined}[t]
-      (\forall X \in \Gamma\text{. }\forall Y, Z \in \Delta\text{. }\\
-      Y \ne Z \Rightarrow \neg \texttt{\textup{p}}(X, Y) \lor \neg \texttt{\textup{p}}(X, Z)) \land
-    \end{multlined}\\
-    &\begin{multlined}[t]
-      (\forall X, Z \in \Gamma\text{. }\forall Y \in \Delta\text{. }\\
-      X \ne Z \Rightarrow \neg \texttt{\textup{p}}(X, Y) \lor \neg \texttt{\textup{p}}(Z, Y))
-    \end{multlined}
-  \end{align*}
-  for some predicate $\texttt{\textup{p}}/2$ and domains $\Gamma$ and $\Delta$.
-  Then \IFO{} is liftable by \textsc{Crane}.
-\end{conjecture}
-
-Recall that \Ctwo{} is the class of formulas with counting quantifiers and at
-most two variables. \Ctwo{} was recently shown to be
-liftable~\cite{DBLP:journals/jair/Kuzelka21} but without providing a usable
-(W)FOMC algorithm. Since the tasks of counting injections and bijections fall
-into the \Ctwo{} fragment, we can conjecture the following.
-
-\begin{conjecture}
-  \Ctwo{} is liftable by \textsc{Crane} by either reformulating formulas in
-  \Ctwo{} to avoid counting quantifiers or extending \textsc{Crane} to support
-  them.
-\end{conjecture}
-
-However, the most important direction for future work is to fully automate this
-new process. First, we need an algorithm that transforms FCGs into definitions
-of functions. Formalising this process would also allow us to prove the
-correctness of the new compilation rules in constructing FCGs that indeed
-compute the right (weighted) model counts. Second, these definitions must be
-simplified before they can be used, perhaps by a computer algebra system. Third,
-we need a way to find the base cases for the recursive definitions provided by
-\textsc{Crane}. Fourth, since the first solution found by \textsc{Crane} is not
-always optimal in terms of its complexity, an automated way to determine the
-asymptotic complexity of a solution would be helpful as well. Achieving these
-goals would enable \textsc{Crane} to automatically constructing efficient ways
-to compute various functions and sequences. In addition to the potential impact
-on areas of artificial intelligence (AI) such as statistical relational
-AI~\cite{DBLP:series/synthesis/2016Raedt}, \textsc{Crane} could be beneficial to
-research in combinatorics as well~\cite{DBLP:conf/ilp/BarvinekB0ZK21}.
-
 \appendix
@@
 In this appendix, we list the exact function definitions produced by
-\textsc{Crane} for all of the problem instances in \cref{sec:results} both
-before and after algebraic simplification (excluding multiplications by one).
-The correctness of all of them has been checked by identifying suitable base
-cases and verifying the numerical answers across a range of domain sizes.
+\textsc{Crane} for all of the problem instances in Section~6 both before and
+after algebraic simplification (excluding multiplications by one). The
+correctness of all of them has been checked by identifying suitable base cases
+and verifying the numerical answers across a range of domain sizes.
 
@@
 
-\bibliographystyle{kr}
-\bibliography{paper}
-
 \end{document}

### 2023-02-16 doc/paper/paper.tex
A slide about applications
Initial draft of the function-building algorithm

@@
 
+\begin{algorithm}[t]
+  \caption{Construct functions from an FCG}
+  \SetKwProg{Fn}{Function}{:}{}
+
+  \SetKwData{domains}{domains}
+  \SetKwData{functionCall}{call}
+  \SetKwData{functionSignature}{signature}
+  \SetKwData{functionNames}{F}
+  \SetKwData{variableNames}{V} % TODO: mathcal? Same for function names?
+  \SetKwData{newVariableNames}{V'}
+  \SetKwData{expression}{e}
+  \SetKwData{functions}{funs}
+
+  \SetKwFunction{newFunctionName}{newFunctionName}
+  \SetKwFunction{newVariableName}{newVarName}
+  \SetKwFunction{visit}{visit}
+  \SetKwFunction{actuallyVisit}{actuallyVisit}
+
+  \KwIn{$\mathcal{D}$---the set of domains of the input formula}
+  \KwIn{$s$---the source of the FCG}
+  \KwData{$\functionNames = \emptyset$}
+  \KwOut{a list of Strings, each defining a function (the top one is the main one)}
+  $\variableNames \gets \{\, d \mapsto \newVariableName{} \mid d \in \mathcal{D} \,\}$\;
+  \uIf{$s$ is a direct successor of a $\Reff$ node}{
+    $(\expression, \functions) \gets \visit{$s$, $\variableNames$}$\;
+    \Return{\functions}\;
+  }
+  \Else{
+    $f \gets \newFunctionName{$s$}$\;
+    $(\expression, \functions) \gets \visit{$s$, $\variableNames$}$\;
+    \Return{$\langle f(\langle \variableNames{$d$} \mid d \in \mathcal{D} \rangle) = \expression \rangle + \functions$}\;
+  }
+  \Fn{\visit{node $v$, \variableNames}}{
+    \If{$v$ is not a direct successor of a $\Reff$ node}{ % TODO: boldface the NOT
+      \Return{\actuallyVisit{$v$, \variableNames}}\;
+    }
+    $f \gets \newFunctionName{$v$}$\;
+    $\newVariableNames \gets \{\, \text{if } d \in v.\domains \text{ and } n \text{ contains subtraction then } d \mapsto \newVariableName{} \text{ else } d \mapsto n \mid d \mapsto n \in \variableNames \,\}$\;
+    $(\expression, \functions) \gets \actuallyVisit{$v$, \newVariableNames}$\;
+    $\functionCall \gets f(\langle \variableNames{$d$} \mid d \in v.\domains \rangle)$\;
+    $\functionSignature \gets f(\langle \newVariableNames{$d$} \mid d \in v.\domains \rangle)$\;
+    \Return{$(\functionCall, \langle \functionSignature = \expression \rangle + \functions)$}\;
+  }
+  \Fn{\actuallyVisit{node $v$, \variableNames}}{
+    \Switch{type of $v$}{
+      \uCase{$\Reff_{\rho}(v')$}{
+        \Return{$(\functionNames{$v'$}(\langle \variableNames{$\rho(d)$} \mid d \in v'.\domains \rangle), \langle \rangle)$}\;
+      }
+      \lCase{$\GDR(v')$}{\Return{\visit{$v'$, \variableNames}}}
+      \uCase{$\CR_{d,d'}(v')$}{\Return{\visit{$v'$, $\variableNames \cup \{\, d' \mapsto (\variableNames(d) - 1) \,\}$}}\;}
+      \dots
+    }
+  }
+\end{algorithm}
+% TODO: introduce symbol for list concatenation (4 places)
+% 'is a direct successor of a Ref node' = the in-degree is > 1
+% TODO: check if the distinction between data and function is appropriate and that all function calls use the right {} syntax
+% TODO: DeclareMathOperator for Or, etc.
+% TODO: check if all semicolons are there
+
+\begin{itemize}
+  \item for each node v, v.domains is a precomputed set of domains that are used
+        by v and all of its successors (except the ones that are introduced by v
+        or its successors) (this was already part of ForcLift, although had to
+        be reimplemented in a way that avoids infinite loops when dealing with
+        cycles in graphs)
+  \item NOTE: for list generators over a set of domains, we assume an arbitrary
+        fixed ordering over all domains
+  \item functionNames is a partial map (initially empty) from the set of nodes
+        of the FCG to Strings
+  \item newVariableName() just generates a unique identifier for a variable
+  \item newFunctionName(node n) does the same thing for function names and also
+        records the new name in functionNames
+\end{itemize}
+
 When \textsc{ForcLift}~\cite{DBLP:conf/ijcai/BroeckTMDR11} compiles a WFOMC

### 2023-02-16 doc/talks/3_long/talk.tex
Improvements to the paper and more slides
A slide about applications
Initial draft of the function-building algorithm

@@
 \usepackage[style=authoryear]{biblatex}
+\usepackage{forest}
+\usepackage{soul}
 
@@
 \usetikzlibrary{calc}
+\usetikzlibrary{backgrounds}
+\usetikzlibrary{fit}
+
+\renewcommand<>{\hl}[1]{\only#2{\beameroriginal{\hl}}{#1}}
+\makeatletter
+\newcommand\SoulColor{%
+  \let\set@color\beamerorig@set@color
+  \let\reset@color\beamerorig@reset@color}
+\makeatother
+\SoulColor
 
@@
 \addbibresource{talk.bib}
-%\usecolortheme{rose}
 
 \definecolor{color1}{HTML}{1B9E77}
-\definecolor{color2}{HTML}{D95F02}
-\definecolor{color3}{HTML}{7570b3}
-\definecolor{color4}{HTML}{e7298a}
+\definecolor{color2}{HTML}{7570b3}
+\definecolor{color3}{HTML}{e7298a}
+
+\colorlet{redish}{color2!25}
+\sethlcolor{redish}
+
+\tikzset{
+  inner/.style={
+    ellipse,
+    draw,
+  },
+  inner on/.style={alt=#1{inner}{}},
+  leaf/.style={
+    rectangle,
+    draw,
+    fill=gray!25,
+  },
+  leaf on/.style={alt=#1{leaf}{}},
+  invisible/.style={opacity=0,text opacity=0},
+  visible on/.style={alt=#1{}{invisible}},
+  alt/.code args={<#1>#2#3}{%
+    \alt<#1>{\pgfkeysalso{#2}}{\pgfkeysalso{#3}} % \pgfkeysalso doesn't change the path
+  },
+}
+
+\forestset{
+sn edges/.style={for tree={edge={-Latex}}},
+  visible on/.style={
+    for tree={
+      /tikz/visible on={#1},
+      edge+={/tikz/visible on={#1}}}}
+}
 
@@
 \newcommand{\y}{\textcolor{color3}{y}}
-\newcommand{\pP}{\textcolor{color3}{P}}
+\newcommand{\pP}{\texttt{P}}
+\newcommand{\qQ}{\texttt{Q}}
 \newcommand{\dDelta}{\textcolor{color2}{\Delta}}
@@
 \newcommand{\WMC}{\textup{WMC}}
-\newcommand{\WFOMC}{\textup{(W)FOMC}}
 \newcommand{\WMI}{\textup{WMI}}
@@
 
-% 15 min introduction
-% 20-25 min presentation
-% 5-10 min summary
+% 15 min (8 slides of content) introduction
+% 25 min presentation
+% 5 min summary
 % 20-25 slides
@@
 % make sure there's a clear and coherent storyline
-% TODO: use \alert instead of \structure
-% TODO: add a very clear example of what a model is
-% TODO: could add the step-by-step walkthrough of what FOKC looks like
 
@@
 
+\begin{frame}{Who Cares About Counting?}
+  \begin{columns}
+    \begin{column}{0.5\textwidth}
+      \pause
+      \begin{block}{\alert{Probabilistic Programming}}
+        \centering
+        \includegraphics[width=\textwidth]{programming.png}
+      \end{block}
+      \pause
+      \begin{block}{\alert{Neuro-symbolic AI}}
+        \centering
+        \includegraphics[width=\textwidth]{neurosymbolic.png}
+      \end{block}
+      \pause
+      \begin{block}{\alert{Natural Language Processing}}
+        \centering
+        \includegraphics[width=\textwidth]{knowledge.png}
+      \end{block}
+      \pause
+    \end{column}
+    \begin{column}{0.5\textwidth}
+      \begin{block}{\alert{Robotics}}
+        \centering
+        \includegraphics[width=\textwidth]{ICRA.png}
+      \end{block}
+      \pause
+      \begin{block}{\alert{Bioinformatics}}
+        \centering
+        \includegraphics[width=\textwidth]{bio.png}
+      \end{block}
+      \pause
+      \begin{block}{\alert{Combinatorics}}
+        \centering
+        \includegraphics[width=\textwidth]{recurrence.png}
+      \end{block}
+    \end{column}
+  \end{columns}
+\end{frame}
+
 \begin{frame}[fragile]{(Some of the) Many Ways to Count}
@@
       |[alias=WMI,visible on=<7->]|\WMI{} & |[visible on=<7->]|\WFOMI{} \\
-      |[alias=WMC]|\#\SAT{}/\WMC{} \arrow[u,visible on=<7->] \ar[d,visible on=<8->] \ar[r,visible on=<5->] & |[visible on=<5->]|\WFOMC{} \arrow[u,visible on=<7->] \ar[d,visible on=<8->] \\
+      |[alias=WMC]|\#\SAT{}/\WMC{} \arrow[u,visible on=<7->] \ar[d,visible on=<8->] \ar[r,visible on=<5->] & |[visible on=<5->]|\textup{(W)\alert<9>{FOMC}} \arrow[u,visible on=<7->] \ar[d,visible on=<8->] \\
       |[alias=PBP,visible on=<8->]|\AMC{}, \pbp{} & |[alias=SP,visible on=<8->]|\SPPP{}
@@
 \end{frame}
-% maybe mention #CSP and other non-SAT ways of counting (SMT?, counting paths in automata and directed graphs)
+% maybe mention #CSP and other non-SAT ways of counting (SMT?, counting paths in
+% automata and directed graphs)
 
-% TODO: for future work, come back to this slide and add more arrows (e.g., beyond FOL)
-
-% TODO: a big chunk of the introduction should provide motivation to my work (e.g., mention applications) (maybe before this slide?)
-
-\begin{frame}{Some Elementary Counting}
-  \begin{exampleblock}{A Counting Problem}
-    Suppose this room has \alert{$n$} seats, and there are \alert{$m \le n$}
-    people in the audience. How many ways are there to seat everyone?
-  \end{exampleblock}
-
-  \pause
-  More explicitly, we assume that:
-  \begin{itemize}
-  \item each attendee gets exactly one seat,
-  \item and a seat can accommodate at most one person.
-  \end{itemize}
-
-  \pause
-  \alert{Answer:} $n^{\underline{m}} = n \cdot (n-1)\cdots(n-m+1)$.
-
-  Note: this problem is equivalent to counting \alert{$[m] \to [n]$} injections.
-
-\end{frame}
-% wouldn't it be nice if we could just describe this problem and have an algorithm solve it for us?
-
-\begin{frame}{Let's Express This Problem in Logic!}
-  \begin{itemize}
-    \item Let \alert{$\Gamma$} and \alert{$\Delta$} be sets (i.e., domains)
-    \begin{itemize}
-      \item such that \alert{$|\Gamma| = m$}, and \alert{$|\Delta| = n$}.
-    \end{itemize}
-    \item Let \alert{$P \subseteq \Gamma \times \Delta$} be a relation (i.e.,
-          predicate) over \alert{$\Gamma$} and \alert{$\Delta$}.
-    \item We can describe all of the constraints in first-order logic:
-    \begin{itemize}
-      \item \pause each attendee gets a seat (i.e., at least one seat)
-      \[
-        \forall x \in \Gamma\text{. }\exists y \in \Delta\text{. }P(x, y)
-      \]
-      \item \pause one person cannot occupy multiple seats
-      \[
-        \forall x \in \Gamma\text{. }\forall y, z \in \Delta\text{. }P(x, y) \land P(x, z) \Rightarrow y=z
-      \]
-      \item \pause one seat cannot accommodate multiple attendees
-      \[
-        \forall w, x \in \Gamma\text{. }\forall y \in \Delta\text{. }P(w, y) \land P(x, y) \Rightarrow w=x
-      \]
-    \end{itemize}
-  \end{itemize}
-  \pause The first two sentences constrain \alert{$P$} to be a function, and the
-  last one makes it injective.
-\end{frame}
-% one could also add probabilities to these sentences to say that, e.g., there is a 1% probability of somebody taking up two seats, somebody sitting on somebody else's lap, somebody sitting on the floor, etc.
-
-\begin{frame}{Overview of the Problem}
+% TODO: add a very clear example of what a model is
+% TODO: (maybe) add a slide about other approaches to WFOMC, making it crystal clear what my contributions are
+\begin{frame}{First-Order Model Counting (in More Detail)}
   \begin{itemize}
@@
 \end{frame}
+
+\begin{frame}{First-Order Knowledge Compilation: An Approach to FOMC}
+  \centering
+  \begin{forest}
+    for tree={s sep=10mm, sn edges}
+    [\alt<2->{$\bigwedge_{c \in \Delta}$}{$\forall x \in \Delta\text{. } \pP(x) \lor \qQ(x)$},inner on=<2->,label={[visible on=<{8-9,14-}>]right:{\alert{\alt<10->{$3^{n}$}{$\{\,\pP(c), \qQ(c)\,\}$}}}}
+    [\alt<3->{$\lor$}{$\pP(c) \lor \qQ(c)$},for tree={visible on=<2->},inner on=<3->,label={[visible on=<{7-9,13-}>]right:{\alert{\alt<10->{$2 + 1 = 3$}{$\{\,\pP(c), \qQ(c)\,\}$}}}}
+    [\alt<4->{$\land$}{$\begin{aligned}\qQ(c)\\ \pP(c) \lor \qQ(c)\end{aligned}$},name=and,for tree={visible on=<3->},inner on=<4->,label={[name=foobar,visible on=<{6-9,12-}>]left:{\alert<-8,12->{\alt<10->{$2 \times 1 = 2$}{$\{\,\qQ(c)\,\}$}}}}
+    [\alt<10->{$\pP(c) \lor \neg \pP(c)$}{$\qQ(c)$},name=smoothing,for tree={visible on=<4->},rectangle,draw,fill=gray!25,label={[visible on=<11->]below:{\alert{2}}}]
+    [\alt<10->{$\land$}{$\top$},for tree={visible on=<4->},leaf on=<4-9>,inner on=<10->,label={[label distance=0cm,visible on=<12->]87:{\alert{$1 \times 1 = 1$}}}
+    [$\qQ(c)$,for tree={visible on=<10->},rectangle,draw,fill=gray!25,label={[visible on=<11->]below:{\alert{1}}}]
+    [$\top$,for tree={visible on=<10->},rectangle,draw,fill=gray!25,label={[visible on=<11->]below:{\alert{1}}}]
+    ]
+    ]
+    [\alt<5->{$\land$}{$\begin{aligned}\neg\qQ(c)\\ \pP(c) \lor \qQ(c)\end{aligned}$},for tree={visible on=<3->},inner on=<5->,label={[visible on=<{6-9,12-}>]right:{\alert{\alt<10->{$1 \times 1 = 1$}{$\{\,\pP(c), \qQ(c)\,\}$}}}}
+    [$\neg \qQ(c)$,for tree={visible on=<5->},rectangle,draw,fill=gray!25,label={[visible on=<11->]below:{\alert{1}}}]
+    [$\pP(c)$,for tree={visible on=<5->},rectangle,draw,fill=gray!25,label={[visible on=<11->]below:{\alert{1}}}]
+    ]
+    ]
+    ]
+    \begin{scope}[on background layer]
+      \uncover<9>{\node [fill=redish, ellipse, fit=(foobar)] {};}
+      \uncover<10>{\node [fill=redish, ellipse, fit={(smoothing) (and)}, inner sep=0.5pt] {};}
+    \end{scope}
+  \end{forest}
+\end{frame}
+% TODO: add compilation rule names at the bottom
+% TODO: add arrows explaining unit clauses and tautology
+% TODO: maybe use \alert instead of blue?
+% TODO: change both highlight colors (a light shade of red?)
+% TODO: maybe visualise P and Q as subsets of Delta?
+
+\begin{frame}{An Example Counting Problem}
+  Suppose this room has \alert{$n$} seats, and there are \alert{$m \le n$}
+  people in the audience. How many ways are there to seat everyone?
+  \vfill
+
+  \pause
+  More explicitly, we assume that:
+  \begin{itemize}
+  \item each attendee gets exactly one seat,
+  \item and a seat can accommodate at most one person.
+  \end{itemize}
+  \vfill
+
+  \pause
+  \alert{Answer:} $n^{\underline{m}} = n \cdot (n-1)\cdots(n-m+1)$.
+
+  Note: this problem is equivalent to counting \alert{$[m] \to [n]$} injections.
+
+\end{frame}
+% wouldn't it be nice if we could just describe this problem and have an algorithm solve it for us?
+
+\begin{frame}{Let's Express This Problem in Logic!}
+  \begin{itemize}
+    \item Let \alert{$\Gamma$} and \alert{$\Delta$} be sets (i.e., domains)
+    \begin{itemize}
+      \item such that \alert{$|\Gamma| = m$}, and \alert{$|\Delta| = n$}.
+    \end{itemize}
+    \item Let $\pP \subseteq \Gamma \times \Delta$ be a relation (i.e.,
+          predicate) over \alert{$\Gamma$} and \alert{$\Delta$}.
+    \item We can describe all of the constraints in first-order logic:
+    \begin{itemize}
+      \item \pause each attendee gets a seat (i.e., at least one seat)
+      \begin{equation}\label{eq:a1}
+        \forall x \in \Gamma\text{. }\exists y \in \Delta\text{. }\pP(x, y)
+      \end{equation}
+      \item \pause one person cannot occupy multiple seats
+      \begin{equation}\label{eq:a2}
+        \forall x \in \Gamma\text{. }\forall y, z \in \Delta\text{. }\pP(x, y) \land \pP(x, z) \Rightarrow y=z
+      \end{equation}
+      \item \pause one seat cannot accommodate multiple attendees
+      \begin{equation}\label{eq:a3}
+        \forall w, x \in \Gamma\text{. }\forall y \in \Delta\text{. }\pP(w, y) \land \pP(x, y) \Rightarrow w=x
+      \end{equation}
+    \end{itemize}
+  \end{itemize}
+  \pause \eqref{eq:a1} and \eqref{eq:a2} constrain $\pP$ to be a function, and
+  \eqref{eq:a3} makes it injective.
+\end{frame}
+% one could also add probabilities to these sentences to say that, e.g., there is a 1% probability of somebody taking up two seats, somebody sitting on somebody else's lap, somebody sitting on the floor, etc.
 
@@
   \begin{itemize}
-    \item \structure{$f$} can be computed in \structure{$\Theta(mn)$} time (via
-          dynamic programming).
-    \item Optimal time complexity to compute \structure{$n^{\underline{m}}$} is
-          \structure{$\Theta(m)$}.
-    \item But \structure{$\Theta(mn)$} is still much better than translating to
+    \item \alert{$f$} can be computed in \alert{$\Theta(mn)$} time (via dynamic
+          programming).
+    \item Optimal time complexity to compute \alert{$n^{\underline{m}}$} is
+          \alert{$\Theta(m)$}.
+    \item But \alert{$\Theta(mn)$} is still much better than translating to
           propositional logic and running a WMC algorithm.
@@
   \begin{definition}
-    A \alert{first-order deterministic decomposable negation normal form computational graph} (FCG) is a
+    A \emph{first-order deterministic decomposable negation normal form computational graph} (FCG) is a
     \begin{itemize}
@@
   \begin{definition}
-    A \alert{(compilation) rule} is a function that takes a \alert{formula} and returns a set of \structure{$(G, L)$} pairs, where
+    A \alert{(compilation) rule} is a function that takes a \alert{formula} and returns a set of \alert{$(G, L)$} pairs, where
     \begin{itemize}
-    \item \structure{$G$} is an FCG,
-    \item and \structure{$L$} is a list of formulas.
+    \item \alert{$G$} is an FCG,
+    \item and \alert{$L$} is a list of formulas.
     \end{itemize}
@@
     ({\color{color1} \forall x, y \in \Omega\text{. }x=y}) \land \label{eq:1} \tag{{\color{color1} 1}} \\
-    ({\color{color2} \forall x \in \Gamma\text{. }\forall y, z \in \Delta\text{. }P(x, y) \land P(x, z) \Rightarrow y=z}) \land \label{eq:2} \tag{{\color{color2} 2}} \\
-    ({\color{color2} \forall w, x \in \Gamma\text{. }\forall y \in \Delta\text{. }P(w, y) \land P(x, y) \Rightarrow w=x}) \label{eq:3} \tag{{\color{color2} 3}}
+    ({\color{color2} \forall x \in \Gamma\text{. }\forall y, z \in \Delta\text{. }\texttt{P}(x, y) \land \texttt{P}(x, z) \Rightarrow y=z}) \land \label{eq:2} \tag{{\color{color2} 2}} \\
+    ({\color{color2} \forall w, x \in \Gamma\text{. }\forall y \in \Delta\text{. }\texttt{P}(w, y) \land \texttt{P}(x, y) \Rightarrow w=x}) \label{eq:3} \tag{{\color{color2} 3}}
   \end{gather}
   \pause
-  Only one \structure{(G, L)} pair:
+  Only one \alert{(G, L)} pair:
   \[
@@
   \]
-  %% Later, both \structure{$G$} and \structure{$L$} are incorporated into a larger \alert{search state}.
 \end{frame}
@@
             \[
-              \forall x \in \Gamma\text{. }\forall y, z \in \Delta\text{. }y \ne z \Rightarrow \neg P(x, y) \lor \neg P(x, z)
+              \forall x \in \Gamma\text{. }\forall y, z \in \Delta\text{. }y \ne z \Rightarrow \neg \texttt{P}(x, y) \lor \neg \texttt{P}(x, z)
             \]
-            Output formula (with a new constant \structure{$c \in \Gamma$}):
+            Output formula (with a new constant \alert{$c \in \Gamma$}):
             \begin{gather*}
-              \forall y, z \in \Delta\text{. }y \ne z \Rightarrow \neg P(\alert{c}, y) \lor \neg P(\alert{c}, z) \\
+              \forall y, z \in \Delta\text{. }y \ne z \Rightarrow \neg \texttt{P}(\alert{c}, y) \lor \neg \texttt{P}(\alert{c}, z) \\
               \begin{multlined}
                 \forall x \in \Gamma\text{. }\forall y, z \in \Delta\text{. }\alert{x \ne c} \land y \ne z \Rightarrow \\
-                \neg P(x, y) \lor \neg P(x, z)
+                \neg \texttt{P}(x, y) \lor \neg \texttt{P}(x, z)
               \end{multlined}
@@
           \begin{example}
-            Input formula (with a constant \structure{$c \in \Gamma$}):
+            Input formula (with a constant \alert{$c \in \Gamma$}):
             \begin{gather*}
@@
                 \forall x \in \alert{\Gamma}\text{. }\forall y, z \in \Delta\text{. }\alert{x \ne c} \land y \ne z \Rightarrow \\
-                \neg P(x, y) \lor \neg P(x, z)
+                \neg \texttt{P}(x, y) \lor \neg \texttt{P}(x, z)
               \end{multlined} \\
@@
                 \forall w,x \in \alert{\Gamma}\text{. }\forall y \in \Delta\text{. }\alert{w \ne c} \land \alert{x \ne c} \land w \ne x \Rightarrow \\
-                \neg P(w, y) \lor \neg P(x, y)
+                \neg \texttt{P}(w, y) \lor \neg \texttt{P}(x, y)
               \end{multlined}
             \end{gather*}
-            Output formula (with a new domain \structure{$\Gamma' \coloneqq \Gamma \setminus \{\, c \,\}$}):
+            Output formula (with a new domain \alert{$\Gamma' \coloneqq \Gamma \setminus \{\, c \,\}$}):
             \begin{gather*}
-              \forall x \in \alert{\Gamma'}\text{. }\forall y, z \in \Delta\text{. }y \ne z \Rightarrow \neg P(x, y) \lor \neg P(x, z) \\
-              \forall w,x \in \alert{\Gamma'}\text{. }\forall y \in \Delta\text{. }w \ne x \Rightarrow \neg P(w, y) \lor \neg P(x, y)
+              \forall x \in \alert{\Gamma'}\text{. }\forall y, z \in \Delta\text{. }y \ne z \Rightarrow \neg \texttt{P}(x, y) \lor \neg \texttt{P}(x, z) \\
+              \forall w,x \in \alert{\Gamma'}\text{. }\forall y \in \Delta\text{. }w \ne x \Rightarrow \neg \texttt{P}(w, y) \lor \neg \texttt{P}(x, y)
             \end{gather*}
@@
 \begin{frame}{Resulting Improvements to Counting Functions}
-  Let \structure{$\Gamma$} and \structure{$\Delta$} be two sets with
-  cardinalities \structure{$|\Gamma| = m$} and \structure{$|\Delta| = n$}.
+  Let \alert{$\Gamma$} and \alert{$\Delta$} be two sets with
+  cardinalities \alert{$|\Gamma| = m$} and \alert{$|\Delta| = n$}.
 
   Our new rules enable \textsc{ForcLift} to efficiently count
-  \structure{$\Gamma \to \Delta$} functions such as:
+  \alert{$\Gamma \to \Delta$} functions such as:
   \begin{itemize}
-    \item injections in \structure{$\Theta(mn)$} time
+    \item injections in \alert{$\Theta(mn)$} time
           \begin{itemize}
-            \item best: \structure{$\Theta(m)$}
+            \item best: \alert{$\Theta(m)$}
           \end{itemize}
-    \item partial injections in \structure{$\Theta(mn)$} time
+    \item partial injections in \alert{$\Theta(mn)$} time
           \begin{itemize}
-            \item best: \structure{$\Theta({\min\{\, m, n \,\}}^2)$}
+            \item best: \alert{$\Theta({\min\{\, m, n \,\}}^2)$}
           \end{itemize}
-          \item bijections in \structure{$\Theta(m)$} time
+          \item bijections in \alert{$\Theta(m)$} time
           \begin{itemize}
@@
 \end{frame}
-% TODO: mention Crane
+% TODO: mention Crane, don't forget to introduce forclift
 % TODO: mention that everything used to be unliftable (by any algorithm with a publicly available implementation)
+% TODO: what font do I want to use for forclift/crane? It's mentioned on a slide title as well
 
@@
 \end{frame}
+% TODO: for future work, come back to the 'many ways to count' slide and add more arrows (e.g., beyond FOL)
 

### 2023-02-16 doc/paper/paper.tex
Clean-up

--- 2023-02-14 doc/paper/paper.tex
@@
 \newcommand{\IFO}{$\mathsf{I}\mathsf{FO}^{2}$}
+\newcommand\mdoubleplus{\mathbin{+\mkern-10mu+}}
 
@@
 $\langle x \rangle$ for a list with one element $x$, $|l|$ for the length of
-list $l$, and $\pfun$ to denote partial functions. Let $S$ be a set of
-constraints or literals, $V$ a set of variables, and $x$ a variable or a
-constant. We write $S[x/V]$ to denote $S$ with all occurrences of all variables
-in $V$ replaced with $x$. Let $\Doms$ (respectively, $\Preds$) be the function
-that maps any clause or formula to the set of domains (respectively, predicates)
-used within, and let $\dom(f)$ denote the domain of function $f$.
+list $l$, $\mdoubleplus$ for list concatenation, and $\pfun$ to denote partial
+functions. Let $S$ be a set of constraints or literals, $V$ a set of variables,
+and $x$ a variable or a constant. We write $S[x/V]$ to denote $S$ with all
+occurrences of all variables in $V$ replaced with $x$. Let $\Doms$
+(respectively, $\Preds$) be the function that maps any clause or formula to the
+set of domains (respectively, predicates) used within, and let $\dom(f)$ denote
+the domain of function $f$.
 
@@
     for tree={sn edges}
-    [$\GDR_{\Gamma \gets \Gamma \setminus \{\, x \,\}}$,ellipse,draw,name=gdr
+    [$\GDR$,ellipse,draw,name=gdr
     [$\bigvee_{\Delta^\top \subseteq \Delta}$,ellipse,draw
@@
 and $\star$'s as all of its direct successors. See \cref{fig:examplefcg} for an
-example FCG\@. Its source node has out-degree 1, label
-$\GDR_{\Gamma \gets \Gamma \setminus \{\, x \,\}}$, and type $\GDR$.
+example FCG\@. Its source node has out-degree 1, label $\GDR$, and type $\GDR$.
+% TODO: update the last sentence
 
@@
     }
-    $S \gets S \cup \{\, (\GDR_{\Omega \gets \Omega \setminus \{\, x \,\}}, \langle\phi'\rangle) \,\}$\;
+    $S \gets S \cup \{\, (\GDR, \langle\phi'\rangle) \,\}$\;
   }
@@
 
+\begin{algorithm}[t]
+  \caption{Construct functions from an FCG}
+  \SetKwProg{Fn}{Function}{:}{}
+
+  \SetKwData{functionCall}{call}
+  \SetKwData{functionSignature}{signature}
+  \SetKwData{functionNames}{F}
+  \SetKwData{variableNames}{V}
+  \SetKwData{newVariableNames}{V'}
+  \SetKwData{expression}{e}
+  \SetKwData{functions}{funs}
+  \SetKwData{args}{args}
+
+  \SetKwFunction{newFunctionName}{newFunctionName}
+  \SetKwFunction{newVariableName}{newVarName}
+  \SetKwFunction{visit}{v}
+  \SetKwFunction{actuallyVisit}{visit}
+
+  \KwIn{$\mathcal{D}$---the set of domains of the input formula}
+  \KwIn{$s$---the source node of the FCG}
+  \KwData{$\functionNames = \emptyset$ (function names)}
+  \KwOut{a list of function definitions}
+  $\variableNames \gets \{\, \Omega \mapsto \newVariableName{} \mid \Omega \in \mathcal{D} \,\}$\;
+  \If{$s$ is a direct successor of a $\Reff$ node}{
+    $(\expression, \functions) \gets \visit{$s$, $\variableNames$}$\;
+    \Return{\functions}\;
+  }
+  $f \gets \newFunctionName{$s$}$\;
+  $(\expression, \functions) \gets \visit{$s$, $\variableNames$}$\;
+  \Return{$\langle f(\langle \variableNames{$\Omega$} \mid \Omega \in \mathcal{D} \rangle) = \expression \rangle \mdoubleplus \functions$}\;
+  \Fn{\visit{node $v$, variable names \variableNames}}{
+    \If{$v$ is \textbf{not} a direct successor of a $\Reff$ node}{
+      \Return{\actuallyVisit{$v$, \variableNames}}\;
+    }
+    $f \gets \newFunctionName{$v$}$\;
+    $\newVariableNames \gets \variableNames$\;
+    \For{$\Omega \in \mathfrak{D}(v)$ s.t. $\newVariableNames(\Omega)$ is non-atomic}{
+      $\newVariableNames(\Omega) \gets \newVariableName{}$\;
+    }
+    $(\expression, \functions) \gets \actuallyVisit{$v$, \newVariableNames}$\;
+    $\functionCall \gets f(\langle \variableNames{$\Omega$} \mid \Omega \in \mathfrak{D}(v) \rangle)$\;
+    $\functionSignature \gets f(\langle \newVariableNames{$\Omega$} \mid \Omega \in \mathfrak{D}(v) \rangle)$\;
+    \Return{$(\functionCall, \langle \functionSignature = \expression \rangle \mdoubleplus \functions)$}\;
+  }
+  \Fn{\actuallyVisit{node $v$, variable names \variableNames}}{
+    \Switch{label of $v$}{
+      \lCase{$\GDR(v')$}{\Return{\visit{$v'$, \variableNames}}}
+      \uCase{$\CR_{\Omega \mapsto \Omega'}(v')$}{
+        \Return{\visit{$v'$, $\variableNames \cup \{\, \Omega' \mapsto (\variableNames(\Omega) - 1) \,\}$}}\;
+      }
+      \uCase{$\Reff_{\rho}(v')$}{
+        $\args \gets \langle \variableNames{$\rho(\Omega)$} \mid \Omega \in \mathfrak{D}(v') \rangle$\;
+        \Return{$(\functionNames{$v'$}(\args), \langle \rangle)$}\;
+      }
+      \dots
+    }
+  }
+\end{algorithm}
+% TODO: have I introduced the GDR(v') syntax? (for other types as well)
+
+\begin{itemize}
+  \item TODO: define atomic --- no subtraction, i.e., just a variable name
+  \item for each FCG node $v$, $\mathfrak{D}(v)$ is a precomputed set of domains
+        that are used by $v$ and all of its successors (except the ones that are
+        introduced by $v$ or one of its successors) (this was already part of
+        \textsc{ForcLift}, although had to be reimplemented in a way that avoids
+        infinite loops when dealing with cycles in graphs)
+  \item for list generators over a set of domains, we assume an arbitrary fixed
+        ordering over all domains
+  \item $\mathsf{F}$ is a partial map from the set of FCG nodes to Strings,
+        i.e., function names
+  \item \newVariableName just generates a unique identifier for a variable
+  \item \newFunctionName does the same thing for function names and also records
+        the new name in $\mathsf{F}$
+  \item the top function is the main one
+  \item `is a direct successor of a $\Reff$ node' --- the in-degree is greater
+        than 1
+\end{itemize}
+
 When \textsc{ForcLift}~\cite{DBLP:conf/ijcai/BroeckTMDR11} compiles a WFOMC
@@
 \section{Experimental Results}\label{sec:results}
-
-We compare \textsc{Crane} and
-\textsc{ForcLift}\footnote{\url{https://dtaid.cs.kuleuven.be/wfomc}}~\cite{DBLP:conf/ijcai/BroeckTMDR11}
-on their ability to count various kinds of functions. This class of instances is
-chosen because of its simplicity and ubiquity and the inability of
-state-of-the-art WFOMC algorithms to solve many such instances. Note that other
-WFOMC algorithms mentioned in \cref{sec:introduction} are unable to solve any of
-the instances that \textsc{ForcLift} fails on. We begin by describing how such
-function-counting problems can be expressed in FOL\@. \textsc{ForcLift} then
-translates these sentences in FOL to formulas as defined in \cref{def:formula}.
-
-Let $\texttt{p}$ be a predicate that models relations between sets $\Gamma$ and
-$\Delta$. To restrict all such relations to just $\Gamma \to \Delta$ functions,
-in FOL one might write
-\[
-  \forall X \in \Gamma\text{. }\forall Y,Z \in \Delta\text{. }\texttt{p}(X, Y) \land \texttt{p}(X, Z) \Rightarrow Y = Z
-\]
-and
-\begin{equation}\label{eq:def2}
-  \forall X \in \Gamma\text{. }\exists Y \in \Delta\text{. }\texttt{p}(X, Y).
-\end{equation}
-The former sentence says that one element of $\Gamma$ can map to at \emph{most}
-one element of $\Delta$, and the latter sentence says that each element of
-$\Gamma$ must map to at \emph{least} one element of $\Delta$. One can then add
-\[
-  \forall X,Z \in \Gamma\text{. }\forall Y \in \Delta\text{. }\texttt{p}(X, Y) \land \texttt{p}(Z, Y) \Rightarrow X = Z
-\]
-to restrict $\texttt{p}$ to injections or
-\[
-  \forall Y \in \Delta\text{. }\exists X \in \Gamma\text{. }\texttt{p}(X, Y)
-\]
-to ensure surjectivity or remove \cref{eq:def2} to consider partial functions.
-Lastly, one can replace all occurrences of $\Delta$ with $\Gamma$ to model
-endofunctions (i.e., functions with the same domain and codomain) instead.
-
-% the process: both for running algorithms and for determining complexities
-In our experiments, we consider all sixteen combinations of these properties,
-i.e., injectivity, surjectivity, partiality, and endo-. We run each algorithm
-once on each of the sixteen instances.\footnote{While domain sizes have to be
-  specified as part of the input, they are immaterial to the search procedure.}
-\textsc{Crane} is run in hybrid search mode until either five solutions are
-found or the search tree reaches height six. \textsc{ForcLift} is always run
-until it terminates. If successful, \textsc{ForcLift} generates a circuit, and
-\textsc{Crane} generates one or more (complete) FCGs. In both cases, we manually
-convert the resulting graphs into definitions of functions as described in
-\cref{sec:interpret}. We then assess the complexity of each solution by hand and
-pick the best in case \textsc{Crane} returns several solutions of varying
-complexities.
-
-% \footnote{The search tree has a high
-%   branching factor, so exploring all nodes at depth five takes at most a few
-%   seconds, whereas doing the same for depth six can be computationally
-%   infeasible in some cases.}
-
-% how the complexity of a solution is determined
-Previous work often compares WFOMC algorithms by running them on a few instances
-with increasing domain sizes and measuring
-runtime~\cite{DBLP:conf/nips/Broeck11,DBLP:conf/ijcai/BroeckTMDR11,DBLP:conf/aaai/BroeckD12}.
-However, we can do much better and identify the exact worst-case asymptotic
-complexity of a solution produced by either \textsc{Crane} or \textsc{ForcLift}.
-The asymptotic complexity of a solution can be determined by considering the
-total number of arithmetic operations needed to follow the definitions of
-constituent functions without recomputing the same quantity multiple times. In
-particular, we assume that each function call and binomial coefficient is
-computed at most once. We also assume that computing $\binom{n}{k}$ takes
-$\Theta(nk)$ time. For example, the complexity of \cref{eq:solution} is
-$\Theta(mn)$ since $f(m, n)$ can be computed by a dynamic programming algorithm
-that computes $f(i, j)$ for all $i = 0, \dots, m$ and $j = 0, \dots, n$, taking
-a constant amount of time on the computation of each $f(i, j)$.
 
@@
 
+We compare \textsc{Crane} and
+\textsc{ForcLift}\footnote{\url{https://dtaid.cs.kuleuven.be/wfomc}}~\cite{DBLP:conf/ijcai/BroeckTMDR11}
+on their ability to count various kinds of functions. This class of instances is
+chosen because of its simplicity and ubiquity and the inability of
+state-of-the-art WFOMC algorithms to solve many such instances. Note that other
+WFOMC algorithms mentioned in \cref{sec:introduction} are unable to solve any of
+the instances that \textsc{ForcLift} fails on. We begin by describing how such
+function-counting problems can be expressed in FOL\@. \textsc{ForcLift} then
+translates these sentences in FOL to formulas as defined in \cref{def:formula}.
+
+Let $\texttt{p}$ be a predicate that models relations between sets $\Gamma$ and
+$\Delta$. To restrict all such relations to just $\Gamma \to \Delta$ functions,
+in FOL one might write
+\[
+  \forall X \in \Gamma\text{. }\forall Y,Z \in \Delta\text{. }\texttt{p}(X, Y) \land \texttt{p}(X, Z) \Rightarrow Y = Z
+\]
+and
+\begin{equation}\label{eq:def2}
+  \forall X \in \Gamma\text{. }\exists Y \in \Delta\text{. }\texttt{p}(X, Y).
+\end{equation}
+The former sentence says that one element of $\Gamma$ can map to at \emph{most}
+one element of $\Delta$, and the latter sentence says that each element of
+$\Gamma$ must map to at \emph{least} one element of $\Delta$. One can then add
+\[
+  \forall X,Z \in \Gamma\text{. }\forall Y \in \Delta\text{. }\texttt{p}(X, Y) \land \texttt{p}(Z, Y) \Rightarrow X = Z
+\]
+to restrict $\texttt{p}$ to injections or
+\[
+  \forall Y \in \Delta\text{. }\exists X \in \Gamma\text{. }\texttt{p}(X, Y)
+\]
+to ensure surjectivity or remove \cref{eq:def2} to consider partial functions.
+Lastly, one can replace all occurrences of $\Delta$ with $\Gamma$ to model
+endofunctions (i.e., functions with the same domain and codomain) instead.
+
+% the process: both for running algorithms and for determining complexities
+In our experiments, we consider all sixteen combinations of these properties,
+i.e., injectivity, surjectivity, partiality, and endo-. We run each algorithm
+once on each of the sixteen instances.\footnote{While domain sizes have to be
+  specified as part of the input, they are immaterial to the search procedure.}
+\textsc{Crane} is run in hybrid search mode until either five solutions are
+found or the search tree reaches height six. \textsc{ForcLift} is always run
+until it terminates. If successful, \textsc{ForcLift} generates a circuit, and
+\textsc{Crane} generates one or more (complete) FCGs. In both cases, we manually
+convert the resulting graphs into definitions of functions as described in
+\cref{sec:interpret}. We then assess the complexity of each solution by hand and
+pick the best in case \textsc{Crane} returns several solutions of varying
+complexities.
+
+% \footnote{The search tree has a high
+%   branching factor, so exploring all nodes at depth five takes at most a few
+%   seconds, whereas doing the same for depth six can be computationally
+%   infeasible in some cases.}
+
+% how the complexity of a solution is determined
+Previous work often compares WFOMC algorithms by running them on a few instances
+with increasing domain sizes and measuring
+runtime~\cite{DBLP:conf/nips/Broeck11,DBLP:conf/ijcai/BroeckTMDR11,DBLP:conf/aaai/BroeckD12}.
+However, we can do much better and identify the exact worst-case asymptotic
+complexity of a solution produced by either \textsc{Crane} or \textsc{ForcLift}.
+The asymptotic complexity of a solution can be determined by considering the
+total number of arithmetic operations needed to follow the definitions of
+constituent functions without recomputing the same quantity multiple times. In
+particular, we assume that each function call and binomial coefficient is
+computed at most once. We also assume that computing $\binom{n}{k}$ takes
+$\Theta(nk)$ time. For example, the complexity of \cref{eq:solution} is
+$\Theta(mn)$ since $f(m, n)$ can be computed by a dynamic programming algorithm
+that computes $f(i, j)$ for all $i = 0, \dots, m$ and $j = 0, \dots, n$, taking
+a constant amount of time on the computation of each $f(i, j)$.
+
 The experimental results are summarised in \cref{tbl:results}, where we compare

### 2023-02-21 doc/paper/paper.tex
One more slide

@@
 % make sure the result table (as well as other floating objects) are on the right pages
+
+% TODO: I found the choice for what goes into a footnote and what doesn't rather
+% inconsistent, which made it a bit irritating to read for me. Maybe review if
+% the current use of footnotes is really necessary and helpful?
+% TODO: anna's feedback
 
@@
 \section{Preliminaries}\label{sec:recprelims}
+% TODO: I find the writing mostly clear, but the structure of the Preliminaries
+% somewhat confusing. It starts with some notation, then some definitions, then
+% suddenly a paragraph titled "Notation", and so on. Maybe see if you can
+% rearrange some things and/or add some (more) helpful paragraph titles?
 
@@
 ($\GDR$). And third, for reasoning about partially-constructed FCGs, we write
-$\star$ for a placeholder type that is yet to be replaced. Similarly to Van den
-Broeck et al.~\shortcite{DBLP:conf/ijcai/BroeckTMDR11}, we write $T_p$ for an
-FCG that has a node with the label $T_p$ (i.e., type $T$ and parameter(s) $p$)
-and $\star$'s as all of its direct successors. See \cref{fig:examplefcg} for an
-example FCG\@. Its source node has out-degree 1, label $\GDR$, and type $\GDR$.
-% TODO: update the last sentence
+$\star$ for a placeholder type that is yet to be replaced. We write $T_p$ for an
+FCG that has a node with label $T_p$ (i.e., type $T$ and parameter(s) $p$) and
+$\star$'s as all of its direct successors. We also write $T_p(v)$ for an FCG
+with one edge from a node labelled $T_{p}$ to some other node $v$ (and no other
+nodes or edges). See \cref{fig:examplefcg} for an example FCG\@.
 
@@
 \section{How to Interpret an FCG}\label{sec:interpret}
+% TODO: rewrite this section
 
@@
 \end{algorithm}
-% TODO: have I introduced the GDR(v') syntax? (for other types as well)
-
-\begin{itemize}
-  \item TODO: define atomic --- no subtraction, i.e., just a variable name
-  \item for each FCG node $v$, $\mathfrak{D}(v)$ is a precomputed set of domains
-        that are used by $v$ and all of its successors (except the ones that are
-        introduced by $v$ or one of its successors) (this was already part of
-        \textsc{ForcLift}, although had to be reimplemented in a way that avoids
-        infinite loops when dealing with cycles in graphs)
-  \item for list generators over a set of domains, we assume an arbitrary fixed
-        ordering over all domains
-  \item $\mathsf{F}$ is a partial map from the set of FCG nodes to Strings,
-        i.e., function names
-  \item \newVariableName just generates a unique identifier for a variable
-  \item \newFunctionName does the same thing for function names and also records
-        the new name in $\mathsf{F}$
-  \item the top function is the main one
-  \item `is a direct successor of a $\Reff$ node' --- the in-degree is greater
-        than 1
-\end{itemize}
+
+% \begin{itemize}
+%   \item atomic --- no subtraction, i.e., just a variable name
+%   \item for each FCG node $v$, $\mathfrak{D}(v)$ is a precomputed set of domains
+%         that are used by $v$ and all of its successors (except the ones that are
+%         introduced by $v$ or one of its successors) (this was already part of
+%         \textsc{ForcLift}, although had to be reimplemented in a way that avoids
+%         infinite loops when dealing with cycles in graphs)
+%   \item for list generators over a set of domains, we assume an arbitrary fixed
+%         ordering over all domains
+%   \item $\mathsf{F}$ is a partial map from the set of FCG nodes to Strings,
+%         i.e., function names
+%   \item \newVariableName just generates a unique identifier for a variable
+%   \item \newFunctionName does the same thing for function names and also records
+%         the new name in $\mathsf{F}$
+%   \item the top function is the main one
+%   \item `is a direct successor of a $\Reff$ node' --- the in-degree is greater
+%         than 1
+% \end{itemize}
 
@@
 traversing the circuit. With \textsc{Crane}, the interpretation of an FCG is a
-collection of functions. Each function has (some) domain sizes as parameters and
-may contain recursive calls to other functions, including itself. While there
-may be any number of subsidiary functions, there is always one main function
-that can be called with the sizes of the domains of the input formula as
-arguments. Henceforth, this function is always called $f$, and it is defined by
-the source node.
+list of functions. Each function has (some) domain sizes as parameters and may
+contain recursive calls to other functions, including itself. While there may be
+any number of subsidiary functions, there is always one main function that can
+be called with the sizes of the domains of the input formula as arguments.
+Henceforth, this function is always called $f$, and it is defined by the source
+node.
 

### 2023-02-21 doc/talks/3_long/talk.tex
One more slide

@@
 \usepackage{soul}
+\usepackage{csquotes}
+\usepackage{pifont}
 
@@
 \setbeamercolor{background canvas}{bg=white}
+
 \addbibresource{talk.bib}
@@
 \definecolor{color3}{HTML}{e7298a}
+\definecolor{forestgreen}{HTML}{009B55}
 
@@
 
-\newcommand{\x}{\textcolor{color1}{x}}
-\newcommand{\y}{\textcolor{color3}{y}}
+\newcommand{\cmark}{\ding{51}}%
+\newcommand{\xx}{\textcolor{color1}{x}}
+\newcommand{\yy}{\textcolor{color3}{y}}
 \newcommand{\pP}{\texttt{P}}
@@
         \begin{itemize}
-          \item Input formula: $\x \lor \y$
-          \item Interpretations: $\emptyset$, $\{\, \x \,\}$, $\{\, \y \,\}$,
-                $\{\, \x, \y \,\}$
-          \item Models: $\{\, \x \,\}$, $\{\, \y \,\}$, $\{\, \x, \y \,\}$
+          \item Input formula: $\xx \lor \yy$
+          \item Interpretations: $\emptyset$, $\{\, \xx \,\}$, $\{\, \yy \,\}$,
+                $\{\, \xx, \yy \,\}$
+          \item Models: $\{\, \xx \,\}$, $\{\, \yy \,\}$, $\{\, \xx, \yy \,\}$
           \item<2-> Answer (model count): 3
@@
         \begin{itemize}
-          \item Input formula: $\x \lor \y$
+          \item Input formula: $\xx \lor \yy$
           \item Input weights: $\begin{aligned}[t]
-                                  &w(\x) = 0.3\text{, }w(\neg \x) = 0.7,\\
-                                  &w(\y) = 0.2\text{, }w(\neg \y) = 0.8
+                                  &w(\xx) = 0.3\text{, }w(\neg \xx) = 0.7,\\
+                                  &w(\yy) = 0.2\text{, }w(\neg \yy) = 0.8
                                 \end{aligned}$
           \item<4-> Answer (weighted model count):
-                $w(\x)w(\y) + w(\x)w(\neg \y) + w(\neg \x)w(\y) = 0.44$
+                $w(\xx)w(\yy) + w(\xx)w(\neg \yy) + w(\neg \xx)w(\yy) = 0.44$
         \end{itemize}
@@
         \begin{itemize}
-          \item Input formula: $\forall \x \in \Delta\text{. }\pP(\x)$
+          \item Input formula: $\forall \xx \in \Delta\text{. }\pP(\xx)$
           \item Input weights: $w^{+}(\pP) = 0.3$, $w^{-}(\pP) = 0.7$
@@
 % TODO: add a very clear example of what a model is
+% TODO: introduce the problem from the next side, visualise P and Q as subsets of Delta?
 % TODO: (maybe) add a slide about other approaches to WFOMC, making it crystal clear what my contributions are
@@
 \begin{frame}{First-Order Knowledge Compilation: An Approach to FOMC}
+  \begin{minipage}[t][0.81\textheight][t]{\textwidth}
     \centering
@@
       for tree={s sep=10mm, sn edges}
-    [\alt<2->{$\bigwedge_{c \in \Delta}$}{$\forall x \in \Delta\text{. } \pP(x) \lor \qQ(x)$},inner on=<2->,label={[visible on=<{8-9,14-}>]right:{\alert{\alt<10->{$3^{n}$}{$\{\,\pP(c), \qQ(c)\,\}$}}}}
-    [\alt<3->{$\lor$}{$\pP(c) \lor \qQ(c)$},for tree={visible on=<2->},inner on=<3->,label={[visible on=<{7-9,13-}>]right:{\alert{\alt<10->{$2 + 1 = 3$}{$\{\,\pP(c), \qQ(c)\,\}$}}}}
-    [\alt<4->{$\land$}{$\begin{aligned}\qQ(c)\\ \pP(c) \lor \qQ(c)\end{aligned}$},name=and,for tree={visible on=<3->},inner on=<4->,label={[name=foobar,visible on=<{6-9,12-}>]left:{\alert<-8,12->{\alt<10->{$2 \times 1 = 2$}{$\{\,\qQ(c)\,\}$}}}}
-    [\alt<10->{$\pP(c) \lor \neg \pP(c)$}{$\qQ(c)$},name=smoothing,for tree={visible on=<4->},rectangle,draw,fill=gray!25,label={[visible on=<11->]below:{\alert{2}}}]
-    [\alt<10->{$\land$}{$\top$},for tree={visible on=<4->},leaf on=<4-9>,inner on=<10->,label={[label distance=0cm,visible on=<12->]87:{\alert{$1 \times 1 = 1$}}}
-    [$\qQ(c)$,for tree={visible on=<10->},rectangle,draw,fill=gray!25,label={[visible on=<11->]below:{\alert{1}}}]
-    [$\top$,for tree={visible on=<10->},rectangle,draw,fill=gray!25,label={[visible on=<11->]below:{\alert{1}}}]
+      [\alt<3->{$\bigwedge_{c \in \Delta}$}{$\forall x \in \Delta\text{. } \pP(x) \lor \qQ(x)$},
+      inner on=<3->,
+      label={[visible on=<{13-14,19-}>]right:{\alert{\alt<15->{$3^{|\Delta|}$}{$\{\,\pP(c), \qQ(c)\,\}$}}}}
+      [\alt<5->{$\lor$}{$\pP(c) \lor \qQ(c)$},
+      name=lor,
+      for tree={visible on=<3->},
+      inner on=<5->,
+      label={[visible on=<{12-14,18-}>]right:{\alert{\only<18->{$2 + 1 = 3$}\only<12-13>{\colorbox{white}{$\{\,\pP(c), \qQ(c)\,\}$}}\only<14>{\colorbox{redish}{$\{\,\pP(c), \qQ(c)\,\}$}}}}}
+      [\alt<7->{$\land$}{$\begin{aligned}\qQ(c)\\ \pP(c) \lor \qQ(c)\end{aligned}$},
+      name=and,
+      for tree={visible on=<5->},
+      inner on=<7->,
+      label={[visible on=<{11-14,17-}>]left:{\alert{\only<17->{$2 \times 1 = 2$}\only<11-13>{\colorbox{white}{$\{\,\qQ(c)\,\}$}}\only<14>{\colorbox{redish}{$\{\,\qQ(c)\,\}$}}}}}
+      [\alt<15->{$\pP(c) \lor \neg \pP(c)$}{$\qQ(c)$},
+      name=smoothing,
+      for tree={visible on=<7->},
+      rectangle,
+      draw,
+      fill=gray!25,
+      label={[visible on=<16->]below:{\alert{2}}}]
+      [\alt<15->{$\land$}{$\top$},
+      for tree={visible on=<7->},
+      leaf on=<6-14>,
+      inner on=<15->,
+      label={[label distance=0cm,visible on=<17->]87:{\alert{$1 \times 1 = 1$}}},
+      label={[visible on=<10>]below:{\alert{tautology}}},
+      [$\qQ(c)$,
+      for tree={visible on=<15->},
+      rectangle,
+      draw,
+      fill=gray!25,
+      label={[visible on=<16->]below:{\alert{1}}}]
+      [$\top$,
+      for tree={visible on=<15->},
+      rectangle,
+      draw,
+      fill=gray!25,
+      label={[visible on=<16->]below:{\alert{1}}}]
       ]
       ]
-    [\alt<5->{$\land$}{$\begin{aligned}\neg\qQ(c)\\ \pP(c) \lor \qQ(c)\end{aligned}$},for tree={visible on=<3->},inner on=<5->,label={[visible on=<{6-9,12-}>]right:{\alert{\alt<10->{$1 \times 1 = 1$}{$\{\,\pP(c), \qQ(c)\,\}$}}}}
-    [$\neg \qQ(c)$,for tree={visible on=<5->},rectangle,draw,fill=gray!25,label={[visible on=<11->]below:{\alert{1}}}]
-    [$\pP(c)$,for tree={visible on=<5->},rectangle,draw,fill=gray!25,label={[visible on=<11->]below:{\alert{1}}}]
+      [\alt<9->{$\land$}{$\begin{aligned}\neg\qQ(c)\\ \pP(c) \lor \qQ(c)\end{aligned}$},
+      name=negformula,
+      for tree={visible on=<5->},
+      inner on=<9->,
+      label={[visible on=<{11-14,17-}>]right:{\alert{\alt<15->{$1 \times 1 = 1$}{$\{\,\pP(c), \qQ(c)\,\}$}}}}
+      [$\neg \qQ(c)$,
+      name=negq,
+      for tree={visible on=<9->},
+      rectangle,
+      draw,
+      fill=gray!25,
+      label={[visible on=<16->]below:{\alert{1}}}]
+      [$\pP(c)$,
+      name=pnode,
+      for tree={visible on=<9->},
+      rectangle,
+      draw,
+      fill=gray!25,
+      label={[visible on=<16->]below:{\alert{1}}}]
       ]
@@
       \begin{scope}[on background layer]
-      \uncover<9>{\node [fill=redish, ellipse, fit=(foobar)] {};}
-      \uncover<10>{\node [fill=redish, ellipse, fit={(smoothing) (and)}, inner sep=0.5pt] {};}
+        \uncover<6>{\node[fill=redish, ellipse, fit={(and)}, inner sep=0.5pt] {};}
+        \uncover<8>{\node[fill=redish, ellipse, fit={(negformula)}, inner sep=0.5pt] {};}
+        \uncover<15>{\node[fill=redish, ellipse, fit={(smoothing) (and)}, inner sep=0.5pt] {};}
       \end{scope}
+      \node<10>[below = 3cm of lor] (n1) {\alert{unit clauses}};
+      \path[-Latex,draw]<10> (n1) edge[bend right] (pnode);
+      \path[-Latex,draw]<10> (n1) edge (negq);
+      \path[-Latex,draw]<10> (n1) edge[bend left] (smoothing);
     \end{forest}
+  \end{minipage}
+  \begin{minipage}{\textwidth}
+    \begin{overlayarea}{\textwidth}{4cm}
+      \only<2-3>{\centerline{Independent partial grounding (introduces a constant \alert{$c \in \Delta$})}}%
+      \only<4-5>{\centerline{Shannon decomposition (a.k.a. Boole's expansion theorem) on \alert{$\qQ(c)$}}}%
+      \only<6-7>{\centerline{Positive unit propagation of \alert{$\qQ(c)$}}}%
+      \only<8-9>{\centerline{Negative unit propagation of \alert{$\neg\qQ(c)$}}}%
+      \only<10>{\centerline{Compilation is complete \textcolor{forestgreen}{\cmark}}}%
+      \only<11-13>{\centerline{Smoothing: propagating atoms upwards}}%
+      \only<14-15>{\centerline{Smoothing: adding new atoms}}%
+      \only<16->{\centerline{Propagating the model count}}%
+    \end{overlayarea}
+  \end{minipage}
 \end{frame}
-% TODO: add compilation rule names at the bottom
-% TODO: add arrows explaining unit clauses and tautology
-% TODO: maybe use \alert instead of blue?
-% TODO: change both highlight colors (a light shade of red?)
-% TODO: maybe visualise P and Q as subsets of Delta?
 
@@
 \end{frame}
-% TODO: for future work, come back to the 'many ways to count' slide and add more arrows (e.g., beyond FOL)
-
+% TODO: for future work, come back to the 'many ways to count' slide and add
+% more arrows (e.g., beyond FOL)
 \end{document}

### 2023-02-26 doc/paper/paper.tex
Some writing and some more feedback

@@
 % the current use of footnotes is really necessary and helpful?
-% TODO: anna's feedback
+% TODO: replace references with the condensed version
+% TODO: feedback2.pdf
+% TODO: feedback1.pdf
+
+% TODO: what's the punchline? make sure the introduction tells the reader what
+% to expect from section 5
 
@@
 \newcommand\mdoubleplus{\mathbin{+\mkern-10mu+}}
+\newcommand{\Vone}{\mathsf{V}_{1}}
+\newcommand{\Vtwo}{\mathsf{V}_{2}}
+\newcommand{\Vthree}{\mathsf{V}_{3}}
 
@@
 \section{Introduction}\label{sec:introduction}
+
+% TODO: also cite 'WFOMC with DAG axioms'
+% \cite{DBLP:journals/corr/abs-2302-09830}
+
+% TODO: add a flow graph: \phi -> Box (Compilation) -> \G_\phi -> Box (Algorithm
+% 4) -> \mathcal{F}_\phi -> Box (simplification) -> \mathcal{F|_\phi, base
+% cases, domain sizes -> Box (Propagation (?))
+
+% TODO: too many acronyms (e.g., FOL)
 
@@
 
+% TODO: must remove this footnote
 However, none of the publicly available exact (W)FOMC algorithms can efficiently
@@
 needed.
+% TODO: explain why we're not losing anything by dropping equality constraints
+% (e.g., X = Y). Answer: having two variables that are equal is the same thing
+% as having one variable (since by the definition of a clause, this equality can
+% only be at the beginning of a clause.
 
@@
 \end{figure}
+
+% TODO: the definition of FCG is hard to miss (highlight its importance, maybe
+% remind the reader later on in the paper)
+
+% TODO: instead of FO d-DNNF computational graph, say 'first-order computational
+% graph' (FOCG?)
 
@@
 
-\section{How to Interpret an FCG}\label{sec:interpret}
-% TODO: rewrite this section
+\section{Converting FCGs to Function Definitions}\label{sec:interpret}
 
 \begin{algorithm}[t]
-  \caption{Construct functions from an FCG}
+  \caption{Construct functions from an FCG}\label{alg:interpretation}
   \SetKwProg{Fn}{Function}{:}{}
@@
   \KwOut{a list of function definitions}
-  $\variableNames \gets \{\, \Omega \mapsto \newVariableName{} \mid \Omega \in \mathcal{D} \,\}$\;
+  $\variableNames \gets \{\, \Omega \mapsto \newVariableName{} \mid \Omega \in \mathcal{D} \,\}$\;\label{line:varnames}
   \If{$s$ is a direct successor of a $\Reff$ node}{
-    $(\expression, \functions) \gets \visit{$s$, $\variableNames$}$\;
-    \Return{\functions}\;
+    $(\expression, \functions) \gets \visit{$s$, $\variableNames$}$\;\label{line:initialcall}
+    \Return{\functions}\;\label{line:initialcalltwo}
   }
@@
     $\newVariableNames \gets \variableNames$\;
-    \For{$\Omega \in \mathfrak{D}(v)$ s.t. $\newVariableNames(\Omega)$ is non-atomic}{
-      $\newVariableNames(\Omega) \gets \newVariableName{}$\;
-    }
-    $(\expression, \functions) \gets \actuallyVisit{$v$, \newVariableNames}$\;
+    \For{$\Omega \in \mathfrak{D}(v)$ s.t. $\newVariableNames(\Omega)$ is non-atomic}{\label{line:nonone}
+      $\newVariableNames(\Omega) \gets \newVariableName{}$\;\label{line:nontwo}
+    }
+    $(\expression, \functions) \gets \actuallyVisit{$v$, \newVariableNames}$\;\label{line:actuallyvisit}
     $\functionCall \gets f(\langle \variableNames{$\Omega$} \mid \Omega \in \mathfrak{D}(v) \rangle)$\;
@@
       \uCase{$\CR_{\Omega \mapsto \Omega'}(v')$}{
-        \Return{\visit{$v'$, $\variableNames \cup \{\, \Omega' \mapsto (\variableNames(\Omega) - 1) \,\}$}}\;
+        \Return{\visit{$v'$, $\variableNames \cup \{\, \Omega' \mapsto (\variableNames(\Omega) - 1) \,\}$}}\;\label{line:cr}
       }
       \uCase{$\Reff_{\rho}(v')$}{
-        $\args \gets \langle \variableNames{$\rho(\Omega)$} \mid \Omega \in \mathfrak{D}(v') \rangle$\;
+        $\args \gets \langle \variableNames\circ\rho(\Omega) \mid \Omega \in \mathfrak{D}(v') \rangle$\;\label{line:args}
         \Return{$(\functionNames{$v'$}(\args), \langle \rangle)$}\;
@@
 
-% \begin{itemize}
-%   \item atomic --- no subtraction, i.e., just a variable name
-%   \item for each FCG node $v$, $\mathfrak{D}(v)$ is a precomputed set of domains
-%         that are used by $v$ and all of its successors (except the ones that are
-%         introduced by $v$ or one of its successors) (this was already part of
-%         \textsc{ForcLift}, although had to be reimplemented in a way that avoids
-%         infinite loops when dealing with cycles in graphs)
-%   \item for list generators over a set of domains, we assume an arbitrary fixed
-%         ordering over all domains
-%   \item $\mathsf{F}$ is a partial map from the set of FCG nodes to Strings,
-%         i.e., function names
-%   \item \newVariableName just generates a unique identifier for a variable
-%   \item \newFunctionName does the same thing for function names and also records
-%         the new name in $\mathsf{F}$
-%   \item the top function is the main one
-%   \item `is a direct successor of a $\Reff$ node' --- the in-degree is greater
-%         than 1
-% \end{itemize}
+\begin{itemize}
+  \item TODO: is maybe `parameter name' (or something similar) would be more
+        appropriate than `variable name'?
+  \item We call a variable name is \emph{atomic} if it is free of subtraction
+        (e.g., $m$, $n$); otherwise it is \emph{non-atomic} (e.g., $m-1$,
+        $n-l$).
+  \item For each node $v$, let $\mathfrak{D}(v)$ denote the (precomputed) set of
+        domains, the sizes of which we would use as parameters if we were to
+        define a function that begins at $v$. This set is computed by
+        iteratively setting
+        $\mathfrak{D}(v) \gets \left(\bigcup_{u} \mathfrak{D}(u) \setminus I_{v}\right) \cup U_{v}$
+        until convergence, where
+        \begin{itemize}
+          \item $u$ is any direct successor of $v$,
+          \item $I_{v}$ is the set of domains \emph{introduced} at node $v$, and
+          \item $U_{v}$ is the set of domains \emph{used} by $v$.
+        \end{itemize}
+  \item We assume a fixed total ordering of all domains names. In particular, in
+        our running example we assume that $\Gamma$ goes before $\Delta$.
+  \item $\mathsf{F}$ is a partial map from the set of FCG nodes to function
+        names (e.g., $f$, $g$).
+  \item \newVariableName just generates a unique identifier for a variable
+  \item \newFunctionName does the same thing for function names and also records
+        the new name in $\mathsf{F}$
+  \item The first function in the list is the main one.
+  \item Note that a node is a direct successor of a $\Reff$ node if and only if
+        it has an in-degree greater than one.
+  \item For simplicity, we refer to FCG nodes using their types.
+  \item The algorithm consists of two main functions: \visit and \actuallyVisit.
+        The former handles new function definitions, and the latter produces an
+        algebraic interpretation of each node depending on its type. As there
+        are many node types, \cref{alg:interpretation} only includes the ones
+        pertinent to the contributions of this paper; see previous
+        work~\cite{DBLP:conf/ijcai/BroeckTMDR11} for information about the other
+        types.
+  \item Given some node $v$ as input, both \visit and \actuallyVisit return a
+        pair $(\mathsf{e}, \mathsf{funs})$. Here, $\mathsf{e}$ is the algebraic
+        expression that should be used to evaluate $v$ or use it in another
+        expression, and $\mathsf{funs}$ is a list of auxiliary functions that
+        were created while constructing $\mathsf{e}$.
+  \item TODO: $\mathfrak{D}$ must be a list. That's the ordering of domain names
+        comes in, not in list comprehensions.
+\end{itemize}
 
@@
 
+\begin{figure}
+  \centering
+  \begin{tikzcd}
+    \ar[d] & \\
+    \text{\Cref{alg:interpretation}} \ar[d] \ar[u, swap, shift right=0.7ex, "{\left\langle f(m, n) = \sum_{l=0}^{n}[l<2]f(m-1,n-l) \right\rangle}"] & \\
+    \visit{$\GDR$, $\Vone$} \ar[d] \ar[u, swap, shift right=0.7ex, "\left({f(m, n), \left\langle f(m, n) = \sum_{l=0}^{n}[l<2]f(m-1,n-l) \right\rangle}\right)"] & \\
+    \actuallyVisit{$\GDR$, $\Vone$} \ar[d] \ar[u, swap, shift right=0.7ex, "\left({\sum_{l=0}^{n}[l<2]f(m-1,n-l), \langle\rangle}\right)"] & \\
+    \visit/\actuallyVisit{$\bigvee$, $\Vone$} \ar[d] \ar[u, swap, shift right=0.7ex, "\left({\sum_{l=0}^{n}[l<2]f(m-1,n-l), \langle\rangle}\right)"] & \\
+    \visit/\actuallyVisit{$\CR$, $\Vtwo$} \ar[d] \ar[u, swap, shift right=0.7ex, "\left({[l<2]f(m-1,n-l), \langle\rangle}\right)"] & \\
+    \visit/\actuallyVisit{$\land$, $\Vthree$} \ar[d] \ar[dr] \ar[u, swap, shift right=0.7ex, "\left({[l<2]f(m-1,n-l), \langle\rangle}\right)"] & \\
+    \visit/\actuallyVisit{$\bot$, $\Vthree$} \ar[u, swap, shift right=0.7ex, "\left({[l<2], \langle\rangle}\right)"] & \visit/\actuallyVisit{$\Reff$, $\Vthree$} \ar[ul, swap, shift right=0.7ex, "\left({f(m-1, n-l), \langle\rangle}\right)"]
+  \end{tikzcd}
+  \caption{Function calls and their return values when \cref{alg:interpretation}
+    is run on the FCG from \cref{fig:examplefcg}. When \protect\visit calls
+    \protect\actuallyVisit and returns its output unchanged, the two function
+    calls are shortened as a single call to
+    $\protect\visit/\protect\actuallyVisit$. TODO: this last sentence should be
+    explained in text.}\label{fig:functioncalls}
+\end{figure}
+
 \begin{example}\label{example:interpretation}
-  Consider the FCG from \cref{fig:examplefcg}. The input formula (i.e., the
-  formula from \cref{example:first}) has two domains: $\Gamma$ and $\Delta$.
-  Thus, the interpretation of the FCG is a function
-  $f\colon \mathbb{N}_{0} \times \mathbb{N}_{0} \to \mathbb{R}_{\ge 0}$. Let
-  $m \coloneqq |\Gamma|$, and $n \coloneqq |\Delta|$. The node labelled
-  $\bigvee_{\Delta^{\top} \subseteq \Delta}$ tells us that
-  $f(m, n) = \sum_{l = 0}^{n} \binom{n}{l} \square$, where $\square$ is the
-  interpretation of the remaining subgraph, and $l$ iterates over all possible
-  sizes of $\Delta^{\top}$. It also creates two subdomains
-  $\Delta^{\top}, \Delta^{\bot} \subseteq \Delta$ that partition $\Delta$, i.e.,
-  as the size of $\Delta^{\top}$ increases, the size of $\Delta^{\bot}$
-  correspondingly decreases. Nodes labelled $\land$ correspond to
-  multiplication. Therefore,
-  $f(m, n) = \sum_{l = 0}^{n} \binom{n}{l} \diamondsuit \times \heartsuit$,
-  where $\diamondsuit$ is the interpretation of the contradiction (i.e., $\bot$)
-  node, and $\heartsuit$ is the interpretation of the $\Reff$ node.
-
-  A contradiction node with clause $c$ as a parameter is interpreted as one if
-  the clause has groundings and zero otherwise. In this case, the parameter is
+  Let us see how \cref{alg:interpretation} handles the FCG from
+  \cref{fig:examplefcg}. Here, $\mathcal{D} = \{\, \Gamma, \Delta \,\}$. Let
+  $\Vone \coloneqq \{\, \Gamma \mapsto m, \Delta \mapsto n \,\}$,
+  $\Vtwo \coloneqq \Vone \cup \{\, \Delta^{\top} \mapsto l, \Delta^{\bot} \mapsto (n-l) \,\}$,
+  and $\Vthree \coloneqq \Vtwo \cup \{\, \Gamma' \mapsto (m-1) \,\}$ denote
+  versions of $\mathsf{V}$ at various points throughout the algorithm's
+  execution. Here, $l$, $m$, and $n$ are all arbitrary variable names generated
+  by \newVariableName. \Cref{line:varnames} initialises $\mathsf{V}$ to $\Vone$.
+
+  \Cref{fig:functioncalls} shows the outline of function calls and their return
+  values. Once \visit{$\GDR$, $\Vone$} is called on \cref{line:initialcall},
+  \newFunctionName updates $\mathsf{F}$ to $\{\, \GDR \mapsto f \,\}$, where $f$
+  is a new function name. There are no non-atomic names in $\Vone$, so
+  \cref{line:nonone,line:nontwo} are skipped, and calls to
+  \actuallyVisit{$\GDR$, $\Vone$} and
+  $\visit/\actuallyVisit{$\bigvee$, $\Vone$}$ follow. Here, $\Vone$ becomes
+  $\Vtwo$, i.e., the $\bigvee$ node introduces two domains $\Delta^{\top}$ and
+  $\Delta^{\bot}$ that `partition' $\Delta$, i.e.,
+  $\Vtwo(\Delta^{\top}) + \Vtwo(\Delta^{\bot}) = l + (n-l) = n = \Vtwo(\Delta)$.
+  Similarly, \actuallyVisit{$\CR$, $\Vtwo$} on \cref{line:cr} adds $\Gamma'$,
+  replacing $\Vtwo$ with $\Vthree$.
+
+  Eventually, \actuallyVisit{$\bot$, $\Vthree$} is called. A contradiction node
+  with clause $c$ as a parameter is interpreted as one if the clause has
+  groundings and zero otherwise. In this case, the parameter is
   $c = (\emptyset, \{\, (X, Y) \,\}, \{\, X \mapsto \Delta^\top, Y \mapsto \Delta^\top \,\})$
-  (not shown in \cref{fig:examplefcg}), which can be read as
+  (not shown in \cref{fig:examplefcg}). Equivalently,
   $\forall X, Y \in \Delta^{\top}\text{. }X \ne Y \Rightarrow \bot$, i.e.,
-  $\forall X, Y \in \Delta^{\top}\text{. }X = Y$. This latter sentence is true
-  if and only if $|\Delta^{\top}| < 2$. Therefore, we can use the Iverson
-  bracket notation to write
+  $\forall X, Y \in \Delta^{\top}\text{. }X = Y$. This sentence is true if and
+  only if $\Vthree(\Delta^{\top}) < 2$. Thus, we can use the Iverson bracket
+  notation to write
   \[
-    \diamondsuit = [l < 2] \coloneqq
+    [l < 2] \coloneqq
     \begin{cases}
@@
   \]
-
-  It remains to interpret the $\Reff$ node. Parameter
-  $\{\, \Gamma \mapsto \Gamma', \Delta \mapsto \Delta^\bot \,\}$ tells us that
-  the interpretation of the $\Reff$ node should be the same as that of the
-  source node, but with domains $\Gamma$ and $\Delta$ replaced with $\Gamma'$
-  and $\Delta^{\bot}$, respectively. Domain $\Gamma'$ was created by the CR rule
-  applied on $\Gamma$, so $|\Gamma'| = m - 1$. Now
-  $\Delta^{\bot} = \Delta \setminus \Delta^{\top}$, and $|\Delta^{\top}| = l$,
-  so $|\Delta^{\bot}| = n - l$. Thus, the interpretation of the $\Reff$ node is
-  a recursive call to $f(m - 1, n - l)$. Therefore,
+  for the output expression of \actuallyVisit{$\bot$, $\Vthree$}.
+
+  Next, \actuallyVisit{$\land$, $\Vthree$} calls
+  $\visit/\actuallyVisit{$\Reff$, $\Vthree$}$. Since
+  $\mathfrak{D}(\GDR) = \langle \Gamma, \Delta \rangle$, and
+  $\begin{tikzcd} \langle\Gamma, \Delta\rangle \ar[r, mapsto, "\rho"] & \langle\Gamma', \Delta^{\bot}\rangle \ar[r, mapsto, "\Vthree"] & \langle m-1, n-l \rangle\end{tikzcd}$,
+  \textsf{args} is set to $\langle m-1, n-l \rangle$ on \cref{line:args}, and
+  the output expression becomes $f(m-1, n-l)$. The call to
+  \actuallyVisit{$\land$, $\Vthree$} then returns the product of the two
+  expressions $[l<2]f(m-1, n-l)$. Next, the call to \actuallyVisit{$\bigvee$,
+    $\Vone$} prepends a summation and returns $\sum_{l=0}^{n}[l<2]f(m-1,n-l)$.
+  The same expression (and an empty list of functions) is then returned to
+  \cref{line:actuallyvisit} of the call to \visit{$\GDR$, $\Vone$}. Here, both
+  \textsf{call} and \textsf{signature} are set to $f(m, n)$. As the definition
+  of $f$ is the final answer and not part of some other algebraic expression,
+  \cref{line:initialcall,line:initialcalltwo} discard the function call
+  expression and return the definition of $f$.
+
+  Therefore,
   \begin{align}
@@
 \section{Experimental Results}\label{sec:results}
+% TODO: rename 'experimental results' -> 'complexity results' (not just the
+% title of the section but review every mention of the word 'experimental')
+% TODO: make it clear that I'm not doing this by hand anymore, but I'm still
+% removing multiplications by one.
+% TODO (here or somewhere else): emphasise that there are two parts: search
+% (with some artificial limit) + inference (whose complexity we can easily
+% determine)
+% TODO: Must do one of these:
+% 1. determine the complexity of the counting quantifiers algorithm when run on
+% these instances
+% 2. find instances that are not in C^2 and make the paper about them
+% 3. run the counting quantifiers algorithm on these instances with increasing
+% domain sizes, statistically estimating the degree of the polynomial and
+% juxtaposing it with my complexity results shifted to overlap as much as
+% possible
 
@@
 \end{table*}
+% TODO: 'Asymptotic Complexity of Counting' -> 'Complexity of \mathcal{F}_\phi'
+% (introduce \mathcal{F}_\phi in the introduction, together with the flow graph)
+
+% TODO: remove the rows that say 'same as..', putting the explanation about them
+% in text. And don't say 'same as', instead say that the formulas are in some
+% sence equivalent (maybe in a stronger sense than the usual equivalence).
+
+% TODO: emphasise that the reader should focus on the last two columns
+% TODO: the last sentence of the caption could be confusing
+% TODO: 'best known' sounds disappointing. Find a better alternative.
 
@@
 a constant amount of time on the computation of each $f(i, j)$.
+% TODO: look for a better place to put the 'In particular...' remark
 

### 2023-02-26 doc/talks/3_long/talk.tex
Some writing and some more feedback

@@
 \usepackage{pifont}
+\usepackage{venndiagram}
 
@@
 \definecolor{color2}{HTML}{7570b3}
-\definecolor{color3}{HTML}{e7298a}
+\definecolor{color3}{HTML}{e7298a} % TODO: I don't like pink
 \definecolor{forestgreen}{HTML}{009B55}
@@
 \newcommand{\cmark}{\ding{51}}%
+
 \newcommand{\xx}{\textcolor{color1}{x}}
@@
 \newcommand{\dDelta}{\textcolor{color2}{\Delta}}
+
+\newcommand{\pone}{\textcolor{color1}{\pP(1)}}
+\newcommand{\ptwo}{\textcolor{color1}{\pP(2)}}
+\newcommand{\qone}{\textcolor{color2}{\qQ(1)}}
+\newcommand{\qtwo}{\textcolor{color2}{\qQ(2)}}
+\newcommand{\pqone}{\textcolor{color3}{\pP(1)}, \textcolor{color3}{\qQ(1)}}
+\newcommand{\pqtwo}{\textcolor{color3}{\pP(2)}, \textcolor{color3}{\qQ(2)}}
 
@@
 \author{\textbf{Paulius Dilkas} \inst{1} \and Vaishak Belle \inst{2}}
-\title{Recursive Solutions to \\First-Order Model Counting}
+\title{Synthesising Recursive Functions for\\ First-Order Model Counting}
 \institute{\inst{1} National University of Singapore, Singapore \and \inst{2} University of Edinburgh, UK}
@@
 
-% TODO: add a very clear example of what a model is
-% TODO: introduce the problem from the next side, visualise P and Q as subsets of Delta?
 % TODO: (maybe) add a slide about other approaches to WFOMC, making it crystal clear what my contributions are
-\begin{frame}{First-Order Model Counting (in More Detail)}
+
+\begin{frame}{(Unweighted) First-Order Model Counting}
+  \begin{columns}[T]
+    \begin{column}{0.5\textwidth}
       \begin{itemize}
-    \item \alert{First-order model counting} (FOMC) is the problem of counting
-          the models of a sentence in first-order logic.
-    \item The \alert{(symmetric) weighted} variation of the problem adds weights
-          (e.g., probabilities) to predicates.
-          \begin{itemize}
-            \item It is used for efficient \alert{probabilistic inference} in
-                  relational models such as Markov logic networks.
+        \item Example formula: $\forall x \in \Delta\text{. } \pP(x) \lor \qQ(x)$
+        \item Let $\Delta \coloneqq \{\, 1, 2 \,\}$
+        \item Interpretations: all subsets of $\{\, \pP(1), \qQ(1), \pP(2), \qQ(2) \,\}$
+        \item Models:
+        \[
+          \begin{matrix}
+            \{\, \pone, \ptwo \,\}, & \{\, \pone, \qtwo \,\}, & \{\, \pone, \pqtwo \,\},\\
+            \{\, \qone, \ptwo \,\}, & \{\, \qone, \qtwo \,\}, & \{\, \qone, \pqtwo \,\},\\
+            \{\, \pqone, \ptwo \,\}, & \{\, \pqone, \qtwo \,\}, & \{\, \pqone, \pqtwo \,\}\\
+          \end{matrix}
+        \]
+        \item Each 1-ary predicate...
       \end{itemize}
-    \item None of the (implemented) (W)FOMC algorithms are able to count, e.g.,
-          \alert{injective} and \alert{bijective} functions.
-  \end{itemize}
-  \begin{block}{Claim}
-    This shortcoming can be addressed via support for \alert{recursive functions}.
-  \end{block}
+    \end{column}
+    \begin{column}{0.5\textwidth}
+      \centering
+      \begin{overlayarea}{\textwidth}{4cm}
+        \only<1>{
+          \begin{venndiagram2sets}[labelNotAB={$\Delta$},labelA={$\pP$},labelB={$\qQ$}]
+          \end{venndiagram2sets}
+        }%
+        \only<2>{
+          \begin{venndiagram2sets}[labelNotAB={$\Delta$},labelA={$\pP$},labelB={$\qQ$}]
+            \fillOnlyA;
+          \end{venndiagram2sets}
+        }%
+        \only<3>{
+          \begin{venndiagram2sets}[labelNotAB={$\Delta$},labelA={$\pP$},labelB={$\qQ$}]
+            \fillOnlyB;
+          \end{venndiagram2sets}
+        }%
+        \only<4>{
+          \begin{venndiagram2sets}[labelNotAB={$\Delta$},labelA={$\pP$},labelB={$\qQ$}]
+            \fillACapB;
+          \end{venndiagram2sets}
+        }%
+        \only<5>{
+          \begin{venndiagram2sets}[labelNotAB={$\Delta$},labelA={$\pP$},labelB={$\qQ$}]
+            \fillA;
+            \fillB;
+          \end{venndiagram2sets}
+        }%
+      \end{overlayarea}
+    \end{column}
+  \end{columns}
 \end{frame}
+% TODO: mention that n-ary predicates ~= relations
+
+% \begin{frame}{First-Order Model Counting (in More Detail)}
+%   \begin{itemize}
+%     \item \alert{First-order model counting} (FOMC) is the problem of counting
+%           the models of a sentence in first-order logic.
+%     \item The \alert{(symmetric) weighted} variation of the problem adds weights
+%           (e.g., probabilities) to predicates.
+%           \begin{itemize}
+%             \item It is used for efficient \alert{probabilistic inference} in
+%                   relational models such as Markov logic networks.
+%           \end{itemize}
+%     \item None of the (implemented) (W)FOMC algorithms are able to count, e.g.,
+%           \alert{injective} and \alert{bijective} functions.
+%   \end{itemize}
+%   \begin{block}{Claim}
+%     This shortcoming can be addressed via support for \alert{recursive functions}.
+%   \end{block}
+% \end{frame}
 

### 2023-02-26 solutions.py

@@ -269,7 +269,10 @@ def factorial(n):
 def friendsmoker(n):
     return 2**n * sum(math.comb(n, m) * 2**((n-m)*(n-m-1) + (n-m)*m + m*(m-1)) for m in range(n + 1))
 
-MAX = 10
+def friendsmoker_simple(n):
+    return sum(math.comb(n, k)*2**(n*n-k*(n-k)) for k in range(n+1))
+
+MAX = 100
 
 # for m in range(1, MAX):
 #     for n in range(1, MAX):
@@ -302,9 +305,4 @@ MAX = 10
 #     )
 
 for n in range(0, MAX):
-    print(
-        "f({}) = {}".format(
-            n,
-            friendsmoker(n)
-        )
-    )
+    print(str(friendsmoker_simple(n)) + ", ", end="")

### 2023-02-26 solvers/Crane/src/main/scala/edu/ucla/cs/starai/forclift/nnf/visitors/DomainsVisitor.scala

@@ -105,6 +105,7 @@ class DomainsVisitor(val nodes: ListBuffer[NNFNode])
     returnValue
   }
 
+  // TODO: maybe this should just be the image of rho?
   protected def visitRefNode(ref: Ref, u: Unit): Boolean = {
     val returnValue = ref.domains != ref.nnfNode.get.domains
     ref.domains = ref.nnfNode.get.domains

### 2023-02-26 solvers/fastwfomc/main.py
Add support for cardinality constraints to FastWFOMC

@@ -4,7 +4,7 @@ from collections import defaultdict
 from aima3.logic import to_cnf
 from aima3.utils import expr, Expr
 
-from wfomc import WFOMC
+from wfomc_cc import WFOMCWithCC
 
 
 def main():
@@ -27,7 +27,7 @@ def main():
         '(~E(x,y) | (~(C1(x) & C1(y)) & ~(C2(x) & C2(y)) & ~(C3(x) & C3(y)) & ~(C4(x) & C4(y))))'
     )
 
-    counter = WFOMC(four_coloured, n)
+    counter = WFOMCWithCC(four_coloured, n)
     print(counter.get_wfomc(defaultdict(lambda: (1, 1))))
 
 

### 2023-02-26 solvers/python-flint/src/flint/acb.pyx

@@ -1,0 +1,2563 @@
+cdef int acb_set_python(acb_t x, obj, bint allow_conversion):
+    cdef double re, im
+
+    if typecheck(obj, acb):
+        acb_set(x, (<acb>obj).val)
+        return 1
+
+    if arb_set_python(acb_realref(x), obj, allow_conversion):
+        arb_zero(acb_imagref(x))
+        return 1
+
+    if PyComplex_Check(<PyObject*>obj):
+        re = PyComplex_RealAsDouble(<PyObject*>obj)
+        im = PyComplex_ImagAsDouble(<PyObject*>obj)
+        arf_set_d(arb_midref(acb_realref(x)), re)
+        arf_set_d(arb_midref(acb_imagref(x)), im)
+        mag_zero(arb_radref(acb_realref(x)))
+        mag_zero(arb_radref(acb_imagref(x)))
+        return 1
+
+    if hasattr(obj, "_mpc_"):
+        xre, xim = obj._mpc_
+        arb_set_mpmath_mpf(acb_realref(x), xre)
+        arb_set_mpmath_mpf(acb_imagref(x), xim)
+        return 1
+
+    return 0
+
+cdef inline int acb_set_any_ref(acb_t x, obj):
+    if typecheck(obj, acb):  # should be exact check?
+        x[0] = (<acb>obj).val[0]
+        return FMPZ_REF
+
+    acb_init(x)
+    if acb_set_python(x, obj, 0):
+        return FMPZ_TMP
+
+    return FMPZ_UNKNOWN
+
+cdef any_as_acb(x):
+    cdef acb t
+    if typecheck(x, acb):
+        return x
+    t = acb()
+    if acb_set_python(t.val, x, 0) == 0:
+        raise TypeError("cannot create acb from type %s" % type(x))
+    return t
+
+cdef any_as_acb_or_notimplemented(x):
+    cdef acb t
+    if typecheck(x, acb):
+        return x
+    t = acb()
+    if acb_set_python(t.val, x, 0) == 0:
+        return NotImplemented
+    return t
+
+"""
+cdef any_as_arb_or_acb(x):
+    if typecheck(x, arb) or typecheck(x, acb):
+        return x
+    try:
+        return arb(x)
+    except (TypeError, ValueError):
+        return acb(x)
+"""
+
+# Copied with modifications from sage/rings/complex_arb.pyx
+@cython.internal
+cdef class IntegrationContext:
+    cdef object f
[…]

### 2023-02-26 solvers/python-flint/src/flint/acb_series.pyx

@@ -1,0 +1,807 @@
+cdef acb_series_coerce_operands(x, y):
+    if typecheck(x, acb_series):
+        if isinstance(y, (int, long, float, complex, fmpz, fmpz_poly, fmpz_series, fmpq, fmpq_poly, fmpq_series, arb, arb_poly, arb_series, acb, acb_poly)):
+            return x, acb_series(y)
+    else:
+        if isinstance(x, (int, long, float, complex, fmpz, fmpz_poly, fmpz_series, fmpq, fmpq_poly, fmpq_series, arb, arb_poly, arb_series, acb, acb_poly)):
+            return acb_series(x), y
+    return NotImplemented, NotImplemented
+
+cdef class acb_series(flint_series):
+
+    cdef acb_poly_t val
+    cdef long prec
+
+    def __cinit__(self):
+        acb_poly_init(self.val)
+        self.prec = 0
+
+    def __dealloc__(self):
+        acb_poly_clear(self.val)
+
+    def __init__(self, val=None, prec=None):
+        if prec is None:
+            self.prec = getcap()
+        else:
+            self.prec = prec
+        if self.prec < 0:
+            self.prec = -1
+        if val is not None:
+            if typecheck(val, acb_series):
+                acb_poly_set(self.val, (<acb_series>val).val)
+                self.prec = min((<acb_series>val).prec, getcap())
+            elif typecheck(val, arb_series):
+                acb_poly_set_arb_poly(self.val, (<arb_series>val).val)
+                self.prec = min((<arb_series>val).prec, getcap())
+            elif typecheck(val, fmpz_series):
+                acb_poly_set_fmpz_poly(self.val, (<fmpz_series>val).val, getprec())
+                self.prec = min((<fmpz_series>val).prec, getcap())
+            elif typecheck(val, fmpz_poly):
+                acb_poly_set_fmpz_poly(self.val, (<fmpz_poly>val).val, getprec())
+            elif typecheck(val, acb_poly):
+                acb_poly_set(self.val, (<acb_poly>val).val)
+            elif typecheck(val, list):
+                acb_poly_set_list(self.val, val, getprec())
+            else:
+                acb_poly_set_list(self.val, [val], getprec())
+        acb_poly_truncate(self.val, max(0, self.prec))
+
+    def __len__(self):
+        return acb_poly_length(self.val)
+
+    cpdef long length(self):
+        return acb_poly_length(self.val)
+
+    def __getitem__(self, long i):
+        cdef acb x
[…]

### 2023-02-26 solvers/python-flint/src/flint/arb_mat.pyx

@@ -1,0 +1,667 @@
+cdef arb_mat_coerce_operands(x, y):
+    if typecheck(x, arb_mat):
+        if isinstance(y, (fmpz_mat, fmpq_mat)):
+            return x, arb_mat(y)
+        if isinstance(y, (int, long, float, fmpz, fmpq, arb)):
+            return x, arb_mat(x.nrows(), x.ncols(), y)
+        if isinstance(y, (complex, acb)):
+            return acb_mat(x), acb_mat(x.nrows(), x.ncols(), y)
+    elif typecheck(y, arb_mat):
+        if isinstance(x, (fmpz_mat, fmpq_mat)):
+            return arb_mat(x), y
+        if isinstance(y, (int, long, float, fmpz, fmpq, arb)):
+            return arb_mat(y.nrows(), y.ncols(), x), y
+        if isinstance(y, (complex, acb)):
+            return acb_mat(y.nrows(), y.ncols(), x), acb_mat(y)
+    return NotImplemented, NotImplemented
+
+cdef arb_mat_coerce_scalar(x, y):
+    if isinstance(y, (int, long, float, fmpz, fmpq, arb)):
+        return x, any_as_arb(y)
+    if isinstance(y, (complex, acb)):
+        return acb_mat(x), any_as_acb(y)
+    return NotImplemented, NotImplemented
+
+cdef class arb_mat(flint_mat):
+    """
+    Represents a matrix over the real numbers.
+
+        >>> A = arb_mat([[1,2],[3,4]]) ** 2 / 5
+        >>> A
+        [[1.40000000000000 +/- 3.12e-16],                2.00000000000000]
+        [               3.00000000000000, [4.40000000000000 +/- 1.43e-15]]
+        >>> print(A.str(5, radius=False))
+        [1.4000, 2.0000]
+        [3.0000, 4.4000]
+
+    """
+
+    cdef arb_mat_t val
+
+    def __cinit__(self):
+        arb_mat_init(self.val, 0, 0)
+
+    def __dealloc__(self):
+        arb_mat_clear(self.val)
+
+    @classmethod
+    def convert_operand(cls, x):
+        """
+        Attempts to convert *x* to an *arb_mat*, returning NotImplemented
+        if unsuccessful.
+        """
+        if typecheck(x, cls):
+            return x
+        if typecheck(x, fmpz_mat) or typecheck(x, fmpq_mat):
+            return cls(x)
+        return NotImplemented
+
+    @classmethod
[…]

### 2023-02-27 doc/paper/paper.tex
Add support for cardinality constraints to FastWFOMC
Transfer feedback to TeX

@@
 
-\title{Synthesising Recursive Functions for First-Order Model Counting}
+\title{Synthesising Recursive Functions for First-Order Model Counting:\\
+  Challenges, Progress, and Conjectures}
 
@@
 % TODO: replace references with the condensed version
-% TODO: feedback2.pdf
-% TODO: feedback1.pdf
-
-% TODO: what's the punchline? make sure the introduction tells the reader what
-% to expect from section 5
 
@@
 }
+
+\hyphenation{ForcLift}
+\hyphenation{Crane}
+\hyphenation{Alchemy}
+\hyphenation{FastWFOMC}
+\hyphenation{Magician}
+\hyphenation{Tuffy}
 
@@
 
+% TODO: what's the punchline? make sure the introduction tells the reader what
+% to expect from section 5
+
 % 1. What is the problem?
@@
 
+% TODO (about the sentence "Lifted ... (Kersting)"): This developed
+% simultaneously, with the development of so-called probabilistic relational
+% models, that combined syntactic power of FOL with, b networks & m networks,
+% allowing for a more relational view of uncertainty modelling
 \emph{First-order model counting} (FOMC) is the problem of computing the number
@@
 
-% TODO: must remove this footnote
+% TODO: must remove this footnote. Also, two more papers to mention:
+% 1. the L2C paper has the factorial example as well. But then why doesn't L2C work on it?
+% 2.
+cite the new paper "On Discovering Interesting Combinatorial Integer Sequences" as another example of computing n!
+using publicly unavailable code and as an example of applications to combinatorics
 However, none of the publicly available exact (W)FOMC algorithms can efficiently
 compute functions as simple as a factorial.\footnote{There is some previous work
-  showing how FOMC can compute
+  discussing FOMC for
   factorials~\cite{DBLP:journals/jair/Kuzelka21,DBLP:conf/kr/BremenK21,DBLP:conf/ijcai/Broeck16}.
@@
   third~\cite{DBLP:conf/kr/BremenK21} contains experimental results performed
-  with an algorithm, which is not publicly available.} We claim that the
+  with an algorithm that is not publicly available.} We claim that the
 capabilities of (W)FOMC algorithms can be significantly extended by empowering
@@
   work~\cite{DBLP:conf/ijcai/BroeckTMDR11} for more information about the
-  rules.} This alternative was introduced since there is no reason to expect
+  rules.} This alternative was introduced because there is no reason to expect
 greedy search to be optimal. Second, the product of compilation is not directly
@@
 synthesis~\cite{DBLP:conf/cav/GoliaRM20,DBLP:conf/pldi/KuncakMPS10,sanathanan1963transfer}.
-
-% similarly to the other domains, there are many functions that fit the
-% specification, i.e., can correctly count the number of models as a function of
-% domain size(s). Whereas in [...] one typically wants to select the smallest
-% definition of a function, we are primarily concerned with its worst-case
-% complexity as measured by the number of arithmetic operations needed for an
-% arbitrary function call
-% \begin{itemize}
-%   \item Boolean functions~\cite{DBLP:conf/cav/GoliaRM20}
-%   \item dynamical systems~\cite{sanathanan1963transfer}
-%   \item program fragments~\cite{DBLP:conf/pldi/KuncakMPS10}
-% \end{itemize}
-
-% \footnote{There is also an intermediate stage called \emph{smoothing} that takes
-%   place between compilation and evaluation. As our changes to smoothing are
-%   rather elementary, we do not discuss them to not distract the reader from the
-%   main contributions of this paper.}
 
@@
 \end{definition}
-
+% TODO: what is its semantic meaning? Meaning what logically: a \ne b? (say
+% that)
+
+% TODO: c = (L, E, \delta), E - inequality constraints
 \begin{definition}[Clause]\label{def:clause}
@@
   the function that maps clauses and sets of either literals or constraints to
-  the set of variables contained within. In particular,
+  the set of variables in them. In particular,
   $\Vars(c) \coloneqq \Vars(L) \cup \Vars(C)$. \emph{Domain map}
@@
 
+% TODO: The first paragraph already introduced some notation.
+% TODO: so S^2 \coloneqq {(a, b) \mid a, b \in S}
 \paragraph{Notation.}
@@
 finite length of elements of $S$. For any $n \in \mathbb{N}_{0}$, let
-$[n] \coloneqq \{\, 1, \dots, n \,\}$. For example, $[0] = \emptyset$, and
+$[n] \coloneqq \{\, 1, \dots, n \,\}$, e.g., $[0] = \emptyset$, and
 $[2] = \{\, 1, 2 \,\}$. We write $\langle\rangle$ for an empty list,
@@
 
+% TODO: why was 'c-clause' a footnote but not this? Combine with previous
+% footnote.
 \begin{definition}[Formula]\label{def:formula}
@@
 \end{definition}
+% TODO: why is this a footnote?
 
@@
 
+% TODO: the 'but note' part is confusing
+% TODO: add \, for when a line ends with a \land
 One can read a formula in our format as a sentence in FOL\@. All variables in a
@@
 
+% TODO: the first sentence comes out of nowhere
 Once domains are mapped to finite sets and constants to elements in those sets,
@@
   $(\phi, \sigma)$ is a map
-  $\mathfrak{M}\colon \Preds(\phi) \to 2^{\mathbb{N}_{0}^{\ast}}$ such that the
+  $\mathfrak{M}\colon \Preds(\phi) \to 2^{\mathbb{N}_{0}^{\ast}}$ s.t.\ the
   following two conditions are satisfied.
@@
 \end{definition}
-
+% TODO (about the second condition): inductive defin?
+% M entails p(a) /\ p'(b) iff M entails p(a) and M entails p'(b)
+% M entails \neg p(a) iff M \not\entails p(a)
+% M entails \forall X. p(a) iff M entails p(d) \forall d \in D.
+
+% TODO: make the relations more concrete
 \begin{example}
@@
 
+% TODO (about the footnote): say: this shows that there is no loss of
+% expressiveness/compilation completeness with our new algorithm. Would be nice
+% if you could also show formally how it has improved on Guy, e.g., Prop.
+% \exists formula \phi such that AlgoGuy(\phi) may fail but NewAlg(\phi) \ne
+% \emptyset. Therefore, our algorithms is `more' complete than Guy's
 \begin{theorem}[Correctness of $\GDR$\footnote{\Cref{thm:correctness1} is equivalent to
@@
   $\Omega \in \mathcal{D}$ the domain selected on \cref{line:condition}, and
-  $\phi'$ the formula constructed by the algorithm for $\Omega$. Assume that
+  $\phi'$ the formula constructed by the algorithm for $\Omega$. Suppose that
   $\Omega \ne \emptyset$. Then $\phi \equiv \phi'$.
@@
 \end{proof}
+% TODO: Does this have analogue in Guy? If yes, explain difference. If no,
+% emphasize this point. Same for Theorem 3.
 
@@
   Let $\phi$ be the formula used as input to \cref{alg:trycache}. Let $\psi$ be
-  any formula selected on \cref{line:selectformula} of the algorithm such that
+  any formula selected on \cref{line:selectformula} of the algorithm s.t.\
   $\rho \ne {\normalfont\texttt{null}}$ on \cref{line:rho}. Let $\sigma$ be a
@@
 
+% TODO: I think I said this the last time, but alog with the complexities as a
+% way of representing the empirical evaluation, I think you should also include
+% a few plots, even if they say nothing more than what the table already says.
+% The point is that the readers can see what this behaviour looks like so even
+% if you include a few plots and say we just give a few representative examples
+% and the rest follow the table of all that will be better
+
 We compare \textsc{Crane} and

### 2023-02-28 doc/paper/paper.tex
Improve references

@@
 % the current use of footnotes is really necessary and helpful?
-% TODO: replace references with the condensed version
 
@@
 
-% TODO: also cite 'WFOMC with DAG axioms'
-% \cite{DBLP:journals/corr/abs-2302-09830}
+TODO: also cite 'WFOMC with DAG axioms'~\cite{DBLP:journals/corr/abs-2302-09830}
 
@@
 if it can be solved in time polynomial in the size(s) of the
-domain(s)~\cite{jaeger2012liftability}. Over more than a decade, many classes of
-instances were shown to be
+domain(s)~\cite{DBLP:conf/starai/JaegerB12}. Over more than a decade, many
+classes of instances were shown to be
 liftable~\cite{DBLP:conf/kr/BremenK21,DBLP:conf/nips/KazemiKBP16,DBLP:conf/lics/KuusistoL18,DBLP:journals/jair/Kuzelka21}.
@@
 % possible
+% TODO: describe ternary.mln as an example instance that's not in C^2 that can
+% be lifted
 

### 2023-03-01 doc/paper/paper.tex
Move proofs to supplementary material

@@
 \newtheorem{example}{Example}
+\theoremstyle{remark}
+\newtheorem*{remark}{Remark}
 
@@
 % make sure the result table (as well as other floating objects) are on the right pages
-
-% TODO: I found the choice for what goes into a footnote and what doesn't rather
-% inconsistent, which made it a bit irritating to read for me. Maybe review if
-% the current use of footnotes is really necessary and helpful?
 
@@
 
+% TODO: I found the choice for what goes into a footnote and what doesn't rather
+% inconsistent, which made it a bit irritating to read for me. Maybe review if
+% the current use of footnotes is really necessary and helpful?
+
 \section{Introduction}\label{sec:introduction}
-
-TODO: also cite 'WFOMC with DAG axioms'~\cite{DBLP:journals/corr/abs-2302-09830}
 
@@
 
-% TODO: too many acronyms (e.g., FOL)
-
 % TODO: what's the punchline? make sure the introduction tells the reader what
@@
 
-% TODO (about the sentence "Lifted ... (Kersting)"): This developed
-% simultaneously, with the development of so-called probabilistic relational
-% models, that combined syntactic power of FOL with, b networks & m networks,
-% allowing for a more relational view of uncertainty modelling
 \emph{First-order model counting} (FOMC) is the problem of computing the number
-of models of a sentence in first-order logic (FOL) given the size(s) of its
+of models of a sentence in first-order logic given the size(s) of its
 domain(s)~\cite{DBLP:conf/pods/BeameBGS15}. \emph{Symmetric weighted FOMC}
@@
 individuals~\cite{DBLP:conf/ecai/Kersting12}. By doing so, many instances become
-solvable in polynomial time~\cite{DBLP:conf/nips/Broeck11}. Lifted inference
-algorithms are typically used on probabilistic models such as probabilistic
-programming
-languages~\cite{DBLP:journals/ml/RaedtK15,DBLP:journals/ijar/RiguzziBZCL17},
-Markov logic
-networks~\cite{DBLP:conf/ijcai/BroeckTMDR11,DBLP:journals/cacm/GogateD16,DBLP:journals/ml/RichardsonD06},
-and other lifted graphical~\cite{DBLP:journals/ml/KimmigMG15} and statistical
-relational~\cite{DBLP:series/synthesis/2016Raedt} models. Lifted inference
-techniques for probabilistic databases, while developed somewhat independently,
-have also been inspired by
+solvable in polynomial time~\cite{DBLP:conf/nips/Broeck11}. The development of
+lifted inference algorithms coincided with work on probabilistic relational
+models that combine the syntactic power of first-order logic with probabilistic
+models such as Bayesian and Markov networks, allowing for a more relational view
+of uncertainty
+modelling~\cite{DBLP:series/synthesis/2016Raedt,DBLP:journals/ml/KimmigMG15,DBLP:journals/ml/RichardsonD06}.
+Lifted inference techniques for probabilistic databases, while developed
+somewhat independently, have also been inspired by
 WFOMC~\cite{DBLP:journals/pvldb/GatterbauerS15,DBLP:journals/debu/GribkoffSB14}.
@@
 
+% Lifted inference algorithms are typically used on probabilistic models such as
+% probabilistic programming
+% languages~\cite{DBLP:journals/ml/RaedtK15,DBLP:journals/ijar/RiguzziBZCL17},
+% Markov logic
+% networks~\cite{DBLP:conf/ijcai/BroeckTMDR11,DBLP:journals/cacm/GogateD16}.
+
 % 3. Why is it hard? (E.g., why do naive approaches fail?)
@@
 domain(s)~\cite{DBLP:conf/starai/JaegerB12}. Over more than a decade, many
-classes of instances were shown to be
-liftable~\cite{DBLP:conf/kr/BremenK21,DBLP:conf/nips/KazemiKBP16,DBLP:conf/lics/KuusistoL18,DBLP:journals/jair/Kuzelka21}.
-First, Van den Broeck~\shortcite{DBLP:conf/nips/Broeck11} showed that the class
-of all sentences of FOL with up to two variables (denoted \FOtwo{}) is liftable.
-Then Beame et al.~\shortcite{DBLP:conf/pods/BeameBGS15} proved that there exists
-a sentence with three variables for which FOMC is $\#\P_{1}$-complete (i.e.,
-\FOthree{} is not liftable). Since these two seminal results, most of the
-research on (W)FOMC focused on developing faster solutions for the \FOtwo{}
+classes of instances were shown to be liftable. First, Van den
+Broeck~\shortcite{DBLP:conf/nips/Broeck11} showed that the class of all
+sentences of first-order logic with up to two variables (denoted \FOtwo{}) is
+liftable. Then Beame et al.~\shortcite{DBLP:conf/pods/BeameBGS15} proved that
+there exists a sentence with three variables for which FOMC is
+$\#\P_{1}$-complete (i.e., \FOthree{} is not liftable). Since these two seminal
+results, most of the research on (W)FOMC focused on developing faster solutions
+for the \FOtwo{}
 fragment~\cite{DBLP:conf/uai/BremenK21,DBLP:conf/aaai/MalhotraS22} and defining
@@
 quantifiers)~\cite{DBLP:journals/jair/Kuzelka21,DBLP:conf/aaai/MalhotraS22}, and
-\Ctwo{} extended with tree axioms~\cite{DBLP:conf/kr/BremenK21} and linear order
-axiom~\cite{DBLP:journals/corr/abs-2211-01164}. On the empirical front, there
+\Ctwo{} extended with axioms describing trees~\cite{DBLP:conf/kr/BremenK21},
+directed acyclic graphs~\cite{DBLP:journals/corr/abs-2302-09830}, and linear
+order~\cite{DBLP:journals/corr/abs-2211-01164}. On the empirical front, there
 are several implementations of exact WFOMC algorithms:
@@
 
-We begin by defining the representation used for sentences in FOL in
-\cref{sec:recprelims}. Then, in \cref{sec:methods}, we define the graphs that
+We begin by defining the representation used for sentences in first-order logic
+in \cref{sec:recprelims}. Then, in \cref{sec:methods}, we define the graphs that
 replace circuits in representing a solution to a (W)FOMC problem.
@@
 \section{Preliminaries}\label{sec:recprelims}
+
+% TODO: Maybe some of the info from the preliminaries is redundant now that I've
+% moved the proofs elsewhere?
+
 % TODO: I find the writing mostly clear, but the structure of the Preliminaries
@@
 Broeck et al.~\shortcite{DBLP:conf/ijcai/BroeckTMDR11}. \textsc{ForcLift} can
-translate sentences in a variant of function-free many-sorted FOL with equality
-to this internal format. We use lowercase Latin letters for predicates (e.g.,
-$\texttt{p}$) and constants (e.g., $x$), uppercase Latin letters for variables
-(e.g., $X$), and uppercase Greek letters for domains (e.g., $\Delta$). Sometimes
-we write predicate $\texttt{p}$ as $\texttt{p}/n$, where $n \in \mathbb{N}^{+}$
-is the \emph{arity} of $\texttt{p}$. An \emph{atom} is
-$\texttt{p}(t_1, \dots, t_n)$ for some predicate $\texttt{p}/n$ and terms
+translate sentences in a variant of function-free many-sorted first-order logic
+with equality to this internal format. We use lowercase Latin letters for
+predicates (e.g., $\texttt{p}$) and constants (e.g., $x$), uppercase Latin
+letters for variables (e.g., $X$), and uppercase Greek letters for domains
+(e.g., $\Delta$). Sometimes we write predicate $\texttt{p}$ as $\texttt{p}/n$,
+where $n \in \mathbb{N}^{+}$ is the \emph{arity} of $\texttt{p}$. An \emph{atom}
+is $\texttt{p}(t_1, \dots, t_n)$ for some predicate $\texttt{p}/n$ and terms
 $t_{1}, \dots, t_{n}$. A \emph{term} is either a constant or a variable. A
@@
   An \emph{(inequality) constraint} is a pair $(a, b)$, where $a$ is a variable,
-  and $b$ is either a variable or a constant.
+  and $b$ is either a variable or a constant. As the name implies, it constrains
+  $a$ and $b$ to be unequal.
 \end{definition}
-% TODO: what is its semantic meaning? Meaning what logically: a \ne b? (say
-% that)
 
@@
 \begin{definition}[Clause]\label{def:clause}
-  A \emph{clause}\footnote{Van den Broeck et
-    al.~\shortcite{DBLP:conf/ijcai/BroeckTMDR11} refer to clauses as c-clauses.}
+  A \emph{clause}
   is a triple $c = (L, C, \delta_c)$, where $L$ is a set of literals, $C$ is a
@@
 % TODO: The first paragraph already introduced some notation.
-% TODO: so S^2 \coloneqq {(a, b) \mid a, b \in S}
 \paragraph{Notation.}
@@
 $S^{\ast} \coloneqq \bigcup_{i=0}^{\infty} S^{i}$ the set of tuples of any
-finite length of elements of $S$. For any $n \in \mathbb{N}_{0}$, let
-$[n] \coloneqq \{\, 1, \dots, n \,\}$, e.g., $[0] = \emptyset$, and
-$[2] = \{\, 1, 2 \,\}$. We write $\langle\rangle$ for an empty list,
-$\langle x \rangle$ for a list with one element $x$, $|l|$ for the length of
-list $l$, $\mdoubleplus$ for list concatenation, and $\pfun$ to denote partial
-functions. Let $S$ be a set of constraints or literals, $V$ a set of variables,
-and $x$ a variable or a constant. We write $S[x/V]$ to denote $S$ with all
-occurrences of all variables in $V$ replaced with $x$. Let $\Doms$
+finite length of elements of $S$. For example,
+$\{\,a, b\,\}^{\ast} = \{\, (), (a), (b), (a, a), \dots \,\}$. For any
+$n \in \mathbb{N}_{0}$, let $[n] \coloneqq \{\, 1, \dots, n \,\}$, e.g.,
+$[0] = \emptyset$, and $[2] = \{\, 1, 2 \,\}$. We write $\langle\rangle$ for an
+empty list, $\langle x \rangle$ for a list with one element $x$, $|l|$ for the
+length of list $l$, $\mdoubleplus$ for list concatenation, and $\pfun$ to denote
+partial functions. Let $S$ be a set of constraints or literals, $V$ a set of
+variables, and $x$ a variable or a constant. We write $S[x/V]$ to denote $S$
+with all occurrences of all variables in $V$ replaced with $x$. Let $\Doms$
 (respectively, $\Preds$) be the function that maps any clause or formula to the
@@
 
-% TODO: why was 'c-clause' a footnote but not this? Combine with previous
-% footnote.
 \begin{definition}[Formula]\label{def:formula}
-  A \emph{formula} (called a c-theory by Van den Broeck et
-  al.~\shortcite{DBLP:conf/ijcai/BroeckTMDR11}) is a set of clauses s.t.\ all
-  constraints and atoms `type check' with respect to domains. Each formula
-  $\phi$ has a map $\pi_{\phi}\colon \Preds(\phi) \to {\Doms(\phi)}^{\ast}$ such
-  that, for each predicate $\texttt{p}/n \in \Preds(\phi)$, we have that
-  $\pi_{\phi}(\texttt{p}) \in {\Doms(\phi)}^{n}$.\footnote{Similarly to
-    variables and predicates, constants are also mapped to domains, although we
-    keep this mapping implicit.}
+  A \emph{formula} is a set of clauses s.t.\ all constraints and atoms `type
+  check' with respect to domains. Each formula $\phi$ has a map
+  $\pi_{\phi}\colon \Preds(\phi) \to {\Doms(\phi)}^{\ast}$ such that, for each
+  predicate $\texttt{p}/n \in \Preds(\phi)$, we have that
+  $\pi_{\phi}(\texttt{p}) \in {\Doms(\phi)}^{n}$.
 \end{definition}
-% TODO: why is this a footnote?
+
+\begin{remark}
+  Constants are also mapped to domains, although we keep this mapping implicit.
+\end{remark}
 
@@
 First, we decouple variable-to-domain assignments from constraints and move them
-to a separate function $\delta_{c}$ in \cref{def:clause}. Second, while Van den
-Broeck et al.~\shortcite{DBLP:conf/ijcai/BroeckTMDR11} allow for equality
-constraints and constraints of the form $X \not\in \Delta$ for some variable $X$
-and domain $\Delta$, we exclude such constraints simply because they are not
-needed.
+to a separate function $\delta_{c}$ in \cref{def:clause}. Second, while they
+allow for equality constraints and constraints of the form $X \not\in \Delta$
+for some variable $X$ and domain $\Delta$, we exclude such constraints simply
+because they are not needed. Moreover, note that Van den Broeck et
+al.~\shortcite{DBLP:conf/ijcai/BroeckTMDR11} refer to clauses and formulas as
+c-clauses and c-theories, respectively.
 % TODO: explain why we're not losing anything by dropping equality constraints
@@
 
-% TODO: the 'but note' part is confusing
-% TODO: add \, for when a line ends with a \land
-One can read a formula in our format as a sentence in FOL\@. All variables in a
-clause are implicitly universally quantified (but note that variables are never
-shared among clauses), and all clauses in a formula are implicitly linked by a
-conjunction. Thus, formula $\phi$ from \cref{example:first} reads as
+One can read a formula in our format as a sentence in first-order logic. All
+variables in a clause are implicitly universally quantified, and all clauses in
+a formula are implicitly linked by a conjunction. Thus, formula $\phi$ from
+\cref{example:first} reads as
 \begin{align*}
@@
     (\forall X \in \Gamma\text{. }\forall Y, Z \in \Delta\text{. }\\
-    Y \ne Z \Rightarrow \neg \texttt{p}(X, Y) \lor \neg \texttt{p}(X, Z)) \land
+    Y \ne Z \Rightarrow \neg \texttt{p}(X, Y) \lor \neg \texttt{p}(X, Z)) \land{}
     \end{multlined}\\
@@
     \item As a collection of relations, $\mathfrak{M}$ satisfies $\phi$.
+    \begin{itemize}
+      \item TODO: introduce the substitution for formulas, moving the definition from elsewhere
+      \item define inductively as...
+      \item (not exhaustive)
+      \item $\mathfrak{M} \models \phi \land \psi$ iff $\mathfrak{M} \models \phi$ and $\mathfrak{M} \models \psi$
+      \item $\mathfrak{M} \models \phi \lor \psi$ iff $\mathfrak{M} \models \phi$ or $\mathfrak{M} \models \psi$
+      \item $\mathfrak{M} \models \neg\phi$ iff $\mathfrak{M} \not\models \phi$
+      \item $\mathfrak{M} \models (\forall X \in \Delta\text{. }\phi)$ iff $\mathfrak{M} \models \phi[x/\{\, X \,\}]$ for all $x \in \Delta$
+      \item One can then add inequality constraints to the semantics as follows
+      \item $\mathfrak{M} \models (\forall X \in \Delta\text{. } X \ne c \Rightarrow \phi)$ iff $\mathfrak{M} \models \phi[x/\{\, X \,\}]$ for all $x \in \Delta \setminus \{\, c \,\}$
+      \item $\mathfrak{M} \models (\forall X,Y \in \Delta\text{. } X \ne Y \Rightarrow \phi)$ iff $\mathfrak{M} \models \phi[x/\{\, X \,\}][y/\{\, Y \,\}]$ for all $x,y \in \Delta$ such that $x \ne y$
+    \end{itemize}
   \end{enumerate}
 \end{definition}
-% TODO (about the second condition): inductive defin?
-% M entails p(a) /\ p'(b) iff M entails p(a) and M entails p'(b)
-% M entails \neg p(a) iff M \not\entails p(a)
-% M entails \forall X. p(a) iff M entails p(d) \forall d \in D.
 
@@
 Van den Broeck et al.~\shortcite{DBLP:conf/ijcai/BroeckTMDR11} generalised them
-to FOL via \emph{first-order d-DNNF (FO d-DNNF) circuits}. FO d-DNNF circuits
-(hereafter simply called \emph{circuits}) are directed acyclic graphs with nodes
-corresponding to formulas in FOL---see \cref{fig:simplecircuit} for an example.
-The following types of nodes are supported by \textsc{ForcLift}: caching
-($\Reff$), contradiction ($\bot$), tautology ($\top$), decomposable conjunction
-($\land$), decomposable set-conjunction ($\bigwedge$), deterministic disjunction
-($\lor$), deterministic set-disjunction ($\bigvee$), domain recursion,
-grounding, inclusion-exclusion, smoothing, and unit clause. We refer the reader
-to previous work~\cite{DBLP:conf/nips/Broeck11,DBLP:conf/ijcai/BroeckTMDR11} for
-more information about node types and their interpretations for computing the
+to first-order logic via \emph{first-order d-DNNF (FO d-DNNF) circuits}. FO
+d-DNNF circuits (hereafter simply called \emph{circuits}) are directed acyclic
+graphs with nodes corresponding to formulas in first-order logic---see
+\cref{fig:simplecircuit} for an example. The following types of nodes are
+supported by \textsc{ForcLift}: caching ($\Reff$), contradiction ($\bot$),
+tautology ($\top$), decomposable conjunction ($\land$), decomposable
+set-conjunction ($\bigwedge$), deterministic disjunction ($\lor$), deterministic
+set-disjunction ($\bigvee$), domain recursion, grounding, inclusion-exclusion,
+smoothing, and unit clause. We refer the reader to previous
+work~\cite{DBLP:conf/nips/Broeck11,DBLP:conf/ijcai/BroeckTMDR11} for more
+information about node types and their interpretations for computing the
 (W)FOMC\@.
@@
 
-% TODO (about the footnote): say: this shows that there is no loss of
-% expressiveness/compilation completeness with our new algorithm. Would be nice
-% if you could also show formally how it has improved on Guy, e.g., Prop.
-% \exists formula \phi such that AlgoGuy(\phi) may fail but NewAlg(\phi) \ne
-% \emptyset. Therefore, our algorithms is `more' complete than Guy's
-\begin{theorem}[Correctness of $\GDR$\footnote{\Cref{thm:correctness1} is equivalent to
-    Proposition~3 by Van den Broeck~\shortcite{DBLP:conf/nips/Broeck11}.}]\label{thm:correctness1}
+\begin{theorem}[Correctness of $\GDR$]\label{thm:correctness1}
   Let $\phi$ be the formula used as input to \cref{alg:domainrecursion},
@@
 \end{theorem}
-\begin{proof}
-  Let $x$ be the constant introduced on \cref{line:constant} and $c$ a clause of
-  $\phi$ selected on \cref{line:forclause} of the algorithm. We will show that
-  $c$ is equivalent to the conjunction of clauses added to $\phi'$ on
-  \cref{line:conditions,line:generation}.
-
-  If $c$ has no variables with domain $\Omega$, then
-  \cref{line:conditions,line:generation} simply add a copy of $c$ to $\phi'$. If
-  $c$ has one variable with domain $\Omega$, say, $X$, then
-  $c \equiv \forall X \in \Omega\text{. } \psi$ for some formula $\psi$ with one
-  free variable $X$. In this case, \cref{line:conditions,line:generation} create
-  two clauses: $\psi[x/\{\, X \,\}]$ and $\forall X \in \Omega\text{.
-  } X \ne x \Rightarrow \psi$. It is easy to see that their conjunction is
-  equivalent to $c$ provided that $\Omega \ne \emptyset$ and so $x$ is a
-  well-defined constant.
-
-  Let $V$ be the set of variables introduced on \cref{line:V}. It remains to
-  show that repeating the transformation
-  \[
-    \forall X \in \Omega\text{. } \psi \mapsto \{\, \psi[x/\{\, X \,\}], \forall X \in \Omega\text{. } X \ne x \Rightarrow \psi \,\}
-  \]
-  for all variables $X \in V$ produces the same clauses as
-  \cref{line:conditions,line:generation} (except for some tautologies that the
-  latter method skips). Note that the order in which these operations are
-  applied is immaterial. In other words, if we add inequality constraints for
-  variables ${\{\, X_{i} \,\}}_{i=1}^{n}$, and apply substitution for variables
-  $V \setminus {\{\, X_{i} \,\}}_{i=1}^{n}$, then---regardless of the order of
-  operations---we get
-  \[
-    \forall X_{1}, \dots, X_{n} \in \Omega\text{.} \bigwedge_{i=1}^{n} X_{i} \ne x \Rightarrow \psi\left[x / \left(V \setminus {\{\, X_{i} \,\}}_{i=1}^{n}\right)\right].
-  \]
-  This formula is equivalent to the clause generated on \cref{line:generation}
-  with $W = V \setminus {\{\, X_{i} \,\}}_{i=1}^{n}$. Thus, for every clause $c$
-  of $\phi$, the new formula $\phi'$ gets a set of clauses whose conjunction is
-  equivalent to $c$. Hence, the two formulas are equivalent.
-\end{proof}
+
+Note that \Cref{thm:correctness1} is equivalent to Proposition~3 by Van den
+Broeck~\shortcite{DBLP:conf/nips/Broeck11}. For the proofs of this and other
+theorems, see supplementary material.
+% TODO (about the first sentence): say: this shows that there is no loss of
+% expressiveness/compilation completeness with our new algorithm. Would be nice
+% if you could also show formally how it has improved on Guy, e.g., Prop.
+% \exists formula \phi such that AlgoGuy(\phi) may fail but NewAlg(\phi) \ne
+% \emptyset. Therefore, our algorithms is `more' complete than Guy's
 
@@
 \end{theorem}
-\begin{proof}
-  Since there is a natural bijection between the clauses of $\phi$ and $\phi'$,
-  we shall argue about the equivalence of each pair of clauses. Let $c$ be an
-  arbitrary clause of $\phi$ and $c'$ its corresponding clause of $\phi'$.
-
-  If $c$ has no variables with domain $\Omega$, then it cannot have any
-  constraints involving $x$, so $c' = c$. Otherwise, for notational simplicity,
-  let us assume that $X$ is the only variable in $c$ with domain $\Omega$ (the
-  proof for an arbitrary number of variables is virtually the same). By
-  \cref{def:replaceable}, we can rewrite $c$ as $\forall X \in \Omega\text{.
-  } X \ne x \Rightarrow \psi$, where $\psi$ is a formula with $X$ as the only free
-  variable and with no mention of either $x$ or $\Omega$. Then
-  $c' \equiv \forall X \in \Omega'\text{. } \psi$. Since
-  $\Omega' \coloneqq \Omega \setminus \{\, x \,\}$, we have that $c \equiv c'$.
-  Since $c$ was an arbitrary clause of $\phi$, this completes the proof that
-  $\phi \equiv \phi'$.
-\end{proof}
 % TODO: Does this have analogue in Guy? If yes, explain difference. If no,
@@
 \end{theorem}
-\begin{proof}
-  We first show that the right-hand side of \cref{eq:subset} is the same for
-  models of both $(\phi, \sigma)$ and $(\psi, \sigma \circ \rho)$.
-  \Cref{alg:trycache} ensures that $\psi \equiv \phi$ up to domains. In
-  particular, this means that $\Preds(\psi) = \Preds(\phi)$. The square in
-  \begin{equation}\label[diagram]{diagram:ref}
-    \begin{tikzcd}
-      \Preds(\psi) \ar[equal]{r} \ar[d, swap, "\pi_{\psi}"] & \Preds(\phi) \ar[d, "\pi_{\phi}"] \\
-      {\Doms(\psi)}^{\ast} \ar[r, "\rho"] & {\Doms(\phi)}^{\ast} \ar[r, "\sigma"] & \mathbb{N}_{0}^{\ast}
-    \end{tikzcd}
-  \end{equation}
-  commutes by \cref{def:formula} and the definition of $\rho$. In other words,
-  for any predicate $\texttt{p}/n \in \Preds(\psi) = \Preds(\phi)$, function
-  $\rho$ translates the domains associated with $\texttt{p}$ in $\psi$ to the
-  domains associated with $\texttt{p}$ in $\phi$. Let
-  $\pi_{\phi}(\texttt{p}) = {(d_{i})}_{i=1}^{n}$ and
-  $\pi_{\psi}(\texttt{p}) = {(e_{i})}_{i=1}^{n}$ for some domains
-  $d_{i} \in \Doms(\phi)$ and $e_{i} \in \Doms(\psi)$. Since
-  $\rho(e_{i}) = d_{i}$ for all $i = 1, \dots, n$ by the commutativity in
-  \cref{diagram:ref}, we get that
-  \begin{equation}\label{eq:equality}
-    \prod_{i=1}^{n}[\sigma(d_{i})] = \prod_{i=1}^{n}[\sigma \circ \rho(e_{i})]
-  \end{equation}
-  as required. Certainly, any subset of the left-hand side of \cref{eq:equality}
-  (e.g., $\mathfrak{M}(\texttt{p})$, where $\mathfrak{M}$ is a model of
-  $(\phi, \sigma)$) is a subset of the right-hand side and vice versa. Since
-  $\phi$ and $\psi$ semantically only differ in what domains they refer to,
-  every model of $\phi$ satisfies $\psi$ and vice versa, completing the proof.
-\end{proof}
 
@@
 the instances that \textsc{ForcLift} fails on. We begin by describing how such
-function-counting problems can be expressed in FOL\@. \textsc{ForcLift} then
-translates these sentences in FOL to formulas as defined in \cref{def:formula}.
+function-counting problems can be expressed in first-order logic.
+\textsc{ForcLift} then translates these sentences in first-order logic to
+formulas as defined in \cref{def:formula}.
 
@@
 $\Delta$. To restrict all such relations to just $\Gamma \to \Delta$ functions,
-in FOL one might write
+in first-order logic one might write
 \[
@@
 \begin{conjecture}
-  Let \IFO{} be the class of formulas in FOL that contain clauses with at most
-  two variables as well as any number of copies of
+  Let \IFO{} be the class of formulas in first-order logic that contain clauses
+  with at most two variables as well as any number of copies of
   \begin{align*}
@@
       (\forall X \in \Gamma\text{. }\forall Y, Z \in \Delta\text{. }\\
-      Y \ne Z \Rightarrow \neg \texttt{\textup{p}}(X, Y) \lor \neg \texttt{\textup{p}}(X, Z)) \land
+      Y \ne Z \Rightarrow \neg \texttt{\textup{p}}(X, Y) \lor \neg \texttt{\textup{p}}(X, Z)) \land{}
     \end{multlined}\\

### 2023-03-01 doc/paper/supplementary_material.tex
Move proofs to supplementary material

@@
 \usepackage[inline]{enumitem}
+\usepackage{xr}
+\externaldocument{paper}
 
@@
 \appendix
-\section{Solutions Found by \textsc{Crane}}\label{app:solutions}
+
+\section{Proofs}
+
+\begin{theorem}[Correctness of $\GDR$]
+  Let $\phi$ be the formula used as input to \cref{alg:domainrecursion},
+  $\Omega \in \mathcal{D}$ the domain selected on \cref{line:condition}, and
+  $\phi'$ the formula constructed by the algorithm for $\Omega$. Suppose that
+  $\Omega \ne \emptyset$. Then $\phi \equiv \phi'$.
+\end{theorem}
+\begin{proof}
+  Let $x$ be the constant introduced on \cref{line:constant} and $c$ a clause of
+  $\phi$ selected on \cref{line:forclause} of the algorithm. We will show that
+  $c$ is equivalent to the conjunction of clauses added to $\phi'$ on
+  \cref{line:conditions,line:generation}.
+
+  If $c$ has no variables with domain $\Omega$, then
+  \cref{line:conditions,line:generation} simply add a copy of $c$ to $\phi'$. If
+  $c$ has one variable with domain $\Omega$, say, $X$, then
+  $c \equiv \forall X \in \Omega\text{. } \psi$ for some formula $\psi$ with one
+  free variable $X$. In this case, \cref{line:conditions,line:generation} create
+  two clauses: $\psi[x/\{\, X \,\}]$ and $\forall X \in \Omega\text{.
+  } X \ne x \Rightarrow \psi$. It is easy to see that their conjunction is
+  equivalent to $c$ provided that $\Omega \ne \emptyset$ and so $x$ is a
+  well-defined constant.
+
+  Let $V$ be the set of variables introduced on \cref{line:V}. It remains to
+  show that repeating the transformation
+  \[
+    \forall X \in \Omega\text{. } \psi \mapsto \{\, \psi[x/\{\, X \,\}], \forall X \in \Omega\text{. } X \ne x \Rightarrow \psi \,\}
+  \]
+  for all variables $X \in V$ produces the same clauses as
+  \cref{line:conditions,line:generation} (except for some tautologies that the
+  latter method skips). Note that the order in which these operations are
+  applied is immaterial. In other words, if we add inequality constraints for
+  variables ${\{\, X_{i} \,\}}_{i=1}^{n}$, and apply substitution for variables
+  $V \setminus {\{\, X_{i} \,\}}_{i=1}^{n}$, then---regardless of the order of
+  operations---we get
+  \[
+    \forall X_{1}, \dots, X_{n} \in \Omega\text{.} \bigwedge_{i=1}^{n} X_{i} \ne x \Rightarrow \psi\left[x / \left(V \setminus {\{\, X_{i} \,\}}_{i=1}^{n}\right)\right].
+  \]
+  This formula is equivalent to the clause generated on \cref{line:generation}
+  with $W = V \setminus {\{\, X_{i} \,\}}_{i=1}^{n}$. Thus, for every clause $c$
+  of $\phi$, the new formula $\phi'$ gets a set of clauses whose conjunction is
+  equivalent to $c$. Hence, the two formulas are equivalent.
+\end{proof}
+
+\begin{theorem}[Correctness of $\CR$]
+  Let $\phi$ be the input formula of \cref{alg:constraintremoval}, $(\Omega, x)$
+  a replaceable pair, and $\phi'$ the formula constructed by the algorithm, when
+  $(\Omega, x)$ is selected on \cref{line:crconditions}. Then
+  $\phi \equiv \phi'$, where the domain $\Omega'$ introduced on
+  \cref{line:newdomain} is interpreted as $\Omega \setminus \{\, x \,\}$.
+\end{theorem}
+\begin{proof}
+  Since there is a natural bijection between the clauses of $\phi$ and $\phi'$,
+  we shall argue about the equivalence of each pair of clauses. Let $c$ be an
+  arbitrary clause of $\phi$ and $c'$ its corresponding clause of $\phi'$.
+
+  If $c$ has no variables with domain $\Omega$, then it cannot have any
+  constraints involving $x$, so $c' = c$. Otherwise, for notational simplicity,
+  let us assume that $X$ is the only variable in $c$ with domain $\Omega$ (the
+  proof for an arbitrary number of variables is virtually the same). By
+  \cref{def:replaceable}, we can rewrite $c$ as $\forall X \in \Omega\text{.
+  } X \ne x \Rightarrow \psi$, where $\psi$ is a formula with $X$ as the only free
+  variable and with no mention of either $x$ or $\Omega$. Then
+  $c' \equiv \forall X \in \Omega'\text{. } \psi$. Since
+  $\Omega' \coloneqq \Omega \setminus \{\, x \,\}$, we have that $c \equiv c'$.
+  Since $c$ was an arbitrary clause of $\phi$, this completes the proof that
+  $\phi \equiv \phi'$.
+\end{proof}
+
+\begin{theorem}[Correctness of $\Reff$]
+  Let $\phi$ be the formula used as input to \cref{alg:trycache}. Let $\psi$ be
+  any formula selected on \cref{line:selectformula} of the algorithm s.t.\
+  $\rho \ne {\normalfont\texttt{null}}$ on \cref{line:rho}. Let $\sigma$ be a
+  domain size function. Then the set of models of $(\psi, \sigma \circ \rho)$ is
+  equal to the set of models of $(\phi, \sigma)$.
+\end{theorem}
+\begin{proof}
+  We first show that the right-hand side of \cref{eq:subset} is the same for
+  models of both $(\phi, \sigma)$ and $(\psi, \sigma \circ \rho)$.
+  \Cref{alg:trycache} ensures that $\psi \equiv \phi$ up to domains. In
+  particular, this means that $\Preds(\psi) = \Preds(\phi)$. The square in
+  \begin{equation}\label[diagram]{diagram:ref}
+    \begin{tikzcd}
+      \Preds(\psi) \ar[equal]{r} \ar[d, swap, "\pi_{\psi}"] & \Preds(\phi) \ar[d, "\pi_{\phi}"] \\
+      {\Doms(\psi)}^{\ast} \ar[r, "\rho"] & {\Doms(\phi)}^{\ast} \ar[r, "\sigma"] & \mathbb{N}_{0}^{\ast}
+    \end{tikzcd}
+  \end{equation}
+  commutes by \cref{def:formula} and the definition of $\rho$. In other words,
+  for any predicate $\texttt{p}/n \in \Preds(\psi) = \Preds(\phi)$, function
+  $\rho$ translates the domains associated with $\texttt{p}$ in $\psi$ to the
+  domains associated with $\texttt{p}$ in $\phi$. Let
+  $\pi_{\phi}(\texttt{p}) = {(d_{i})}_{i=1}^{n}$ and
+  $\pi_{\psi}(\texttt{p}) = {(e_{i})}_{i=1}^{n}$ for some domains
+  $d_{i} \in \Doms(\phi)$ and $e_{i} \in \Doms(\psi)$. Since
+  $\rho(e_{i}) = d_{i}$ for all $i = 1, \dots, n$ by the commutativity in
+  \cref{diagram:ref}, we get that
+  \begin{equation}\label{eq:equality}
+    \prod_{i=1}^{n}[\sigma(d_{i})] = \prod_{i=1}^{n}[\sigma \circ \rho(e_{i})]
+  \end{equation}
+  as required. Certainly, any subset of the left-hand side of \cref{eq:equality}
+  (e.g., $\mathfrak{M}(\texttt{p})$, where $\mathfrak{M}$ is a model of
+  $(\phi, \sigma)$) is a subset of the right-hand side and vice versa. Since
+  $\phi$ and $\psi$ semantically only differ in what domains they refer to,
+  every model of $\phi$ satisfies $\psi$ and vice versa, completing the proof.
+\end{proof}
+
+\section{Solutions Found by \textsc{Crane}}
 

### 2023-03-01 doc/paper/paper.tex
Various changes to the paper

@@
 
+\crefname{algocf}{Algorithm}{Algorithms}
+\Crefname{algocf}{Algorithm}{Algorithms}
+\crefname{condition}{Condition}{Conditions}
+\Crefname{condition}{Condition}{Conditions}
+\crefname{line}{line}{lines}
+
 \crefalias{diagram}{equation}
@@
 
-\crefname{algocf}{Algorithm}{Algorithms}
-\Crefname{algocf}{Algorithm}{Algorithms}
-\crefname{condition}{Condition}{Conditions}
-\Crefname{condition}{Condition}{Conditions}
+\crefalias{formula}{equation}
+\crefname{formula}{Formula}{Formulas}
+\Crefname{formula}{Formula}{Formulas}
+\creflabelformat{formula}{#2\textup{(#1)}#3}
 
@@
 \makeatother
-\Crefname{algocf}{Algorithm}{Algorithms}
-\crefname{line}{line}{lines}
 
@@
 % to expect from section 5
+
+% TODO: (everywhere in the paper): emphasise that the experimental results show
+% Crane to be strictly more capable than ForcLift in a sense that it can solve
+% everything that ForcLift can and more (including instances beyond C^2).
 
@@
 theory~\cite{DBLP:conf/kr/BremenK21} and applications in enumerative
-combinatorics~\cite{DBLP:conf/ilp/BarvinekB0ZK21}. There is also a recent line
-of work that uses FOMC-based methods to count solutions to constraint
-satisfaction problems~\cite{DBLP:journals/jair/TotisDRK23}.
+combinatorics~\cite{DBLP:conf/ilp/BarvinekB0ZK21,DBLP:journals/corr/abs-2302-04606}.
+There is also a recent line of work that uses FOMC-based methods to count
+solutions to constraint satisfaction
+problems~\cite{DBLP:journals/jair/TotisDRK23}.
 
@@
 
-% Magician: an approach to improve the efficiency of sampling and local search
-% based MLN inference algorithms by utilising \#CSP algorithms. Tuffy: grounding
-% and stochastic local search.
-
 % 4. Why hasn't it been solved before? (Or, what's wrong with previous proposed
@@
 
-% TODO: must remove this footnote. Also, two more papers to mention:
-% 1. the L2C paper has the factorial example as well. But then why doesn't L2C work on it?
-% 2.
-cite the new paper "On Discovering Interesting Combinatorial Integer Sequences" as another example of computing n!
-using publicly unavailable code and as an example of applications to combinatorics
-However, none of the publicly available exact (W)FOMC algorithms can efficiently
-compute functions as simple as a factorial.\footnote{There is some previous work
-  discussing FOMC for
-  factorials~\cite{DBLP:journals/jair/Kuzelka21,DBLP:conf/kr/BremenK21,DBLP:conf/ijcai/Broeck16}.
-  One of them~\cite{DBLP:conf/ijcai/Broeck16} is an example `by hand' that does
-  not directly correspond to any algorithm.
-  Another~\cite{DBLP:journals/jair/Kuzelka21} proves that the problem is
-  liftable but contains no experimental results. The
-  third~\cite{DBLP:conf/kr/BremenK21} contains experimental results performed
-  with an algorithm that is not publicly available.} We claim that the
-capabilities of (W)FOMC algorithms can be significantly extended by empowering
-them with the ability to construct recursive solutions. The topic of recursion
-in the context of WFOMC has been studied before but in limited ways.
-Barv{\'{\i}}nek et al.~\shortcite{DBLP:conf/ilp/BarvinekB0ZK21} use WFOMC to
-generate numerical data that is then used to conjecture recurrence relations
-that explain that data. Van den Broeck~\shortcite{DBLP:conf/nips/Broeck11}
-introduced the idea of \emph{domain recursion}. Intuitively, domain recursion
-partitions a domain of size $n$ into a single explicitly named constant and the
-remaining domain of size $n-1$. However, many stringent conditions are enforced
-to ensure that the search for a tractable solution always terminates.
+% However, none of the publicly available exact (W)FOMC algorithms can efficiently
+% compute functions as simple as a factorial.\footnote{There is some previous work
+%   discussing FOMC for
+%   factorials~\cite{DBLP:journals/jair/Kuzelka21,DBLP:conf/kr/BremenK21,DBLP:conf/ijcai/Broeck16}.
+%   One of them~\cite{DBLP:conf/ijcai/Broeck16} is an example `by hand' that does
+%   not directly correspond to any algorithm.
+%   Another~\cite{DBLP:journals/jair/Kuzelka21} proves that the problem is
+%   liftable but contains no experimental results. The
+%   third~\cite{DBLP:conf/kr/BremenK21} contains experimental results performed
+%   with an algorithm that is not publicly available.}
+% Two more papers to mention:
+% 1. The L2C paper has the factorial example as well. But then why doesn't L2C
+% work on it?
+% 2. \cite{DBLP:journals/corr/abs-2302-04606} computes n! using publicly
+% unavailable code
+
+% TODO: add a different introductory problem statement
+We claim that the capabilities of (W)FOMC algorithms can be significantly
+extended by empowering them with the ability to construct recursive solutions.
+The topic of recursion in the context of WFOMC has been studied before but in
+limited ways. Barv{\'{\i}}nek et al.~\shortcite{DBLP:conf/ilp/BarvinekB0ZK21}
+use WFOMC to generate numerical data that is then used to conjecture recurrence
+relations that explain that data. Van den
+Broeck~\shortcite{DBLP:conf/nips/Broeck11} introduced the idea of \emph{domain
+  recursion}. Intuitively, domain recursion partitions a domain of size $n$ into
+a single explicitly named constant and the remaining domain of size $n-1$.
+However, many stringent conditions are enforced to ensure that the search for a
+tractable solution always terminates.
 
@@
 
-% TODO: c = (L, E, \delta), E - inequality constraints
 \begin{definition}[Clause]\label{def:clause}
   A \emph{clause}
-  is a triple $c = (L, C, \delta_c)$, where $L$ is a set of literals, $C$ is a
+  is a triple $c = (L, E, \delta_c)$, where $L$ is a set of literals, $E$ is a
   set of constraints, and $\delta_c$ is the domain map of $c$. Let $\Vars$ be
@@
   the set of variables in them. In particular,
-  $\Vars(c) \coloneqq \Vars(L) \cup \Vars(C)$. \emph{Domain map}
+  $\Vars(c) \coloneqq \Vars(L) \cup \Vars(E)$. \emph{Domain map}
   $\delta_{c}\colon \Vars(c) \to \mathcal{D}$ is a function that maps all
-  variables in $c$ to their domains such that (s.t.) if $(X, Y) \in C$ for some
+  variables in $c$ to their domains such that (s.t.) if $(X, Y) \in E$ for some
   variables $X$ and $Y$, then $\delta_c(X) = \delta_c(Y)$. For convenience, we
@@
 
-There are two major differences between
-\cref{def:constraint,def:clause,def:formula} and the corresponding concepts
-introduced by Van den Broeck et al.~\shortcite{DBLP:conf/ijcai/BroeckTMDR11}.
-First, we decouple variable-to-domain assignments from constraints and move them
-to a separate function $\delta_{c}$ in \cref{def:clause}. Second, while they
-allow for equality constraints and constraints of the form $X \not\in \Delta$
-for some variable $X$ and domain $\Delta$, we exclude such constraints simply
-because they are not needed. Moreover, note that Van den Broeck et
-al.~\shortcite{DBLP:conf/ijcai/BroeckTMDR11} refer to clauses and formulas as
-c-clauses and c-theories, respectively.
-% TODO: explain why we're not losing anything by dropping equality constraints
-% (e.g., X = Y). Answer: having two variables that are equal is the same thing
-% as having one variable (since by the definition of a clause, this equality can
-% only be at the beginning of a clause.
-
 One can read a formula in our format as a sentence in first-order logic. All
@@
 \cref{example:first} reads as
-\begin{align*}
+\begin{equation}\label[formula]{eq:formula}
+  \begin{split}
     &\begin{multlined}[t]
@@
     \end{multlined}
-\end{align*}
+  \end{split}
+\end{equation}
+
+There are two major differences between
+\cref{def:constraint,def:clause,def:formula} and the corresponding concepts
+introduced by Van den Broeck et
+al.~\shortcite{DBLP:conf/ijcai/BroeckTMDR11}.\footnote{Van den Broeck et
+  al.~\shortcite{DBLP:conf/ijcai/BroeckTMDR11} refer to clauses and formulas as
+  c-clauses and c-theories, respectively.} First, we decouple variable-to-domain
+assignments from constraints and move them to a separate function $\delta_{c}$
+in \cref{def:clause}. Second, while they allow for equality constraints and
+constraints of the form $X \not\in \Delta$ for some variable $X$ and domain
+$\Delta$, we exclude such constraints simply because they are not needed. Note
+that if, e.g., $Y \ne Z$ in \cref{eq:formula} is replaced by $Y = Z$, then
+\cref{eq:formula} can be simplified to have one fewer variables. Similarly, if
+the same inequality is replaced by $Y = c$ for some constant $c$, then $Y$ can
+be eliminated as well. Since constraints are always interpreted as preconditions
+for the disjunction of literals in the clause (as in \cref{eq:formula}),
+equality constraints can be eliminated without any loss in expressivity.
 
@@
 
-\section{From Circuits to Graphs}\label{sec:methods}
+\section{First-Order Computational Graphs}\label{sec:methods}
 
@@
 
-% TODO: the definition of FCG is hard to miss (highlight its importance, maybe
-% remind the reader later on in the paper)
-
-% TODO: instead of FO d-DNNF computational graph, say 'first-order computational
-% graph' (FOCG?)
-
-In this paper, we introduce \emph{FO d-DNNF computational graphs} (FCGs) that
+In this paper, we introduce \emph{first-order computational graphs} (FCGs) that
 generalise circuits by dispensing with acyclicity. Formally, an FCG is a (weakly
@@
     $x \gets \text{a new constant in domain } \Omega$\;\label{line:constant}
-    \ForEach{clause $c = (L, C, \delta) \in \phi$\label{line:forclause}}{
+    \ForEach{clause $c = (L, E, \delta) \in \phi$\label{line:forclause}}{
       $V \gets \{\, X \in \Vars(L) \mid \delta(X) = \Omega \,\}$\;\label{line:V}
-      \ForEach{$W \subseteq V$ s.t. $W^2 \cap C = \emptyset$ {\bf and} $W \cap \{\, X \in \Vars(C) \mid (X, y) \in C \text{ for some constant } y \,\} = \emptyset$\label{line:conditions}}{
+      \ForEach{$W \subseteq V$ s.t. $W^2 \cap E = \emptyset$ {\bf and} $W \cap \{\, X \in \Vars(E) \mid (X, y) \in E \text{ for some constant } y \,\} = \emptyset$\label{line:conditions}}{
         \tcc{$\delta'$ restricts $\delta$ to the new set of variables}
-        $\phi' \gets \phi' \cup \{\, (L[x/W], C[x/W] \cup \{\, (X, x) \mid (X \in V \setminus W) \,\}, \delta') \,\}$\;\label{line:generation}
+        $\phi' \gets \phi' \cup \{\, (L[x/W], E[x/W] \cup \{\, (X, x) \mid (X \in V \setminus W) \,\}, \delta') \,\}$\;\label{line:generation}
       }
@@
   unsatisfiable formulas. We impose two restrictions on $W$. First,
-  $W^2 \cap C = \emptyset$ ensures that there are no pairs of variables in $W$
+  $W^2 \cap E = \emptyset$ ensures that there are no pairs of variables in $W$
   that are constrained to be distinct, since that would result in an $x \ne x$
@@
 theorems, see supplementary material.
-% TODO (about the first sentence): say: this shows that there is no loss of
-% expressiveness/compilation completeness with our new algorithm. Would be nice
-% if you could also show formally how it has improved on Guy, e.g., Prop.
-% \exists formula \phi such that AlgoGuy(\phi) may fail but NewAlg(\phi) \ne
-% \emptyset. Therefore, our algorithms is `more' complete than Guy's
 
@@
   \emph{replaceable} if
-  \begin{itemize}
-    \item $x$ does not occur in any literal of any clause of $\phi$,
-    \item and for each clause $c = (L, C, \delta_c) \in \phi$ and variable
-          $X \in \Vars(c)$, either $\delta_c(X) \ne \Omega$ or $(X, x) \in C$.
-  \end{itemize}
+  \begin{enumerate*}[label=(\roman*)]
+    \item $x$ does not occur in any literal of any clause of $\phi$, and
+    \item for each clause $c = (L, E, \delta_c) \in \phi$ and variable
+    $X \in \Vars(c)$, either $\delta_c(X) \ne \Omega$ or $(X, x) \in E$.
+  \end{enumerate*}
 \end{definition}
@@
     $\phi' \gets \emptyset$\;
-    \ForEach{clause $(L, C, \delta) \in \phi$}{
-      $C' \gets \{\, (a, b) \in C \mid b \ne x \,\}$\;\label{line:constraintremoval}
+    \ForEach{clause $(L, E, \delta) \in \phi$}{
+      $E' \gets \{\, (a, b) \in E \mid b \ne x \,\}$\;\label{line:constraintremoval}
       \nosemic$\delta' \gets X \mapsto
@@
       \end{cases}$\;\label{line:newdelta}
-      $\phi' \gets \phi' \cup \{\, (L, C', \delta') \,\}$\;
+      $\phi' \gets \phi' \cup \{\, (L, E', \delta') \,\}$\;
     }
@@
 \end{theorem}
-% TODO: Does this have analogue in Guy? If yes, explain difference. If no,
-% emphasize this point. Same for Theorem 3.
+
+There is no analogue to $\CR$ in previous work on first-order knowledge
+compilation. $\CR$ plays a key role by recognising when the constraints of a
+formula essentially reduce the size of a domain by one and extracting this
+observation into the definition of a new domain. This then allows us to relate
+maps between sets of domains to the arguments of a function call.
+\Cref{sec:ref,sec:interpret} describe this process.
 
@@
 different for recursion to work. The hash code of a clause
-$c = (L, C, \delta_{c})$ (denoted by $\# c$) combines the hash codes of the sets
+$c = (L, E, \delta_{c})$ (denoted by $\# c$) combines the hash codes of the sets
 of constants and predicates in $c$, the numbers of positive and negative
-literals, the number of inequality constraints $|C|$, and the number of
+literals, the number of inequality constraints $|E|$, and the number of
 variables $|\Vars(c)|$. The hash code of a formula $\phi$ combines the hash
@@
 
+As \textsc{ForcLift} only supports $\Reff$ nodes for when the two formulas are
+equal, our approach is significantly more general and can even construct more
+complex recursive calls such as $f(n-k-2)$.
+
 \section{Converting FCGs to Function Definitions}\label{sec:interpret}
@@
         $n-l$).
-  \item For each node $v$, let $\mathfrak{D}(v)$ denote the (precomputed) set of
-        domains, the sizes of which we would use as parameters if we were to
-        define a function that begins at $v$. This set is computed by
+  \item We assume a fixed total ordering of all domains names. In particular, in
+        our running example we assume that $\Gamma$ goes before $\Delta$.
+  \item For each node $v$, let $\mathfrak{D}(v)$ denote the (precomputed) list
+        of domains, the sizes of which we would use as parameters if we were to
+        define a function that begins at $v$. As a set, it is computed by
         iteratively setting
         $\mathfrak{D}(v) \gets \left(\bigcup_{u} \mathfrak{D}(u) \setminus I_{v}\right) \cup U_{v}$
-        until convergence, where
-        \begin{itemize}
-          \item $u$ is any direct successor of $v$,
+        until convergence, where:
+        \begin{enumerate*}[label=(\roman*)]
+          \item the union is over all direct successors of $v$,
           \item $I_{v}$ is the set of domains \emph{introduced} at node $v$, and
           \item $U_{v}$ is the set of domains \emph{used} by $v$.
-        \end{itemize}
-  \item We assume a fixed total ordering of all domains names. In particular, in
-        our running example we assume that $\Gamma$ goes before $\Delta$.
+        \end{enumerate*}
+        The set is then sorted according to the fixed ordering of domains.
   \item $\mathsf{F}$ is a partial map from the set of FCG nodes to function
         names (e.g., $f$, $g$).
-  \item \newVariableName just generates a unique identifier for a variable
-  \item \newFunctionName does the same thing for function names and also records
-        the new name in $\mathsf{F}$
-  \item The first function in the list is the main one.
+  \item Functions \newVariableName and \newFunctionName generate
+        previously-unused names for variables and functions, respectively. The
+        latter also records the new name in $\mathsf{F}$.
   \item Note that a node is a direct successor of a $\Reff$ node if and only if
@@
         were created while constructing $\mathsf{e}$.
-  \item TODO: $\mathfrak{D}$ must be a list. That's the ordering of domain names
-        comes in, not in list comprehensions.
 \end{itemize}
@@
   \cref{line:initialcall,line:initialcalltwo} discard the function call
-  expression and return the definition of $f$.
-
-  Therefore,
+  expression and return the definition of $f$. Therefore,
   \begin{align}
@@
 % determine)
-% TODO: Must do one of these:
-% 1. determine the complexity of the counting quantifiers algorithm when run on
-% these instances
-% 2. find instances that are not in C^2 and make the paper about them
-% 3. run the counting quantifiers algorithm on these instances with increasing
-% domain sizes, statistically estimating the degree of the polynomial and
-% juxtaposing it with my complexity results shifted to overlap as much as
-% possible
 % TODO: describe ternary.mln as an example instance that's not in C^2 that can
@@
     \rowcolor{gray!25}\cmark/\xmark & \cmark/\xmark & Functions & $\log m$ & $m$ & $m$ \\
-    \xmark & \xmark & \multirow{4}{*}{Surjections} & $n \log m$ & $m^{3}+n^{3}$ & $m^{3}+n^{3}$ \\
+    \xmark & \xmark & \multirow{2}{*}{Surjections} & $n \log m$ & $m^{3}+n^{3}$ & $m^{3}+n^{3}$ \\
     \xmark & \cmark & & $m \log m$ & $m^{3}$ & $m^{3}$ \\
-    \cmark & \xmark & & \multicolumn{3}{c}{Same as injections from $\Delta$ to $\Gamma$} \\
-    \cmark & \cmark & & \multicolumn{3}{c}{Same as endo-injections} \\
     \rowcolor{gray!25}\xmark & \xmark & & $m$ & --- & $mn$ \\
@@
     \rowcolor{gray!25}\cmark & \cmark & \multirow{-4}{*}{Injections} & $m^2$ & --- & --- \\
-    \xmark & \xmark & \multirow{3}{*}{Bijections} & $m$ & --- & $m$ \\
-    \xmark & \cmark & & \multicolumn{3}{c}{\multirow{2}{*}{Same as (partial) (endo-)injections}} \\
-    \cmark & \cmark/\xmark & & \multicolumn{3}{c}{} \\
+    \xmark & \xmark & Bijections & $m$ & --- & $m$ \\
     \bottomrule
@@
 
-% TODO: remove the rows that say 'same as..', putting the explanation about them
-% in text. And don't say 'same as', instead say that the formulas are in some
-% sence equivalent (maybe in a stronger sense than the usual equivalence).
+% TODO: Explain (in text) why there are fewer than 16 rows in the table. And
+% don't say 'same as', instead say that the formulas are in some sense
+% equivalent (maybe in a stronger sense than the usual equivalence).
 
 % TODO: emphasise that the reader should focus on the last two columns
-% TODO: the last sentence of the caption could be confusing
+% TODO: the caption sentence about not finding a solution could be confusing
 % TODO: 'best known' sounds disappointing. Find a better alternative.
@@
 to restrict $\texttt{p}$ to injections or
-\[
-  \forall Y \in \Delta\text{. }\exists X \in \Gamma\text{. }\texttt{p}(X, Y)
-\]
+  $\forall Y \in \Delta\text{. }\exists X \in \Gamma\text{. }\texttt{p}(X, Y)$
 to ensure surjectivity or remove \cref{eq:def2} to consider partial functions.
@@
 AI~\cite{DBLP:series/synthesis/2016Raedt}, \textsc{Crane} could be beneficial to
-research in combinatorics as well~\cite{DBLP:conf/ilp/BarvinekB0ZK21}.
+research in combinatorics as
+well~\cite{DBLP:conf/ilp/BarvinekB0ZK21,DBLP:journals/corr/abs-2302-04606}.
 

### 2023-03-02 doc/paper/paper.tex
Clean up the Preliminaries

@@
 \newcommand\mdoubleplus{\mathbin{+\mkern-10mu+}}
-\newcommand{\Vone}{\mathsf{V}_{1}}
-\newcommand{\Vtwo}{\mathsf{V}_{2}}
-\newcommand{\Vthree}{\mathsf{V}_{3}}
+\newcommand{\Done}{\mathsf{D}_{1}}
+\newcommand{\Dtwo}{\mathsf{D}_{2}}
+\newcommand{\Dthree}{\mathsf{D}_{3}}
 
@@
   First-order model counting (FOMC) is a computational problem that asks to
-  count the models of a sentence in finite-domain first-order logic. Despite
-  being around for more than a decade, practical FOMC algorithms are still
-  unable to compute functions as simple as a factorial. We argue that the
-  capabilities of FOMC algorithms to date are limited by their inability to
-  express arbitrary recursive computations. To enable arbitrary recursion, we
-  relax the restrictions that typically accompany domain recursion and
-  generalise circuits used to express a solution to an FOMC problem to graphs
-  that may contain cycles. To this end, we enhance the most well-established
-  (weighted) FOMC algorithm \textsc{ForcLift} with new compilation rules and an
-  algorithm to check whether a recursive call is feasible. These improvements
-  allow the algorithm to construct efficient solutions to counting fundamental
-  structures such as injections and bijections. We end with a few conjectures on
-  what classes of instances could be liftable as a result.
+  count the models of a sentence in finite-domain first-order logic. In this
+  paper, we argue that the capabilities of FOMC algorithms to date are limited
+  by their inability to express many types of recursive computations. To enable
+  such computations, we relax the restrictions that typically accompany domain
+  recursion and generalise the circuits used to express a solution to an FOMC
+  problem to directed graphs that may contain cycles. To this end, we adapt the
+  most well-established (weighted) FOMC algorithm \textsc{ForcLift} to work with
+  such graphs and introduce new compilation rules that can create cycle-inducing
+  edges that encode recursive function calls. These improvements allow the
+  algorithm to find efficient solutions to counting problems that were
+  previously beyond its reach, including those that cannot be solved efficiently
+  by any other exact FOMC algorithm. We end with a few conjectures on what
+  classes of instances could be domain-liftable as a result.
 \end{abstract}
 
-% TODO: I found the choice for what goes into a footnote and what doesn't rather
-% inconsistent, which made it a bit irritating to read for me. Maybe review if
-% the current use of footnotes is really necessary and helpful?
+% KEYWORDS:
+% model counting
+% first-order logic
+% recursion
+% knowledge compilation
+
+% TOPICS:
+% KR & ML: probabilistic reasoning and learning
+% KR & ML: statistical relational learning
+% (no) computational aspects of knowledge representation
+% (no) knowledge representation languages
+% (no) KR & ML: graphical models for knowledge representation and reasoning
 
@@
 
-% TODO: Maybe some of the info from the preliminaries is redundant now that I've
-% moved the proofs elsewhere?
-
-% TODO: I find the writing mostly clear, but the structure of the Preliminaries
-% somewhat confusing. It starts with some notation, then some definitions, then
-% suddenly a paragraph titled "Notation", and so on. Maybe see if you can
-% rearrange some things and/or add some (more) helpful paragraph titles?
-
 Our representation of FOMC instances is largely based on the format used
@@
 
+We use $\langle\cdot\rangle$ to denote lists, $|\cdot|$ for the length of a
+list, and $\mdoubleplus$ for list concatenation. We write $\pfun$ to denote
+partial functions and $\dom(\cdot)$ for the domain of a function. Let $\Doms$ be
+the function that maps any clause or formula to the set of domains used within.
+Similarly, let $\Vars$ be the function that maps clauses and sets of either
+literals or constraints to the set of variables in them. Let $S$ be a set of
+constraints or literals, $V$ a set of variables, and $x$ a variable or a
+constant. We write $S[x/V]$ to denote $S$ with all occurrences of all variables
+in $V$ replaced with $x$.
+
 \begin{definition}[Constraint]\label{def:constraint}
@@
 \begin{definition}[Clause]\label{def:clause}
-  A \emph{clause}
-  is a triple $c = (L, E, \delta_c)$, where $L$ is a set of literals, $E$ is a
-  set of constraints, and $\delta_c$ is the domain map of $c$. Let $\Vars$ be
-  the function that maps clauses and sets of either literals or constraints to
-  the set of variables in them. In particular,
-  $\Vars(c) \coloneqq \Vars(L) \cup \Vars(E)$. \emph{Domain map}
-  $\delta_{c}\colon \Vars(c) \to \mathcal{D}$ is a function that maps all
-  variables in $c$ to their domains such that (s.t.) if $(X, Y) \in E$ for some
-  variables $X$ and $Y$, then $\delta_c(X) = \delta_c(Y)$. For convenience, we
-  sometimes write $\delta_c$ for the domain map of $c$ without unpacking $c$
-  into its three constituents.
+  A \emph{clause} is a triple $c = (L, E, \delta_c)$, where $L$ is a set of
+  literals, $E$ is a set of constraints, and $\delta_c$ is the domain map.
+  \emph{Domain map} $\delta_{c}\colon \Vars(c) \to \mathcal{D}$ is a function
+  that maps all variables in $c$ to their domains such that (s.t.) if
+  $(X, Y) \in E$ for some variables $X$ and $Y$, then
+  $\delta_c(X) = \delta_c(Y)$. For convenience, we sometimes write $\delta_c$
+  for the domain map of $c$ without unpacking $c$ into its three constituents.
 \end{definition}
-
-% TODO: The first paragraph already introduced some notation.
-\paragraph{Notation.}
-For any set $S$, let $2^{S}$ denote its power set and
-$S^{\ast} \coloneqq \bigcup_{i=0}^{\infty} S^{i}$ the set of tuples of any
-finite length of elements of $S$. For example,
-$\{\,a, b\,\}^{\ast} = \{\, (), (a), (b), (a, a), \dots \,\}$. For any
-$n \in \mathbb{N}_{0}$, let $[n] \coloneqq \{\, 1, \dots, n \,\}$, e.g.,
-$[0] = \emptyset$, and $[2] = \{\, 1, 2 \,\}$. We write $\langle\rangle$ for an
-empty list, $\langle x \rangle$ for a list with one element $x$, $|l|$ for the
-length of list $l$, $\mdoubleplus$ for list concatenation, and $\pfun$ to denote
-partial functions. Let $S$ be a set of constraints or literals, $V$ a set of
-variables, and $x$ a variable or a constant. We write $S[x/V]$ to denote $S$
-with all occurrences of all variables in $V$ replaced with $x$. Let $\Doms$
-(respectively, $\Preds$) be the function that maps any clause or formula to the
-set of domains (respectively, predicates) used within, and let $\dom(f)$ denote
-the domain of function $f$.
 
@@
   A \emph{formula} is a set of clauses s.t.\ all constraints and atoms `type
-  check' with respect to domains. Each formula $\phi$ has a map
-  $\pi_{\phi}\colon \Preds(\phi) \to {\Doms(\phi)}^{\ast}$ such that, for each
-  predicate $\texttt{p}/n \in \Preds(\phi)$, we have that
-  $\pi_{\phi}(\texttt{p}) \in {\Doms(\phi)}^{n}$.
+  check' with respect to domains.
 \end{definition}
-
-\begin{remark}
-  Constants are also mapped to domains, although we keep this mapping implicit.
-\end{remark}
 
@@
   for some predicate $\texttt{p}/2$, variables $X$, $Y$, $Z$, and domains
-  $\Gamma$ and $\Delta$. Based on $\delta_{c_{1}}$ and $\delta_{c_{2}}$, we can
-  infer that $\pi_{\phi} = \{\, \texttt{p} \mapsto (\Gamma, \Delta) \,\}$. All
-  variables that occur as the first argument to $\texttt{p}$ are in $\Gamma$,
-  and, likewise, all variables that occur as the second argument to $\texttt{p}$
-  are in $\Delta$. Therefore, $\phi$ `type checks' as a valid formula.
+  $\Gamma$ and $\Delta$. All variables that occur as the first argument to
+  $\texttt{p}$ are in $\Gamma$, and, likewise, all variables that occur as the
+  second argument to $\texttt{p}$ are in $\Delta$. Therefore, $\phi$ `type
+  checks' as a valid formula.
 \end{example}
@@
 
-% TODO: the first sentence comes out of nowhere
-Once domains are mapped to finite sets and constants to elements in those sets,
-a formula can be viewed as a set of conditions that the predicates (interpreted
-as relations) have to satisfy. Hence, FOMC is the problem of counting the number
-of combinations of relations that satisfy these conditions.
-
 \begin{example}\label{example:simple}
@@
 
-To formalise the idea of a model, let
-$\sigma\colon \mathcal{D} \to \mathbb{N}_{0}$ be the \emph{domain size function}
-that maps each domain to a non-negative integer.
-
-\begin{definition}\label{def:model}
-  Let $\phi$ be a formula and $\sigma$ a domain size function. A \emph{model} of
-  $(\phi, \sigma)$ is a map
-  $\mathfrak{M}\colon \Preds(\phi) \to 2^{\mathbb{N}_{0}^{\ast}}$ s.t.\ the
-  following two conditions are satisfied.
-  \begin{enumerate}
-    \item Let $\texttt{p}/n \in \Preds(\phi)$ be a predicate and let
-          $\pi_{\phi}(\texttt{p}) = {(d_{i})}_{i=1}^{n}$ for some domains
-          $d_{i} \in \Doms(\phi)$. Then
-          \begin{equation}\label{eq:subset}
-            \mathfrak{M}(\texttt{p}) \subseteq \prod_{i=1}^{n}[\sigma(d_{i})].\footnote{For simplicity, \cref{def:model} ignores constants.
-To include constants, one would replace $[\sigma(d_{i})]$ with a set that contains all constants associated with domain $d_{i}$, extended with enough new elements to make its cardinality $\sigma(d_{i})$.}
-          \end{equation}
-    \item As a collection of relations, $\mathfrak{M}$ satisfies $\phi$.
-    \begin{itemize}
-      \item TODO: introduce the substitution for formulas, moving the definition from elsewhere
-      \item define inductively as...
-      \item (not exhaustive)
-      \item $\mathfrak{M} \models \phi \land \psi$ iff $\mathfrak{M} \models \phi$ and $\mathfrak{M} \models \psi$
-      \item $\mathfrak{M} \models \phi \lor \psi$ iff $\mathfrak{M} \models \phi$ or $\mathfrak{M} \models \psi$
-      \item $\mathfrak{M} \models \neg\phi$ iff $\mathfrak{M} \not\models \phi$
-      \item $\mathfrak{M} \models (\forall X \in \Delta\text{. }\phi)$ iff $\mathfrak{M} \models \phi[x/\{\, X \,\}]$ for all $x \in \Delta$
-      \item One can then add inequality constraints to the semantics as follows
-      \item $\mathfrak{M} \models (\forall X \in \Delta\text{. } X \ne c \Rightarrow \phi)$ iff $\mathfrak{M} \models \phi[x/\{\, X \,\}]$ for all $x \in \Delta \setminus \{\, c \,\}$
-      \item $\mathfrak{M} \models (\forall X,Y \in \Delta\text{. } X \ne Y \Rightarrow \phi)$ iff $\mathfrak{M} \models \phi[x/\{\, X \,\}][y/\{\, Y \,\}]$ for all $x,y \in \Delta$ such that $x \ne y$
-    \end{itemize}
-  \end{enumerate}
-\end{definition}
-
-% TODO: make the relations more concrete
+The model count of a formula $\phi$ also depends on the sizes of the domains in
+$\phi$. Let $\sigma\colon \mathcal{D} \to \mathbb{N}_{0}$ be the \emph{domain
+  size function} that maps each domain to a non-negative integer.
+
 \begin{example}
   Let $\phi$ be as in \cref{example:first} and let
-  $\sigma(\Gamma) = \sigma(\Delta) = 2$. Then the right-hand side of
-  \cref{eq:subset} becomes
-  \[
-    [\sigma(\Gamma)] \times [\sigma(\Delta)] = [2] \times [2] = \{\,(1, 1), (1, 2), (2, 1), (2, 2)\,\}
-  \]
-  There are $2^{4} = 16$ possible relations between $\Gamma$ and $\Delta$. Let
-  us count how many of them satisfy the conditions imposed on predicate
-  $\texttt{p}$. The empty relation does. All four relations of cardinality one
-  do too. Finally, there are two relations of cardinality two that satisfy the
-  conditions as well. Thus, the FOMC of $(\phi, \sigma)$ is 7. Incidentally, it
-  counts partial injections. We will continue to use the problem of counting
-  partial injections (and the formula from \cref{example:first} specifically) as
-  the main running example throughout the paper.
+  $\Gamma = \Delta = \{\,1, 2\,\}$, i.e., $\sigma(\Gamma) = \sigma(\Delta) = 2$.
+  There are $2^{2 \times 2} = 16$ possible relations between $\Gamma$ and
+  $\Delta$. Let us count how many of them satisfy the conditions imposed on
+  predicate $\texttt{p}$. The empty relation does. All four relations of
+  cardinality one (e.g., $\{\, (1, 1) \,\}$) do too. Finally, there are two
+  relations of cardinality two ($\{\, (1, 1), (2, 2) \,\}$ and
+  $\{\, (1, 2), (2, 1) \,\}$) that satisfy the conditions as well. Thus, the
+  FOMC of $(\phi, \sigma)$ is 7. Incidentally, the FOMC of $\phi$ counts partial
+  injections from $\Gamma$ to $\Delta$. We will continue to use the problem of
+  counting partial injections (and the formula from \cref{example:first}
+  specifically) as the main running example.
 \end{example}
@@
   \SetKwData{functionNames}{F}
-  \SetKwData{variableNames}{V}
-  \SetKwData{newVariableNames}{V'}
+  \SetKwData{domainNames}{D}
+  \SetKwData{newDomainNames}{D'}
   \SetKwData{expression}{e}
@@
   \SetKwFunction{newFunctionName}{newFunctionName}
-  \SetKwFunction{newVariableName}{newVarName}
+  \SetKwFunction{newDomainName}{newDomainName}
   \SetKwFunction{visit}{v}
@@
   \KwOut{a list of function definitions}
-  $\variableNames \gets \{\, \Omega \mapsto \newVariableName{} \mid \Omega \in \mathcal{D} \,\}$\;\label{line:varnames}
+  $\domainNames \gets \{\, \Omega \mapsto \newDomainName{} \mid \Omega \in \mathcal{D} \,\}$\;\label{line:varnames}
   \If{$s$ is a direct successor of a $\Reff$ node}{
-    $(\expression, \functions) \gets \visit{$s$, $\variableNames$}$\;\label{line:initialcall}
+    $(\expression, \functions) \gets \visit{$s$, $\domainNames$}$\;\label{line:initialcall}
     \Return{\functions}\;\label{line:initialcalltwo}
@@
   $f \gets \newFunctionName{$s$}$\;
-  $(\expression, \functions) \gets \visit{$s$, $\variableNames$}$\;
-  \Return{$\langle f(\langle \variableNames{$\Omega$} \mid \Omega \in \mathcal{D} \rangle) = \expression \rangle \mdoubleplus \functions$}\;
-  \Fn{\visit{node $v$, variable names \variableNames}}{
+  $(\expression, \functions) \gets \visit{$s$, $\domainNames$}$\;
+  \Return{$\langle f(\langle \domainNames{$\Omega$} \mid \Omega \in \mathcal{D} \rangle) = \expression \rangle \mdoubleplus \functions$}\;
+  \Fn{\visit{node $v$, domain names \domainNames}}{
     \If{$v$ is \textbf{not} a direct successor of a $\Reff$ node}{
-      \Return{\actuallyVisit{$v$, \variableNames}}\;
+      \Return{\actuallyVisit{$v$, \domainNames}}\;
     }
     $f \gets \newFunctionName{$v$}$\;
-    $\newVariableNames \gets \variableNames$\;
-    \For{$\Omega \in \mathfrak{D}(v)$ s.t. $\newVariableNames(\Omega)$ is non-atomic}{\label{line:nonone}
-      $\newVariableNames(\Omega) \gets \newVariableName{}$\;\label{line:nontwo}
-    }
-    $(\expression, \functions) \gets \actuallyVisit{$v$, \newVariableNames}$\;\label{line:actuallyvisit}
-    $\functionCall \gets f(\langle \variableNames{$\Omega$} \mid \Omega \in \mathfrak{D}(v) \rangle)$\;
-    $\functionSignature \gets f(\langle \newVariableNames{$\Omega$} \mid \Omega \in \mathfrak{D}(v) \rangle)$\;
+    $\newDomainNames \gets \domainNames$\;
+    \For{$\Omega \in \mathfrak{D}(v)$ s.t. $\newDomainNames(\Omega)$ is non-atomic}{\label{line:nonone}
+      $\newDomainNames(\Omega) \gets \newDomainName{}$\;\label{line:nontwo}
+    }
+    $(\expression, \functions) \gets \actuallyVisit{$v$, \newDomainNames}$\;\label{line:actuallyvisit}
+    $\functionCall \gets f(\langle \domainNames{$\Omega$} \mid \Omega \in \mathfrak{D}(v) \rangle)$\;
+    $\functionSignature \gets f(\langle \newDomainNames{$\Omega$} \mid \Omega \in \mathfrak{D}(v) \rangle)$\;
     \Return{$(\functionCall, \langle \functionSignature = \expression \rangle \mdoubleplus \functions)$}\;
   }
-  \Fn{\actuallyVisit{node $v$, variable names \variableNames}}{
+  \Fn{\actuallyVisit{node $v$, domain names \domainNames}}{
     \Switch{label of $v$}{
-      \lCase{$\GDR(v')$}{\Return{\visit{$v'$, \variableNames}}}
+      \lCase{$\GDR(v')$}{\Return{\visit{$v'$, \domainNames}}}
       \uCase{$\CR_{\Omega \mapsto \Omega'}(v')$}{
-        \Return{\visit{$v'$, $\variableNames \cup \{\, \Omega' \mapsto (\variableNames(\Omega) - 1) \,\}$}}\;\label{line:cr}
+        \Return{\visit{$v'$, $\domainNames \cup \{\, \Omega' \mapsto (\domainNames(\Omega) - 1) \,\}$}}\;\label{line:cr}
       }
       \uCase{$\Reff_{\rho}(v')$}{
-        $\args \gets \langle \variableNames\circ\rho(\Omega) \mid \Omega \in \mathfrak{D}(v') \rangle$\;\label{line:args}
+        $\args \gets \langle \domainNames\circ\rho(\Omega) \mid \Omega \in \mathfrak{D}(v') \rangle$\;\label{line:args}
         \Return{$(\functionNames{$v'$}(\args), \langle \rangle)$}\;
@@
 \begin{itemize}
-  \item TODO: is maybe `parameter name' (or something similar) would be more
-        appropriate than `variable name'?
-  \item We call a variable name is \emph{atomic} if it is free of subtraction
-        (e.g., $m$, $n$); otherwise it is \emph{non-atomic} (e.g., $m-1$,
-        $n-l$).
-  \item We assume a fixed total ordering of all domains names. In particular, in
-        our running example we assume that $\Gamma$ goes before $\Delta$.
+  \item We call a domain name \emph{atomic} if it is free of subtraction (e.g.,
+        $m$, $n$); otherwise it is \emph{non-atomic} (e.g., $m-1$, $n-l$).
+  \item We assume a fixed total ordering of all domains. In particular, in our
+        running example we assume that $\Gamma$ goes before $\Delta$.
   \item For each node $v$, let $\mathfrak{D}(v)$ denote the (precomputed) list
@@
         names (e.g., $f$, $g$).
-  \item Functions \newVariableName and \newFunctionName generate
-        previously-unused names for variables and functions, respectively. The
-        latter also records the new name in $\mathsf{F}$.
+  \item Functions \newDomainName and \newFunctionName both generate
+        previously-unused names. The latter also records the new name in
+        $\mathsf{F}$.
   \item Note that a node is a direct successor of a $\Reff$ node if and only if
         it has an in-degree greater than one.
-  \item For simplicity, we refer to FCG nodes using their types.
   \item The algorithm consists of two main functions: \visit and \actuallyVisit.
@@
 types. The interpretation of a $\CR$ or a $\GDR$ node is simply the
-interpretation of its only direct successor. Obviously, $\star$ nodes have no
-interpretation as incomplete FCGs are not meant to be interpreted. The
-interpretation of a $\Reff$ node is a function call. The direct successor of the
-$\Reff$ node (say, $v$) then must introduce a function. The parameters of this
-function are the sizes of all domains used by nodes reachable from $v$.
+interpretation of its only direct successor. The interpretation of a $\Reff$
+node is a function call. The direct successor of the $\Reff$ node (say, $v$)
+then must introduce a function. The parameters of this function are the sizes of
+all domains used by nodes reachable from $v$.
 
@@
     \text{\Cref{alg:interpretation}} \ar[d] \ar[u, swap, shift right=0.7ex, "{\left\langle f(m, n) = \sum_{l=0}^{n}[l<2]f(m-1,n-l) \right\rangle}"] & \\
-    \visit{$\GDR$, $\Vone$} \ar[d] \ar[u, swap, shift right=0.7ex, "\left({f(m, n), \left\langle f(m, n) = \sum_{l=0}^{n}[l<2]f(m-1,n-l) \right\rangle}\right)"] & \\
-    \actuallyVisit{$\GDR$, $\Vone$} \ar[d] \ar[u, swap, shift right=0.7ex, "\left({\sum_{l=0}^{n}[l<2]f(m-1,n-l), \langle\rangle}\right)"] & \\
-    \visit/\actuallyVisit{$\bigvee$, $\Vone$} \ar[d] \ar[u, swap, shift right=0.7ex, "\left({\sum_{l=0}^{n}[l<2]f(m-1,n-l), \langle\rangle}\right)"] & \\
-    \visit/\actuallyVisit{$\CR$, $\Vtwo$} \ar[d] \ar[u, swap, shift right=0.7ex, "\left({[l<2]f(m-1,n-l), \langle\rangle}\right)"] & \\
-    \visit/\actuallyVisit{$\land$, $\Vthree$} \ar[d] \ar[dr] \ar[u, swap, shift right=0.7ex, "\left({[l<2]f(m-1,n-l), \langle\rangle}\right)"] & \\
-    \visit/\actuallyVisit{$\bot$, $\Vthree$} \ar[u, swap, shift right=0.7ex, "\left({[l<2], \langle\rangle}\right)"] & \visit/\actuallyVisit{$\Reff$, $\Vthree$} \ar[ul, swap, shift right=0.7ex, "\left({f(m-1, n-l), \langle\rangle}\right)"]
+    \visit{$\GDR$, $\Done$} \ar[d] \ar[u, swap, shift right=0.7ex, "\left({f(m, n), \left\langle f(m, n) = \sum_{l=0}^{n}[l<2]f(m-1,n-l) \right\rangle}\right)"] & \\
+    \actuallyVisit{$\GDR$, $\Done$} \ar[d] \ar[u, swap, shift right=0.7ex, "\left({\sum_{l=0}^{n}[l<2]f(m-1,n-l), \langle\rangle}\right)"] & \\
+    \visit/\actuallyVisit{$\bigvee$, $\Done$} \ar[d] \ar[u, swap, shift right=0.7ex, "\left({\sum_{l=0}^{n}[l<2]f(m-1,n-l), \langle\rangle}\right)"] & \\
+    \visit/\actuallyVisit{$\CR$, $\Dtwo$} \ar[d] \ar[u, swap, shift right=0.7ex, "\left({[l<2]f(m-1,n-l), \langle\rangle}\right)"] & \\
+    \visit/\actuallyVisit{$\land$, $\Dthree$} \ar[d] \ar[dr] \ar[u, swap, shift right=0.7ex, "\left({[l<2]f(m-1,n-l), \langle\rangle}\right)"] & \\
+    \visit/\actuallyVisit{$\bot$, $\Dthree$} \ar[u, swap, shift right=0.7ex, "\left({[l<2], \langle\rangle}\right)"] & \visit/\actuallyVisit{$\Reff$, $\Dthree$} \ar[ul, swap, shift right=0.7ex, "\left({f(m-1, n-l), \langle\rangle}\right)"]
   \end{tikzcd}
   \caption{Function calls and their return values when \cref{alg:interpretation}
-    is run on the FCG from \cref{fig:examplefcg}. When \protect\visit calls
-    \protect\actuallyVisit and returns its output unchanged, the two function
-    calls are shortened as a single call to
-    $\protect\visit/\protect\actuallyVisit$. TODO: this last sentence should be
-    explained in text.}\label{fig:functioncalls}
+    is run on the FCG from \cref{fig:examplefcg}.}\label{fig:functioncalls} % TODO: do I need a dot?
 \end{figure}
 
+% TODO: examine the order in which everything is introduced
 \begin{example}\label{example:interpretation}
   Let us see how \cref{alg:interpretation} handles the FCG from
-  \cref{fig:examplefcg}. Here, $\mathcal{D} = \{\, \Gamma, \Delta \,\}$. Let
-  $\Vone \coloneqq \{\, \Gamma \mapsto m, \Delta \mapsto n \,\}$,
-  $\Vtwo \coloneqq \Vone \cup \{\, \Delta^{\top} \mapsto l, \Delta^{\bot} \mapsto (n-l) \,\}$,
-  and $\Vthree \coloneqq \Vtwo \cup \{\, \Gamma' \mapsto (m-1) \,\}$ denote
-  versions of $\mathsf{V}$ at various points throughout the algorithm's
-  execution. Here, $l$, $m$, and $n$ are all arbitrary variable names generated
-  by \newVariableName. \Cref{line:varnames} initialises $\mathsf{V}$ to $\Vone$.
+  \cref{fig:examplefcg}. In this case, $\mathcal{D} = \{\, \Gamma, \Delta \,\}$.
+  Let $\Done \coloneqq \{\, \Gamma \mapsto m, \Delta \mapsto n \,\}$,
+  $\Dtwo \coloneqq \Done \cup \{\, \Delta^{\top} \mapsto l, \Delta^{\bot} \mapsto (n-l) \,\}$,
+  and $\Dthree \coloneqq \Dtwo \cup \{\, \Gamma' \mapsto (m-1) \,\}$ denote
+  versions of $\mathsf{D}$ at various points throughout the algorithm's
+  execution. Here, $l$, $m$, and $n$ are all arbitrary names generated by
+  \newDomainName.
 
   \Cref{fig:functioncalls} shows the outline of function calls and their return
-  values. Once \visit{$\GDR$, $\Vone$} is called on \cref{line:initialcall},
-  \newFunctionName updates $\mathsf{F}$ to $\{\, \GDR \mapsto f \,\}$, where $f$
-  is a new function name. There are no non-atomic names in $\Vone$, so
-  \cref{line:nonone,line:nontwo} are skipped, and calls to
-  \actuallyVisit{$\GDR$, $\Vone$} and
-  $\visit/\actuallyVisit{$\bigvee$, $\Vone$}$ follow. Here, $\Vone$ becomes
-  $\Vtwo$, i.e., the $\bigvee$ node introduces two domains $\Delta^{\top}$ and
+  values. For simplicity, we refer to FCG nodes by their types. When \visit
+  calls \actuallyVisit and returns its output unchanged, the two function calls
+  are shortened as a single call to $\visit/\actuallyVisit$.
+
+  \Cref{line:varnames} initialises $\mathsf{D}$ to $\Done$. Once \visit{$\GDR$,
+    $\Done$} is called on \cref{line:initialcall}, \newFunctionName updates
+  $\mathsf{F}$ to $\{\, \GDR \mapsto f \,\}$, where $f$ is a new function name.
+  There are no non-atomic names in $\Done$, so \cref{line:nonone,line:nontwo}
+  are skipped, and calls to \actuallyVisit{$\GDR$, $\Done$} and
+  $\visit/\actuallyVisit{$\bigvee$, $\Done$}$ follow. Here, $\Done$ becomes
+  $\Dtwo$, i.e., the $\bigvee$ node introduces two domains $\Delta^{\top}$ and
   $\Delta^{\bot}$ that `partition' $\Delta$, i.e.,
-  $\Vtwo(\Delta^{\top}) + \Vtwo(\Delta^{\bot}) = l + (n-l) = n = \Vtwo(\Delta)$.
-  Similarly, \actuallyVisit{$\CR$, $\Vtwo$} on \cref{line:cr} adds $\Gamma'$,
-  replacing $\Vtwo$ with $\Vthree$.
-
-  Eventually, \actuallyVisit{$\bot$, $\Vthree$} is called. A contradiction node
+  $\Dtwo(\Delta^{\top}) + \Dtwo(\Delta^{\bot}) = l + (n-l) = n = \Dtwo(\Delta)$.
+  Similarly, \actuallyVisit{$\CR$, $\Dtwo$} on \cref{line:cr} adds $\Gamma'$,
+  replacing $\Dtwo$ with $\Dthree$.
+
+  Eventually, \actuallyVisit{$\bot$, $\Dthree$} is called. A contradiction node
   with clause $c$ as a parameter is interpreted as one if the clause has
@@
   $\forall X, Y \in \Delta^{\top}\text{. }X = Y$. This sentence is true if and
-  only if $\Vthree(\Delta^{\top}) < 2$. Thus, we can use the Iverson bracket
+  only if $\Dthree(\Delta^{\top}) < 2$. Thus, we can use the Iverson bracket
   notation to write
@@
   \]
-  for the output expression of \actuallyVisit{$\bot$, $\Vthree$}.
-
-  Next, \actuallyVisit{$\land$, $\Vthree$} calls
-  $\visit/\actuallyVisit{$\Reff$, $\Vthree$}$. Since
+  for the output expression of \actuallyVisit{$\bot$, $\Dthree$}.
+
+  Next, \actuallyVisit{$\land$, $\Dthree$} calls
+  $\visit/\actuallyVisit{$\Reff$, $\Dthree$}$. Since
   $\mathfrak{D}(\GDR) = \langle \Gamma, \Delta \rangle$, and
-  $\begin{tikzcd} \langle\Gamma, \Delta\rangle \ar[r, mapsto, "\rho"] & \langle\Gamma', \Delta^{\bot}\rangle \ar[r, mapsto, "\Vthree"] & \langle m-1, n-l \rangle\end{tikzcd}$,
+  $\begin{tikzcd} \langle\Gamma, \Delta\rangle \ar[r, mapsto, "\rho"] & \langle\Gamma', \Delta^{\bot}\rangle \ar[r, mapsto, "\Dthree"] & \langle m-1, n-l \rangle\end{tikzcd}$,
   \textsf{args} is set to $\langle m-1, n-l \rangle$ on \cref{line:args}, and
   the output expression becomes $f(m-1, n-l)$. The call to
-  \actuallyVisit{$\land$, $\Vthree$} then returns the product of the two
+  \actuallyVisit{$\land$, $\Dthree$} then returns the product of the two
   expressions $[l<2]f(m-1, n-l)$. Next, the call to \actuallyVisit{$\bigvee$,
-    $\Vone$} prepends a summation and returns $\sum_{l=0}^{n}[l<2]f(m-1,n-l)$.
+    $\Done$} prepends a summation and returns $\sum_{l=0}^{n}[l<2]f(m-1,n-l)$.
   The same expression (and an empty list of functions) is then returned to
-  \cref{line:actuallyvisit} of the call to \visit{$\GDR$, $\Vone$}. Here, both
+  \cref{line:actuallyvisit} of the call to \visit{$\GDR$, $\Done$}. Here, both
   \textsf{call} and \textsf{signature} are set to $f(m, n)$. As the definition
@@
 
-% TODO: I think I said this the last time, but alog with the complexities as a
+% TODO: I think I said this the last time, but along with the complexities as a
 % way of representing the empirical evaluation, I think you should also include

### 2023-03-02 doc/paper/supplementary_material.tex
Clean up the Preliminaries

@@
 
-\title{Synthesising Recursive Functions for First-Order Model Counting}
-
-% TODO (at the very end)
-% put the appendix in a separate file
-% grammarly the whole thing
-% read the formatting instructions and their LaTeX source (email font?)
-% make sure there are no overflow errors
-% clean up unnecessary things from the header (e.g., packages and definitions)
-%  make sure the result table (as well as other floating objects) are on the right pages
-
-\author{%
-Paulius Dilkas$^1$\and
-Vaishak Belle$^2$\\
-\affiliations
-$^1$National University of Singapore, Singapore, Singapore\\
-$^2$University of Edinburgh, Edinburgh, UK\\
-\emails
-paulius.dilkas@nus.edu.sg,
-vbelle@ed.ac.uk
-}
-
 \crefalias{diagram}{equation}
-\crefname{diagram}{Diagram}{Diagrams}
+\crefname{diagram}{diagram}{diagrams}
 \Crefname{diagram}{Diagram}{Diagrams}
@@
 \section{Proofs}
+
+TODO: finish arranging the definitions
+
+We begin with a few definitions that formalise the notion of a model.
+
+For any set $S$, let $2^{S}$ denote its power set and
+$S^{\ast} \coloneqq \bigcup_{i=0}^{\infty} S^{i}$ the set of tuples of any
+finite length of elements of $S$. For example,
+$\{\,a, b\,\}^{\ast} = \{\, (), (a), (b), (a, a), \dots \,\}$.
+
+Let $\Preds$ be the function that maps any clause or formula to the set of
+predicates used within.
+
+For any $n \in \mathbb{N}_{0}$, let $[n] \coloneqq \{\, 1, \dots, n \,\}$, e.g.,
+$[0] = \emptyset$, and $[2] = \{\, 1, 2 \,\}$.
+
+Each formula $\phi$ has a map
+$\pi_{\phi}\colon \Preds(\phi) \to {\Doms(\phi)}^{\ast}$ s.t., for each
+predicate $\texttt{p}/n \in \Preds(\phi)$, we have that
+$\pi_{\phi}(\texttt{p}) \in {\Doms(\phi)}^{n}$.
+
+\begin{definition}\label{def:model}
+  Let $\phi$ be a formula and $\sigma$ a domain size function. A \emph{model} of
+  $(\phi, \sigma)$ is a map
+  $\mathfrak{M}\colon \Preds(\phi) \to 2^{\mathbb{N}_{0}^{\ast}}$ s.t.\ the
+  following two conditions are satisfied.
+  \begin{enumerate}
+    \item Let $\texttt{p}/n \in \Preds(\phi)$ be a predicate and let
+          $\pi_{\phi}(\texttt{p}) = {(d_{i})}_{i=1}^{n}$ for some domains
+          $d_{i} \in \Doms(\phi)$. Then
+          \begin{equation}\label{eq:subset}
+            \mathfrak{M}(\texttt{p}) \subseteq \prod_{i=1}^{n}[\sigma(d_{i})].\footnote{For simplicity, \cref{def:model} ignores constants.
+To include constants, one would replace $[\sigma(d_{i})]$ with a set that contains all constants associated with domain $d_{i}$, extended with enough new elements to make its cardinality $\sigma(d_{i})$.}
+          \end{equation}
+    \item As a collection of relations, $\mathfrak{M}$ satisfies $\phi$.
+    \begin{itemize}
+      \item TODO: introduce the substitution for formulas, moving the definition from elsewhere
+      \item define inductively as...
+      \item (not exhaustive)
+      \item $\mathfrak{M} \models \phi \land \psi$ iff $\mathfrak{M} \models \phi$ and $\mathfrak{M} \models \psi$
+      \item $\mathfrak{M} \models \phi \lor \psi$ iff $\mathfrak{M} \models \phi$ or $\mathfrak{M} \models \psi$
+      \item $\mathfrak{M} \models \neg\phi$ iff $\mathfrak{M} \not\models \phi$
+      \item $\mathfrak{M} \models (\forall X \in \Delta\text{. }\phi)$ iff $\mathfrak{M} \models \phi[x/\{\, X \,\}]$ for all $x \in \Delta$
+      \item One can then add inequality constraints to the semantics as follows
+      \item $\mathfrak{M} \models (\forall X \in \Delta\text{. } X \ne c \Rightarrow \phi)$ iff $\mathfrak{M} \models \phi[x/\{\, X \,\}]$ for all $x \in \Delta \setminus \{\, c \,\}$
+      \item $\mathfrak{M} \models (\forall X,Y \in \Delta\text{. } X \ne Y \Rightarrow \phi)$ iff $\mathfrak{M} \models \phi[x/\{\, X \,\}][y/\{\, Y \,\}]$ for all $x,y \in \Delta$ s.t. $x \ne y$
+    \end{itemize}
+  \end{enumerate}
+\end{definition}
 
@@
 
-In this appendix, we list the exact function definitions produced by
-\textsc{Crane} for all of the problem instances in Section~6 both before and
-after algebraic simplification (excluding multiplications by one). The
-correctness of all of them has been checked by identifying suitable base cases
-and verifying the numerical answers across a range of domain sizes.
+Here we list the exact function definitions produced by \textsc{Crane} for all
+of the problem instances in Section~6 both before and after algebraic
+simplification (excluding multiplications by one). The correctness of all of
+them has been checked by identifying suitable base cases and verifying the
+numerical answers across a range of domain sizes.
 

### 2023-03-02 doc/paper/paper.tex
Rewrite Section 5

@@
   $\domainNames \gets \{\, \Omega \mapsto \newDomainName{} \mid \Omega \in \mathcal{D} \,\}$\;\label{line:varnames}
+  \tcc{Equivalent condition: $s$ has in-degree greater than one.}
   \If{$s$ is a direct successor of a $\Reff$ node}{
@@
 
-\begin{itemize}
-  \item We call a domain name \emph{atomic} if it is free of subtraction (e.g.,
-        $m$, $n$); otherwise it is \emph{non-atomic} (e.g., $m-1$, $n-l$).
-  \item We assume a fixed total ordering of all domains. In particular, in our
-        running example we assume that $\Gamma$ goes before $\Delta$.
-  \item For each node $v$, let $\mathfrak{D}(v)$ denote the (precomputed) list
-        of domains, the sizes of which we would use as parameters if we were to
-        define a function that begins at $v$. As a set, it is computed by
-        iteratively setting
+\Cref{alg:interpretation} describes how to construct a list of function
+definitions from a (complete) FCG\@. The algorithm consists of two main
+functions: \visit and \actuallyVisit. The former handles new function
+definitions while the latter produces an algebraic interpretation of each node
+depending on its type. As there are many node types, we only include the ones
+pertinent to the contributions of this paper; see previous
+work~\cite{DBLP:conf/ijcai/BroeckTMDR11} for information about the other types.
+Given some node $v$ as input, both \visit and \actuallyVisit return a pair
+$(\mathsf{e}, \mathsf{funs})$. Here, $\mathsf{e}$ is the algebraic expression
+that represent $v$, and $\mathsf{funs}$ is a list of auxiliary functions that
+were created while formulating $\mathsf{e}$.
+
+The algorithm gradually constructs two partial maps $\mathsf{F}$ and
+$\mathsf{D}$ that give names to functions and domains, respectively.
+$\mathsf{F}$ is a global variable that maps FCG nodes to function names (e.g.,
+$f$, $g$). $\mathsf{D}$ maps domains to their names, and it is passed as an
+argument to \visit and \actuallyVisit. Here, a \emph{domain name} is either a
+parameter of a function or an algebraic expression consisting of function
+parameters, subtraction, and parentheses. We call a domain name \emph{atomic} if
+it is free of subtraction (e.g., $m$, $n$); otherwise it is \emph{non-atomic}
+(e.g., $m-1$, $n-l$). Functions \newDomainName and \newFunctionName both
+generate previously-unused names. The latter also takes an FCG node as input and
+links it with the new name in $\mathsf{F}$.
+
+We assume a fixed total ordering of all domains. In particular, in
+\cref{example:interpretation} below we assume that $\Gamma$ goes before
+$\Delta$. For each node $v$, let $\mathfrak{D}(v)$ denote the (precomputed) list
+of domains, the sizes of which we would use as parameters if we were to define a
+function that begins at $v$. As a set, it is computed by iteratively setting
 $\mathfrak{D}(v) \gets \left(\bigcup_{u} \mathfrak{D}(u) \setminus I_{v}\right) \cup U_{v}$
@@
 The set is then sorted according to the fixed ordering of domains.
-  \item $\mathsf{F}$ is a partial map from the set of FCG nodes to function
-        names (e.g., $f$, $g$).
-  \item Functions \newDomainName and \newFunctionName both generate
-        previously-unused names. The latter also records the new name in
-        $\mathsf{F}$.
-  \item Note that a node is a direct successor of a $\Reff$ node if and only if
-        it has an in-degree greater than one.
-  \item The algorithm consists of two main functions: \visit and \actuallyVisit.
-        The former handles new function definitions, and the latter produces an
-        algebraic interpretation of each node depending on its type. As there
-        are many node types, \cref{alg:interpretation} only includes the ones
-        pertinent to the contributions of this paper; see previous
-        work~\cite{DBLP:conf/ijcai/BroeckTMDR11} for information about the other
-        types.
-  \item Given some node $v$ as input, both \visit and \actuallyVisit return a
-        pair $(\mathsf{e}, \mathsf{funs})$. Here, $\mathsf{e}$ is the algebraic
-        expression that should be used to evaluate $v$ or use it in another
-        expression, and $\mathsf{funs}$ is a list of auxiliary functions that
-        were created while constructing $\mathsf{e}$.
-\end{itemize}
-
-When \textsc{ForcLift}~\cite{DBLP:conf/ijcai/BroeckTMDR11} compiles a WFOMC
-instance into a circuit, each node type encodes an arithmetic operation on its
-inputs and parameters. These operations are then immediately performed while
-traversing the circuit. With \textsc{Crane}, the interpretation of an FCG is a
-list of functions. Each function has (some) domain sizes as parameters and may
-contain recursive calls to other functions, including itself. While there may be
-any number of subsidiary functions, there is always one main function that can
-be called with the sizes of the domains of the input formula as arguments.
-Henceforth, this function is always called $f$, and it is defined by the source
-node.
-
-The interpretation of a node is decided by its type. Here we describe the
-interpretations of new (or significantly changed) types and refer the reader to
-previous work~\cite{DBLP:conf/ijcai/BroeckTMDR11} for information on other
-types. The interpretation of a $\CR$ or a $\GDR$ node is simply the
-interpretation of its only direct successor. The interpretation of a $\Reff$
-node is a function call. The direct successor of the $\Reff$ node (say, $v$)
-then must introduce a function. The parameters of this function are the sizes of
-all domains used by nodes reachable from $v$.
 
@@
   \caption{Function calls and their return values when \cref{alg:interpretation}
-    is run on the FCG from \cref{fig:examplefcg}.}\label{fig:functioncalls} % TODO: do I need a dot?
+    is run on the FCG from \cref{fig:examplefcg}}\label{fig:functioncalls}
 \end{figure}
 
-% TODO: examine the order in which everything is introduced
 \begin{example}\label{example:interpretation}
-  Let us see how \cref{alg:interpretation} handles the FCG from
+  Here we examine how \cref{alg:interpretation} works on the FCG from
   \cref{fig:examplefcg}. In this case, $\mathcal{D} = \{\, \Gamma, \Delta \,\}$.
@@
   $\visit/\actuallyVisit{$\Reff$, $\Dthree$}$. Since
-  $\mathfrak{D}(\GDR) = \langle \Gamma, \Delta \rangle$, and
-  $\begin{tikzcd} \langle\Gamma, \Delta\rangle \ar[r, mapsto, "\rho"] & \langle\Gamma', \Delta^{\bot}\rangle \ar[r, mapsto, "\Dthree"] & \langle m-1, n-l \rangle\end{tikzcd}$,
+  $\mathfrak{D}(\GDR) = \langle \Gamma, \Delta \rangle$, and the pair
+  $\langle\Gamma, \Delta\rangle$ is transformed by $\Dthree{} \circ \rho$ as
+  \[
+    \begin{tikzcd}
+      \langle\Gamma, \Delta\rangle \ar[r, mapsto, "\rho"] & \langle\Gamma', \Delta^{\bot}\rangle \ar[r, mapsto, "\Dthree"] & \langle m-1, n-l \rangle,
+    \end{tikzcd}
+  \]
   \textsf{args} is set to $\langle m-1, n-l \rangle$ on \cref{line:args}, and
@@
   \cref{line:initialcall,line:initialcalltwo} discard the function call
-  expression and return the definition of $f$. Therefore,
+  expression and return the definition of $f$. Thus,
   \begin{align}
     f(m, n) &= \sum_{l = 0}^{n} \binom{n}{l} [l < 2] f(m-1, n-l)\nonumber \\
-            &= f(m-1, n) + n f(m-1, n-1).\label{eq:solution}
+            &= f(m-1, n) + n f(m-1, n-1)\label{eq:solution}
   \end{align}
-  To use this recursive function to compute the model count of the input formula
-  for any domain sizes, one just needs to find the base cases $f(0, n)$ and
-  $f(m, 0)$ for all $m, n \in \mathbb{N}_{0}$.
+  is the function that \textsc{Crane} constructed for computing partial
+  injections. To use $f$ in practice, one just needs to identify the base cases
+  $f(0, n)$ and $f(m, 0)$ for all $m, n \in \mathbb{N}_{0}$.
 \end{example}
@@
 % be lifted
+% TODO: say that 'f' will always denote the main function
 

### 2023-03-03 doc/paper/paper.tex
Describe one more instance

@@
 
-% TODO: (everywhere in the paper): emphasise that the experimental results show
+% TODO: (everywhere in the paper): emphasise that the (complexity) results show
 % Crane to be strictly more capable than ForcLift in a sense that it can solve
@@
 
-% However, none of the publicly available exact (W)FOMC algorithms can efficiently
-% compute functions as simple as a factorial.\footnote{There is some previous work
-%   discussing FOMC for
-%   factorials~\cite{DBLP:journals/jair/Kuzelka21,DBLP:conf/kr/BremenK21,DBLP:conf/ijcai/Broeck16}.
-%   One of them~\cite{DBLP:conf/ijcai/Broeck16} is an example `by hand' that does
-%   not directly correspond to any algorithm.
-%   Another~\cite{DBLP:journals/jair/Kuzelka21} proves that the problem is
-%   liftable but contains no experimental results. The
-%   third~\cite{DBLP:conf/kr/BremenK21} contains experimental results performed
-%   with an algorithm that is not publicly available.}
-% Two more papers to mention:
-% 1. The L2C paper has the factorial example as well. But then why doesn't L2C
-% work on it?
-% 2. \cite{DBLP:journals/corr/abs-2302-04606} computes n! using publicly
-% unavailable code
-
 % TODO: add a different introductory problem statement
@@
 
-\section{Experimental Results}\label{sec:results}
-% TODO: rename 'experimental results' -> 'complexity results' (not just the
-% title of the section but review every mention of the word 'experimental')
+\section{Complexity Results}\label{sec:results}
 % TODO: make it clear that I'm not doing this by hand anymore, but I'm still
 % removing multiplications by one.
+
+% TODO: say that 'f' will always denote the main function
+
 % TODO (here or somewhere else): emphasise that there are two parts: search
@@
 % determine)
-% TODO: describe ternary.mln as an example instance that's not in C^2 that can
-% be lifted
-% TODO: say that 'f' will always denote the main function
+
+% TODO: I think I need to mention what m and n are in the text, not just in the caption.
 
@@
     \multicolumn{3}{c}{Function Class} & \multicolumn{3}{c}{Asymptotic Complexity of Counting} \\
-    Partial & Endo- & Class & Best Known & With \textsc{ForcLift} & With \textsc{Crane} \\
+    Partial & Endo- & Class & By Hand & With \textsc{ForcLift} & With \textsc{Crane} \\
     \midrule
@@
     $\Delta$. All asymptotic complexities are in $\Theta(\cdot)$. A dash means
-    that the algorithm was not able to find a solution.}\label{tbl:results}
+    that the algorithm was not able to find a solution. In the case of
+    \textsc{ForcLift}, this means that the greedy search algorithm ended with a
+    formula not suitable for any compilation rule. In the case of
+    \textsc{Crane}, this means that a complete solution could not be found after
+    having explored the maximum allowed depth of the search
+    tree.}\label{tbl:results}
 \end{table*}
@@
 % TODO: emphasise that the reader should focus on the last two columns
-% TODO: the caption sentence about not finding a solution could be confusing
-% TODO: 'best known' sounds disappointing. Find a better alternative.
 
@@
 
-% \footnote{The search tree has a high
-%   branching factor, so exploring all nodes at depth five takes at most a few
-%   seconds, whereas doing the same for depth six can be computationally
-%   infeasible in some cases.}
-
 % how the complexity of a solution is determined
@@
 
-The experimental results are summarised in \cref{tbl:results}, where we compare
-the solutions found by both algorithms to the best known ways of computing the
-same quantities. The best-known asymptotic complexity for computing total
-surjections is by Earnest~\shortcite{30049}. All other best-known complexity
-results are inferred from the formulas and programs on the on-line encyclopedia
-of integer sequences~\cite{oeis}. On instances that could already be solved by
-\textsc{ForcLift}, the two algorithms perform equally well. However,
-\textsc{Crane} can also solve all but one of the instances that
+The results are summarised in \cref{tbl:results}, where we compare the solutions
+found by both algorithms to the manually-constructed ways of computing the same
+functions that have been proposed before. In particular, the complexity for
+computing total surjections is by Earnest~\shortcite{30049}, and all other such
+complexities are inferred from the formulas and programs on the on-line
+encyclopedia of integer sequences~\cite{oeis}. On instances that could already
+be solved by \textsc{ForcLift}, the two algorithms perform equally well.
+However, \textsc{Crane} can also solve all but one of the instances that
 \textsc{ForcLift} fails on in at most cubic time. See supplementary material for
 the exact solutions produced by \textsc{Crane} that correspond to the complexity
-results in \cref{tbl:results}. We also note that standard (W)FOMC benchmarks
-such as \cref{example:smokers} that are already supported by \textsc{ForcLift}
-remain feasible for \textsc{Crane} as well. Moreover, our algorithm can also
-handle the linear order axiom, for which a bespoke algorithm was recently
-proposed by T{\'{o}}th and
-Ku\v{z}elka~\shortcite{DBLP:journals/corr/abs-2211-01164}.
+results in \cref{tbl:results}.
+
+\paragraph{Miscellaneous other instances.}
+We also note that standard (W)FOMC benchmarks such as \cref{example:smokers}
+that are already supported by \textsc{ForcLift} remain feasible for
+\textsc{Crane} as well. Moreover, our algorithm can also handle the linear order
+axiom, for which a bespoke algorithm was recently proposed by T{\'{o}}th and
+Ku\v{z}elka~\shortcite{DBLP:journals/corr/abs-2211-01164}. To demonstrate that
+\textsc{Crane} is capable of finding efficient solutions to problems beyond
+known domain-liftable fragments such as \Ctwo{}, we run \textsc{Crane} in greedy
+search mode on the following formula:
+\begin{equation}\label[formula]{eq:ternary}
+  \begin{split}
+    &\begin{multlined}[t]
+      (\forall X,W \in \Gamma\text{. }\forall Y \in \Delta\text{. }\forall Z \in \Lambda\text{. }\\
+      \texttt{p}(X, Y, Z) \land \texttt{p}(W, Y, Z) \Rightarrow X = W) \land{}
+    \end{multlined}\\
+    &\begin{multlined}[t]
+      (\forall X \in \Gamma\text{. }\forall Y,W \in \Delta\text{. }\forall Z \in \Lambda\text{. }\\
+      \texttt{p}(X, Y, Z) \land \texttt{p}(X, W, Z) \Rightarrow Y = W).
+    \end{multlined}
+  \end{split}
+\end{equation}
+For every element $z$ of $\Lambda$, \cref{eq:ternary} restricts
+$\texttt{p}(X, Y, z)$ to be a $\Gamma \to \Delta$ partial injection, independent
+of $\texttt{p}(X, Y, z')$ for any $z' \ne z$. \textsc{Crane} instantly returns a
+solution of complexity $\Theta(l+mn)$, where $l = |\Lambda|$.
 
@@
 graph that encodes a solution. To construct such graphs, \textsc{Crane}
-supplements \textsc{ForcLift}~\cite{DBLP:conf/ijcai/BroeckTMDR11} with three
-new compilation rules. Our experiments revealed a range of counting problems
-that are liftable to \textsc{Crane} but not to any other (W)FOMC algorithm.
-Although in this paper we focus on unweighted counting, \textsc{ForcLift}'s
-support for weights trivially transfers to \textsc{Crane} as well. The common
-thread across these newly liftable problems is (partial) injectivity. Thus, we
-can formulate the following conjecture.
+supplements \textsc{ForcLift}~\cite{DBLP:conf/ijcai/BroeckTMDR11} with three new
+compilation rules. Our results in \cref{sec:results} revealed a range of
+counting problems that are liftable to \textsc{Crane} but not to any other
+(W)FOMC algorithm. Although in this paper we focus on unweighted counting,
+\textsc{ForcLift}'s support for weights trivially transfers to \textsc{Crane} as
+well. The common thread across these newly liftable problems is (partial)
+injectivity. Thus, we can formulate the following conjecture.
 
@@
 
+% TODO: argue about the possibilities of optimising the recurrence formula
+% further, relate this to skolem function synthesis (maybe elsewhere as well)
+
 \bibliographystyle{kr}

### 2023-03-06 doc/paper/paper.tex
Revisions to Sections 1 and 6

@@
 \usepackage[inline]{enumitem}
+\usepackage{subcaption}
 
@@
 \usetikzlibrary{shapes}
+\usetikzlibrary{fit}
 
@@
 
-% TODO: add a flow graph: \phi -> Box (Compilation) -> \G_\phi -> Box (Algorithm
-% 4) -> \mathcal{F}_\phi -> Box (simplification) -> \mathcal{F|_\phi, base
-% cases, domain sizes -> Box (Propagation (?))
-
-% TODO: what's the punchline? make sure the introduction tells the reader what
-% to expect from section 5
-
-% TODO: (everywhere in the paper): emphasise that the (complexity) results show
-% Crane to be strictly more capable than ForcLift in a sense that it can solve
-% everything that ForcLift can and more (including instances beyond C^2).
+\begin{figure*}[t]
+  \centering
+  \begin{subfigure}{\textwidth}
+    \centering
+    \begin{tikzpicture}
+      \node at (-2, 0) (start) {$\phi$};
+      \node[draw,rounded rectangle] at (0, 0) (kc) {Compilation};
+      \node[draw,rounded rectangle] at (9, 0) (evaluation) {Propagation};
+      \node at (12, 0) (end) {Model count};
+      \node at (9, -1) (sizes) {Domain sizes};
+      \node at (-0.3, 0.5) {\textsc{ForcLift}};
+      \node[draw,fit={(kc) (evaluation)},inner ysep=6pt,yshift=5pt] {};
+      \draw[-Latex] (start) -- (kc);
+      \draw[-Latex] (kc) -- node[above] {$C_{\phi}$} (evaluation);
+      \draw[-Latex] (evaluation) -- (end);
+      \draw[-Latex] (sizes) -- (evaluation);
+    \end{tikzpicture}
+    \caption{\textsc{ForcLift} compiles $\phi$ into a circuit $C_{\phi}$. The
+      domain sizes are then used to propagate values through $C_{\phi}$,
+      computing the model count.}
+  \end{subfigure}
+  \begin{subfigure}{\textwidth}
+    \centering
+    \begin{tikzpicture}
+      \node at (-2, 0) (start) {$\phi$};
+      \node[draw,rounded rectangle] at (0, 0) (kc) {Compilation};
+      \node[draw,rounded rectangle] at (3, 0) (interpretation) {\Cref{alg:interpretation}};
+      \node[draw,rounded rectangle] at (6, 0) (simplification) {Simplification};
+      \node[draw,rounded rectangle] at (9, 0) (evaluation) {Evaluation};
+      \node at (12, 0) (end) {Model count};
+      \node at (7, -1) (base) {Base cases};
+      \node at (9, -1) (sizes) {Domain sizes};
+      \node at (-0.55, 0.5) {\textsc{Crane}};
+      \node[draw,fit={(kc) (interpretation)},inner ysep=6pt,yshift=5pt] {};
+      \draw[-Latex] (start) -- (kc);
+      \draw[-Latex] (kc) -- node[above] {$G_{\phi}$} (interpretation);
+      \draw[-Latex] (interpretation) -- node[above] {$\mathcal{F}_{\phi}$} (simplification);
+      \draw[-Latex] (simplification) -- node[above] {$\mathcal{F}_{\phi}'$} (evaluation);
+      \draw[-Latex] (evaluation) -- (end);
+      \draw[-Latex] (base) -- (evaluation);
+      \draw[-Latex] (sizes) -- (evaluation);
+    \end{tikzpicture}
+    \caption{\textsc{Crane} compiles $\phi$ into a graph $G_{\phi}$ and then
+      converts $G_{\phi}$ into a collection of functions $\mathcal{F}_{\phi}$.
+      In some cases, these functions can benefit from algebraic simplification.
+      If some of the functions are defined recursively, base cases need to be
+      established. One can then compute the model count of $\phi$ by running the
+      main function in $\mathcal{F}'_{\phi}$ with domain sizes as arguments.}
+  \end{subfigure}
+  \caption{A comparison of how \textsc{ForcLift} and \textsc{Crane} can be used
+    to compute the model count of a formula $\phi$.}\label{fig:process}
+\end{figure*}
 
@@
 problems~\cite{DBLP:journals/jair/TotisDRK23}.
-
-% Lifted inference algorithms are typically used on probabilistic models such as
-% probabilistic programming
-% languages~\cite{DBLP:journals/ml/RaedtK15,DBLP:journals/ijar/RiguzziBZCL17},
-% Markov logic
-% networks~\cite{DBLP:conf/ijcai/BroeckTMDR11,DBLP:journals/cacm/GogateD16}.
 
@@
 
-% TODO: add a different introductory problem statement
 We claim that the capabilities of (W)FOMC algorithms can be significantly
@@
 In this work, we show how to relax these restrictions in a way that results in a
-stronger (W)FOMC algorithm, capable of handling more instances (e.g., counting
-various injective mappings) in a lifted manner. The ideas presented in this
-paper are implemented in \textsc{Crane}---an extension of the arguably most
-well-known WFOMC algorithm \textsc{ForcLift}. \textsc{ForcLift} works in two
-stages: compilation and evaluation/propagation. In the first stage, various
-\emph{(compilation) rules} are applied to the input (or some derivative)
-formula, gradually constructing a circuit. In the second stage, the weights of
-the instance are propagated through the circuit, computing the weighted model
-count. Along with new compilation rules, \textsc{Crane} introduces changes to
-both stages of the process. First, while \textsc{ForcLift} applies compilation
-rules via greedy search, \textsc{Crane} also supports a hybrid search algorithm
-that applies some rules greedily and some using breadth-first
+stronger algorithm, capable of handling more instances in a lifted manner. The
+ideas presented in this paper are implemented in \textsc{Crane}---an extension
+of the (W)FOMC algorithm \textsc{ForcLift}. The differences in how these
+algorithms operate are depicted in \cref{fig:process}. Compilation is performed
+by applying various \emph{(compilation) rules} to the input (or some derivative)
+formula, gradually constructing a circuit (in the case of \textsc{ForcLift}) or
+a graph (in the case of \textsc{Crane}). \textsc{ForcLift} applies compilation
+rules via greedy search, whereas \textsc{Crane} also supports a hybrid search
+algorithm that applies some rules greedily and some using breadth-first
 search.\footnote{In the current implementation, the rules that are applied in a
@@
   rules.} This alternative was introduced because there is no reason to expect
-greedy search to be optimal. Second, the product of compilation is not directly
-evaluated but rather interpreted as a collection of functions on domain sizes.
-Hence, our approach is reminiscent of previous work on lifted inference via
-compilation to C++ programs~\cite{DBLP:conf/kr/KazemiP16} and the broader area
-of functional
+greedy search to be complete. Another major difference is that---in
+\textsc{Crane}---the product of compilation is not directly evaluated but rather
+transformed into a collection of functions on domain sizes. Hence, our approach
+is reminiscent of previous work on lifted inference via compilation to C++
+programs~\cite{DBLP:conf/kr/KazemiP16} and the broader area of functional
 synthesis~\cite{DBLP:conf/cav/GoliaRM20,DBLP:conf/pldi/KuncakMPS10,sanathanan1963transfer}.
@@
 
-The main conceptual difference between \textsc{Crane} and \textsc{ForcLift} is
-that we utilise labelled directed graphs instead of circuits, where cycles
-represent recursive calls. Suppose the input formula $\phi$ depends on a domain
-of size $n \in \mathbb{N}_{0}$. \emph{Generalised domain recursion} (GDR)---one
-of the new compilation rules---transforms $\phi$ into a different formula $\psi$
-that has an additional constant and some new \emph{constraints}. After some
+The use of labelled directed graphs in lieu of circuits enables \textsc{Crane}
+to construct recursive solutions by representing recursive function calls via
+cycle-inducing edges. A hypothetical instance of compilation could proceed as
+follows. Suppose the input formula $\phi$ depends on a domain of size
+$n \in \mathbb{N}_{0}$. \emph{Generalised domain recursion} (GDR)---one of the
+new compilation rules---transforms $\phi$ into a different formula $\psi$ that
+has an additional constant and some new \emph{constraints}. After some
 additional transformations, the constraints in $\psi$ become `uniform' and can
@@
 compilation rule. Afterwards, another compilation rule recognizes that the
-resulting formula is just like the input formula $\phi$ but with a different
-domain. This observation allows us to add a cycle-forming edge to the graph,
-which can be interpreted as function $f$ relying on $f(n-1)$ to compute $f(n)$.
+resulting formula matches the input formula $\phi$ except for referring to a
+different domain. This observation allows us to add a cycle-forming edge to the
+graph, which can be interpreted as function $f$ relying on $f(n-1)$ to compute
+$f(n)$.
 
@@
 
-We begin by defining the representation used for sentences in first-order logic
-in \cref{sec:recprelims}. Then, in \cref{sec:methods}, we define the graphs that
-replace circuits in representing a solution to a (W)FOMC problem.
-\Cref{sec:rules} introduces the new compilation rules. In \cref{sec:interpret},
-we discuss how a graph can be interpreted as a collection of (potentially
+We begin by introducing some notation, terminology, and the problem of FOMC in
+\cref{sec:recprelims}. Then, in \cref{sec:methods}, we define the graphs that
+replace circuits in representing a solution to such a problem. \Cref{sec:rules}
+introduces the new compilation rules. \Cref{sec:interpret} describes an
+algorithm that can convert such a graph into a collection of (potentially
 recursive) functions. In \cref{sec:results}, we compare \textsc{ForcLift} and
-\textsc{Crane} on a range of function-counting problems. We show that
-\textsc{Crane} performs as well as \textsc{ForcLift} on the instances that were
-already solvable by \textsc{ForcLift} but is also able to handle most of the
-instances that \textsc{ForcLift} fails on. Finally, in \cref{sec:conclusion}, we
-conclude by outlining some conjectures and directions for future work.
+\textsc{Crane} on a range of counting problems. We show that:
+\begin{enumerate*}[label=(\roman*)]
+  \item \textsc{Crane} performs as well as \textsc{ForcLift} on the instances
+  that were already solvable by \textsc{ForcLift},
+  \item \textsc{Crane} is also able to handle most of the instances that
+  \textsc{ForcLift} fails on, \emph{including those outside of currently-known
+    domain-liftable fragments} such as \Ctwo{}.
+\end{enumerate*}
+Finally, in \cref{sec:conclusion}, we conclude by outlining some conjectures and
+directions for future work.
 
@@
   cardinality one (e.g., $\{\, (1, 1) \,\}$) do too. Finally, there are two
-  relations of cardinality two ($\{\, (1, 1), (2, 2) \,\}$ and
-  $\{\, (1, 2), (2, 1) \,\}$) that satisfy the conditions as well. Thus, the
+  relations of cardinality two---$\{\, (1, 1), (2, 2) \,\}$ and
+  $\{\, (1, 2), (2, 1) \,\}$---that satisfy the conditions as well. Thus, the
   FOMC of $(\phi, \sigma)$ is 7. Incidentally, the FOMC of $\phi$ counts partial
@@
 \section{Complexity Results}\label{sec:results}
-% TODO: make it clear that I'm not doing this by hand anymore, but I'm still
-% removing multiplications by one.
-
-% TODO: say that 'f' will always denote the main function
-
-% TODO (here or somewhere else): emphasise that there are two parts: search
-% (with some artificial limit) + inference (whose complexity we can easily
-% determine)
-
-% TODO: I think I need to mention what m and n are in the text, not just in the caption.
 
@@
     \toprule
-    \multicolumn{3}{c}{Function Class} & \multicolumn{3}{c}{Asymptotic Complexity of Counting} \\
+    \multicolumn{3}{c}{Function class} & \multicolumn{3}{c}{Complexity of $\mathcal{F}_{\phi}$ (as in \cref{fig:process})} \\
     Partial & Endo- & Class & By Hand & With \textsc{ForcLift} & With \textsc{Crane} \\
@@
   \end{tabular}
-  \caption{The worst-case complexity of counting various types of functions,
-    where $m$ is the size of domain $\Gamma$, and $n$ is the size of domain
-    $\Delta$. All asymptotic complexities are in $\Theta(\cdot)$. A dash means
-    that the algorithm was not able to find a solution. In the case of
-    \textsc{ForcLift}, this means that the greedy search algorithm ended with a
-    formula not suitable for any compilation rule. In the case of
-    \textsc{Crane}, this means that a complete solution could not be found after
-    having explored the maximum allowed depth of the search
-    tree.}\label{tbl:results}
+  \caption{The worst-case complexity of counting various types of functions. All
+    asymptotic complexities are in $\Theta(\cdot)$. A dash means that the
+    algorithm was not able to find a solution. In the case of \textsc{ForcLift},
+    this means that the greedy search algorithm ended with a formula not
+    suitable for any compilation rule. In the case of \textsc{Crane}, this means
+    that a complete solution could not be found after having explored the
+    maximum allowed depth of the search tree.}\label{tbl:results}
 \end{table*}
-% TODO: 'Asymptotic Complexity of Counting' -> 'Complexity of \mathcal{F}_\phi'
-% (introduce \mathcal{F}_\phi in the introduction, together with the flow graph)
-
-% TODO: Explain (in text) why there are fewer than 16 rows in the table. And
-% don't say 'same as', instead say that the formulas are in some sense
-% equivalent (maybe in a stronger sense than the usual equivalence).
-
-% TODO: emphasise that the reader should focus on the last two columns
 
@@
 % if you include a few plots and say we just give a few representative examples
-% and the rest follow the table of all that will be better
+% and the rest follow the table of all that will be better [an experiment with
+% non-partial endo injections?]
+
+% TODO: emphasise that there are two parts: search (with some artificial limit)
+% + inference (whose complexity we can easily determine)
 
@@
 % the process: both for running algorithms and for determining complexities
-In our experiments, we consider all sixteen combinations of these properties,
-i.e., injectivity, surjectivity, partiality, and endo-. We run each algorithm
-once on each of the sixteen instances.\footnote{While domain sizes have to be
-  specified as part of the input, they are immaterial to the search procedure.}
+We consider all sixteen combinations of these properties (injectivity,
+surjectivity, partiality, and endo-), omitting duplicate descriptions of the
+same function/sequence. We run each algorithm once on each instance.
 \textsc{Crane} is run in hybrid search mode until either five solutions are
 found or the search tree reaches height six. \textsc{ForcLift} is always run
-until it terminates. If successful, \textsc{ForcLift} generates a circuit, and
-\textsc{Crane} generates one or more (complete) FCGs. In both cases, we manually
-convert the resulting graphs into definitions of functions as described in
-\cref{sec:interpret}. We then assess the complexity of each solution by hand and
-pick the best in case \textsc{Crane} returns several solutions of varying
-complexities.
+until it terminates. If successful, \textsc{Crane} generates one or more sets of
+function definitions, and \textsc{ForcLift} generates a circuit, which can
+similarly be interpreted as a function definition. We then assess the complexity
+of each solution by hand and pick the best in case \textsc{Crane} returns
+several solutions of varying complexities.
 
@@
 that computes $f(i, j)$ for all $i = 0, \dots, m$ and $j = 0, \dots, n$, taking
-a constant amount of time on the computation of each $f(i, j)$.
-% TODO: look for a better place to put the 'In particular...' remark
-
-The results are summarised in \cref{tbl:results}, where we compare the solutions
-found by both algorithms to the manually-constructed ways of computing the same
-functions that have been proposed before. In particular, the complexity for
-computing total surjections is by Earnest~\shortcite{30049}, and all other such
-complexities are inferred from the formulas and programs on the on-line
-encyclopedia of integer sequences~\cite{oeis}. On instances that could already
-be solved by \textsc{ForcLift}, the two algorithms perform equally well.
-However, \textsc{Crane} can also solve all but one of the instances that
-\textsc{ForcLift} fails on in at most cubic time. See supplementary material for
-the exact solutions produced by \textsc{Crane} that correspond to the complexity
-results in \cref{tbl:results}.
+a constant amount of time on each $f(i, j)$.
+
+Let $m = |\Gamma|$ and $n = |\Delta|$ be domain sizes. We summarise the results
+in \cref{tbl:results}, where we compare the solutions found by both algorithms
+to the manually-constructed ways of computing the same quantities that have been
+proposed before. In particular, the complexity of computing total surjections is
+by Earnest~\shortcite{30049}, and all other such complexities are inferred from
+the formulas and programs on the on-line encyclopedia of integer
+sequences~\cite{oeis}. Examining the last two columns of the table, we see that
+the two algorithms perform equally well on instances that could already be
+solved by \textsc{ForcLift}. However, \textsc{Crane} can also solve all but one
+of the instances that \textsc{ForcLift} fails on in at most cubic time. See
+supplementary material for the exact solutions produced by \textsc{Crane}.
 
@@
 
+% TODO:: emphasise that the (complexity) results show Crane to be strictly more
+% capable than ForcLift in a sense that it can solve everything that ForcLift
+% can and more (including instances beyond C^2).
+
 \bibliographystyle{kr}

### 2023-03-06 solvers/fastwfomc/main.py

@@ -28,13 +28,12 @@ def main():
     )
 
     bijections = expr(
-        '(S1(x) | ~P(x, y)) & ' +
-        '(S3(x) | ~P(y, x))'
+        'S(x) | ~P(x, y)'
     )
 
-    counter = WFOMCWithCC(bijections, n)
+    counter = WFOMCWithCC(bijections, n, [('P', n)])
     #print(counter.get_wfomc(defaultdict(lambda: (1, 1))))
-    print(counter.get_wfomc({'S1': (1, -1), 'S3': (1, -1), 'P': (1, 1)}))
+    print(counter.get_wfomc({'S': (1, -1), 'P': (1, 1)}))
 
 
 if __name__ == "__main__":

### 2023-03-06 doc/paper/paper.tex
Improve conclusions

@@
 \newtheorem*{remark}{Remark}
+
+\setlength{\multlinegap}{0pt}
 
@@
       established. One can then compute the model count of $\phi$ by running the
-      main function in $\mathcal{F}'_{\phi}$ with domain sizes as arguments.}
+      main function in $\mathcal{F}'_{\phi}$ with domain sizes as
+      arguments.}\label{fig:processcrane}
   \end{subfigure}
@@
 
-In this paper, we showed how a state-of-the-art (W)FOMC algorithm can be
-empowered by generalising domain recursion and adding support for cycles in the
-graph that encodes a solution. To construct such graphs, \textsc{Crane}
-supplements \textsc{ForcLift}~\cite{DBLP:conf/ijcai/BroeckTMDR11} with three new
-compilation rules. Our results in \cref{sec:results} revealed a range of
-counting problems that are liftable to \textsc{Crane} but not to any other
-(W)FOMC algorithm. Although in this paper we focus on unweighted counting,
-\textsc{ForcLift}'s support for weights trivially transfers to \textsc{Crane} as
-well. The common thread across these newly liftable problems is (partial)
-injectivity. Thus, we can formulate the following conjecture.
-
+This paper presents \textsc{Crane}---an extension of
+\textsc{ForcLift}~\cite{DBLP:conf/ijcai/BroeckTMDR11} that benefits from a more
+general version of domain recursion and the support for graphs with cycles. Our
+results in \cref{sec:results} reveal a range of counting problems that became
+newly feasible as a result of these enhancements, including instances outside of
+currently-known domain-liftable fragments such as \Ctwo{}. (Although here we
+focus on unweighted counting, \textsc{ForcLift}'s support for weights trivially
+transfers to \textsc{Crane} as well.) The common thread across these newly
+liftable problems is a version of partial injectivity. Thus, we formulate the
+following conjecture.
 \begin{conjecture}
@@
   \begin{align*}
-    &\begin{multlined}[t]
-      (\forall X \in \Gamma\text{. }\forall Y, Z \in \Delta\text{. }\\
-      Y \ne Z \Rightarrow \neg \texttt{\textup{p}}(X, Y) \lor \neg \texttt{\textup{p}}(X, Z)) \land{}
+    &\begin{multlined}[t][0.9\linewidth]
+      (\forall X_{1} \in \Delta_{1}\text{. }\dots\,\forall X_{n} \in \Delta_{n}\text{. }\forall Y \in \Delta_{i}\text{. }\texttt{\textup{p}}(X_{1}, \dots, X_{n}) \land{}\\
+      \texttt{\textup{p}}(X_{1}, \dots, X_{i-1}, Y, X_{i+1}, \dots, X_{n}) \Rightarrow X_{i} = Y) \land{}
     \end{multlined}\\
-    &\begin{multlined}[t]
-      (\forall X, Z \in \Gamma\text{. }\forall Y \in \Delta\text{. }\\
-      X \ne Z \Rightarrow \neg \texttt{\textup{p}}(X, Y) \lor \neg \texttt{\textup{p}}(Z, Y))
+    &\begin{multlined}[t][0.9\linewidth]
+      (\forall X_{1} \in \Delta_{1}\text{. }\dots\,\forall X_{n} \in \Delta_{n}\text{. }\forall Y \in \Delta_{j}\text{. }\texttt{\textup{p}}(X_{1}, \dots, X_{n}) \land{}\\
+      \texttt{\textup{p}}(X_{1}, \dots, X_{j-1}, Y, X_{j+1}, \dots, X_{n}) \Rightarrow X_{j} = Y)
     \end{multlined}
   \end{align*}
-  for some predicate $\texttt{\textup{p}}/2$ and domains $\Gamma$ and $\Delta$.
-  Then \IFO{} is liftable by \textsc{Crane}.
+  for some predicate $\texttt{\textup{p}}/n$, domains
+  $\Delta_{1}, \dots, \Delta_{n}$, and $i, j \in \{\, 1, \dots, n \,\}$. Then
+  \IFO{} is liftable by \textsc{Crane}.
 \end{conjecture}
-
 Recall that \Ctwo{} is the class of formulas with counting quantifiers and at
-most two variables. \Ctwo{} was recently shown to be
-liftable~\cite{DBLP:journals/jair/Kuzelka21} but without providing a usable
-(W)FOMC algorithm. Since the tasks of counting injections and bijections fall
-into the \Ctwo{} fragment, we can conjecture the following.
-
-\begin{conjecture}
-  \Ctwo{} is liftable by \textsc{Crane} by either reformulating formulas in
-  \Ctwo{} to avoid counting quantifiers or extending \textsc{Crane} to support
-  them.
-\end{conjecture}
-
-However, the most important direction for future work is to fully automate this
-new process. First, we need an algorithm that transforms FCGs into definitions
-of functions. Formalising this process would also allow us to prove the
-correctness of the new compilation rules in constructing FCGs that indeed
-compute the right (weighted) model counts. Second, these definitions must be
-simplified before they can be used, perhaps by a computer algebra system. Third,
-we need a way to find the base cases for the recursive definitions provided by
-\textsc{Crane}. Fourth, since the first solution found by \textsc{Crane} is not
-always optimal in terms of its complexity, an automated way to determine the
-asymptotic complexity of a solution would be helpful as well. Achieving these
-goals would enable \textsc{Crane} to automatically constructing efficient ways
-to compute various functions and sequences. In addition to the potential impact
-on areas of artificial intelligence (AI) such as statistical relational
-AI~\cite{DBLP:series/synthesis/2016Raedt}, \textsc{Crane} could be beneficial to
-research in combinatorics as
+most two variables that was recently shown to be
+liftable~\cite{DBLP:journals/jair/Kuzelka21}. Since most of the instances in
+\cref{sec:results} are in \Ctwo{}, we can also conjecture that \Ctwo{} is
+liftable by \textsc{Crane}.
+
+The most important direction for future work is in fully automating the process
+in \cref{fig:processcrane}. First, we need a way to find the base cases for the
+recursive definitions produced by \textsc{Crane}. Second, since the first
+solution found by \textsc{Crane} is not always optimal in terms of its
+complexity, an automated way to determine the asymptotic complexity of a
+solution would be helpful as well. Third, as we saw at the end of
+\cref{example:interpretation}, the functions constructed by \textsc{Crane} can
+often benefit from elementary algebraic simplifications, and this process can be
+automated using a computer algebra system. Furthermore, note that having the
+solution to a (W)FOMC problem expressed in terms of functions enables many new
+possibilities such as
+\begin{enumerate*}[label=(\roman*)]
+  \item the use of more sophisticated simplification techniques,
+  \item asymptotic analysis of, e.g., how the model count grows as the domain
+  size goes to infinity, and
+  \item answering questions parameterised by domain sizes, e.g., `how big does
+  domain $\Delta$ have to be for the probability of event $E$ to be above
+  \SI{95}{\percent}?'
+\end{enumerate*}
+In addition to the potential impact on areas of artificial intelligence (AI)
+such as statistical relational AI~\cite{DBLP:series/synthesis/2016Raedt},
+\textsc{Crane} could be beneficial to research in combinatorics as
 well~\cite{DBLP:conf/ilp/BarvinekB0ZK21,DBLP:journals/corr/abs-2302-04606}.
-
-% TODO: argue about the possibilities of optimising the recurrence formula
-% further, relate this to skolem function synthesis (maybe elsewhere as well)
-
-% TODO:: emphasise that the (complexity) results show Crane to be strictly more
-% capable than ForcLift in a sense that it can solve everything that ForcLift
-% can and more (including instances beyond C^2).
 

### 2023-03-07 doc/paper/paper.tex
Clean up supplementary material

@@
 \usepackage{tikz}
-\usepackage[capitalize]{cleveref}
+\usepackage[capitalize,noabbrev]{cleveref}
 \usepackage{multirow}
@@
 \newtheorem{claim}{Claim}[theorem]
-\theoremstyle{definition}
+\newtheorem{example}{Example}
 \newtheorem{definition}{Definition}
-\newtheorem{example}{Example}
-\theoremstyle{remark}
-\newtheorem*{remark}{Remark}
-
-\setlength{\multlinegap}{0pt}
 
@@
 % TODO (at the very end)
-% grammarly the whole thing
-% read the formatting instructions and their LaTeX source (email font?)
-% make sure there are no overflow errors
+% grammarly the whole thing (supplementary material as well)
 % make sure the result table (as well as other floating objects) are on the right pages
+% make sure the abstract, introduction, and conclusion are all in line with each other
+% maybe improve the indentation of equations
 
@@
 \newcommand{\Dthree}{\mathsf{D}_{3}}
+\newcommand{\predicate}{\texttt{\textup{p}}}
 
@@
 \begin{algorithm}[t]
-  \caption{The compilation rule for $\GDR$ nodes.}\label{alg:domainrecursion}
+  \caption{The compilation rule for $\GDR$ nodes}\label{alg:domainrecursion}
   \KwIn{formula $\phi$, set of all relevant domains $\mathcal{D}$}
@@
 \begin{algorithm}[t]
-  \caption{The compilation rule for $\CR$ nodes.}\label{alg:constraintremoval}
+  \caption{The compilation rule for $\CR$ nodes}\label{alg:constraintremoval}
   \KwIn{formula $\phi$, set of all relevant domains $\mathcal{D}$}
@@
 
-\paragraph{Hashing.}
+\subsubsection{Hashing}
 We use (integer-valued) hash functions to discard pairs of formulas that are too
@@
 
-\paragraph{Caching.}
+\subsubsection{Caching}
 \textsc{ForcLift}~\cite{DBLP:conf/ijcai/BroeckTMDR11} uses a cache to check if
@@
 \begin{algorithm}[t]
-  \caption{The compilation rule for $\Reff$ nodes.}\label{alg:trycache}
+  \caption{The compilation rule for $\Reff$ nodes}\label{alg:trycache}
   \KwIn{formula $\phi$, cache $C$}
@@
 
-\paragraph{Miscellaneous other instances.}
+\subsubsection{Miscellaneous Other Instances}
 We also note that standard (W)FOMC benchmarks such as \cref{example:smokers}
@@
 \section{Conclusion and Future Work}\label{sec:conclusion}
+\setlength{\multlinegap}{0pt}
 
@@
 
+% TODO: The reference list should not include unpublished work. (earnest + OEIS + 3 corr references)
+% TODO: replace all instances of {p} with \predicate (by hand)
 \bibliographystyle{kr}

### 2023-03-07 doc/paper/supplementary_material.tex
Describe one more instance
Clean up supplementary material

--- 2023-03-01 doc/paper/supplementary_material.tex
@@
 \newtheorem{claim}{Claim}[theorem]
-\theoremstyle{definition}
 \newtheorem{definition}{Definition}
@@
 /TemplateVersion (KR.2022.0, KR.2023.0)
-}
-
-\title{Synthesising Recursive Functions for First-Order Model Counting}
-
-% TODO (at the very end)
-% put the appendix in a separate file
-% grammarly the whole thing
-% read the formatting instructions and their LaTeX source (email font?)
-% make sure there are no overflow errors
-% clean up unnecessary things from the header (e.g., packages and definitions)
-%  make sure the result table (as well as other floating objects) are on the right pages
-
-\author{%
-Paulius Dilkas$^1$\and
-Vaishak Belle$^2$\\
-\affiliations
-$^1$National University of Singapore, Singapore, Singapore\\
-$^2$University of Edinburgh, Edinburgh, UK\\
-\emails
-paulius.dilkas@nus.edu.sg,
-vbelle@ed.ac.uk
 }
@@
 \newcommand{\IFO}{$\mathsf{I}\mathsf{FO}^{2}$}
+\newcommand{\predicate}{\texttt{\textup{p}}}
 
@@
 \section{Proofs}
+
+We begin with a few definitions that formalise the notion of a model. For any
+set $S$, let $2^{S}$ denote its power set and
+$S^{\ast} \coloneqq \bigcup_{i=0}^{\infty} S^{i}$ the set of tuples---of any
+finite length---of elements of $S$. For example,
+${\{\,a, b\,\}}^{\ast} = \{\, (), (a), (b), (a, a), \dots \,\}$. For any
+$n \in \mathbb{N}_{0}$, let $[n] \coloneqq \{\, 1, \dots, n \,\}$, e.g.,
+$[0] = \emptyset$, and $[2] = \{\, 1, 2 \,\}$. Extending the notation for
+substitution introduced in \cref{sec:recprelims}, for a formula $\phi$, constant
+$c$, and set of variables $V$, let $\phi[c/V]$ denote $\phi$ with all
+occurrences of all variables in $V$ replaced with $c$. Let $\Preds$ be the
+function that maps any clause or formula to the set of predicates used within.
+With each formula $\phi$ we associate a map
+$\pi_{\phi}\colon \Preds(\phi) \to {\Doms(\phi)}^{\ast}$ s.t., for each
+predicate $\predicate/n \in \Preds(\phi)$, we have that
+$\pi_{\phi}(\predicate) \in {\Doms(\phi)}^{n}$. This map makes explicit the idea
+that each $n$-ary predicate is associated with an $n$-tuple of domains. In the
+case of formula $\phi$ from \cref{example:first},
+$\pi_{\phi} = \{\, \predicate \mapsto (\Gamma, \Delta) \,\}$.
+
+\begin{definition}\label{def:model}
+  Let $\phi$ be a formula and $\sigma$ a domain size function, A \emph{model} of
+  $(\phi, \sigma)$ is a map
+  $\mathfrak{M}\colon \Preds(\phi) \to 2^{\mathbb{N}_{0}^{\ast}}$ s.t.\ the
+  following two conditions are satisfied.
+  \begin{enumerate}
+    \item For all predicates $\predicate/n \in \Preds(\phi)$ with
+          $\pi_{\phi}(\predicate) \coloneqq {(\Delta_{i})}_{i=1}^{n}$ for some
+          domains $\Delta_{i} \in \Doms(\phi)$,
+    \begin{equation}\label{eq:subset}
+      \mathfrak{M}(\predicate) \subseteq \prod_{i=1}^{n}[\sigma(\Delta_{i})].\footnote{For simplicity, \cref{def:model} ignores constants.
+To include constants, one would replace $[\sigma(\Delta_{i})]$ with a set that contains all constants associated with domain $\Delta_{i}$, extended with enough new elements to make its cardinality $\sigma(\Delta_{i})$.}
+    \end{equation}
+    \item $\mathfrak{M} \models \phi$ according to the (non-exhaustive)
+          recursive definition below. Let $\chi$ and $\psi$ be formulas,
+          $\Delta$ a domain, $c \in \Delta$ a constant, $\predicate/n$ a
+          predicate associated with domains $\Delta_{1},\dots,\Delta_{n}$, and
+          $t \in \prod_{i=1}^{n} \Delta_{i}$ a tuple of constants.
+    \begin{itemize}
+      \item $\mathfrak{M} \models \predicate(t)$ if and only if (iff)
+            $t \in \mathfrak{M}(\predicate)$.
+      \item $\mathfrak{M} \models \neg\chi$ iff $\mathfrak{M} \not\models \chi$.
+      \item $\mathfrak{M} \models \chi \land \psi$ iff
+            $\mathfrak{M} \models \chi$ and $\mathfrak{M} \models \psi$.
+      \item $\mathfrak{M} \models \chi \lor \psi$ iff
+            $\mathfrak{M} \models \chi$ or $\mathfrak{M} \models \psi$.
+      \item $\mathfrak{M} \models (\forall X \in \Delta\text{. }\chi)$ iff
+            $\mathfrak{M} \models \chi[x/\{\, X \,\}]$ for all constants
+            $x \in \Delta$.
+      \item $\mathfrak{M} \models (\forall X \in \Delta\text{.
+            } X \ne c \Rightarrow \chi)$ iff
+            $\mathfrak{M} \models \chi[x/\{\, X \,\}]$ for all
+            $x \in \Delta \setminus \{\, c \,\}$.
+      \item $\mathfrak{M} \models (\forall X,Y \in \Delta\text{.
+            } X \ne Y \Rightarrow \chi)$ iff
+            $\mathfrak{M} \models \chi[x/\{\, X \,\}][y/\{\, Y \,\}]$ for all
+            $x,y \in \Delta$ s.t. $x \ne y$.
+    \end{itemize}
+  \end{enumerate}
+\end{definition}
 
@@
   commutes by \cref{def:formula} and the definition of $\rho$. In other words,
-  for any predicate $\texttt{p}/n \in \Preds(\psi) = \Preds(\phi)$, function
-  $\rho$ translates the domains associated with $\texttt{p}$ in $\psi$ to the
-  domains associated with $\texttt{p}$ in $\phi$. Let
-  $\pi_{\phi}(\texttt{p}) = {(d_{i})}_{i=1}^{n}$ and
-  $\pi_{\psi}(\texttt{p}) = {(e_{i})}_{i=1}^{n}$ for some domains
-  $d_{i} \in \Doms(\phi)$ and $e_{i} \in \Doms(\psi)$. Since
-  $\rho(e_{i}) = d_{i}$ for all $i = 1, \dots, n$ by the commutativity in
-  \cref{diagram:ref}, we get that
+  for any predicate $\predicate/n \in \Preds(\psi) = \Preds(\phi)$, function
+  $\rho$ translates the domains associated with $\predicate$ in $\psi$ to the
+  domains associated with $\predicate$ in $\phi$. Let
+  $\pi_{\phi}(\predicate) = {(\Delta_{i})}_{i=1}^{n}$ and
+  $\pi_{\psi}(\predicate) = {(\Gamma_{i})}_{i=1}^{n}$ for some domains
+  $\Delta_{i} \in \Doms(\phi)$ and $\Gamma_{i} \in \Doms(\psi)$. Since
+  $\rho(\Gamma_{i}) = \Delta_{i}$ for all $i = 1, \dots, n$ by the commutativity
+  in \cref{diagram:ref}, we get that
   \begin{equation}\label{eq:equality}
-    \prod_{i=1}^{n}[\sigma(d_{i})] = \prod_{i=1}^{n}[\sigma \circ \rho(e_{i})]
+    \prod_{i=1}^{n}[\sigma(\Delta_{i})] = \prod_{i=1}^{n}[\sigma \circ \rho(\Gamma_{i})]
   \end{equation}
   as required. Certainly, any subset of the left-hand side of \cref{eq:equality}
-  (e.g., $\mathfrak{M}(\texttt{p})$, where $\mathfrak{M}$ is a model of
+  (e.g., $\mathfrak{M}(\predicate)$, where $\mathfrak{M}$ is a model of
   $(\phi, \sigma)$) is a subset of the right-hand side and vice versa. Since
@@
 
-In this appendix, we list the exact function definitions produced by
-\textsc{Crane} for all of the problem instances in Section~6 both before and
-after algebraic simplification (excluding multiplications by one). The
-correctness of all of them has been checked by identifying suitable base cases
-and verifying the numerical answers across a range of domain sizes.
+Here we list the exact function definitions produced by \textsc{Crane} for all
+of the problem instances in Section~6 both before and after algebraic
+simplification (excluding multiplications by one). The correctness of all of
+them has been checked by identifying suitable base cases and verifying the
+numerical answers across a range of domain sizes.
 
 \begin{enumerate}
-  \item $\Theta(m)$ solution for counting $\Gamma \to \Gamma$ functions:
+  \item A $\Theta(m)$ solution for counting $\Gamma \to \Gamma$ functions:
         \[
@@
         \]
-  \item $\Theta(m^3 + n^3)$ solution for counting $\Gamma \to \Delta$
+  \item A $\Theta(m^3 + n^3)$ solution for counting $\Gamma \to \Delta$
         surjections:
@@
                      &{\left( \sum_{j=0}^{k} \binom{k}{j} [j < 2] \right)}^{l} \\
-    ={}& \sum_{l=0}^{m} \binom{m}{l}{(-1)}^{m-l} \sum_{k=0}^{n} \binom{n}{k} {(-1)}^{n-k} {(k+1)}^{l}.
+          ={}& \sum_{l=0}^{m} \binom{m}{l}{(-1)}^{m-l}\\
+                     &\sum_{k=0}^{n} \binom{n}{k} {(-1)}^{n-k} {(k+1)}^{l}.
         \end{align*}
-  \item $\Theta(m^{3})$ solution for counting $\Gamma \to \Gamma$ surjections:
+  \item A $\Theta(m^{3})$ solution for counting $\Gamma \to \Gamma$ surjections:
         \begin{align*}
@@
                   &{\left( \sum_{j=0}^{k} \binom{k}{j} [j < 2] \right)}^{l} \\
-    ={}& \sum_{l=0}^{m} \binom{m}{l}{(-1)}^{m-l} \sum_{k=0}^{m} \binom{m}{k} {(-1)}^{m-k} {(k+1)}^{l}.
+          ={}& \sum_{l=0}^{m} \binom{m}{l}{(-1)}^{m-l}\\
+                  &\sum_{k=0}^{m} \binom{m}{k} {(-1)}^{m-k} {(k+1)}^{l}.
         \end{align*}
-  \item $\Theta(mn)$ solution for counting $\Gamma \to \Delta$ injections and
+  \item A $\Theta(mn)$ solution for counting $\Gamma \to \Delta$ injections and
         partial injections (with different base cases):
@@
         \end{align*}
-  \item $\Theta(m^{3})$ solution for counting $\Gamma \to \Gamma$ injections:
+  \item A $\Theta(m^{3})$ solution for counting $\Gamma \to \Gamma$ injections:
         \begin{align*}
@@
         \end{align*}
-  % \item $\Theta(m^{2})$ solution for counting $\Gamma \to \Gamma$ partial
-  %       injections:
-  % \begin{align*}
-  %   f(m) ={}& f(m - 1) + \sum_{l = 0}^{m} \binom{m}{l} \sum_{k = 0}^{m} \binom{m}{k}\\
-  %           &[1 \le l < 3] [k < 2] 2^{m - l} g(m - l, m - k - 1)\\
-  %   ={}& f(m - 1) + m2^{m-1}g(m-1, m-1)\\
-  %   +{}& m^{2}2^{m-1}g(m-1, m-2)\\
-  %   +{}& \binom{m}{2}2^{m-2}g(m-2, m-1) \\
-  %   +{}& \binom{m}{2}m2^{m-2}g(m-2, m-2)\\
-  %   g(i, j) ={}& \sum_{h = 0}^{j} \binom{j}{h} [h < 2] g(i - 1, j - h)\\
-  %   ={}& g(i-1, j) + jg(i-1, j-1).
-  %   \end{align*}
-  \item $\Theta(m)$ solution for counting $\Gamma \to \Delta$ bijections:
+  \item A $\Theta(m)$ solution for counting $\Gamma \to \Delta$ bijections:
         \[
@@
         \]
+  \item A $\Theta(l+mn)$ solution for counting $|\Lambda|$ partial injections
+        $\Gamma \to \Delta$:
+        \begin{align*}
+          f(l, m, n) ={}& {g(m, n)}^{l}\\
+          g(m, n) ={}& \sum_{k=0}^{n}\binom{n}{k} [k < 2] g(m-1, n-k)\\
+          ={}& g(m-1, n) + ng(m-1, n-1).
+        \end{align*}
 \end{enumerate}

### 2023-03-07 doc/paper/paper.tex
Formatting improvements

@@
 
+\SetKwProg{Fn}{Function}{:}{}
+
+\SetKwData{functionCall}{call}
+\SetKwData{functionSignature}{signature}
+\SetKwData{functionNames}{F}
+\SetKwData{domainNames}{D}
+\SetKwData{newDomainNames}{D'}
+\SetKwData{expression}{e}
+\SetKwData{functions}{funs}
+\SetKwData{args}{args}
+
+\SetKwFunction{newFunctionName}{newFunctionName}
+\SetKwFunction{newDomainName}{newDomainName}
+\SetKwFunction{visit}{v}
+\SetKwFunction{actuallyVisit}{visit}
+
 % the following package is optional:
@@
 \newcommand\mdoubleplus{\mathbin{+\mkern-10mu+}}
-\newcommand{\Done}{\mathsf{D}_{1}}
-\newcommand{\Dtwo}{\mathsf{D}_{2}}
-\newcommand{\Dthree}{\mathsf{D}_{3}}
+\newcommand{\Done}{\domainNames_{1}}
+\newcommand{\Dtwo}{\domainNames_{2}}
+\newcommand{\Dthree}{\domainNames_{3}}
 \newcommand{\predicate}{\texttt{\textup{p}}}
-
-\DeclareMathOperator{\friends}{\texttt{friends}}
-\DeclareMathOperator{\smokes}{\texttt{smokes}}
+\newcommand{\predicateq}{\texttt{\textup{q}}}
+\newcommand{\nulll}{\texttt{\textup{null}}}
+
+\DeclareMathOperator{\friends}{\texttt{\textup{friends}}}
+\DeclareMathOperator{\smokes}{\texttt{\textup{smokes}}}
 \DeclareMathOperator{\CR}{\textsc{CR}}
@@
 theory~\cite{DBLP:conf/kr/BremenK21} and applications in enumerative
-combinatorics~\cite{DBLP:conf/ilp/BarvinekB0ZK21,DBLP:journals/corr/abs-2302-04606}.
+combinatorics~\cite{DBLP:conf/ilp/BarvinekB0ZK21}.
 There is also a recent line of work that uses FOMC-based methods to count
@@
 quantifiers)~\cite{DBLP:journals/jair/Kuzelka21,DBLP:conf/aaai/MalhotraS22}, and
-\Ctwo{} extended with axioms describing trees~\cite{DBLP:conf/kr/BremenK21},
-directed acyclic graphs~\cite{DBLP:journals/corr/abs-2302-09830}, and linear
-order~\cite{DBLP:journals/corr/abs-2211-01164}. On the empirical front, there
-are several implementations of exact WFOMC algorithms:
+\Ctwo{} extended with axioms for trees~\cite{DBLP:conf/kr/BremenK21}. On the
+empirical front, there are several implementations of exact WFOMC algorithms:
 \textsc{Alchemy}~\cite{DBLP:journals/cacm/GogateD16},
@@
 with equality to this internal format. We use lowercase Latin letters for
-predicates (e.g., $\texttt{p}$) and constants (e.g., $x$), uppercase Latin
+predicates (e.g., $\predicate$) and constants (e.g., $x$), uppercase Latin
 letters for variables (e.g., $X$), and uppercase Greek letters for domains
-(e.g., $\Delta$). Sometimes we write predicate $\texttt{p}$ as $\texttt{p}/n$,
-where $n \in \mathbb{N}^{+}$ is the \emph{arity} of $\texttt{p}$. An \emph{atom}
-is $\texttt{p}(t_1, \dots, t_n)$ for some predicate $\texttt{p}/n$ and terms
+(e.g., $\Delta$). Sometimes we write predicate $\predicate$ as $\predicate/n$,
+where $n \in \mathbb{N}^{+}$ is the \emph{arity} of $\predicate$. An \emph{atom}
+is $\predicate(t_1, \dots, t_n)$ for some predicate $\predicate/n$ and terms
 $t_{1}, \dots, t_{n}$. A \emph{term} is either a constant or a variable. A
 \emph{literal} is either an atom or the negation of an atom (denoted by
-$\neg \texttt{p}(t_1, \dots, t_n)$). Let $\mathcal{D}$ be the set of all
+$\neg \predicate(t_1, \dots, t_n)$). Let $\mathcal{D}$ be the set of all
 relevant (finite) domains. Initially, $\mathcal{D}$ contains all domains
@@
           \begin{multlined}[t]
-            (\{\, \neg \texttt{p}(X, Y), \neg \texttt{p}(X, Z) \,\}, \{\, (Y, Z) \,\}, \\
+            (\{\, \neg \predicate(X, Y), \neg \predicate(X, Z) \,\}, \{\, (Y, Z) \,\}, \\
             \{\, X \mapsto \Gamma, Y \mapsto \Delta, Z \mapsto \Delta \,\}),
@@
           \begin{multlined}[t]
-            (\{\, \neg \texttt{p}(X, Y), \neg \texttt{p}(Z, Y) \,\}, \{\, (X, Z) \,\}, \\
+            (\{\, \neg \predicate(X, Y), \neg \predicate(Z, Y) \,\}, \{\, (X, Z) \,\}, \\
             \{\, X \mapsto \Gamma, Y \mapsto \Delta, Z \mapsto \Gamma \,\})
@@
   \end{align*}
-  for some predicate $\texttt{p}/2$, variables $X$, $Y$, $Z$, and domains
+  for some predicate $\predicate/2$, variables $X$, $Y$, $Z$, and domains
   $\Gamma$ and $\Delta$. All variables that occur as the first argument to
-  $\texttt{p}$ are in $\Gamma$, and, likewise, all variables that occur as the
-  second argument to $\texttt{p}$ are in $\Delta$. Therefore, $\phi$ `type
+  $\predicate$ are in $\Gamma$, and, likewise, all variables that occur as the
+  second argument to $\predicate$ are in $\Delta$. Therefore, $\phi$ `type
   checks' as a valid formula.
@@
       (\forall X \in \Gamma\text{. }\forall Y, Z \in \Delta\text{. }\\
-      Y \ne Z \Rightarrow \neg \texttt{p}(X, Y) \lor \neg \texttt{p}(X, Z)) \land{}
+      Y \ne Z \Rightarrow \neg \predicate(X, Y) \lor \neg \predicate(X, Z)) \land{}
     \end{multlined}\\
@@
       (\forall X, Z \in \Gamma\text{. }\forall Y \in \Delta\text{. }\\
-      X \ne Z \Rightarrow \neg \texttt{p}(X, Y) \lor \neg \texttt{p}(Z, Y)).
+      X \ne Z \Rightarrow \neg \predicate(X, Y) \lor \neg \predicate(Z, Y)).
     \end{multlined}
@@
   Let $\Delta$ be a domain of size $n \in \mathbb{N}_{0}$. The model count of
-  $\forall X \in \Delta\text{. } \texttt{p}(X) \lor \texttt{q}(X)$ is then
+  $\forall X \in \Delta\text{. } \predicate(X) \lor \predicateq(X)$ is then
   $3^{n}$. Intuitively, since both predicates are of arity one, they can be
   interpreted as subsets of $\Delta$. Thus, the formula says that each element
-  of $\Delta$ has to be included in $\texttt{p}$ or in $\texttt{q}$ or in both,
+  of $\Delta$ has to be included in $\predicate$ or in $\predicateq$ or in both,
   i.e., there are three possibilities.
@@
   $\Delta$. Let us count how many of them satisfy the conditions imposed on
-  predicate $\texttt{p}$. The empty relation does. All four relations of
+  predicate $\predicate$. The empty relation does. All four relations of
   cardinality one (e.g., $\{\, (1, 1) \,\}$) do too. Finally, there are two
@@
   \begin{multline*}
-    (\{\, \neg \texttt{p}(X, Y), \neg \texttt{p}(X, Z) \,\}, \{\, (Y, Z) \,\}, \\
+    (\{\, \neg \predicate(X, Y), \neg \predicate(X, Z) \,\}, \{\, (Y, Z) \,\}, \\
     \{\, X \mapsto \Gamma, Y \mapsto \Delta, Z \mapsto \Delta \,\}).
@@
     c_{1} &= \begin{multlined}[t]
-      (\{\, \neg \texttt{p}(x, Y), \neg \texttt{p}(x, Z) \,\}, \{\, (Y, Z) \,\}, \\
+      (\{\, \neg \predicate(x, Y), \neg \predicate(x, Z) \,\}, \{\, (Y, Z) \,\}, \\
       \{\, Y \mapsto \Delta, Z \mapsto \Delta \,\}),
@@
     c_{2} &= \begin{multlined}[t]
-      (\{\, \neg \texttt{p}(X, Y), \neg \texttt{p}(X, Z) \,\}, \{\, (X, x), (Y, Z) \,\}, \\
+      (\{\, \neg \predicate(X, Y), \neg \predicate(X, Z) \,\}, \{\, (X, x), (Y, Z) \,\}, \\
       \{\, X \mapsto \Gamma', Y \mapsto \Delta, Z \mapsto \Delta \,\}),
@@
   \begin{multline*}
-    (\{\, \neg \texttt{p}(X, Y), \neg \texttt{p}(X, Z) \,\}, \{\, (Y, Z), (X, x) \,\}, \\
+    (\{\, \neg \predicate(X, Y), \neg \predicate(X, Z) \,\}, \{\, (Y, Z), (X, x) \,\}, \\
     \{\, X \mapsto \Gamma, Y \mapsto \Delta, Z \mapsto \Delta \,\}),
@@
   \[
-    (\{\, \neg \texttt{p}(x, Y), \neg \texttt{p}(x, Z) \,\}, \{\, (Y, Z) \,\}, \{\, Y \mapsto \Delta, Z \mapsto \Delta \,\})
+    (\{\, \neg \predicate(x, Y), \neg \predicate(x, Z) \,\}, \{\, (Y, Z) \,\}, \{\, Y \mapsto \Delta, Z \mapsto \Delta \,\})
   \]
@@
   \begin{multline*}
-    (\{\, \neg \texttt{p}(X, Y), \neg \texttt{p}(Z, Y) \,\}, \{\, (X, Z), (X, x), (Z, x) \,\}, \\
+    (\{\, \neg \predicate(X, Y), \neg \predicate(Z, Y) \,\}, \{\, (X, Z), (X, x), (Z, x) \,\}, \\
     \{\, X \mapsto \Gamma, Y \mapsto \Delta, Z \mapsto \Gamma \,\}),
@@
   \[
-    (\{\, \neg \texttt{p}(x, Y), \neg \texttt{p}(Z, Y) \,\}, \{\, (Z, x) \,\}, \{\, Y \mapsto \Delta, Z \mapsto \Gamma \,\}),
+    (\{\, \neg \predicate(x, Y), \neg \predicate(Z, Y) \,\}, \{\, (Z, x) \,\}, \{\, Y \mapsto \Delta, Z \mapsto \Gamma \,\}),
   \]
@@
   \[
-    (\{\, \neg \texttt{p}(X, Y), \neg \texttt{p}(x, Y) \,\}, \{\, (X, x) \,\}, \{\, X \mapsto \Gamma, Y \mapsto \Delta \,\}).
+    (\{\, \neg \predicate(X, Y), \neg \predicate(x, Y) \,\}, \{\, (X, x) \,\}, \{\, X \mapsto \Gamma, Y \mapsto \Delta \,\}).
   \]
@@
           \begin{multlined}[t]
-            (\{\, \neg \texttt{p}(X, Y), \neg \texttt{p}(X, Z) \,\}, \{\, (X, x), (Y, Z) \,\}, \\
+            (\{\, \neg \predicate(X, Y), \neg \predicate(X, Z) \,\}, \{\, (X, x), (Y, Z) \,\}, \\
             \{\, X \mapsto \Gamma, Y \mapsto \Delta, Z \mapsto \Delta \,\}),
@@
           \begin{multlined}[t]
-            (\{\, \neg \texttt{p}(X, Y), \neg \texttt{p}(Z, Y) \,\}, \\
+            (\{\, \neg \predicate(X, Y), \neg \predicate(Z, Y) \,\}, \\
             \{\, (X, x), (Z, X), (Z, x) \,\}, \\
@@
            \begin{multlined}[t]
-             (\{\, \neg \texttt{p}(X, Y), \neg \texttt{p}(X, Z) \,\}, \{\, (Y, Z) \,\}, \\
+             (\{\, \neg \predicate(X, Y), \neg \predicate(X, Z) \,\}, \{\, (Y, Z) \,\}, \\
              \{\, X \mapsto \Gamma', Y \mapsto \Delta, Z \mapsto \Delta \,\}),
@@
            \begin{multlined}[t]
-             (\{\, \neg \texttt{p}(X, Y), \neg \texttt{p}(Z, Y) \,\}, \{\, (Z, X) \,\}, \\
+             (\{\, \neg \predicate(X, Y), \neg \predicate(Z, Y) \,\}, \{\, (Z, X) \,\}, \\
              \{\, X \mapsto \Gamma', Y \mapsto \Delta, Z \mapsto \Gamma' \,\}).
@@
     $\rho \gets \identifyRecursion{$\phi$, $\psi$}$\;
-    \lIf{$\rho \ne {\normalfont \texttt{null}}$}{\Return{$\{\, (\Reff_\rho(v), \langle\rangle) \,\}$}}\label{line:rho}
+    \lIf{$\rho \ne \nulll$}{\Return{$\{\, (\Reff_\rho(v), \langle\rangle) \,\}$}}\label{line:rho}
   }
@@
   \Fn{\identifyRecursion{formula $\phi$, formula $\psi$, map $\rho = \emptyset$}}{
-    \lIf{$|\phi| \ne |\psi|$ {\bf or} $\#\phi \ne \#\psi$}{\Return{\normalfont\texttt{null}}}
+    \lIf{$|\phi| \ne |\psi|$ {\bf or} $\#\phi \ne \#\psi$}{\Return{\nulll}}
     \lIf{$\phi = \emptyset$}{\Return{$\rho$}}
@@
           $\rho' \gets \identifyRecursion{$\phi\setminus\{\, d \,\}$, $\psi\setminus\{\, c \,\}$, $\rho\cup\gamma$}$\;\label{line:recursion}
-          \lIf{$\rho' \ne {\normalfont \texttt{null}}$}{\Return{$\rho'$}}
-        }
-      }
-      \Return{\normalfont\texttt{null}}\;
+          \lIf{$\rho' \ne \nulll$}{\Return{$\rho'$}}
+        }
+      }
+      \Return{\nulll}\;
     }
@@
 For every formula $\psi$ in the cache s.t. $\#\psi = \#\phi$, function
-\texttt{r} is called to check whether a recursive call is feasible. If it is,
-\texttt{r} returns a (total) map $\rho\colon \Doms(\psi) \to \Doms(\phi)$ that
-shows how $\psi$ can be transformed into $\phi$ by replacing each domain
-$\Omega \in \Doms(\psi)$ with $\rho(\Omega) \in \Doms(\phi)$. Otherwise,
-\texttt{r} returns \texttt{null} to signify that $\phi$ and $\psi$ are too
-different for recursion to work. This happens if $\phi$ and $\psi$ (or their
-subformulas explored in recursive calls) are structurally different (i.e., the
-numbers of clauses or the hash codes fail to match) or if a clause of $\psi$
-cannot be paired with a sufficiently similar clause of $\phi$. Function
-\texttt{r} works by iterating over pairs of clauses of $\phi$ and $\psi$ that
-have the same hash codes. For every pair of sufficiently similar clauses,
-\texttt{r} calls itself on the remaining clauses until the map
-$\rho\colon \Doms(\psi) \pfun \Doms(\phi)$ becomes total, and all clauses are
-successfully coupled.
-
-Function \texttt{genMaps} checks the compatibility of a pair of clauses. It
+\identifyRecursion is called to check whether a recursive call is feasible. If
+it is, \identifyRecursion returns a (total) map
+$\rho\colon \Doms(\psi) \to \Doms(\phi)$ that shows how $\psi$ can be
+transformed into $\phi$ by replacing each domain $\Omega \in \Doms(\psi)$ with
+$\rho(\Omega) \in \Doms(\phi)$. Otherwise, \identifyRecursion returns \nulll{}
+to signify that $\phi$ and $\psi$ are too different for recursion to work. This
+happens if $\phi$ and $\psi$ (or their subformulas explored in recursive calls)
+are structurally different (i.e., the numbers of clauses or the hash codes fail
+to match) or if a clause of $\psi$ cannot be paired with a sufficiently similar
+clause of $\phi$. Function \identifyRecursion works by iterating over pairs of
+clauses of $\phi$ and $\psi$ that have the same hash codes. For every pair of
+sufficiently similar clauses, \identifyRecursion calls itself on the remaining
+clauses until the map $\rho\colon \Doms(\psi) \pfun \Doms(\phi)$ becomes total,
+and all clauses are successfully coupled.
+
+Function \generateMaps checks the compatibility of a pair of clauses. It
 considers every possible bijection $\beta\colon \Vars(c) \to \Vars(d)$ and map
@@
   any formula selected on \cref{line:selectformula} of the algorithm s.t.\
-  $\rho \ne {\normalfont\texttt{null}}$ on \cref{line:rho}. Let $\sigma$ be a
-  domain size function. Then the set of models of $(\psi, \sigma \circ \rho)$ is
-  equal to the set of models of $(\phi, \sigma)$.
+  $\rho \ne \nulll$ on \cref{line:rho}. Let $\sigma$ be a domain size function.
+  Then the set of models of $(\psi, \sigma \circ \rho)$ is equal to the set of
+  models of $(\phi, \sigma)$.
 \end{theorem}
@@
   \caption{Construct functions from an FCG}\label{alg:interpretation}
-  \SetKwProg{Fn}{Function}{:}{}
-
-  \SetKwData{functionCall}{call}
-  \SetKwData{functionSignature}{signature}
-  \SetKwData{functionNames}{F}
-  \SetKwData{domainNames}{D}
-  \SetKwData{newDomainNames}{D'}
-  \SetKwData{expression}{e}
-  \SetKwData{functions}{funs}
-  \SetKwData{args}{args}
-
-  \SetKwFunction{newFunctionName}{newFunctionName}
-  \SetKwFunction{newDomainName}{newDomainName}
-  \SetKwFunction{visit}{v}
-  \SetKwFunction{actuallyVisit}{visit}
-
   \KwIn{$\mathcal{D}$---the set of domains of the input formula}
@@
 Given some node $v$ as input, both \visit and \actuallyVisit return a pair
-$(\mathsf{e}, \mathsf{funs})$. Here, $\mathsf{e}$ is the algebraic expression
-that represent $v$, and $\mathsf{funs}$ is a list of auxiliary functions that
-were created while formulating $\mathsf{e}$.
-
-The algorithm gradually constructs two partial maps $\mathsf{F}$ and
-$\mathsf{D}$ that give names to functions and domains, respectively.
-$\mathsf{F}$ is a global variable that maps FCG nodes to function names (e.g.,
-$f$, $g$). $\mathsf{D}$ maps domains to their names, and it is passed as an
+$(\expression, \functions)$. Here, \expression is the algebraic expression that
+represent $v$, and \functions is a list of auxiliary functions that were created
+while formulating \expression.
+
+The algorithm gradually constructs two partial maps \functionNames and
+\domainNames that give names to functions and domains, respectively.
+\functionNames is a global variable that maps FCG nodes to function names (e.g.,
+$f$, $g$). \domainNames maps domains to their names, and it is passed as an
 argument to \visit and \actuallyVisit. Here, a \emph{domain name} is either a
@@
 generate previously-unused names. The latter also takes an FCG node as input and
-links it with the new name in $\mathsf{F}$.
+links it with the new name in \functionNames.
 
@@
   and $\Dthree \coloneqq \Dtwo \cup \{\, \Gamma' \mapsto (m-1) \,\}$ denote
-  versions of $\mathsf{D}$ at various points throughout the algorithm's
+  versions of \domainNames at various points throughout the algorithm's
   execution. Here, $l$, $m$, and $n$ are all arbitrary names generated by
@@
 
-  \Cref{line:varnames} initialises $\mathsf{D}$ to $\Done$. Once \visit{$\GDR$,
+  \Cref{line:varnames} initialises \domainNames to $\Done$. Once \visit{$\GDR$,
     $\Done$} is called on \cref{line:initialcall}, \newFunctionName updates
-  $\mathsf{F}$ to $\{\, \GDR \mapsto f \,\}$, where $f$ is a new function name.
-  There are no non-atomic names in $\Done$, so \cref{line:nonone,line:nontwo}
-  are skipped, and calls to \actuallyVisit{$\GDR$, $\Done$} and
+  \functionNames to $\{\, \GDR \mapsto f \,\}$, where $f$ is a new function
+  name. There are no non-atomic names in $\Done$, so
+  \cref{line:nonone,line:nontwo} are skipped, and calls to
+  \actuallyVisit{$\GDR$, $\Done$} and
   $\visit/\actuallyVisit{$\bigvee$, $\Done$}$ follow. Here, $\Done$ becomes
@@
   \]
-  \textsf{args} is set to $\langle m-1, n-l \rangle$ on \cref{line:args}, and
-  the output expression becomes $f(m-1, n-l)$. The call to
-  \actuallyVisit{$\land$, $\Dthree$} then returns the product of the two
-  expressions $[l<2]f(m-1, n-l)$. Next, the call to \actuallyVisit{$\bigvee$,
-    $\Done$} prepends a summation and returns $\sum_{l=0}^{n}[l<2]f(m-1,n-l)$.
-  The same expression (and an empty list of functions) is then returned to
+  \args is set to $\langle m-1, n-l \rangle$ on \cref{line:args}, and the output
+  expression becomes $f(m-1, n-l)$. The call to \actuallyVisit{$\land$,
+    $\Dthree$} then returns the product of the two expressions
+  $[l<2]f(m-1, n-l)$. Next, the call to \actuallyVisit{$\bigvee$, $\Done$}
+  prepends a summation and returns $\sum_{l=0}^{n}[l<2]f(m-1,n-l)$. The same
+  expression (and an empty list of functions) is then returned to
   \cref{line:actuallyvisit} of the call to \visit{$\GDR$, $\Done$}. Here, both
-  \textsf{call} and \textsf{signature} are set to $f(m, n)$. As the definition
+  \functionCall and \functionSignature are set to $f(m, n)$. As the definition
   of $f$ is the final answer and not part of some other algebraic expression,
@@
 
-% TODO: emphasise that there are two parts: search (with some artificial limit)
-% + inference (whose complexity we can easily determine)
-
 We compare \textsc{Crane} and
@@
 on their ability to count various kinds of functions. This class of instances is
-chosen because of its simplicity and ubiquity and the inability of
-state-of-the-art WFOMC algorithms to solve many such instances. Note that other
+chosen because of its simplicity and ubiquity and the inability of publicly
+available WFOMC algorithms to solve many such instances. Note that other exact
 WFOMC algorithms mentioned in \cref{sec:introduction} are unable to solve any of
@@
 \textsc{ForcLift} then translates these sentences in first-order logic to
-formulas as defined in \cref{def:formula}.
-
-Let $\texttt{p}$ be a predicate that models relations between sets $\Gamma$ and
+formulas as in \cref{def:formula}.
+
+Let $\predicate$ be a predicate that models relations between sets $\Gamma$ and
 $\Delta$. To restrict all such relations to just $\Gamma \to \Delta$ functions,
@@
 \[
-  \forall X \in \Gamma\text{. }\forall Y,Z \in \Delta\text{. }\texttt{p}(X, Y) \land \texttt{p}(X, Z) \Rightarrow Y = Z
+  \forall X \in \Gamma\text{. }\forall Y,Z \in \Delta\text{. }\predicate(X, Y) \land \predicate(X, Z) \Rightarrow Y = Z
 \]
@@
 \begin{equation}\label{eq:def2}
-  \forall X \in \Gamma\text{. }\exists Y \in \Delta\text{. }\texttt{p}(X, Y).
+  \forall X \in \Gamma\text{. }\exists Y \in \Delta\text{. }\predicate(X, Y).
 \end{equation}
@@
 \[
-  \forall X,Z \in \Gamma\text{. }\forall Y \in \Delta\text{. }\texttt{p}(X, Y) \land \texttt{p}(Z, Y) \Rightarrow X = Z
+  \forall X,Z \in \Gamma\text{. }\forall Y \in \Delta\text{. }\predicate(X, Y) \land \predicate(Z, Y) \Rightarrow X = Z
 \]
-to restrict $\texttt{p}$ to injections or
-  $\forall Y \in \Delta\text{. }\exists X \in \Gamma\text{. }\texttt{p}(X, Y)$
+to restrict $\predicate$ to injections or
+  $\forall Y \in \Delta\text{. }\exists X \in \Gamma\text{. }\predicate(X, Y)$
 to ensure surjectivity or remove \cref{eq:def2} to consider partial functions.
@@
 % how the complexity of a solution is determined
-Previous work often compares WFOMC algorithms by running them on a few instances
-with increasing domain sizes and measuring
-runtime~\cite{DBLP:conf/nips/Broeck11,DBLP:conf/ijcai/BroeckTMDR11,DBLP:conf/aaai/BroeckD12}.
-However, we can do much better and identify the exact worst-case asymptotic
-complexity of a solution produced by either \textsc{Crane} or \textsc{ForcLift}.
-The asymptotic complexity of a solution can be determined by considering the
-total number of arithmetic operations needed to follow the definitions of
-constituent functions without recomputing the same quantity multiple times. In
-particular, we assume that each function call and binomial coefficient is
-computed at most once. We also assume that computing $\binom{n}{k}$ takes
-$\Theta(nk)$ time. For example, the complexity of \cref{eq:solution} is
-$\Theta(mn)$ since $f(m, n)$ can be computed by a dynamic programming algorithm
-that computes $f(i, j)$ for all $i = 0, \dots, m$ and $j = 0, \dots, n$, taking
-a constant amount of time on each $f(i, j)$.
+
+% Previous work often compares WFOMC algorithms by running them on a few instances
+% with increasing domain sizes and measuring
+% runtime~\cite{DBLP:conf/nips/Broeck11,DBLP:conf/ijcai/BroeckTMDR11,DBLP:conf/aaai/BroeckD12}.
+% However, we can do better and identify the exact worst-case asymptotic
+% complexity of a solution produced by either \textsc{Crane} or \textsc{ForcLift}.
+
+Recall that, in the case of \textsc{ForcLift}, the process of solving a (W)FOMC
+problem consists of two parts: compilation (via search) and propagation. (A
+similar dichotomy applies to \textsc{Crane} as well.) The complexity of the
+former depends only on the formula and so far has received very little attention
+with the exception of Beame et al.~\shortcite{DBLP:conf/pods/BeameBGS15}. The
+complexity of the latter, on the other hand, is a function of domain sizes and
+can be determined exactly (without measuring runtime). We establish the
+asymptotic complexity of a solution by counting the total number of arithmetic
+operations needed to follow the definitions of constituent functions without
+recomputing the same quantity multiple times. In particular, we assume that each
+function call and binomial coefficient is computed at most once. We also assume
+that computing $\binom{n}{k}$ takes $\Theta(nk)$ time. For example, the
+complexity of \cref{eq:solution} is $\Theta(mn)$ since $f(m, n)$ can be computed
+by a dynamic programming algorithm that computes $f(i, j)$ for all
+$i = 0, \dots, m$ and $j = 0, \dots, n$, taking a constant amount of time on
+each $f(i, j)$.
+
+% In particular, the complexity of computing total surjections is by
+% Earnest~\shortcite{30049}, and all other such complexities are inferred from the
+% formulas and programs on the on-line encyclopedia of integer
+% sequences~\cite{oeis}.
 
@@
 to the manually-constructed ways of computing the same quantities that have been
-proposed before. In particular, the complexity of computing total surjections is
-by Earnest~\shortcite{30049}, and all other such complexities are inferred from
-the formulas and programs on the on-line encyclopedia of integer
-sequences~\cite{oeis}. Examining the last two columns of the table, we see that
-the two algorithms perform equally well on instances that could already be
-solved by \textsc{ForcLift}. However, \textsc{Crane} can also solve all but one
-of the instances that \textsc{ForcLift} fails on in at most cubic time. See
+proposed
+before.\footnote{\url{https://scicomp.stackexchange.com/q/30049}}\textsuperscript{,}\footnote{\url{https://oeis.org}}
+Examining the last two columns of the table, we see that the two algorithms
+perform equally well on instances that could already be solved by
+\textsc{ForcLift}. However, \textsc{Crane} can also solve all but one of the
+instances that \textsc{ForcLift} fails on in at most cubic time. See
 supplementary material for the exact solutions produced by \textsc{Crane}.
@@
 that are already supported by \textsc{ForcLift} remain feasible for
-\textsc{Crane} as well. Moreover, our algorithm can also handle the linear order
-axiom, for which a bespoke algorithm was recently proposed by T{\'{o}}th and
-Ku\v{z}elka~\shortcite{DBLP:journals/corr/abs-2211-01164}. To demonstrate that
-\textsc{Crane} is capable of finding efficient solutions to problems beyond
-known domain-liftable fragments such as \Ctwo{}, we run \textsc{Crane} in greedy
-search mode on the following formula:
+\textsc{Crane} as well. To demonstrate that \textsc{Crane} is capable of finding
+efficient solutions to problems beyond known domain-liftable fragments such as
+\Ctwo{}, we run \textsc{Crane} in greedy search mode on the following formula:
 \begin{equation}\label[formula]{eq:ternary}
@@
       (\forall X,W \in \Gamma\text{. }\forall Y \in \Delta\text{. }\forall Z \in \Lambda\text{. }\\
-      \texttt{p}(X, Y, Z) \land \texttt{p}(W, Y, Z) \Rightarrow X = W) \land{}
+      \predicate(X, Y, Z) \land \predicate(W, Y, Z) \Rightarrow X = W) \land{}
     \end{multlined}\\
@@
       (\forall X \in \Gamma\text{. }\forall Y,W \in \Delta\text{. }\forall Z \in \Lambda\text{. }\\
-      \texttt{p}(X, Y, Z) \land \texttt{p}(X, W, Z) \Rightarrow Y = W).
+      \predicate(X, Y, Z) \land \predicate(X, W, Z) \Rightarrow Y = W).
     \end{multlined}
@@
 For every element $z$ of $\Lambda$, \cref{eq:ternary} restricts
-$\texttt{p}(X, Y, z)$ to be a $\Gamma \to \Delta$ partial injection, independent
-of $\texttt{p}(X, Y, z')$ for any $z' \ne z$. \textsc{Crane} instantly returns a
+$\predicate(X, Y, z)$ to be a $\Gamma \to \Delta$ partial injection, independent
+of $\predicate(X, Y, z')$ for any $z' \ne z$. \textsc{Crane} instantly returns a
 solution of complexity $\Theta(l+mn)$, where $l = |\Lambda|$.
@@
     &\begin{multlined}[t][0.9\linewidth]
-      (\forall X_{1} \in \Delta_{1}\text{. }\dots\,\forall X_{n} \in \Delta_{n}\text{. }\forall Y \in \Delta_{i}\text{. }\texttt{\textup{p}}(X_{1}, \dots, X_{n}) \land{}\\
-      \texttt{\textup{p}}(X_{1}, \dots, X_{i-1}, Y, X_{i+1}, \dots, X_{n}) \Rightarrow X_{i} = Y) \land{}
+      (\forall X_{1} \in \Delta_{1}\text{. }\dots\,\forall X_{n} \in \Delta_{n}\text{. }\forall Y \in \Delta_{i}\text{. }\predicate(X_{1}, \dots, X_{n}) \land{}\\
+      \predicate(X_{1}, \dots, X_{i-1}, Y, X_{i+1}, \dots, X_{n}) \Rightarrow X_{i} = Y) \land{}
     \end{multlined}\\
     &\begin{multlined}[t][0.9\linewidth]
-      (\forall X_{1} \in \Delta_{1}\text{. }\dots\,\forall X_{n} \in \Delta_{n}\text{. }\forall Y \in \Delta_{j}\text{. }\texttt{\textup{p}}(X_{1}, \dots, X_{n}) \land{}\\
-      \texttt{\textup{p}}(X_{1}, \dots, X_{j-1}, Y, X_{j+1}, \dots, X_{n}) \Rightarrow X_{j} = Y)
+      (\forall X_{1} \in \Delta_{1}\text{. }\dots\,\forall X_{n} \in \Delta_{n}\text{. }\forall Y \in \Delta_{j}\text{. }\predicate(X_{1}, \dots, X_{n}) \land{}\\
+      \predicate(X_{1}, \dots, X_{j-1}, Y, X_{j+1}, \dots, X_{n}) \Rightarrow X_{j} = Y)
     \end{multlined}
   \end{align*}
-  for some predicate $\texttt{\textup{p}}/n$, domains
+  for some predicate $\predicate/n$, domains
   $\Delta_{1}, \dots, \Delta_{n}$, and $i, j \in \{\, 1, \dots, n \,\}$. Then
@@
 \textsc{Crane} could be beneficial to research in combinatorics as
-well~\cite{DBLP:conf/ilp/BarvinekB0ZK21,DBLP:journals/corr/abs-2302-04606}.
-
-% TODO: The reference list should not include unpublished work. (earnest + OEIS + 3 corr references)
-% TODO: replace all instances of {p} with \predicate (by hand)
+well~\cite{DBLP:conf/ilp/BarvinekB0ZK21}.
+
 \bibliographystyle{kr}

### 2023-03-08 doc/paper/paper.tex
An experiment

@@
 % make sure the result table (as well as other floating objects) are on the right pages
-% make sure the abstract, introduction, and conclusion are all in line with each other
-% maybe improve the indentation of equations
+% reread the entire paper
 
@@
 \newcommand{\predicateq}{\texttt{\textup{q}}}
+\newcommand{\predicates}{\texttt{\textup{s}}}
+\newcommand{\predicater}{\texttt{\textup{r}}}
 \newcommand{\nulll}{\texttt{\textup{null}}}
@@
 
-% TODO: I think I said this the last time, but along with the complexities as a
-% way of representing the empirical evaluation, I think you should also include
-% a few plots, even if they say nothing more than what the table already says.
-% The point is that the readers can see what this behaviour looks like so even
-% if you include a few plots and say we just give a few representative examples
-% and the rest follow the table of all that will be better [an experiment with
-% non-partial endo injections?]
-
 We compare \textsc{Crane} and
@@
 supplementary material for the exact solutions produced by \textsc{Crane}.
+
+\subsubsection{A Comparison with \textsc{\normalfont FastWFOMC}}
+
+\begin{figure}[t]
+  \includegraphics{plot}
+  \caption{The runtime data of \textsc{FastWFOMC} on the problem of counting
+    permutations together with a quartic regression model fitted on all of the
+    data and a linear model fitted on the first half of the data points.}
+\end{figure}
+
+\begin{itemize}
+  \item permutations of a set (i.e., bijective/injective endofunctions)
+  \item an extension of \textsc{FastWFOMC}~\cite{DBLP:conf/uai/BremenK21} with
+        cardinality constraints as described by
+        Ku\v{z}elka~\shortcite{DBLP:journals/jair/Kuzelka21}, provided by one of
+        the authors of \textsc{FastWFOMC}.
+  \item can be described in \FOtwo{} with cardinality constraints as
+  \begin{align*}
+    &(|\predicate| = |\Delta|) \land{}\\
+    &(\forall X, Y \in \Delta\text{. } \predicater(X) \lor \neg \predicate(X, Y)) \land{}\\
+    &(\forall X, Y \in \Delta\text{. } \predicates(X) \lor \neg\predicate(Y, X)),
+  \end{align*}
+        where $\predicater$ and $\predicates$ are Skolem predicates as described
+        by Van den Broeck et al.~\shortcite{DBLP:conf/kr/BroeckMD14}, and
+        $|\Delta|$ ranges from 1 to 50.
+  \item \textsc{FastWFOMC} was run on an AMD Ryzen~7~5800H processor with
+        \SI{16}{\giga\byte} of memory, running Arch Linux~6.2.2-arch1-1 and
+        Python~3.10.9.
+  \item degrees 4--7 are about equally well-fitting (maybe include the fit
+        numbers?)
+\end{itemize}
 

### 2023-03-08 doc/paper/plot.tex
An experiment

% Created by tikzDevice version 0.12.3.1 on 2023-03-08 13:57:11
% !TEX encoding = UTF-8 Unicode
\documentclass[10pt]{article}
\usepackage{tikz}

\usepackage[active,tightpage,psfixbb]{preview}

\PreviewEnvironment{pgfpicture}

\setlength\PreviewBorder{0pt}
\begin{document}

\begin{tikzpicture}[x=1pt,y=1pt]
\definecolor{fillColor}{RGB}{255,255,255}
\path[use as bounding box,fill=fillColor,fill opacity=0.00] (0,0) rectangle (239.21,148.15);
\begin{scope}
\path[clip] ( 36.11, 30.69) rectangle (233.71,142.65);
\definecolor{drawColor}{gray}{0.92}

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 36.11, 51.57) --
	(233.71, 51.57);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 36.11, 81.09) --
	(233.71, 81.09);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 36.11,110.61) --
	(233.71,110.61);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 36.11,140.13) --
	(233.71,140.13);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 59.76, 30.69) --
	( 59.76,142.65);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 96.42, 30.69) --
	( 96.42,142.65);

\path[draw=drawColor,line width= 0.3pt,line join=round] (133.08, 30.69) --
	(133.08,142.65);

\path[draw=drawColor,line width= 0.3pt,line join=round] (169.74, 30.69) --
	(169.74,142.65);

\path[draw=drawColor,line width= 0.3pt,line join=round] (206.40, 30.69) --
	(206.40,142.65);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 36.11, 36.81) --
	(233.71, 36.81);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 36.11, 66.33) --
	(233.71, 66.33);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 36.11, 95.85) --
	(233.71, 95.85);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 36.11,125.37) --
	(233.71,125.37);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 41.43, 30.69) --
	( 41.43,142.65);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 78.09, 30.69) --
	( 78.09,142.65);

\path[draw=drawColor,line width= 0.6pt,line join=round] (114.75, 30.69) --
	(114.75,142.65);

\path[draw=drawColor,line width= 0.6pt,line join=round] (151.41, 30.69) --
	(151.41,142.65);

\path[draw=drawColor,line width= 0.6pt,line join=round] (188.07, 30.69) --
	(188.07,142.65);

\path[draw=drawColor,line width= 0.6pt,line join=round] (224.73, 30.69) --
	(224.73,142.65);
\definecolor{drawColor}{RGB}{0,0,0}
\definecolor{fillColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 45.09, 36.81) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 48.76, 36.81) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 52.43, 36.81) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 56.09, 36.81) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 59.76, 36.81) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 63.42, 36.82) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 67.09, 36.82) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 70.76, 36.82) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 74.42, 36.83) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 78.09, 36.83) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 81.75, 36.84) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 85.42, 36.85) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 89.09, 36.87) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 92.75, 36.89) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 96.42, 36.92) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (100.08, 37.06) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (103.75, 37.00) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (107.42, 37.05) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (111.08, 37.12) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (114.75, 37.20) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (118.42, 37.30) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (122.08, 37.44) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (125.75, 37.58) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (129.41, 37.77) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (133.08, 38.01) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (136.75, 38.27) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (140.41, 38.63) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (144.08, 39.00) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (147.74, 39.52) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (151.41, 40.24) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (155.08, 40.81) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (158.74, 41.68) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (162.41, 43.30) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (166.07, 43.85) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (169.74, 45.33) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (173.41, 47.04) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (177.07, 48.94) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (180.74, 51.21) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (184.40, 53.81) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (188.07, 57.94) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (191.74, 62.58) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (195.40, 65.03) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (199.07, 71.20) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (202.74, 75.90) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (206.40, 82.86) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (210.07, 93.40) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (213.73,100.82) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (217.40,111.86) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (221.07,123.28) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (224.73,137.56) circle (  1.96);
\definecolor{drawColor}{RGB}{217,95,2}

\path[draw=drawColor,line width= 1.1pt,line join=round] ( 45.09, 38.60) --
	( 47.37, 37.94) --
	( 49.64, 37.39) --
	( 51.91, 36.93) --
	( 54.19, 36.56) --
	( 56.46, 36.27) --
	( 58.74, 36.06) --
	( 61.01, 35.91) --
	( 63.28, 35.82) --
	( 65.56, 35.78) --
	( 67.83, 35.78) --
	( 70.11, 35.82) --
	( 72.38, 35.89) --
	( 74.65, 35.99) --
	( 76.93, 36.11) --
	( 79.20, 36.25) --
	( 81.48, 36.40) --
	( 83.75, 36.56) --
	( 86.02, 36.72) --
	( 88.30, 36.88) --
	( 90.57, 37.04) --
	( 92.85, 37.20) --
	( 95.12, 37.35) --
	( 97.39, 37.49) --
	( 99.67, 37.62) --
	(101.94, 37.74) --
	(104.21, 37.84) --
	(106.49, 37.94) --
	(108.76, 38.02) --
	(111.04, 38.08) --
	(113.31, 38.14) --
	(115.58, 38.18) --
	(117.86, 38.22) --
	(120.13, 38.24) --
	(122.41, 38.26) --
	(124.68, 38.27) --
	(126.95, 38.29) --
	(129.23, 38.30) --
	(131.50, 38.32) --
	(133.78, 38.35) --
	(136.05, 38.39) --
	(138.32, 38.45) --
	(140.60, 38.53) --
	(142.87, 38.64) --
	(145.15, 38.79) --
	(147.42, 38.97) --
	(149.69, 39.20) --
	(151.97, 39.48) --
	(154.24, 39.82) --
	(156.51, 40.23) --
	(158.79, 40.71) --
	(161.06, 41.27) --
	(163.34, 41.93) --
	(165.61, 42.69) --
	(167.88, 43.55) --
	(170.16, 44.53) --
	(172.43, 45.65) --
	(174.71, 46.90) --
	(176.98, 48.30) --
	(179.25, 49.86) --
	(181.53, 51.59) --
	(183.80, 53.51) --
	(186.08, 55.62) --
	(188.35, 57.94) --
	(190.62, 60.48) --
	(192.90, 63.25) --
	(195.17, 66.27) --
	(197.44, 69.56) --
	(199.72, 73.11) --
	(201.99, 76.96) --
	(204.27, 81.11) --
	(206.54, 85.59) --
	(208.81, 90.40) --
	(211.09, 95.56) --
	(213.36,101.08) --
	(215.64,107.00) --
	(217.91,113.31) --
	(220.18,120.05) --
	(222.46,127.22) --
	(224.73,134.85);
\definecolor{drawColor}{RGB}{27,158,119}

\path[draw=drawColor,line width= 1.1pt,line join=round] ( 45.09, 36.59) --
	( 47.37, 36.61) --
	( 49.64, 36.64) --
	( 51.91, 36.66) --
	( 54.19, 36.68) --
	( 56.46, 36.71) --
	( 58.74, 36.73) --
	( 61.01, 36.75) --
	( 63.28, 36.78) --
	( 65.56, 36.80) --
	( 67.83, 36.82) --
	( 70.11, 36.85) --
	( 72.38, 36.87) --
	( 74.65, 36.89) --
	( 76.93, 36.92) --
	( 79.20, 36.94) --
	( 81.48, 36.97) --
	( 83.75, 36.99) --
	( 86.02, 37.01) --
	( 88.30, 37.04) --
	( 90.57, 37.06) --
	( 92.85, 37.08) --
	( 95.12, 37.11) --
	( 97.39, 37.13) --
	( 99.67, 37.15) --
	(101.94, 37.18) --
	(104.21, 37.20) --
	(106.49, 37.22) --
	(108.76, 37.25) --
	(111.04, 37.27) --
	(113.31, 37.30) --
	(115.58, 37.32) --
	(117.86, 37.34) --
	(120.13, 37.37) --
	(122.41, 37.39) --
	(124.68, 37.41) --
	(126.95, 37.44) --
	(129.23, 37.46) --
	(131.50, 37.48) --
	(133.78, 37.51) --
	(136.05, 37.53) --
	(138.32, 37.55) --
	(140.60, 37.58) --
	(142.87, 37.60) --
	(145.15, 37.63) --
	(147.42, 37.65) --
	(149.69, 37.67) --
	(151.97, 37.70) --
	(154.24, 37.72) --
	(156.51, 37.74) --
	(158.79, 37.77) --
	(161.06, 37.79) --
	(163.34, 37.81) --
	(165.61, 37.84) --
	(167.88, 37.86) --
	(170.16, 37.88) --
	(172.43, 37.91) --
	(174.71, 37.93) --
	(176.98, 37.96) --
	(179.25, 37.98) --
	(181.53, 38.00) --
	(183.80, 38.03) --
	(186.08, 38.05) --
	(188.35, 38.07) --
	(190.62, 38.10) --
	(192.90, 38.12) --
	(195.17, 38.14) --
	(197.44, 38.17) --
	(199.72, 38.19) --
	(201.99, 38.21) --
	(204.27, 38.24) --
	(206.54, 38.26) --
	(208.81, 38.28) --
	(211.09, 38.31) --
	(213.36, 38.33) --
	(215.64, 38.36) --
	(217.91, 38.38) --
	(220.18, 38.40) --
	(222.46, 38.43) --
	(224.73, 38.45);
\end{scope}
\begin{scope}
\path[clip] ( 36.11, 30.69) rectangle (233.71,142.65);
\definecolor{drawColor}{RGB}{217,95,2}
\definecolor{fillColor}{RGB}{255,255,255}

\path[draw=drawColor,line width= 0.3pt,line join=round,line cap=round,fill=fillColor] (179.66,120.51) --
	(218.89,120.51) --
	(218.82,120.52) --
	(219.11,120.53) --
	(219.39,120.59) --
	(219.66,120.69) --
	(219.92,120.83) --
	(220.14,121.02) --
	(220.33,121.24) --
	(220.49,121.48) --
	(220.60,121.75) --
	(220.67,122.03) --
	(220.70,122.32) --
	(220.70,122.32) --
	(220.70,132.33) --
	(220.70,132.33) --
	(220.67,132.62) --
	(220.60,132.91) --
	(220.49,133.17) --
	(220.33,133.42) --
	(220.14,133.64) --
	(219.92,133.82) --
	(219.66,133.97) --
	(219.39,134.07) --
	(219.11,134.13) --
	(218.89,134.14) --
	(179.66,134.14) --
	(179.88,134.13) --
	(179.59,134.14) --
	(179.30,134.10) --
	(179.02,134.02) --
	(178.75,133.90) --
	(178.52,133.73) --
	(178.31,133.53) --
	(178.13,133.30) --
	(178.00,133.04) --
	(177.90,132.77) --
	(177.86,132.48) --
	(177.85,132.33) --
	(177.85,122.32) --
	(177.86,122.47) --
	(177.86,122.18) --
	(177.90,121.89) --
	(178.00,121.61) --
	(178.13,121.36) --
	(178.31,121.12) --
	(178.52,120.92) --
	(178.75,120.76) --
	(179.02,120.63) --
	(179.30,120.55) --
	(179.59,120.52) --
	cycle;
\end{scope}
\begin{scope}
\path[clip] ( 36.11, 30.69) rectangle (233.71,142.65);
\definecolor{drawColor}{RGB}{217,95,2}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (199.27,123.53) {Quartic};
\definecolor{drawColor}{RGB}{27,158,119}
\definecolor{fillColor}{RGB}{255,255,255}

\path[draw=drawColor,line width= 0.3pt,line join=round,line cap=round,fill=fillColor] (185.61, 41.17) --
	(218.87, 41.17) --
	(218.79, 41.17) --
	(219.08, 41.18) --
	(219.37, 41.24) --
	(219.64, 41.34) --
	(219.89, 41.49) --
	(220.12, 41.67) --
	(220.31, 41.89) --
	(220.47, 42.14) --
	(220.58, 42.40) --
	(220.65, 42.69) --
	(220.67, 42.98) --
	(220.67, 42.98) --
	(220.67, 52.99) --
	(220.67, 52.99) --
	(220.65, 53.28) --
	(220.58, 53.56) --
	(220.47, 53.83) --
	(220.31, 54.07) --
	(220.12, 54.29) --
	(219.89, 54.48) --
	(219.64, 54.62) --
	(219.37, 54.72) --
	(219.08, 54.78) --
	(218.87, 54.80) --
	(185.61, 54.80) --
	(185.83, 54.78) --
	(185.54, 54.79) --
	(185.25, 54.76) --
	(184.97, 54.68) --
	(184.71, 54.55) --
	(184.47, 54.39) --
	(184.26, 54.19) --
	(184.09, 53.95) --
	(183.95, 53.70) --
	(183.86, 53.42) --
	(183.81, 53.13) --
	(183.81, 52.99) --
	(183.81, 42.98) --
	(183.81, 43.12) --
	(183.81, 42.83) --
	(183.86, 42.54) --
	(183.95, 42.27) --
	(184.09, 42.01) --
	(184.26, 41.78) --
	(184.47, 41.58) --
	(184.71, 41.41) --
	(184.97, 41.29) --
	(185.25, 41.21) --
	(185.54, 41.17) --
	cycle;
\end{scope}
\begin{scope}
\path[clip] ( 36.11, 30.69) rectangle (233.71,142.65);
\definecolor{drawColor}{RGB}{27,158,119}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (202.24, 44.18) {Linear};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (239.21,148.15);
\definecolor{drawColor}{gray}{0.30}

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 31.16, 33.78) {0};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 31.16, 63.30) {250};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 31.16, 92.82) {500};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 31.16,122.34) {750};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (239.21,148.15);
\definecolor{drawColor}{gray}{0.30}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 41.43, 19.68) {0};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 78.09, 19.68) {10};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (114.75, 19.68) {20};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (151.41, 19.68) {30};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (188.07, 19.68) {40};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (224.73, 19.68) {50};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (239.21,148.15);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (134.91,  7.64) {Domain size};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (239.21,148.15);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at ( 13.08, 86.67) {Runtime (s)};
\end{scope}
\end{tikzpicture}

\end{document}

### 2023-03-09 doc/paper/paper.tex
Almost done?

--- 2023-03-07 doc/paper/paper.tex
@@
   Challenges, Progress, and Conjectures}
-
-% TODO (at the very end)
-% grammarly the whole thing (supplementary material as well)
-% make sure the result table (as well as other floating objects) are on the right pages
-% make sure the abstract, introduction, and conclusion are all in line with each other
-% maybe improve the indentation of equations
 
@@
       In some cases, these functions can benefit from algebraic simplification.
-      If some of the functions are defined recursively, base cases need to be
+      If some functions are defined recursively, base cases need to be
       established. One can then compute the model count of $\phi$ by running the
@@
   \caption{A comparison of how \textsc{ForcLift} and \textsc{Crane} can be used
-    to compute the model count of a formula $\phi$.}\label{fig:process}
+    to compute the model count of a formula $\phi$}\label{fig:process}
 \end{figure*}
@@
 modelling~\cite{DBLP:series/synthesis/2016Raedt,DBLP:journals/ml/KimmigMG15,DBLP:journals/ml/RichardsonD06}.
-Lifted inference techniques for probabilistic databases, while developed
-somewhat independently, have also been inspired by
+Lifted inference techniques for probabilistic databases have also been inspired
+by
 WFOMC~\cite{DBLP:journals/pvldb/GatterbauerS15,DBLP:journals/debu/GribkoffSB14}.
 While WFOMC has received more attention in the literature, FOMC is an
-interesting problem in an of itself because of its connections to finite model
+interesting problem in and of itself because of its connections to finite model
 theory~\cite{DBLP:conf/kr/BremenK21} and applications in enumerative
-combinatorics~\cite{DBLP:conf/ilp/BarvinekB0ZK21}.
-There is also a recent line of work that uses FOMC-based methods to count
-solutions to constraint satisfaction
-problems~\cite{DBLP:journals/jair/TotisDRK23}.
+combinatorics~\cite{DBLP:conf/ilp/BarvinekB0ZK21}. Totis et
+al.~\shortcite{DBLP:journals/jair/TotisDRK23} proposed an FOMC-based approach to
+counting solutions to constraint satisfaction problems.
 
@@
 if it can be solved in time polynomial in the size(s) of the
-domain(s)~\cite{DBLP:conf/starai/JaegerB12}. Over more than a decade, many
-classes of instances were shown to be liftable. First, Van den
-Broeck~\shortcite{DBLP:conf/nips/Broeck11} showed that the class of all
-sentences of first-order logic with up to two variables (denoted \FOtwo{}) is
-liftable. Then Beame et al.~\shortcite{DBLP:conf/pods/BeameBGS15} proved that
-there exists a sentence with three variables for which FOMC is
-$\#\P_{1}$-complete (i.e., \FOthree{} is not liftable). Since these two seminal
-results, most of the research on (W)FOMC focused on developing faster solutions
-for the \FOtwo{}
+domain(s)~\cite{DBLP:conf/starai/JaegerB12}. Many classes of instances are known
+to be liftable. First, Van den Broeck~\shortcite{DBLP:conf/nips/Broeck11} showed
+that the class of all sentences of first-order logic with up to two variables
+(denoted \FOtwo{}) is liftable. Then Beame et
+al.~\shortcite{DBLP:conf/pods/BeameBGS15} proved that there exists a sentence
+with three variables for which FOMC is $\#\P_{1}$-complete (i.e., \FOthree{} is
+not liftable). Since these two seminal results, most research on (W)FOMC focused
+on developing faster solutions for the \FOtwo{}
 fragment~\cite{DBLP:conf/uai/BremenK21,DBLP:conf/aaai/MalhotraS22} and defining
@@
 
-In this work, we show how to relax these restrictions in a way that results in a
-stronger algorithm, capable of handling more instances in a lifted manner. The
-ideas presented in this paper are implemented in \textsc{Crane}---an extension
-of the (W)FOMC algorithm \textsc{ForcLift}. The differences in how these
-algorithms operate are depicted in \cref{fig:process}. Compilation is performed
-by applying various \emph{(compilation) rules} to the input (or some derivative)
-formula, gradually constructing a circuit (in the case of \textsc{ForcLift}) or
-a graph (in the case of \textsc{Crane}). \textsc{ForcLift} applies compilation
-rules via greedy search, whereas \textsc{Crane} also supports a hybrid search
-algorithm that applies some rules greedily and some using breadth-first
-search.\footnote{In the current implementation, the rules that are applied in a
-  non-greedy fashion are: atom counting, inclusion-exclusion, independent
-  partial groundings, Shannon decomposition, shattering, and two of our new
-  rules introduced in \cref{sec:dr,sec:ref}---see previous
-  work~\cite{DBLP:conf/ijcai/BroeckTMDR11} for more information about the
-  rules.} This alternative was introduced because there is no reason to expect
-greedy search to be complete. Another major difference is that---in
-\textsc{Crane}---the product of compilation is not directly evaluated but rather
-transformed into a collection of functions on domain sizes. Hence, our approach
-is reminiscent of previous work on lifted inference via compilation to C++
-programs~\cite{DBLP:conf/kr/KazemiP16} and the broader area of functional
+In this work, we show how to relax these restrictions in a way that results in
+an algorithm capable of handling more instances in a lifted manner. The ideas
+presented in this paper are implemented in \textsc{Crane}---an extension of the
+(W)FOMC algorithm \textsc{ForcLift}. The differences in how these algorithms
+operate are depicted in \cref{fig:process}. Compilation is performed by applying
+various \emph{(compilation) rules} to the input (or some derivative) formula,
+gradually constructing a circuit (in the case of \textsc{ForcLift}) or a graph
+(in the case of \textsc{Crane}). \textsc{ForcLift} applies compilation rules via
+greedy search, whereas \textsc{Crane} also supports a hybrid search algorithm
+that applies some rules greedily and some using breadth-first
+search.\footnote{In the current implementation, the rules applied in a
+  non-greedily are: atom counting, inclusion-exclusion, independent partial
+  groundings, Shannon decomposition, shattering, and two new rules described in
+  \cref{sec:dr,sec:ref}---see previous work~\cite{DBLP:conf/ijcai/BroeckTMDR11}
+  for more information about the rules.} This alternative was introduced because
+there is no reason to expect greedy search to be complete. Another difference is
+that---in \textsc{Crane}---the product of compilation is not directly evaluated
+but transformed into a collection of functions on domain sizes. Hence, our
+approach is reminiscent of previous work on lifted inference via compilation to
+C++ programs~\cite{DBLP:conf/kr/KazemiP16} and the broader area of functional
 synthesis~\cite{DBLP:conf/cav/GoliaRM20,DBLP:conf/pldi/KuncakMPS10,sanathanan1963transfer}.
@@
 
-The use of labelled directed graphs in lieu of circuits enables \textsc{Crane}
-to construct recursive solutions by representing recursive function calls via
+Using labelled directed graphs instead of circuits enables \textsc{Crane} to
+construct recursive solutions by representing recursive function calls via
 cycle-inducing edges. A hypothetical instance of compilation could proceed as
@@
 $n \in \mathbb{N}_{0}$. \emph{Generalised domain recursion} (GDR)---one of the
-new compilation rules---transforms $\phi$ into a different formula $\psi$ that
-has an additional constant and some new \emph{constraints}. After some
-additional transformations, the constraints in $\psi$ become `uniform' and can
-be removed, replacing the domain of size $n$ with a new domain of size
-$n-1$---this is the responsibility of the \emph{constraint removal} (CR)
-compilation rule. Afterwards, another compilation rule recognizes that the
-resulting formula matches the input formula $\phi$ except for referring to a
-different domain. This observation allows us to add a cycle-forming edge to the
-graph, which can be interpreted as function $f$ relying on $f(n-1)$ to compute
-$f(n)$.
+new compilation rules---transforms $\phi$ into a different formula $\psi$ with
+an additional constant and some \emph{constraints}. After some more
+transformations, the constraints in $\psi$ can be removed, replacing the domain
+of size $n$ with a new domain of size $n-1$---this is the responsibility of the
+\emph{constraint removal} (CR) compilation rule. Afterwards, another compilation
+rule recognises that the resulting formula matches the input formula $\phi$
+except for referring to a different domain. This observation allows us to add a
+cycle-forming edge to the graph, which can be interpreted as a function $f$
+relying on $f(n-1)$ to compute $f(n)$.
 
@@
 introduces the new compilation rules. \Cref{sec:interpret} describes an
-algorithm that can convert such a graph into a collection of (potentially
-recursive) functions. In \cref{sec:results}, we compare \textsc{ForcLift} and
-\textsc{Crane} on a range of counting problems. We show that:
+algorithm that converts such a graph into a collection of (potentially
+recursive) functions. \Cref{sec:results} compares \textsc{ForcLift} and
+\textsc{Crane} on various counting problems. We show that:
 \begin{enumerate*}[label=(\roman*)]
@@
 \end{enumerate*}
-Finally, in \cref{sec:conclusion}, we conclude by outlining some conjectures and
-directions for future work.
+Finally, \cref{sec:conclusion} outlines some conjectures and directions for
+future work.
 
@@
 
-Our representation of FOMC instances is largely based on the format used
-internally by \textsc{ForcLift}, some aspects of which are described by Van den
-Broeck et al.~\shortcite{DBLP:conf/ijcai/BroeckTMDR11}. \textsc{ForcLift} can
-translate sentences in a variant of function-free many-sorted first-order logic
-with equality to this internal format. We use lowercase Latin letters for
-predicates (e.g., $\predicate$) and constants (e.g., $x$), uppercase Latin
-letters for variables (e.g., $X$), and uppercase Greek letters for domains
-(e.g., $\Delta$). Sometimes we write predicate $\predicate$ as $\predicate/n$,
-where $n \in \mathbb{N}^{+}$ is the \emph{arity} of $\predicate$. An \emph{atom}
-is $\predicate(t_1, \dots, t_n)$ for some predicate $\predicate/n$ and terms
+Our representation of FOMC instances builds on the format used internally by
+\textsc{ForcLift}, some aspects of which are described by Van den Broeck et
+al.~\shortcite{DBLP:conf/ijcai/BroeckTMDR11}. \textsc{ForcLift} can translate
+sentences in a variant of function-free many-sorted first-order logic with
+equality to this internal format. We use lowercase Latin letters for predicates
+(e.g., $\predicate$) and constants (e.g., $x$), uppercase Latin letters for
+variables (e.g., $X$), and uppercase Greek letters for domains (e.g., $\Delta$).
+Sometimes we write predicate $\predicate$ as $\predicate/n$, where
+$n \in \mathbb{N}^{+}$ is the \emph{arity} of $\predicate$. An \emph{atom} is
+$\predicate(t_1, \dots, t_n)$ for some predicate $\predicate/n$ and terms
 $t_{1}, \dots, t_{n}$. A \emph{term} is either a constant or a variable. A
-\emph{literal} is either an atom or the negation of an atom (denoted by
+\emph{literal} is either an atom or the negation thereof (denoted by
 $\neg \predicate(t_1, \dots, t_n)$). Let $\mathcal{D}$ be the set of all
@@
 mentioned by the input formula. During compilation, new domains are added to
-$\mathcal{D}$ by some of the compilation rules. Each such new domain is
-interpreted as a subset of some other domain in $\mathcal{D}$.
-
-We use $\langle\cdot\rangle$ to denote lists, $|\cdot|$ for the length of a
-list, and $\mdoubleplus$ for list concatenation. We write $\pfun$ to denote
-partial functions and $\dom(\cdot)$ for the domain of a function. Let $\Doms$ be
-the function that maps any clause or formula to the set of domains used within.
-Similarly, let $\Vars$ be the function that maps clauses and sets of either
-literals or constraints to the set of variables in them. Let $S$ be a set of
-constraints or literals, $V$ a set of variables, and $x$ a variable or a
-constant. We write $S[x/V]$ to denote $S$ with all occurrences of all variables
-in $V$ replaced with $x$.
+$\mathcal{D}$. Each new domain is interpreted as a subset of another domain in
+$\mathcal{D}$.
+
+We write $\langle\cdot\rangle$ for lists, $|\cdot|$ for the length of a list,
+and $\mdoubleplus$ for list concatenation. We write $\pfun$ to denote partial
+functions and $\dom(\cdot)$ for the domain of a function. Let $\Doms$
+(respectively, $\Vars$) be the function that maps any expression to the set of
+domains (respectively, variables) used in it. Let $S$ be a set of constraints or
+literals, $V$ a set of variables, and $x$ a variable or a constant. We write
+$S[x/V]$ to denote $S$ with all occurrences of all variables in $V$ replaced
+with $x$.
 
@@
   An \emph{(inequality) constraint} is a pair $(a, b)$, where $a$ is a variable,
-  and $b$ is either a variable or a constant. As the name implies, it constrains
-  $a$ and $b$ to be unequal.
+  and $b$ is a variable or a constant. It constrains $a$ and $b$ to be
+  different.
 \end{definition}
@@
 \begin{definition}[Clause]\label{def:clause}
-  A \emph{clause} is a triple $c = (L, E, \delta_c)$, where $L$ is a set of
-  literals, $E$ is a set of constraints, and $\delta_c$ is the domain map.
-  \emph{Domain map} $\delta_{c}\colon \Vars(c) \to \mathcal{D}$ is a function
-  that maps all variables in $c$ to their domains such that (s.t.) if
-  $(X, Y) \in E$ for some variables $X$ and $Y$, then
-  $\delta_c(X) = \delta_c(Y)$. For convenience, we sometimes write $\delta_c$
-  for the domain map of $c$ without unpacking $c$ into its three constituents.
+  A \emph{clause} is $c = (L, E, \delta_c)$, where $L$ is a set of literals, $E$
+  is a set of constraints, and $\delta_c$ is the domain map. \emph{Domain map}
+  $\delta_{c}\colon \Vars(c) \to \mathcal{D}$ is a function that maps all
+  variables in $c$ to their domains such that (s.t.) if $(X, Y) \in E$ for some
+  variables $X$ and $Y$, then $\delta_c(X) = \delta_c(Y)$. For convenience, we
+  sometimes write $\delta_c$ for the domain map of $c$ without unpacking $c$
+  into its three constituents.
 \end{definition}
@@
   $\predicate$ are in $\Gamma$, and, likewise, all variables that occur as the
-  second argument to $\predicate$ are in $\Delta$. Therefore, $\phi$ `type
-  checks' as a valid formula.
+  second argument to $\predicate$ are in $\Delta$. Therefore, $\phi$ is a valid
+  formula.
 \end{example}
 
-One can read a formula in our format as a sentence in first-order logic. All
-variables in a clause are implicitly universally quantified, and all clauses in
-a formula are implicitly linked by a conjunction. Thus, formula $\phi$ from
+One can read such a formula as a sentence in first-order logic. All variables in
+a clause are implicitly universally quantified, and all clauses in a formula are
+implicitly linked by a conjunction. Thus, formula $\phi$ from
 \cref{example:first} reads as
@@
 
-There are two major differences between
-\cref{def:constraint,def:clause,def:formula} and the corresponding concepts
-introduced by Van den Broeck et
+There are two differences between \cref{def:constraint,def:clause,def:formula}
+and the corresponding concepts by Van den Broeck et
 al.~\shortcite{DBLP:conf/ijcai/BroeckTMDR11}.\footnote{Van den Broeck et
@@
 constraints of the form $X \not\in \Delta$ for some variable $X$ and domain
-$\Delta$, we exclude such constraints simply because they are not needed. Note
-that if, e.g., $Y \ne Z$ in \cref{eq:formula} is replaced by $Y = Z$, then
+$\Delta$, we exclude these constraints simply because they are inessential. Note
+that if we replace $Y \ne Z$ in \cref{eq:formula} with $Y = Z$, then
 \cref{eq:formula} can be simplified to have one fewer variables. Similarly, if
@@
   interpreted as subsets of $\Delta$. Thus, the formula says that each element
-  of $\Delta$ has to be included in $\predicate$ or in $\predicateq$ or in both,
-  i.e., there are three possibilities.
+  of $\Delta$ has to be in $\predicate$ or $\predicateq$ or both.
 \end{example}
@@
   } \smokes(X) \land \friends(X, Y) \Rightarrow \smokes(Y)$. Letting
-  $n \coloneqq |\Delta|$ as in \cref{example:simple}, the model count can be
-  expressed as
+  $n \coloneqq |\Delta|$ as before, the model count is
   $\sum_{k=0}^{n} \binom{n}{k}2^{n^{2} - k(n-k)}$~\cite{DBLP:conf/kr/BroeckMD14}.
@@
 \begin{example}
-  Let $\phi$ be as in \cref{example:first} and let
-  $\Gamma = \Delta = \{\,1, 2\,\}$, i.e., $\sigma(\Gamma) = \sigma(\Delta) = 2$.
-  There are $2^{2 \times 2} = 16$ possible relations between $\Gamma$ and
-  $\Delta$. Let us count how many of them satisfy the conditions imposed on
-  predicate $\predicate$. The empty relation does. All four relations of
-  cardinality one (e.g., $\{\, (1, 1) \,\}$) do too. Finally, there are two
-  relations of cardinality two---$\{\, (1, 1), (2, 2) \,\}$ and
-  $\{\, (1, 2), (2, 1) \,\}$---that satisfy the conditions as well. Thus, the
-  FOMC of $(\phi, \sigma)$ is 7. Incidentally, the FOMC of $\phi$ counts partial
-  injections from $\Gamma$ to $\Delta$. We will continue to use the problem of
-  counting partial injections (and the formula from \cref{example:first}
-  specifically) as the main running example.
+  Let $\phi$ be as in \cref{example:first} and $\Gamma = \Delta = \{\,1, 2\,\}$,
+  i.e., $\sigma(\Gamma) = \sigma(\Delta) = 2$. There are $2^{2 \times 2} = 16$
+  possible relations between $\Gamma$ and $\Delta$. Let us count how many of
+  them satisfy the conditions imposed on predicate $\predicate$. The empty
+  relation does. All four relations of cardinality one (e.g.,
+  $\{\, (1, 1) \,\}$) do too. Finally, there are two relations of cardinality
+  two---$\{\, (1, 1), (2, 2) \,\}$ and $\{\, (1, 2), (2, 1) \,\}$---that satisfy
+  the conditions as well. Therefore, the FOMC of $(\phi, \sigma)$ is 7.
+  Incidentally, the FOMC of $\phi$ counts partial injections from $\Gamma$ to
+  $\Delta$. We will continue to use the problem of counting partial injections
+  as the main running example.
 \end{example}
@@
 to first-order logic via \emph{first-order d-DNNF (FO d-DNNF) circuits}. FO
-d-DNNF circuits (hereafter simply called \emph{circuits}) are directed acyclic
-graphs with nodes corresponding to formulas in first-order logic---see
+d-DNNF circuits (hereafter called \emph{circuits}) are directed acyclic graphs
+with nodes corresponding to formulas in first-order logic---see
 \cref{fig:simplecircuit} for an example. The following types of nodes are
@@
 
-In this paper, we introduce \emph{first-order computational graphs} (FCGs) that
-generalise circuits by dispensing with acyclicity. Formally, an FCG is a (weakly
-connected) directed graph with a single source, node labels, and ordered
-outgoing edges. Node labels consist of two parts: the \emph{type} and the
-\emph{parameters}. The type of a node determines its out-degree. We make the
-following changes and additions to the node types already supported by
-\textsc{ForcLift}. First, we introduce a new node type for constraint removal
-($\CR$). Second, we replace domain recursion with generalised domain recursion
-($\GDR$). And third, for reasoning about partially-constructed FCGs, we write
-$\star$ for a placeholder type that is yet to be replaced. We write $T_p$ for an
-FCG that has a node with label $T_p$ (i.e., type $T$ and parameter(s) $p$) and
-$\star$'s as all of its direct successors. We also write $T_p(v)$ for an FCG
-with one edge from a node labelled $T_{p}$ to some other node $v$ (and no other
-nodes or edges). See \cref{fig:examplefcg} for an example FCG\@.
+We introduce \emph{first-order computational graphs} (FCGs) that generalise
+circuits by dispensing with acyclicity. An FCG is a (weakly connected) directed
+graph with a single source, node labels, and ordered outgoing edges. Node labels
+consist of two parts: the \emph{type} and the \emph{parameters}. The type of a
+node determines its out-degree. We make the following changes to the node types
+already supported by \textsc{ForcLift}. First, we introduce a new type for
+constraint removal ($\CR$). Second, we replace domain recursion with generalised
+domain recursion ($\GDR$). And third, for reasoning about partially-constructed
+FCGs, we write $\star$ for a placeholder type that is yet to be replaced. We
+write $T_p$ for an FCG that has a node with label $T_p$ (i.e., type $T$ and
+parameter(s) $p$) and $\star$'s as all of its direct successors. We also write
+$T_p(v)$ for an FCG with one edge from a node labelled $T_{p}$ to another node
+$v$. See \cref{fig:examplefcg} for an example FCG\@.
 
 % Connecting FCGs with formulas
-Finally, we introduce a structure that represents a solution to a (W)FOMC
-problem while it is still being built. A \emph{chip} is a pair $(G, L)$, where
-$G$ is an FCG, and $L$ is a list of formulas, s.t. $|L|$ is equal to the number
-of $\star$'s in $G$. $L$ contains formulas that still need to be compiled. Once
-a formula is compiled, it replaces one of the $\star$'s in $G$ according to a
-set order. We say that an FCG is \emph{complete} (i.e., it represents a
-\emph{complete solution}) if it has no $\star$'s. Similarly, a chip is complete
-if its FCG is complete (or, equivalently, the list of formulas is empty).
+Finally, we introduce a structure that represents a solution while it is still
+being built. A \emph{chip} is a pair $(G, L)$, where $G$ is an FCG, and $L$ is a
+list of formulas, s.t. $|L|$ is equal to the number of $\star$'s in $G$. $L$
+contains formulas that still need to be compiled. Once a formula is compiled, it
+replaces one of the $\star$'s in $G$ according to a set order. We call an FCG
+\emph{complete} (i.e., it represents a \emph{complete solution}) if it has no
+$\star$'s. Similarly, a chip is complete if its FCG is complete.
 
@@
 A \emph{(compilation) rule} takes a formula and returns a set of chips. The
-cardinality of this set is the number of different ways in which the rule can be
-applied to the input formula. While
-\textsc{ForcLift}~\cite{DBLP:conf/ijcai/BroeckTMDR11} heuristically chooses one
-of them, in an attempt to not miss a solution, \textsc{Crane} returns them all.
-In particular, if a rule returns an empty set, then that rule does not apply to
-the formula.
+cardinality of this set is the number of ways the rule can be applied to the
+input formula. While \textsc{ForcLift}~\cite{DBLP:conf/ijcai/BroeckTMDR11}
+heuristically chooses one of them, in an attempt to not miss a solution,
+\textsc{Crane} returns them all. In particular, if a rule returns an empty set,
+then that rule does not apply to the formula.
 
@@
 % Main idea
-The main idea behind domain recursion (both the original version by Van den
+The main idea behind domain recursion (the original version by Van den
 Broeck~\shortcite{DBLP:conf/nips/Broeck11} and the one presented here) is as
@@
 formula are then partitioned into three parts based on whether the
-transformation introduced constants or constraints or both. The aforementioned
-conditions ensure that these parts can be treated independently.
+transformation introduced constants, constraints, or both. The conditions ensure
+that these parts can be treated independently.
 
@@
 $\Omega \in \mathcal{D}$, there must be at least one variable with domain
-$\Omega$ that is featured in a literal (and not just in constraints). Without
-such variables, GDR would have no effect on the formula. GDR is also simpler in
-that the expanded formula is left as-is to be handled by other compilation
-rules. Typically, after a few more rules are applied, a combination of $\CR$ and
-$\Reff$ nodes introduces a cycle-inducing edge back to the $\GDR$ node, thus
-completing the definition of a recursive function. The GDR compilation rule is
-summarised as \cref{alg:domainrecursion} and explained in more detail using the
-example below.
+$\Omega$ featured in a literal (and not just in constraints). Without such
+variables, GDR would have no effect on the formula. The expanded formula is then
+left as-is to be handled by other compilation rules. Typically, after a few more
+rules are applied, a combination of $\CR$ and $\Reff$ nodes introduces a
+cycle-inducing edge back to the $\GDR$ node, thus completing the definition of a
+recursive function. The GDR compilation rule is summarised as
+\cref{alg:domainrecursion} and explained in more detail using the example below.
 
@@
   Let $\phi \coloneqq \{\, c_1, c_2 \,\}$ be the formula from
-  \cref{example:first}. While GDR is possible on both domains, here we
-  illustrate how it works on $\Gamma$. Having chosen a domain, the algorithm
-  iterates over the clauses of $\phi$. Suppose \cref{line:forclause} picks
-  $c = c_1$ as the first clause. Then, set $V$ is constructed to contain all
-  variables with domain $\Omega = \Gamma$ that occur in the literals of clause
-  $c$. In this case, $V = \{\, X \,\}$.
+  \cref{example:first}. While GDR is possible on both domains, we illustrate how
+  it works on $\Gamma$. The algorithm iterates over the clauses of $\phi$.
+  Suppose \cref{line:forclause} picks $c = c_1$ as the first clause. Then, set
+  $V$ is constructed to contain all variables with domain $\Omega = \Gamma$ that
+  occur in the literals of clause $c$. In this case, $V = \{\, X \,\}$.
 
@@
   unsatisfiable formulas. We impose two restrictions on $W$. First,
-  $W^2 \cap E = \emptyset$ ensures that there are no pairs of variables in $W$
-  that are constrained to be distinct, since that would result in an $x \ne x$
-  constraint after substitution. Similarly, we want to avoid variables in $W$
-  that have inequality constraints with constants: after the substitution, such
-  constraints would transform into inequality constraints between two constants.
-  In this case, both subsets of $V$ satisfy these conditions, and
-  \cref{line:generation} generates two clauses for the output formula:
+  $W^2 \cap E = \emptyset$ ensures that no pairs of variables in $W$ are
+  constrained to be distinct since that would result in an $x \ne x$ constraint
+  after substitution. Similarly, we want to avoid variables in $W$ that have
+  inequality constraints with constants: after the substitution, such
+  constraints transform into inequality constraints between two constants. In
+  this case, both subsets of $V$ satisfy the conditions, and
+  \cref{line:generation} generates two clauses:
   \begin{multline*}
@@
 
-  When \cref{line:forclause} picks $c = c_2$, then $V = \{\, X, Z \,\}$. The
+  When \cref{line:forclause} picks $c = c_2$, we have $V = \{\, X, Z \,\}$. The
   subset $W = V$ fails to satisfy the conditions on \cref{line:conditions}
@@
 
-Note that \Cref{thm:correctness1} is equivalent to Proposition~3 by Van den
+\Cref{thm:correctness1} is equivalent to Proposition~3 by Van den
 Broeck~\shortcite{DBLP:conf/nips/Broeck11}. For the proofs of this and other
@@
 for some constant $x \in \Omega$ and family of variables $X_i \in \Omega$. Once
-certain conditions are satisfied, we can eliminate these constraints and replace
-$\Omega$ with a new domain $\Omega'$, which can be interpreted as
-$\Omega \setminus \{\, x \,\}$. These conditions are that a constraint of the
-form $X \ne x$ exists for all variables $X \in \Omega$ across all clauses, and
-such constraints are the only place where $x$ occurs. We formalise the
-conditions as \cref{def:replaceable}.
+some conditions are satisfied, we can eliminate these constraints and replace
+$\Omega$ with a new domain $\Omega' \coloneqq \Omega \setminus \{\, x \,\}$.
+These conditions are that a constraint of the form $X \ne x$ exists for all
+variables $X \in \Omega$ across all clauses, and such constraints are the only
+place where $x$ occurs. We formalise the conditions as \cref{def:replaceable}.
 
 \begin{definition}\label{def:replaceable}
-  With respect to a formula $\phi$, a pair $(\Omega, x)$ of a domain
+  For a formula $\phi$, a pair $(\Omega, x)$ of a domain
   $\Omega \in \mathcal{D}$ and its element $x \in \Omega$ is called
@@
 
-Once a replaceable pair is found, \cref{alg:constraintremoval} proceeds to
-construct the new formula by removing constraints (on
-\cref{line:constraintremoval}) and constructing a new domain map $\delta'$ that
-replaces $\Omega$ with $\Omega'$ (on \cref{line:newdelta}).
+Once a replaceable pair is found, \cref{alg:constraintremoval} constructs the
+new formula by removing constraints and defining a new domain map $\delta'$ that
+replaces $\Omega$ with $\Omega'$.
 
@@
   Let $\phi$ be the input formula of \cref{alg:constraintremoval}, $(\Omega, x)$
-  a replaceable pair, and $\phi'$ the formula constructed by the algorithm, when
-  $(\Omega, x)$ is selected on \cref{line:crconditions}. Then
-  $\phi \equiv \phi'$, where the domain $\Omega'$ introduced on
-  \cref{line:newdomain} is interpreted as $\Omega \setminus \{\, x \,\}$.
+  a replaceable pair, and $\phi'$ the output formula for when $(\Omega, x)$ is
+  selected on \cref{line:crconditions}. Then $\phi \equiv \phi'$, where the
+  domain $\Omega'$ introduced on \cref{line:newdomain} is interpreted as
+  $\Omega \setminus \{\, x \,\}$.
 \end{theorem}
@@
 \subsubsection{Hashing}
-We use (integer-valued) hash functions to discard pairs of formulas that are too
-different for recursion to work. The hash code of a clause
-$c = (L, E, \delta_{c})$ (denoted by $\# c$) combines the hash codes of the sets
-of constants and predicates in $c$, the numbers of positive and negative
-literals, the number of inequality constraints $|E|$, and the number of
-variables $|\Vars(c)|$. The hash code of a formula $\phi$ combines the hash
-codes of all its clauses and is denoted by $\#\phi$.
+We use (integer-valued) hash functions to discard pairs of formulas too
+different for recursion. The hash code of a clause $c = (L, E, \delta_{c})$
+(denoted by $\# c$) combines the hash codes of the sets of constants and
+predicates in $c$, the numbers of positive and negative literals, the number of
+inequality constraints $|E|$, and the number of variables $|\Vars(c)|$. The hash
+code of a formula $\phi$ combines the hash codes of all its clauses and is
+denoted by $\#\phi$.
 
 \subsubsection{Caching}
-\textsc{ForcLift}~\cite{DBLP:conf/ijcai/BroeckTMDR11} uses a cache to check if
-a formula is identical to one of the formulas that have already been fully
+\textsc{ForcLift}~\cite{DBLP:conf/ijcai/BroeckTMDR11} uses a cache to check if a
+formula is identical to one of the formulas that have already been fully
 compiled. To facilitate recursion, we extend the caching scheme to include
-formulas that have been encountered but not fully compiled yet. Formally, we
-define a \emph{cache} to be a map from integers (e.g., hash codes) to sets of
-pairs of the form $(\phi, v)$, where $\phi$ is a formula, and $v$ is an FCG
-node.
+formulas encountered before but not fully compiled yet. Formally, we define a
+\emph{cache} as a map from integers (e.g., hash codes) to sets of pairs of the
+form $(\phi, v)$, where $\phi$ is a formula, and $v$ is an FCG node.
 
@@
 For every formula $\psi$ in the cache s.t. $\#\psi = \#\phi$, function
-\identifyRecursion is called to check whether a recursive call is feasible. If
-it is, \identifyRecursion returns a (total) map
+\identifyRecursion checks whether a recursive call is feasible. If it is,
+\identifyRecursion returns a (total) map
 $\rho\colon \Doms(\psi) \to \Doms(\phi)$ that shows how $\psi$ can be
@@
 clause of $\phi$. Function \identifyRecursion works by iterating over pairs of
-clauses of $\phi$ and $\psi$ that have the same hash codes. For every pair of
-sufficiently similar clauses, \identifyRecursion calls itself on the remaining
-clauses until the map $\rho\colon \Doms(\psi) \pfun \Doms(\phi)$ becomes total,
-and all clauses are successfully coupled.
-
+clauses of $\phi$ and $\psi$ with the same hash codes. For every pair of similar
+clauses, \identifyRecursion calls itself on the remaining clauses until the map
+$\rho\colon \Doms(\psi) \pfun \Doms(\phi)$ becomes total.
+
+% TODO: double check the first sentence and if this paragraph still makes sense
 Function \generateMaps checks the compatibility of a pair of clauses. It
@@
 $\gamma\colon \Doms(c) \to \Doms(d)$ s.t.
-\[
-  \begin{tikzcd}
-    \Vars(c) \ar[r, dashed, "\beta"] \arrow[d, swap, "\delta_c"] & \Vars(d) \ar[d, "\delta_d"] \\
-    \Doms(c) \ar[r, dashed, "\gamma"] \ar[d, hookrightarrow] & \Doms(d) \ar[d, hookrightarrow] \\
-    \Doms(\psi) \ar[r, swap, "\rho", "|" marking, outer sep=5pt] & \Doms(\phi).
-  \end{tikzcd}
-\]
-commutes, and $c$ becomes equal to $d$ when its variables are replaced according
-to $\beta$ and its domains replaced according to $\gamma$. The function then
-returns each such $\gamma$ as soon as possible. The commutativity check also
-ensures that $\rho \cup \gamma$ is possible on \cref{line:recursion} of
-\cref{alg:trycache}. The resulting (partial) function $\rho \cup \gamma$ is the
-unique function s.t. $\rho \cup \gamma|_{\dom(\rho)} = \rho$, and
-$\rho \cup \gamma|_{\dom(\gamma)} = \gamma$. The operation is defined when
-$\rho|_{\dom(\rho)\cap\dom(\gamma)} = \gamma|_{\dom(\rho)\cap\dom(\gamma)}$.
+\begin{enumerate*}[label=(\roman*)]
+  \item $\delta_{d} \circ \beta(X) = \rho \circ \delta_{c}(X)$ for all
+  $X \in \Vars(c)$,
+  \item $\gamma(\Omega) = \rho(\Omega)$ for all $\Omega \in \Doms(c)$, and
+  \item $c$ becomes equal to $d$ when its variables are replaced according to
+  $\beta$, and its domains replaced according to $\gamma$.
+\end{enumerate*}
+The function then returns each such $\gamma$ as soon as possible.
+
+% The
+% commutativity check also ensures that $\rho \cup \gamma$ is possible on
+% \cref{line:recursion} of \cref{alg:trycache}. The resulting (partial) function
+% $\rho \cup \gamma$ is the unique function s.t.
+% $\rho \cup \gamma|_{\dom(\rho)} = \rho$, and
+% $\rho \cup \gamma|_{\dom(\gamma)} = \gamma$. The operation is defined when
+% $\rho|_{\dom(\rho)\cap\dom(\gamma)} = \gamma|_{\dom(\rho)\cap\dom(\gamma)}$.
+
+% \[
+%   \begin{tikzcd}
+%     \Vars(c) \ar[r, dashed, "\beta"] \arrow[d, swap, "\delta_c"] & \Vars(d) \ar[d, "\delta_d"] \\
+%     \Doms(c) \ar[r, dashed, "\gamma"] \ar[d, hookrightarrow] & \Doms(d) \ar[d, hookrightarrow] \\
+%     \Doms(\psi) \ar[r, swap, "\rho", "|" marking, outer sep=5pt] & \Doms(\phi).
+%   \end{tikzcd}
+% \]
 
@@
 
-As \textsc{ForcLift} only supports $\Reff$ nodes for when the two formulas are
-equal, our approach is significantly more general and can even construct more
-complex recursive calls such as $f(n-k-2)$.
+As \textsc{ForcLift} only supports $\Reff$ nodes when the two formulas are
+equal, our approach is much more general and capable of creating function calls
+as complex as $f(n-k-2)$.
 
@@
 
-\Cref{alg:interpretation} describes how to construct a list of function
-definitions from a (complete) FCG\@. The algorithm consists of two main
-functions: \visit and \actuallyVisit. The former handles new function
-definitions while the latter produces an algebraic interpretation of each node
-depending on its type. As there are many node types, we only include the ones
-pertinent to the contributions of this paper; see previous
-work~\cite{DBLP:conf/ijcai/BroeckTMDR11} for information about the other types.
-Given some node $v$ as input, both \visit and \actuallyVisit return a pair
-$(\expression, \functions)$. Here, \expression is the algebraic expression that
-represent $v$, and \functions is a list of auxiliary functions that were created
-while formulating \expression.
+\Cref{alg:interpretation} constructs a list of function definitions from an
+FCG\@. The algorithm consists of two main functions: \visit and \actuallyVisit.
+The former handles new function definitions, while the latter produces an
+algebraic interpretation of each node depending on its type. As there are many
+node types, we only include the ones pertinent to the contributions of this
+paper; see previous work~\cite{DBLP:conf/ijcai/BroeckTMDR11} for information
+about other types. Given a node $v$ as input, both \visit and \actuallyVisit
+return a pair $(\expression, \functions)$. Here, \expression is the algebraic
+expression representing $v$, and \functions is a list of auxiliary functions
+created while formulating \expression.
 
 The algorithm gradually constructs two partial maps \functionNames and
-\domainNames that give names to functions and domains, respectively.
+\domainNames providing names to functions and domains, respectively.
 \functionNames is a global variable that maps FCG nodes to function names (e.g.,
@@
 We assume a fixed total ordering of all domains. In particular, in
-\cref{example:interpretation} below we assume that $\Gamma$ goes before
-$\Delta$. For each node $v$, let $\mathfrak{D}(v)$ denote the (precomputed) list
-of domains, the sizes of which we would use as parameters if we were to define a
-function that begins at $v$. As a set, it is computed by iteratively setting
+\cref{example:interpretation} below, let $\Gamma$ go before $\Delta$. For each
+node $v$, let $\mathfrak{D}(v)$ denote the (pre-computed) list of domains, the
+sizes of which we would use as parameters if we were to define a function that
+begins at $v$. As a set, it is computed by iteratively setting
 $\mathfrak{D}(v) \gets \left(\bigcup_{u} \mathfrak{D}(u) \setminus I_{v}\right) \cup U_{v}$
@@
 \begin{enumerate*}[label=(\roman*)]
-  \item the union is over all direct successors of $v$,
+  \item the union is over the direct successors of $v$,
   \item $I_{v}$ is the set of domains \emph{introduced} at node $v$, and
@@
 \end{enumerate*}
-The set is then sorted according to the fixed ordering of domains.
+The set is then sorted according to the ordering.
 
@@
   values. For simplicity, we refer to FCG nodes by their types. When \visit
-  calls \actuallyVisit and returns its output unchanged, the two function calls
-  are shortened as a single call to $\visit/\actuallyVisit$.
+  calls \actuallyVisit and returns its output unchanged, we shorten the two
+  function calls to $\visit/\actuallyVisit$.
 
@@
   $\forall X, Y \in \Delta^{\top}\text{. }X \ne Y \Rightarrow \bot$, i.e.,
-  $\forall X, Y \in \Delta^{\top}\text{. }X = Y$. This sentence is true if and
-  only if $\Dthree(\Delta^{\top}) < 2$. Thus, we can use the Iverson bracket
-  notation to write
+  $\forall X, Y \in \Delta^{\top}\text{. }X = Y$, i.e.,
+  $\Dthree(\Delta^{\top}) < 2$. We use the Iverson bracket notation to write
   \[
@@
       1 & \text{if } l < 2 \\
-      0 & \text{otherwise.}
+      0 & \text{otherwise}
     \end{cases}
@@
   $\mathfrak{D}(\GDR) = \langle \Gamma, \Delta \rangle$, and the pair
-  $\langle\Gamma, \Delta\rangle$ is transformed by $\Dthree{} \circ \rho$ as
-  \[
-    \begin{tikzcd}
-      \langle\Gamma, \Delta\rangle \ar[r, mapsto, "\rho"] & \langle\Gamma', \Delta^{\bot}\rangle \ar[r, mapsto, "\Dthree"] & \langle m-1, n-l \rangle,
-    \end{tikzcd}
-  \]
-  \args is set to $\langle m-1, n-l \rangle$ on \cref{line:args}, and the output
-  expression becomes $f(m-1, n-l)$. The call to \actuallyVisit{$\land$,
-    $\Dthree$} then returns the product of the two expressions
-  $[l<2]f(m-1, n-l)$. Next, the call to \actuallyVisit{$\bigvee$, $\Done$}
-  prepends a summation and returns $\sum_{l=0}^{n}[l<2]f(m-1,n-l)$. The same
-  expression (and an empty list of functions) is then returned to
-  \cref{line:actuallyvisit} of the call to \visit{$\GDR$, $\Done$}. Here, both
-  \functionCall and \functionSignature are set to $f(m, n)$. As the definition
-  of $f$ is the final answer and not part of some other algebraic expression,
+  $\langle\Gamma, \Delta\rangle$ is transformed by $\rho$ to
+  $\langle\Gamma', \Delta^{\bot}\rangle$ and then by $\Dthree{}$ to
+  $\langle m-1, n-l \rangle$, \args is set to $\langle m-1, n-l \rangle$ on
+  \cref{line:args}, and the output expression becomes $f(m-1, n-l)$. The call to
+  \actuallyVisit{$\land$, $\Dthree$} then returns the product of the two
+  expressions $[l<2]f(m-1, n-l)$. Next, \actuallyVisit{$\bigvee$, $\Done$}
+  returns $\sum_{l=0}^{n}[l<2]f(m-1,n-l)$. The same expression (and an empty
+  list of functions) is then returned to \cref{line:actuallyvisit} of the call
+  to \visit{$\GDR$, $\Done$}. Here, both \functionCall and \functionSignature
+  are set to $f(m, n)$. As the definition of $f$ is the final answer and not
+  part of some other algebraic expression,
   \cref{line:initialcall,line:initialcalltwo} discard the function call
@@
   is the function that \textsc{Crane} constructed for computing partial
-  injections. To use $f$ in practice, one just needs to identify the base cases
+  injections. To use $f$ in practice, one has to identify the base cases
   $f(0, n)$ and $f(m, 0)$ for all $m, n \in \mathbb{N}_{0}$.
@@
     algorithm was not able to find a solution. In the case of \textsc{ForcLift},
-    this means that the greedy search algorithm ended with a formula not
-    suitable for any compilation rule. In the case of \textsc{Crane}, this means
-    that a complete solution could not be found after having explored the
-    maximum allowed depth of the search tree.}\label{tbl:results}
+    this means that the greedy search algorithm ended with a formula unsuitable
+    for any compilation rule. In the case of \textsc{Crane}, this means that a
+    complete solution could not be found after having explored the maximum
+    allowed depth of the search tree.}\label{tbl:results}
 \end{table*}
 
-% TODO: I think I said this the last time, but along with the complexities as a
-% way of representing the empirical evaluation, I think you should also include
-% a few plots, even if they say nothing more than what the table already says.
-% The point is that the readers can see what this behaviour looks like so even
-% if you include a few plots and say we just give a few representative examples
-% and the rest follow the table of all that will be better [an experiment with
-% non-partial endo injections?]
-
+% TODO: rewrite to include references to the subsections?
 We compare \textsc{Crane} and
 \textsc{ForcLift}\footnote{\url{https://dtaid.cs.kuleuven.be/wfomc}}~\cite{DBLP:conf/ijcai/BroeckTMDR11}
-on their ability to count various kinds of functions. This class of instances is
-chosen because of its simplicity and ubiquity and the inability of publicly
-available WFOMC algorithms to solve many such instances. Note that other exact
-WFOMC algorithms mentioned in \cref{sec:introduction} are unable to solve any of
-the instances that \textsc{ForcLift} fails on. We begin by describing how such
-function-counting problems can be expressed in first-order logic.
-\textsc{ForcLift} then translates these sentences in first-order logic to
-formulas as in \cref{def:formula}.
+on their ability to count various classes of functions. We chose this class of
+instances because of its simplicity and the inability of publicly available
+WFOMC algorithms to solve many such counting problems. Note that, except for a
+particular version of \textsc{FastWFOMC}, other exact WFOMC algorithms cannot
+solve any instances \textsc{ForcLift} fails on. First, we describe how to
+express these function-counting problems in first-order logic. \textsc{ForcLift}
+then translates these sentences in first-order logic to formulas as in
+\cref{def:formula}.
 
@@
 $\Delta$. To restrict all such relations to just $\Gamma \to \Delta$ functions,
-in first-order logic one might write
-\[
-  \forall X \in \Gamma\text{. }\forall Y,Z \in \Delta\text{. }\predicate(X, Y) \land \predicate(X, Z) \Rightarrow Y = Z
-\]
-and
+one might write $\forall X \in \Gamma\text{. }\forall Y,Z \in \Delta\text{.
+}\predicate(X, Y) \land \predicate(X, Z) \Rightarrow Y = Z$ and
 \begin{equation}\label{eq:def2}
@@
 $\Gamma$ must map to at \emph{least} one element of $\Delta$. One can then add
-\[
-  \forall X,Z \in \Gamma\text{. }\forall Y \in \Delta\text{. }\predicate(X, Y) \land \predicate(Z, Y) \Rightarrow X = Z
-\]
-to restrict $\predicate$ to injections or
-  $\forall Y \in \Delta\text{. }\exists X \in \Gamma\text{. }\predicate(X, Y)$
-to ensure surjectivity or remove \cref{eq:def2} to consider partial functions.
-Lastly, one can replace all occurrences of $\Delta$ with $\Gamma$ to model
-endofunctions (i.e., functions with the same domain and codomain) instead.
+$\forall X,Z \in \Gamma\text{. }\forall Y \in \Delta\text{.
+}\predicate(X, Y) \land \predicate(Z, Y) \Rightarrow X = Z$ to restrict
+$\predicate$ to injections or $\forall Y \in \Delta\text{.
+}\exists X \in \Gamma\text{. }\predicate(X, Y)$ to ensure surjectivity or remove
+\cref{eq:def2} to consider partial functions. Lastly, one can replace all
+occurrences of $\Delta$ with $\Gamma$ to model endofunctions (i.e., functions
+with the same domain and codomain) instead.
 
@@
 same function/sequence. We run each algorithm once on each instance.
-\textsc{Crane} is run in hybrid search mode until either five solutions are
-found or the search tree reaches height six. \textsc{ForcLift} is always run
-until it terminates. If successful, \textsc{Crane} generates one or more sets of
-function definitions, and \textsc{ForcLift} generates a circuit, which can
-similarly be interpreted as a function definition. We then assess the complexity
-of each solution by hand and pick the best in case \textsc{Crane} returns
-several solutions of varying complexities.
+\textsc{Crane} is run in hybrid search mode until either it finds five solutions
+or the search tree reaches height six. \textsc{ForcLift} is always run until it
+terminates. If successful, \textsc{Crane} returns one or more sets of function
+definitions, and \textsc{ForcLift} returns a circuit, which can similarly be
+interpreted as a function definition. We then assess the complexity of each
+solution by hand and pick the best in case \textsc{Crane} returns several
+solutions of varying complexities.
 
@@
 
-% Previous work often compares WFOMC algorithms by running them on a few instances
-% with increasing domain sizes and measuring
-% runtime~\cite{DBLP:conf/nips/Broeck11,DBLP:conf/ijcai/BroeckTMDR11,DBLP:conf/aaai/BroeckD12}.
-% However, we can do better and identify the exact worst-case asymptotic
-% complexity of a solution produced by either \textsc{Crane} or \textsc{ForcLift}.
-
-Recall that, in the case of \textsc{ForcLift}, the process of solving a (W)FOMC
-problem consists of two parts: compilation (via search) and propagation. (A
-similar dichotomy applies to \textsc{Crane} as well.) The complexity of the
-former depends only on the formula and so far has received very little attention
-with the exception of Beame et al.~\shortcite{DBLP:conf/pods/BeameBGS15}. The
+Recall that, in the case of \textsc{ForcLift}, solving a (W)FOMC problem
+consists of two parts: compilation (via search) and propagation. (A similar
+dichotomy applies to \textsc{Crane} as well.) The complexity of the former
+depends only on the formula and so far has received very little attention except
+for the work by Beame et al.~\shortcite{DBLP:conf/pods/BeameBGS15}. The
 complexity of the latter, on the other hand, is a function of domain sizes and
-can be determined exactly (without measuring runtime). We establish the
-asymptotic complexity of a solution by counting the total number of arithmetic
-operations needed to follow the definitions of constituent functions without
-recomputing the same quantity multiple times. In particular, we assume that each
-function call and binomial coefficient is computed at most once. We also assume
-that computing $\binom{n}{k}$ takes $\Theta(nk)$ time. For example, the
-complexity of \cref{eq:solution} is $\Theta(mn)$ since $f(m, n)$ can be computed
-by a dynamic programming algorithm that computes $f(i, j)$ for all
-$i = 0, \dots, m$ and $j = 0, \dots, n$, taking a constant amount of time on
-each $f(i, j)$.
-
-% In particular, the complexity of computing total surjections is by
-% Earnest~\shortcite{30049}, and all other such complexities are inferred from the
-% formulas and programs on the on-line encyclopedia of integer
-% sequences~\cite{oeis}.
+can be determined without measuring runtime. We establish the asymptotic
+complexity of a solution by counting the number of arithmetic operations needed
+to follow the definitions of constituent functions without recomputing the same
+quantity multiple times. In particular, we assume that each function call and
+binomial coefficient is computed at most once, and computing $\binom{n}{k}$
+takes $\Theta(nk)$ time. For example, the complexity of \cref{eq:solution} is
+$\Theta(mn)$ since $f(m, n)$ can be computed by a dynamic programming algorithm
+that computes $f(i, j)$ for all $i = 0, \dots, m$ and $j = 0, \dots, n$, taking
+a constant amount of time on each $f(i, j)$.
 
@@
 to the manually-constructed ways of computing the same quantities that have been
-proposed
-before.\footnote{\url{https://scicomp.stackexchange.com/q/30049}}\textsuperscript{,}\footnote{\url{https://oeis.org}}
-Examining the last two columns of the table, we see that the two algorithms
-perform equally well on instances that could already be solved by
-\textsc{ForcLift}. However, \textsc{Crane} can also solve all but one of the
-instances that \textsc{ForcLift} fails on in at most cubic time. See
-supplementary material for the exact solutions produced by \textsc{Crane}.
-
-\subsubsection{Miscellaneous Other Instances}
-We also note that standard (W)FOMC benchmarks such as \cref{example:smokers}
-that are already supported by \textsc{ForcLift} remain feasible for
-\textsc{Crane} as well. To demonstrate that \textsc{Crane} is capable of finding
-efficient solutions to problems beyond known domain-liftable fragments such as
-\Ctwo{}, we run \textsc{Crane} in greedy search mode on the following formula:
+proposed before.\footnote{\url{https://oeis.org},
+  \url{https://scicomp.stackexchange.com/q/30049}} Examining the last two
+columns of the table, we see that the two algorithms perform equally well on
+instances that could already be solved by \textsc{ForcLift}. However,
+\textsc{Crane} can also solve all but one of the instances that
+\textsc{ForcLift} fails on in at most cubic time. See supplementary material for
+the exact solutions produced by \textsc{Crane}.
+
+\subsection{A Comparison with \textsc{\normalfont FastWFOMC}}
+
+The function-counting problems described above can be expressed in \FOtwo{} with
+cardinality constraints, and so are known to be
+liftable~\cite{DBLP:journals/jair/Kuzelka21}. However, two algorithms that both
+run in polynomial time are not necessarily equally good: the degree of the
+polynomial can make a substantial difference. Hence, we compare \textsc{Crane}
+with \textsc{FastWFOMC}~\cite{DBLP:conf/uai/BremenK21}, extended to support
+cardinality constraints, which was provided to us by one of the authors. We
+compare them on the task of counting permutations of a set, i.e.,
+bijective/injective endofunctions. We can describe this problem in \FOtwo{} with
+cardinality constraints as
+\begin{align*}
+  (|\predicate| = |\Delta|) \land{} &(\forall X, Y \in \Delta\text{. } \predicater(X) \lor \neg \predicate(X, Y)) \land{}\\
+  &(\forall X, Y \in \Delta\text{. } \predicates(X) \lor \neg\predicate(Y, X)),
+\end{align*}
+where $\predicater$ and $\predicates$ are Skolem predicates as described by Van
+den Broeck et al.~\shortcite{DBLP:conf/kr/BroeckMD14}.
+
+\begin{figure}[t]
+  \includegraphics{plot}
+  \caption{The runtime of \textsc{FastWFOMC} when counting permutations,
+    together with a quartic regression model fitted on all of the data and a
+    linear model fitted on the first half of the data
+    points}\label{fig:fastwfomc}
+\end{figure}
+
+We run \textsc{FastWFOMC} on an AMD Ryzen~7~5800H processor with
+\SI{16}{\giga\byte} of memory, running Arch Linux~6.2.2-arch1-1 and
+Python~3.10.9, with $|\Delta|$ ranging from 1 to 50. The results are in
+\cref{fig:fastwfomc}. We use ten-fold cross-validation to check the degree of
+the polynomial that best fits the data. The best-fitting degree is 6 with a mean
+mean squared error (MMSE) of 16.9, although all degrees above 4 fit the data
+almost equally well. As \cref{fig:fastwfomc} demonstrates, a quartic (i.e.,
+degree 4) polynomial (with an MMSE of 113.5) fits well too. However, the MMSE
+quickly grows to 949.5 and higher values for degrees less than 4. According to
+\cref{tbl:results}, \textsc{Crane} finds a cubic solution to this problem.
+However, we can also use the linear solution for counting bijections between
+different domains for this task simply by setting $n \coloneqq m$.
+
+\subsection{Miscellaneous Other Instances}
+
+We also note that standard (W)FOMC benchmarks such as
+\cref{example:smokers}---that are already supported by
+\textsc{ForcLift}---remain feasible for \textsc{Crane} as well. To demonstrate
+that \textsc{Crane} is capable of finding efficient solutions to problems beyond
+known domain-liftable fragments such as \Ctwo{}, we run \textsc{Crane} in greedy
+search mode on the following formula:
 \begin{equation}\label[formula]{eq:ternary}
@@
 \textsc{ForcLift}~\cite{DBLP:conf/ijcai/BroeckTMDR11} that benefits from a more
-general version of domain recursion and the support for graphs with cycles. Our
+general version of domain recursion and support for graphs with cycles. Our
 results in \cref{sec:results} reveal a range of counting problems that became
 newly feasible as a result of these enhancements, including instances outside of
-currently-known domain-liftable fragments such as \Ctwo{}. (Although here we
-focus on unweighted counting, \textsc{ForcLift}'s support for weights trivially
-transfers to \textsc{Crane} as well.) The common thread across these newly
-liftable problems is a version of partial injectivity. Thus, we formulate the
-following conjecture.
+currently-known domain-liftable fragments such as \Ctwo{}. (Although we focused
+on unweighted counting, \textsc{ForcLift}'s support for weights trivially
+transfers to \textsc{Crane} too.) The common thread across these newly liftable
+problems is a version of partial injectivity. Thus, we formulate the following
+conjecture.
 \begin{conjecture}
@@
 \end{conjecture}
-Recall that \Ctwo{} is the class of formulas with counting quantifiers and at
-most two variables that was recently shown to be
-liftable~\cite{DBLP:journals/jair/Kuzelka21}. Since most of the instances in
-\cref{sec:results} are in \Ctwo{}, we can also conjecture that \Ctwo{} is
-liftable by \textsc{Crane}.
-
-The most important direction for future work is in fully automating the process
-in \cref{fig:processcrane}. First, we need a way to find the base cases for the
+Since most of the instances in \cref{sec:results} are in \Ctwo{}, we can also
+conjecture that \Ctwo{} is liftable by \textsc{Crane}.
+
+The most important direction for future work is to automate the process in
+\cref{fig:processcrane}. First, we need a way to find the base cases for the
 recursive definitions produced by \textsc{Crane}. Second, since the first
@@
 \cref{example:interpretation}, the functions constructed by \textsc{Crane} can
-often benefit from elementary algebraic simplifications, and this process can be
+often benefit from elementary algebraic simplifications. This process can be
 automated using a computer algebra system. Furthermore, note that having the
@@
 In addition to the potential impact on areas of artificial intelligence (AI)
-such as statistical relational AI~\cite{DBLP:series/synthesis/2016Raedt},
+like statistical relational AI~\cite{DBLP:series/synthesis/2016Raedt},
 \textsc{Crane} could be beneficial to research in combinatorics as

### 2023-03-09 doc/paper/supplementary_material.tex
Formatting improvements
Almost done?

@@
 \newcommand{\predicate}{\texttt{\textup{p}}}
+\newcommand{\nulll}{\texttt{\textup{null}}}
 
-\DeclareMathOperator{\friends}{\texttt{friends}}
-\DeclareMathOperator{\smokes}{\texttt{smokes}}
 \DeclareMathOperator{\CR}{\textsc{CR}}
@@
 set $S$, let $2^{S}$ denote its power set and
-$S^{\ast} \coloneqq \bigcup_{i=0}^{\infty} S^{i}$ the set of tuples---of any
-finite length---of elements of $S$. For example,
+$S^{\ast} \coloneqq \bigcup_{i=0}^{\infty} S^{i}$ the (infinite) set of
+tuples---of any finite length---of elements of $S$. For example,
 ${\{\,a, b\,\}}^{\ast} = \{\, (), (a), (b), (a, a), \dots \,\}$. For any
@@
 occurrences of all variables in $V$ replaced with $c$. Let $\Preds$ be the
-function that maps any clause or formula to the set of predicates used within.
-With each formula $\phi$ we associate a map
+function that maps any clause or formula to the set of predicates used in it.
+With each formula $\phi$, we associate a map
 $\pi_{\phi}\colon \Preds(\phi) \to {\Doms(\phi)}^{\ast}$ s.t., for each
@@
 \begin{definition}\label{def:model}
-  Let $\phi$ be a formula and $\sigma$ a domain size function, A \emph{model} of
+  Let $\phi$ be a formula and $\sigma$ a domain size function. A \emph{model} of
   $(\phi, \sigma)$ is a map
@@
 
-  If $c$ has no variables with domain $\Omega$, then
-  \cref{line:conditions,line:generation} simply add a copy of $c$ to $\phi'$. If
-  $c$ has one variable with domain $\Omega$, say, $X$, then
+  If $c$ has no variables with domain $\Omega$,
+  \cref{line:conditions,line:generation} add a copy of $c$ to $\phi'$. If $c$
+  has one variable with domain $\Omega$, say, $X$, then
   $c \equiv \forall X \in \Omega\text{. } \psi$ for some formula $\psi$ with one
@@
   Let $V$ be the set of variables introduced on \cref{line:V}. It remains to
-  show that repeating the transformation
+  prove that repeating the transformation
   \[
@@
   \end{equation}
-  as required. Certainly, any subset of the left-hand side of \cref{eq:equality}
+  as required. Obviously, any subset of the left-hand side of \cref{eq:equality}
   (e.g., $\mathfrak{M}(\predicate)$, where $\mathfrak{M}$ is a model of
@@
 Here we list the exact function definitions produced by \textsc{Crane} for all
-of the problem instances in Section~6 both before and after algebraic
+of the problem instances in Section~6, both before and after algebraic
 simplification (excluding multiplications by one). The correctness of all of

### 2023-03-10 doc/paper/paper.tex
Submitted

@@
 theory~\cite{DBLP:conf/kr/BremenK21} and applications in enumerative
-combinatorics~\cite{DBLP:conf/ilp/BarvinekB0ZK21}. Totis et
-al.~\shortcite{DBLP:journals/jair/TotisDRK23} proposed an FOMC-based approach to
-counting solutions to constraint satisfaction problems.
+combinatorics~\cite{DBLP:conf/ilp/BarvinekB0ZK21}.
+
+% Totis et
+% al.~\shortcite{DBLP:journals/jair/TotisDRK23} proposed an FOMC-based approach to
+% counting solutions to constraint satisfaction problems.
 
@@
 that applies some rules greedily and some using breadth-first
-search.\footnote{In the current implementation, the rules applied in a
-  non-greedily are: atom counting, inclusion-exclusion, independent partial
-  groundings, Shannon decomposition, shattering, and two new rules described in
+search.\footnote{In the current implementation, the rules applied non-greedily
+  are: atom counting, inclusion-exclusion, independent partial groundings,
+  Shannon decomposition, shattering, and two new rules described in
   \cref{sec:dr,sec:ref}---see previous work~\cite{DBLP:conf/ijcai/BroeckTMDR11}
@@
 $n \in \mathbb{N}^{+}$ is the \emph{arity} of $\predicate$. An \emph{atom} is
-$\predicate(t_1, \dots, t_n)$ for some predicate $\predicate/n$ and terms
-$t_{1}, \dots, t_{n}$. A \emph{term} is either a constant or a variable. A
+$\predicate(x_1, \dots, x_n)$ for some predicate $\predicate/n$ and terms
+$x_{1}, \dots, x_{n}$. A \emph{term} is either a constant or a variable. A
 \emph{literal} is either an atom or the negation thereof (denoted by
-$\neg \predicate(t_1, \dots, t_n)$). Let $\mathcal{D}$ be the set of all
+$\neg \predicate(x_1, \dots, x_n)$). Let $\mathcal{D}$ be the set of all
 relevant (finite) domains. Initially, $\mathcal{D}$ contains all domains
@@
 domains (respectively, variables) used in it. Let $S$ be a set of constraints or
-literals, $V$ a set of variables, and $x$ a variable or a constant. We write
-$S[x/V]$ to denote $S$ with all occurrences of all variables in $V$ replaced
-with $x$.
+literals, $V$ a set of variables, and $x$ a term. We write $S[x/V]$ to denote
+$S$ with all occurrences of all variables in $V$ replaced with $x$.
 
@@
   An \emph{(inequality) constraint} is a pair $(a, b)$, where $a$ is a variable,
-  and $b$ is a variable or a constant. It constrains $a$ and $b$ to be
-  different.
+  and $b$ is a term. It constrains $a$ and $b$ to be different.
 \end{definition}
@@
 \cref{eq:formula} can be simplified to have one fewer variables. Similarly, if
-the same inequality is replaced by $Y = c$ for some constant $c$, then $Y$ can
+the same inequality is replaced by $Y = x$ for some constant $x$, then $Y$ can
 be eliminated as well. Since constraints are always interpreted as preconditions
@@
   \begin{align*}
-    c_{1} &= \begin{multlined}[t]
+    c_{1} &\coloneqq \begin{multlined}[t]
       (\{\, \neg \predicate(x, Y), \neg \predicate(x, Z) \,\}, \{\, (Y, Z) \,\}, \\
@@
       \end{multlined}\\
-    c_{2} &= \begin{multlined}[t]
+    c_{2} &\coloneqq \begin{multlined}[t]
       (\{\, \neg \predicate(X, Y), \neg \predicate(X, Z) \,\}, \{\, (X, x), (Y, Z) \,\}, \\
@@
   \end{align*}
-  and $\Gamma' = \Gamma \setminus \{\, x \,\}$.
+  and $\Gamma' \coloneqq \Gamma \setminus \{\, x \,\}$.
 \end{example}
@@
 % Description of GDR, in contrast to DR
-In contrast, GDR has only one precondition: for GDR to be applicable on domain
+In contrast, GDR has only one precondition: for GDR to be applicable to domain
 $\Omega \in \mathcal{D}$, there must be at least one variable with domain
@@
       \ForEach{clause $d \in \phi$ s.t. $\#d=\#c$\label{line:for2}}{
-        \ForAll{$\gamma \in \generateMaps{$c$, $d$, $\rho$}$\label{line:generateMaps}}{
+        \ForEach{$\gamma \in \generateMaps{$c$, $d$, $\rho$}$\label{line:generateMaps}}{
           $\rho' \gets \identifyRecursion{$\phi\setminus\{\, d \,\}$, $\psi\setminus\{\, c \,\}$, $\rho\cup\gamma$}$\;\label{line:recursion}
@@
 
-% TODO: double check the first sentence and if this paragraph still makes sense
 Function \generateMaps checks the compatibility of a pair of clauses. It
@@
 $\gamma\colon \Doms(c) \to \Doms(d)$ s.t.
-\begin{enumerate*}[label=(\roman*)]
-  \item $\delta_{d} \circ \beta(X) = \rho \circ \delta_{c}(X)$ for all
-  $X \in \Vars(c)$,
-  \item $\gamma(\Omega) = \rho(\Omega)$ for all $\Omega \in \Doms(c)$, and
-  \item $c$ becomes equal to $d$ when its variables are replaced according to
-  $\beta$, and its domains replaced according to $\gamma$.
-\end{enumerate*}
-The function then returns each such $\gamma$ as soon as possible.
-
-% The
-% commutativity check also ensures that $\rho \cup \gamma$ is possible on
-% \cref{line:recursion} of \cref{alg:trycache}. The resulting (partial) function
-% $\rho \cup \gamma$ is the unique function s.t.
-% $\rho \cup \gamma|_{\dom(\rho)} = \rho$, and
-% $\rho \cup \gamma|_{\dom(\gamma)} = \gamma$. The operation is defined when
-% $\rho|_{\dom(\rho)\cap\dom(\gamma)} = \gamma|_{\dom(\rho)\cap\dom(\gamma)}$.
-
-% \[
-%   \begin{tikzcd}
-%     \Vars(c) \ar[r, dashed, "\beta"] \arrow[d, swap, "\delta_c"] & \Vars(d) \ar[d, "\delta_d"] \\
-%     \Doms(c) \ar[r, dashed, "\gamma"] \ar[d, hookrightarrow] & \Doms(d) \ar[d, hookrightarrow] \\
-%     \Doms(\psi) \ar[r, swap, "\rho", "|" marking, outer sep=5pt] & \Doms(\phi).
-%   \end{tikzcd}
-% \]
+\[
+  \begin{tikzcd}
+    \Vars(c) \ar[r, dashed, "\beta"] \arrow[d, swap, "\delta_c"] & \Vars(d) \ar[d, "\delta_d"] \\
+    \Doms(c) \ar[r, dashed, "\gamma"] \ar[d, hookrightarrow] & \Doms(d) \ar[d, hookrightarrow] \\
+    \Doms(\psi) \ar[r, swap, "\rho", "|" marking, outer sep=5pt] & \Doms(\phi).
+  \end{tikzcd}
+\]
+commutes, and $c$ becomes equal to $d$ when its variables are replaced according
+to $\beta$ and its domains replaced according to $\gamma$. The function then
+returns each such $\gamma$ as soon as possible.
 
@@
     $\newDomainNames \gets \domainNames$\;
-    \For{$\Omega \in \mathfrak{D}(v)$ s.t. $\newDomainNames(\Omega)$ is non-atomic}{\label{line:nonone}
+    \ForEach{$\Omega \in \mathfrak{D}(v)$ s.t. $\newDomainNames(\Omega)$ is non-atomic}{\label{line:nonone}
       $\newDomainNames(\Omega) \gets \newDomainName{}$\;\label{line:nontwo}
@@
 
-% TODO: rewrite to include references to the subsections?
 We compare \textsc{Crane} and
@@
 \cref{fig:fastwfomc}. We use ten-fold cross-validation to check the degree of
-the polynomial that best fits the data. The best-fitting degree is 6 with a mean
-mean squared error (MMSE) of 16.9, although all degrees above 4 fit the data
-almost equally well. As \cref{fig:fastwfomc} demonstrates, a quartic (i.e.,
-degree 4) polynomial (with an MMSE of 113.5) fits well too. However, the MMSE
+the polynomial that best fits the data. The best-fitting degree is 6 with an
+average mean squared error (aMSE) of 16.9, although all degrees above 4 fit the
+data almost equally well. As \cref{fig:fastwfomc} demonstrates, a quartic (i.e.,
+degree 4) polynomial (with an aMSE of 113.5) fits well too. However, the aMSE
 quickly grows to 949.5 and higher values for degrees less than 4. According to
@@
 However, we can also use the linear solution for counting bijections between
-different domains for this task simply by setting $n \coloneqq m$.
+different domains for this task by setting $n \coloneqq m$.
 

### 2023-03-14 doc/talks/3_long/talk.tex
Describe one more instance
Additions and improvements to the slides

@@
 \usepackage{pifont}
-\usepackage{venndiagram}
 
@@
 \usetikzlibrary{fit}
+
+\newcommand\blfootnote[1]{%
+  \begingroup
+  \renewcommand\thefootnote{}\footnote{#1}%
+  \addtocounter{footnote}{-1}%
+  \endgroup
+}
 
@@
 \definecolor{color2}{HTML}{7570b3}
-\definecolor{color3}{HTML}{e7298a} % TODO: I don't like pink
+\definecolor{color3}{HTML}{a6761d}
 \definecolor{forestgreen}{HTML}{009B55}
+
+\DeclareMathOperator{\GDR}{\textsc{GDR}}
+\DeclareMathOperator{\CR}{\textsc{CR}}
+\DeclareMathOperator{\Reff}{\textsc{Ref}}
 
@@
 
-% 15 min (8 slides of content) introduction
-% 25 min presentation
-% 5 min summary
-% 20-25 slides
-% before it was 15 slides and 20 min
+% 15 min (8 slides, currently have 7) introduction
+% 25 min (13 slides, currently have 10) presentation
+% 5 min (3 slides, currently have 1) summary
 % make sure there's a clear and coherent storyline
 
-\author{\textbf{Paulius Dilkas} \inst{1} \and Vaishak Belle \inst{2}}
+\author{Paulius Dilkas \\ \vspace{1cm} \tiny{Joint work with Vaishak Belle (Univeristy of Edinburgh, UK)}}
 \title{Synthesising Recursive Functions for\\ First-Order Model Counting}
-\institute{\inst{1} National University of Singapore, Singapore \and \inst{2} University of Edinburgh, UK}
-\date{TODO: date}
+\institute{National University of Singapore, Singapore}
+\date{\today}
+% TODO: update the date
+% TODO: unify the use of colours
+% TODO: do I want to mention forclift and/or crane?
 
@@
     \node<5>[ellipse callout, draw, right=0cm, callout relative pointer={(-1, -0.15)}, text width=5cm] at (stickman.north east) {If I shuffle a deck of \alert{$n$} cards, how many possible outcomes are there?};
-    \node<5>[left,shift=({-1, -1})] at (current page.east) (computer2) {\includegraphics[height=0.5\textheight]{overheating_computer}};
+    \node<5>[left,shift=({-1, -1})] at (current page.east) (computer2) {\includegraphics[height=0.5\textheight]{overheating_computer}\blfootnote{Terms and conditions apply.}};
     \node[shift=({1.3, 0.1})] at (current page.south west) {\tiny \color{lightgray}{Vector art by Vecteezy.com}};
@@
 \end{frame}
+% TODO: replace the cat thing with a funny DALL-E picture
 
@@
 
-% TODO: (maybe) add a slide about other approaches to WFOMC, making it crystal clear what my contributions are
+% TODO: add a slide about other approaches to WFOMC, making it crystal clear
+% what my contributions are. This will finish the introduction
 
 \begin{frame}{(Unweighted) First-Order Model Counting}
-  \begin{columns}[T]
-    \begin{column}{0.5\textwidth}
   \begin{itemize}
-        \item Example formula: $\forall x \in \Delta\text{. } \pP(x) \lor \qQ(x)$
-        \item Let $\Delta \coloneqq \{\, 1, 2 \,\}$
-        \item Interpretations: all subsets of $\{\, \pP(1), \qQ(1), \pP(2), \qQ(2) \,\}$
-        \item Models:
+    \item Example formula: \\
+          \alert{$\forall x \in \Delta\text{. } \pP(x) \lor \qQ(x)$}
+    \item Let \alert{$\Delta \coloneqq \{\, 1, 2 \,\}$}
+    \item Interpretations: all subsets of\\
+          \alert{$\{\, \pP(1), \qQ(1), \pP(2), \qQ(2) \,\}$}
+    \item<2-> Models:
     \[
@@
     \]
-        \item Each 1-ary predicate...
   \end{itemize}
-    \end{column}
-    \begin{column}{0.5\textwidth}
-      \centering
-      \begin{overlayarea}{\textwidth}{4cm}
-        \only<1>{
-          \begin{venndiagram2sets}[labelNotAB={$\Delta$},labelA={$\pP$},labelB={$\qQ$}]
-          \end{venndiagram2sets}
-        }%
-        \only<2>{
-          \begin{venndiagram2sets}[labelNotAB={$\Delta$},labelA={$\pP$},labelB={$\qQ$}]
-            \fillOnlyA;
-          \end{venndiagram2sets}
-        }%
-        \only<3>{
-          \begin{venndiagram2sets}[labelNotAB={$\Delta$},labelA={$\pP$},labelB={$\qQ$}]
-            \fillOnlyB;
-          \end{venndiagram2sets}
-        }%
-        \only<4>{
-          \begin{venndiagram2sets}[labelNotAB={$\Delta$},labelA={$\pP$},labelB={$\qQ$}]
-            \fillACapB;
-          \end{venndiagram2sets}
-        }%
-        \only<5>{
-          \begin{venndiagram2sets}[labelNotAB={$\Delta$},labelA={$\pP$},labelB={$\qQ$}]
-            \fillA;
-            \fillB;
-          \end{venndiagram2sets}
-        }%
-      \end{overlayarea}
-    \end{column}
-  \end{columns}
+  \onslide<3->{
+    \begin{block}{Intuition}
+      \begin{itemize}
+        \item Each 1-ary predicate is like a \alert{subset}
+        \item For \alert{$n>1$}, each \alert{$n$}-ary predicate is like a
+              \alert{relation}
+        \item FOMC counts \alert{combinations of relations}
+      \end{itemize}
+    \end{block}
+  }
+  \begin{tikzpicture}[remember picture,overlay,visible on=<2->]
+    \tikzset{shift={(current page.north east)}}
+    \tikzset{shift={(-4, -2.9)}}
+    \node[draw,circle,minimum size=3cm,label={135:$\pP$},fill=color1] (P) at (0,0) {};
+    \node[draw,circle,minimum size=3cm,label={45:$\qQ$},fill=color2] (Q) at (1.8,0) {};
+    \begin{scope}
+      \clip (0,0) circle(1.5cm);
+      \clip (1.8,0) circle(1.5cm);
+      \fill[color3](0,0) circle(1.5cm);
+    \end{scope}
+    \draw (0,0) circle(1.5cm);
+    \draw (1.8,0) circle(1.5cm);
+  \end{tikzpicture}
 \end{frame}
-% TODO: mention that n-ary predicates ~= relations
 
@@
 
-\begin{frame}{An Example Counting Problem}
+\begin{frame}{A (Slightly) More Complicated Example}
   Suppose this room has \alert{$n$} seats, and there are \alert{$m \le n$}
@@
 
+% TODO: it would be good to have a similar compilation walkthrough for an instance with Ref as well
+
 \begin{frame}{Back to Our Example}
-  For instance, the following function counts injections
+  The following function counts injections:
   \[
@@
   \begin{itemize}
-    \item \alert{$f$} can be computed in \alert{$\Theta(mn)$} time (via dynamic
-          programming).
-    \item Optimal time complexity to compute \alert{$n^{\underline{m}}$} is
-          \alert{$\Theta(m)$}.
+    \item \alert{$f(m, n)$} can be computed in \alert{$\Theta(mn)$} time
+    \begin{itemize}
+      \item using dynamic programming
+    \end{itemize}\pause
+    \item \alert{Optimal} time complexity to compute \alert{$n^{\underline{m}}$}
+          is \alert{$\Theta(m)$}
     \item But \alert{$\Theta(mn)$} is still much better than translating to
-          propositional logic and running a WMC algorithm.
-    \item The rest of this talk is about how such functions can be found
-          automatically.
+          propositional logic and running a WMC algorithm \pause
+    \item The rest of this talk is about how to find such functions automatically
   \end{itemize}
@@
 
-\begin{frame}{First-Order Knowledge Compilation with \textsc{ForcLift}}
-  \begin{columns}
-    \begin{column}{0.25\textwidth}
+\begin{frame}{First-Order Knowledge Compilation: Before and After}
   \centering
-      \begin{tikzpicture}[every node/.style={draw,ellipse},edge from parent/.style={draw,-latex},sibling distance=10mm,level distance=10mm]
-        \node[fill=red!50,fill on=<2>] (dr) {}
-        child {node {}
-          child {node[fill=red!50,fill on=<2>] {}
-            child {node {}
-              child {node {}}
-              child {node[fill=red!50,fill on=<2>] (ref) {}}
-            }}};
-        \draw[-latex, bend right,alt=<2>{red}{black}] (ref) to (dr);
+  \begin{tikzpicture}
+    \node (start) {\tiny $\begin{gathered}
+        \forall x \in \Gamma\text{. }\exists y \in \Delta\text{. }\pP(x, y)\\
+        \forall x \in \Gamma\text{. }\forall y, z \in \Delta\text{. }\pP(x, y) \land \pP(x, z) \Rightarrow y=z\\
+        \forall w, x \in \Gamma\text{. }\forall y \in \Delta\text{. }\pP(w, y) \land \pP(x, y) \Rightarrow w=x
+      \end{gathered}$};
+    \node[draw,rounded rectangle,fill=color2!50,below=0.3cm of start] (kc) {Compilation};
+    \node[below=0.09cm of kc] (graph) {
+      \scalebox{.5}{
+      \begin{forest}
+        for tree={sn edges,grow=0,reversed,fill=red!50}
+        [,ellipse,draw,name=gdr
+        [,ellipse,draw
+        [,ellipse,draw
+        [,ellipse,draw
+        [,ellipse,draw]
+        [,ellipse,draw,name=ref]
+        ]
+        ]
+        ]
+        ]
+        \draw[-Latex,bend left=20] (ref) to (gdr);
+      \end{forest}
+      }
+    };
+    \node[draw,rounded rectangle,fill=color2!50,below=0.1cm of graph] (interpretation) {Conversion};
+    \node[below=0.3cm of interpretation] (initial) {\tiny $f(m, n) = \sum_{l=0}^m \binom{m}{l} [l<2] \times f(m-l, n-1)$};
+    \node[draw,rounded rectangle,fill=color2!50,below=0.3cm of initial] (simplification) {Simplification};
+    \node[below=0.3cm of simplification] (simplified) {\tiny $f(m, n) = f(m, n-1) + mf(m-1, n-1)$};
+    \node[draw,rounded rectangle,fill=color2!50,below=0.3cm of simplified] (evaluation) {Evaluation};
+    \node[below=0.3cm of evaluation] (end) {\includegraphics[height=0.4cm]{42.png}};
+    \node[right=0.3cm of evaluation] (sizes) {\tiny $\begin{aligned}
+        f(0,0) = 1&\text{{,} }f(m, 0) = 0\\
+        m = 7&\text{{,} }n=2
+      \end{aligned}$};
+    %\node at (0.5, -0.55) {\textsc{Crane}};
+    %\node[draw,fit={(kc) (interpretation)},inner ysep=6pt,yshift=5pt] {};
+    \draw[-Latex,color=color2] (start) -- (kc);
+    \draw[-Latex,color=color2] (kc) -- ($(graph)+(0,0.2)$);
+    \draw[-Latex,color=color2] ($(graph)+(0,-0.3)$) -- (interpretation);
+    \draw[-Latex,color=color2] (interpretation) -- (initial);
+    \draw[-Latex,color=color2] (initial) -- (simplification);
+    \draw[-Latex,color=color2] (simplification) -- (simplified);
+    \draw[-Latex,color=color2] (simplified) -- (evaluation);
+    \draw[-Latex,color=color2] (evaluation) -- (end);
+    \draw[-Latex,color=color2] (sizes) -- (evaluation);
   \end{tikzpicture}
-    \end{column}
-    \begin{column}{0.75\textwidth}
-      \begin{block}{Workflow Before}
-        \begin{enumerate}
-        \item Compile the formula to a \alert{circuit}
-        \item Evaluate to get the answer
-        \end{enumerate}
-      \end{block}
-      \pause
-      \begin{block}{Workflow After}
-        \begin{enumerate}
-        \item Compile the formula to a \alert{graph}
-        \item Extract the definitions of functions
-        \item Simplify
-        \item Supplement with \alert{base cases}
-        \item Evaluate to get the answer
-        \end{enumerate}
-      \end{block}
-    \end{column}
-  \end{columns}
 \end{frame}
-% Only Step 1 is fully automated at this point. The other steps are executed by hand.
-% Two parts: compilation and inference/evaluation.
+% TODO: optimize edge lengths
+% TODO: add forclift on the left, with its own example instance
+% TODO: check if the math works out
+
+% TODO: talk #4 might have some useful additions to this section
 
@@
 
+% TODO: maybe replace the zoom picture with some galaxy picture?
 { % all template changes are local to this group.

### 2023-03-14 solutions.py

@@ -290,14 +290,17 @@ def weird1(n, fun=weird2): # should compute partial injections from [n] to [n]
             2**(n-1) * n * (fun(n-1, n-1) + n * fun(n-1, n-2)) +
             2**(n-2) * (n-1) * (fun(n-2, n-1) + n * fun(n-2, n-2)))
 
-MAX = 10
+def example(m, n):
+    return int(math.factorial(m)/math.factorial(m-n))
 
-# for m in range(1, MAX):
-#     for n in range(1, MAX):
-#         print("f({}, {}) = {}".format(m, n, my_partial_injections(m, n)))
+MAX = 20
 
-for n in range(1, MAX):
-    print("f({}) = {} ({})".format(n, weird1(n), two_dimensional_partial_injections(n, n)))
+for m in range(1, MAX):
+    for n in range(1, m+1):
+        print("f({}, {}) = {}".format(m, n, example(m, n)))
+
+# for n in range(1, MAX):
+#     print("f({}) = {} ({})".format(n, weird1(n), two_dimensional_partial_injections(n, n)))
 
 # for m in range(0, MAX):
 #     for n in range(0, MAX):

### 2023-03-17 doc/talks/3_long/talk.tex
Ditto

@@
 \sethlcolor{redish}
+\setstcolor{black}
 
@@
 % TODO: do I want to mention forclift and/or crane?
+% TODO: maybe replace red!50 with one of the main colours
+% TODO: \color -> \textcolor everywhere
+% TODO: how do we capitalise blocks?
 
@@
 \begin{frame}{First-Order Knowledge Compilation: Before and After}
+  \begin{columns}[b]
+    \begin{column}{0.4\textwidth}
+      \centering
+      \begin{tikzpicture}
+        \node (start) {\tiny $\forall x \in \Delta\text{. } \pP(x) \lor \qQ(x)$};
+        \node[draw,rounded rectangle,fill=color2!50,below=0.7cm of start] (kc) {Compilation};
+        \node[below=0.7cm of kc] (graph) {
+          \scalebox{.5}{
+            \begin{forest}
+              for tree={sn edges,fill=red!50,ellipse,draw}
+              [[
+              [
+              []
+              []
+              ]
+              [
+              [
+              []
+              []
+              ]
+              []
+              ]
+              ]]
+            \end{forest}
+          }
+        };
+        \node[draw,rounded rectangle,fill=color2!50,below=0.7cm of graph] (evaluation) {Propagation};
+        \node[below=0.7cm of evaluation] (end) {\includegraphics[height=0.4cm]{81.png}};
+        \node[right=0.3cm of evaluation] (sizes) {\tiny $|\Delta| = 4$};
+        \draw[-Latex,color=color2] (start) -- (kc);
+        \draw[-Latex,color=color2] (kc) -- (graph);
+        \draw[-Latex,color=color2] (graph) -- (evaluation);
+        \draw[-Latex,color=color2] (evaluation) -- (end);
+        \draw[-Latex,color=color2] (sizes) -- (evaluation);
+      \end{tikzpicture}
+    \end{column}
+    \pause
+    \begin{column}{0.6\textwidth}
       \centering
@@
                                                            f(0,0) = 1&\text{{,} }f(m, 0) = 0\\
-        m = 7&\text{{,} }n=2
+                                                           m = 2&\text{{,} }n=7
                                                          \end{aligned}$};
-    %\node at (0.5, -0.55) {\textsc{Crane}};
-    %\node[draw,fit={(kc) (interpretation)},inner ysep=6pt,yshift=5pt] {};
         \draw[-Latex,color=color2] (start) -- (kc);
@@
       \end{tikzpicture}
+    \end{column}
+  \end{columns}
 \end{frame}
-% TODO: optimize edge lengths
-% TODO: add forclift on the left, with its own example instance
-% TODO: check if the math works out
 
-% TODO: talk #4 might have some useful additions to this section
-
-\begin{frame}{More Formally\ldots}
-  \begin{definition}
-    A \emph{first-order deterministic decomposable negation normal form computational graph} (FCG) is a
+\begin{frame}{Circuits vs Graphs}
+  \begin{block}{Circuits
+      \textcolor{gray}{\parencite{DBLP:conf/ijcai/BroeckTMDR11}}\ldots}
     \begin{itemize}
-    \item directed graph
-    \item (which is weakly connected)
-    \item with a single source,
-    \item labelled vertices,
+      \item \ldots extend d-DNNF circuits
+            \textcolor{gray}{\parencite{DBLP:journals/jancl/Darwiche01}} for
+            propositional knowledge compilation with \alert{more node types}
+      \item \ldots are \alert{acyclic}.
+    \end{itemize}
+  \end{block}
+  \pause
+  \begin{block}{First-Order Computational Graphs (FCGs) are\ldots}
+    directed \alert{\st{acyclic}} (weakly connected) graphs with:
+    \begin{itemize}
+    \item a single source,
+    \item labelled nodes,
     \item and ordered outgoing edges.
     \end{itemize}
-  \end{definition}
+  \end{block}
 \end{frame}
 
+% TODO: add arrows that explain the meaning/definition of each node type
 \begin{frame}{How to Interpret an FCG}
@@
       \centering
-      \begin{tikzpicture}[every node/.style={draw,ellipse},edge from parent/.style={draw,-latex},sibling distance=10mm,level distance=10mm]
-        \node[fill=red!50,fill on=<2>] (dr) {}
-        child {node[fill=red!50,fill on=<3>] {}
-                child {node[fill=red!50, fill on=<4>] {}
-                  child {node[fill=red!50, fill on=<5>] {}
-                    child {node[fill=red!50, fill on=<6>] {}}
-                    child {node[fill=red!50, fill on=<7>] (ref) {}}
+      \begin{tikzpicture}[every node/.style={draw,ellipse},edge from parent/.style={draw,-latex},sibling distance=12mm,level distance=15mm]
+        \node[fill=red!50,fill on=<2>] (dr) {\textsc{GDR}}
+        child {node[fill=red!50,fill on=<3>] {$\bigvee$}
+                child {node[fill=red!50, fill on=<4>] {\textsc{CR}}
+                  child {node[fill=red!50, fill on=<5>] {$\land$}
+                    child {node[fill=red!50, fill on=<6>] {$\bot$}}
+                    child {node[fill=red!50, fill on=<7>] (ref) {\textsc{Ref}}}
         }}};
@@
 \end{frame}
-% We're still creating a vertex in a graph with one outgoing edge.
 
@@
 %%     \item \structure{$G$} is an FCG (or \texttt{null}),
-%%     \item \structure{$C$} is a compilation cache that maps integers to sets of pairs $(\phi, v)$, where $\phi$ is a formula, and $v$ is a vertex of $G$ (which is used to identify opportunities for recursion),
+%%     \item \structure{$C$} is a compilation cache that maps integers to sets of pairs $(\phi, v)$, where $\phi$ is a formula, and $v$ is a node of $G$ (which is used to identify opportunities for recursion),
 %%     \item and \structure{$L$} is a list of formulas (that are yet to be compiled). (Note that the order is crucial!)
@@
 % more arrows (e.g., beyond FOL)
+% TODO: also incorporate the last slide of the 4th talk
 \end{document}

### 2023-03-17 doc/talks/3_long/talk.tex
Improve the slide on the algebraic interpretation of an FCG

@@
 % TODO: how do we capitalise blocks?
+% TODO: make sure I'm using the 'forest' package whenever possible
+% TODO: use Latex and not latex everywhere
 
@@
 
-% TODO: add arrows that explain the meaning/definition of each node type
 \begin{frame}{How to Interpret an FCG}
@@
       \centering
-      \begin{tikzpicture}[every node/.style={draw,ellipse},edge from parent/.style={draw,-latex},sibling distance=12mm,level distance=15mm]
-        \node[fill=red!50,fill on=<2>] (dr) {\textsc{GDR}}
-        child {node[fill=red!50,fill on=<3>] {$\bigvee$}
-                child {node[fill=red!50, fill on=<4>] {\textsc{CR}}
-                  child {node[fill=red!50, fill on=<5>] {$\land$}
-                    child {node[fill=red!50, fill on=<6>] {$\bot$}}
-                    child {node[fill=red!50, fill on=<7>] (ref) {\textsc{Ref}}}
-        }}};
-        \draw[-latex, bend right] (ref) to (dr);
-      \end{tikzpicture}
+      \vspace{1cm}
+      \begin{forest}
+        for tree={sn edges}
+        [$\GDR$,ellipse,draw,name=gdr,fill=red!50,fill on=<4>
+        [$\bigvee$,ellipse,draw,name=bigvee,fill=red!50,fill on=<5>
+        [$\CR$,ellipse,draw,name=cr,fill=red!50,fill on=<6>
+        [$\land$,ellipse,draw,name=conj,fill=red!50,fill on=<7>
+        [$\bot$,rectangle,draw,alt=<8>{fill=red!50}{fill=gray!25},name=contradiction]
+        [$\Reff$,ellipse,draw,name=ref,fill=red!50,fill on=<9>]
+        ]
+        ]
+        ]
+        ]
+        \draw[-Latex,bend right=45] (ref) to (gdr);
+        \draw[visible on=<2-3>] (5, 42 |- gdr) node[text width=5cm,name=gdrtwo,text=color2] {\alert<3>{Generalised domain recursion}};
+        \draw[visible on=<2-3>] (5, 42 |- bigvee) node[text width=5cm,name=bigveetwo,text=color2] {Deterministic set-disjunction};
+        \draw[visible on=<2-3>] (5, 42 |- cr) node[text width=5cm,name=crtwo,text=color2] {\alert<3>{Constraint removal}};
+        \draw[visible on=<2-3>] (5, 42 |- conj) node[text width=5cm,name=conjtwo,text=color2] {Decomposable conjunction};
+        \draw[visible on=<2-3>] (5, 42 |- ref) node[text width=5cm,name=reftwo,text=color2] {\alert<3>{Caching}};
+        \node[visible on=<2-3>,below=0.5cm of contradiction,name=contradictiontwo,text=color2] {Contradiction};
+        \draw[visible on=<2-3>,-Latex,dashed,color=color2] (gdrtwo) -- (gdr);
+        \draw[visible on=<2-3>,-Latex,dashed,color=color2] (bigveetwo) -- (bigvee);
+        \draw[visible on=<2-3>,-Latex,dashed,color=color2] (crtwo) -- (cr);
+        \draw[visible on=<2-3>,-Latex,dashed,color=color2] (conjtwo) -- (conj);
+        \draw[visible on=<2-3>,-Latex,dashed,color=color2] (reftwo) -- (ref);
+        \draw[visible on=<2-3>,-Latex,dashed,color=color2] (contradictiontwo) -- (contradiction);
+      \end{forest}
     \end{column}
@@
       \begin{align*}
-        f(m, n) &= \onslide<3->{\sum_{l=0}^m \binom{m}{l}} \onslide<6->{[l<2]} \onslide<5->{\times} \onslide<7->{f(m-l, n-1)}\\
-        \onslide<8>{&= f(m, n-1) + mf(m-1, n-1)}
+        \onslide<4->{f(m, n) &=} \onslide<5->{\sum_{l=0}^m \binom{m}{l}} \onslide<8->{[l<2]} \onslide<7->{\times} \onslide<9->{f(m-l, n-1)}\\
+        \onslide<10>{&= f(m, n-1) + mf(m-1, n-1)}
       \end{align*}
-      \onslide<6>{
+      \onslide<8>{
         \[

### 2023-03-30 doc/talks/3_long/talk.tex
Finish the introduction

@@
 % TODO: unify the use of colours
-% TODO: do I want to mention forclift and/or crane?
 % TODO: maybe replace red!50 with one of the main colours
 % TODO: \color -> \textcolor everywhere
-% TODO: how do we capitalise blocks?
+% TODO: how do we capitalise titles of \block?
 % TODO: make sure I'm using the 'forest' package whenever possible
@@
 
-% TODO: add a slide about other approaches to WFOMC, making it crystal clear
-% what my contributions are. This will finish the introduction
-
 \begin{frame}{(Unweighted) First-Order Model Counting}
@@
 
+\begin{frame}{Approaches to FOMC}
+  \begin{itemize}
+    \item \alert{ForcLift}~\textcolor{gray}{\parencite{DBLP:conf/ijcai/BroeckTMDR11}}
+    \begin{itemize}
+      \item knowledge compilation to \alert{FO d-DNNF}
+    \end{itemize}
+    \item \alert{L2C}~\textcolor{gray}{\parencite{DBLP:conf/kr/KazemiP16}}
+    \begin{itemize}
+      \item knowledge compilation to \alert{C++} code
+    \end{itemize}
+    \item \alert{Alchemy}~\textcolor{gray}{\parencite{DBLP:journals/cacm/GogateD16}}
+    \begin{itemize}
+      \item \alert{DPLL}-style search
+    \end{itemize}
+    \item \alert{FastWFOMC}~\textcolor{gray}{\parencite{DBLP:conf/uai/BremenK21}}
+    \begin{itemize}
+      \item knowledge compilation to \alert{sd-DNNF}
+    \end{itemize}
+  \end{itemize}
+  \pause
+  \vfill
+  \begin{block}{Our Contribution}
+    \centering
+    \begin{tikzpicture}[align=center,node distance=0.1cm]
+      \node[label=below:{ForcLift}] (forclift) {\includegraphics[width=0.2\paperwidth]{forklift.png}};
+      \node[right=of forclift] (plus) {\Huge$+$};
+      \node[right=of plus,label=below:{Recursion}] (recursion) {\includegraphics[width=0.2\paperwidth]{matryoshka.jpg}};
+      \node[right=of recursion] (equal) {\Huge$=$};
+      \node[right=of equal,label=below:{Crane}] (crane) {\includegraphics[width=0.2\paperwidth]{crane.jpg}};
+    \end{tikzpicture}
+  \end{block}
+\end{frame}
+
 % \begin{frame}{First-Order Model Counting (in More Detail)}
@@
 
-\begin{frame}{First-Order Knowledge Compilation: An Approach to FOMC}
+\begin{frame}{ForcLift and First-Order Knowledge Compilation}
   \begin{minipage}[t][0.81\textheight][t]{\textwidth}
@@
 
-\begin{frame}{Compilation Rules}
+\begin{frame}{How FCGs Are Built}
   \begin{definition}
@@
   \end{definition}
+  \vfill The formulas in \alert{$L$} are then \alert{compiled}, and the
+  resulting FCGs are \alert{inserted} into \alert{$G$} according to a \alert{set
+    order}.
 \end{frame}
 
-\begin{frame}{Example Rule: Independence}
+\begin{frame}{Example Compilation Rule: Independence}
   Input formula:
@@
           \begin{block}{Goal}
-            Check if the input formula is isomorphic (up to domains) to a
+            Check if the input formula is equivalent (up to domains) to a
             previously encountered formula.
           \end{block}
-          \begin{block}{Rough Outline}
+          \begin{block}{Outline}
             \begin{enumerate}
@@
 
-  Our new rules enable \textsc{ForcLift} to efficiently count
+  Our new rules enable Crane to efficiently count
   \alert{$\Gamma \to \Delta$} functions such as:
@@
           \begin{itemize}
-            \item best: \alert{$\Theta(m)$}
+            \item by hand: \alert{$\Theta(m)$}
           \end{itemize}
@@
           \begin{itemize}
-            \item best: \alert{$\Theta({\min\{\, m, n \,\}}^2)$}
+            \item by hand: \alert{$\Theta({\min\{\, m, n \,\}}^2)$}
           \end{itemize}
@@
 \end{frame}
-% TODO: mention Crane, don't forget to introduce forclift
-% TODO: mention that everything used to be unliftable (by any algorithm with a publicly available implementation)
-% TODO: what font do I want to use for forclift/crane? It's mentioned on a slide title as well
 
-% TODO: maybe replace the zoom picture with some galaxy picture?
+% TODO: add a slide with the runtime plot
+
 { % all template changes are local to this group.
@@
             \node[at=(current page.center)] {
-                \includegraphics[keepaspectratio, height=\paperheight]{zoom.jpg}
+                \includegraphics[keepaspectratio, width=\paperwidth]{hubble.jpg}
             };
+            \node[shift=({-0.7, 0.1})] at (current page.south east) {\tiny \color{lightgray}{Source: NASA}};
         \end{tikzpicture}

### 2023-04-06 doc/talks/3_long/talk.tex
Finish the main section

@@
 \usetikzlibrary{fit}
+\usetikzlibrary{decorations.pathreplacing}
 
@@
 \colorlet{redish}{color2!25}
+\colorlet{greenish}{color1!25}
+\colorlet{blueish}{color3!25}
 \sethlcolor{redish}
@@
 \institute{National University of Singapore, Singapore}
-\date{\today}
-% TODO: update the date
-% TODO: unify the use of colours
-% TODO: maybe replace red!50 with one of the main colours
-% TODO: \color -> \textcolor everywhere
+\date{18th April 2023}
+% TODO: unify the use of colours, maybe replace red!50 with one of the main colours
 % TODO: how do we capitalise titles of \block?
 % TODO: make sure I'm using the 'forest' package whenever possible
-% TODO: use Latex and not latex everywhere
 
@@
     \node<2>[ellipse callout, draw, left=-0.5cm, below=0.5cm] at (computer.north west) {$\sqrt{\pi}$};
-    \node<3>[ellipse callout, draw, right=-1cm, callout relative pointer={(-2.5, -0.5)}] at (stickman.north east) {Produce a schedule for the nurses at NUH.};
+    \node<3>[ellipse callout, draw, right=0cm, callout relative pointer={(-1, -0.15)},text width=5cm] at (stickman.north east) {Produce a schedule for the nurses at the local hospital.};
     \node<3>[ellipse callout, draw, below=0.5cm, shift=({-0.5,0}), callout relative pointer={(0.5, -0.25)}] at (computer.north west) {\includegraphics[width=0.1\textwidth]{schedule}};
-    \node<4>[ellipse callout, draw, right=0cm, callout relative pointer={(-1, -0.15)}] at (stickman.north east) {Describe this picture. \includegraphics[width=0.25\textwidth]{cat.jpg}};
-    \node<4>[ellipse callout, draw, below=0.5cm, shift=({-0.5,0.5}), callout relative pointer={(0.5, -0.5)}] at (computer.north west) {It's a cat with its eyes closed.};
+    \node<4>[ellipse callout, draw, right=0cm, callout relative pointer={(-1, -0.15)},text width=6cm] at (stickman.north east) {Paint a baroque oil painting of a \alert{raccoon queen wearing a crown}.};
+    \node<4>[ellipse callout, draw, below=0cm, shift=({-1.5,1}), callout relative pointer={(0.4, -0.2)}] at (computer.north west) {\includegraphics[width=0.25\textwidth]{dalle.png}};
     \node<5>[ellipse callout, draw, right=0cm, callout relative pointer={(-1, -0.15)}, text width=5cm] at (stickman.north east) {If I shuffle a deck of \alert{$n$} cards, how many possible outcomes are there?};
     \node<5>[left,shift=({-1, -1})] at (current page.east) (computer2) {\includegraphics[height=0.5\textheight]{overheating_computer}\blfootnote{Terms and conditions apply.}};
-    \node[shift=({1.3, 0.1})] at (current page.south west) {\tiny \color{lightgray}{Vector art by Vecteezy.com}};
+    \node[shift=({1.3, 0.1})] at (current page.south west) {\tiny \textcolor{lightgray}{Vector art by Vecteezy.com}};
   \end{tikzpicture}
 \end{frame}
-% TODO: replace the cat thing with a funny DALL-E picture
 
@@
     \begin{scope}[transform canvas={xshift=-3em}]
-      \draw[->,draw=gray] ($(WMC)+(0,0.1)$)--($(WMI)+(0,0.5)$) node[midway,left,visible on=<7->] {\color{gray}{$\sum \to \int$}};
-      \draw[->,draw=gray] ($(WMC)-(0,0.1)$)--($(PBP)-(0,0.5)$) node[midway,left,visible on=<8->] {\color{gray}{Generalising weights}};
+      \draw[->,draw=gray] ($(WMC)+(0,0.1)$)--($(WMI)+(0,0.5)$) node[midway,left,visible on=<7->] {\textcolor{gray}{$\sum \to \int$}};
+      \draw[->,draw=gray] ($(WMC)-(0,0.1)$)--($(PBP)-(0,0.5)$) node[midway,left,visible on=<8->] {\textcolor{gray}{Generalising weights}};
     \end{scope}
     \begin{scope}[transform canvas={yshift=-2em}]
-      \draw[->,draw=gray] ($(PBP)-(1,0)$)--($(SP)+(1,0)$) node[midway,below,visible on=<5->] {\color{gray}{From propositional to first-order logic}};
+      \draw[->,draw=gray] ($(PBP)-(1,0)$)--($(SP)+(1,0)$) node[midway,below,visible on=<5->] {\textcolor{gray}{From propositional to first-order logic}};
     \end{scope}
@@
       \onslide<1,2>
-      \begin{block}{\#SAT~\color{gray}{\parencite{DBLP:journals/tcs/Valiant79}}}
+      \begin{block}{\#SAT~\textcolor{gray}{\parencite{DBLP:journals/tcs/Valiant79}}}
         \begin{itemize}
@@
       \onslide<3,4>
-      \begin{block}{Weighted Model Counting~\color{gray}{\parencite{DBLP:journals/ai/ChaviraD08}}}
+      \begin{block}{Weighted Model Counting~\textcolor{gray}{\parencite{DBLP:journals/ai/ChaviraD08}}}
         \begin{itemize}
@@
       \begin{block}{(Weighted) (Symmetric) First-Order Model Counting\\
-          \color{gray}{\parencite{DBLP:conf/ijcai/BroeckTMDR11}}}
+          \textcolor{gray}{\parencite{DBLP:conf/ijcai/BroeckTMDR11}}}
         \begin{itemize}
@@
           \begin{itemize}
-            \item \color{gray}{\parencite{DBLP:conf/ijcai/BellePB15}}
+            \item \textcolor{gray}{\parencite{DBLP:conf/ijcai/BellePB15}}
           \end{itemize}
@@
           \begin{itemize}
-            \item \color{gray}{\parencite{DBLP:conf/uai/FeldsteinB21}}
+            \item \textcolor{gray}{\parencite{DBLP:conf/uai/FeldsteinB21}}
           \end{itemize}
@@
           \end{itemize}
-          \item Semiring programming~\color{gray}{\parencite{DBLP:journals/ijar/BelleR20}}
+          \item Semiring programming~\textcolor{gray}{\parencite{DBLP:journals/ijar/BelleR20}}
         \end{itemize}
@@
 \end{frame}
-
-% \begin{frame}{First-Order Model Counting (in More Detail)}
-%   \begin{itemize}
-%     \item \alert{First-order model counting} (FOMC) is the problem of counting
-%           the models of a sentence in first-order logic.
-%     \item The \alert{(symmetric) weighted} variation of the problem adds weights
-%           (e.g., probabilities) to predicates.
-%           \begin{itemize}
-%             \item It is used for efficient \alert{probabilistic inference} in
-%                   relational models such as Markov logic networks.
-%           \end{itemize}
-%     \item None of the (implemented) (W)FOMC algorithms are able to count, e.g.,
-%           \alert{injective} and \alert{bijective} functions.
-%   \end{itemize}
-%   \begin{block}{Claim}
-%     This shortcoming can be addressed via support for \alert{recursive functions}.
-%   \end{block}
-% \end{frame}
 
@@
 
-% TODO: it would be good to have a similar compilation walkthrough for an instance with Ref as well
-
 \begin{frame}{Back to Our Example}
@@
     \item But \alert{$\Theta(mn)$} is still much better than translating to
-          propositional logic and running a WMC algorithm \pause
+          propositional logic and solving a $\#\P$-complete problem \pause
     \item The rest of this talk is about how to find such functions automatically
@@
 
-\begin{frame}{How FCGs Are Built}
+\begin{frame}{Compilation: How FCGs Are Built}
   \begin{definition}
@@
   G =
-  \begin{tikzpicture}[edge from parent/.style={draw,-latex},baseline=(current bounding box.center)]
+  \begin{tikzpicture}[edge from parent/.style={draw,-Latex},baseline=(current bounding box.center)]
     \node[draw,circle] {$\land$}
@@
 \begin{frame}
-  \frametitle<1>{New Rule 1: Generalised Domain Recursion}
-  \frametitle<2>{New Rule 2: Constraint Removal}
-  \frametitle<3>{New Rule 3: Identifying Possibilities for Recursion}
+  \frametitle<1>{New Rule 1/3: Generalised Domain Recursion}
+  \frametitle<2>{New Rule 2/3: Constraint Removal}
+  \frametitle<3>{New Rule 3/3: Identifying Possibilities for Recursion}
   \begin{columns}
@@
       \centering
-      \begin{tikzpicture}[every node/.style={draw,ellipse},edge from parent/.style={draw,-latex},sibling distance=10mm,level distance=10mm]
+      \begin{tikzpicture}[every node/.style={draw,ellipse},edge from parent/.style={draw,-Latex},sibling distance=10mm,level distance=10mm]
         \node[fill=red!50, fill on=<1>] (dr) {}
@@
             }}};
-        \draw[-latex, bend right,alt=<3>{red}{black}] (ref) to (dr);
+        \draw[-Latex, bend right,alt=<3>{red}{black}] (ref) to (dr);
       \end{tikzpicture}
@@
 
+% an example on partial injection (i.e., bipartite matching) counting
+\begin{frame}{How These Rules Fit Together (1/5)}
+  \begin{tikzpicture}[overlay,remember picture]
+    \node[draw,rounded rectangle,fill=color2!50,anchor=center,above=0.5cm] at (current page.center) (rules) {Generalised domain recursion};
+    \node[above=of rules] (before) {$\begin{gathered}
+        \forall x \in \alert{\Gamma}\text{. }\forall y, z \in \Delta\text{. }y \ne z \Rightarrow \neg\pP(x, y) \lor \neg\pP(x, z)\\
+        \forall w,x \in \alert{\Gamma}\text{. }\forall y \in \Delta\text{. }w \ne x \Rightarrow \neg\pP(w, y) \lor \neg\pP(x, y)
+      \end{gathered}$};
+    \node[below=of rules] (after) {$\begin{gathered}
+        \forall y, z \in \Delta\text{. }y \ne z \Rightarrow \neg\pP(\alert{c}, y) \lor \neg\pP(\alert{c}, z)\\
+        \forall x \in \Gamma\text{. }\forall y,z \in \Delta\text{. }y \ne z \land \alert{x \ne c} \Rightarrow \neg\pP(x, y) \lor \neg\pP(x, z)\\
+        \forall x \in \Gamma\text{. }\forall y \in \Delta\text{. }\alert{x \ne c} \Rightarrow \neg\pP(\alert{c}, y) \lor \neg\pP(x, y)\\
+        \forall w \in \Gamma\text{. }\forall y \in \Delta\text{. }\alert{w \ne c} \Rightarrow \neg\pP(w, y) \lor \neg\pP(\alert{c}, y)\\
+        \forall w,x \in \Gamma\text{. }\forall y \in \Delta\text{. }w \ne x \land \alert{w \ne c} \land \alert{x \ne c} \Rightarrow \neg\pP(w, y) \lor \neg\pP(x, y)
+      \end{gathered}$};
+    \begin{scope}[on background layer]
+      \node[anchor=north,fill=greenish,minimum width=11.1cm,minimum height=0.7cm] at (before.north) {};
+      \node[anchor=south,fill=blueish,minimum width=11.1cm,minimum height=0.7cm] at (before.south) {};
+      \node[anchor=north,fill=greenish,minimum width=11.1cm,minimum height=1.3cm] at (after.north) {};
+      \node[anchor=south,fill=blueish,minimum width=11.1cm,minimum height=2cm] at (after.south) {};
+    \end{scope}
+    \draw[-Latex,color=color2,ultra thick,shorten <=0.1cm,shorten >=0.1cm] (before) -- (rules);
+    \draw[-Latex,color=color2,ultra thick,shorten <=0.1cm,shorten >=0.1cm] (rules) -- (after);
+  \end{tikzpicture}
+\end{frame}
+
+\begin{frame}{How These Rules Fit Together (2/5)}
+  \begin{tikzpicture}[overlay,remember picture]
+    \node[draw,rounded rectangle,fill=color2!50,anchor=center,below=1cm] at (current page.center) (rules) {Atom counting and unit propagation};
+    \node[above=of rules] (before) {$\begin{gathered}
+        \forall y, z \in \Delta\text{. }y \ne z \Rightarrow \neg\pP(\alert{c}, y) \lor \neg\pP(\alert{c}, z)\\
+        \forall x \in \Gamma\text{. }\forall y,z \in \Delta\text{. }y \ne z \land \alert{x \ne c} \Rightarrow \neg\pP(x, y) \lor \neg\pP(x, z)\\
+        \forall x \in \Gamma\text{. }\forall y \in \Delta\text{. }\alert{x \ne c} \Rightarrow \neg\pP(\alert{c}, y) \lor \neg\pP(x, y)\\
+        \forall w \in \Gamma\text{. }\forall y \in \Delta\text{. }\alert{w \ne c} \Rightarrow \neg\pP(w, y) \lor \neg\pP(\alert{c}, y)\\
+        \forall w,x \in \Gamma\text{. }\forall y \in \Delta\text{. }w \ne x \land \alert{w \ne c} \land \alert{x \ne c} \Rightarrow \neg\pP(w, y) \lor \neg\pP(x, y)
+      \end{gathered}$};
+    \node[below=of rules] (after) {$\begin{gathered}
+        \forall y, z \in \alert{\Delta^{\top}}\text{. }y \ne z \Rightarrow \bot\\
+        \forall x \in \Gamma\text{. }\forall y, z \in \alert{\Delta^{\bot}}\text{. }y \ne z \land x \ne c \Rightarrow \neg\pP(x, y) \lor \neg\pP(x, z) \\
+        \forall w, x \in \Gamma\text{. }\forall y \in \alert{\Delta^{\bot}}\text{. }w \ne x \land w \ne c \land x \ne c \Rightarrow \neg\pP(w, y) \lor \neg\pP(x, y)
+      \end{gathered}$};
+    \draw[-Latex,color=color2,ultra thick,shorten <=0.1cm,shorten >=0.1cm] (before) -- (rules);
+    \draw[-Latex,color=color2,ultra thick,shorten <=0.1cm,shorten >=0.1cm] (rules) -- (after);
+    \draw[-Latex,color=color2,ultra thick,shorten <=0.1cm,shorten >=0.1cm] (rules) -- (after);
+  \end{tikzpicture}
+\end{frame}
+
+\begin{frame}{How These Rules Fit Together (3/5)}
+  \begin{tikzpicture}[overlay,remember picture]
+    \node[draw,rounded rectangle,fill=color2!50,anchor=center] at (current page.center) (rules) {Constraint removal};
+    \node[above=of rules] (before) {$\begin{gathered}
+        \forall y, z \in \Delta^{\top}\text{. }y \ne z \Rightarrow \bot\\
+        \forall x \in \alert{\Gamma}\text{. }\forall y, z \in \Delta^{\bot}\text{. }y \ne z \land \alert{x \ne c} \Rightarrow \neg\pP(x, y) \lor \neg\pP(x, z) \\
+        \forall w, x \in \alert{\Gamma}\text{. }\forall y \in \Delta^{\bot}\text{. }w \ne x \land \alert{w \ne c} \land \alert{x \ne c} \Rightarrow \neg\pP(w, y) \lor \neg\pP(x, y)
+      \end{gathered}$};
+    \node[below=of rules] (after) {$\begin{gathered}
+        \forall y, z \in \Delta^{\top}\text{. }y \ne z \Rightarrow \bot\\
+        \forall x \in \alert{\Gamma'}\text{. }\forall y, z \in \Delta^{\bot}\text{. }y \ne z \Rightarrow \neg\pP(x, y) \lor \neg\pP(x, z) \\
+        \forall w, x \in \alert{\Gamma'}\text{. }\forall y \in \Delta^{\bot}\text{. }w \ne x \Rightarrow \neg\pP(w, y) \lor \neg\pP(x, y)
+      \end{gathered}$};
+    \draw[-Latex,color=color2,ultra thick,shorten <=0.1cm,shorten >=0.1cm] (before) -- (rules);
+    \draw[-Latex,color=color2,ultra thick,shorten <=0.1cm,shorten >=0.1cm] (rules) -- (after);
+  \end{tikzpicture}
+\end{frame}
+
+\begin{frame}{How These Rules Fit Together (4/5)}
+  \begin{tikzpicture}[overlay,remember picture]
+    \node[draw,rounded rectangle,fill=color2!50,anchor=center] at (current page.center) (rules) {Independence};
+    \node[above=of rules] (before) {$\begin{gathered}
+        \forall y, z \in \alert{\Delta^{\top}}\text{. }y \ne z \Rightarrow \bot\\
+        \forall x \in \alert{\Gamma'}\text{. }\forall y, z \in \alert{\Delta^{\bot}}\text{. }y \ne z \Rightarrow \neg\pP(x, y) \lor \neg\pP(x, z) \\
+        \forall w, x \in \alert{\Gamma'}\text{. }\forall y \in \alert{\Delta^{\bot}}\text{. }w \ne x \Rightarrow \neg\pP(w, y) \lor \neg\pP(x, y)
+      \end{gathered}$};
+    \node[below left=of rules,fill=greenish] (after1) {$\forall y, z \in \alert{\Delta^{\top}}\text{. }y \ne z \Rightarrow \bot$};
+    \node[below right=2cm and -4cm of rules,fill=blueish] (after2) {$\begin{gathered}
+        \forall x \in \alert{\Gamma'}\text{. }\forall y, z \in \alert{\Delta^{\bot}}\text{. }y \ne z \Rightarrow \neg\pP(x, y) \lor \neg\pP(x, z) \\
+        \forall w, x \in \alert{\Gamma'}\text{. }\forall y \in \alert{\Delta^{\bot}}\text{. }w \ne x \Rightarrow \neg\pP(w, y) \lor \neg\pP(x, y)
+      \end{gathered}$};
+    \begin{scope}[on background layer]
+      \node[anchor=north,fill=greenish,minimum width=9cm,minimum height=0.7cm] at (before.north) {};
+      \node[anchor=south,fill=blueish,minimum width=9cm,minimum height=1.3cm] at (before.south) {};
+    \end{scope}
+    \draw[-Latex,color=color2,ultra thick,shorten <=0.1cm,shorten >=0.1cm] (before) -- (rules);
+    \draw[-Latex,color=color2,ultra thick,shorten <=0.1cm,shorten >=0.1cm] (rules) -- (after1);
+    \draw[-Latex,color=color2,ultra thick,shorten <=0.1cm,shorten >=0.1cm] (rules) -- (after2);
+  \end{tikzpicture}
+\end{frame}
+
+\begin{frame}{How These Rules Fit Together (5/5): Recursion}
+  \centering
+  \begin{tikzpicture}[overlay,remember picture]
+    \node[anchor=center,above=0.5cm] at (current page.center) (equal) {\rotatebox{90}{\textcolor{color2}{\Huge$=$}}};
+    \node[below=0.5cm of equal] (after1) {$\begin{gathered}
+        \forall x \in \alert{\Gamma}\text{. }\forall y, z \in \alert{\Delta}\text{. }y \ne z \Rightarrow \neg\pP(x, y) \lor \neg\pP(x, z)\\
+        \forall w,x \in \alert{\Gamma}\text{. }\forall y \in \alert{\Delta}\text{. }w \ne x \Rightarrow \neg\pP(w, y) \lor \neg\pP(x, y)
+      \end{gathered}$};
+    \node[above=0.5cm of equal] (foo) {$\begin{gathered}
+        \forall x \in \alert{\Gamma'}\text{. }\forall y, z \in \alert{\Delta^{\bot}}\text{. }y \ne z \Rightarrow \neg\pP(x, y) \lor \neg\pP(x, z) \\
+        \forall w, x \in \alert{\Gamma'}\text{. }\forall y \in \alert{\Delta^{\bot}}\text{. }w \ne x \Rightarrow \neg\pP(w, y) \lor \neg\pP(x, y)
+      \end{gathered}$};
+    \node[below=0.5cm of after1] (plus) {\textcolor{color2}{\Huge$+$}};
+    \node[below=0.5cm of plus] {$\{\, \alert{\Gamma} \mapsto \alert{\Gamma'}, \alert{\Delta^{\bot}} \mapsto \alert{\Delta} \,\}$};
+  \end{tikzpicture}
+\end{frame}
+
 %% \begin{frame}{Compilation as Search}
@@
             \item \alert{optimal!}
+            \item FastWFOMC seems to be \alert{$\Omega(m^{4})$}
           \end{itemize}
@@
 \end{frame}
-
-% TODO: add a slide with the runtime plot
+% TODO: add 2 more statements about fastwfomc, showing their plots on the RHS
+% when revealing them
 
@@
             };
-            \node[shift=({-0.7, 0.1})] at (current page.south east) {\tiny \color{lightgray}{Source: NASA}};
+            \node[shift=({-0.7, 0.1})] at (current page.south east) {\tiny \textcolor{lightgray}{Source: NASA}};
         \end{tikzpicture}
@@
 
+% TODO: need 3 slides in total for the ending
+
+% really focus on the 'so what?'
 \begin{frame}{Summary \& Future Work}
@@
 \end{frame}
-% TODO: for future work, come back to the 'many ways to count' slide and add
-% more arrows (e.g., beyond FOL)
-% TODO: also incorporate the last slide of the 4th talk
+
+\begin{frame}{Major Directions for Future Work}
+  \begin{itemize}
+    \item An algebraic description of what kind of sequences and functions with
+          domain $\mathbb{N}_{0}^{k}$ are computable in this way
+          \begin{itemize}
+            \item monotonicity, maximal growth rate, etc.
+          \end{itemize}
+    \item A different input format or logic that allows the same approach to
+          capture more computations
+          \begin{itemize} % TODO: come back to the 'many ways to count' slide
+                          % and add more arrows (e.g., beyond FOL)
+            \item fixed-point logic with counting
+            \item `let domain $\Delta \coloneqq \{\, 1, 2, \dots, MC(\phi) \,\}$'
+          \end{itemize}
+    \item parameterised Markov logic networks
+    \begin{itemize}
+      \item `What equations do the domain sizes have to satisfy for the
+            probability of event $E$ to be at least $95\%$?'
+    \end{itemize}
+  \end{itemize}
+\end{frame}
+
 \end{document}

### 2023-04-11 doc/talks/3_long/talk.tex
First version of the summary part of the talk

@@
 % TODO: make sure I'm using the 'forest' package whenever possible
+% TODO: consider adding an outline slide
+% TODO: add periods at the end of sentences
 
@@
     \item But \alert{$\Theta(mn)$} is still much better than translating to
-          propositional logic and solving a $\#\P$-complete problem \pause
+          propositional logic and solving a \alert{$\#\P$-complete} problem
+          \pause
     \item The rest of this talk is about how to find such functions automatically
@@
 
-% TODO: need 3 slides in total for the ending
-
-% really focus on the 'so what?'
-\begin{frame}{Summary \& Future Work}
-  \begin{block}{Summary}
-    The circuits hitherto used for FOMC become more powerful with:
-    \begin{itemize}
-    \item cycles,
-    \item generalised domain recursion,
-    \item and some more new compilation rules that support domain recursion.
-    \end{itemize}
-  \end{block}
-  \begin{block}{Future Work}
-    \begin{itemize}
-    \item Automate:
-      \begin{itemize}
-      \item extracting and simplifying the definitions of functions,
-      \item finding all base cases.
-      \end{itemize}
-    \item Open questions:
-      \begin{itemize}
-      \item What kind of \alert{sequences} are computable in this way?
-      \item Would using a \alert{different logic} extend the capabilities of FOMC further?
-      \end{itemize}
-    \end{itemize}
-  \end{block}
-\end{frame}
-
-\begin{frame}{Major Directions for Future Work}
-  \begin{itemize}
-    \item An algebraic description of what kind of sequences and functions with
-          domain $\mathbb{N}_{0}^{k}$ are computable in this way
-          \begin{itemize}
-            \item monotonicity, maximal growth rate, etc.
-          \end{itemize}
-    \item A different input format or logic that allows the same approach to
-          capture more computations
-          \begin{itemize} % TODO: come back to the 'many ways to count' slide
-                          % and add more arrows (e.g., beyond FOL)
-            \item fixed-point logic with counting
-            \item `let domain $\Delta \coloneqq \{\, 1, 2, \dots, MC(\phi) \,\}$'
-          \end{itemize}
-    \item parameterised Markov logic networks
-    \begin{itemize}
-      \item `What equations do the domain sizes have to satisfy for the
-            probability of event $E$ to be at least $95\%$?'
-    \end{itemize}
-  \end{itemize}
-\end{frame}
+\begin{frame}{What Have We Learned?}
+  \begin{itemize}
+    \item Knowledge compilation can build \alert{graphs with cycles}.
+    \item Graphs (as well as circuits) define \alert{functions}.
+    \item Cycles can represent \alert{recursive calls}, including:
+    \begin{itemize}
+      \item mutual recursion
+      \item and function calls as complex as \alert{$f(n-k-2)$}.
+    \end{itemize}
+    \item Recursion helps us solve counting problems that were \alert{previously
+          beyond the reach of FOMC}\@.
+    \item In some cases, even if a polynomial-time solution is already known,
+          Crane is able to find \alert{more efficient solutions}, with a lower
+          degree polynomial.
+  \end{itemize}
+\end{frame}
+
+% TODO: maybe add a future <-> past picture slide
+
+\begin{frame}[fragile]{Beyond First-Order Logic}
+  \vspace{0.5cm}
+  \hspace*{0.25\linewidth}
+  \begin{tikzcd}[remember picture]
+    |[alias=WMI]|\WMI{} & \WFOMI{} & \\
+    |[alias=WMC]|\#\SAT{}/\WMC{} \arrow[u] \ar[d] \ar[r] & \textup{(W)FOMC} \arrow[u] \ar[d] \ar[r,dashed] & \raisebox{-0.4\height}{\includegraphics[width=0.1\linewidth]{question-mark.jpg}} \\
+    |[alias=PBP]|\AMC{}, \pbp{} & |[alias=SP]|\SPPP{} &
+  \end{tikzcd}
+  \begin{tikzpicture}[overlay,remember picture]
+    \begin{scope}[transform canvas={xshift=-3em}]
+      \draw[->,draw=gray] ($(WMC)+(0,0.1)$)--($(WMI)+(0,0.5)$) node[midway,left] {\textcolor{gray}{$\sum \to \int$}};
+      \draw[->,draw=gray] ($(WMC)-(0,0.1)$)--($(PBP)-(0,0.5)$) node[midway,left] {\textcolor{gray}{Generalising weights}};
+    \end{scope}
+    \begin{scope}[transform canvas={yshift=-2em}]
+      \draw[->,draw=gray] ($(PBP)-(1,0)$)--($(SP)+(1,0)$) node[midway,below] {\textcolor{gray}{From propositional to first-order logic}};
+    \end{scope}
+  \end{tikzpicture}
+  \vfill
+  \vspace{1.5cm}
+  What kind of logic is needed to succinctly describe, e.g.,
+  \begin{itemize}
+    \item $f(n) = f(f(n-1))$
+    \item or the Fibonacci sequence?
+  \end{itemize}
+\end{frame}
+% impossibility results as well (finite model theory)
+
+\begin{frame}{Algebraic Solutions to Parameterised Problems (1/2)}
+  \begin{itemize}
+    \item Suppose we have a Markov logic network that models the probability
+          \alert{$P$} that some system will fail.
+    \item Here:
+    \begin{itemize}
+      \item domain sizes describe the numbers of various components,
+      \item and weights express probabilities that:
+      \begin{itemize}
+        \item some component fails,
+        \item or some combination of failures leads to another failure.
+      \end{itemize}
+    \end{itemize}
+    \item Crane can express \alert{$P$} as a function of the domain sizes and
+          weights.
+  \end{itemize}
+\end{frame}
+
+\begin{frame}{Algebraic Solutions to Parameterised Problems (2/2)}
+  With the help of a computer algebra system, we can then:
+  \begin{itemize}
+    \item determine how \alert{$P$} scales with the number of users,
+    \item find combinations of domain sizes that keep \alert{$P$} below some
+          threshold,
+    \item find ranges of weights that keep \alert{$P$} sufficiently small across
+          a range of domain size values.
+  \end{itemize}
+\end{frame}
+% TODO: add a concluding diagram: 'reasoning with functions'(in a box) >(big) 'reasoning with numbers'
 

### 2023-04-13 doc/talks/3_long/plot.tex
First draft of the entire talk

% Created by tikzDevice version 0.12.3.1 on 2023-04-13 13:23:15
% !TEX encoding = UTF-8 Unicode
\documentclass[10pt]{article}
\usepackage{tikz}

\usepackage[active,tightpage,psfixbb]{preview}

\PreviewEnvironment{pgfpicture}

\setlength\PreviewBorder{0pt}
\begin{document}

\begin{tikzpicture}[x=1pt,y=1pt]
\definecolor{fillColor}{RGB}{255,255,255}
\path[use as bounding box,fill=fillColor,fill opacity=0.00] (0,0) rectangle (153.94, 95.40);
\begin{scope}
\path[clip] ( 36.11, 30.69) rectangle (148.44, 89.90);
\definecolor{drawColor}{gray}{0.92}

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 36.11, 41.73) --
	(148.44, 41.73);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 36.11, 57.34) --
	(148.44, 57.34);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 36.11, 72.95) --
	(148.44, 72.95);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 36.11, 88.56) --
	(148.44, 88.56);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 49.55, 30.69) --
	( 49.55, 89.90);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 70.39, 30.69) --
	( 70.39, 89.90);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 91.23, 30.69) --
	( 91.23, 89.90);

\path[draw=drawColor,line width= 0.3pt,line join=round] (112.07, 30.69) --
	(112.07, 89.90);

\path[draw=drawColor,line width= 0.3pt,line join=round] (132.91, 30.69) --
	(132.91, 89.90);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 36.11, 33.93) --
	(148.44, 33.93);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 36.11, 49.54) --
	(148.44, 49.54);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 36.11, 65.15) --
	(148.44, 65.15);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 36.11, 80.76) --
	(148.44, 80.76);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 39.13, 30.69) --
	( 39.13, 89.90);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 59.97, 30.69) --
	( 59.97, 89.90);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 80.81, 30.69) --
	( 80.81, 89.90);

\path[draw=drawColor,line width= 0.6pt,line join=round] (101.65, 30.69) --
	(101.65, 89.90);

\path[draw=drawColor,line width= 0.6pt,line join=round] (122.49, 30.69) --
	(122.49, 89.90);

\path[draw=drawColor,line width= 0.6pt,line join=round] (143.33, 30.69) --
	(143.33, 89.90);
\definecolor{drawColor}{RGB}{0,0,0}
\definecolor{fillColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 41.22, 33.93) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 43.30, 33.93) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 45.38, 33.93) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 47.47, 33.93) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 49.55, 33.93) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 51.64, 33.93) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 53.72, 33.93) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 55.80, 33.93) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 57.89, 33.93) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 59.97, 33.94) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 62.06, 33.94) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 64.14, 33.95) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 66.22, 33.96) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 68.31, 33.97) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 70.39, 33.98) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 72.48, 34.06) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 74.56, 34.02) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 76.64, 34.05) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 78.73, 34.09) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 80.81, 34.13) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 82.90, 34.18) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 84.98, 34.26) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 87.06, 34.33) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 89.15, 34.43) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 91.23, 34.56) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 93.32, 34.70) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 95.40, 34.89) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 97.48, 35.08) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 99.57, 35.36) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (101.65, 35.74) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (103.73, 36.04) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (105.82, 36.50) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (107.90, 37.36) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (109.99, 37.65) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (112.07, 38.43) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (114.15, 39.34) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (116.24, 40.34) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (118.32, 41.54) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (120.41, 42.91) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (122.49, 45.10) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (124.57, 47.55) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (126.66, 48.85) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (128.74, 52.11) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (130.83, 54.60) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (132.91, 58.27) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (134.99, 63.85) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (137.08, 67.78) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (139.16, 73.61) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (141.25, 79.65) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (143.33, 87.21) circle (  1.96);
\definecolor{drawColor}{RGB}{27,158,119}

\path[draw=drawColor,line width= 1.1pt,line join=round] ( 41.22, 34.87) --
	( 42.51, 34.52) --
	( 43.80, 34.23) --
	( 45.09, 33.99) --
	( 46.39, 33.79) --
	( 47.68, 33.64) --
	( 48.97, 33.53) --
	( 50.26, 33.45) --
	( 51.56, 33.40) --
	( 52.85, 33.38) --
	( 54.14, 33.38) --
	( 55.44, 33.40) --
	( 56.73, 33.44) --
	( 58.02, 33.49) --
	( 59.31, 33.56) --
	( 60.61, 33.63) --
	( 61.90, 33.71) --
	( 63.19, 33.79) --
	( 64.48, 33.88) --
	( 65.78, 33.96) --
	( 67.07, 34.05) --
	( 68.36, 34.13) --
	( 69.65, 34.21) --
	( 70.95, 34.28) --
	( 72.24, 34.35) --
	( 73.53, 34.42) --
	( 74.82, 34.47) --
	( 76.12, 34.52) --
	( 77.41, 34.56) --
	( 78.70, 34.60) --
	( 79.99, 34.63) --
	( 81.29, 34.65) --
	( 82.58, 34.67) --
	( 83.87, 34.68) --
	( 85.16, 34.69) --
	( 86.46, 34.70) --
	( 87.75, 34.70) --
	( 89.04, 34.71) --
	( 90.33, 34.72) --
	( 91.63, 34.74) --
	( 92.92, 34.76) --
	( 94.21, 34.79) --
	( 95.50, 34.84) --
	( 96.80, 34.89) --
	( 98.09, 34.97) --
	( 99.38, 35.07) --
	(100.67, 35.19) --
	(101.97, 35.34) --
	(103.26, 35.52) --
	(104.55, 35.73) --
	(105.85, 35.99) --
	(107.14, 36.29) --
	(108.43, 36.63) --
	(109.72, 37.03) --
	(111.02, 37.49) --
	(112.31, 38.01) --
	(113.60, 38.60) --
	(114.89, 39.26) --
	(116.19, 40.00) --
	(117.48, 40.82) --
	(118.77, 41.74) --
	(120.06, 42.75) --
	(121.36, 43.87) --
	(122.65, 45.10) --
	(123.94, 46.44) --
	(125.23, 47.91) --
	(126.53, 49.51) --
	(127.82, 51.24) --
	(129.11, 53.12) --
	(130.40, 55.16) --
	(131.70, 57.35) --
	(132.99, 59.72) --
	(134.28, 62.26) --
	(135.57, 64.99) --
	(136.87, 67.91) --
	(138.16, 71.04) --
	(139.45, 74.38) --
	(140.74, 77.94) --
	(142.04, 81.73) --
	(143.33, 85.77);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (153.94, 95.40);
\definecolor{drawColor}{gray}{0.30}

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 31.16, 30.89) {0};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 31.16, 46.51) {250};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 31.16, 62.12) {500};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 31.16, 77.73) {750};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (153.94, 95.40);
\definecolor{drawColor}{gray}{0.30}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 39.13, 19.68) {0};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 59.97, 19.68) {10};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 80.81, 19.68) {20};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (101.65, 19.68) {30};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (122.49, 19.68) {40};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (143.33, 19.68) {50};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (153.94, 95.40);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at ( 92.27,  7.64) {Domain size};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (153.94, 95.40);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at ( 13.08, 60.29) {Runtime (s)};
\end{scope}
\end{tikzpicture}

\end{document}

### 2023-04-13 doc/talks/3_long/talk.tex
First draft of the entire talk

@@
 \date{18th April 2023}
-% TODO: unify the use of colours, maybe replace red!50 with one of the main colours
-% TODO: how do we capitalise titles of \block?
-% TODO: make sure I'm using the 'forest' package whenever possible
-% TODO: consider adding an outline slide
-% TODO: add periods at the end of sentences
 
@@
       \onslide<8>
-      \begin{block}{Generalisations of the weight function}
+      \begin{block}{Generalisations of the Weight Function}
         \begin{itemize}
@@
     \item Example formula: \\
-          \alert{$\forall x \in \Delta\text{. } \pP(x) \lor \qQ(x)$}
-    \item Let \alert{$\Delta \coloneqq \{\, 1, 2 \,\}$}
+          \alert{$\forall x \in \Delta\text{. } \pP(x) \lor \qQ(x)$}.
+    \item Let \alert{$\Delta \coloneqq \{\, 1, 2 \,\}$}.
     \item Interpretations: all subsets of\\
-          \alert{$\{\, \pP(1), \qQ(1), \pP(2), \qQ(2) \,\}$}
+          \alert{$\{\, \pP(1), \qQ(1), \pP(2), \qQ(2) \,\}$}.
     \item<2-> Models:
@@
         \{\, \qone, \ptwo \,\}, & \{\, \qone, \qtwo \,\}, & \{\, \qone, \pqtwo \,\},\\
-        \{\, \pqone, \ptwo \,\}, & \{\, \pqone, \qtwo \,\}, & \{\, \pqone, \pqtwo \,\}\\
+        \{\, \pqone, \ptwo \,\}, & \{\, \pqone, \qtwo \,\}, & \{\, \pqone, \pqtwo \,\}.\\
       \end{matrix}
@@
       \begin{itemize}
-        \item Each 1-ary predicate is like a \alert{subset}
+        \item Each 1-ary predicate is like a \alert{subset}.
         \item For \alert{$n>1$}, each \alert{$n$}-ary predicate is like a
-              \alert{relation}
-        \item FOMC counts \alert{combinations of relations}
+              \alert{relation}.
+        \item FOMC counts \alert{combinations of relations}.
       \end{itemize}
@@
     \begin{itemize}
-      \item using dynamic programming
+      \item using dynamic programming.
     \end{itemize}\pause
     \item \alert{Optimal} time complexity to compute \alert{$n^{\underline{m}}$}
-          is \alert{$\Theta(m)$}
+          is \alert{$\Theta(m)$}.
     \item But \alert{$\Theta(mn)$} is still much better than translating to
-          propositional logic and solving a \alert{$\#\P$-complete} problem
-          \pause
-    \item The rest of this talk is about how to find such functions automatically
+          propositional logic and solving a \alert{$\#\P$-complete} problem.
+          \pause
+    \item The rest of this talk is about how to find such functions
+          automatically.
   \end{itemize}
@@
 \begin{frame}{Resulting Improvements to Counting Functions}
-  Let \alert{$\Gamma$} and \alert{$\Delta$} be two sets with
-  cardinalities \alert{$|\Gamma| = m$} and \alert{$|\Delta| = n$}.
-
-  Our new rules enable Crane to efficiently count
-  \alert{$\Gamma \to \Delta$} functions such as:
+  Let \alert{$\Gamma$} and \alert{$\Delta$} be two sets with cardinalities
+  \alert{$|\Gamma| = m$} and \alert{$|\Delta| = n$}.
+
+  Our new rules enable Crane to efficiently count \alert{$\Gamma \to \Delta$}
+  functions such as:\pause
   \begin{itemize}
@@
     \begin{itemize}
-            \item by hand: \alert{$\Theta(m)$}
+      \item by hand: \alert{$\Theta(m)$}\pause
     \end{itemize}
@@
     \begin{itemize}
-            \item by hand: \alert{$\Theta({\min\{\, m, n \,\}}^2)$}
+      \item by hand: \alert{$\Theta({\min\{\, m, n \,\}}^2)$}\pause
     \end{itemize}
@@
     \begin{itemize}
-            \item \alert{optimal!}
-            \item FastWFOMC seems to be \alert{$\Omega(m^{4})$}
-          \end{itemize}
-  \end{itemize}
-\end{frame}
-% TODO: add 2 more statements about fastwfomc, showing their plots on the RHS
-% when revealing them
+      \item \alert{optimal!}\pause
+      \item experimentally, FastWFOMC runtime appears to be \alert{$\Omega(m^{4})$}
+    \end{itemize}
+  \end{itemize}
+  \begin{tikzpicture}[remember picture,overlay]
+    \node[draw,rectangle,color=gray] at ([xshift=-3cm]current page.east) {\includegraphics{plot}};
+  \end{tikzpicture}
+\end{frame}
 
@@
 
-% TODO: maybe add a future <-> past picture slide
+{ % all template changes are local to this group.
+    \setbeamertemplate{navigation symbols}{}
+    \begin{frame}<article:0>[plain]
+        \begin{tikzpicture}[remember picture,overlay]
+            \node[at=(current page.center)] {
+                \includegraphics[keepaspectratio, height=\paperheight]{future.jpg}
+            };
+        \end{tikzpicture}
+     \end{frame}
+}
 
@@
   \end{itemize}
-\end{frame}
-% TODO: add a concluding diagram: 'reasoning with functions'(in a box) >(big) 'reasoning with numbers'
+  \pause
+  \vfill
+  \centering
+  \begin{tikzpicture}
+    \node[draw] (a) {Reasoning with \alert{functions}};
+    \node[right=0.5cm of a] (b) {\Huge\textcolor{color2}{$>$}};
+    \node[draw,right=0.5cm of b] (c) {Reasoning with \alert{numbers}};
+  \end{tikzpicture}
+\end{frame}
 

### 2023-04-13 solvers/fastwfomc/plot.R

@@ -75,3 +75,15 @@ ggplot(df, aes(x = n, y = time)) +
                    min.segment.length = Inf)
 dev.off()
 
+tikz(file = "../../doc/talks/3_long/plot.tex", width = 2.13, height = 1.32,
+     standAlone = TRUE)
+ggplot(df, aes(x = n, y = time)) +
+  geom_point() +
+  stat_smooth(method = 'lm', se = FALSE, formula = y ~ poly(x, BEST_DEGREE),
+              aes(color = NAME), fill = colours[2]) +
+  xlab('Domain size') +
+  ylab('Runtime (s)') +
+  theme_set(theme_gray(base_size = 9)) +
+  theme_minimal() +
+  scale_color_manual(name = "Model fit", values = colours, guide = FALSE)
+dev.off()

### 2023-04-18 doc/talks/3_long/talk.tex
Minor changes to the slides

@@
     \node<2>[ellipse callout, draw, left=-0.5cm, below=0.5cm] at (computer.north west) {$\sqrt{\pi}$};
-    \node<3>[ellipse callout, draw, right=0cm, callout relative pointer={(-1, -0.15)},text width=5cm] at (stickman.north east) {Produce a schedule for the nurses at the local hospital.};
+    \node<3>[ellipse callout, draw, right=0cm, callout relative pointer={(-1, -0.15)},text width=5cm] at (stickman.north east) {Produce a \alert{schedule} for the nurses at the local hospital.};
     \node<3>[ellipse callout, draw, below=0.5cm, shift=({-0.5,0}), callout relative pointer={(0.5, -0.25)}] at (computer.north west) {\includegraphics[width=0.1\textwidth]{schedule}};
@@
   \end{itemize}
-  \onslide<3->{
+  \onslide<2->{
     \begin{block}{Intuition}
@@
 
-\begin{frame}{Approaches to FOMC}
+\begin{frame}{Exact Algorithms for FOMC}
   \begin{itemize}
@@
     \end{itemize}
-    \item Let $\pP \subseteq \Gamma \times \Delta$ be a relation (i.e.,
+    \item Let \alert{$\pP \subseteq \Gamma \times \Delta$} be a relation (i.e.,
           predicate) over \alert{$\Gamma$} and \alert{$\Delta$}.
@@
   \end{itemize}
-  \pause \eqref{eq:a1} and \eqref{eq:a2} constrain $\pP$ to be a function, and
-  \eqref{eq:a3} makes it injective.
+  \pause \alert{\eqref{eq:a1}} and \alert{\eqref{eq:a2}} constrain \alert{$\pP$}
+  to be a function, and \alert{\eqref{eq:a3}} makes it injective.
 \end{frame}
@@
           \pause
-    \item The rest of this talk is about how to find such functions
+    \item The rest of this talk is about how to construct such functions
           automatically.
@@
     \begin{itemize}
-    \item \alert{$G$} is an FCG,
+    \item \alert{$G$} is a (possibly incomplete) FCG,
     \item and \alert{$L$} is a list of formulas.
@@
   \pause
-  Only one \alert{(G, L)} pair:
+  The independence compilation rule returns one \alert{(G, L)} pair:
   \[
@@
               \item Extend each such bijection to a map between sets of domains.
-              \item If the bijection makes the clauses equal, and the domain map
-                    is compatible with previous domain maps, move on to another
-                    pair of clauses.
+              \item If the bijection makes the clauses equivalent, and the
+                    domain map is compatible with previous domain maps, move on
+                    to another pair of clauses.
             \end{enumerate}
@@
     \node[below=0.5cm of after1] (plus) {\textcolor{color2}{\Huge$+$}};
-    \node[below=0.5cm of plus] {$\{\, \alert{\Gamma} \mapsto \alert{\Gamma'}, \alert{\Delta^{\bot}} \mapsto \alert{\Delta} \,\}$};
+    \node[below=0.5cm of plus] {$\{\, \alert{\Gamma} \mapsto \alert{\Gamma'}, \alert{\Delta} \mapsto \alert{\Delta^{\bot}} \,\}$};
   \end{tikzpicture}
@@
   Our new rules enable Crane to efficiently count \alert{$\Gamma \to \Delta$}
-  functions such as:\pause
+  functions such as:
   \begin{itemize}
@@
     \begin{itemize}
-      \item by hand: \alert{$\Theta(m)$}\pause
+      \item by hand: \alert{$\Theta(m)$}
     \end{itemize}
@@
     \begin{itemize}
-      \item by hand: \alert{$\Theta({\min\{\, m, n \,\}}^2)$}\pause
+      \item by hand: \alert{$\Theta({\min\{\, m, n \,\}}^2)$}
     \end{itemize}
@@
     \begin{itemize}
-      \item \alert{optimal!}\pause
-      \item experimentally, FastWFOMC runtime appears to be \alert{$\Omega(m^{4})$}
-    \end{itemize}
-  \end{itemize}
-  \begin{tikzpicture}[remember picture,overlay]
-    \node[draw,rectangle,color=gray] at ([xshift=-3cm]current page.east) {\includegraphics{plot}};
-  \end{tikzpicture}
+      \item \alert{optimal!}%\pause
+      %\item In comparison, FastWFOMC scales as \alert{$\Omega(m^{4})$}.
+    \end{itemize}
+  \end{itemize}
+  % \begin{tikzpicture}[remember picture,overlay]
+  %   \node[draw,rectangle,color=gray] at ([xshift=-3cm]current page.east) {\includegraphics{plot}};
+  % \end{tikzpicture}
 \end{frame}

### 2023-04-19 doc/talks/3_long/talk.tex
Minor changes based on feedback

@@
 \institute{National University of Singapore, Singapore}
-\date{18th April 2023}
+\date{PLSE Seminar, 21st April 2023}
 
@@
     0 & \text{if } m > 0 \text{ and } n = 0 \\
-    f(m, n-1) + mf(m-1, n-1) & \text{otherwise.}
+    f(m, n-1) + m \times f(m-1, n-1) & \text{otherwise.}
   \end{cases}
@@
         \draw[-Latex,color=color2] (sizes) -- (evaluation);
+        \node[draw,fit={(kc) (graph) (evaluation)},inner xsep=1pt,inner ysep=2pt] {};
       \end{tikzpicture}
@@
         \node[draw,rounded rectangle,fill=color2!50,below=0.3cm of initial] (simplification) {Simplification};
-        \node[below=0.3cm of simplification] (simplified) {\tiny $f(m, n) = f(m, n-1) + mf(m-1, n-1)$};
+        \node[below=0.3cm of simplification] (simplified) {\tiny $f(m, n) = f(m, n-1) + m \times f(m-1, n-1)$};
         \node[draw,rounded rectangle,fill=color2!50,below=0.3cm of simplified] (evaluation) {Evaluation};
@@
         \draw[-Latex,color=color2] (sizes) -- (evaluation);
+        \node[draw,fit={(kc) (graph) (interpretation)},inner xsep=1pt,inner ysep=2pt,visible on=<3->] {};
       \end{tikzpicture}
@@
         \onslide<4->{f(m, n) &=} \onslide<5->{\sum_{l=0}^m \binom{m}{l}} \onslide<8->{[l<2]} \onslide<7->{\times} \onslide<9->{f(m-l, n-1)}\\
-        \onslide<10>{&= f(m, n-1) + mf(m-1, n-1)}
+        \onslide<10->{&= \binom{m}{0} \times f(m-0, n-1)}\\
+        \onslide<10->{&+ \binom{m}{1} \times f(m-1, n-1)}\\
+        \onslide<11->{&= f(m, n-1) + m \times f(m-1, n-1)}
       \end{align*}
@@
 \end{frame}
+% NOTE: need to explain how atom counting splits the domain
 

### 2023-05-10 solutions.py
One more slide

@@ -293,28 +293,28 @@ def weird1(n, fun=weird2): # should compute partial injections from [n] to [n]
 def example(m, n):
     return int(math.factorial(m)/math.factorial(m-n))
 
-MAX = 20
+def two_dimensional_partial_surjections(x, y):
+    return sum(math.comb(x, z) * (-1)**(x-z) * (1+z)**y for z in range(x+1))
 
-# for m in range(1, MAX):
-#     for n in range(1, m+1):
-#         print("f({}, {}) = {}".format(m, n, example(m, n)))
+MAX = 5
 
-for m in range(1, MAX):
-    print(m, int(3 ** m))
+# for m in range(0, MAX+1):
+#     for n in range(0, MAX+1):
+#         print("f({}, {}) = {}".format(m, n, two_dimensional_partial_surjections(n, m)))
 
 # for n in range(1, MAX):
 #     print("f({}) = {} ({})".format(n, weird1(n), two_dimensional_partial_injections(n, n)))
 
-# for m in range(0, MAX):
-#     for n in range(0, MAX):
-#         print(
-#             "f({}, {}) = {} ({})".format(
-#                 m,
-#                 n,
-#                 weird2(m, n),
-#                 two_dimensional_injections(n, m),
-#             )
-#         )
+for m in range(0, MAX+1):
+    for n in range(0, MAX+1):
+        print(
+            "f({}, {}) = {} ({})".format(
+                m,
+                n,
+                two_dimensional_partial_surjections(m, n),
+                my_two_dimensional_surjections(n, m+1),
+            )
+        )
 
 # for n in range(0, MAX):
 #     print(str(weird1(n)) + ", ", end="")

### 2023-05-25 doc/talks/3_long/talk.tex
One more slide
Make the talk slightly longer

@@
 \SoulColor
+
+\newcommand\Wider[2][3em]{%
+\makebox[\linewidth][c]{%
+  \begin{minipage}{\dimexpr\textwidth+#1\relax}
+  \raggedright#2
+  \end{minipage}%
+  }%
+}
 
@@
 
-% 15 min (8 slides, currently have 7) introduction
-% 25 min (13 slides, currently have 10) presentation
-% 5 min (3 slides, currently have 1) summary
-% make sure there's a clear and coherent storyline
-
 \author{Paulius Dilkas \\ \vspace{1cm} \tiny{Joint work with Vaishak Belle (Univeristy of Edinburgh, UK)}}
@@
 \institute{National University of Singapore, Singapore}
-\date{PLSE Seminar, 21st April 2023}
+\date{DTAI Seminar, 26th May 2023}
 
@@
 \end{frame}
-% maybe mention #CSP and other non-SAT ways of counting (SMT?, counting paths in
-% automata and directed graphs)
 
@@
 
+\begin{frame}{More Formally: What Is the Input?}
+  \[
+    \forall x \in \alert<2>{\Gamma}\text{. }\forall y, z \in \alert<2>{\Delta}\text{. }\pP(x, y) \land \pP(x, z) \Rightarrow \alert<4>{y=z}
+  \]
+  \begin{block}{\alert<2>{Many-Sorted} \alert<3>{Function-Free} First-Order Logic with \alert<4>{Equality}}
+  \begin{itemize}
+    \item<5-> Any number of variables
+    \item<5-> All variables are bound
+    \item<6-> \alert{$\forall$} and \alert{$\exists$} quantifiers can be nested arbitrarily deep
+    \item<6-> All domains are finite
+    \item<6-> Predicates can have any arity
+  \end{itemize}
+  \end{block}
+\end{frame}
+
 \begin{frame}{Exact Algorithms for FOMC}
@@
 \end{frame}
+% NOTE: explain what knowledge compilation is
 
@@
 
-% an example on partial injection (i.e., bipartite matching) counting
+%% \begin{frame}{Compilation as Search}
+%%   \begin{definition}
+%%     A \alert{(search) state} is a tuple \structure{$(G, C, L)$}, where:
+%%     \begin{itemize}
+%%     \item \structure{$G$} is an FCG (or \texttt{null}),
+%%     \item \structure{$C$} is a compilation cache that maps integers to sets of pairs $(\phi, v)$, where $\phi$ is a formula, and $v$ is a node of $G$ (which is used to identify opportunities for recursion),
+%%     \item and \structure{$L$} is a list of formulas (that are yet to be compiled). (Note that the order is crucial!)
+%%     \end{itemize}
+%%   \end{definition}
+%%   The search algorithm combines greedy and breadth-first search:
+%% \end{frame}
+
 \begin{frame}{How These Rules Fit Together (1/5)}
@@
 
-%% \begin{frame}{Compilation as Search}
-%%   \begin{definition}
-%%     A \alert{(search) state} is a tuple \structure{$(G, C, L)$}, where:
-%%     \begin{itemize}
-%%     \item \structure{$G$} is an FCG (or \texttt{null}),
-%%     \item \structure{$C$} is a compilation cache that maps integers to sets of pairs $(\phi, v)$, where $\phi$ is a formula, and $v$ is a node of $G$ (which is used to identify opportunities for recursion),
-%%     \item and \structure{$L$} is a list of formulas (that are yet to be compiled). (Note that the order is crucial!)
-%%     \end{itemize}
-%%   \end{definition}
-%%   The search algorithm combines greedy and breadth-first search:
-%% \end{frame}
-
 \begin{frame}{Resulting Improvements to Counting Functions}
-  Let \alert{$\Gamma$} and \alert{$\Delta$} be two sets with cardinalities
-  \alert{$|\Gamma| = m$} and \alert{$|\Delta| = n$}.
+  \Wider[3em]{ Let \alert{$\Gamma$} and \alert{$\Delta$} be two sets with
+    cardinalities \alert{$|\Gamma| = m$} and \alert{$|\Delta| = n$}.
 
     Our new rules enable Crane to efficiently count \alert{$\Gamma \to \Delta$}
-  functions such as:
-  \begin{itemize}
+    functions such as: \vspace{1em}
+    \begin{itemize}
+            \setlength\itemsep{1em}
       \item injections in \alert{$\Theta(mn)$} time
@@
             \begin{itemize}
-      \item \alert{optimal!}%\pause
-      %\item In comparison, FastWFOMC scales as \alert{$\Omega(m^{4})$}.
-    \end{itemize}
-  \end{itemize}
-  % \begin{tikzpicture}[remember picture,overlay]
-  %   \node[draw,rectangle,color=gray] at ([xshift=-3cm]current page.east) {\includegraphics{plot}};
-  % \end{tikzpicture}
+              \item \alert{optimal!}\pause
+              \item In comparison, FastWFOMC scales as \alert{$\Omega(m^{4})$}.
+            \end{itemize}
+    \end{itemize}
+  }
+  \begin{tikzpicture}[remember picture,overlay]
+    \node[draw,rectangle,color=gray] at ([xshift=-3.3cm,yshift=-0.2cm]current page.east) {\includegraphics{plot}};
+  \end{tikzpicture}
 \end{frame}

### 2023-06-07 doc/arxiv_version/paper.tex
Cleanup

--- 2023-03-10 doc/paper/paper.tex
@@
 \end{abstract}
-
-% KEYWORDS:
-% model counting
-% first-order logic
-% recursion
-% knowledge compilation
-
-% TOPICS:
-% KR & ML: probabilistic reasoning and learning
-% KR & ML: statistical relational learning
-% (no) computational aspects of knowledge representation
-% (no) knowledge representation languages
-% (no) KR & ML: graphical models for knowledge representation and reasoning
 
@@
 an algorithm capable of handling more instances in a lifted manner. The ideas
-presented in this paper are implemented in \textsc{Crane}---an extension of the
-(W)FOMC algorithm \textsc{ForcLift}. The differences in how these algorithms
-operate are depicted in \cref{fig:process}. Compilation is performed by applying
-various \emph{(compilation) rules} to the input (or some derivative) formula,
-gradually constructing a circuit (in the case of \textsc{ForcLift}) or a graph
-(in the case of \textsc{Crane}). \textsc{ForcLift} applies compilation rules via
-greedy search, whereas \textsc{Crane} also supports a hybrid search algorithm
-that applies some rules greedily and some using breadth-first
-search.\footnote{In the current implementation, the rules applied non-greedily
-  are: atom counting, inclusion-exclusion, independent partial groundings,
-  Shannon decomposition, shattering, and two new rules described in
-  \cref{sec:dr,sec:ref}---see previous work~\cite{DBLP:conf/ijcai/BroeckTMDR11}
-  for more information about the rules.} This alternative was introduced because
-there is no reason to expect greedy search to be complete. Another difference is
-that---in \textsc{Crane}---the product of compilation is not directly evaluated
-but transformed into a collection of functions on domain sizes. Hence, our
-approach is reminiscent of previous work on lifted inference via compilation to
-C++ programs~\cite{DBLP:conf/kr/KazemiP16} and the broader area of functional
-synthesis~\cite{DBLP:conf/cav/GoliaRM20,DBLP:conf/pldi/KuncakMPS10,sanathanan1963transfer}.
+presented in this paper are implemented in
+\textsc{Crane}\footnote{\url{https://github.com/dilkas/crane}}\textsuperscript{,}\footnote{\url{https://doi.org/10.5281/zenodo.8004077}}---an
+extension of the (W)FOMC algorithm \textsc{ForcLift}. The differences in how
+these algorithms operate are depicted in \cref{fig:process}. Compilation is
+performed by applying various \emph{(compilation) rules} to the input (or some
+derivative) formula, gradually constructing a circuit (in the case of
+\textsc{ForcLift}) or a graph (in the case of \textsc{Crane}). \textsc{ForcLift}
+applies compilation rules via greedy search, whereas \textsc{Crane} also
+supports a hybrid search algorithm that applies some rules greedily and some
+using breadth-first search.\footnote{In the current implementation, the rules
+  applied non-greedily are: atom counting, inclusion-exclusion, independent
+  partial groundings, Shannon decomposition, shattering, and two new rules
+  described in \cref{sec:dr,sec:ref}. See previous work for more information
+  about the rules~\cite{DBLP:conf/ijcai/BroeckTMDR11} and the search
+  algorithm~\cite{dilkas2023generalising}.} This alternative was introduced
+because there is no reason to expect greedy search to be complete. Another
+difference is that---in \textsc{Crane}---the product of compilation is not
+directly evaluated but transformed into a collection of functions on domain
+sizes. Hence, our approach is reminiscent of previous work on lifted inference
+via compilation to C++ programs~\cite{DBLP:conf/kr/KazemiP16} and the broader
+area of functional
+synthesis~\cite{DBLP:conf/cav/GoliaRM20,DBLP:conf/pldi/KuncakMPS10}.
 
@@
 
-Our representation of FOMC instances builds on the format used internally by
+Our representation of FOMC instances builds on the format used by
 \textsc{ForcLift}, some aspects of which are described by Van den Broeck et
@@
 $\neg \predicate(x_1, \dots, x_n)$). Let $\mathcal{D}$ be the set of all
-relevant (finite) domains. Initially, $\mathcal{D}$ contains all domains
-mentioned by the input formula. During compilation, new domains are added to
-$\mathcal{D}$. Each new domain is interpreted as a subset of another domain in
-$\mathcal{D}$.
+relevant domains. Initially, $\mathcal{D}$ contains all domains mentioned by the
+input formula. During compilation, new domains are added to $\mathcal{D}$. Each
+new domain is interpreted as a subset of another domain in $\mathcal{D}$.
 
@@
 
-The model count of a formula $\phi$ also depends on the sizes of the domains in
-$\phi$. Let $\sigma\colon \mathcal{D} \to \mathbb{N}_{0}$ be the \emph{domain
-  size function} that maps each domain to a non-negative integer.
+Let $\sigma\colon \mathcal{D} \to \mathbb{N}_{0}$ be the \emph{domain size
+  function} that maps each domain to a non-negative integer.
+
+% By a relation between two (potentially distinct) sets, we mean any
+% subset of their Cartesian product. Thus, if both sets have cardinality two,
+% their Cartesian product has cardinality four, and this product set has 2^4 =
+% 16 subsets. To check whether a subset S is a model, we interpret S as the set
+% of all pairs (X, Y) for which p(X, Y) is true. Each of the two clauses in the
+% example (c_1 and c_2) imposes certain constraints on S. For example, for
+% domains Gamma = Delta = {1, 2}, clause c_1 requires that:
+% 1) either (1, 1) or (1, 2) is not in S,
+% 2) either (2, 1) or (2, 2) is not in S.
 
@@
   i.e., $\sigma(\Gamma) = \sigma(\Delta) = 2$. There are $2^{2 \times 2} = 16$
-  possible relations between $\Gamma$ and $\Delta$. Let us count how many of
-  them satisfy the conditions imposed on predicate $\predicate$. The empty
-  relation does. All four relations of cardinality one (e.g.,
-  $\{\, (1, 1) \,\}$) do too. Finally, there are two relations of cardinality
-  two---$\{\, (1, 1), (2, 2) \,\}$ and $\{\, (1, 2), (2, 1) \,\}$---that satisfy
-  the conditions as well. Therefore, the FOMC of $(\phi, \sigma)$ is 7.
-  Incidentally, the FOMC of $\phi$ counts partial injections from $\Gamma$ to
-  $\Delta$. We will continue to use the problem of counting partial injections
-  as the main running example.
+  possible relations between $\Gamma$ and $\Delta$, i.e., subsets of
+  $\Gamma \times \Delta$. Let us count how many of them satisfy the conditions
+  imposed on predicate $\predicate$. The empty relation does. All four relations
+  of cardinality one (e.g., $\{\, (1, 1) \,\}$) do too. Finally, there are two
+  relations of cardinality two---$\{\, (1, 1), (2, 2) \,\}$ and
+  $\{\, (1, 2), (2, 1) \,\}$---that satisfy the conditions as well. Therefore,
+  the FOMC of $(\phi, \sigma)$ is 7. Incidentally, the FOMC of $\phi$ counts
+  partial injections from $\Gamma$ to $\Delta$. We will continue to use the
+  problem of counting partial injections as the main running example.
 \end{example}
@@
 Van den Broeck~\shortcite{DBLP:conf/nips/Broeck11} imposes stringent conditions
-on the input formula to ensure that the expanded version of the formula (as in
-\cref{example:dr}) can be handled efficiently. For instance,
-\cref{example:first} cannot be handled by \textsc{ForcLift} because there is no
-root binding class, i.e., the two root variables belong to different equivalence
-classes with respect to the binding relationship. The clauses in this expanded
-formula are then partitioned into three parts based on whether the
-transformation introduced constants, constraints, or both. The conditions ensure
-that these parts can be treated independently.
+on the input formula to ensure that its expanded version (as in
+\cref{example:dr}) can be handled efficiently. \Cref{example:first} cannot be
+handled by \textsc{ForcLift} because there is no root binding class, i.e., the
+two root variables belong to different equivalence classes with respect to the
+binding relationship.
+
+% The clauses in this expanded
+% formula are then partitioned into three parts based on whether the
+% transformation introduced constants, constraints, or both. The conditions ensure
+% that these parts can be treated independently.
 
@@
   after substitution. Similarly, we want to avoid variables in $W$ that have
-  inequality constraints with constants: after the substitution, such
-  constraints transform into inequality constraints between two constants. In
-  this case, both subsets of $V$ satisfy the conditions, and
-  \cref{line:generation} generates two clauses:
+  inequality constraints with constants. In this case, both subsets of $V$
+  satisfy the conditions, and \cref{line:generation} generates two clauses:
   \begin{multline*}
@@
 Broeck~\shortcite{DBLP:conf/nips/Broeck11}. For the proofs of this and other
-theorems, see supplementary material.
+theorems, see \cref{sec:proofs}.
 
@@
 \subsubsection{Caching}
-\textsc{ForcLift}~\cite{DBLP:conf/ijcai/BroeckTMDR11} uses a cache to check if a
-formula is identical to one of the formulas that have already been fully
-compiled. To facilitate recursion, we extend the caching scheme to include
-formulas encountered before but not fully compiled yet. Formally, we define a
-\emph{cache} as a map from integers (e.g., hash codes) to sets of pairs of the
-form $(\phi, v)$, where $\phi$ is a formula, and $v$ is an FCG node.
+\textsc{ForcLift} uses a cache to check if a formula is identical to one of the
+formulas that have already been fully compiled. To facilitate recursion, we
+extend the caching scheme to include formulas encountered before but not fully
+compiled yet. Formally, we define a \emph{cache} as a map from integers (e.g.,
+hash codes) to sets of pairs of the form $(\phi, v)$, where $\phi$ is a formula,
+and $v$ is an FCG node.
 
@@
 We compare \textsc{Crane} and
-\textsc{ForcLift}\footnote{\url{https://dtaid.cs.kuleuven.be/wfomc}}~\cite{DBLP:conf/ijcai/BroeckTMDR11}
-on their ability to count various classes of functions. We chose this class of
-instances because of its simplicity and the inability of publicly available
-WFOMC algorithms to solve many such counting problems. Note that, except for a
+\textsc{ForcLift}\footnote{\url{https://dtaid.cs.kuleuven.be/wfomc}} on their
+ability to count various classes of functions. We chose this class of instances
+because of its simplicity and the inability of publicly available WFOMC
+algorithms to solve many such counting problems. Note that, except for a
 particular version of \textsc{FastWFOMC}, other exact WFOMC algorithms cannot
@@
 surjectivity, partiality, and endo-), omitting duplicate descriptions of the
-same function/sequence. We run each algorithm once on each instance.
-\textsc{Crane} is run in hybrid search mode until either it finds five solutions
-or the search tree reaches height six. \textsc{ForcLift} is always run until it
-terminates. If successful, \textsc{Crane} returns one or more sets of function
-definitions, and \textsc{ForcLift} returns a circuit, which can similarly be
-interpreted as a function definition. We then assess the complexity of each
-solution by hand and pick the best in case \textsc{Crane} returns several
-solutions of varying complexities.
+same function, e.g., the number of partial $\Gamma \to \Delta$ bijections is the
+same as the number of $\Delta \to \Gamma$ injections. We run each algorithm once
+on each instance. \textsc{Crane} is run in hybrid search mode until either it
+finds five solutions or the search tree reaches height six. \textsc{ForcLift} is
+always run until it terminates. If successful, \textsc{Crane} returns one or
+more sets of function definitions, and \textsc{ForcLift} returns a circuit,
+which can similarly be interpreted as a function definition. We then assess the
+complexity of each solution by hand and pick the best in case \textsc{Crane}
+returns several solutions of varying complexities. In our experiments,
+\textsc{Crane} found at most four solutions per problem instance, and most
+solution had the same complexity.
+
+% Automatically determining the complexity of a solution generated by
+% Crane is another area for future work. Alternatively, one could evaluate
+% several solutions in parallel until one of them produces the model count. In
+% our experiments, Crane found at most four solutions per problem instance. Most
+% had the same complexity, although some were less efficient (e.g., cubic
+% instead of linear or quintic instead of cubic).
 
@@
 to follow the definitions of constituent functions without recomputing the same
-quantity multiple times. In particular, we assume that each function call and
-binomial coefficient is computed at most once, and computing $\binom{n}{k}$
-takes $\Theta(nk)$ time. For example, the complexity of \cref{eq:solution} is
+quantity multiple times.\footnote{Although this is not done by default, one
+  could also use arbitrary-precision arithmetic and consider bit complexity
+  instead.} In particular, we assume that each function call and binomial
+coefficient is computed at most once, and computing $\binom{n}{k}$ takes
+$\Theta(nk)$ time. For example, the complexity of \cref{eq:solution} is
 $\Theta(mn)$ since $f(m, n)$ can be computed by a dynamic programming algorithm
@@
 \textsc{Crane} can also solve all but one of the instances that
-\textsc{ForcLift} fails on in at most cubic time. See supplementary material for
+\textsc{ForcLift} fails on in at most cubic time. See \cref{sec:solutions} for
 the exact solutions produced by \textsc{Crane}.
@@
   \includegraphics{plot}
-  \caption{The runtime of \textsc{FastWFOMC} when counting permutations,
-    together with a quartic regression model fitted on all of the data and a
-    linear model fitted on the first half of the data
+  \caption{The runtime of \textsc{FastWFOMC} when counting permutations
+    (indicated by points), together with a quartic regression model fitted on
+    all of the data and a linear model fitted on the first half of the data
     points}\label{fig:fastwfomc}
@@
 
-\section{Conclusion and Future Work}\label{sec:conclusion}
+\section{Discussion}\label{sec:conclusion}
 \setlength{\multlinegap}{0pt}
@@
 \textsc{ForcLift}~\cite{DBLP:conf/ijcai/BroeckTMDR11} that benefits from a more
-general version of domain recursion and support for graphs with cycles. Our
-results in \cref{sec:results} reveal a range of counting problems that became
-newly feasible as a result of these enhancements, including instances outside of
-currently-known domain-liftable fragments such as \Ctwo{}. (Although we focused
-on unweighted counting, \textsc{ForcLift}'s support for weights trivially
-transfers to \textsc{Crane} too.) The common thread across these newly liftable
-problems is a version of partial injectivity. Thus, we formulate the following
-conjecture.
-\begin{conjecture}
+general version of domain recursion and support for graphs with cycles. In
+\cref{sec:results}, we listed a range of counting problems that became newly
+feasible as a result, including instances outside of currently-known
+domain-liftable fragments such as \Ctwo{}. (Although we focused on unweighted
+counting, \textsc{ForcLift}'s support for weights trivially transfers to
+\textsc{Crane} too.) The common thread across these newly liftable problems is a
+version of partial injectivity. Thus, we formulate the following conjecture for
+a class of formulas with an injectivity-like constraint on at most two
+parameters of a predicate $\predicate$.
+
+\begin{conjecture}\label{conj}
   Let \IFO{} be the class of formulas in first-order logic that contain clauses
@@
 \end{conjecture}
-Since most of the instances in \cref{sec:results} are in \Ctwo{}, we can also
-conjecture that \Ctwo{} is liftable by \textsc{Crane}.
+
+Note that the unsolved instance in \cref{tbl:results} does not invalidate
+\cref{conj} for two reasons. First, in our experiments, the depth of the search
+procedure is limited, so there is a possibility that increasing the depth would
+make the algorithm succeed. Second, the conjecture assumes distinct domains,
+while the unsolved instance pertains to endofunctions.
+
+% In general, our results demonstrate that Crane
+% performs better when all domains are distinct. A solution for distinct domains
+% can always be applied to the case when some domains are equal.
+
+% ===========================================
+
+% Since most of the instances in \cref{sec:results} are in \Ctwo{}, we can also
+% conjecture that \Ctwo{} is liftable by \textsc{Crane}.
+
+% Every sentence in C2 can be rewritten to avoid counting quantifiers by
+% introducing more variables. For example, to claim that there are exactly two
+% Xs that satisfy p(X), one would introduce two existentially-quantified
+% variables X_1 and X_2 such that X_1 != X_2, p(X_1), and p(X_2) and add a
+% constraint that any other variable X_3 such that p(X_3) has to be equal to
+% either X_1 or X_2.
 
@@
 \end{enumerate*}
-In addition to the potential impact on areas of artificial intelligence (AI)
-like statistical relational AI~\cite{DBLP:series/synthesis/2016Raedt},
-\textsc{Crane} could be beneficial to research in combinatorics as
-well~\cite{DBLP:conf/ilp/BarvinekB0ZK21}.
+
+\section*{Acknowledgments}
+
+We thank Anna L.D. Latour and Kuldeep S. Meel for comments on earlier drafts of
+this paper. Most of the work for this paper was done while the first author was
+a PhD student at the University of Edinburgh. The first author was supported by
+the EPSRC Centre for Doctoral Training in Robotics and Autonomous Systems,
+funded by the UK Engineering and Physical Sciences Research Council (grant
+EP/L016834/1). The second author was partly supported by a Royal Society
+University Research Fellowship, UK, and partly supported by a Grant from the
+UKRI Strategic Priorities Fund, UK to the UKRI Research Node on Trustworthy
+Autonomous Systems Governance and Regulation (EP/ V026607/1, 2020–2024). For the
+purpose of open access, the authors have applied a Creative Commons Attribution
+(CC BY) licence to any Author Accepted Manuscript version arising from this
+submission.
+
+\appendix
+\section{Proofs}\label{sec:proofs}
+
+We begin with a few definitions that formalise the notion of a model. For any
+set $S$, let $2^{S}$ denote its power set and
+$S^{\ast} \coloneqq \bigcup_{i=0}^{\infty} S^{i}$ the (infinite) set of
+tuples---of any finite length---of elements of $S$. For example,
+${\{\,a, b\,\}}^{\ast} = \{\, (), (a), (b), (a, a), \dots \,\}$. For any
+$n \in \mathbb{N}_{0}$, let $[n] \coloneqq \{\, 1, \dots, n \,\}$, e.g.,
+$[0] = \emptyset$, and $[2] = \{\, 1, 2 \,\}$. Extending the notation for
+substitution introduced in \cref{sec:recprelims}, for a formula $\phi$, constant
+$c$, and set of variables $V$, let $\phi[c/V]$ denote $\phi$ with all
+occurrences of all variables in $V$ replaced with $c$. Let $\Preds$ be the
+function that maps any clause or formula to the set of predicates used in it.
+With each formula $\phi$, we associate a map
+$\pi_{\phi}\colon \Preds(\phi) \to {\Doms(\phi)}^{\ast}$ s.t., for each
+predicate $\predicate/n \in \Preds(\phi)$, we have that
+$\pi_{\phi}(\predicate) \in {\Doms(\phi)}^{n}$. This map makes explicit the idea
+that each $n$-ary predicate is associated with an $n$-tuple of domains. In the
+case of formula $\phi$ from \cref{example:first},
+$\pi_{\phi} = \{\, \predicate \mapsto (\Gamma, \Delta) \,\}$.
+
+\begin{definition}\label{def:model}
+  Let $\phi$ be a formula and $\sigma$ a domain size function. A \emph{model} of
+  $(\phi, \sigma)$ is a map
+  $\mathfrak{M}\colon \Preds(\phi) \to 2^{\mathbb{N}_{0}^{\ast}}$ s.t.\ the
+  following two conditions are satisfied.
+  \begin{enumerate}
+    \item For all predicates $\predicate/n \in \Preds(\phi)$ with
+          $\pi_{\phi}(\predicate) \coloneqq {(\Delta_{i})}_{i=1}^{n}$ for some
+          domains $\Delta_{i} \in \Doms(\phi)$,
+    \begin{equation}\label{eq:subset}
+      \mathfrak{M}(\predicate) \subseteq \prod_{i=1}^{n}[\sigma(\Delta_{i})].\footnote{For simplicity, \cref{def:model} ignores constants.
+To include constants, one would replace $[\sigma(\Delta_{i})]$ with a set that contains all constants associated with domain $\Delta_{i}$, extended with enough new elements to make its cardinality $\sigma(\Delta_{i})$.}
+    \end{equation}
+    \item $\mathfrak{M} \models \phi$ according to the (non-exhaustive)
+          recursive definition below. Let $\chi$ and $\psi$ be formulas,
+          $\Delta$ a domain, $c \in \Delta$ a constant, $\predicate/n$ a
+          predicate associated with domains $\Delta_{1},\dots,\Delta_{n}$, and
+          $t \in \prod_{i=1}^{n} \Delta_{i}$ a tuple of constants.
+    \begin{itemize}
+      \item $\mathfrak{M} \models \predicate(t)$ if and only if (iff)
+            $t \in \mathfrak{M}(\predicate)$.
+      \item $\mathfrak{M} \models \neg\chi$ iff $\mathfrak{M} \not\models \chi$.
+      \item $\mathfrak{M} \models \chi \land \psi$ iff
+            $\mathfrak{M} \models \chi$ and $\mathfrak{M} \models \psi$.
+      \item $\mathfrak{M} \models \chi \lor \psi$ iff
+            $\mathfrak{M} \models \chi$ or $\mathfrak{M} \models \psi$.
+      \item $\mathfrak{M} \models (\forall X \in \Delta\text{. }\chi)$ iff
+            $\mathfrak{M} \models \chi[x/\{\, X \,\}]$ for all constants
+            $x \in \Delta$.
+      \item $\mathfrak{M} \models (\forall X \in \Delta\text{.
+            } X \ne c \Rightarrow \chi)$ iff
+            $\mathfrak{M} \models \chi[x/\{\, X \,\}]$ for all
+            $x \in \Delta \setminus \{\, c \,\}$.
+      \item $\mathfrak{M} \models (\forall X,Y \in \Delta\text{.
+            } X \ne Y \Rightarrow \chi)$ iff
+            $\mathfrak{M} \models \chi[x/\{\, X \,\}][y/\{\, Y \,\}]$ for all
+            $x,y \in \Delta$ s.t. $x \ne y$.
+    \end{itemize}
+  \end{enumerate}
+\end{definition}
+
+\begin{theorem}[Correctness of $\GDR$]
+  Let $\phi$ be the formula used as input to \cref{alg:domainrecursion},
+  $\Omega \in \mathcal{D}$ the domain selected on \cref{line:condition}, and
+  $\phi'$ the formula constructed by the algorithm for $\Omega$. Suppose that
+  $\Omega \ne \emptyset$. Then $\phi \equiv \phi'$.
+\end{theorem}
+\begin{proof}
+  Let $x$ be the constant introduced on \cref{line:constant} and $c$ a clause of
+  $\phi$ selected on \cref{line:forclause} of the algorithm. We will show that
+  $c$ is equivalent to the conjunction of clauses added to $\phi'$ on
+  \cref{line:conditions,line:generation}.
+
+  If $c$ has no variables with domain $\Omega$,
+  \cref{line:conditions,line:generation} add a copy of $c$ to $\phi'$. If $c$
+  has one variable with domain $\Omega$, say, $X$, then
+  $c \equiv \forall X \in \Omega\text{. } \psi$ for some formula $\psi$ with one
+  free variable $X$. In this case, \cref{line:conditions,line:generation} create
+  two clauses: $\psi[x/\{\, X \,\}]$ and $\forall X \in \Omega\text{.
+  } X \ne x \Rightarrow \psi$. It is easy to see that their conjunction is
+  equivalent to $c$ provided that $\Omega \ne \emptyset$ and so $x$ is a
+  well-defined constant.
+
+  Let $V$ be the set of variables introduced on \cref{line:V}. It remains to
+  prove that repeating the transformation
+  \[
+    \forall X \in \Omega\text{. } \psi \mapsto \{\, \psi[x/\{\, X \,\}], \forall X \in \Omega\text{. } X \ne x \Rightarrow \psi \,\}
+  \]
+  for all variables $X \in V$ produces the same clauses as
+  \cref{line:conditions,line:generation} (except for some tautologies that the
+  latter method skips). Note that the order in which these operations are
+  applied is immaterial. In other words, if we add inequality constraints for
+  variables ${\{\, X_{i} \,\}}_{i=1}^{n}$, and apply substitution for variables
+  $V \setminus {\{\, X_{i} \,\}}_{i=1}^{n}$, then---regardless of the order of
+  operations---we get
+  \[
+    \forall X_{1}, \dots, X_{n} \in \Omega\text{.} \bigwedge_{i=1}^{n} X_{i} \ne x \Rightarrow \psi\left[x / \left(V \setminus {\{\, X_{i} \,\}}_{i=1}^{n}\right)\right].
+  \]
+  This formula is equivalent to the clause generated on \cref{line:generation}
+  with $W = V \setminus {\{\, X_{i} \,\}}_{i=1}^{n}$. Thus, for every clause $c$
+  of $\phi$, the new formula $\phi'$ gets a set of clauses whose conjunction is
+  equivalent to $c$. Hence, the two formulas are equivalent.
+\end{proof}
+
+\begin{theorem}[Correctness of $\CR$]
+  Let $\phi$ be the input formula of \cref{alg:constraintremoval}, $(\Omega, x)$
+  a replaceable pair, and $\phi'$ the output formula for when $(\Omega, x)$ is
+  selected on \cref{line:crconditions}. Then $\phi \equiv \phi'$, where the
+  domain $\Omega'$ introduced on \cref{line:newdomain} is interpreted as
+  $\Omega \setminus \{\, x \,\}$.
+\end{theorem}
+\begin{proof}
+  Since there is a natural bijection between the clauses of $\phi$ and $\phi'$,
+  we shall argue about the equivalence of each pair of clauses. Let $c$ be an
+  arbitrary clause of $\phi$ and $c'$ its corresponding clause of $\phi'$.
+
+  If $c$ has no variables with domain $\Omega$, then it cannot have any
+  constraints involving $x$, so $c' = c$. Otherwise, for notational simplicity,
+  let us assume that $X$ is the only variable in $c$ with domain $\Omega$ (the
+  proof for an arbitrary number of variables is virtually the same). By
+  \cref{def:replaceable}, we can rewrite $c$ as $\forall X \in \Omega\text{.
+  } X \ne x \Rightarrow \psi$, where $\psi$ is a formula with $X$ as the only free
+  variable and with no mention of either $x$ or $\Omega$. Then
+  $c' \equiv \forall X \in \Omega'\text{. } \psi$. Since
+  $\Omega' \coloneqq \Omega \setminus \{\, x \,\}$, we have that $c \equiv c'$.
+  Since $c$ was an arbitrary clause of $\phi$, this completes the proof that
+  $\phi \equiv \phi'$.
+\end{proof}
+
+\begin{theorem}[Correctness of $\Reff$]
+  Let $\phi$ be the formula used as input to \cref{alg:trycache}. Let $\psi$ be
+  any formula selected on \cref{line:selectformula} of the algorithm s.t.\
+  $\rho \ne \nulll$ on \cref{line:rho}. Let $\sigma$ be a domain size function.
+  Then the set of models of $(\psi, \sigma \circ \rho)$ is equal to the set of
+  models of $(\phi, \sigma)$.
+\end{theorem}
+\begin{proof}
+  We first show that the right-hand side of \cref{eq:subset} is the same for
+  models of both $(\phi, \sigma)$ and $(\psi, \sigma \circ \rho)$.
+  \Cref{alg:trycache} ensures that $\psi \equiv \phi$ up to domains. In
+  particular, this means that $\Preds(\psi) = \Preds(\phi)$. The square in
+  \begin{equation}\label[diagram]{diagram:ref}
+    \begin{tikzcd}
+      \Preds(\psi) \ar[equal]{r} \ar[d, swap, "\pi_{\psi}"] & \Preds(\phi) \ar[d, "\pi_{\phi}"] \\
+      {\Doms(\psi)}^{\ast} \ar[r, "\rho"] & {\Doms(\phi)}^{\ast} \ar[r, "\sigma"] & \mathbb{N}_{0}^{\ast}
+    \end{tikzcd}
+  \end{equation}
+  commutes by \cref{def:formula} and the definition of $\rho$. In other words,
+  for any predicate $\predicate/n \in \Preds(\psi) = \Preds(\phi)$, function
+  $\rho$ translates the domains associated with $\predicate$ in $\psi$ to the
+  domains associated with $\predicate$ in $\phi$. Let
+  $\pi_{\phi}(\predicate) = {(\Delta_{i})}_{i=1}^{n}$ and
+  $\pi_{\psi}(\predicate) = {(\Gamma_{i})}_{i=1}^{n}$ for some domains
+  $\Delta_{i} \in \Doms(\phi)$ and $\Gamma_{i} \in \Doms(\psi)$. Since
+  $\rho(\Gamma_{i}) = \Delta_{i}$ for all $i = 1, \dots, n$ by the commutativity
+  in \cref{diagram:ref}, we get that
+  \begin{equation}\label{eq:equality}
+    \prod_{i=1}^{n}[\sigma(\Delta_{i})] = \prod_{i=1}^{n}[\sigma \circ \rho(\Gamma_{i})]
+  \end{equation}
+  as required. Obviously, any subset of the left-hand side of \cref{eq:equality}
+  (e.g., $\mathfrak{M}(\predicate)$, where $\mathfrak{M}$ is a model of
+  $(\phi, \sigma)$) is a subset of the right-hand side and vice versa. Since
+  $\phi$ and $\psi$ semantically only differ in what domains they refer to,
+  every model of $\phi$ satisfies $\psi$ and vice versa, completing the proof.
+\end{proof}
+
+\section{Solutions Found by \textsc{Crane}}\label{sec:solutions}
+
+Here we list the exact function definitions produced by \textsc{Crane} for all
+of the problem instances in Section~6, both before and after algebraic
+simplification (excluding multiplications by one). The correctness of all of
+them has been checked by identifying suitable base cases and verifying the
+numerical answers across a range of domain sizes.
+
+\begin{enumerate}
+  \item A $\Theta(m)$ solution for counting $\Gamma \to \Gamma$ functions:
+        \[
+        f(m) = {\left(-1 + \sum_{l=0}^{m} \binom{m}{l} [l < 2]\right)}^{m} = m^{m}.
+        \]
+  \item A $\Theta(m^3 + n^3)$ solution for counting $\Gamma \to \Delta$
+        surjections:
+        \begin{align*}
+          f(m, n) ={}& \sum_{l=0}^{m} \binom{m}{l}{(-1)}^{m-l} \sum_{k=0}^{n} \binom{n}{k} {(-1)}^{n-k}\\
+                     &{\left( \sum_{j=0}^{k} \binom{k}{j} [j < 2] \right)}^{l} \\
+          ={}& \sum_{l=0}^{m} \binom{m}{l}{(-1)}^{m-l}\\
+                     &\sum_{k=0}^{n} \binom{n}{k} {(-1)}^{n-k} {(k+1)}^{l}.
+        \end{align*}
+  \item A $\Theta(m^{3})$ solution for counting $\Gamma \to \Gamma$ surjections:
+        \begin{align*}
+          f(m) ={}& \sum_{l=0}^{m} \binom{m}{l}{(-1)}^{m-l} \sum_{k=0}^{m} \binom{m}{k} {(-1)}^{m-k}\\
+                  &{\left( \sum_{j=0}^{k} \binom{k}{j} [j < 2] \right)}^{l} \\
+          ={}& \sum_{l=0}^{m} \binom{m}{l}{(-1)}^{m-l}\\
+                  &\sum_{k=0}^{m} \binom{m}{k} {(-1)}^{m-k} {(k+1)}^{l}.
+        \end{align*}
+  \item A $\Theta(mn)$ solution for counting $\Gamma \to \Delta$ injections and
+        partial injections (with different base cases):
+        \begin{align*}
+          f(m, n) ={}& \sum_{l=0}^m \binom{m}{l} [l<2] f(m-l, n-1)\\
+          ={}& f(m, n-1) + mf(m-1, n-1).
+        \end{align*}
+  \item A $\Theta(m^{3})$ solution for counting $\Gamma \to \Gamma$ injections:
+        \begin{align*}
+          f(m) ={}& \sum_{l=0}^{m} \binom{m}{l} {(-1)}^{m-l} g(m, l); \\
+          g(m, l) ={}& \sum_{k=0}^{l} \binom{l}{k} [k < 2] g(m - 1, l - k)\\
+          ={}& g(m - 1, l) + lg(m - 1, l - 1).
+        \end{align*}
+  \item A $\Theta(m)$ solution for counting $\Gamma \to \Delta$ bijections:
+        \[
+        f(m, n) = mf(m-1, n-1).
+        \]
+  \item A $\Theta(l+mn)$ solution for counting $|\Lambda|$ partial injections
+        $\Gamma \to \Delta$:
+        \begin{align*}
+          f(l, m, n) ={}& {g(m, n)}^{l}\\
+          g(m, n) ={}& \sum_{k=0}^{n}\binom{n}{k} [k < 2] g(m-1, n-k)\\
+          ={}& g(m-1, n) + ng(m-1, n-1).
+        \end{align*}
+\end{enumerate}
 

### 2023-06-07 propositional/d4/core/Main.cc

@@ -1,305 +1,0 @@
-/*
-* d4
-* Copyright (C) 2020  Univ. Artois & CNRS
-* 
-* This program is free software: you can redistribute it and/or modify
-* it under the terms of the GNU General Public License as published by
-* the Free Software Foundation, either version 3 of the License, or
-* (at your option) any later version.
-* 
-* This program is distributed in the hope that it will be useful,
-* but WITHOUT ANY WARRANTY; without even the implied warranty of
-* MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
-* GNU General Public License for more details.
-* 
-* You should have received a copy of the GNU General Public License
-* along with this program.  If not, see <http://www.gnu.org/licenses/>.
-*/
-#include <iostream>
-#include <cassert>
-
-
-#include "../manager/OptionManager.hh"
-#include "../modelCounters/ModelCounter.hh"
-
-#include "../compilers/dDnnfCompiler.hh"
-#include "../preproc/Preproc.hh"
-
-#include "../utils/System.hh"
-#include "../utils/Options.hh"
-#include "../utils/Solver.hh"
-
-#include "../manager/ParserProblem.hh"
-
-#include <boost/multiprecision/gmp.hpp>
-#include <boost/archive/binary_oarchive.hpp>
-#include <boost/archive/binary_iarchive.hpp>
-
-#include <sstream>
-#include <iostream>
-#include <iomanip>
-
-#include <boost/multiprecision/cpp_int.hpp>
-#include <boost/archive/binary_oarchive.hpp>
-#include <boost/archive/binary_iarchive.hpp>
-#include <boost/serialization/map.hpp>
-#include <boost/multiprecision/cpp_bin_float.hpp>
-#include <boost/math/special_functions/gamma.hpp>
-#include <boost/multiprecision/cpp_bin_float.hpp>
-#include <iostream>
-#include <iomanip>
-#include <vector>
-#include <iterator>
-
-using namespace boost::multiprecision;
-using namespace std;
-
-
-#include "../manager/dynamicOccurrenceManager.hh"
-#include "../manager/BucketManager.hh"
-#include "../manager/CacheCNFManager.hh"
-
-
-/**
-   Call a model counter.
-
-   @param[in] clauses, the input CNF formula (that means a set of clauses)
-   @param[in] weightLit, the weight of the literals
-   @param[in] optList, the list of options
[…]

### 2023-06-07 propositional/d4/heuristics/MinCutPartitioner.cc

@@ -1,110 +1,0 @@
-/*
-* d4
-* Copyright (C) 2020  Univ. Artois & CNRS
-* 
-* This program is free software: you can redistribute it and/or modify
-* it under the terms of the GNU General Public License as published by
-* the Free Software Foundation, either version 3 of the License, or
-* (at your option) any later version.
-* 
-* This program is distributed in the hope that it will be useful,
-* but WITHOUT ANY WARRANTY; without even the implied warranty of
-* MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
-* GNU General Public License for more details.
-* 
-* You should have received a copy of the GNU General Public License
-* along with this program.  If not, see <http://www.gnu.org/licenses/>.
-*/
-#include <iostream>
-#include <tgmath.h>
-
-#include <boost/graph/adjacency_list.hpp>
-#include <boost/graph/graph_traits.hpp>
-#include <boost/graph/one_bit_color_map.hpp>
-#include <boost/graph/stoer_wagner_min_cut.hpp>
-#include <boost/property_map/property_map.hpp>
-#include <boost/typeof/typeof.hpp>
-
-#include "../interfaces/OccurrenceManagerInterface.hh"
-#include "../mtl/Vec.hh"
-#include "../utils/SolverTypes.hh"
-
-#include "../interfaces/PartitionerInterface.hh"
-#include "../heuristics/MinCutPartitioner.hh"
-
-using namespace std;
-
-/**
-   This function compute a min cut of the graph.
-   
-*/
-void MinCutPartition::minCut(vec<Var> &component)
-{
-  for(int i = 0 ; i<component.size() ; i++) inCurrentComponent[component[i]] = true;
-
-  vec<int> idxClauses;
-  for(int i = 0 ; i<om->getNbClause() ; i++)
-    {
-      vec<Lit> &c = om->getClause(i);
-      if(om->isSatisfiedClause(i)) continue;
-      if(!inCurrentComponent[var(c[0])]) continue;
-      idxClauses.push(i);
-    }
-
-  if(idxClauses.size() <= 1) return;
-
-  vec<edge_t> vecEdges;
-  for(int i = 0 ; i<idxClauses.size() ; i++)
-    {
-      vec<Lit> &c = om->getClause(idxClauses[i]);
-      for(int j = 0 ; j<c.size() ; j++) markedVar[var(c[j])] = true;
-
[…]

### 2023-06-07 propositional/d4/manager/greedyOccurrenceManager.cc

@@ -1,102 +1,0 @@
-/*
-* d4
-* Copyright (C) 2020  Univ. Artois & CNRS
-* 
-* This program is free software: you can redistribute it and/or modify
-* it under the terms of the GNU General Public License as published by
-* the Free Software Foundation, either version 3 of the License, or
-* (at your option) any later version.
-* 
-* This program is distributed in the hope that it will be useful,
-* but WITHOUT ANY WARRANTY; without even the implied warranty of
-* MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
-* GNU General Public License for more details.
-* 
-* You should have received a copy of the GNU General Public License
-* along with this program.  If not, see <http://www.gnu.org/licenses/>.
-*/
-#include "../manager/greedyOccurrenceManager.hh"
-
-/**
-   Constructor.
-   
-   @param[in] clauses, the set of clauses.
-   @param[in] nbVar, the number of variable present in the problem.
- */
-GreedyOccurrenceManager::GreedyOccurrenceManager(vec<vec<Lit> > &_clauses, int _nbVar) : CnfOccurrenceManager(_clauses, _nbVar)
-{
-  for(int i = 0 ; i<(nbVar<<1) ; i++) initOccList.push();
-  
-  counterStampViewClause = 0;
-  for(int i = 0 ; i<clauses.size() ; i++)
-    {
-      for(int j = 0 ; j<clauses[i].size() ; j++)
-        initOccList[toInt(clauses[i][j])].push(i);
-
-      stampViewClause.push(0);
-    }
-}// constructor
-
-
-/**
-   Visit the set of not already visided clauses where the literal l
-   occur and initialize the data structures nbSat, nbUnsat and the
-   occList w.r.t. the currentValue table.
-
-   @param[in] l, a literal
- */
-void GreedyOccurrenceManager::initializeFromLiteral(Lit l)
-{
-  vec<int> &occ = initOccList[toInt(l)];
-
-  for(int j = 0 ; j<occ.size() ; j++)
-    if(stampViewClause[occ[j]] != counterStampViewClause)
-      {
-        stampViewClause[occ[j]] = counterStampViewClause;
-        nbUnsat[occ[j]] = 0;
-
-        assert(occ[j] < clauses.size());        
-        vec<Lit> &cl = clauses[occ[j]];
-        bool isSAT = false;
[…]

### 2023-06-07 propositional/d4/utils/InterpretationRefiner.cc

@@ -1,345 +1,0 @@
-/*
-* d4
-* Copyright (C) 2020  Univ. Artois & CNRS
-* 
-* This program is free software: you can redistribute it and/or modify
-* it under the terms of the GNU General Public License as published by
-* the Free Software Foundation, either version 3 of the License, or
-* (at your option) any later version.
-* 
-* This program is distributed in the hope that it will be useful,
-* but WITHOUT ANY WARRANTY; without even the implied warranty of
-* MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
-* GNU General Public License for more details.
-* 
-* You should have received a copy of the GNU General Public License
-* along with this program.  If not, see <http://www.gnu.org/licenses/>.
-*/
-#include <iostream>
-
-#include "InterpretationRefiner.hh"
-
-using namespace std;
-
-/**
-   Constructor that take in input a CNF formula as well as a boolean
-   vector that identifies the protected variables.
-
-   @param[in] formula, the input CNF formula
-   @param[in] pvar, the boolean vector used to identify the protected variables
- */
-InterpretationRefiner::InterpretationRefiner(vec<vec<Lit> > &formula, vec<bool> &pvar)
-{
-  for(int i = 0 ; i<formula.size() ; i++) addClause(formula[i]);
-  pvar.copyTo(isProtected);
-}// constructor
-
-/**
-   Constructor that take in input a boolean
-   vector that identifies the protected variables.
-
-   @param[in] pvar, the boolean vector used to identify the protected variables
- */
-InterpretationRefiner::InterpretationRefiner(vec<bool> &pvar)
-{
-  pvar.copyTo(isProtected);
-}// constructor
-
-/**
-   Add a clause in the CNF formula attribute.
-
-   @param[in] cl, the clause we want to add
- */
-void InterpretationRefiner::addClause(vec<Lit> &cl)
-{
-  nbTrueLit.push();
-  satisfiedByAssums.push(false);
-
-  for(int i = 0 ; i<cl.size() ; i++)
-    {
-      Lit l = cl[i];
-      while(((var(l) + 1) << 1) > occurrences.size()) occurrences.push();
[…]

### 2023-06-07 propositional/d4/utils/RenamableHorn.cc

@@ -1,332 +1,0 @@
-/*
-* d4
-* Copyright (C) 2020  Univ. Artois & CNRS
-* 
-* This program is free software: you can redistribute it and/or modify
-* it under the terms of the GNU General Public License as published by
-* the Free Software Foundation, either version 3 of the License, or
-* (at your option) any later version.
-* 
-* This program is distributed in the hope that it will be useful,
-* but WITHOUT ANY WARRANTY; without even the implied warranty of
-* MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
-* GNU General Public License for more details.
-* 
-* You should have received a copy of the GNU General Public License
-* along with this program.  If not, see <http://www.gnu.org/licenses/>.
-*/
-#include "RenamableHorn.hh"
-
-
-/**
-   Add a clause in the CNF formula attribute.
-
-   @param[in] cl, the clause we want to add
- */
-void RenamableHorn::addClause(vec<Lit> &cl)
-{
-  cnf.push();
-  countPositive.push(0);
-  whereFalse.push(0);
-  cl.copyTo(cnf.last());
-
-  for(int i = 0 ; i<cl.size() ; i++) occurrences[toInt(cl[i])].push(cnf.size() - 1);
-}// addClause
-
-
-/**
-   Initialize the data structure with the information contained in the
-   given model (that means we initialize the vector nbTrueLit).
-
-   @param[in] assums, the current assumption we work with
-   @param[in] model, the given model
- */
-void RenamableHorn::init(bool initRandom)
-{
-  // generate a random renaming
-  if(!initRandom) heuristicInterpretation(); 
-  else randomInterpretation();
-
-  assert(countPositive.size() == cnf.size());
-  for(int i = 0 ; i<countPositive.size() ; i++) countPositive[i] = 0;
-  for(int i = 0 ; i<makeCount.size() ; i++) makeCount[i] = 0;
-  for(int i = 0 ; i<breakCount.size() ; i++) breakCount[i] = 0;
-  notHornClauses.clear();
-
-  for(int i = 0 ; i<cnf.size() ; i++)
-    {
-      vec<Lit> &cl = cnf[i];
-      
-      for(int j = 0 ; j<cl.size() ; j++)
-        if(isPositive(cl[j])) countPositive[i]++;
-
-      if(countPositive[i] > 1)
-        {
-          notHornClauses.push(i);
[…]

### 2023-06-07 propositional/d4/utils/System.cc

@@ -1,112 +1,0 @@
-/*
-* d4
-* Copyright (C) 2020  Univ. Artois & CNRS
-* 
-* This program is free software: you can redistribute it and/or modify
-* it under the terms of the GNU General Public License as published by
-* the Free Software Foundation, either version 3 of the License, or
-* (at your option) any later version.
-* 
-* This program is distributed in the hope that it will be useful,
-* but WITHOUT ANY WARRANTY; without even the implied warranty of
-* MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
-* GNU General Public License for more details.
-* 
-* You should have received a copy of the GNU General Public License
-* along with this program.  If not, see <http://www.gnu.org/licenses/>.
-*/
-/***************************************************************************************[System.cc]
-Copyright (c) 2003-2006, Niklas Een, Niklas Sorensson
-Copyright (c) 2007-2010, Niklas Sorensson
-
-Permission is hereby granted, free of charge, to any person obtaining a copy of this software and
-associated documentation files (the "Software"), to deal in the Software without restriction,
-including without limitation the rights to use, copy, modify, merge, publish, distribute,
-sublicense, and/or sell copies of the Software, and to permit persons to whom the Software is
-furnished to do so, subject to the following conditions:
-
-The above copyright notice and this permission notice shall be included in all copies or
-substantial portions of the Software.
-
-THE SOFTWARE IS PROVIDED "AS IS", WITHOUT WARRANTY OF ANY KIND, EXPRESS OR IMPLIED, INCLUDING BUT
-NOT LIMITED TO THE WARRANTIES OF MERCHANTABILITY, FITNESS FOR A PARTICULAR PURPOSE AND
-NONINFRINGEMENT. IN NO EVENT SHALL THE AUTHORS OR COPYRIGHT HOLDERS BE LIABLE FOR ANY CLAIM,
-DAMAGES OR OTHER LIABILITY, WHETHER IN AN ACTION OF CONTRACT, TORT OR OTHERWISE, ARISING FROM, OUT
-OF OR IN CONNECTION WITH THE SOFTWARE OR THE USE OR OTHER DEALINGS IN THE SOFTWARE.
-**************************************************************************************************/
-
-#include "System.hh"
-
-#if defined(__linux__)
-
[…]

### 2023-06-07 solvers/Forclift/src/main/scala/edu/ucla/cs/starai/forclift/examples/MljSmokersExperiment.scala

@@ -1,130 +1,0 @@
-/*
- * Copyright 2016 Guy Van den Broeck and Wannes Meert (UCLA and KU Leuven)
- *
- * Licensed under the Apache License, Version 2.0 (the "License");
- * you may not use this file except in compliance with the License.
- * You may obtain a copy of the License at
- *
- *     http://www.apache.org/licenses/LICENSE-2.0
- *
- * Unless required by applicable law or agreed to in writing, software
- * distributed under the License is distributed on an "AS IS" BASIS,
- * WITHOUT WARRANTIES OR CONDITIONS OF ANY KIND, either express or implied.
- * See the License for the specific language governing permissions and
- * limitations under the License.
- */
-
-package edu.ucla.cs.starai.forclift.examples
-
-import java.io.File
-import util.Random
-import java.io.PrintWriter
-import edu.ucla.cs.starai.forclift._
-import edu.ucla.cs.starai.forclift.learning.LiftedLearning
-import edu.ucla.cs.starai.forclift.languages.mln.MLNParser
-import java.io.OutputStream
-import java.io.PrintStream
-
-object MljSmokersExperiment extends App {
-
-  val dir = new File("experiments/mlj-smokers")
-  dir.mkdirs()
-
-  val data = new PrintWriter(new File(dir, "timings.dat"))
-  data.printf("%10s %10s %10s %10s %10s %10s\n", "DomSize", "GradCalls", 
-      "CountTime", "CompTime", "InfTime", "LearnTime")
-
-  
-  for (size <- List(30000,2,2,2,2, 3, 4, 10, 20, 50, 100, 500, 1000, 5000, 10000, 15000, 20000, 25000, 30000)) {
-    println(s"Domain size is $size")
-
-    val structStr =
-s"""
-person = $size {}
-Smokes(person)
-Friends(person,person)
-
-!Friends(x,y) v !Smokes(x) v Smokes(y)
-"""
-  
-    val structFile = new PrintWriter(new File(dir, s"struct-$size.mln"))
-    structFile.println(structStr)
-    structFile.close
-
-    val r = new Random
-    val trainingDBStr = {
-      val people = (1 to size)
-      // generate smokers
-      val smokers = r.shuffle(people).take((size*0.4).toInt)
-      val nonsmokers = people diff smokers
-      val smokesDb = smokers.map(s => {s"Smokes(P$s)"}).toSet
-      // generate friends
[…]

### 2023-06-07 solvers/L2C/L2C.rb

@@ -1,87 +1,0 @@
-#Copyright (C) 2016  Seyed Mehran Kazemi, Licensed under the GPL V3; see: <https://www.gnu.org/licenses/gpl-3.0.en.html>
-
-require './classes/parser'
-require './classes/domain'
-require './classes/Helper'
-require './classes/constant'
-require './classes/logvar'
-require './classes/prv'
-require './classes/literal'
-require './classes/clause'
-require './classes/cache'
-require './classes/wfomc'
-require './classes/cnf'
-require './classes/constraint'
-require './classes/cpphandler'
-require './classes/branchingorder'
-
-#parameters
-order_heuristic = "MNL"
-num_sls = 25
-readable = false
-
-#arguments
-arguments = Hash.new
-(0..ARGV.size / 2).each do |i|
-	arguments[ARGV[2 * i]] = ARGV[2 * i + 1]
-end
-
-if arguments["-f"].nil?
-	Helper.error("Please specify the input file")
-elsif !File.file?(arguments["-f"])
-	Helper.error("No such file found!")
-end
-if !arguments["-h"].nil?
-	if arguments["-h"] != "MTS" or arguments["-h"] != "MNL"
-		Helper.error("Invalid elimination ordering heuristic")
-	else
-		order_heuristic = arguments["-h"]
-	end
-end
-if !arguments["-k"].nil?
-	if !Helper.all_digit(arguments["-k"])
-		Helper.error("Invalid number of stochastic local search iterations for elimination order optimization.")
-	else
-		num_sls = arguments["-k"].to_i
-	end
-end
-if !arguments["-r"].nil?
-	if arguments["-r"] != "true" and arguments["-r"] != "false"
-		Helper.error("The readability command specified using '-r' must be either true or false.")
-	elsif arguments["-r"] == "true"
-		readable = true
-	end
-end
-
-content = File.read(arguments["-f"])
-parser = Parser.new(content)
-parser.produce_cnf
-cnf = CNF.new(parser.formulae)
-cnf.preemptive_shatter
-puts "Initial theory after shattering:"
-puts cnf.my2string + "\n"
-puts "Finding the branching order"
-t_start = Time.now
-bo = BranchingOrder.new(cnf)
-order = bo.min_nested_loop_order(num_sls)
-puts "The branching Order is: " + order.join(", ")
-puts "Finding the branching order took " + (Time.now - t_start).to_s + " seconds.\n\n"
[…]

### 2023-06-07 solvers/L2C/classes/cache.rb

@@ -1,80 +1,0 @@
-#Copyright (C) 2016  Seyed Mehran Kazemi, Licensed under the GPL V3; see: <https://www.gnu.org/licenses/gpl-3.0.en.html>
-
-class Cache
-	attr_accessor :memory, :counter, :queues
-
-	def initialize()
-		@memory = Hash.new
-		@counter = 0
-	end
-
-	def queues_declaration
-		return "" if queues.empty?
-		str = "queue<double> "
-		str += queues.join(",") + ";\n"
-		return str
-	end
-
-	def get(cnf)
-		identifier = cnf.unique_identifier
-		return nil if @memory[identifier].nil?
-		@memory[identifier][0] += 1 #counts the number of times it has ben used
-		return @memory[identifier][1][1..-2] #[1..-2] is because there is an extra " at the beginning and the end of the string
-	end
-
-	def add(cnf, value)
-		return "" if cnf.has_no_lvs
-		identifier = cnf.unique_identifier
-		@counter += 1
-		@memory[identifier] = [0, "\"#{@counter}:#{str_inspect(identifier)}\""] #0 indicates it has not been used yet.
-		return "q#{@counter}.push(#{value});\n"
-	end
-
-	def str_inspect(str) #gets a cnf identifier and removes the parts that are not necessary for the c++ program
-		new_str = ""
-		i_i_list = Array.new #we keep the list of i_..._i variables, because we only need to know their value once.
-		while str.include? "_i"
-			index1 = str.index("i_")
-			index2 = str.index("_i") + 2
-			new_i_i_variable = str[index1..index2-1]
-			if not i_i_list.include? new_i_i_variable #otherwise, we have already included the value of this i_..._i variable
-				new_str += "_" if i_i_list.size > 0
-				new_str += "\"+to_string(" + new_i_i_variable + ")+\""
-				i_i_list << new_i_i_variable
-			end
-			str = str[index2, str.size]
-		end
-		return new_str
-	end
-
-	def remove_inserts(c_prog)
-		@queues = Array.new
-		new_prog = ""
-		q_usage = Hash.new
-		c_prog.each_line do |line|
-			if line.include? ".push("
-				q_number = line[line.index("q")..line.index(".")-1]
-				used_count = c_prog.scan(/#{q_number}.front()/).count
-				new_push = ""
-				used_count.times.each do |i|
[…]

### 2023-06-07 solvers/L2C/classes/clause.rb

@@ -1,115 +1,0 @@
-#Copyright (C) 2016  Seyed Mehran Kazemi, Licensed under the GPL V3; see: <https://www.gnu.org/licenses/gpl-3.0.en.html>
-
-class Clause
-	attr_accessor :literals, :constraints, :is_true
-
-	def initialize(literals, constraints)
-		@literals = literals.map{|lit| lit.duplicate}
-		@is_true = false
-		@constraints = constraints
-	end
-
-	def is_false
-		not @is_true and @literals.size == 0
-	end
-
-	def num_distinct_lvs
-		return @literals.map{|literal| literal.prv.logvars.map{|lv| lv.name}}.flatten.uniq.size
-	end
-
-	def can_be_evaluated?
-		@is_true or @literals.size == 0
-	end
-
-	def has_lv_with_type? (type)
-		@literals.each {|literal| return true if literal.prv.has_lv_with_type?(type)}
-		return false
-	end
-
-	def has_constraint_with_name? (term1, term2, constraint)
-		@constraints.each {|clause_constraint| return true if clause_constraint.match_name?(term1, term2, constraint)}
-		return false
-	end
-
-	def has_constraint_with_type? (term1, term2, constraint)
-		@constraints.each {|clause_constraint| return true if clause_constraint.match_type?(term1, term2, constraint)}
-		return false
-	end
-
-	def has_lv_neq_lv_constraint_with_type? (type)
-		@constraints.each {|constraint| return true if constraint.match_type2?(type, "!=") }
-		return false
-	end
-
-	def has_contradictory_constraint?
-		@constraints.each {|constraint| return true if constraint.contradicts?}
-		return false
-	end
-
-	def add_constraint(term1, term2, constraint)
-		@constraints << Constraint.new(term1, term2, constraint)
-	end
-
-	def decrement_lv_size(lv)
-		@literals.each {|literal| literal.prv.logvars.each_with_index {|prv_lv, i| literal.prv.logvars[i].decrement_psize if prv_lv.is_same_as(lv)}}
-	end
-
-	def get_all_lvs
-		@literals.map{|literal| literal.prv.logvars}.flatten
-	end
-
-	def get_all_distinct_lvs #distinct in terms of names (not types)
-		lv_hash = Hash.new
-		lvs = Array.new
-		get_all_lvs.each do |lv|
-			lvs << lv if lv_hash[lv.name].nil?
-			lv_hash[lv.name] = "true"
-		end
[…]

### 2023-06-07 solvers/L2C/classes/constant.rb

@@ -1,25 +1,0 @@
-#Copyright (C) 2016  Seyed Mehran Kazemi, Licensed under the GPL V3; see: <https://www.gnu.org/licenses/gpl-3.0.en.html>
-
-class Constant
-	attr_accessor :name
-
-	def initialize(name)
-		@name = name
-	end
-
-	def psize
-		return "1"
-	end
-
-	def is_same_as(constant)
-		@name == constant.name ? true : false
-	end
-
-	def my2string
-		return name
-	end
-
-	def duplicate
-		Marshal::load(Marshal.dump(self))
-	end
-end

### 2023-06-07 solvers/L2C/classes/literal.rb

@@ -1,27 +1,0 @@
-#Copyright (C) 2016  Seyed Mehran Kazemi, Licensed under the GPL V3; see: <https://www.gnu.org/licenses/gpl-3.0.en.html>
-
-class Literal
-	attr_accessor :prv, :value
-
-	def initialize(prv, value)
-		@prv = prv.duplicate
-		@value = value
-	end
-
-	def name
-		@prv.full_name
-	end
-
-	def my2string
-		value == "true" ? @prv.my2string : "~" << @prv.my2string
-	end
-
-	def flip_value
-		return Literal.new(@prv.duplicate, "false") if @value == "true"
-		return Literal.new(@prv.duplicate, "true")
-	end
-
-	def duplicate
-		Marshal::load(Marshal.dump(self))
-	end
-end

### 2023-06-07 solvers/L2C/classes/prv.rb

@@ -1,156 +1,0 @@
-#Copyright (C) 2016  Seyed Mehran Kazemi, Licensed under the GPL V3; see: <https://www.gnu.org/licenses/gpl-3.0.en.html>
-
-class PRV
-	attr_accessor :core_name, :full_name, :terms, :name_addendum
-
-	def initialize(name, terms)
-		@core_name = name.dup
-		@full_name = name.dup
-		@terms = terms.map{|term| term.duplicate}
-		@name_addendum = Hash.new
-	end
-
-	def confirm_name_addendum
-		@name_addendum.keys.sort.each {|key| @full_name << @name_addendum[key]}
-		@name_addendum = Hash.new
-	end
-
-	def num_terms
-		return @terms.size
-	end
-
-	def lit(value)
-		return Literal.new(self, value)
-	end
-
-	def replace_parameters(param, number)
-		@terms.each {|term| term.replace_parameters(param, number) if term.class == LogVar}
-	end
-
-	def num_lvs #returns the number of lvs: F(x,x) has two lvs
-		return @terms.select{|term| term.class == LogVar}.size
-	end
-
-	def num_distinct_lvs #returns number of lvs with different names: F(x,x) has one distinct lv
-		return logvars.map{|lv| lv.name}.uniq.size
-	end
-
-	def logvars
-		return @terms.select{|term| term.class == LogVar}
-	end
-
-	def first_lv
-		return logvars.first
-	end
-
-	def first_lv_with_type(type)
-		@terms.each {|term| return term if term.class == LogVar and term.type == type}
-		return nil
-	end
-
-	def has_lv_with_type?(type)
-		@terms.each {|term| return true if term.class == LogVar and term.type == type}
-		return false
-	end
-
-	def index_lv_with_name(name)
-		@terms.each_with_index {|term, i| return i if term.class == LogVar and term.name == name}
-		return -1
-	end
-
-	def num_psize
-		return @terms.inject(1) {|result, term| result * term.psize.to_i}
-	end
-
-	def psize(constraints)
-		return "1" if logvars.size == 0
-		all_num = true
-		@terms.each {|term| all_num = false if term.psize.to_i.to_s != term.psize}
-		if(num_distinct_lvs < 2)
-			return eval(@terms.inject(""){|result, term| result += term.psize + "*"}.chop).to_s if all_num
[…]

### 2023-06-07 solvers/alchemy/src/infer/bp.h

@@ -1,1081 +1,0 @@
-/*
- * All of the documentation and software included in the
- * Alchemy Software is copyrighted by Stanley Kok, Parag
- * Singla, Matthew Richardson, Pedro Domingos, Marc
- * Sumner, Hoifung Poon, Daniel Lowd, and Jue Wang.
- * 
- * Copyright [2004-09] Stanley Kok, Parag Singla, Matthew
- * Richardson, Pedro Domingos, Marc Sumner, Hoifung
- * Poon, Daniel Lowd, and Jue Wang. All rights reserved.
- * 
- * Contact: Pedro Domingos, University of Washington
- * (pedrod@cs.washington.edu).
- * 
- * Redistribution and use in source and binary forms, with
- * or without modification, are permitted provided that
- * the following conditions are met:
- * 
- * 1. Redistributions of source code must retain the above
- * copyright notice, this list of conditions and the
- * following disclaimer.
- * 
- * 2. Redistributions in binary form must reproduce the
- * above copyright notice, this list of conditions and the
- * following disclaimer in the documentation and/or other
- * materials provided with the distribution.
- * 
- * 3. All advertising materials mentioning features or use
- * of this software must display the following
- * acknowledgment: "This product includes software
- * developed by Stanley Kok, Parag Singla, Matthew
- * Richardson, Pedro Domingos, Marc Sumner, Hoifung
- * Poon, Daniel Lowd, and Jue Wang in the Department of
- * Computer Science and Engineering at the University of
- * Washington".
- * 
- * 4. Your publications acknowledge the use or
- * contribution made by the Software to your research
- * using the following citation(s): 
- * Stanley Kok, Parag Singla, Matthew Richardson and
- * Pedro Domingos (2005). "The Alchemy System for
- * Statistical Relational AI", Technical Report,
- * Department of Computer Science and Engineering,
- * University of Washington, Seattle, WA.
- * http://alchemy.cs.washington.edu.
- * 
- * 5. Neither the name of the University of Washington nor
[…]

### 2023-06-07 solvers/alchemy/src/infer/factor.cpp

@@ -1,388 +1,0 @@
-/*
- * All of the documentation and software included in the
- * Alchemy Software is copyrighted by Stanley Kok, Parag
- * Singla, Matthew Richardson, Pedro Domingos, Marc
- * Sumner, Hoifung Poon, Daniel Lowd, and Jue Wang.
- * 
- * Copyright [2004-09] Stanley Kok, Parag Singla, Matthew
- * Richardson, Pedro Domingos, Marc Sumner, Hoifung
- * Poon, Daniel Lowd, and Jue Wang. All rights reserved.
- * 
- * Contact: Pedro Domingos, University of Washington
- * (pedrod@cs.washington.edu).
- * 
- * Redistribution and use in source and binary forms, with
- * or without modification, are permitted provided that
- * the following conditions are met:
- * 
- * 1. Redistributions of source code must retain the above
- * copyright notice, this list of conditions and the
- * following disclaimer.
- * 
- * 2. Redistributions in binary form must reproduce the
- * above copyright notice, this list of conditions and the
- * following disclaimer in the documentation and/or other
- * materials provided with the distribution.
- * 
- * 3. All advertising materials mentioning features or use
- * of this software must display the following
- * acknowledgment: "This product includes software
- * developed by Stanley Kok, Parag Singla, Matthew
- * Richardson, Pedro Domingos, Marc Sumner, Hoifung
- * Poon, Daniel Lowd, and Jue Wang in the Department of
- * Computer Science and Engineering at the University of
- * Washington".
- * 
- * 4. Your publications acknowledge the use or
- * contribution made by the Software to your research
- * using the following citation(s): 
- * Stanley Kok, Parag Singla, Matthew Richardson and
- * Pedro Domingos (2005). "The Alchemy System for
- * Statistical Relational AI", Technical Report,
- * Department of Computer Science and Engineering,
- * University of Washington, Seattle, WA.
- * http://alchemy.cs.washington.edu.
- * 
- * 5. Neither the name of the University of Washington nor
- * the names of its contributors may be used to endorse or
- * promote products derived from this software without
- * specific prior written permission.
- * 
[…]

### 2023-06-07 solvers/alchemy/src/infer/factorgraph.h

@@ -1,2851 +1,0 @@
-/*
- * All of the documentation and software included in the
- * Alchemy Software is copyrighted by Stanley Kok, Parag
- * Singla, Matthew Richardson, Pedro Domingos, Marc
- * Sumner, Hoifung Poon, Daniel Lowd, and Jue Wang.
- * 
- * Copyright [2004-09] Stanley Kok, Parag Singla, Matthew
- * Richardson, Pedro Domingos, Marc Sumner, Hoifung
- * Poon, Daniel Lowd, and Jue Wang. All rights reserved.
- * 
- * Contact: Pedro Domingos, University of Washington
- * (pedrod@cs.washington.edu).
- * 
- * Redistribution and use in source and binary forms, with
- * or without modification, are permitted provided that
- * the following conditions are met:
- * 
- * 1. Redistributions of source code must retain the above
- * copyright notice, this list of conditions and the
- * following disclaimer.
- * 
- * 2. Redistributions in binary form must reproduce the
- * above copyright notice, this list of conditions and the
- * following disclaimer in the documentation and/or other
- * materials provided with the distribution.
- * 
- * 3. All advertising materials mentioning features or use
- * of this software must display the following
- * acknowledgment: "This product includes software
- * developed by Stanley Kok, Parag Singla, Matthew
- * Richardson, Pedro Domingos, Marc Sumner, Hoifung
- * Poon, Daniel Lowd, and Jue Wang in the Department of
- * Computer Science and Engineering at the University of
- * Washington".
- * 
- * 4. Your publications acknowledge the use or
- * contribution made by the Software to your research
- * using the following citation(s): 
- * Stanley Kok, Parag Singla, Matthew Richardson and
- * Pedro Domingos (2005). "The Alchemy System for
- * Statistical Relational AI", Technical Report,
- * Department of Computer Science and Engineering,
- * University of Washington, Seattle, WA.
- * http://alchemy.cs.washington.edu.
- * 
- * 5. Neither the name of the University of Washington nor
- * the names of its contributors may be used to endorse or
- * promote products derived from this software without
- * specific prior written permission.
- * 
[…]

### 2023-06-07 solvers/alchemy/src/infer/hypercubeoperations.h

@@ -1,125 +1,0 @@
-/*
- * All of the documentation and software included in the
- * Alchemy Software is copyrighted by Stanley Kok, Parag
- * Singla, Matthew Richardson, Pedro Domingos, Marc
- * Sumner, Hoifung Poon, Daniel Lowd, and Jue Wang.
- * 
- * Copyright [2004-09] Stanley Kok, Parag Singla, Matthew
- * Richardson, Pedro Domingos, Marc Sumner, Hoifung
- * Poon, Daniel Lowd, and Jue Wang. All rights reserved.
- * 
- * Contact: Pedro Domingos, University of Washington
- * (pedrod@cs.washington.edu).
- * 
- * Redistribution and use in source and binary forms, with
- * or without modification, are permitted provided that
- * the following conditions are met:
- * 
- * 1. Redistributions of source code must retain the above
- * copyright notice, this list of conditions and the
- * following disclaimer.
- * 
- * 2. Redistributions in binary form must reproduce the
- * above copyright notice, this list of conditions and the
- * following disclaimer in the documentation and/or other
- * materials provided with the distribution.
- * 
- * 3. All advertising materials mentioning features or use
- * of this software must display the following
- * acknowledgment: "This product includes software
- * developed by Stanley Kok, Parag Singla, Matthew
- * Richardson, Pedro Domingos, Marc Sumner, Hoifung
- * Poon, Daniel Lowd, and Jue Wang in the Department of
- * Computer Science and Engineering at the University of
- * Washington".
- * 
- * 4. Your publications acknowledge the use or
- * contribution made by the Software to your research
- * using the following citation(s): 
- * Stanley Kok, Parag Singla, Matthew Richardson and
- * Pedro Domingos (2005). "The Alchemy System for
- * Statistical Relational AI", Technical Report,
- * Department of Computer Science and Engineering,
- * University of Washington, Seattle, WA.
- * http://alchemy.cs.washington.edu.
- * 
- * 5. Neither the name of the University of Washington nor
- * the names of its contributors may be used to endorse or
- * promote products derived from this software without
- * specific prior written permission.
- * 
- * THIS SOFTWARE IS PROVIDED BY THE UNIVERSITY OF WASHINGTON
[…]

### 2023-06-07 solvers/alchemy/src/infer/infer.cpp

@@ -1,689 +1,0 @@
-/*
- * All of the documentation and software included in the
- * Alchemy Software is copyrighted by Stanley Kok, Parag
- * Singla, Matthew Richardson, Pedro Domingos, Marc
- * Sumner, Hoifung Poon, Daniel Lowd, and Jue Wang.
- * 
- * Copyright [2004-09] Stanley Kok, Parag Singla, Matthew
- * Richardson, Pedro Domingos, Marc Sumner, Hoifung
- * Poon, Daniel Lowd, and Jue Wang. All rights reserved.
- * 
- * Contact: Pedro Domingos, University of Washington
- * (pedrod@cs.washington.edu).
- * 
- * Redistribution and use in source and binary forms, with
- * or without modification, are permitted provided that
- * the following conditions are met:
- * 
- * 1. Redistributions of source code must retain the above
- * copyright notice, this list of conditions and the
- * following disclaimer.
- * 
- * 2. Redistributions in binary form must reproduce the
- * above copyright notice, this list of conditions and the
- * following disclaimer in the documentation and/or other
- * materials provided with the distribution.
- * 
- * 3. All advertising materials mentioning features or use
- * of this software must display the following
- * acknowledgment: "This product includes software
- * developed by Stanley Kok, Parag Singla, Matthew
- * Richardson, Pedro Domingos, Marc Sumner, Hoifung
- * Poon, Daniel Lowd, and Jue Wang in the Department of
- * Computer Science and Engineering at the University of
- * Washington".
- * 
- * 4. Your publications acknowledge the use or
- * contribution made by the Software to your research
- * using the following citation(s): 
- * Stanley Kok, Parag Singla, Matthew Richardson and
- * Pedro Domingos (2005). "The Alchemy System for
- * Statistical Relational AI", Technical Report,
- * Department of Computer Science and Engineering,
- * University of Washington, Seattle, WA.
- * http://alchemy.cs.washington.edu.
- * 
- * 5. Neither the name of the University of Washington nor
- * the names of its contributors may be used to endorse or
[…]

### 2023-06-07 solvers/alchemy/src/infer/mcmc.h

@@ -1,1405 +1,0 @@
-/*
- * All of the documentation and software included in the
- * Alchemy Software is copyrighted by Stanley Kok, Parag
- * Singla, Matthew Richardson, Pedro Domingos, Marc
- * Sumner, Hoifung Poon, Daniel Lowd, and Jue Wang.
- * 
- * Copyright [2004-09] Stanley Kok, Parag Singla, Matthew
- * Richardson, Pedro Domingos, Marc Sumner, Hoifung
- * Poon, Daniel Lowd, and Jue Wang. All rights reserved.
- * 
- * Contact: Pedro Domingos, University of Washington
- * (pedrod@cs.washington.edu).
- * 
- * Redistribution and use in source and binary forms, with
- * or without modification, are permitted provided that
- * the following conditions are met:
- * 
- * 1. Redistributions of source code must retain the above
- * copyright notice, this list of conditions and the
- * following disclaimer.
- * 
- * 2. Redistributions in binary form must reproduce the
- * above copyright notice, this list of conditions and the
- * following disclaimer in the documentation and/or other
- * materials provided with the distribution.
- * 
- * 3. All advertising materials mentioning features or use
- * of this software must display the following
- * acknowledgment: "This product includes software
- * developed by Stanley Kok, Parag Singla, Matthew
- * Richardson, Pedro Domingos, Marc Sumner, Hoifung
- * Poon, Daniel Lowd, and Jue Wang in the Department of
- * Computer Science and Engineering at the University of
- * Washington".
- * 
- * 4. Your publications acknowledge the use or
- * contribution made by the Software to your research
- * using the following citation(s): 
- * Stanley Kok, Parag Singla, Matthew Richardson and
- * Pedro Domingos (2005). "The Alchemy System for
- * Statistical Relational AI", Technical Report,
- * Department of Computer Science and Engineering,
- * University of Washington, Seattle, WA.
[…]

### 2023-06-07 solvers/alchemy/src/infer/mrf.h

@@ -1,464 +1,0 @@
-/*
- * All of the documentation and software included in the
- * Alchemy Software is copyrighted by Stanley Kok, Parag
- * Singla, Matthew Richardson, Pedro Domingos, Marc
- * Sumner, Hoifung Poon, and Daniel Lowd.
- * 
- * Copyright [2004-07] Stanley Kok, Parag Singla, Matthew
- * Richardson, Pedro Domingos, Marc Sumner, Hoifung
- * Poon, and Daniel Lowd. All rights reserved.
- * 
- * Contact: Pedro Domingos, University of Washington
- * (pedrod@cs.washington.edu).
- * 
- * Redistribution and use in source and binary forms, with
- * or without modification, are permitted provided that
- * the following conditions are met:
- * 
- * 1. Redistributions of source code must retain the above
- * copyright notice, this list of conditions and the
- * following disclaimer.
- * 
- * 2. Redistributions in binary form must reproduce the
- * above copyright notice, this list of conditions and the
- * following disclaimer in the documentation and/or other
- * materials provided with the distribution.
- * 
- * 3. All advertising materials mentioning features or use
- * of this software must display the following
- * acknowledgment: "This product includes software
- * developed by Stanley Kok, Parag Singla, Matthew
- * Richardson, Pedro Domingos, Marc Sumner, Hoifung
- * Poon, and Daniel Lowd in the Department of Computer Science and
- * Engineering at the University of Washington".
- * 
- * 4. Your publications acknowledge the use or
- * contribution made by the Software to your research
- * using the following citation(s): 
- * Stanley Kok, Parag Singla, Matthew Richardson and
- * Pedro Domingos (2005). "The Alchemy System for
- * Statistical Relational AI", Technical Report,
- * Department of Computer Science and Engineering,
- * University of Washington, Seattle, WA.
- * http://www.cs.washington.edu/ai/alchemy.
- * 
- * 5. Neither the name of the University of Washington nor
- * the names of its contributors may be used to endorse or
- * promote products derived from this software without
- * specific prior written permission.
- * 
- * THIS SOFTWARE IS PROVIDED BY THE UNIVERSITY OF WASHINGTON
[…]

### 2023-06-07 solvers/alchemy/src/infer/superclause.h

@@ -1,748 +1,0 @@
-/*
- * All of the documentation and software included in the
- * Alchemy Software is copyrighted by Stanley Kok, Parag
- * Singla, Matthew Richardson, Pedro Domingos, Marc
- * Sumner, Hoifung Poon, Daniel Lowd, and Jue Wang.
- * 
- * Copyright [2004-09] Stanley Kok, Parag Singla, Matthew
- * Richardson, Pedro Domingos, Marc Sumner, Hoifung
- * Poon, Daniel Lowd, and Jue Wang. All rights reserved.
- * 
- * Contact: Pedro Domingos, University of Washington
- * (pedrod@cs.washington.edu).
- * 
- * Redistribution and use in source and binary forms, with
- * or without modification, are permitted provided that
- * the following conditions are met:
- * 
- * 1. Redistributions of source code must retain the above
- * copyright notice, this list of conditions and the
- * following disclaimer.
- * 
- * 2. Redistributions in binary form must reproduce the
- * above copyright notice, this list of conditions and the
- * following disclaimer in the documentation and/or other
- * materials provided with the distribution.
- * 
- * 3. All advertising materials mentioning features or use
- * of this software must display the following
- * acknowledgment: "This product includes software
- * developed by Stanley Kok, Parag Singla, Matthew
- * Richardson, Pedro Domingos, Marc Sumner, Hoifung
- * Poon, Daniel Lowd, and Jue Wang in the Department of
- * Computer Science and Engineering at the University of
- * Washington".
- * 
- * 4. Your publications acknowledge the use or
- * contribution made by the Software to your research
- * using the following citation(s): 
- * Stanley Kok, Parag Singla, Matthew Richardson and
- * Pedro Domingos (2005). "The Alchemy System for
- * Statistical Relational AI", Technical Report,
- * Department of Computer Science and Engineering,
- * University of Washington, Seattle, WA.
- * http://alchemy.cs.washington.edu.
- * 
- * 5. Neither the name of the University of Washington nor
- * the names of its contributors may be used to endorse or
- * promote products derived from this software without
- * specific prior written permission.
- * 
- * THIS SOFTWARE IS PROVIDED BY THE UNIVERSITY OF WASHINGTON
- * AND CONTRIBUTORS "AS IS" AND ANY EXPRESS OR IMPLIED
[…]

### 2023-06-07 solvers/alchemy/src/learnwts/discriminativelearner.h

@@ -1,1926 +1,0 @@
-/*
- * All of the documentation and software included in the
- * Alchemy Software is copyrighted by Stanley Kok, Parag
- * Singla, Matthew Richardson, Pedro Domingos, Marc
- * Sumner, Hoifung Poon, Daniel Lowd, and Jue Wang.
- *
- * Copyright [2004-09] Stanley Kok, Parag Singla, Matthew
- * Richardson, Pedro Domingos, Marc Sumner, Hoifung
- * Poon, Daniel Lowd, and Jue Wang. All rights reserved.
- *
- * Contact: Pedro Domingos, University of Washington
- * (pedrod@cs.washington.edu).
- *
- * Redistribution and use in source and binary forms, with
- * or without modification, are permitted provided that
- * the following conditions are met:
- *
- * 1. Redistributions of source code must retain the above
- * copyright notice, this list of conditions and the
- * following disclaimer.
- *
- * 2. Redistributions in binary form must reproduce the
- * above copyright notice, this list of conditions and the
- * following disclaimer in the documentation and/or other
- * materials provided with the distribution.
- *
- * 3. All advertising materials mentioning features or use
- * of this software must display the following
- * acknowledgment: "This product includes software
- * developed by Stanley Kok, Parag Singla, Matthew
- * Richardson, Pedro Domingos, Marc Sumner, Hoifung
- * Poon, Daniel Lowd, and Jue Wang in the Department of
- * Computer Science and Engineering at the University of
- * Washington".
- *
- * 4. Your publications acknowledge the use or
- * contribution made by the Software to your research
- * using the following citation(s):
- * Stanley Kok, Parag Singla, Matthew Richardson and
- * Pedro Domingos (2005). "The Alchemy System for
- * Statistical Relational AI", Technical Report,
- * Department of Computer Science and Engineering,
- * University of Washington, Seattle, WA.
- * http://alchemy.cs.washington.edu.
- *
- * 5. Neither the name of the University of Washington nor
- * the names of its contributors may be used to endorse or
- * promote products derived from this software without
- * specific prior written permission.
- *
[…]

### 2023-06-07 solvers/alchemy/src/liftedinfer/bridge/includes/liftedalgshandler.h

@@ -1,30 +1,0 @@
-#ifndef __LIFTEDALGS_HANDLER
-#define __LIFTEDALGS_HANDLER
-#include "lvrmln.h"
-#include "lvparams.h"
-#include "clustercreator.h"
-#include "gibbsprocesshandler.h"
-#include "proposalconstructor.h"
-
-struct LiftedAlgsHandler
-{
-	LiftedAlgsHandler(LvrMLN& mln_);
-	~LiftedAlgsHandler();
-	//Lifted Blocked Gibbs Sampler
-	void LBGApproxMarginals(LvrParams* params);
-	//Lifted Importance Sampler
-	void LISApproxPartition(LvrParams* params);
-	void LISApproxMarginals(LvrParams* params);
-	//Lifted Weighted Model Counter (PTP)
-	void WMPTPZApprox(LvrParams* params);
-	void WMPTPZExact(LvrParams* params);
-	void buildProposal(LvrParams* params);
-private:
-	LvrMLN& mln;
-	LPTPSearch* ptpSearch;
-	LClusterCreator* clusterCreator;
-	LProposalConstructor* proposalConstructor;
-	GibbsProcessHandler* gibbsProcessHandler;
-};
-
-#endif

### 2023-06-07 solvers/alchemy/src/liftedinfer/bridge/src/liftedalgsconvertor.cpp

@@ -1,453 +1,0 @@
-#include "liftedalgsconvertor.h"
-#include "queryupdater.h"
-
-//constructor for weight learning where information needs to be converted back and forth
-//between the alchemy format and the lifted inference format (I.E. WEIGHT LEARNING)
-LiftedAlgsConvertor::LiftedAlgsConvertor(VariableState* state):state_(state),mln_(state_->getMLN()),
-domain_(state_->getDomain())
-{
-	lvrMln = new LvrMLN();
-	//convertInputMLNToLifted(state_->getMLN(),state_->getDomain());
-	bool mlncontainsGrndClause=false;
-	convertInputMLNToLifted(mln_,domain_,mlncontainsGrndClause);
-	//mln_= state->getMLN();
-	//domain_ = domain;
-	//intilialize the query updater to contain all atoms in the state
-	const GroundPredicateHashArray* grndPredHashArray = state_->getGndPredHashArrayPtr();
-	vector<vector<int> > queryIntRep(grndPredHashArray->size());
-	//cout<<grndPredHashArray->size()<<endl;
-	for(int i=0;i<grndPredHashArray->size();i++)
-	{
-		//const Array<unsigned int*> intRep = (*grndPredHashArray)[i]->getIntArrRep();
-		int sz = (*grndPredHashArray)[i]->getIntArrRep()->size();
-		vector<int> tmp(sz);
-		for(int j=0;j<sz;j++)
-		{
-			tmp[j]=(*((*grndPredHashArray)[i]->getIntArrRep()))[j];
-		}
-		queryIntRep[i] = tmp;
-		//(*grndPredHashArray)[i]->print(cout,domain_);
-		//cout<<endl;
-		//LFileDump::dumpQueriesToFile(queryIntRep);
-	}
-	//no need for query strings or results file since never written to file
-	vector<string> qstrings;
- 	LvrQueryUpdater::createInstance(queryIntRep,qstrings,"");
- 	liftedAlgsHandler = NULL;
-}
-
-//constructor for marginal estimations where information only needs to be converted
-//from alchemy format to lifted inference format
-LiftedAlgsConvertor::LiftedAlgsConvertor(MLN* mln, Domain* domain,GroundPredicateHashArray queries):mln_(mln),
-		domain_(domain)
[…]

### 2023-06-07 solvers/alchemy/src/liftedinfer/common/includes/cleanuputils.h

@@ -1,83 +1,0 @@
-#ifndef __CLEANUP_UTILS_H
-#define __CLEANUP_UTILS_H
-
-template<typename Container>
-void cleanup(Container& c)
-{
-	while(!c.empty())
-	{
-		
-		if(c.back())
-		{
-			delete c.back();
-			c.back() = NULL;
-		}
-		c.pop_back();
-	}
-}
-
-template<typename Container>
-void removeItem(Container& c, int itemIndex)
-{
-	
-	if(c.at(itemIndex))
-	{
-		delete c.at(itemIndex);
-		c.at(itemIndex) = NULL;
-	}
-	c.erase(c.begin()+itemIndex);
-}
-
-
-template<typename Container>
-void removeUnusedItems(Container& oldC, Container& newC)
-{
-	while(!oldC.empty())
-	{
-		if(!oldC.back())
-			continue;
-		bool found = false;
-		for(unsigned int i=0;i<newC.size();i++)
-		{
-			if(oldC.back() == newC[i])
-			{
-				found =true;
-				break;
-			}
-		}
-		if(!found)
-		{
-			//element does not occur in new container, delete it
-			delete oldC.back();
-			oldC.back() = NULL;
-
-		}
-	oldC.pop_back();
-	}
-}
-
-template<typename Container>
-void cleanupItems(Container& c,int startIndex = -1,int endIndex = -1)
-{
-	int start;
-	startIndex == -1?start = 0:start = startIndex;
-	int end;
-	endIndex == -1?end = c.size():end = endIndex;
-	for(unsigned int m=start;m<end;m++)
-		cleanup(c[m]);
-}
-
-template<typename Container>
-void removeItems(Container& c,int startIndex = -1,int endIndex = -1)
-{
-	int start;
-	startIndex == -1?start = 0:start = startIndex;
-	int end;
-	endIndex == -1?end = c.size():end = endIndex;
-	for(unsigned int m=start;m<end;m++)
-	{
-		delete c[m];
-	}
-	c.erase(c.begin()+start,c.begin()+end);
-}
-#endif

### 2023-06-07 solvers/alchemy/src/liftedinfer/common/includes/decomposer.h

@@ -1,56 +1,0 @@
-#ifndef LDECOMPOSER_H_
-#define LDECOMPOSER_H_
-#include <vector>
-#include <iostream>
-#include <set>
-#include <map>
-using namespace std;
-
-#include "lvrmln.h"
-
-struct Decomposer
-{
-	vector<LvrTerm*> decomposer_terms;
-	//key is predicatesymbol id, value is position the term occupies
-	map<int,int> predicate_positions;
-	map<int,int> norm_predicate_positions;
-	//key is predicatesymbol id, value is number of predicates sharing a common position
-	map<int,int> atomCounter;
-	bool deletionMarker;
-	Decomposer(){}
-	Decomposer(vector<LvrTerm*> decomposer_terms_, map<int,int> predicate_positions_,map<int,int> atomCounter_,
-		map<int,int> norm_predicate_positions_):decomposer_terms(decomposer_terms_),
-		predicate_positions(predicate_positions_),atomCounter(atomCounter_),deletionMarker(false),norm_predicate_positions(norm_predicate_positions_)
-	{}
-	void print()
-	{
-		cout<<"[";
-		for(unsigned int j=0;j<decomposer_terms.size();j++)
-		{
-			cout<<decomposer_terms[j];
-			if(j!=decomposer_terms.size()-1)
-				cout<<" , ";
-		}
-		cout<<"]";
-	}
-
-	~Decomposer();
-};
-
-struct LDecomposer
-{
-	LvrMLN& mln;
-	bool decomposeCNF(vector<WClause*>& CNF,int& powerFactor);
-	void find_decomposer(vector<WClause*>& CNF, vector<Decomposer*>& decomposer_list);
-	//void find_decomposer_new(vector<WClause*>& CNF,vector<Decomposer*>& decomposer_list, int curr_predicate_count);
-	LDecomposer(LvrMLN& mln_):mln(mln_){}
-private:
-	bool append_to_decomposer (vector<int> atom_list,vector<LvrTerm*> terms,vector<vector<int> >positions,vector<Decomposer*>& decomposer_list,
-		vector<int> norm_atom_list);
-	Decomposer* create_new_decomposer(LvrTerm* term,vector<int> atom_list,vector<int> position_list,vector<int> norm_atom_list);
-	void removeRowsFromDecomposer(WClause* clause, vector<Decomposer*>& decomposer_list);
-	Decomposer* merge(Decomposer* d1, Decomposer* d2);
-	int unify(Decomposer* d1, Decomposer* d2);
-};
-
-#endif

### 2023-06-07 solvers/alchemy/src/liftedinfer/common/includes/hashalgorithm.h

@@ -1,98 +1,0 @@
-#ifndef __LVRHASH_ALGORITHM
-#define __LVRHASH_ALGORITHM
-#include "lvrmln.h"
-
-struct LvrHashAlgorithm
-{
-	//format of input for hashing grounded atom: <normparentid,term1,term2,....>
-	//Note:Only to be called for atoms that are completely grounded (no variables)
-	static int DJBHash(vector<int> vals)
-	{
-		augmentVector(vals);
-		unsigned int hash = 5381;
-		for(std::size_t i = 0; i < vals.size(); i++)
-		{
-			hash = ((hash << 5) + hash) + vals[i];
-		}
-		return hash;
-	}
-
-	static unsigned int DJBHashUS(vector<int> vals)
-	{
-		augmentVector(vals);
-		unsigned int hash = 5381;
-		for(std::size_t i = 0; i < vals.size(); i++)
-		{
-			hash = ((hash << 5) + hash) + vals[i];
-		}
-		return hash;
-	}
-
-	static int convertToHash(Atom* atom)
-	{
-		if(atom->isConstant())
-		{
-			vector<int> signature;
-			signature.push_back(atom->symbol->normParentId);
-			for(unsigned int jj=0;jj<atom->terms.size();jj++)
-			{
-				signature.push_back(atom->terms[jj]->domain[0]);
-			}
-			return DJBHash(signature);
-
-		}
-		vector<vector<int> > signature;
-		vector<int> id(1);
-		id[0] = atom->symbol->normParentId;
-		signature.push_back(id);
-		for(unsigned int i=0;i<atom->terms.size();i++)
-		{
-			vector<int> trm(atom->terms[i]->domain.size());
-			for(unsigned int j=0;j<atom->terms[i]->domain.size();j++)
-				trm[j] = atom->terms[i]->domain[j];
-			signature.push_back(trm);
-		}
-		return DJBLHash(signature);
-	}
-
-	//format of input for hashing atom with variables: <normparentid><[val(if term is constant)][<domval0><domval1>....(if variable)]>....
-	//TO be only called for atoms with atleast 1 variable in its terms
-	static int DJBLHash(vector<vector<int> > vals)
-	{
-		vector<int> signature;
-		signature.push_back(vals[0].at(0));
-		for(unsigned int i=1;i<vals.size();i++)
-		{
-			for(unsigned int j=0;j<vals[i].size();j++)
-				signature.push_back(vals[i].at(j));
-		}
[…]

### 2023-06-07 solvers/alchemy/src/liftedinfer/common/includes/heuristics.h

@@ -1,15 +1,0 @@
-#ifndef __HEURISTICS__
-#define __HEURISTICS__
-#include "decomposer.h"
-
-struct LHeuristics
-{
-	LDecomposer& decomposer;
-	LvrMLN& mln;
-	LHeuristics(LDecomposer& decomposer_,LvrMLN& mln_):decomposer(decomposer_),mln(mln_){}
-	Atom* decomposition_lookahead(vector<WClause*> clauses);
-	Atom* getAtomToSplit(vector<WClause*> CNF,bool ptpexactmar=false);
-	static Atom* getAtomToSplitH2(vector<WClause*> CNF);
-	static int proposalCouplingScore(vector<WClause*> origClauses,Atom* a1, Atom* a2);
-};
-#endif

### 2023-06-07 solvers/alchemy/src/liftedinfer/common/includes/lvratomhashtemplate.h

@@ -1,257 +1,0 @@
-#ifndef __LVRATOMHASH_TEMPLATE
-#define __LVRATOMHASH_TEMPLATE
-#include "hashalgorithm.h"
-#include <map>
-using namespace std;
-
-template<typename T>
-struct LvrAtomHashTemplate
-{
-private:
-	map<int,T> data;
-public:
-	LvrAtomHashTemplate(){}
-	~LvrAtomHashTemplate(){}
-
-	void insertOrReplaceValue(Atom* atom,T value_)
-	{
-
-		int key = LvrHashAlgorithm::convertToHash(atom);
-		T value = value_;
-		typename map<int,T>::iterator it = data.find(key);
-		if(it == data.end())
-		{
-			data.insert(pair<int,T>(key,value));
-		}
-		else
-		{
-			it->second = (T) value;
-		}
-	}
-	bool find(Atom* atom)
-	{
-		int key = LvrHashAlgorithm::convertToHash(atom);
-		if(data.find(key)!=data.end())
-			return true;
-		else
-			return false;
-	}
-	void update(Atom* atom,T value_)
-	{
-		int key = LvrHashAlgorithm::convertToHash(atom);
-		T value = value_;
-		typename map<int,T>::iterator it = data.find(key);
-		if(it!=data.end())
-		{
-			it->second = value;
-		}
-	}
-
-	void update(vector<int> signature,T value_)
-	{
-		int key = LvrHashAlgorithm::DJBHash(signature);
-		T value = value_;
-		typename map<int,T>::iterator it = data.find(key);
-		if(it!=data.end())
-		{
-			it->second = value;
-		}
-	}
-
-	
-	void insert(Atom* atom,T value_)
-	{
-		int key = LvrHashAlgorithm::convertToHash(atom);
-		T value = value_;
-		typename map<int,T>::iterator it = data.find(key);
-		data.insert(pair<int,T>(key,value));
-	}
-
-	//representation: int[0]=atom's normparentid, followed by each term's grounded value
-	void insert(vector<int> signature,T value_)
-	{
-		int key = LvrHashAlgorithm::DJBHash(signature);		
-		T value = value_;
-		typename map<int,T>::iterator it = data.find(key);
-		data.insert(pair<int,T>(key,value));
-	}
-
-	void incrementValue(vector<int> signature,int value_)
-	{
-		if(value_==0)
-			return;
[…]

### 2023-06-07 solvers/alchemy/src/liftedinfer/common/includes/lvrnormpropagation.h

@@ -1,482 +1,0 @@
-#ifndef __LVRNORM_PROPAGATION
-#define __LVRNORM_PROPAGATION
-#include "lvrmln.h"
-#include "hashalgorithm.h"
-#include "lvrpermutations.h"
-#include "cleanuputils.h"
-#include "randomgenutil.h"
-
-struct LvrNormPropagation
-{
-	LvrMLN& mln;
-	set<int> hashCodesToSetTrue;
-	map<int,int> isolatedHashCodeMap;
-	enum ERules{AGB,IV,NONE};
-	ERules ruleToApply;
-	vector<bool>isolatedTerms;
-	LvrNormPropagation(LvrMLN& mln_):mln(mln_){}
-
-	void propagateNormalizedCNF(vector<WClause*>& CNF, Atom* atomToSplit,vector<bool> isolatedTerms_)
-	{
-		if(atomToSplit->isConstant())
-		{
-			//efficient to split
-			processConstants(CNF,atomToSplit,false);
-		}
-		else
-		{
-			isolatedTerms = isolatedTerms_;
-			ruleToApply = NONE;
-			doPropagateNormalizedCNF(CNF,atomToSplit);
-		}
-	}
-	/*
-	void processConstants(vector<WClause*>& CNF, Atom* atom, bool setTrue)
-	{
-		unsigned int hash = LvrHashAlgorithm::convertToHash(atom);
-		for(int i=0;i<CNF.size();i++)
-		{
-			for(int j=0;j<CNF[i]->atoms.size();j++)
-			{
-				unsigned int hash1 = LvrHashAlgorithm::convertToHash(CNF[i]->atoms[j]);
-				if(hash == hash1)
-				{
-					if(CNF[i]->sign[j] && !setTrue)
-						CNF[i]->satisfied= true;
-					else if(!CNF[i]->sign[j] && setTrue)
-						CNF[i]->satisfied= true;
-					CNF[i]->removeAtom(j);
-					j--;
-				}
-			}
-			if(CNF[i]->atoms.size()==0 && !CNF[i]->satisfied)
-			{
-				removeItem(CNF,i);
-				i--;
-			}
-		}
-		
-	}
-	*/
-	void processConstants(vector<WClause*>& CNF, Atom* atom, bool setTrue)
-	{
-		for(int i=0;i<CNF.size();i++)
-		{
-			for(int j=0;j<CNF[i]->atoms.size();j++)
-			{
[…]

### 2023-06-07 solvers/alchemy/src/liftedinfer/common/includes/lvrpermutations.h

@@ -1,48 +1,0 @@
-#ifndef __LVRPERMUTATIONS
-#define __LVRPERMUTATIONS
-#include "lvrmln.h"
-struct LvrPermutations
-{
-static void permuteTerms(vector<LvrTerm*> terms, vector<vector<int> >& permutedDomainList)
-{
-	if(terms.size()==0)
-		return;
-	map<int,int> domainIndex;
-	int numberOfGroundings=1;
-	for(unsigned int i=0;i<terms.size();i++)
-	{
-		//Initialize to first position
-		domainIndex.insert(pair<int,int>(i,0));
-		numberOfGroundings *= terms[i]->domain.size();
-	}	
-	int iter = 0;
-	while(1)
-	{
-		vector<int> domainValues;
-		for(unsigned int i=0;i<terms.size();i++)
-		{
-			//get current index
-			int currDomainIndex = domainIndex[i];
-			domainValues.push_back(terms[i]->domain[currDomainIndex]);
-		}
-		permutedDomainList.push_back(domainValues);
-		//Update pointers
-		int ind=terms.size()-1;
-		domainIndex[ind]++;
-		while(domainIndex[ind] == terms[ind]->domain.size())
-		{
-			domainIndex[ind]=0;
-			if(ind!=0)
-				domainIndex[ind-1]++;
-			else
-				break;
-			ind--;
-		}
-		iter++;
-		//check if we finished all domains
-		if(iter >= numberOfGroundings)
-			break;
-	}
-}
-};
-#endif

### 2023-06-07 solvers/alchemy/src/liftedinfer/common/includes/paramconstants.h

@@ -1,24 +1,0 @@
-#ifndef __LPARAM_CONSTANTS
-#define __LPARAM_CONSTANTS
-#define NEWPREDICATEPREFIX "NSM"
-#define CLUSTERFILE "cluster.cls"
-#define RESULTFILE "result.dat"
-#define MAXTIMEOUTCLUSTERING 60
-#define PROPOSALNUMPARENTS 2
-#define SPLITCHUNKSIZE 25
-#define PRINTRESULTSINTERVAL 25
-#define CLUSTERINGWINDOWSIZE 100
-//parameters for  inference
-#define PROPOSALUPDATEINTERVAL 50
-#define MAXSTEPSINFER 1000
-#define MAXSTEPSWL 20
-#define MAXSECONDSWL 120
-#define MAXSECONDSINFER 10000
-#define BURNINSTEPS 50
-#define LEARNINGRATE 0.001
-#define SLEEPTIME 5
-//caching in PTP exact inference
-#define CACHESIZE 1024
-#define MOSTRECENTSIZE 50
-#define MAXCNFSIZE 256
-#endif

### 2023-06-07 solvers/alchemy/src/liftedinfer/common/includes/ptptree.h

@@ -1,145 +1,0 @@
-#ifndef __LPTPTREE__
-#define __LPTPTREE__
-#include "lvrmln.h"
-#include "cleanuputils.h"
-
-enum NodeType
-{
-	ESPLIT,
-	EDECOMPOSER,
-	EDISJOINT
-};
-
-struct LAssignment
-{
-	vector<Atom*> atoms;
-	vector<int> assignment;
-	vector<LogDouble> probabilities;
-	~LAssignment()
-	{
-		//cleanup(atoms);
-	}
-	void cleanAssignments()
-	{
-		cleanup(atoms);
-		assignment.clear();
-		probabilities.clear();
-	}
-};
-struct LPTPNode
-{
-	int type;
-	Atom* atom;
-	int powerFactor;
-	vector<LogDouble> zValues;
-	vector<LogDouble> binCoeff;
-	LogDouble norm;
-	vector<LPTPNode*> children;
-	int id;
-	int parentId;
-	int parentBranchNo;
-	int assignment;
-	vector<LogDouble> cdf;
-	LogDouble downValue;
-	vector<LogDouble> branchWeights;
-	LogDouble nodeValue;
-	//key = hash(normid+termid),value = domainvalue
-	vector<map<int,int> > decomposerMappings;
-	vector<int> domainPowerFactors;
-	//vector<vector<WClause*> > decomposedList;
-	LPTPNode():downValue(LogDouble(1,false))
-	{
-	}
-	~LPTPNode()
-	{
-		if(type==ESPLIT)
-			delete atom;
-	}
-	
-	LogDouble getProbability(int index)
-	{
-		if(type==ESPLIT)
-		{
-			return (zValues[index]*binCoeff[index])/norm;
-		}
-		return LogDouble(0,false);
-	}
-
-	void constructCDF()
-	{
-		if(type==ESPLIT)
-		{
-			cdf.clear();
-			cdf.resize(zValues.size());
-			cdf[0] = (zValues[0]*binCoeff[0])/norm;
-			for(unsigned int i=1;i<zValues.size()-1;i++)
-			{
-				cdf[i]=cdf[i-1] + (zValues[i]*binCoeff[i])/norm;
-			}
-			cdf[zValues.size()-1]=LogDouble(1,false);			
-		}
-		
-}
-
-
-	void print()
-	{
-		cout<<"Id="<<id<<endl;
-		cout<<"ParentId="<<parentId<<endl;
[…]

### 2023-06-07 solvers/alchemy/src/liftedinfer/common/includes/rulesutil.h

@@ -1,119 +1,0 @@
-#ifndef LRULESUTIL_H_
-#define LRULESUTIL_H_
-#include "lvrmln.h"
-#include "cleanuputils.h"
-#include "normalizer.h"
-#include "lvrpermutations.h"
-
-struct LRulesUtil
-{
-	static bool computeIsolatedTerms(Atom* atom, vector<WClause*> clauses,vector<bool>& isolatedTerms)
-	{
-		isolatedTerms.clear();
-		isolatedTerms.resize(atom->terms.size());
-		int falseCnt = 0;
-		for(unsigned int i=0;i<isolatedTerms.size();i++)
-		{
-			//a constant is never isolated
-			if(atom->terms[i]->domain.size()==1)
-			{
-				falseCnt++;
-				isolatedTerms[i] = false;
-			}
-			else
-			{
-				isolatedTerms[i] = true;
-			}
-		}
-		if(falseCnt == isolatedTerms.size())
-			return false;
-
-		for(unsigned int i=0;i<clauses.size();i++)
-		{
-			for(unsigned int j=0;j<clauses[i]->atoms.size();j++)
-			{
-				if(clauses[i]->atoms[j]->symbol->id == atom->symbol->id)
-				{
-					for(unsigned int k=0;k<clauses[i]->atoms[j]->terms.size();k++)
-					{
-						if(isolatedTerms[k])
-						{
-							if(clauses[i]->atoms[j]->terms[k]->domain.size()>1)
-							{
-								bool shared = checkOccurrence(clauses[i]->atoms[j]->terms[k],clauses[i],j);
-								if(shared)
-								{
-									isolatedTerms[k]=false;
-									falseCnt++;
-									if(falseCnt == isolatedTerms.size())
-										return false;
-								}
-							}
-						}
-					}
-				}
-			}
-		}
-		return true;
-	}
-
-	static bool isBlocked(Atom* atom, int singletonIndex,vector<WClause*> clauses)
-	{
-		for(unsigned int i=0;i<clauses.size();i++)
-		{
-			vector<LvrTerm*> terms;
-			vector<int> occurences;
-			for(unsigned int j=0;j<clauses[i]->atoms.size();j++)
-			{
-				if(clauses[i]->atoms[j]->symbol->id == atom->symbol->id)
-				{
-					terms.push_back(clauses[i]->atoms[j]->terms[singletonIndex]);
-					occurences.push_back(j);
-				}
-			}
-			if(terms.size()==0)
[…]

### 2023-06-07 solvers/alchemy/src/liftedinfer/common/src/decomposer.cpp

@@ -1,357 +1,0 @@
-#include "decomposer.h"
-#include "cleanuputils.h"
-
-Decomposer::~Decomposer()
-{
-	decomposer_terms.clear();
-	predicate_positions.clear();
-	atomCounter.clear();
-}
-
-//creates a new decomposer item
-Decomposer* LDecomposer::create_new_decomposer(LvrTerm* term,vector<int> atom_list,vector<int> position_list,vector<int> norm_atom_list)
-{
-	vector<LvrTerm*> decomposer_terms;
-	map<int,int> predicate_positions;
-	map<int,int> atomCounter;
-	map<int,int> norm_predicate_positions;
-	decomposer_terms.push_back(term);
-	for(unsigned int k=0;k<atom_list.size();k++)
-	{
-		predicate_positions[atom_list[k]]=position_list[k];
-		norm_predicate_positions[norm_atom_list[k]] = position_list[k];
-		atomCounter[atom_list[k]]=1;
-	}
-	Decomposer* d = new Decomposer(decomposer_terms,predicate_positions,atomCounter,norm_predicate_positions);
-	return d;
-}
-//0 - did not unify, 1- unified, -1 - disjoint
-int LDecomposer::unify(Decomposer* d1, Decomposer* d2)
-{
-	bool found=false;
-	for(map<int,int>::iterator it1=d1->predicate_positions.begin();it1!=d1->predicate_positions.end();it1++)
-	{
-		map<int,int>::iterator tmp = d2->predicate_positions.find(it1->first);
-		if(tmp!=d2->predicate_positions.end())
-		{
-			found=true;
-			//found d1's predicate in d2, match the positions
-			if(tmp->second != it1->second)
-				return 0;
-		}
-	}
-	if(found)
-		return 1;
-	else
-		return -1;
-}
-
-Decomposer* LDecomposer::merge(Decomposer* d1, Decomposer* d2)
-{
-	vector<LvrTerm*> decomposerTerms;
-	map<int,int> predicate_positions;
-	map<int,int> atomCounter;
-	map<int,int> norm_predicate_positions;
-	for(unsigned int i=0;i<d1->decomposer_terms.size();i++)
-	{
-		decomposerTerms.push_back(d1->decomposer_terms[i]);
-	}
-	for(unsigned int i=0;i<d2->decomposer_terms.size();i++)
-	{
-		decomposerTerms.push_back(d2->decomposer_terms[i]);
-	}
[…]

### 2023-06-07 solvers/alchemy/src/liftedinfer/common/src/lvrmln.cpp

@@ -1,633 +1,0 @@
-#include "lvrmln.h"
-#include "cleanuputils.h"
-#include "normalizer.h"
-#include "hashalgorithm.h"
-
-
-#include <sstream>
-using namespace std;
-
-
-
-void Atom::print(bool verbose)
-{
-	if(verbose)
-	{
-		cout<<symbol->symbol.c_str()<<"["<< symbol->id<<","<<symbol->parentId<<"{"<<symbol->pweight<<","<<symbol->nweight<<"}]"<<" (";
-		for(unsigned int j=0;j<terms.size();j++){
-			if((int)terms[j]->domain.size()==1){
-				cout<<terms[j]->domain[0];
-			}
-			else{
-				cout<<terms[j]<<"[ #"<<terms[j]->domain.size()<<" ]";
-			}
-			if(j!=terms.size()-1)
-				cout<<",";
-		}
-		cout<<")";
-	}
-	else
-	{
-		cout<<symbol->symbol.c_str()<<symbol->id<<"(";
-		for(unsigned int j=0;j<terms.size();j++){
-			if((int)terms[j]->domain.size()==1){
-				cout<<terms[j]->domain[0];
-			}
-			else{
-				cout<<terms[j]<<"#"<<terms[j]->domain.size();
-			}
-			/*if(terms[j]->origDomainSize!=-1)
-			{
-				cout<<"D#"<<terms[j]->origDomainSize;
-			}
-			*/
-			if(j!=terms.size()-1)
-				cout<<",";
-		}
-		cout<<")";
-
-
-	}
-}
-
-
-bool Atom::isConstant()
-{
-	bool constantDomain = true;
-	for(unsigned int i=0;i<terms.size();i++)
-	{
-		if(terms[i]->domain.size() > 1)
-		{
-			constantDomain = false;
-			break;
-		}
-	}
-	return constantDomain;
-}
-
-bool Atom::isSingletonAtom(int& variableIndex)
-{
-	/*
-	if(terms.size() == 1)
-	{
-		variableIndex = 0;
-		return true;
-	}
-	*/
-
-	variableIndex = -1;
-	int numVariables = 0;
-	for(unsigned int i=0;i<terms.size();i++)
-	{
-		if(terms[i]->domain.size() > 1)
-		{
-			//variable
-			numVariables++;
-			if(numVariables > 1)
-				break;
-			//store index of the first variable
-			if(variableIndex == -1)
-				variableIndex = i;
-		}
-	}
[…]

### 2023-06-07 solvers/alchemy/src/liftedinfer/common/src/lvrptptreesampling.cpp

@@ -1,231 +1,0 @@
-#include "lvrptptreesampling.h"
-#include "randomgenutil.h"
-#include <assert.h>
-#include "hashalgorithm.h"
-
-bool compareChildren(LPTPNode* l1, LPTPNode* l2)
-{
-	if(l1->parentBranchNo < l2->parentBranchNo)
-		return true;
-	else
-		return false;
-}
-
-LvrPTPTreeSampling::LvrPTPTreeSampling()
-{
-	ptpTree = new LPTPTree();
-}
-
-LvrPTPTreeSampling::~LvrPTPTreeSampling()
-{
-	delete ptpTree;
-}
-
-void LvrPTPTreeSampling::addTreeNode(Atom* atom,vector<LogDouble> weights,vector<LogDouble> binCoeffs,
-	LogDouble norm,NodeType nodeType,int nodeId, int parentId, 
-	int parentBranchNo,vector<LogDouble>* branchWeights,LogDouble nodeValue)
-{
-	assert(nodeType == ESPLIT);
-	Atom* newAtom = LvrMLN::create_new_atom(atom);
-	LPTPNode* nd = new LPTPNode();
-	nd->atom = newAtom;
-	nd->zValues = weights;
-	nd->norm = norm;
-	nd->binCoeff = binCoeffs;
-	nd->type = nodeType;
-	nd->id = nodeId;
-	nd->parentId = parentId;
-	nd->parentBranchNo = parentBranchNo;
-	if(branchWeights!=NULL)
-		nd->branchWeights = (*branchWeights);
-	ptpTree->treeNodes.push_back(nd);
-	nd->nodeValue = nodeValue;
-}
-
-LPTPNode* LvrPTPTreeSampling::addTreeNode(NodeType nodeType,int nodeId, int parentId, int parentBranchNo,int powerFactor,LogDouble nodeValue)
-{
-	LPTPNode* nd = new LPTPNode();
-	nd->type = nodeType;
-	nd->id = nodeId;
-	nd->parentId = parentId;
-	nd->parentBranchNo = parentBranchNo;
-	nd->powerFactor = powerFactor;
-	nd->nodeValue = nodeValue;
-	ptpTree->treeNodes.push_back(nd);
-	return nd;
-}
-
-void LvrPTPTreeSampling::sampleTree(LPTPNode* node,vector<map<int,int>* >& addedDecompMappings)
-{
-	if(node->type == ESPLIT)
-	{
-		//sample atom to obtain assignment
[…]

### 2023-06-07 solvers/alchemy/src/liftedinfer/common/src/mathutils.cpp

@@ -1,131 +1,0 @@
-#include "mathutils.h"
-#include "randomgenutil.h"
-#include <algorithm>
-using namespace std;
-
-LMathUtils* LMathUtils::m_pInstance = NULL;
-
-LMathUtils* LMathUtils::Instance()
-{
-   if (!m_pInstance)
-      m_pInstance = new LMathUtils;
-   return m_pInstance;
-}
-
-LMathUtils::LMathUtils()
-{
-	constructMatrix();
-	computeDistributionTable();
-}
-/*
-double LMathUtils::factorial(int n)
-{
-	if(n==0)
-		return 1.0;
-	double fact = n;
-	for(int i=n-1;i>1;i--)
-	{
-		fact *= i;
-	}
-	return fact;
-}
-
-double LMathUtils::binomVal(int n,int r)
-{
-	double fact = factorial(n)/(factorial(n-r)*factorial(r));	
-	return fact;
-}
-*/
-void LMathUtils::constructMatrix()
-{
-	binaryCoeffMatrix.resize(MAXCOEFFTABLESIZE + 1);
-	for(unsigned int n=0;n<=MAXCOEFFTABLESIZE;n++)
-	{
-		binaryCoeffMatrix[n].resize(n+1);
-		for(unsigned int i=0;i<=n;i++)
-		{
-			binaryCoeffMatrix[n].at(i) = LogDouble::Binomial(n,i);
-		}
-	}
-}
-
-LogDouble LMathUtils::getCoeff(int n,int i)
-{
-	if(i > n)
-		return LogDouble(0,false);
-	if(n > MAXCOEFFTABLESIZE)
-	{
-		//compute the value
-		return LogDouble::Binomial(n,i);
-	}
-	else
-		return binaryCoeffMatrix[n].at(i);
-}
-
-void LMathUtils::computeCumulativeDistribution(int domainSize,vector<LogDouble>& cdf)
-{
-	LogDouble norm_const(0,false);
-	cdf.resize(domainSize+1);
-	vector<LogDouble> prob(domainSize+1);
-	for(unsigned int j=0;j<=domainSize;j++)
-	{
-		cdf[j] = getCoeff(domainSize,j);
-		norm_const += cdf[j];
-	}
-	cdf[0] = cdf[0]/norm_const;
-	for(unsigned int j=1;j<cdf.size()-1;j++)
-	{
-		cdf[j] = cdf[j]/norm_const;
[…]

### 2023-06-07 solvers/alchemy/src/liftedinfer/common/src/randomgenutil.cpp

@@ -1,29 +1,0 @@
-#include "randomgenutil.h"
-#include <time.h>
-#include <stdlib.h>
-LvRandomGenUtil* LvRandomGenUtil::m_pInstance = NULL;
-
-LvRandomGenUtil* LvRandomGenUtil::Instance()
-{
-	if(!m_pInstance)
-	{
-		m_pInstance = new LvRandomGenUtil();
-	}
-	return m_pInstance;
-}
-
-LvRandomGenUtil::LvRandomGenUtil()
-{
-	srand(time(NULL));
-	//srand(2350877);
-}
-
-int LvRandomGenUtil::getRandomPosition(int maxSize)
-{
-	return rand()%maxSize;
-}
-
-double LvRandomGenUtil::getNormRand()
-{
-	return (double)rand()/(double)RAND_MAX;
-}

### 2023-06-07 solvers/alchemy/src/liftedinfer/common/src/samplingalgs.cpp

@@ -1,103 +1,0 @@
-#include "samplingalgs.h"
-#include "mathutils.h"
-#include "randomgenutil.h"
-#include <algorithm>
-using namespace std;
-
-LSamplingAlgs* LSamplingAlgs::m_pInstance = NULL;
-
-LSamplingAlgs* LSamplingAlgs::Instance()
-{
-   if (!m_pInstance)
-      m_pInstance = new LSamplingAlgs;
-   return m_pInstance;
-}
-
-LSamplingAlgs::LSamplingAlgs()
-{
-}
-
-void LSamplingAlgs::sample(int domainSize,int numValuesToSample,LogDouble& sampleWeight,
-	vector<int>& sampledValues,ESamplingMode samplingMode, LProposalDistributionElement* lpe)
-{
-	switch(samplingMode) 
-	{
-		case EUNIFORM:
-		{
-				LogDouble binCoeff(1,false);
-				for(unsigned int i=0;i<numValuesToSample;i++)
-				{
-					sampledValues.push_back(LvRandomGenUtil::Instance()->getRandomPosition(domainSize + 1));
-					LogDouble b = LMathUtils::Instance()->getCoeff(domainSize,sampledValues[i]);
-					binCoeff *= b;
-				}
-				double p = (double)numValuesToSample/(double)(domainSize + 1);
-				sampleWeight = binCoeff/LogDouble(p,false);
-				break;
-		}
-		case EBINOMIAL:
-		{
-			LogDouble prob(1,false);
-			LogDouble binCoeff(1,false);
-			for(int i=0;i<numValuesToSample;i++)
-			{
-				LogDouble p(1,false);
-				int val;
-				LMathUtils::Instance()->sample(domainSize,p,val);
-				prob *= p;
-				if(val<0)
-					val = 0;
-				sampledValues.push_back(val);
-				LogDouble b = LMathUtils::Instance()->getCoeff(domainSize,sampledValues[i]);
-				binCoeff *= b;
-			}
-			sampleWeight = binCoeff/prob;
-			break;
-		}
-		default:
-		{
-			if(lpe!=NULL)
-			{
-				LogDouble binCoeff(1,false);
-				LogDouble prob(1,false);
-				if(samplingMode == EINFORMED)
-					lpe->sample(prob,sampledValues,domainSize);
-				else
-					lpe->sample(prob,sampledValues);
-				if(sampledValues.size() < numValuesToSample)
-				{
-					int currSize = sampledValues.size();
[…]

### 2023-06-07 solvers/alchemy/src/liftedinfer/common/src/setutils.h

@@ -1,138 +1,0 @@
-/***************************************************************************
-*   Copyright (C) 2004 by Vibhav Gogate                                   *
-*   vgogate@ics.uci.edu                                                   *
-*                                                                         *
-*   This program is free software; you can redistribute it and/or modify  *
-*   it under the terms of the GNU General Public License as published by  *
-*   the Free Software Foundation; either version 2 of the License, or     *
-*   (at your option) any later version.                                   *
-*                                                                         *
-*   This program is distributed in the hope that it will be useful,       *
-*   but WITHOUT ANY WARRANTY; without even the implied warranty of        *
-*   MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the         *
-*   GNU General Public License for more details.                          *
-*                                                                         *
-*   You should have received a copy of the GNU General Public License     *
-*   along with this program; if not, write to the                         *
-*   Free Software Foundation, Inc.,                                       *
-*   59 Temple Place - Suite 330, Boston, MA  02111-1307, USA.             *
-**************************************************************************/
-#ifndef UTIL_HPP
-#define UTIL_HPP
-#include <iostream>
-#include <vector>
-#include <algorithm>
-
-
-using namespace std;
-
-template<typename _Classname>
-void do_set_union(const vector<_Classname> &a, const vector<_Classname> &b, vector<_Classname> &c_)
-{
-	vector<_Classname> c;
-	c.resize(a.size()+b.size());
-	typename vector<_Classname>::iterator curr,last;
-	last=c.end();
-	curr=set_union(a.begin(),a.end(),b.begin(),b.end(),c.begin());
-	c.erase(curr,last);
-	c_=c;
-}
-
-template<typename _Classname, typename _Compare>
-void do_set_union(const vector<_Classname> &a, const vector<_Classname> &b, vector<_Classname> &c_,_Compare comp)
-{
-	vector<_Classname> c;
-	c.resize(a.size()+b.size());
[…]

### 2023-06-07 solvers/alchemy/src/liftedinfer/liftedblockedgibbs/includes/lbgsampler.h

@@ -1,48 +1,0 @@
-#ifndef __LBGSAMPLER_H
-#define __LBGSAMPLER_H
-#include "lvrmln.h"
-#include "ptpsampler.h"
-#include "lvparams.h"
-#include "lvrcluster.h"
-
-struct LBGSampler
-{
-	LBGSampler(LvrMLN& mln_):mln(mln_)
-	{
-		clusterLevel = -1;
-		originalNumPredicates = -1;
-		numTimesSampled = 0;
-		iterationsSinceLastMerge = 0;
-		iterationsAcrossCalls = 0;
-		lp = new LPTPSampler(mln);
-	}
-	~LBGSampler()
-	{
-		cleanup(LVRClusterList);
-		delete lp;
-	}
-	void startLVBGibbs(LvrParams* params);
-private:
-	int clusterLevel;
-	int originalNumPredicates;
-	int numTimesSampled;
-	int windowSize;
-	int iterationsSinceLastMerge;
-	//used in weight learning only, since called multiple times
-	int iterationsAcrossCalls;
-	LPTPSampler* lp;
-	vector<LVRCluster*> LVRClusterList;
-	LvrMLN& mln;
-	bool useEvidenceCaching;
-	void mergeCluster(int clusterId1,int clusterId2);
-	void computeClusterLiftedSharings();
-	int getClusterIndex(LVRCluster* cluster);
-	void initializeClusters();
-	void computeClusterMB();	
-	void addPTPEvidence(int clusterIndex,vector<WClause*>& newClauses, bool storeEvidence=false);
-	void getAtomsMatchingTerm(Atom* atom, int termIndex, vector<Atom*>& matchingMLNAtoms);
-	void groundClusterWithMB(int clusterIndex,vector<WClause*>& newClauses);
-};
-
-
-#endif

### 2023-06-07 solvers/alchemy/src/liftedinfer/liftedblockedgibbs/src/ptpsampler.cpp

@@ -1,156 +1,0 @@
-#include "ptpsampler.h"
-#include <fstream>
-using namespace std;
-#include "lvrpermutations.h"
-#include "queryupdater.h"
-
-
-LPTPSampler::LPTPSampler(LvrMLN& mln)
-{
-	ls= new LBlockExactInference(mln);
-}
-
-LPTPSampler::~LPTPSampler()
-{
-	delete ls;
-}
-
-
-int LPTPSampler::runMockPTP(vector<WClause*>& CNF,LVRCluster* lvrCluster,int& lvpCost,int remainingCost)
-{
-	return ls->doMockInferenceOnCluster(CNF,lvpCost,remainingCost);
-}
-
-int LPTPSampler::runPTP(vector<WClause*>& CNF,LVRCluster* lvrCluster)
-{
-	if(lvrCluster->isUniConstantCluster())
-	{
-		doLightWeightSampling(lvrCluster,CNF);
-		return 0;
-	}
-	int ret = ls->doExactInferenceOnCluster(CNF);
-	if( ret <= 0)
-		return ret;
-	lvrCluster->resetAllAssignments();	
-	for(unsigned int i=0;i<ls->getPTPTreeRef().sampledAssignments.atoms.size();i++)
-	{
-		int ind = lvrCluster->getEquivalentElementIndex(ls->getPTPTreeRef().sampledAssignments.atoms[i]);
-		if(ind==-1)
-			continue;
-		for(unsigned int j=0;j<lvrCluster->lAssignments[ind].size();j++)
-		{
-			bool match = true;
-			for(unsigned int k=0;k<lvrCluster->sharedGroundedPositions[ind].size();k++)
-			{
-				if(ls->getPTPTreeRef().sampledAssignments.atoms[i]->terms[lvrCluster->sharedGroundedPositions[ind].at(k)]->domain[0] !=
-					lvrCluster->lAssignments[ind].at(j)->grounding[lvrCluster->sharedGroundedPositions[ind].at(k)])
-				{
-					match = false;
-					break;
-				}
-			}
-			if(match)
-			{
-				if(lvrCluster->lAssignments[ind].at(j)->nTrueValues == -1)
-				{
-					lvrCluster->lAssignments[ind].at(j)->nTrueValues = ls->getPTPTreeRef().sampledAssignments.assignment[i];
-					lvrCluster->lAssignments[ind].at(j)->nFalseValues = lvrCluster->lAssignments[ind].at(j)->nFalseValues
[…]

### 2023-06-07 solvers/alchemy/src/liftedinfer/liftedimportancesampling/includes/importancedistribution.h

@@ -1,18 +1,0 @@
-#ifndef __LVRIMPORTANCE_DISTRIBUTION
-#define __LVRIMPORTANCE_DISTRIBUTION
-#include <map>
-#include <vector>
-using namespace std;
-struct LvrDistributionElement
-{
-	map<int,vector<double> > distributionElement;
-};
-struct LvrImportanceDistribution
-{
-	map<int,map<int,vector<LvrDistributionElement*> > distributions;
-	LvrImportanceDistribution(){}
-	~LvrImportanceDistribution(){}
-
-
-};
-#endif

### 2023-06-07 solvers/alchemy/src/liftedinfer/liftedimportancesampling/includes/lisapproxinference.h

@@ -1,62 +1,0 @@
-#ifndef LIS_APPROX_INFERENCE_H_
-#define LIS_APPROX_INFERENCE_H_
-
-#include <vector>
-#include <iostream>
-#include <set>
-#include <map>
-using namespace std;
-#include "lvrmln.h"
-#include "decomposer.h"
-#include "propositionalresolution.h"
-#include "logdouble.h"
-#include "extensions.h"
-#include "heuristics.h"
-#include "normalizer.h"
-#include "clusterutil.h"
-#include "proposalstructure.h"
-#include "lvrnormpropagation.h"
-#include "lvrsingletonnormpropagation.h"
-#include "lvparams.h"
-
-struct LISApproxInference
-{
-	void setSamplingMode(ESamplingMode samplingMode_)
-	{
-		samplingMode = samplingMode_;
-	}
-	void setProposalDistribution(LProposalDistribution* distribution_)
-	{
-		distribution = distribution_;
-	}
-	LISApproxInference(LvrMLN& mln);
-	~LISApproxInference()
-	{
-		delete decomposer;
-		delete heuristics;
-		delete lvrNormPropagate;
-	}
-	LogDouble doLvApproxPartitionInformed(vector<WClause*>& CNF);
-	LogDouble doLvApproxPartitionInformedV1(vector<WClause*>& CNF);
-	LogDouble doLvApproxPartitionBinomial(vector<WClause*>& CNF);
-	void estimateApproxMarginals(LvrParams* params, LProposalDistribution* distribution = NULL);
-	LogDouble estimatePartitionFunction(LvrParams* params,LProposalDistribution* distribution= NULL);
-	Atom* selectAtomToCondition(vector<WClause*> clauses)
-	{
-		return heuristics->getAtomToSplit(clauses);
-	}
-	bool decomposeCNF(vector<WClause*>& CNF,int& powerFactor);
-
-private:
-	LvrMLN& mln;
-	LDecomposer* decomposer;
-	LHeuristics* heuristics;	
-	LvrNormPropagation* lvrNormPropagate;
-	ESamplingMode samplingMode;
-	//not owned
-	LProposalDistribution* distribution;
-
-	void seperateDisjointCNF(vector<WClause*> CNF, vector<vector<WClause*> >& disjointCNFList);
-	LogDouble CNFWeight(vector<WClause*>& CNF);
-};
-#endif

### 2023-06-07 solvers/alchemy/src/liftedinfer/liftedimportancesampling/includes/proposalconstructor.h

@@ -1,39 +1,0 @@
-#ifndef __LPROPOSAL_CONSTRUCTOR
-#define __LPROPOSAL_CONSTRUCTOR
-#include "lvrmln.h"
-#include "proposalstructure.h"
-#include "cleanuputils.h"
-#include "normalizer.h"
-#include "clusterutil.h"
-#include "filedump.h"
-#include "ptpsearch.h"
-#include "heuristics.h"
-#include "rulesutil.h"
-#include "lisapproxinference.h"
-#include "lvrnormpropagation.h"
-#include "lvparams.h"
-
-
-struct LProposalConstructor
-{
-LProposalConstructor(LvrMLN& mln_);
-~LProposalConstructor();
-void getParents(vector<WClause*> clauses,Atom* atom, vector<Atom*> potentialParents,vector<Atom*>& parents);
-void constructProposal(vector<WClause*>& clauses,vector<Atom*>& potentialParents);
-void constructProposalV1(vector<WClause*>& CNF,vector<Atom*>& potentialParents);
-void print(){}
-void startConstruction(LvrParams* params);
-void startMARInference(LvrParams* params);
-void startPartitionFunction(LvrParams* params);
-void readDistributionFromDumpFile();
-void dumpDistributionToDumpFile();
-private:
-LProposalDistribution* lpd;
-LvrMLN& mln;
-LClusterUtil* lc;
-LISApproxInference* lsearch;
-LvrNormPropagation* lpg;
-LvrSingletonNormPropagation* lvrSingletonNormPropagation;
-};
-
-#endif

### 2023-06-07 solvers/alchemy/src/liftedinfer/liftedimportancesampling/includes/proposalstructure.h

@@ -1,64 +1,0 @@
-#ifndef __LPROPOSAL_STRUCTURE
-#define __LPROPOSAL_STRUCTURE
-#include "lvrmln.h"
-#include "lvratomhashtemplate.h"
-#include "lvparams.h"
-
-struct LProposalTable
-{
-	LogDouble sampledProbability;
-	int sampledValue;	
-	LProposalTable(int parentsSize,int maxTruthValue_);
-	void updateDistribution(double learningRate);
-	void sampleDistribution(int index);
-	void printDistribution();
-	int getTableSize(int index);
-	LogDouble getDistributionValue(int index,int numTrue);
-	LogDouble getNormConstant(int index);
-private:
-	vector<vector<LogDouble> > distribution;
-	vector<vector<int> > adaptiveMLECounter;
-	vector<int> totalSamplesCollected;
-	int maxTruthValue;
-	vector<LogDouble> normConstants;
-};
-
-struct LProposalDistributionElement
-{
-	LProposalDistributionElement(Atom* atom_,vector<LProposalDistributionElement*> parents_,
-		vector<bool> isolatedTerms_,int id_);
-	~LProposalDistributionElement();
-	void initializeProposalTables();
-	void sample(LogDouble& prob,vector<int>& sampledValues,int domainSize = -1);
-	void print();
-	void updateProposals(double learningRate);
-
-	Atom* atom;
-	int id;
-	vector<LProposalTable*> proposalTables;
-	vector<bool> isolatedTerms;
-	//do not delete pointers
-	vector<LProposalDistributionElement*> parents;
-	int nTrueValues;
-	LogDouble probability;
-
-};
-
-
-struct LProposalDistribution
-{
-	LProposalDistribution(ESamplingMode samplingMode_);
-	~LProposalDistribution();
-	LProposalDistributionElement* insertElement(Atom* atom, vector<Atom*> parents,vector<bool> isolatedTerms);
-	void updateDistributions(double learningRate);
-	LProposalDistributionElement* findElement(Atom* atom);
-	void dumpDistributionToFile();
-	void readDistributionFromDumpFile();
-	void print();
-private:
-	int counter;
-	LvrAtomHashTemplate<LProposalDistributionElement*>* hashedDistributions;
-	ESamplingMode samplingMode;
-};
-
-#endif

### 2023-06-07 solvers/alchemy/src/liftedinfer/liftedimportancesampling/src/lisapproxinference.cpp

@@ -1,567 +1,0 @@
-#include "lisapproxinference.h"
-#include "cleanuputils.h"
-#include "rulesutil.h"
-#include <time.h>
-#include "mathutils.h"
-#include "samplingalgs.h"
-#include "queryupdater.h"
-
-
-LogDouble LISApproxInference::CNFWeight(vector<WClause*>& CNF)
-{
-	/*for(unsigned int i=0;i<CNF.size();i++)
-	{
-		if(CNF[i]->satisfied)
-			cout<<"Satisfied v";
-		CNF[i]->print();
-	}
-	*/
-	vector<Atom*> removedAtoms;
-	set<int> completedIds;
-	LogDouble totalWeight(1,false);
-	vector<WClause*> remainingCNF;
-	for(unsigned int i=0;i<CNF.size();i++)
-	{
-		if(CNF[i]->satisfied)
-		{
-			for(unsigned int j=0;j<CNF[i]->atoms.size();j++)
-			{
-				if(completedIds.count(CNF[i]->atoms[j]->symbol->id) == 0)
-				{
-					removedAtoms.push_back(CNF[i]->atoms[j]);
-					completedIds.insert(CNF[i]->atoms[j]->symbol->id);
-				}
-				
-			}
-			//get weight of formula
-			set<LvrTerm*> terms;
-			for(unsigned int kk=0;kk<CNF[i]->atoms.size();kk++)
-			{
-				for(unsigned int mm=0;mm<CNF[i]->atoms[kk]->terms.size();mm++)
-				{
-					terms.insert(CNF[i]->atoms[kk]->terms[mm]);
-				}
-			}
-			int sz=1;
-			for(set<LvrTerm*>::iterator it=terms.begin();it!=terms.end();it++)
-			{
-				sz *= (*it)->domain.size();
-			}
-			//totalWeight += CNF[i]->weight*LogDouble(sz,false);
-			//if(!CNF[i]->weight.is_zero)
-			{
-				LogDouble tmpL = CNF[i]->weight*LogDouble(sz,false);
-				double tmp = exp(tmpL.value);
-				LogDouble newWt(tmp,true);
-				totalWeight *= newWt;
-			}
-		}
-		else
-		{
-			remainingCNF.push_back(LvrMLN::create_new_clause(CNF[i]));
-		}
-		
-	}
-	int totalDontcare = 0;
[…]

### 2023-06-07 solvers/alchemy/src/liftedinfer/liftedweightedmodelcounting/includes/resolver.h

@@ -1,18 +1,0 @@
-#ifndef __LRESOLVER__
-#define __LRESOLVER__
-#include "lvrmln.h"
-struct LResolver
-{
-	void getMatchingTerms(WClause* clause,Atom* atom, vector<LvrTerm*>& terms);
-	void permute(vector<LvrTerm*> terms, vector<vector<int> >& permutedDomainList);
-	int getIndex(vector<vector<int> > allGroundings, Atom* groundedAtom);
-	void resolveGroundClause(WClause* clause,int predicateId, vector<int> truthVector, 
-		vector<vector<int> > allGroundings, WClause& resolvedClause);
-	void doFullGrounding(vector<WClause*> CNF,Atom* atom,vector<WClause*>& groundCNF,
-		vector<vector<int> >& allGroundings,int& numGroundings);
-	void reduceDomains(WClause* clause, Atom* atom, vector<int> truthValues, 
-		vector<WClause*>& domainModifiedClauses, int singletonIndex);
-	void reduceDomainsSelfJoins(WClause* clause, Atom* atom, vector<int> truthValues, 
-		vector<WClause*>& domainModifiedClauses, int singletonIndex);
-};
-#endif

### 2023-06-07 solvers/alchemy/src/liftedinfer/liftedweightedmodelcounting/src/cache.cpp

@@ -1,191 +1,0 @@
-#include "cache.h"
-#include "cleanuputils.h"
-
-LCacheEntry::LCacheEntry(vector<WClause*> CNF_,LogDouble wCount_):wCount(wCount_),deleteFlag(false),hits(0)
-{
-	//store a copy
-	LvrMLN::copyAllClauses(CNF_,CNF);
-}
-
-LCacheEntry::~LCacheEntry()
-{
-	cleanup(CNF);
-}
-
-
-LCache::LCache(LvrMLN& mln_,int cacheSize_):mln(mln_),currentIndex(0),successfulHits(0),misses(0),hits(0),numEntries(0),mostRecentCounter(0)
-{
-	cout<<"Initializing cache with size = "<<cacheSize_<<endl;
-	cacheEntries.resize(cacheSize_);
-	for(unsigned int i=0;i<cacheEntries.size();i++)
-	{
-		cacheEntries[i] = NULL;
-	}
-	unifier = new LUnifier(mln);
-	mostRecentList.resize(MOSTRECENTSIZE);
-	cacheIndex.resize(MAXCNFSIZE);
-}
-LCache::~LCache()
-{
-	cleanup(cacheEntries);
-	cacheIndex.clear();
-	delete unifier;
-}
-
-bool LCache::addToCache(vector<WClause*> CNF, LogDouble wCount)
-{
-	if(CNF.size() > MAXCNFSIZE || CNF.size() == 0)
-		return false;
-	if(!isFull())
-	{
-	for(unsigned int i=0;i<cacheEntries.size();i++)
-	{
-		if(cacheEntries[i] == NULL)
-		{
-			LCacheEntry* lc = new LCacheEntry(CNF,wCount);
-			cacheEntries[i] = lc;
-			numEntries++;
-			if(mostRecentCounter >= MOSTRECENTSIZE)
-				mostRecentCounter = 0;
-			mostRecentList[mostRecentCounter++] = i;
-			if(isFull())
-			{
-				misses = 0;
-				hits = 0;
-			}
-			cacheIndex[CNF.size()-1].push_back(cacheEntries[i]);
-			break;
-		}
-	}
-	}
-
-	return true;
-}
-
-bool LCache::findInCache(vector<WClause*> CNF, LogDouble& val)
-{
-	if(CNF.size() > MAXCNFSIZE || CNF.size() == 0)
-		return false;
-	//for(unsigned int i=0;i<currentIndex;i++)
[…]

### 2023-06-07 solvers/alchemy/src/liftedinfer/liftedweightedmodelcounting/src/splitter.cpp

@@ -1,207 +1,0 @@
-#include "splitter.h"
-#include "cleanuputils.h"
-
-LSplitter::LSplitter()
-{
-	sampler = new LSampler();
-	resolver = new LResolver();
-}
-
-LSplitter::~LSplitter()
-{
-	delete sampler;
-	delete resolver;
-}
-
-void LSplitter::doFullGrounding(vector<WClause*> CNF,Atom* atom,vector<WClause*>& groundCNF,
-			vector<vector<int> >& allGroundings,int& numGroundings)
-{
-	resolver->doFullGrounding(CNF,atom,groundCNF,allGroundings,numGroundings);
-}
-
-void LSplitter::doCompleteSplitInChunks(vector<WClause*> groundCNF,int atomId, vector<vector<int> > allGroundings, int numGroundings,
-	vector<vector<WClause*> >& resolvedCNFList,int startnum, int chunkSize,bool& done)
-{
-
-	vector<int> binVector(numGroundings);
-	for(unsigned int i=0;i<numGroundings;i++)
-	{
-		binVector[i] = 0;
-	}
-	int mask = 1;
-	int iter=numGroundings-1;
-	while(startnum)
-	{
-		int x = startnum & mask;
-		binVector[iter--] = x;
-		startnum = startnum >> 1;
-
-	}
-	iter = 0;
-	
-	while(1)
-	{
-		vector<WClause*> resolvedCNF;
-		for(unsigned int i=0;i<groundCNF.size();i++)
-		{
-			WClause* resolvedClause=LvrMLN::create_new_clause(groundCNF[i]);
-			resolver->resolveGroundClause(groundCNF[i],atomId,binVector,allGroundings,*resolvedClause);
-			resolvedCNF.push_back(resolvedClause);
-		}
-		resolvedCNFList.push_back(resolvedCNF);
-		int ind = binVector.size()-1;
-		binVector[ind]++;
-		while(binVector[ind] == 2)
-		{
-			binVector[ind]=0;
-			if((ind-1) >= 0)
-				binVector[ind-1]++;
-			else
-			{
-				done=true;
-				break;
-			}
-			ind--;
-		}
-		iter++;
-		//reached chunk size assignments
-		if(iter == chunkSize)
-			break;
-		//reached the end of all assignments
-		if(done)
-			break;
-	}
-	
-}
-
[…]

### 2023-06-07 solvers/alchemy/src/logic/clause.cpp

@@ -1,883 +1,0 @@
-/*
- * All of the documentation and software included in the
- * Alchemy Software is copyrighted by Stanley Kok, Parag
- * Singla, Matthew Richardson, Pedro Domingos, Marc
- * Sumner, Hoifung Poon, Daniel Lowd, and Jue Wang.
- * 
- * Copyright [2004-09] Stanley Kok, Parag Singla, Matthew
- * Richardson, Pedro Domingos, Marc Sumner, Hoifung
- * Poon, Daniel Lowd, and Jue Wang. All rights reserved.
- * 
- * Contact: Pedro Domingos, University of Washington
- * (pedrod@cs.washington.edu).
- * 
- * Redistribution and use in source and binary forms, with
- * or without modification, are permitted provided that
- * the following conditions are met:
- * 
- * 1. Redistributions of source code must retain the above
- * copyright notice, this list of conditions and the
- * following disclaimer.
- * 
- * 2. Redistributions in binary form must reproduce the
- * above copyright notice, this list of conditions and the
- * following disclaimer in the documentation and/or other
- * materials provided with the distribution.
- * 
- * 3. All advertising materials mentioning features or use
- * of this software must display the following
- * acknowledgment: "This product includes software
- * developed by Stanley Kok, Parag Singla, Matthew
- * Richardson, Pedro Domingos, Marc Sumner, Hoifung
- * Poon, Daniel Lowd, and Jue Wang in the Department of
- * Computer Science and Engineering at the University of
- * Washington".
- * 
- * 4. Your publications acknowledge the use or
- * contribution made by the Software to your research
- * using the following citation(s): 
- * Stanley Kok, Parag Singla, Matthew Richardson and
- * Pedro Domingos (2005). "The Alchemy System for
- * Statistical Relational AI", Technical Report,
- * Department of Computer Science and Engineering,
- * University of Washington, Seattle, WA.
- * http://alchemy.cs.washington.edu.
- * 
- * 5. Neither the name of the University of Washington nor
- * the names of its contributors may be used to endorse or
- * promote products derived from this software without
- * specific prior written permission.
- * 
- * THIS SOFTWARE IS PROVIDED BY THE UNIVERSITY OF WASHINGTON
- * AND CONTRIBUTORS "AS IS" AND ANY EXPRESS OR IMPLIED
[…]

### 2023-06-07 solvers/alchemy/src/logic/mlnhelper.h

@@ -1,194 +1,0 @@
-/*
- * All of the documentation and software included in the
- * Alchemy Software is copyrighted by Stanley Kok, Parag
- * Singla, Matthew Richardson, Pedro Domingos, Marc
- * Sumner, Hoifung Poon, Daniel Lowd, and Jue Wang.
- * 
- * Copyright [2004-09] Stanley Kok, Parag Singla, Matthew
- * Richardson, Pedro Domingos, Marc Sumner, Hoifung
- * Poon, Daniel Lowd, and Jue Wang. All rights reserved.
- * 
- * Contact: Pedro Domingos, University of Washington
- * (pedrod@cs.washington.edu).
- * 
- * Redistribution and use in source and binary forms, with
- * or without modification, are permitted provided that
- * the following conditions are met:
- * 
- * 1. Redistributions of source code must retain the above
- * copyright notice, this list of conditions and the
- * following disclaimer.
- * 
- * 2. Redistributions in binary form must reproduce the
- * above copyright notice, this list of conditions and the
- * following disclaimer in the documentation and/or other
- * materials provided with the distribution.
- * 
- * 3. All advertising materials mentioning features or use
- * of this software must display the following
- * acknowledgment: "This product includes software
- * developed by Stanley Kok, Parag Singla, Matthew
- * Richardson, Pedro Domingos, Marc Sumner, Hoifung
- * Poon, Daniel Lowd, and Jue Wang in the Department of
- * Computer Science and Engineering at the University of
- * Washington".
- * 
- * 4. Your publications acknowledge the use or
- * contribution made by the Software to your research
- * using the following citation(s): 
- * Stanley Kok, Parag Singla, Matthew Richardson and
- * Pedro Domingos (2005). "The Alchemy System for
- * Statistical Relational AI", Technical Report,
- * Department of Computer Science and Engineering,
- * University of Washington, Seattle, WA.
- * http://alchemy.cs.washington.edu.
- * 
- * 5. Neither the name of the University of Washington nor
- * the names of its contributors may be used to endorse or
[…]

### 2023-06-07 solvers/alchemy/src/logic/variablestate.h

@@ -1,3411 +1,0 @@
-/*
- * All of the documentation and software included in the
- * Alchemy Software is copyrighted by Stanley Kok, Parag
- * Singla, Matthew Richardson, Pedro Domingos, Marc
- * Sumner, Hoifung Poon, Daniel Lowd, and Jue Wang.
- * 
- * Copyright [2004-09] Stanley Kok, Parag Singla, Matthew
- * Richardson, Pedro Domingos, Marc Sumner, Hoifung
- * Poon, Daniel Lowd, and Jue Wang. All rights reserved.
- * 
- * Contact: Pedro Domingos, University of Washington
- * (pedrod@cs.washington.edu).
- * 
- * Redistribution and use in source and binary forms, with
- * or without modification, are permitted provided that
- * the following conditions are met:
- * 
- * 1. Redistributions of source code must retain the above
- * copyright notice, this list of conditions and the
- * following disclaimer.
- * 
- * 2. Redistributions in binary form must reproduce the
- * above copyright notice, this list of conditions and the
- * following disclaimer in the documentation and/or other
- * materials provided with the distribution.
- * 
- * 3. All advertising materials mentioning features or use
- * of this software must display the following
- * acknowledgment: "This product includes software
- * developed by Stanley Kok, Parag Singla, Matthew
- * Richardson, Pedro Domingos, Marc Sumner, Hoifung
- * Poon, Daniel Lowd, and Jue Wang in the Department of
- * Computer Science and Engineering at the University of
- * Washington".
- * 
- * 4. Your publications acknowledge the use or
- * contribution made by the Software to your research
- * using the following citation(s): 
- * Stanley Kok, Parag Singla, Matthew Richardson and
- * Pedro Domingos (2005). "The Alchemy System for
- * Statistical Relational AI", Technical Report,
- * Department of Computer Science and Engineering,
- * University of Washington, Seattle, WA.
- * http://alchemy.cs.washington.edu.
- * 
- * 5. Neither the name of the University of Washington nor
- * the names of its contributors may be used to endorse or
- * promote products derived from this software without
- * specific prior written permission.
- * 
- * THIS SOFTWARE IS PROVIDED BY THE UNIVERSITY OF WASHINGTON
[…]

### 2023-06-07 solvers/alchemy/src/util/array.h

@@ -1,686 +1,0 @@
-/*
- * All of the documentation and software included in the
- * Alchemy Software is copyrighted by Stanley Kok, Parag
- * Singla, Matthew Richardson, Pedro Domingos, Marc
- * Sumner, Hoifung Poon, and Daniel Lowd.
- * 
- * Copyright [2004-07] Stanley Kok, Parag Singla, Matthew
- * Richardson, Pedro Domingos, Marc Sumner, Hoifung
- * Poon, and Daniel Lowd. All rights reserved.
- * 
- * Contact: Pedro Domingos, University of Washington
- * (pedrod@cs.washington.edu).
- * 
- * Redistribution and use in source and binary forms, with
- * or without modification, are permitted provided that
- * the following conditions are met:
- * 
- * 1. Redistributions of source code must retain the above
- * copyright notice, this list of conditions and the
- * following disclaimer.
- * 
- * 2. Redistributions in binary form must reproduce the
- * above copyright notice, this list of conditions and the
- * following disclaimer in the documentation and/or other
- * materials provided with the distribution.
- * 
- * 3. All advertising materials mentioning features or use
- * of this software must display the following
- * acknowledgment: "This product includes software
- * developed by Stanley Kok, Parag Singla, Matthew
- * Richardson, Pedro Domingos, Marc Sumner, Hoifung
- * Poon, and Daniel Lowd in the Department of Computer Science and
- * Engineering at the University of Washington".
- * 
- * 4. Your publications acknowledge the use or
- * contribution made by the Software to your research
- * using the following citation(s): 
- * Stanley Kok, Parag Singla, Matthew Richardson and
- * Pedro Domingos (2005). "The Alchemy System for
- * Statistical Relational AI", Technical Report,
- * Department of Computer Science and Engineering,
- * University of Washington, Seattle, WA.
- * http://www.cs.washington.edu/ai/alchemy.
- * 
- * 5. Neither the name of the University of Washington nor
- * the names of its contributors may be used to endorse or
- * promote products derived from this software without
- * specific prior written permission.
- * 
[…]

### 2023-06-07 solvers/alchemy/src/util/dualmap.h

@@ -1,171 +1,0 @@
-/*
- * All of the documentation and software included in the
- * Alchemy Software is copyrighted by Stanley Kok, Parag
- * Singla, Matthew Richardson, Pedro Domingos, Marc
- * Sumner, Hoifung Poon, and Daniel Lowd.
- * 
- * Copyright [2004-07] Stanley Kok, Parag Singla, Matthew
- * Richardson, Pedro Domingos, Marc Sumner, Hoifung
- * Poon, and Daniel Lowd. All rights reserved.
- * 
- * Contact: Pedro Domingos, University of Washington
- * (pedrod@cs.washington.edu).
- * 
- * Redistribution and use in source and binary forms, with
- * or without modification, are permitted provided that
- * the following conditions are met:
- * 
- * 1. Redistributions of source code must retain the above
- * copyright notice, this list of conditions and the
- * following disclaimer.
- * 
- * 2. Redistributions in binary form must reproduce the
- * above copyright notice, this list of conditions and the
- * following disclaimer in the documentation and/or other
- * materials provided with the distribution.
- * 
- * 3. All advertising materials mentioning features or use
- * of this software must display the following
- * acknowledgment: "This product includes software
- * developed by Stanley Kok, Parag Singla, Matthew
- * Richardson, Pedro Domingos, Marc Sumner, Hoifung
- * Poon, and Daniel Lowd in the Department of Computer Science and
- * Engineering at the University of Washington".
- * 
- * 4. Your publications acknowledge the use or
- * contribution made by the Software to your research
- * using the following citation(s): 
- * Stanley Kok, Parag Singla, Matthew Richardson and
- * Pedro Domingos (2005). "The Alchemy System for
- * Statistical Relational AI", Technical Report,
- * Department of Computer Science and Engineering,
- * University of Washington, Seattle, WA.
- * http://www.cs.washington.edu/ai/alchemy.
- * 
- * 5. Neither the name of the University of Washington nor
- * the names of its contributors may be used to endorse or
- * promote products derived from this software without
[…]

### 2023-06-07 solvers/alchemy/src/util/equalstr.h

@@ -1,92 +1,0 @@
-/*
- * All of the documentation and software included in the
- * Alchemy Software is copyrighted by Stanley Kok, Parag
- * Singla, Matthew Richardson, Pedro Domingos, Marc
- * Sumner, Hoifung Poon, and Daniel Lowd.
- * 
- * Copyright [2004-07] Stanley Kok, Parag Singla, Matthew
- * Richardson, Pedro Domingos, Marc Sumner, Hoifung
- * Poon, and Daniel Lowd. All rights reserved.
- * 
- * Contact: Pedro Domingos, University of Washington
- * (pedrod@cs.washington.edu).
- * 
- * Redistribution and use in source and binary forms, with
- * or without modification, are permitted provided that
- * the following conditions are met:
- * 
- * 1. Redistributions of source code must retain the above
- * copyright notice, this list of conditions and the
- * following disclaimer.
- * 
- * 2. Redistributions in binary form must reproduce the
- * above copyright notice, this list of conditions and the
- * following disclaimer in the documentation and/or other
- * materials provided with the distribution.
- * 
- * 3. All advertising materials mentioning features or use
- * of this software must display the following
- * acknowledgment: "This product includes software
- * developed by Stanley Kok, Parag Singla, Matthew
- * Richardson, Pedro Domingos, Marc Sumner, Hoifung
- * Poon, and Daniel Lowd in the Department of Computer Science and
- * Engineering at the University of Washington".
- * 
- * 4. Your publications acknowledge the use or
- * contribution made by the Software to your research
- * using the following citation(s): 
- * Stanley Kok, Parag Singla, Matthew Richardson and
- * Pedro Domingos (2005). "The Alchemy System for
- * Statistical Relational AI", Technical Report,
- * Department of Computer Science and Engineering,
- * University of Washington, Seattle, WA.
- * http://www.cs.washington.edu/ai/alchemy.
- * 
- * 5. Neither the name of the University of Washington nor
- * the names of its contributors may be used to endorse or
[…]

### 2023-06-07 solvers/alchemy/src/util/hasharray.h

@@ -1,550 +1,0 @@
-/*
- * All of the documentation and software included in the
- * Alchemy Software is copyrighted by Stanley Kok, Parag
- * Singla, Matthew Richardson, Pedro Domingos, Marc
- * Sumner, Hoifung Poon, and Daniel Lowd.
- * 
- * Copyright [2004-07] Stanley Kok, Parag Singla, Matthew
- * Richardson, Pedro Domingos, Marc Sumner, Hoifung
- * Poon, and Daniel Lowd. All rights reserved.
- * 
- * Contact: Pedro Domingos, University of Washington
- * (pedrod@cs.washington.edu).
- * 
- * Redistribution and use in source and binary forms, with
- * or without modification, are permitted provided that
- * the following conditions are met:
- * 
- * 1. Redistributions of source code must retain the above
- * copyright notice, this list of conditions and the
- * following disclaimer.
- * 
- * 2. Redistributions in binary form must reproduce the
- * above copyright notice, this list of conditions and the
- * following disclaimer in the documentation and/or other
- * materials provided with the distribution.
- * 
- * 3. All advertising materials mentioning features or use
- * of this software must display the following
- * acknowledgment: "This product includes software
- * developed by Stanley Kok, Parag Singla, Matthew
- * Richardson, Pedro Domingos, Marc Sumner, Hoifung
- * Poon, and Daniel Lowd in the Department of Computer Science and
- * Engineering at the University of Washington".
- * 
- * 4. Your publications acknowledge the use or
- * contribution made by the Software to your research
- * using the following citation(s): 
- * Stanley Kok, Parag Singla, Matthew Richardson and
- * Pedro Domingos (2005). "The Alchemy System for
- * Statistical Relational AI", Technical Report,
- * Department of Computer Science and Engineering,
- * University of Washington, Seattle, WA.
- * http://www.cs.washington.edu/ai/alchemy.
- * 
- * 5. Neither the name of the University of Washington nor
- * the names of its contributors may be used to endorse or
- * promote products derived from this software without
- * specific prior written permission.
- * 
[…]

### 2023-06-07 solvers/alchemy/src/util/hashint.h

@@ -1,116 +1,0 @@
-/*
- * All of the documentation and software included in the
- * Alchemy Software is copyrighted by Stanley Kok, Parag
- * Singla, Matthew Richardson, Pedro Domingos, Marc
- * Sumner, Hoifung Poon, and Daniel Lowd.
- * 
- * Copyright [2004-07] Stanley Kok, Parag Singla, Matthew
- * Richardson, Pedro Domingos, Marc Sumner, Hoifung
- * Poon, and Daniel Lowd. All rights reserved.
- * 
- * Contact: Pedro Domingos, University of Washington
- * (pedrod@cs.washington.edu).
- * 
- * Redistribution and use in source and binary forms, with
- * or without modification, are permitted provided that
- * the following conditions are met:
- * 
- * 1. Redistributions of source code must retain the above
- * copyright notice, this list of conditions and the
- * following disclaimer.
- * 
- * 2. Redistributions in binary form must reproduce the
- * above copyright notice, this list of conditions and the
- * following disclaimer in the documentation and/or other
- * materials provided with the distribution.
- * 
- * 3. All advertising materials mentioning features or use
- * of this software must display the following
- * acknowledgment: "This product includes software
- * developed by Stanley Kok, Parag Singla, Matthew
- * Richardson, Pedro Domingos, Marc Sumner, Hoifung
- * Poon, and Daniel Lowd in the Department of Computer Science and
- * Engineering at the University of Washington".
- * 
- * 4. Your publications acknowledge the use or
- * contribution made by the Software to your research
- * using the following citation(s): 
- * Stanley Kok, Parag Singla, Matthew Richardson and
- * Pedro Domingos (2005). "The Alchemy System for
- * Statistical Relational AI", Technical Report,
- * Department of Computer Science and Engineering,
- * University of Washington, Seattle, WA.
- * http://www.cs.washington.edu/ai/alchemy.
- * 
- * 5. Neither the name of the University of Washington nor
- * the names of its contributors may be used to endorse or
[…]

### 2023-06-07 solvers/alchemy/src/util/hashstring.h

@@ -1,99 +1,0 @@
-/*
- * All of the documentation and software included in the
- * Alchemy Software is copyrighted by Stanley Kok, Parag
- * Singla, Matthew Richardson, Pedro Domingos, Marc
- * Sumner, Hoifung Poon, and Daniel Lowd.
- * 
- * Copyright [2004-07] Stanley Kok, Parag Singla, Matthew
- * Richardson, Pedro Domingos, Marc Sumner, Hoifung
- * Poon, and Daniel Lowd. All rights reserved.
- * 
- * Contact: Pedro Domingos, University of Washington
- * (pedrod@cs.washington.edu).
- * 
- * Redistribution and use in source and binary forms, with
- * or without modification, are permitted provided that
- * the following conditions are met:
- * 
- * 1. Redistributions of source code must retain the above
- * copyright notice, this list of conditions and the
- * following disclaimer.
- * 
- * 2. Redistributions in binary form must reproduce the
- * above copyright notice, this list of conditions and the
- * following disclaimer in the documentation and/or other
- * materials provided with the distribution.
- * 
- * 3. All advertising materials mentioning features or use
- * of this software must display the following
- * acknowledgment: "This product includes software
- * developed by Stanley Kok, Parag Singla, Matthew
- * Richardson, Pedro Domingos, Marc Sumner, Hoifung
- * Poon, and Daniel Lowd in the Department of Computer Science and
- * Engineering at the University of Washington".
- * 
- * 4. Your publications acknowledge the use or
- * contribution made by the Software to your research
- * using the following citation(s): 
- * Stanley Kok, Parag Singla, Matthew Richardson and
- * Pedro Domingos (2005). "The Alchemy System for
- * Statistical Relational AI", Technical Report,
- * Department of Computer Science and Engineering,
- * University of Washington, Seattle, WA.
- * http://www.cs.washington.edu/ai/alchemy.
- * 
- * 5. Neither the name of the University of Washington nor
- * the names of its contributors may be used to endorse or
[…]

### 2023-06-07 solvers/fastwfomc/main.py

@@ -1,47 +1,0 @@
-import argparse
-from collections import defaultdict
-
-from aima3.logic import to_cnf
-from aima3.utils import expr, Expr
-
-from wfomc_cc import WFOMCWithCC
-
-
-def main():
-    parser = argparse.ArgumentParser(description='Compute the WFOMC of a two-variable sentence.')
-    parser.add_argument('domainsize', metavar='N', type=int,
-                        help='domain size')
-    args = parser.parse_args()
-    n = args.domainsize
-
-    four_coloured = expr(
-        '~E(x, x) & ' +
-        '(~E(x, y) | E(y, x)) & ' +
-        '(C1(x) | C2(x) | C3(x) | C4(x)) & ' +
-        '(~C1(x) | ~C2(x)) & ' +
-        '(~C2(x) | ~C3(x)) & ' +
-        '(~C1(x) | ~C3(x)) & ' +
-        '(~C1(x) | ~C4(x)) & ' +
-        '(~C2(x) | ~C4(x)) & ' +
-        '(~C3(x) | ~C4(x)) & ' +
-        '(~E(x,y) | (~(C1(x) & C1(y)) & ~(C2(x) & C2(y)) & ~(C3(x) & C3(y)) & ~(C4(x) & C4(y))))'
-    )
-
-    functions = expr('S(x) | ~P(x, y)')
-
-    bijections = expr(
-        '(S1(x) | ~P(x, y)) & (S3(x) | ~P(y, x))'
-    )
-
-    #print(counter.get_wfomc(defaultdict(lambda: (1, 1))))
-
-    counter = WFOMCWithCC(functions, n, [('P', n)])
-    #print(counter.get_wfomc({'S': (1, -1), 'P': (1, 1)}))
-
-    counter = WFOMCWithCC(bijections, n, [('P', n)])
-    print(counter.get_wfomc({'S1': (1, -1), 'S3': (1, -1), 'P': (1, 1)}))
-
-
-
-if __name__ == "__main__":
-    main()

### 2023-06-07 solvers/python-flint/setup.py

@@ -1,82 +1,0 @@
-import sys
-import os
-from subprocess import check_call
-
-from distutils.core import setup
-from distutils.extension import Extension
-from Cython.Distutils import build_ext
-from Cython.Build import cythonize
-from numpy.distutils.system_info import default_include_dirs, default_lib_dirs
-
-from distutils.sysconfig import get_config_vars
-
-
-if sys.platform == 'win32':
-    #
-    # This is used in CI to build wheels with mingw64
-    #
-    if os.getenv('PYTHON_FLINT_MINGW64'):
-        libraries = ["arb", "flint", "mpfr", "gmp"]
-        includedir = os.path.join(os.path.dirname(__file__), '.local', 'include')
-        librarydir1 = os.path.join(os.path.dirname(__file__), '.local', 'bin')
-        librarydir2 = os.path.join(os.path.dirname(__file__), '.local', 'lib')
-        librarydirs = [librarydir1, librarydir2]
-        default_include_dirs += [includedir]
-        default_lib_dirs += librarydirs
-        # Add gcc to the PATH in GitHub Actions when this setup.py is called by
-        # cibuildwheel.
-        os.environ['PATH'] += r';C:\msys64\mingw64\bin'
-    elif os.getenv('PYTHON_FLINT_MINGW64_TMP'):
-        # This would be used to build under Windows against these libraries if
-        # they have been installed somewhere other than .local
-        libraries = ["arb", "flint", "mpfr", "gmp"]
-    else:
-        # For the MSVC toolchain link with mpir instead of gmp
-        libraries = ["arb", "flint", "mpir", "mpfr", "pthreads"]
-else:
-    libraries = ["arb", "flint"]
-    (opt,) = get_config_vars('OPT')
-    os.environ['OPT'] = " ".join(flag for flag in opt.split() if flag != '-Wstrict-prototypes')
-
-
-default_include_dirs += [
-    os.path.join(d, "flint") for d in default_include_dirs
-]
-
-
-define_macros = []
-compiler_directives = {'language_level':2}
-
-
-# Enable coverage tracing
-if os.getenv('PYTHON_FLINT_COVERAGE'):
-    define_macros.append(('CYTHON_TRACE', 1))
-    compiler_directives['linetrace'] = True
-
-
-ext_modules = [
-    Extension(
-        "flint._flint", ["src/flint/pyflint.pyx"],
-        libraries=libraries,
-        library_dirs=default_lib_dirs,
[…]

### 2023-06-07 solvers/python-flint/src/flint/acb_series.pyx

@@ -1,807 +1,0 @@
-cdef acb_series_coerce_operands(x, y):
-    if typecheck(x, acb_series):
-        if isinstance(y, (int, long, float, complex, fmpz, fmpz_poly, fmpz_series, fmpq, fmpq_poly, fmpq_series, arb, arb_poly, arb_series, acb, acb_poly)):
-            return x, acb_series(y)
-    else:
-        if isinstance(x, (int, long, float, complex, fmpz, fmpz_poly, fmpz_series, fmpq, fmpq_poly, fmpq_series, arb, arb_poly, arb_series, acb, acb_poly)):
-            return acb_series(x), y
-    return NotImplemented, NotImplemented
-
-cdef class acb_series(flint_series):
-
-    cdef acb_poly_t val
-    cdef long prec
-
-    def __cinit__(self):
-        acb_poly_init(self.val)
-        self.prec = 0
-
-    def __dealloc__(self):
-        acb_poly_clear(self.val)
-
-    def __init__(self, val=None, prec=None):
-        if prec is None:
-            self.prec = getcap()
-        else:
-            self.prec = prec
-        if self.prec < 0:
-            self.prec = -1
-        if val is not None:
-            if typecheck(val, acb_series):
-                acb_poly_set(self.val, (<acb_series>val).val)
-                self.prec = min((<acb_series>val).prec, getcap())
-            elif typecheck(val, arb_series):
-                acb_poly_set_arb_poly(self.val, (<arb_series>val).val)
-                self.prec = min((<arb_series>val).prec, getcap())
-            elif typecheck(val, fmpz_series):
-                acb_poly_set_fmpz_poly(self.val, (<fmpz_series>val).val, getprec())
-                self.prec = min((<fmpz_series>val).prec, getcap())
-            elif typecheck(val, fmpz_poly):
-                acb_poly_set_fmpz_poly(self.val, (<fmpz_poly>val).val, getprec())
-            elif typecheck(val, acb_poly):
-                acb_poly_set(self.val, (<acb_poly>val).val)
-            elif typecheck(val, list):
-                acb_poly_set_list(self.val, val, getprec())
-            else:
-                acb_poly_set_list(self.val, [val], getprec())
-        acb_poly_truncate(self.val, max(0, self.prec))
-
-    def __len__(self):
-        return acb_poly_length(self.val)
-
-    cpdef long length(self):
-        return acb_poly_length(self.val)
-
-    def __getitem__(self, long i):
-        cdef acb x
[…]

### 2023-06-07 solvers/python-flint/src/flint/arb_series.pyx

@@ -1,809 +1,0 @@
-cdef arb_series_coerce_operands(x, y):
-    if typecheck(x, arb_series):
-        if isinstance(y, (int, long, float, fmpz, fmpz_poly, fmpz_series, fmpq, fmpq_poly, fmpq_series, arb, arb_poly)):
-            return x, arb_series(y)
-        if isinstance(y, (complex, acb, acb_poly, acb_series)):
-            return acb_series(x), acb_series(y)
-    else:
-        if isinstance(x, (int, long, float, fmpz, fmpz_poly, fmpz_series, fmpq, fmpq_poly, fmpq_series, arb, arb_poly)):
-            return arb_series(x), y
-        if isinstance(x, (complex, acb, acb_poly, acb_series)):
-            return acb_series(x), acb_series(y)
-    return NotImplemented, NotImplemented
-
-cdef class arb_series(flint_series):
-
-    cdef arb_poly_t val
-    cdef long prec
-
-    def __cinit__(self):
-        arb_poly_init(self.val)
-        self.prec = 0
-
-    def __dealloc__(self):
-        arb_poly_clear(self.val)
-
-    def __init__(self, val=None, prec=None):
-        if prec is None:
-            self.prec = getcap()
-        else:
-            self.prec = prec
-        if self.prec < 0:
-            self.prec = -1
-        if val is not None:
-            if typecheck(val, arb_series):
-                arb_poly_set(self.val, (<arb_series>val).val)
-                self.prec = min((<fmpz_series>val).prec, getcap())
-            elif typecheck(val, fmpz_series):
-                arb_poly_set_fmpz_poly(self.val, (<fmpz_series>val).val, getprec())
-                self.prec = min((<fmpz_series>val).prec, getcap())
-            elif typecheck(val, fmpz_poly):
-                arb_poly_set_fmpz_poly(self.val, (<fmpz_poly>val).val, getprec())
-            elif typecheck(val, arb_poly):
-                arb_poly_set(self.val, (<arb_poly>val).val)
-            elif typecheck(val, list):
-                arb_poly_set_list(self.val, val, getprec())
-            else:
-                arb_poly_set_list(self.val, [val], getprec())
-        arb_poly_truncate(self.val, max(0, self.prec))
-
-    def __len__(self):
-        return arb_poly_length(self.val)
-
-    cpdef long length(self):
-        return arb_poly_length(self.val)
-
-    def __getitem__(self, long i):
-        cdef arb x
-        x = arb()
[…]

### 2023-06-07 solvers/python-flint/src/flint/arf.pyx

@@ -1,172 +1,0 @@
-cdef class arf:
-
-    cdef arf_t val
-
-    def __cinit__(self):
-        arf_init(self.val)
-
-    def __dealloc__(self):
-        arf_clear(self.val)
-
-    def __init__(self, val=None):
-        """
-        Create a new arf from an integer, a Python float, an existing arf,
-        or a tuple containing (mantissa, exponent)::
-
-            >>> arf(-100)
-            -100.000000000000
-            >>> arf(15.125)
-            15.1250000000000
-            >>> arf(arf(3))
-            3.00000000000000
-            >>> arf((10,-2))
-            2.50000000000000
-
-        """
-        if val is not None:
-            if typecheck(val, fmpz):
-                arf_set_fmpz(self.val, (<fmpz>val).val)
-            elif typecheck(val, arf):
-                arf_set(self.val, (<arf>val).val)
-            elif typecheck(val, float):
-                arf_set_d(self.val, PyFloat_AS_DOUBLE(<PyObject*>val))
-            elif typecheck(val, tuple):
-                man = any_as_fmpz(val[0])
-                exp = any_as_fmpz(val[1])
-                if man is NotImplemented or exp is NotImplemented:
-                    raise TypeError("cannot create arf from tuple (%s, %s)" % (type(val[0]), type(val[1])))
-                arf_set_fmpz_2exp(self.val, (<fmpz>man).val, (<fmpz>exp).val)
-            elif typecheck(val, str):
-                if val == "+inf" or val == "inf":
-                    arf_pos_inf(self.val)
-                elif val == "-inf":
-                    arf_neg_inf(self.val)
-                elif val == "nan":
-                    arf_nan(self.val)
-                else:
-                    raise TypeError("cannot create arf from type %s" % type(val))
-            else:
-                v = any_as_fmpz(val)
-                if v is not NotImplemented:
-                    arf_set_fmpz(self.val, (<fmpz>v).val)
-                else:
-                    raise TypeError("cannot create arf from type %s" % type(val))
-
-    cpdef bint is_finite(self):
-        return arf_is_finite(self.val)
-
-    cpdef bint is_pos_inf(self):
-        return arf_is_pos_inf(self.val)
-
-    cpdef bint is_neg_inf(self):
-        return arf_is_neg_inf(self.val)
-
[…]

### 2023-06-07 solvers/python-flint/src/flint/dirichlet.pyx

@@ -1,197 +1,0 @@
-cdef dict _dirichlet_group_cache = {}
-
-cdef class dirichlet_group(object):
-    """
-    Represents the group of Dirichlet characters modulo a given q.
-
-        >>> G = dirichlet_group(5)
-        >>> G
-        Dirichlet group mod q = 5
-    """
-
-    cdef dirichlet_group_t val
-    cdef int _init
-
-    def __cinit__(self):
-        self._init = 0
-
-    def __dealloc__(self):
-        if self._init != 0:
-            dirichlet_group_clear(self.val)
-
-    def __init__(self, ulong q):
-        assert q >= 1
-        dirichlet_group_init(self.val, q)
-        self._init = 1
-
-    cpdef long size(self):
-        return dirichlet_group_size(self.val)
-
-    @property
-    def q(self):
-        return fmpz(self.val.q)
-
-    def exponent(self):
-        return fmpz(self.val.expo)
-
-    def __repr__(self):
-        return "Dirichlet group mod q = %s" % self.q
-
-    def __str__(self):
-        return repr(self)
-
-
-cdef class dirichlet_char(object):
-    """
-    Represents a Dirichlet character.
-
-    Calling the character evaluates the character at the
-    given integer, returning an acb.
-
-        >>> chi = dirichlet_char(7, 1)
-        >>> for n in range(7):
-        ...     print(chi(n))
-        ... 
-        0
-        1.00000000000000
-        1.00000000000000
-        1.00000000000000
-        1.00000000000000
-        1.00000000000000
-        1.00000000000000
-        >>> chi = dirichlet_char(7, 3)
-        >>> for n in range(7):
-        ...     print(chi(n))
-        ... 
-        0
-        1.00000000000000
-        -0.500000000000000 + [0.866025403784439 +/- 5.15e-16]j
-        0.500000000000000 + [0.866025403784439 +/- 5.15e-16]j
-        -0.500000000000000 + [-0.866025403784439 +/- 5.15e-16]j
-        0.500000000000000 + [-0.866025403784439 +/- 5.15e-16]j
-        -1.00000000000000
-    """
-
-    cdef dirichlet_char_t val
-    cdef dirichlet_group G
-
-    def __cinit__(self):
-        pass
-
-    def __dealloc__(self):
-        dirichlet_char_clear(self.val)
-
-    def __init__(self, ulong q, ulong l=1):
-        """
[…]

### 2023-06-07 solvers/python-flint/src/flint/fmpq.pyx

@@ -1,360 +1,0 @@
-cdef any_as_fmpq(obj):
-    if typecheck(obj, fmpq):
-        return obj
-    z = any_as_fmpz(obj)
-    if z is NotImplemented:
-        return z
-    q = fmpq.__new__(fmpq)
-    fmpz_set(fmpq_numref((<fmpq>q).val), (<fmpz>z).val)
-    fmpz_one(fmpq_denref((<fmpq>q).val))
-    return q
-
-cdef class fmpq(flint_scalar):
-    """
-    The fmpq type represents multiprecision rational numbers.
-
-        >>> fmpq(1,7) + fmpq(50,51)
-        401/357
-
-    """
-
-    cdef fmpq_t val
-
-    def __cinit__(self):
-        fmpq_init(self.val)
-
-    def __dealloc__(self):
-        fmpq_clear(self.val)
-
-    def __init__(self, p=None, q=None):
-        cdef long x
-        if q is None:
-            if p is None:
-                return # zero
-            elif typecheck(p, fmpq):
-                fmpq_set(self.val, (<fmpq>p).val)
-                return
-            elif typecheck(p, str):
-                if "/" in p:
-                    p, q = p.split("/")
-                    p = fmpz(p)
-                    q = fmpz(q)
-                else:
-                    p = fmpz(p)
-                    q = fmpz(1)
-            else:
-                p = any_as_fmpq(p)
-                if p is NotImplemented:
-                    raise ValueError("cannot create fmpq from object of type %s" % type(p))
-                fmpq_set(self.val, (<fmpq>p).val)
-                return
-        p = any_as_fmpz(p)
-        if p is NotImplemented:
-            raise ValueError("cannot create fmpq from object of type %s" % type(p))
-        q = any_as_fmpz(q)
-        if q is NotImplemented:
-            raise ValueError("cannot create fmpq from object of type %s" % type(q))
-        if fmpz_is_zero((<fmpz>q).val):
-            raise ZeroDivisionError("cannot create rational number with zero denominator")
-        fmpz_set(fmpq_numref(self.val), (<fmpz>p).val)
-        fmpz_set(fmpq_denref(self.val), (<fmpz>q).val)
-        fmpq_canonicalise(self.val)
-
-    def __richcmp__(s, t, int op):
-        cdef bint res
-        s = any_as_fmpq(s)
[…]

### 2023-06-07 solvers/python-flint/src/flint/fmpq_poly.pyx

@@ -1,379 +1,0 @@
-cdef any_as_fmpq_poly(obj):
-    if typecheck(obj, fmpq_poly):
-        return obj
-    x = any_as_fmpz(obj)
-    if x is not NotImplemented:
-        r = fmpq_poly.__new__(fmpq_poly)
-        fmpq_poly_set_fmpz((<fmpq_poly>r).val, (<fmpz>x).val)
-        return r
-    x = any_as_fmpz_poly(obj)
-    if x is not NotImplemented:
-        r = fmpq_poly.__new__(fmpq_poly)
-        fmpq_poly_set_fmpz_poly((<fmpq_poly>r).val, (<fmpz_poly>x).val)
-        return r
-    x = any_as_fmpq(obj)
-    if x is not NotImplemented:
-        r = fmpq_poly.__new__(fmpq_poly)
-        fmpq_poly_set_fmpq((<fmpq_poly>r).val, (<fmpq>x).val)
-        return r
-    return NotImplemented
-
-cdef fmpq_poly_set_list(fmpq_poly_t poly, list val):
-    cdef long i, n
-    n = PyList_GET_SIZE(<PyObject*>val)
-    fmpq_poly_fit_length(poly, n)
-    for i from 0 <= i < n:
-        c = val[i]
-        x = any_as_fmpz(c)
-        if x is not NotImplemented:
-            fmpq_poly_set_coeff_fmpz(poly, i, (<fmpz>x).val)
-            continue
-        x = any_as_fmpq(c)
-        if x is not NotImplemented:
-            fmpq_poly_set_coeff_fmpq(poly, i, (<fmpq>x).val)
-            continue
-        raise TypeError("unsupported coefficient in list")
-
-cdef class fmpq_poly(flint_poly):
-    """
-    The *fmpq_poly* type represents dense univariate polynomials
-    over the rational numbers. For efficiency reasons, an *fmpq_poly* is
-    structurally an integer polynomial with a single common denominator.
-
-        >>> fmpq_poly([1,2,3],5) ** 3
-        27/125*x^6 + 54/125*x^5 + 63/125*x^4 + 44/125*x^3 + 21/125*x^2 + 6/125*x + 1/125
-        >>> ctx.pretty = False
-        >>> fmpq_poly([1,2,3],5) ** 3
-        fmpq_poly([1, 6, 21, 44, 63, 54, 27], 125)
[…]

### 2023-06-07 solvers/python-flint/src/flint/fmpq_series.pyx

@@ -1,488 +1,0 @@
-cdef fmpq_series_coerce_operands(x, y):
-    if typecheck(x, fmpq_series):
-        if isinstance(y, (int, long, fmpz, fmpz_poly, fmpz_series, fmpq, fmpq_poly)):
-            return x, fmpq_series(y)
-        #if isinstance(y, (nmod, nmod_poly, nmod_series)):
-        #    return nmod_series(x), nmod_series(y)
-        if isinstance(y, (float, arb, arb_poly, arb_series)):
-            return arb_series(x), arb_series(y)
-        if isinstance(y, (complex, acb, acb_poly, acb_series)):
-            return acb_series(x), acb_series(y)
-    else:
-        if isinstance(x,(int, long, fmpz, fmpz_poly, fmpz_series, fmpq, fmpq_poly)):
-            return fmpq_series(x), y
-        #if isinstance(x, (nmod, nmod_poly, nmod_series)):
-        #    return nmod_series(x), nmod_series(y)
-        if isinstance(x, (float, arb, arb_poly, arb_series)):
-            return arb_series(x), arb_series(y)
-        if isinstance(x, (complex, acb, acb_poly, acb_series)):
-            return acb_series(x), acb_series(y)
-    return NotImplemented, NotImplemented
-
-cdef class fmpq_series(flint_series):
-
-    cdef fmpq_poly_t val
-    cdef long prec
-
-    def __cinit__(self):
-        fmpq_poly_init(self.val)
-        self.prec = 0
-
-    def __dealloc__(self):
-        fmpq_poly_clear(self.val)
-
-    def __init__(self, val=None, den=None, prec=None):
-        if prec is None:
-            self.prec = getcap()
-        else:
-            self.prec = prec
-        if self.prec < 0:
-            self.prec = -1
-        if val is not None:
-            if typecheck(val, fmpq_series):
-                fmpq_poly_set(self.val, (<fmpq_series>val).val)
-                self.prec = min((<fmpz_series>val).prec, getcap())
-            elif typecheck(val, fmpz_series):
-                fmpq_poly_set_fmpz_poly(self.val, (<fmpz_series>val).val)
-                self.prec = min((<fmpz_series>val).prec, getcap())
-            elif typecheck(val, fmpz_poly):
-                fmpq_poly_set_fmpz_poly(self.val, (<fmpz_poly>val).val)
-            elif typecheck(val, fmpq_poly):
-                fmpq_poly_set(self.val, (<fmpq_poly>val).val)
[…]

### 2023-06-07 solvers/python-flint/src/flint/fmpz_poly.pyx

@@ -1,530 +1,0 @@
-cdef any_as_fmpz_poly(x):
-    cdef fmpz_poly res
-    if typecheck(x, fmpz_poly):
-        return x
-    elif typecheck(x, fmpz):
-        res = fmpz_poly.__new__(fmpz_poly)
-        fmpz_poly_set_fmpz(res.val, (<fmpz>x).val)
-        return res
-    elif PY_MAJOR_VERSION < 3 and PyInt_Check(<PyObject*>x):
-        res = fmpz_poly.__new__(fmpz_poly)
-        fmpz_poly_set_si(res.val, PyInt_AS_LONG(<PyObject*>x))
-        return res
-    elif PyLong_Check(<PyObject*>x):
-        res = fmpz_poly.__new__(fmpz_poly)
-        t = fmpz(x)
-        fmpz_poly_set_fmpz(res.val, (<fmpz>t).val)
-        return res
-    return NotImplemented
-
-cdef fmpz_poly_set_list(fmpz_poly_t poly, list val):
-    cdef long i, n
-    cdef fmpz_t x
-    n = PyList_GET_SIZE(<PyObject*>val)
-    fmpz_poly_fit_length(poly, n)
-    fmpz_init(x)
-    for i from 0 <= i < n:
-        if typecheck(val[i], fmpz):
-            fmpz_poly_set_coeff_fmpz(poly, i, (<fmpz>(val[i])).val)
-        elif fmpz_set_python(x, val[i]):
-            fmpz_poly_set_coeff_fmpz(poly, i, x)
-        else:
-            fmpz_clear(x)
-            raise TypeError("unsupported coefficient in list")
-    fmpz_clear(x)
-
-cdef class fmpz_poly(flint_poly):
-    """
-    The *fmpz_poly* type represents dense univariate polynomials over
-    the integers.
-
-        >>> fmpz_poly([1,2,3]) ** 3
-        27*x^6 + 54*x^5 + 63*x^4 + 44*x^3 + 21*x^2 + 6*x + 1
-        >>> divmod(fmpz_poly([2,0,1,1,6]), fmpz_poly([3,5,7]))
-        (0, 6*x^4 + x^3 + x^2 + 2)
-    """
-
-    cdef fmpz_poly_t val
-
-    def __cinit__(self):
-        fmpz_poly_init(self.val)
-
-    def __dealloc__(self):
-        fmpz_poly_clear(self.val)
-
-    def __init__(self, val=None):
-        if val is not None:
[…]

### 2023-06-07 solvers/python-flint/src/flint/pyflint.pyx

@@ -1,326 +1,0 @@
-"""
-Python wrapper for FLINT and Arb.
-"""
-
-cimport flint
-cimport libc.stdlib
-cimport cython
-
-cdef flint_rand_t global_random_state
-flint_randinit(global_random_state)
-
-cdef extern from "Python.h":
-    int PyObject_TypeCheck(object, PyTypeObject*)
-    int PyInt_Check(PyObject *o)
-    PyObject* PyInt_FromLong(long ival)
-    int PyLong_Check(PyObject *o)
-    long PyInt_AS_LONG(PyObject *io)
-    double PyFloat_AS_DOUBLE(PyObject *io)
-    Py_ssize_t PyList_GET_SIZE(PyObject *list)
-    long PyLong_AsLongAndOverflow(PyObject *pylong, int *overflow)
-    int PyComplex_Check(PyObject *o)
-    double PyComplex_RealAsDouble(PyObject *op)
-    double PyComplex_ImagAsDouble(PyObject *op)
-
-from cpython.version cimport PY_MAJOR_VERSION
-
-cdef chars_from_str(s):
-    if PY_MAJOR_VERSION < 3:
-        return s
-    else:
-        return s.encode('ascii')
-
-cdef str_from_chars(s):
-    if PY_MAJOR_VERSION < 3:
-        return str(s)
-    else:
-        return bytes(s).decode('ascii')
-
-cdef matrix_to_str(tab):
-    if len(tab) == 0 or len(tab[0]) == 0:
-        return "[]"
-    tab = [[str(c) for c in row] for row in tab]
-    widths = []
-    for i in xrange(len(tab[0])):
-        w = max([len(row[i]) for row in tab])
-        widths.append(w)
-    for i in xrange(len(tab)):
-        tab[i] = [s.rjust(widths[j]) for j, s in enumerate(tab[i])]
-        tab[i] = "[" + (", ".join(tab[i])) + "]"
-    return "\n".join(tab)
-
-cdef inline bint typecheck(object ob, object tp):
-    return PyObject_TypeCheck(ob, <PyTypeObject*>tp)
-
-DEF FMPZ_UNKNOWN = 0
-DEF FMPZ_REF = 1
-DEF FMPZ_TMP = 2
-
-
-cdef long prec_to_dps(n):
-    return max(1, int(round(int(n)/3.3219280948873626)-1))
-
-cdef long dps_to_prec(n):
-    return max(1, int(round((int(n)+1)*3.3219280948873626)))
-
-cdef class FlintContext:
[…]

### 2023-06-08 doc/paper/paper.tex
Camera-ready

@@
 Broeck~\shortcite{DBLP:conf/nips/Broeck11}. For the proofs of this and other
-theorems, see supplementary material.
+theorems, see the full version of this
+paper\footnote{\url{https://arxiv.org/abs/2306.04189}}.
 
@@
 \textsc{Crane} can also solve all but one of the instances that
-\textsc{ForcLift} fails on in at most cubic time. See supplementary material for
-the exact solutions produced by \textsc{Crane}.
+\textsc{ForcLift} fails on in at most cubic time. See the full version of this
+paper\footnote{\url{https://arxiv.org/abs/2306.04189}} for the exact solutions
+produced by \textsc{Crane}.
 
@@
 \end{enumerate*}
-In addition to the potential impact on areas of artificial intelligence (AI)
-like statistical relational AI~\cite{DBLP:series/synthesis/2016Raedt},
-\textsc{Crane} could be beneficial to research in combinatorics as
-well~\cite{DBLP:conf/ilp/BarvinekB0ZK21}.
+
+\section*{Acknowledgments}
+
+We thank Anna L.D. Latour and Kuldeep S. Meel for comments on earlier drafts of
+this paper. Most of the work for this paper was done while the first author was
+a PhD student at the University of Edinburgh. The first author was supported by
+the EPSRC Centre for Doctoral Training in Robotics and Autonomous Systems,
+funded by the UK Engineering and Physical Sciences Research Council (grant
+EP/L016834/1). The second author was partly supported by a Royal Society
+University Research Fellowship, UK, and partly supported by a Grant from the
+UKRI Strategic Priorities Fund, UK to the UKRI Research Node on Trustworthy
+Autonomous Systems Governance and Regulation (EP/ V026607/1, 2020–2024). For the
+purpose of open access, the authors have applied a Creative Commons Attribution
+(CC BY) licence to any Author Accepted Manuscript version arising from this
+submission.
 

### 2023-08-12 doc/talks/5_kr/talk.tex
Conference talk

--- 2023-04-19 doc/talks/3_long/talk.tex
@@
 \usepackage[UKenglish]{isodate}
-\usepackage{amsmath}
 \usepackage{mathtools}
 \usepackage{tikz}
+\usepackage{microtype}
 \usepackage{complexity}
+\usepackage{forest}
 \usepackage[style=authoryear]{biblatex}
-\usepackage{forest}
 \usepackage{soul}
-\usepackage{csquotes}
-\usepackage{pifont}
 
@@
 
-\newcommand\blfootnote[1]{%
-  \begingroup
-  \renewcommand\thefootnote{}\footnote{#1}%
-  \addtocounter{footnote}{-1}%
-  \endgroup
-}
-
-\renewcommand<>{\hl}[1]{\only#2{\beameroriginal{\hl}}{#1}}
-\makeatletter
-\newcommand\SoulColor{%
-  \let\set@color\beamerorig@set@color
-  \let\reset@color\beamerorig@reset@color}
-\makeatother
-\SoulColor
-
-\beamertemplatenavigationsymbolsempty
-\usetheme{metropolis}
-\setbeamercolor{background canvas}{bg=white}
-
-\addbibresource{talk.bib}
-
-\definecolor{color1}{HTML}{1B9E77}
-\definecolor{color2}{HTML}{7570b3}
-\definecolor{color3}{HTML}{a6761d}
-\definecolor{forestgreen}{HTML}{009B55}
-
-\DeclareMathOperator{\GDR}{\textsc{GDR}}
-\DeclareMathOperator{\CR}{\textsc{CR}}
-\DeclareMathOperator{\Reff}{\textsc{Ref}}
-
-\colorlet{redish}{color2!25}
-\colorlet{greenish}{color1!25}
-\colorlet{blueish}{color3!25}
-\sethlcolor{redish}
-\setstcolor{black}
-
-\tikzset{
-  inner/.style={
-    ellipse,
-    draw,
-  },
-  inner on/.style={alt=#1{inner}{}},
-  leaf/.style={
-    rectangle,
-    draw,
-    fill=gray!25,
-  },
-  leaf on/.style={alt=#1{leaf}{}},
-  invisible/.style={opacity=0,text opacity=0},
-  visible on/.style={alt=#1{}{invisible}},
-  alt/.code args={<#1>#2#3}{%
-    \alt<#1>{\pgfkeysalso{#2}}{\pgfkeysalso{#3}} % \pgfkeysalso doesn't change the path
-  },
-}
-
 \forestset{
@@
 
-\newcommand{\cmark}{\ding{51}}%
+\beamertemplatenavigationsymbolsempty
+\usetheme{default}
+\usecolortheme{rose}
 
-\newcommand{\xx}{\textcolor{color1}{x}}
-\newcommand{\yy}{\textcolor{color3}{y}}
+\definecolor{color1}{HTML}{1B9E77}
+\definecolor{color2}{HTML}{7570b3}
+
 \newcommand{\pP}{\texttt{P}}
 \newcommand{\qQ}{\texttt{Q}}
-\newcommand{\dDelta}{\textcolor{color2}{\Delta}}
+\DeclareMathOperator{\GDR}{\textsc{GDR}}
+\DeclareMathOperator{\CR}{\textsc{CR}}
+\DeclareMathOperator{\Reff}{\textsc{Ref}}
 
-\newcommand{\pone}{\textcolor{color1}{\pP(1)}}
-\newcommand{\ptwo}{\textcolor{color1}{\pP(2)}}
-\newcommand{\qone}{\textcolor{color2}{\qQ(1)}}
-\newcommand{\qtwo}{\textcolor{color2}{\qQ(2)}}
-\newcommand{\pqone}{\textcolor{color3}{\pP(1)}, \textcolor{color3}{\qQ(1)}}
-\newcommand{\pqtwo}{\textcolor{color3}{\pP(2)}, \textcolor{color3}{\qQ(2)}}
+\addbibresource{talk.bib}
 
-\newcommand{\WMC}{\textup{WMC}}
-\newcommand{\WMI}{\textup{WMI}}
-\newcommand{\WFOMI}{\textup{WFOMI}}
-\newcommand{\AMC}{\textup{AMC}}
-\newcommand{\pbp}{\textup{PBP}}
-\newcommand{\SPPP}{\textup{SP}}
-
-% 15 min (8 slides, currently have 7) introduction
-% 25 min (13 slides, currently have 10) presentation
-% 5 min (3 slides, currently have 1) summary
-% make sure there's a clear and coherent storyline
-
-\author{Paulius Dilkas \\ \vspace{1cm} \tiny{Joint work with Vaishak Belle (Univeristy of Edinburgh, UK)}}
-\title{Synthesising Recursive Functions for\\ First-Order Model Counting}
-\institute{National University of Singapore, Singapore}
-\date{PLSE Seminar, 21st April 2023}
+\author{\textbf{Paulius Dilkas}\inst{1} \and Vaishak Belle\inst{2}}
+\title{Synthesising Recursive Functions for\\First-Order Model Counting:}
+\subtitle{Challenges, Progress, and Conjectures}
+\institute{\inst{1}National University of Singapore, Singapore \and \inst{2}University of Edinburgh, UK}
+\date{KR 2023}
 
@@
 
-\begin{frame}{What Computers Can and Cannot Do}
-  \begin{tikzpicture}[remember picture,overlay]
-    \node[right=0.7cm] at (current page.west) (stickman) {\includegraphics[height=0.5\textheight]{stickman.png}};
-    \node<-4>[left,shift=({0, -2})] at (current page.east) (computer) {\includegraphics[height=0.5\textheight]{happy_computer}};
-    \node<2>[ellipse callout, draw, right=0cm, callout relative pointer={(-1, -0.5)}] at (stickman.north east) {$\int_{-\infty}^{\infty} e^{-t^{2}}\,\mathrm{d}t$};
-    \node<2>[ellipse callout, draw, left=-0.5cm, below=0.5cm] at (computer.north west) {$\sqrt{\pi}$};
-    \node<3>[ellipse callout, draw, right=0cm, callout relative pointer={(-1, -0.15)},text width=5cm] at (stickman.north east) {Produce a \alert{schedule} for the nurses at the local hospital.};
-    \node<3>[ellipse callout, draw, below=0.5cm, shift=({-0.5,0}), callout relative pointer={(0.5, -0.25)}] at (computer.north west) {\includegraphics[width=0.1\textwidth]{schedule}};
-    \node<4>[ellipse callout, draw, right=0cm, callout relative pointer={(-1, -0.15)},text width=6cm] at (stickman.north east) {Paint a baroque oil painting of a \alert{raccoon queen wearing a crown}.};
-    \node<4>[ellipse callout, draw, below=0cm, shift=({-1.5,1}), callout relative pointer={(0.4, -0.2)}] at (computer.north west) {\includegraphics[width=0.25\textwidth]{dalle.png}};
-    \node<5>[ellipse callout, draw, right=0cm, callout relative pointer={(-1, -0.15)}, text width=5cm] at (stickman.north east) {If I shuffle a deck of \alert{$n$} cards, how many possible outcomes are there?};
-    \node<5>[left,shift=({-1, -1})] at (current page.east) (computer2) {\includegraphics[height=0.5\textheight]{overheating_computer}\blfootnote{Terms and conditions apply.}};
-    \node[shift=({1.3, 0.1})] at (current page.south west) {\tiny \textcolor{lightgray}{Vector art by Vecteezy.com}};
-  \end{tikzpicture}
-\end{frame}
-
-\begin{frame}{Who Cares About Counting?}
-  \begin{columns}
-    \begin{column}{0.5\textwidth}
-      \pause
-      \begin{block}{\alert{Probabilistic Programming}}
-        \centering
-        \includegraphics[width=\textwidth]{programming.png}
-      \end{block}
-      \pause
-      \begin{block}{\alert{Neuro-symbolic AI}}
-        \centering
-        \includegraphics[width=\textwidth]{neurosymbolic.png}
-      \end{block}
-      \pause
-      \begin{block}{\alert{Natural Language Processing}}
-        \centering
-        \includegraphics[width=\textwidth]{knowledge.png}
-      \end{block}
-      \pause
-    \end{column}
-    \begin{column}{0.5\textwidth}
-      \begin{block}{\alert{Robotics}}
-        \centering
-        \includegraphics[width=\textwidth]{ICRA.png}
-      \end{block}
-      \pause
-      \begin{block}{\alert{Bioinformatics}}
-        \centering
-        \includegraphics[width=\textwidth]{bio.png}
-      \end{block}
-      \pause
-      \begin{block}{\alert{Combinatorics}}
-        \centering
-        \includegraphics[width=\textwidth]{recurrence.png}
-      \end{block}
-    \end{column}
-  \end{columns}
-\end{frame}
-
-\begin{frame}[fragile]{(Some of the) Many Ways to Count}
-  \begin{center}
-    \begin{tikzcd}[remember picture]
-      |[alias=WMI,visible on=<7->]|\WMI{} & |[visible on=<7->]|\WFOMI{} \\
-      |[alias=WMC]|\#\SAT{}/\WMC{} \arrow[u,visible on=<7->] \ar[d,visible on=<8->] \ar[r,visible on=<5->] & |[visible on=<5->]|\textup{(W)\alert<9>{FOMC}} \arrow[u,visible on=<7->] \ar[d,visible on=<8->] \\
-      |[alias=PBP,visible on=<8->]|\AMC{}, \pbp{} & |[alias=SP,visible on=<8->]|\SPPP{}
-    \end{tikzcd}
-  \end{center}
-  \begin{tikzpicture}[overlay,remember picture]
-    \begin{scope}[transform canvas={xshift=-3em}]
-      \draw[->,draw=gray] ($(WMC)+(0,0.1)$)--($(WMI)+(0,0.5)$) node[midway,left,visible on=<7->] {\textcolor{gray}{$\sum \to \int$}};
-      \draw[->,draw=gray] ($(WMC)-(0,0.1)$)--($(PBP)-(0,0.5)$) node[midway,left,visible on=<8->] {\textcolor{gray}{Generalising weights}};
-    \end{scope}
-    \begin{scope}[transform canvas={yshift=-2em}]
-      \draw[->,draw=gray] ($(PBP)-(1,0)$)--($(SP)+(1,0)$) node[midway,below,visible on=<5->] {\textcolor{gray}{From propositional to first-order logic}};
-    \end{scope}
-  \end{tikzpicture}
-  \vfill
-    \begin{overprint}
-      \onslide<1,2>
-      \begin{block}{\#SAT~\textcolor{gray}{\parencite{DBLP:journals/tcs/Valiant79}}}
-        \begin{itemize}
-          \item Input formula: $\xx \lor \yy$
-          \item Interpretations: $\emptyset$, $\{\, \xx \,\}$, $\{\, \yy \,\}$,
-                $\{\, \xx, \yy \,\}$
-          \item Models: $\{\, \xx \,\}$, $\{\, \yy \,\}$, $\{\, \xx, \yy \,\}$
-          \item<2-> Answer (model count): 3
-        \end{itemize}
-      \end{block}
-      \onslide<3,4>
-      \begin{block}{Weighted Model Counting~\textcolor{gray}{\parencite{DBLP:journals/ai/ChaviraD08}}}
-        \begin{itemize}
-          \item Input formula: $\xx \lor \yy$
-          \item Input weights: $\begin{aligned}[t]
-                                  &w(\xx) = 0.3\text{, }w(\neg \xx) = 0.7,\\
-                                  &w(\yy) = 0.2\text{, }w(\neg \yy) = 0.8
-                                \end{aligned}$
-          \item<4-> Answer (weighted model count):
-                $w(\xx)w(\yy) + w(\xx)w(\neg \yy) + w(\neg \xx)w(\yy) = 0.44$
-        \end{itemize}
-      \end{block}
-      \onslide<5,6>
-      \begin{block}{(Weighted) (Symmetric) First-Order Model Counting\\
-          \textcolor{gray}{\parencite{DBLP:conf/ijcai/BroeckTMDR11}}}
-        \begin{itemize}
-          \item Input formula: $\forall \xx \in \Delta\text{. }\pP(\xx)$
-          \item Input weights: $w^{+}(\pP) = 0.3$, $w^{-}(\pP) = 0.7$
-          \item Input domain size(s): $|\dDelta| = 2$
-          \item<6-> Answer: ${(w^{+}(\pP))}^{|\dDelta|} = 0.09$
-        \end{itemize}
-      \end{block}
-      \onslide<7>
-      \begin{block}{Extensions to Continuous Domains}
-        \begin{itemize}
-          \item Weighted model integration
-          \begin{itemize}
-            \item \textcolor{gray}{\parencite{DBLP:conf/ijcai/BellePB15}}
-          \end{itemize}
-          \item Weighted first-order model integration
-          \begin{itemize}
-            \item \textcolor{gray}{\parencite{DBLP:conf/uai/FeldsteinB21}}
-          \end{itemize}
-        \end{itemize}
-      \end{block}
-      \onslide<8>
-      \begin{block}{Generalisations of the Weight Function}
-        \begin{itemize}
-          \item Algebraic model counting
-          \begin{itemize}
-            \item \textcolor{gray}{\parencite{DBLP:journals/japll/KimmigBR17}}
-            \item From $\mathbb{R}_{\ge 0}$ to commutative semirings
-          \end{itemize}
-          \item Pseudo-Boolean projection~\textcolor{gray}{\parencite{DBLP:conf/sat/DilkasB21}}
-          \begin{itemize}
-            \item Weights not necessarily on literals
-          \end{itemize}
-          \item Semiring programming~\textcolor{gray}{\parencite{DBLP:journals/ijar/BelleR20}}
-        \end{itemize}
-      \end{block}
-    \end{overprint}
-\end{frame}
-% maybe mention #CSP and other non-SAT ways of counting (SMT?, counting paths in
-% automata and directed graphs)
-
-\begin{frame}{(Unweighted) First-Order Model Counting}
-  \begin{itemize}
-    \item Example formula: \\
-          \alert{$\forall x \in \Delta\text{. } \pP(x) \lor \qQ(x)$}.
-    \item Let \alert{$\Delta \coloneqq \{\, 1, 2 \,\}$}.
-    \item Interpretations: all subsets of\\
-          \alert{$\{\, \pP(1), \qQ(1), \pP(2), \qQ(2) \,\}$}.
-    \item<2-> Models:
-    \[
-      \begin{matrix}
-        \{\, \pone, \ptwo \,\}, & \{\, \pone, \qtwo \,\}, & \{\, \pone, \pqtwo \,\},\\
-        \{\, \qone, \ptwo \,\}, & \{\, \qone, \qtwo \,\}, & \{\, \qone, \pqtwo \,\},\\
-        \{\, \pqone, \ptwo \,\}, & \{\, \pqone, \qtwo \,\}, & \{\, \pqone, \pqtwo \,\}.\\
-      \end{matrix}
-    \]
-  \end{itemize}
-  \onslide<2->{
-    \begin{block}{Intuition}
-      \begin{itemize}
-        \item Each 1-ary predicate is like a \alert{subset}.
-        \item For \alert{$n>1$}, each \alert{$n$}-ary predicate is like a
-              \alert{relation}.
-        \item FOMC counts \alert{combinations of relations}.
-      \end{itemize}
-    \end{block}
-  }
-  \begin{tikzpicture}[remember picture,overlay,visible on=<2->]
-    \tikzset{shift={(current page.north east)}}
-    \tikzset{shift={(-4, -2.9)}}
-    \node[draw,circle,minimum size=3cm,label={135:$\pP$},fill=color1] (P) at (0,0) {};
-    \node[draw,circle,minimum size=3cm,label={45:$\qQ$},fill=color2] (Q) at (1.8,0) {};
-    \begin{scope}
-      \clip (0,0) circle(1.5cm);
-      \clip (1.8,0) circle(1.5cm);
-      \fill[color3](0,0) circle(1.5cm);
-    \end{scope}
-    \draw (0,0) circle(1.5cm);
-    \draw (1.8,0) circle(1.5cm);
-  \end{tikzpicture}
-\end{frame}
-
-\begin{frame}{Exact Algorithms for FOMC}
-  \begin{itemize}
-    \item \alert{ForcLift}~\textcolor{gray}{\parencite{DBLP:conf/ijcai/BroeckTMDR11}}
-    \begin{itemize}
-      \item knowledge compilation to \alert{FO d-DNNF}
-    \end{itemize}
-    \item \alert{L2C}~\textcolor{gray}{\parencite{DBLP:conf/kr/KazemiP16}}
-    \begin{itemize}
-      \item knowledge compilation to \alert{C++} code
-    \end{itemize}
-    \item \alert{Alchemy}~\textcolor{gray}{\parencite{DBLP:journals/cacm/GogateD16}}
-    \begin{itemize}
-      \item \alert{DPLL}-style search
-    \end{itemize}
-    \item \alert{FastWFOMC}~\textcolor{gray}{\parencite{DBLP:conf/uai/BremenK21}}
-    \begin{itemize}
-      \item knowledge compilation to \alert{sd-DNNF}
-    \end{itemize}
-  \end{itemize}
-  \pause
-  \vfill
-  \begin{block}{Our Contribution}
-    \centering
-    \begin{tikzpicture}[align=center,node distance=0.1cm]
-      \node[label=below:{ForcLift}] (forclift) {\includegraphics[width=0.2\paperwidth]{forklift.png}};
-      \node[right=of forclift] (plus) {\Huge$+$};
-      \node[right=of plus,label=below:{Recursion}] (recursion) {\includegraphics[width=0.2\paperwidth]{matryoshka.jpg}};
-      \node[right=of recursion] (equal) {\Huge$=$};
-      \node[right=of equal,label=below:{Crane}] (crane) {\includegraphics[width=0.2\paperwidth]{crane.jpg}};
-    \end{tikzpicture}
-  \end{block}
-\end{frame}
-
-\begin{frame}{ForcLift and First-Order Knowledge Compilation}
-  \begin{minipage}[t][0.81\textheight][t]{\textwidth}
-    \centering
-    \begin{forest}
-      for tree={s sep=10mm, sn edges}
-      [\alt<3->{$\bigwedge_{c \in \Delta}$}{$\forall x \in \Delta\text{. } \pP(x) \lor \qQ(x)$},
-      inner on=<3->,
-      label={[visible on=<{13-14,19-}>]right:{\alert{\alt<15->{$3^{|\Delta|}$}{$\{\,\pP(c), \qQ(c)\,\}$}}}}
-      [\alt<5->{$\lor$}{$\pP(c) \lor \qQ(c)$},
-      name=lor,
-      for tree={visible on=<3->},
-      inner on=<5->,
-      label={[visible on=<{12-14,18-}>]right:{\alert{\only<18->{$2 + 1 = 3$}\only<12-13>{\colorbox{white}{$\{\,\pP(c), \qQ(c)\,\}$}}\only<14>{\colorbox{redish}{$\{\,\pP(c), \qQ(c)\,\}$}}}}}
-      [\alt<7->{$\land$}{$\begin{aligned}\qQ(c)\\ \pP(c) \lor \qQ(c)\end{aligned}$},
-      name=and,
-      for tree={visible on=<5->},
-      inner on=<7->,
-      label={[visible on=<{11-14,17-}>]left:{\alert{\only<17->{$2 \times 1 = 2$}\only<11-13>{\colorbox{white}{$\{\,\qQ(c)\,\}$}}\only<14>{\colorbox{redish}{$\{\,\qQ(c)\,\}$}}}}}
-      [\alt<15->{$\pP(c) \lor \neg \pP(c)$}{$\qQ(c)$},
-      name=smoothing,
-      for tree={visible on=<7->},
-      rectangle,
-      draw,
-      fill=gray!25,
-      label={[visible on=<16->]below:{\alert{2}}}]
-      [\alt<15->{$\land$}{$\top$},
-      for tree={visible on=<7->},
-      leaf on=<6-14>,
-      inner on=<15->,
-      label={[label distance=0cm,visible on=<17->]87:{\alert{$1 \times 1 = 1$}}},
-      label={[visible on=<10>]below:{\alert{tautology}}},
-      [$\qQ(c)$,
-      for tree={visible on=<15->},
-      rectangle,
-      draw,
-      fill=gray!25,
-      label={[visible on=<16->]below:{\alert{1}}}]
-      [$\top$,
-      for tree={visible on=<15->},
-      rectangle,
-      draw,
-      fill=gray!25,
-      label={[visible on=<16->]below:{\alert{1}}}]
-      ]
-      ]
-      [\alt<9->{$\land$}{$\begin{aligned}\neg\qQ(c)\\ \pP(c) \lor \qQ(c)\end{aligned}$},
-      name=negformula,
-      for tree={visible on=<5->},
-      inner on=<9->,
-      label={[visible on=<{11-14,17-}>]right:{\alert{\alt<15->{$1 \times 1 = 1$}{$\{\,\pP(c), \qQ(c)\,\}$}}}}
-      [$\neg \qQ(c)$,
-      name=negq,
-      for tree={visible on=<9->},
-      rectangle,
-      draw,
-      fill=gray!25,
-      label={[visible on=<16->]below:{\alert{1}}}]
-      [$\pP(c)$,
-      name=pnode,
-      for tree={visible on=<9->},
-      rectangle,
-      draw,
-      fill=gray!25,
-      label={[visible on=<16->]below:{\alert{1}}}]
-      ]
-      ]
-      ]
-      \begin{scope}[on background layer]
-        \uncover<6>{\node[fill=redish, ellipse, fit={(and)}, inner sep=0.5pt] {};}
-        \uncover<8>{\node[fill=redish, ellipse, fit={(negformula)}, inner sep=0.5pt] {};}
-        \uncover<15>{\node[fill=redish, ellipse, fit={(smoothing) (and)}, inner sep=0.5pt] {};}
-      \end{scope}
-      \node<10>[below = 3cm of lor] (n1) {\alert{unit clauses}};
-      \path[-Latex,draw]<10> (n1) edge[bend right] (pnode);
-      \path[-Latex,draw]<10> (n1) edge (negq);
-      \path[-Latex,draw]<10> (n1) edge[bend left] (smoothing);
-    \end{forest}
-  \end{minipage}
-  \begin{minipage}{\textwidth}
-    \begin{overlayarea}{\textwidth}{4cm}
-      \only<2-3>{\centerline{Independent partial grounding (introduces a constant \alert{$c \in \Delta$})}}%
-      \only<4-5>{\centerline{Shannon decomposition (a.k.a. Boole's expansion theorem) on \alert{$\qQ(c)$}}}%
-      \only<6-7>{\centerline{Positive unit propagation of \alert{$\qQ(c)$}}}%
-      \only<8-9>{\centerline{Negative unit propagation of \alert{$\neg\qQ(c)$}}}%
-      \only<10>{\centerline{Compilation is complete \textcolor{forestgreen}{\cmark}}}%
-      \only<11-13>{\centerline{Smoothing: propagating atoms upwards}}%
-      \only<14-15>{\centerline{Smoothing: adding new atoms}}%
-      \only<16->{\centerline{Propagating the model count}}%
-    \end{overlayarea}
-  \end{minipage}
-\end{frame}
-
-\begin{frame}{A (Slightly) More Complicated Example}
-  Suppose this room has \alert{$n$} seats, and there are \alert{$m \le n$}
-  people in the audience. How many ways are there to seat everyone?
-  \vfill
+\begin{frame}{Some Elementary Counting}
+  \begin{exampleblock}{A Counting Problem}
+    Suppose this room has \structure{$n$} seats, and there are
+    \structure{$m \le n$} people in the audience. How many ways are there to
+    seat everyone?
+  \end{exampleblock}
 
@@
   \end{itemize}
-  \vfill
 
   \pause
-  \alert{Answer:} $n^{\underline{m}} = n \cdot (n-1)\cdots(n-m+1)$.
+  \alert{Answer:} \structure{$n^{\underline{m}} = n \cdot (n-1)\cdots(n-m+1)$}.
 
-  Note: this problem is equivalent to counting \alert{$[m] \to [n]$} injections.
+  Note: this problem is equivalent to counting \structure{$[m] \to [n]$} injections.
 
 \end{frame}
-% wouldn't it be nice if we could just describe this problem and have an algorithm solve it for us?
+% wouldn't it be nice if we could just describe this problem and have an
+% algorithm solve it for us?
 
@@
   \begin{itemize}
-    \item Let \alert{$\Gamma$} and \alert{$\Delta$} be sets (i.e., domains)
+    \item Let \structure{$\Gamma$} and \structure{$\Delta$} be sets (i.e.,
+    \alert{domains})
           \begin{itemize}
-      \item such that \alert{$|\Gamma| = m$}, and \alert{$|\Delta| = n$}.
+            \item such that \structure{$|\Gamma| = m$}, and
+                  \structure{$|\Delta| = n$}
           \end{itemize}
-    \item Let \alert{$\pP \subseteq \Gamma \times \Delta$} be a relation (i.e.,
-          predicate) over \alert{$\Gamma$} and \alert{$\Delta$}.
+    \item Let \structure{$\pP{} \subseteq \Gamma \times \Delta$} be a relation
+          (i.e., \alert{predicate}) over \structure{$\Gamma$} and
+          \structure{$\Delta$}
     \item We can describe all of the constraints in first-order logic:
@@
             \item \pause each attendee gets a seat (i.e., at least one seat)
-      \begin{equation}\label{eq:a1}
-        \forall x \in \Gamma\text{. }\exists y \in \Delta\text{. }\pP(x, y)
+                  \begin{equation}\label{eq1}
+                    \forall x \in \Gamma\text{. }\exists y \in \Delta\text{. }\pP{}(x, y)
                   \end{equation}
             \item \pause one person cannot occupy multiple seats
-      \begin{equation}\label{eq:a2}
-        \forall x \in \Gamma\text{. }\forall y, z \in \Delta\text{. }\pP(x, y) \land \pP(x, z) \Rightarrow y=z
+                  \begin{equation}\label{eq2}
+                    \forall x \in \Gamma\text{. }\forall y, z \in \Delta\text{. }\pP{}(x, y) \land \pP{}(x, z) \Rightarrow y=z
                   \end{equation}
             \item \pause one seat cannot accommodate multiple attendees
-      \begin{equation}\label{eq:a3}
-        \forall w, x \in \Gamma\text{. }\forall y \in \Delta\text{. }\pP(w, y) \land \pP(x, y) \Rightarrow w=x
+                  \begin{equation}\label{eq3}
+                    \forall w, x \in \Gamma\text{. }\forall y \in \Delta\text{. }\pP{}(w, y) \land \pP{}(x, y) \Rightarrow w=x
                   \end{equation}
@@
   \end{itemize}
-  \pause \alert{\eqref{eq:a1}} and \alert{\eqref{eq:a2}} constrain \alert{$\pP$}
-  to be a function, and \alert{\eqref{eq:a3}} makes it injective.
+  \pause
+  \alert{\eqref{eq1}} and \alert{\eqref{eq2}} constrain \structure{$\pP{}$} to be a function, and \alert{\eqref{eq3}} makes it injective.
 \end{frame}
@@
 
-{
-  \usebackgroundtemplate{\includegraphics[keepaspectratio,width=\paperwidth]{matryoshka.jpg}}
-  \begin{frame}{Recursion}
+\begin{frame}{Overview of the Problem}
+  \begin{itemize}
+    \item \alert{First-order model counting} (FOMC) is the problem of counting
+          the models of a sentence in first-order logic.
+    \item The \alert{(symmetric) weighted} variation of the problem adds weights
+          (e.g., probabilities) to predicates.
+          \begin{itemize}
+            \item It is used for efficient \alert{probabilistic inference} in
+                  relational models such as Markov logic networks.
+          \end{itemize}
+    \item None of the (implemented) (W)FOMC algorithms are able to count, e.g.,
+          \alert{injective} and \alert{bijective} functions. % TODO: change this claim
+  \end{itemize}
+  \begin{block}{Claim}
+    This shortcoming can be addressed via support for (almost arbitrary)
+    \alert{recursive functions}.
+  \end{block}
 \end{frame}
-}
 
@@
   \begin{itemize}
-    \item \alert{$f(m, n)$} can be computed in \alert{$\Theta(mn)$} time
+    \item \structure{$f(m, n)$} can be computed in \structure{$\Theta(mn)$} time
           \begin{itemize}
             \item using dynamic programming.
-    \end{itemize}\pause
-    \item \alert{Optimal} time complexity to compute \alert{$n^{\underline{m}}$}
-          is \alert{$\Theta(m)$}.
-    \item But \alert{$\Theta(mn)$} is still much better than translating to
+          \end{itemize}
+    \item \alert{Optimal} time complexity to compute
+          \structure{$n^{\underline{m}}$} is \structure{$\Theta(m)$}.
+    \item But \structure{$\Theta(mn)$} is still much better than translating to
           propositional logic and solving a \alert{$\#\P$-complete} problem.
-          \pause
-    \item The rest of this talk is about how to construct such functions
+    \item The rest of this talk is about how such functions can be found
           automatically.
@@
   \begin{definition}
-    A \alert{(compilation) rule} is a function that takes a \alert{formula} and returns a set of \alert{$(G, L)$} pairs, where
+    A \alert{(compilation) rule} is a function that takes a \alert{formula} and
+    returns a set of \structure{$(G, L)$} pairs, where
     \begin{itemize}
-    \item \alert{$G$} is a (possibly incomplete) FCG,
-    \item and \alert{$L$} is a list of formulas.
+      \item \structure{$G$} is a (possibly incomplete) FCG,
+      \item and \structure{$L$} is a list of formulas.
     \end{itemize}
   \end{definition}
-  \vfill The formulas in \alert{$L$} are then \alert{compiled}, and the
-  resulting FCGs are \alert{inserted} into \alert{$G$} according to a \alert{set
-    order}.
+  \vfill The formulas in \structure{$L$} are then \alert{compiled}, and the
+  resulting FCGs are \alert{inserted} into \structure{$G$} according to a
+  \alert{set order}.
 \end{frame}
@@
     ({\color{color1} \forall x, y \in \Omega\text{. }x=y}) \land \label{eq:1} \tag{{\color{color1} 1}} \\
-    ({\color{color2} \forall x \in \Gamma\text{. }\forall y, z \in \Delta\text{. }\texttt{P}(x, y) \land \texttt{P}(x, z) \Rightarrow y=z}) \land \label{eq:2} \tag{{\color{color2} 2}} \\
-    ({\color{color2} \forall w, x \in \Gamma\text{. }\forall y \in \Delta\text{. }\texttt{P}(w, y) \land \texttt{P}(x, y) \Rightarrow w=x}) \label{eq:3} \tag{{\color{color2} 3}}
+    ({\color{color2} \forall x \in \Gamma\text{. }\forall y, z \in \Delta\text{. }\pP{}(x, y) \land \pP{}(x, z) \Rightarrow y=z}) \land \label{eq:2} \tag{{\color{color2} 2}} \\
+    ({\color{color2} \forall w, x \in \Gamma\text{. }\forall y \in \Delta\text{. }\pP{}(w, y) \land \pP{}(x, y) \Rightarrow w=x}) \label{eq:3} \tag{{\color{color2} 3}}
   \end{gather}
   \pause
-  The independence compilation rule returns one \alert{(G, L)} pair:
+  The independence compilation rule returns one \structure{$(G, L)$} pair:
   \[
     G =
-  \begin{tikzpicture}[edge from parent/.style={draw,-Latex},baseline=(current bounding box.center)]
+    \begin{tikzpicture}[edge from parent/.style={draw,-latex},baseline=(current bounding box.center)]
     \node[draw,circle] {$\land$}
@@
   \]
+  %% Later, both \structure{$G$} and \structure{$L$} are incorporated into a larger \alert{search state}.
 \end{frame}
@@
       \centering
-      \begin{tikzpicture}[every node/.style={draw,ellipse},edge from parent/.style={draw,-Latex},sibling distance=10mm,level distance=10mm]
+      \begin{tikzpicture}[every node/.style={draw,ellipse},edge from parent/.style={draw,-latex},sibling distance=10mm,level distance=10mm]
         \node[fill=red!50, fill on=<1>] (dr) {}
@@
             }}};
-        \draw[-Latex, bend right,alt=<3>{red}{black}] (ref) to (dr);
+        \draw[-latex, bend right,alt=<3>{red}{black}] (ref) to (dr);
       \end{tikzpicture}
@@
             \[
-              \forall x \in \Gamma\text{. }\forall y, z \in \Delta\text{. }y \ne z \Rightarrow \neg \texttt{P}(x, y) \lor \neg \texttt{P}(x, z)
+              \forall x \in \Gamma\text{. }\forall y, z \in \Delta\text{. }y \ne z \Rightarrow \neg \pP{}(x, y) \lor \neg \pP{}(x, z)
             \]
-            Output formula (with a new constant \alert{$c \in \Gamma$}):
+            Output formula (with a new constant \structure{$c \in \Gamma$}):
             \begin{gather*}
-              \forall y, z \in \Delta\text{. }y \ne z \Rightarrow \neg \texttt{P}(\alert{c}, y) \lor \neg \texttt{P}(\alert{c}, z) \\
+              \forall y, z \in \Delta\text{. }y \ne z \Rightarrow \neg \pP{}(\alert{c}, y) \lor \neg \pP{}(\alert{c}, z) \\
               \begin{multlined}
                 \forall x \in \Gamma\text{. }\forall y, z \in \Delta\text{. }\alert{x \ne c} \land y \ne z \Rightarrow \\
-                \neg \texttt{P}(x, y) \lor \neg \texttt{P}(x, z)
+                \neg \pP{}(x, y) \lor \neg \pP{}(x, z)
               \end{multlined}
@@
             %% \end{tikzpicture}
+            %% Here, domain recursion is applied to domain \structure{$M$}. It could similarly be applied to \structure{$N$} as well.
           \end{example}
@@
           \begin{example}
-            Input formula (with a constant \alert{$c \in \Gamma$}):
+            Input formula (with a constant \structure{$c \in \Gamma$}):
             \begin{gather*}
@@
                 \forall x \in \alert{\Gamma}\text{. }\forall y, z \in \Delta\text{. }\alert{x \ne c} \land y \ne z \Rightarrow \\
-                \neg \texttt{P}(x, y) \lor \neg \texttt{P}(x, z)
+                \neg \pP{}(x, y) \lor \neg \pP{}(x, z)
               \end{multlined} \\
@@
                 \forall w,x \in \alert{\Gamma}\text{. }\forall y \in \Delta\text{. }\alert{w \ne c} \land \alert{x \ne c} \land w \ne x \Rightarrow \\
-                \neg \texttt{P}(w, y) \lor \neg \texttt{P}(x, y)
+                \neg \pP{}(w, y) \lor \neg \pP{}(x, y)
               \end{multlined}
             \end{gather*}
-            Output formula (with a new domain \alert{$\Gamma' \coloneqq \Gamma \setminus \{\, c \,\}$}):
+            Output formula (with a new domain \structure{$\Gamma' \coloneqq \Gamma \setminus \{\, c \,\}$}):
             \begin{gather*}
-              \forall x \in \alert{\Gamma'}\text{. }\forall y, z \in \Delta\text{. }y \ne z \Rightarrow \neg \texttt{P}(x, y) \lor \neg \texttt{P}(x, z) \\
-              \forall w,x \in \alert{\Gamma'}\text{. }\forall y \in \Delta\text{. }w \ne x \Rightarrow \neg \texttt{P}(w, y) \lor \neg \texttt{P}(x, y)
+              \forall x \in \alert{\Gamma'}\text{. }\forall y, z \in \Delta\text{. }y \ne z \Rightarrow \neg \pP{}(x, y) \lor \neg \pP{}(x, z) \\
+              \forall w,x \in \alert{\Gamma'}\text{. }\forall y \in \Delta\text{. }w \ne x \Rightarrow \neg \pP{}(w, y) \lor \neg \pP{}(x, y)
             \end{gather*}
@@
           \end{block}
-          \begin{block}{Outline}
+          \begin{block}{Rough Outline}
             \begin{enumerate}
@@
               \item Extend each such bijection to a map between sets of domains.
-              \item If the bijection makes the clauses equivalent, and the
-                    domain map is compatible with previous domain maps, move on
-                    to another pair of clauses.
+              \item If the bijection makes the clauses equal, and the domain map
+                    is compatible with previous domain maps, move on to another
+                    pair of clauses.
             \end{enumerate}
@@
 \end{frame}
-
-% an example on partial injection (i.e., bipartite matching) counting
-\begin{frame}{How These Rules Fit Together (1/5)}
-  \begin{tikzpicture}[overlay,remember picture]
-    \node[draw,rounded rectangle,fill=color2!50,anchor=center,above=0.5cm] at (current page.center) (rules) {Generalised domain recursion};
-    \node[above=of rules] (before) {$\begin{gathered}
-        \forall x \in \alert{\Gamma}\text{. }\forall y, z \in \Delta\text{. }y \ne z \Rightarrow \neg\pP(x, y) \lor \neg\pP(x, z)\\
-        \forall w,x \in \alert{\Gamma}\text{. }\forall y \in \Delta\text{. }w \ne x \Rightarrow \neg\pP(w, y) \lor \neg\pP(x, y)
-      \end{gathered}$};
-    \node[below=of rules] (after) {$\begin{gathered}
-        \forall y, z \in \Delta\text{. }y \ne z \Rightarrow \neg\pP(\alert{c}, y) \lor \neg\pP(\alert{c}, z)\\
-        \forall x \in \Gamma\text{. }\forall y,z \in \Delta\text{. }y \ne z \land \alert{x \ne c} \Rightarrow \neg\pP(x, y) \lor \neg\pP(x, z)\\
-        \forall x \in \Gamma\text{. }\forall y \in \Delta\text{. }\alert{x \ne c} \Rightarrow \neg\pP(\alert{c}, y) \lor \neg\pP(x, y)\\
-        \forall w \in \Gamma\text{. }\forall y \in \Delta\text{. }\alert{w \ne c} \Rightarrow \neg\pP(w, y) \lor \neg\pP(\alert{c}, y)\\
-        \forall w,x \in \Gamma\text{. }\forall y \in \Delta\text{. }w \ne x \land \alert{w \ne c} \land \alert{x \ne c} \Rightarrow \neg\pP(w, y) \lor \neg\pP(x, y)
-      \end{gathered}$};
-    \begin{scope}[on background layer]
-      \node[anchor=north,fill=greenish,minimum width=11.1cm,minimum height=0.7cm] at (before.north) {};
-      \node[anchor=south,fill=blueish,minimum width=11.1cm,minimum height=0.7cm] at (before.south) {};
-      \node[anchor=north,fill=greenish,minimum width=11.1cm,minimum height=1.3cm] at (after.north) {};
-      \node[anchor=south,fill=blueish,minimum width=11.1cm,minimum height=2cm] at (after.south) {};
-    \end{scope}
-    \draw[-Latex,color=color2,ultra thick,shorten <=0.1cm,shorten >=0.1cm] (before) -- (rules);
-    \draw[-Latex,color=color2,ultra thick,shorten <=0.1cm,shorten >=0.1cm] (rules) -- (after);
-  \end{tikzpicture}
-\end{frame}
-
-\begin{frame}{How These Rules Fit Together (2/5)}
-  \begin{tikzpicture}[overlay,remember picture]
-    \node[draw,rounded rectangle,fill=color2!50,anchor=center,below=1cm] at (current page.center) (rules) {Atom counting and unit propagation};
-    \node[above=of rules] (before) {$\begin{gathered}
-        \forall y, z \in \Delta\text{. }y \ne z \Rightarrow \neg\pP(\alert{c}, y) \lor \neg\pP(\alert{c}, z)\\
-        \forall x \in \Gamma\text{. }\forall y,z \in \Delta\text{. }y \ne z \land \alert{x \ne c} \Rightarrow \neg\pP(x, y) \lor \neg\pP(x, z)\\
-        \forall x \in \Gamma\text{. }\forall y \in \Delta\text{. }\alert{x \ne c} \Rightarrow \neg\pP(\alert{c}, y) \lor \neg\pP(x, y)\\
-        \forall w \in \Gamma\text{. }\forall y \in \Delta\text{. }\alert{w \ne c} \Rightarrow \neg\pP(w, y) \lor \neg\pP(\alert{c}, y)\\
-        \forall w,x \in \Gamma\text{. }\forall y \in \Delta\text{. }w \ne x \land \alert{w \ne c} \land \alert{x \ne c} \Rightarrow \neg\pP(w, y) \lor \neg\pP(x, y)
-      \end{gathered}$};
-    \node[below=of rules] (after) {$\begin{gathered}
-        \forall y, z \in \alert{\Delta^{\top}}\text{. }y \ne z \Rightarrow \bot\\
-        \forall x \in \Gamma\text{. }\forall y, z \in \alert{\Delta^{\bot}}\text{. }y \ne z \land x \ne c \Rightarrow \neg\pP(x, y) \lor \neg\pP(x, z) \\
-        \forall w, x \in \Gamma\text{. }\forall y \in \alert{\Delta^{\bot}}\text{. }w \ne x \land w \ne c \land x \ne c \Rightarrow \neg\pP(w, y) \lor \neg\pP(x, y)
-      \end{gathered}$};
-    \draw[-Latex,color=color2,ultra thick,shorten <=0.1cm,shorten >=0.1cm] (before) -- (rules);
-    \draw[-Latex,color=color2,ultra thick,shorten <=0.1cm,shorten >=0.1cm] (rules) -- (after);
-    \draw[-Latex,color=color2,ultra thick,shorten <=0.1cm,shorten >=0.1cm] (rules) -- (after);
-  \end{tikzpicture}
-\end{frame}
-% NOTE: need to explain how atom counting splits the domain
-
-\begin{frame}{How These Rules Fit Together (3/5)}
-  \begin{tikzpicture}[overlay,remember picture]
-    \node[draw,rounded rectangle,fill=color2!50,anchor=center] at (current page.center) (rules) {Constraint removal};
-    \node[above=of rules] (before) {$\begin{gathered}
-        \forall y, z \in \Delta^{\top}\text{. }y \ne z \Rightarrow \bot\\
-        \forall x \in \alert{\Gamma}\text{. }\forall y, z \in \Delta^{\bot}\text{. }y \ne z \land \alert{x \ne c} \Rightarrow \neg\pP(x, y) \lor \neg\pP(x, z) \\
-        \forall w, x \in \alert{\Gamma}\text{. }\forall y \in \Delta^{\bot}\text{. }w \ne x \land \alert{w \ne c} \land \alert{x \ne c} \Rightarrow \neg\pP(w, y) \lor \neg\pP(x, y)
-      \end{gathered}$};
-    \node[below=of rules] (after) {$\begin{gathered}
-        \forall y, z \in \Delta^{\top}\text{. }y \ne z \Rightarrow \bot\\
-        \forall x \in \alert{\Gamma'}\text{. }\forall y, z \in \Delta^{\bot}\text{. }y \ne z \Rightarrow \neg\pP(x, y) \lor \neg\pP(x, z) \\
-        \forall w, x \in \alert{\Gamma'}\text{. }\forall y \in \Delta^{\bot}\text{. }w \ne x \Rightarrow \neg\pP(w, y) \lor \neg\pP(x, y)
-      \end{gathered}$};
-    \draw[-Latex,color=color2,ultra thick,shorten <=0.1cm,shorten >=0.1cm] (before) -- (rules);
-    \draw[-Latex,color=color2,ultra thick,shorten <=0.1cm,shorten >=0.1cm] (rules) -- (after);
-  \end{tikzpicture}
-\end{frame}
-
-\begin{frame}{How These Rules Fit Together (4/5)}
-  \begin{tikzpicture}[overlay,remember picture]
-    \node[draw,rounded rectangle,fill=color2!50,anchor=center] at (current page.center) (rules) {Independence};
-    \node[above=of rules] (before) {$\begin{gathered}
-        \forall y, z \in \alert{\Delta^{\top}}\text{. }y \ne z \Rightarrow \bot\\
-        \forall x \in \alert{\Gamma'}\text{. }\forall y, z \in \alert{\Delta^{\bot}}\text{. }y \ne z \Rightarrow \neg\pP(x, y) \lor \neg\pP(x, z) \\
-        \forall w, x \in \alert{\Gamma'}\text{. }\forall y \in \alert{\Delta^{\bot}}\text{. }w \ne x \Rightarrow \neg\pP(w, y) \lor \neg\pP(x, y)
-      \end{gathered}$};
-    \node[below left=of rules,fill=greenish] (after1) {$\forall y, z \in \alert{\Delta^{\top}}\text{. }y \ne z \Rightarrow \bot$};
-    \node[below right=2cm and -4cm of rules,fill=blueish] (after2) {$\begin{gathered}
-        \forall x \in \alert{\Gamma'}\text{. }\forall y, z \in \alert{\Delta^{\bot}}\text{. }y \ne z \Rightarrow \neg\pP(x, y) \lor \neg\pP(x, z) \\
-        \forall w, x \in \alert{\Gamma'}\text{. }\forall y \in \alert{\Delta^{\bot}}\text{. }w \ne x \Rightarrow \neg\pP(w, y) \lor \neg\pP(x, y)
-      \end{gathered}$};
-    \begin{scope}[on background layer]
-      \node[anchor=north,fill=greenish,minimum width=9cm,minimum height=0.7cm] at (before.north) {};
-      \node[anchor=south,fill=blueish,minimum width=9cm,minimum height=1.3cm] at (before.south) {};
-    \end{scope}
-    \draw[-Latex,color=color2,ultra thick,shorten <=0.1cm,shorten >=0.1cm] (before) -- (rules);
-    \draw[-Latex,color=color2,ultra thick,shorten <=0.1cm,shorten >=0.1cm] (rules) -- (after1);
-    \draw[-Latex,color=color2,ultra thick,shorten <=0.1cm,shorten >=0.1cm] (rules) -- (after2);
-  \end{tikzpicture}
-\end{frame}
-
-\begin{frame}{How These Rules Fit Together (5/5): Recursion}
-  \centering
-  \begin{tikzpicture}[overlay,remember picture]
-    \node[anchor=center,above=0.5cm] at (current page.center) (equal) {\rotatebox{90}{\textcolor{color2}{\Huge$=$}}};
-    \node[below=0.5cm of equal] (after1) {$\begin{gathered}
-        \forall x \in \alert{\Gamma}\text{. }\forall y, z \in \alert{\Delta}\text{. }y \ne z \Rightarrow \neg\pP(x, y) \lor \neg\pP(x, z)\\
-        \forall w,x \in \alert{\Gamma}\text{. }\forall y \in \alert{\Delta}\text{. }w \ne x \Rightarrow \neg\pP(w, y) \lor \neg\pP(x, y)
-      \end{gathered}$};
-    \node[above=0.5cm of equal] (foo) {$\begin{gathered}
-        \forall x \in \alert{\Gamma'}\text{. }\forall y, z \in \alert{\Delta^{\bot}}\text{. }y \ne z \Rightarrow \neg\pP(x, y) \lor \neg\pP(x, z) \\
-        \forall w, x \in \alert{\Gamma'}\text{. }\forall y \in \alert{\Delta^{\bot}}\text{. }w \ne x \Rightarrow \neg\pP(w, y) \lor \neg\pP(x, y)
-      \end{gathered}$};
-    \node[below=0.5cm of after1] (plus) {\textcolor{color2}{\Huge$+$}};
-    \node[below=0.5cm of plus] {$\{\, \alert{\Gamma} \mapsto \alert{\Gamma'}, \alert{\Delta} \mapsto \alert{\Delta^{\bot}} \,\}$};
-  \end{tikzpicture}
-\end{frame}
+% We're still creating a vertex in a graph with one outgoing edge.
 
@@
 %%     \item \structure{$G$} is an FCG (or \texttt{null}),
-%%     \item \structure{$C$} is a compilation cache that maps integers to sets of pairs $(\phi, v)$, where $\phi$ is a formula, and $v$ is a node of $G$ (which is used to identify opportunities for recursion),
+%%     \item \structure{$C$} is a compilation cache that maps integers to sets of pairs $(\phi, v)$, where $\phi$ is a formula, and $v$ is a vertex of $G$ (which is used to identify opportunities for recursion),
 %%     \item and \structure{$L$} is a list of formulas (that are yet to be compiled). (Note that the order is crucial!)
@@
 \begin{frame}{Resulting Improvements to Counting Functions}
-  Let \alert{$\Gamma$} and \alert{$\Delta$} be two sets with cardinalities
-  \alert{$|\Gamma| = m$} and \alert{$|\Delta| = n$}.
+  Let \structure{$\Gamma$} and \structure{$\Delta$} be two sets with
+  cardinalities \structure{$|\Gamma| = m$} and \structure{$|\Delta| = n$}.
 
-  Our new rules enable Crane to efficiently count \alert{$\Gamma \to \Delta$}
-  functions such as:
+  Our new compilation rules enables us to count \structure{$\Gamma \to \Delta$}
+  functions such as: \vspace{1em}
   \begin{itemize}
-    \item injections in \alert{$\Theta(mn)$} time
+    \item injections in \structure{$\Theta(mn)$} time
           \begin{itemize}
-      \item by hand: \alert{$\Theta(m)$}
+            \item by hand: \structure{$\Theta(m)$}
           \end{itemize}
-    \item partial injections in \alert{$\Theta(mn)$} time
+    \item partial injections in \structure{$\Theta(mn)$} time
           \begin{itemize}
-      \item by hand: \alert{$\Theta({\min\{\, m, n \,\}}^2)$}
+            \item by hand: \structure{$\Theta({\min\{\, m, n \,\}}^2)$}
           \end{itemize}
-    \item bijections in \alert{$\Theta(m)$} time
+          \item bijections in \structure{$\Theta(m)$} time
           \begin{itemize}
-      \item \alert{optimal!}%\pause
-      %\item In comparison, FastWFOMC scales as \alert{$\Omega(m^{4})$}.
+            \item \alert{optimal!}
           \end{itemize}
-  \end{itemize}
-  % \begin{tikzpicture}[remember picture,overlay]
-  %   \node[draw,rectangle,color=gray] at ([xshift=-3cm]current page.east) {\includegraphics{plot}};
-  % \end{tikzpicture}
-\end{frame}
-
-{ % all template changes are local to this group.
-    \setbeamertemplate{navigation symbols}{}
-    \begin{frame}<article:0>[plain]
-        \begin{tikzpicture}[remember picture,overlay]
-            \node[at=(current page.center)] {
-                \includegraphics[keepaspectratio, width=\paperwidth]{hubble.jpg}
-            };
-            \node[shift=({-0.7, 0.1})] at (current page.south east) {\tiny \textcolor{lightgray}{Source: NASA}};
-        \end{tikzpicture}
-     \end{frame}
-}
-
-\begin{frame}{What Have We Learned?}
-  \begin{itemize}
-    \item Knowledge compilation can build \alert{graphs with cycles}.
-    \item Graphs (as well as circuits) define \alert{functions}.
-    \item Cycles can represent \alert{recursive calls}, including:
-    \begin{itemize}
-      \item mutual recursion
-      \item and function calls as complex as \alert{$f(n-k-2)$}.
-    \end{itemize}
-    \item Recursion helps us solve counting problems that were \alert{previously
-          beyond the reach of FOMC}\@.
-    \item In some cases, even if a polynomial-time solution is already known,
-          Crane is able to find \alert{more efficient solutions}, with a lower
-          degree polynomial.
   \end{itemize}
@@
 
-{ % all template changes are local to this group.
-    \setbeamertemplate{navigation symbols}{}
-    \begin{frame}<article:0>[plain]
-        \begin{tikzpicture}[remember picture,overlay]
-            \node[at=(current page.center)] {
-                \includegraphics[keepaspectratio, height=\paperheight]{future.jpg}
-            };
-        \end{tikzpicture}
-     \end{frame}
-}
-
-\begin{frame}[fragile]{Beyond First-Order Logic}
-  \vspace{0.5cm}
-  \hspace*{0.25\linewidth}
-  \begin{tikzcd}[remember picture]
-    |[alias=WMI]|\WMI{} & \WFOMI{} & \\
-    |[alias=WMC]|\#\SAT{}/\WMC{} \arrow[u] \ar[d] \ar[r] & \textup{(W)FOMC} \arrow[u] \ar[d] \ar[r,dashed] & \raisebox{-0.4\height}{\includegraphics[width=0.1\linewidth]{question-mark.jpg}} \\
-    |[alias=PBP]|\AMC{}, \pbp{} & |[alias=SP]|\SPPP{} &
-  \end{tikzcd}
-  \begin{tikzpicture}[overlay,remember picture]
-    \begin{scope}[transform canvas={xshift=-3em}]
-      \draw[->,draw=gray] ($(WMC)+(0,0.1)$)--($(WMI)+(0,0.5)$) node[midway,left] {\textcolor{gray}{$\sum \to \int$}};
-      \draw[->,draw=gray] ($(WMC)-(0,0.1)$)--($(PBP)-(0,0.5)$) node[midway,left] {\textcolor{gray}{Generalising weights}};
-    \end{scope}
-    \begin{scope}[transform canvas={yshift=-2em}]
-      \draw[->,draw=gray] ($(PBP)-(1,0)$)--($(SP)+(1,0)$) node[midway,below] {\textcolor{gray}{From propositional to first-order logic}};
-    \end{scope}
-  \end{tikzpicture}
-  \vfill
-  \vspace{1.5cm}
-  What kind of logic is needed to succinctly describe, e.g.,
+\begin{frame}{Summary \& Future Work}
+  \begin{block}{Summary}
+    The circuits hitherto used for FOMC become more powerful with:
     \begin{itemize}
-    \item $f(n) = f(f(n-1))$
-    \item or the Fibonacci sequence?
+    \item cycles,
+    \item generalised domain recursion,
+    \item and some more new compilation rules that support domain recursion.
     \end{itemize}
-\end{frame}
-% impossibility results as well (finite model theory)
-
-\begin{frame}{Algebraic Solutions to Parameterised Problems (1/2)}
+  \end{block}
+  \begin{block}{Future Work}
     \begin{itemize}
-    \item Suppose we have a Markov logic network that models the probability
-          \alert{$P$} that some system will fail.
-    \item Here:
+    \item Automate:
       \begin{itemize}
-      \item domain sizes describe the numbers of various components,
-      \item and weights express probabilities that:
+      \item simplifying the definitions of functions,
+      \item finding all base cases.
+      \end{itemize}
+    \item Open questions:
       \begin{itemize}
-        \item some component fails,
-        \item or some combination of failures leads to another failure.
+      \item What kind of \alert{sequences} are computable in this way?
+      \item Would using a \alert{different logic} extend the capabilities of FOMC further?
       \end{itemize}
     \end{itemize}
-    \item Crane can express \alert{$P$} as a function of the domain sizes and
-          weights.
-  \end{itemize}
-\end{frame}
-
-\begin{frame}{Algebraic Solutions to Parameterised Problems (2/2)}
-  With the help of a computer algebra system, we can then:
-  \begin{itemize}
-    \item determine how \alert{$P$} scales with the number of users,
-    \item find combinations of domain sizes that keep \alert{$P$} below some
-          threshold,
-    \item find ranges of weights that keep \alert{$P$} sufficiently small across
-          a range of domain size values.
-  \end{itemize}
-  \pause
-  \vfill
-  \centering
-  \begin{tikzpicture}
-    \node[draw] (a) {Reasoning with \alert{functions}};
-    \node[right=0.5cm of a] (b) {\Huge\textcolor{color2}{$>$}};
-    \node[draw,right=0.5cm of b] (c) {Reasoning with \alert{numbers}};
-  \end{tikzpicture}
+  \end{block}
 \end{frame}
